### 2023-05-26 notes/2loopNLSM.tex
Moved notes into a subfolder.  Fixed typos in gitignore.

\documentclass[12pt,letter]{article}
\usepackage{jheppub}
\usepackage{amsmath,amssymb}
\usepackage[dvipsnames]{xcolor}
%\usepackage{hyperref}
\usepackage{xspace}
\usepackage{ifdraft}
\usepackage{epstopdf}
\usepackage{slashed}
\usepackage{diagbox}
\usepackage{colortbl}
\usepackage{bbold}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{stackengine}
\def\RA{\rlap{\scalebox{1.6}{$\leftrightarrow$}}}
\def\DA{\smash{\bclap{\scalebox{1.6}{$\downarrow$}}}}
\def\mystrut{\rule[-2ex]{0ex}{6ex}}

\usepackage{tikz-feynman} 
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={hred},
    citecolor={hgreen},
    urlcolor={hblue}
}
\tikzset{graviton/.style={decorate, decoration={snake, amplitude=.4mm, segment length=1.5mm, pre length=.5mm, post length=.5mm}, double}}
\tikzfeynmanset{compat=1.1.0}
\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
\usetikzlibrary{external}  
          %% Load the `external` library
\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
\tikzexternalize[                     %% Activate externalization
  prefix=images/,                    %% Avoid cluttering the directory
 system call={                       %% Use lualatex in system call
    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
  },
]

\definecolor{jaxoblue}{HTML}{0086FF}

\newcommand{\cP}{\rm{cov.}\pi}

\newcommand{\ie}{i.e.~}
\newcommand{\eg}{e.g.~}
\usepackage{xspace}
\newcommand{\Poincare}{Poincar\'e\xspace}

\newcommand{\cC}{g} % -- Crossing Count symbol.

\newcommand{\nkmc}[1][k]{N$^{#1}$MC\xspace}

\def\taua{{{\rm t}}}
\def\bartaua{{{\bar {\rm t}}}}

\definecolor{cutred}{RGB}{219,56,49}
\definecolor{hgreen}{RGB}{25,176,146}
\definecolor{hgreen1}{RGB}{175,230,175}
\definecolor{hblue}{RGB}{52,152,219}
\definecolor{hbluedark}{RGB}{36, 106, 160}
\definecolor{hblue1}{RGB}{255,255,166}
\definecolor{hred}{RGB}{216,83,117}
\definecolor{hreddark}{RGB}{151, 58, 81}
\definecolor{hred1}{RGB}{255,155,155}
\definecolor{cutred}{RGB}{219,56,49}
\definecolor{hgrey4}{RGB}{75,75,75}
\definecolor{hgrey5}{RGB}{50,50,50}
\definecolor{hgrey3}{RGB}{100,100,100}
\definecolor{hgrey}{RGB}{125,125,125}
\definecolor{hgrey2}{RGB}{125,125,125}
\definecolor{hgrey1}{RGB}{150,150,150}
\definecolor{hgrey0}{RGB}{175,175,175}
\definecolor{darkgreen}{RGB}{59,126,108}

\newcommand{\simplebox}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1,1){2};
\vertex (a2) at (1,-1){4};
\vertex (a3) at (1,1){3};
\vertex (a4) at (-1,-1){1};
\vertex (mid3) at (.5,.5);
\vertex (mid4) at (.5,-.5);
\vertex (mid5) at (-.5,.5);
\vertex (mid6) at (-.5,-.5);
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid3) --[ultra thick,](mid4),
(mid5) --[ultra thick,](mid6),
(mid5) --[ultra thick,](mid3),
(mid4) --[ultra thick,](mid6),
};
\end{feynman}
\end{tikzpicture}
}
}

\newcommand{\xBox}{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){2};
\vertex (a2) at (1.5,-1){4};
\vertex (a3) at (1.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5);
\vertex (mid4) at (1,-.5);
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5);
\vertex (mid7) at (-.5,0) {};
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,](mid6),
(mid3) --[ultra thick,](mid2),
(mid1) --[ultra thick,](mid4),
(mid5) --[ultra thick,](mid7),
(mid7) --[ultra thick,](mid1),
(mid2) --[ultra thick,](mid6),
(mid5) --[ultra thick,](mid2),
(mid3) --[ultra thick,](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

\newcommand{\dBox}[7]{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){2};
\vertex (a2) at (1.5,-1){4};
\vertex (a3) at (1.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5) ;
\vertex (mid4) at (1,-.5) ;
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5) ;
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,#1](mid2),
(mid3) --[ultra thick,#2](mid2),
(mid1) --[ultra thick,#3](mid6),
(mid1) --[ultra thick,#4](mid4),
(mid5) --[ultra thick,#5](mid2),
(mid5) --[ultra thick,#6](mid6),
(mid3) --[ultra thick,#7](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

\newcommand{\dBoxR}[7]{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){2};
\vertex (a2) at (1.5,-1){4};
\vertex (a3) at (1.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5) ;
\vertex (mid4) at (1,-.5) ;
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5) ;
\diagram{
(a4) --[ultra thick,](mid6),
(a3) --[ultra thick,hred](mid3),
(a2) --[ultra thick,hred](mid4),
(a1) --[ultra thick,](mid5),
(mid1) --[ultra thick,#1](mid2),
(mid3) --[ultra thick,#2](mid2),
(mid1) --[ultra thick,#3](mid6),
(mid1) --[ultra thick,#4](mid4),
(mid5) --[ultra thick,#5](mid2),
(mid5) --[ultra thick,#6](mid6),
(mid3) --[ultra thick,#7](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

\newcommand{\dBoxL}[7]{ {
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
\begin{feynman}
\vertex (a1) at (-1.5,1){2};
\vertex (a2) at (1.5,-1){4};
\vertex (a3) at (1.5,1){3};
\vertex (a4) at (-1.5,-1){1};
\vertex (mid1) at (0,-.5);
\vertex (mid2) at (0,.5);
\vertex (mid3) at (1,.5) ;
\vertex (mid4) at (1,-.5) ;
\vertex (mid5) at (-1,.5);
\vertex (mid6) at (-1,-.5) ;
\diagram{
(a4) --[ultra thick,hred](mid6),
(a3) --[ultra thick,](mid3),
(a2) --[ultra thick,](mid4),
(a1) --[ultra thick,hred](mid5),
(mid1) --[ultra thick,#1](mid2),
(mid3) --[ultra thick,#2](mid2),
(mid1) --[ultra thick,#3](mid6),
(mid1) --[ultra thick,#4](mid4),
(mid5) --[ultra thick,#5](mid2),
(mid5) --[ultra thick,#6](mid6),
(mid3) --[ultra thick,#7](mid4),
};
\end{feynman}
\end{tikzpicture}
}
}

\DeclareMathOperator{\cut}{\mathcal{C}}

 \def\draftnote#1{{\color{red}\it #1}} 
\iffalse \def\draftnote#1{{\color{red}\it}} \fi

\def\sect#1{section~\ref{#1}}
\def\Fig#1{fig.~{\ref{#1}}}
\def\Fig#1{Fig.~{\ref{#1}}}
\def\Figs#1#2{figs.~{\ref{#1}} and {\ref{#2}}}
\def\Figs#1#2{Figs.~{\ref{#1}} and {\ref{#2}}}

\def\tab#1{table~{\ref{#1}}}
\def\Tab#1{Table~{\ref{#1}}}
\def\tabs#1#2{tables~{\ref{#1}} and {\ref{#2}}}
\def\Tabs#1#2{TablesnFigs.~{\ref{#1}} and {\ref{#2}}}

\def\spa#1.#2{\left\langle#1\,#2\right\rangle}
\def\spb#1.#2{\left[#1\,#2\right]}
\def\spash#1.#2{\spa{\smash{#1}}.{\smash{#2}}}
\def\spbsh#1.#2{\spb{\smash{#1}}.{\smash{#2}}}
\def\sand#1.#2.#3{%
\left\langle\smash{#1}{\vphantom1}^{-}\right|{#2}%
\left|\smash{#3}{\vphantom1}^{-}\right\rangle}
\def\sandpp#1.#2.#3{%
\left\langle\smash{#1}{\vphantom1}^{+}\right|{#2}%
\left|\smash{#3}{\vphantom1}^{+}\right\rangle}
\def\sandpm#1.#2.#3{%
\left\langle\smash{#1}{\vphantom1}^{+}\right|{#2}%
\left|\smash{#3}{\vphantom1}^{-}\right\rangle}
\def\sandmp#1.#2.#3{%
\left\langle\smash{#1}{\vphantom1}^{-}\right|{#2}%
\left|\smash{#3}{\vphantom1}^{+}\right\rangle}
\def\Shift#1#2{{[#1,#2\rangle}}
\def\twoloop{{2 \mbox{-} \rm loop}}

\def\tree{{\rm tree}}
\def\pol{\varepsilon}
\def\Tr{\, {\rm Tr}}
\def\tr{\, {\rm tr}}
\def\eps{\varepsilon}
\def\e{\varepsilon}
\def\ep{\varepsilon}
\def\SYM{MSYM}
\def\nn{\nonumber}
\def\sec#1{section~\ref{#1}}
\def\eqn#1{eq.~(\ref{#1})}
\def\Eqn#1{Equation~(\ref{#1})}
\def\eqns#1#2{eqs.~(\ref{#1}) and~(\ref{#2})}
\def\Eqns#1#2{Eqs.~(\ref{#1}) and~(\ref{#2})}
\def\Figref#1{Fig.~\ref{#1}}
\def\secref#1{section~\ref{#1}}
\def\Neqfour{{{\cal N}=4}}
\def\NeqFour{{{\cal N}=4}}
\def\Neqeight{{{\cal N}=8}}
\def\NeqEight{{{\cal N}=8}}
\def\NeqOne{{{\cal N}=1}}
\def\Fact{{\cal F}}
\def\f{\widetilde f}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}
\def\Ksl{{\s K}}
\def\ksl{\s{k}}
\def\Perm{{\cal P}}
\def\M{{\cal M}}
\def\ve{\varepsilon}
\def\tlambda{{\tilde\lambda}}
\def\MHVbar{$\overline{\hbox{MHV}}$}
\def\NMHVbar{$\overline{\hbox{NMHV}}$}
\def\P{{\rm P}}
\def\NHP{{\rm NHP}}
\def\mud{\lambda}
\def\bowtie{{\rm bow\mbox{-}tie}}
\newcommand{\cred}{\bf \color{red}}
 \newcommand{\cblue}{\color{blue}}
 \definecolor{MattOrange}{rgb}{1.0,0.4,0.2}
\newcommand{\cob}{ \bf \color{MattOrange}}
\newcommand{\andd}{\ , \quad \text{and}  \quad}
\newcommand{\forr}{\ , \quad \text{for}  \quad}

\newcommand\citepls{{\bf\color{red}[[Cite Needed]]}}

\newcommand{\afour}{\ensuremath{A_4^{\text{tree}}}}
\definecolor{NUpurple}{RGB}{078,042,132}

\def\dj#1{{\color{NUpurple}\it \bf JJ: #1}}

\author[1]{Alex Edison,}
\author[1]{James Mangan,}
\author[1]{Nicolas H. Pavao}

\affiliation[1]{Department of Physics and Astronomy, Northwestern
  University, Evanston, Illinois 60208, USA}

\title{Color-dual NLSM multi-loop integrands}

\abstract{ For now, let's put the things we need to check/compute here in the abstract. 
\begin{itemize}
\item (1) Does our construction manifest all the cuts for the two-loop n-gon?
\item  (2) Is there a natural extension to 3-loop 
\item (3)  Is there a simple Feynman rule/ghost we can add to correct the one-loop n-gon of YZ theory
\item (4) Can we make our two-loop numerators functionally symmetric 
\item (5) What is the physics story here? Perturbative corrections to special Galilon, DBI for inflation? 
\item (6) What is the rule for cuts we don't care about? Like the weird snaking diagrams that James identified?
\item (7) How can bubble on external legs that are zero by IBP inform generalizations beyond pions?
\end{itemize}
}

  \newpage

\begin{document}
\maketitle
\flushbottom

\setstackgap{S}{6pt}
\setstackgap{L}{7pt}

\section{Introduction}\label{sec:intro} Some refs. \cite{BCJreview, Bern:2022wqg, Adamo:2022dcm,Bern:2012uf, Neq44np, GravityFour,Bjerrum-Bohr:2013iza,Edison:2020uzf,Edison:2022jln,Cheung2016prv,He:2017spx,OneTwoLoopPureYMBCJ, Mogull:2015adi, Bern:2015ooa, Geyer:2019hnn,Johansson:2017bfl,Chen:2019ywi,Chen:2021chy,Brandhuber:2021bsf,Cheung:2021zvb,Ben-Shahar:2021zww,Cheung:2022mix, Ben-Shahar:2022ixa,Cachazo:2014xea,Carrasco:2016ldy,Elvang:2020kuj,Bern:2007xj,Carrasco:2013ypa,Craig:2019zkf,Monteiro:2022nqt,Bern:2017tuc,Bern:2017rjw,Bern:2019isl,Goroff:1985sz,Bern:2013uka,Alishahiha:2004eh,Creminelli:2005hu,Fergusson:2008ra,Carrasco:2015pla,Carrasco:2015rva,Carrasco:2015uma,BICEP:2021xfz,Kallosh:2021mnu,Green:1982sw,Mafra:2016mcc,Broedel:2013tta,Carrasco:2016ygv,Azevedo:2018dgo,Anastasiou:2004vj,vonManteuffel:2012np,Smirnov:2014hma,vonManteuffel:2014ixa,Smirnov:2019qkx,Smirnov:2020quc,Usovitsch:2020jrk,Maierhofer:2018gpa,Carrasco:2019yyn,Carrasco:2021ptp,Chi:2021mio,Bonnefoy:2021qgu,Carrasco:2022lbm,Carrasco:2022sck,Pavao:2022kog,Chen:2022shl,Chen:2023dcx,Brown:2023srz,Carrasco:2022jxn,Caron-Huot:2016icg, Chiodaroli:2021eug,Cangemi:2022abk,Cangemi:2022bew,Geiser:2022exp,Cheung:2022mkw,Fonseca:2019yya,Hays:2018zze,Alioli:2022fng}
\section{Tree-level}
We begin with a review of the construction of NLSM numerators at tree-level. For this work we extend the tree-level construction of $Y\!Z$ model of Cheung and Hsien \cite{Cheung2016prv}. In this construction, the generators of the kinematic algebra can be expressed as follows
\be\label{eq:FeynmanRuleYYZ}
T^a_{ij}= i \varepsilon_a(p_i-p_j)
\ee
where momentum conservation requires
\be
p_a + p_i + p_j =0
\ee
The kinematic half-ladder diagrams then takes on the following concise definition:
\be
n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
\ee
Since there are on pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the chiral current algebra is manifestly cubic. Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom. They can be defined implicitly below:
\be
[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}
\ee
Given this definition, the Feynman rule associated with kinematic structure constant is simply:
\be\label{eq:FeynmanRuleXZZ}
i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c) 
\ee
where $p_{ab}=p_a+p_b$ and $\epsilon$ and $\bar{\epsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively. The on-shell state sum for the polarization vectors is simply:
\be
\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}
\ee
Notice that the vector state sum is gauge fixed since the $Y\,Z$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$. To recover NLSM amplitudes from this these kinematic structure constants at tree-level, we simply plug in the following on-shell polarizations for the $Z$ and $\bar{Z}$ particles:
\be\label{eq:onShellZStates}
\varepsilon^\mu_{(p)} = p^\mu \qquad \bar{\varepsilon}^\mu_{(p)} = \frac{q^\mu}{pq}
\ee
where $q^2=0$ is some null reference momentum. With this, we can define tree-level pion scattering in two equivalent ways:
\be
A^{\text{NLSM}} = A(...,Y,...,Y,...) = A(...,\bar{Z},...) 
\ee
where the ellipses denote additional on-shell $Z$-particles. Subject to a particular gauge choice, the kinematic numerators in latter definition for pion scattering is equivalent to those $J$-theory, first written down by Cheung and one of the authors \cite{Cheung:2021zvb}. In this paradigm, the on-shell $\bar{Z}$ state is equivalent to the root leg appearing in the color-dual $J$-theory numerators.

It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion. First we'll start with two $Y$ particles on legs 1 and 4. Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
\begin{align}
n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
\\
 n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
\end{align}
Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
\be\label{eq:NLSMYZ4point}
A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
\ee
Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration. Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free. This produces the following numerators:
\begin{align}
n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
\\
 n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
\end{align}
where we have defined the short hand notation:
\be
{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
\ee
Similarly, we find the following ordered amplitude when plugging in these numerators:
\be
A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
\ee
Plugging in the on-shell polarizatoin of the conjugate field in \eqn{eq:onShellZStates} produces precisely the desired result of \eqn{eq:NLSMYZ4point}. Indeed, this construction is valid to all orders at tree-level. There are only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut :
\begin{align}
A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
\\
&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
\end{align}
Now we are prepared to discuss the one-loop case. 
\section{One-loop}
At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles. Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.  Thus, $Y\!Z$ theory gives us the following one-loop $n$-gon numerator:
\be
N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+2\, (F^1F^2\cdots F^n)
\ee
where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops. Plugging in the Feynman rule of \eqn{eq:FeynmanRuleYYZ} and \eqn{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
\be
N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
\ee
and similarly so for the internal vector contribution:
\be
 (F^1F^2\cdots F^n) = (D-4)(l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
\ee
The dimension dependent factor essentially counts that number of internal vector states. While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM. However, the scalar contribution, that comes dressed with an overall factor $(D-4)$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality. We leave this as a direction of future work.

While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $Y\!Z$ loop alone gives us a desired expression for the $n$-gon. The important takeaway is that we now have a guess for the form of the off-shell three-point vertex that has a chance of manifesting the duality off-shell. The $n$-gon numerator above has scalar insertions of the following kinematic vertex:
\be
T^{a}_{LR} = k_a(l_L-l_{R}) = (l_L+l_{R}) (l_L-l_{R})  = l_L^2-l_{R}^2 
\ee
Given this structure, in the next section we will attempt to construct two-loop basis diagrams from these cubic vertex assignments and try to reverse engineer the particle content that produces these master numerators.

Before proceeding, we note a strange property of the $n$-gon numerator for the pions. In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs). However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble. The BEL diagram can be reconstructed from the $n$-gon as follows:
\be
N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
\ee
where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
\be
N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
\ee
Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
\be
\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
\ee
where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$. Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram. 
\section{Two-loop}
Let's start with a two-loop four-point example. At this order, the basis diagrams for color-dual representations are any two of the Jacobi triple, the double box, the penta-triangle or the cross-box. First we introduce a bit of shorthand notion:
\be
[LR] \equiv  l_L^2 -l_R^2 \qquad [M] \equiv  l_M^2
\ee
Now let's start with the double-box. Below we treat the color legs as $Y$ particles that will get dressed with factors of $[LR]$. Thus, we wish to manifest the following cut:
\be
N^{\text{2box}}_M\equiv \dBox{}{hred}{hred}{hred}{hred}{hred}{hred} = [12][23][34][45][56][61]
\ee
In addition, we want the following cuts to be simultaneously satisfied:
\be
N^{\text{2box}}_R\equiv \dBoxR{hred}{}{hred}{}{hred}{hred}{hred} = [61][12][27][76][4]^2
\ee
\be
N^{\text{2box}}_L\equiv \dBoxL{hred}{hred}{}{hred}{}{hred}{hred}=[45][57][73][34][1]^2
\ee
Where the middle cut takes $l_7^2\rightarrow 0$, the right cut takes $l_3^2,l_5^2\rightarrow 0$ and the left cut takes $l_2^2,l_6^2\rightarrow 0$. Applying these cuts to all the diagrams above, we obtain the following expressions:
\be
\text{Cut}_R(N^{\text{2box}}_M) = \Delta_R + N^{\text{2box}}_R \qquad \text{Cut}_L(N^{\text{2box}}_M) = \Delta_L + N^{\text{2box}}_L
\ee
However, we find that the remainder terms $\Delta_{L/R}$ are proportional to $l_7^2$, and thus vanish on the middle cut:
\be
\text{Cut}_M(\Delta_{L/R})  = 0
\ee
Similarly, applying the complement left/right cuts to the right/left remainder terms, we obtain a single kinematic function:
\be
\text{Cut}_L(\Delta_R) = \text{Cut}_R(\Delta_L) = \Delta_{LR}
\ee
Thus, the double box numerator that simultaneously manifests all of the cut contributing to NLSM are as follows:
\be
\boxed{N^{\text{NLSM}}_{\text{2box}} = N^{\text{2box}}_M - (\Delta_{L}+\Delta_{R})+\Delta_{LR}}
\ee
Applying the cut relations above, we find that this double box numerator factorizes to the desired expressions:
\be
\text{Cut}_{X}(N^{\text{NLSM}}_{\text{2box}} )= N^{\text{2box}}_{X}
\ee
The kinematic expressions obtained for the remainder functions are provided below:
\begin{align}
\Delta_L &= \frac{1}{2}[61][12]([27]+[67])[4]^2[7] 
\\
 \Delta_R &= \frac{1}{2}[34][45]([37]+[57])[1]^2[7]
 \\
\Delta_{LR}&= [1]^2[4]^2[7]^2
\end{align}
While these numerators are not functionally automorphic like the one-loop $n$-gon numerators, they do obey color-kinematics when evaluated on-shell and thus should be valid representations for double copy construction. 
\section{Discussion}\label{sec:Discussion}

\paragraph{Acknowledgments} The authors would like to thank ... for insightful conversations, related collaboration, and encouragement throughout the completion of this work. This work was supported by the DOE under contract DE-SC0015910 and by the Alfred P. Sloan Foundation. N.H.P. additionally acknowledges the Northwestern University Amplitudes and Insight group, the Department of Physics and Astronomy, and Weinberg College for their generous support.

\bibliographystyle{JHEP}
\bibliography{Refs_2loopNLSM}
\end{document}

### 2023-07-24 notes/2loopNLSM.tex

@@
 While these numerators are not functionally automorphic like the one-loop $n$-gon numerators, they do obey color-kinematics when evaluated on-shell and thus should be valid representations for double copy construction.
+
+\section{Notes}\label{sec:Notes}
+
+\begin{itemize}
+\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
+This observation is due to other people but an easy way to see it.
+ZM and 2D NLSM have the same EOM after a field redefinition.
+This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
+\item Forcing pions to match ZM in 2D does funny things.
+The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
+I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
+Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
+For 4pt tree, $z=2/3$ (I matched the half ladder).
+For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
+For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
+For 6pt tree, $z$ is 12/35 (I matched the half ladder).
+So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
+Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
+\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
+At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
+\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.
+\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
+The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
+I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
+\end{itemize}
+
 \section{Discussion}\label{sec:Discussion}

### 2023-07-25 mma/check-dc.m
Added Alex's double-copy cut check.

@@ -1,0 +1,301 @@
+(* ::Package:: *)
+
+<<AmpToolsM`
+<<AmpToolsM`MaschkeAll`
+<<AmpToolsM`BasisConstruction`
+
+
+<<AmpToolsM`CKDual`
+
+
+<<AmpToolsM`Integrands`
+
+
+(* ::Section:: *)
+(*Prep various Pion reps*)
+
+
+(* ::Subsection:: *)
+(*Actual Prep*)
+
+
+(* ::Subsubsection:: *)
+(*Diag Basis*)
+
+
+fourTwoDiags = SortBy[makeFullBasis[2,4,!tadpoleQ[#]&],{cutLevel[#]&,!planarQ[#]&,-Length/@minimalCycles[#]&}];
+
+
+fourTwoCB = makeCanonicalBasis[fourTwoDiags];
+
+
+loadNPointAnalytics[4];
+{bcjBasis,{unusedJ}} = Reap[prepareBCJBasis[fourTwoDiags],UNUSEDJACOBIS];
+
+
+(*{bcjBasisGen,{unusedJ}} = Reap[prepareBCJBasisSuperPos[fourTwoDiags],UNUSEDJACOBIS];*)
+
+
+n1Cuts = Select[generateCutDiagrams[fourTwoDiags,1],!tadpoleQ[#]&&idDangTrees[#]=={}&];
+n2Cuts = generateCutDiagrams[n1Cuts,1];
+
+
+(*makeISPans[gn_Integer,graph_List]:=Block[
+	{extK = getk[graph]},
+	Array[a[gn,#]&,Length[#]] . #&@Select[DeleteDuplicates[Flatten[Outer[Times
+	,Sequence@@((Join[P/@l/@Complement[#,extK],{Z[3],Z[4]}])&/@Abs[Select[graph,Length[#]>1&]])]]],And@@(NonNegative/@({2,2}-Exponent[#,{Z[3],Z[4]}]))&]
+]
+proposedDB = makeZBasis[bcjBasis[[1,1]],
+makeISPans[1,bcjBasis[[1,1]]]
+,ColorSignsQ->True
+];
+proposedPT = makeZBasis[bcjBasis[[2,1]],
+makeISPans[2,bcjBasis[[2,1]]]
+,ColorSignsQ->True
+];*)
+
+
+(* ::Subsubsection:: *)
+(*Initial load from James*)
+
+
[…]

### 2023-07-31 notes/2loopNLSM.tex
Who does what

@@
 
-\section{Introduction}\label{sec:intro} Some refs.
+\section{Introduction}
+
+\label{sec:intro} Some refs.
 \cite{BCJreview, Bern:2022wqg, Adamo:2022dcm,Bern:2012uf, Neq44np, GravityFour,Bjerrum-Bohr:2013iza,Edison:2020uzf,Edison:2022jln,Cheung2016prv,He:2017spx,OneTwoLoopPureYMBCJ, Mogull:2015adi, Bern:2015ooa, Geyer:2019hnn,Johansson:2017bfl,Chen:2019ywi,Chen:2021chy,Brandhuber:2021bsf,Cheung:2021zvb,Ben-Shahar:2021zww,Cheung:2022mix, Ben-Shahar:2022ixa,Cachazo:2014xea,Carrasco:2016ldy,Elvang:2020kuj,Bern:2007xj,Carrasco:2013ypa,Craig:2019zkf,Monteiro:2022nqt,Bern:2017tuc,Bern:2017rjw,Bern:2019isl,Goroff:1985sz,Bern:2013uka,Alishahiha:2004eh,Creminelli:2005hu,Fergusson:2008ra,Carrasco:2015pla,Carrasco:2015rva,Carrasco:2015uma,BICEP:2021xfz,Kallosh:2021mnu,Green:1982sw,Mafra:2016mcc,Broedel:2013tta,Carrasco:2016ygv,Azevedo:2018dgo,Anastasiou:2004vj,vonManteuffel:2012np,Smirnov:2014hma,vonManteuffel:2014ixa,Smirnov:2019qkx,Smirnov:2020quc,Usovitsch:2020jrk,Maierhofer:2018gpa,Carrasco:2019yyn,Carrasco:2021ptp,Chi:2021mio,Bonnefoy:2021qgu,Carrasco:2022lbm,Carrasco:2022sck,Pavao:2022kog,Chen:2022shl,Chen:2023dcx,Brown:2023srz,Carrasco:2022jxn,Caron-Huot:2016icg, Chiodaroli:2021eug,Cangemi:2022abk,Cangemi:2022bew,Geiser:2022exp,Cheung:2022mkw,Fonseca:2019yya,Hays:2018zze,Alioli:2022fng}
+
 \section{Tree-level}
+
+\subsection{YZ, j-theory, and ZM -- Nic and James}
+
+\subsection{Attempts in literature -- Nic}
+
 We begin with a review of the construction of NLSM numerators at tree-level.
@@
 Now we are prepared to discuss the one-loop case.
+
 \section{One-loop}
+
+\subsection{NLSM -- Nic}
+
+\subsection{BELs and integration zeros -- Nic}
+
 At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles.
@@
 Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
+
 \section{Two-loop}
+\subsection{Cut construction, graph sym, Jacobi -- James}
+
+\subsection{Pions -- James}
 Let's start with a two-loop four-point example.
@@
 
+\subsection{Matching to ZM -- James}
+
+\subsection{Double-copy -- Alex }
+\subsection{YM revisit -- Alex}
+
 \section{Notes}\label{sec:Notes}

### 2023-08-02 notes/2loopNLSM.tex
1-loop YZ reminder
Rearranged things, notes to self

@@
 \abstract{ For now, let's put the things we need to check/compute here in the abstract. 
-\begin{itemize}
-\item (1) Does our construction manifest all the cuts for the two-loop n-gon?
-\item  (2) Is there a natural extension to 3-loop 
-\item (3)  Is there a simple Feynman rule/ghost we can add to correct the one-loop n-gon of YZ theory
-\item (4) Can we make our two-loop numerators functionally symmetric 
-\item (5) What is the physics story here? Perturbative corrections to special Galilon, DBI for inflation? 
-\item (6) What is the rule for cuts we don't care about? Like the weird snaking diagrams that James identified?
-\item (7) How can bubble on external legs that are zero by IBP inform generalizations beyond pions?
-\end{itemize}
+\begin{enumerate}
+\item Does our construction manifest all the cuts for the two-loop n-gon?
+\item What is the physics story here? Perturbative corrections to special Galilon, DBI for inflation? 
+\item How can bubble on external legs that are zero by IBP inform generalizations beyond pions?
+\end{enumerate}
 }
@@
 
+Note from James:  I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.
+
 \subsection{BELs and integration zeros -- Nic}
@@
 \section{Two-loop}
-\subsection{Cut construction, graph sym, Jacobi -- James}
 
-\subsection{Pions -- James}
-Let's start with a two-loop four-point example.
-At this order, the basis diagrams for color-dual representations are any two of the Jacobi triple, the double box, the penta-triangle or the cross-box.
-First we introduce a bit of shorthand notion:
-\be
-[LR] \equiv  l_L^2 -l_R^2 \qquad [M] \equiv  l_M^2
-\ee
-Now let's start with the double-box. Below we treat the color legs as $Y$ particles that will get dressed with factors of $[LR]$. Thus, we wish to manifest the following cut:
-\be
-N^{\text{2box}}_M\equiv \dBox{}{hred}{hred}{hred}{hred}{hred}{hred} = [12][23][34][45][56][61]
-\ee
-In addition, we want the following cuts to be simultaneously satisfied:
-\be
-N^{\text{2box}}_R\equiv \dBoxR{hred}{}{hred}{}{hred}{hred}{hred} = [61][12][27][76][4]^2
-\ee
-\be
-N^{\text{2box}}_L\equiv \dBoxL{hred}{hred}{}{hred}{}{hred}{hred}=[45][57][73][34][1]^2
-\ee
-Where the middle cut takes $l_7^2\rightarrow 0$, the right cut takes $l_3^2,l_5^2\rightarrow 0$ and the left cut takes $l_2^2,l_6^2\rightarrow 0$.
-Applying these cuts to all the diagrams above, we obtain the following expressions:
-\be
-\text{Cut}_R(N^{\text{2box}}_M) = \Delta_R + N^{\text{2box}}_R \qquad \text{Cut}_L(N^{\text{2box}}_M) = \Delta_L + N^{\text{2box}}_L
-\ee
-However, we find that the remainder terms $\Delta_{L/R}$ are proportional to $l_7^2$, and thus vanish on the middle cut:
-\be
-\text{Cut}_M(\Delta_{L/R})  = 0
-\ee
-Similarly, applying the complement left/right cuts to the right/left remainder terms, we obtain a single kinematic function:
-\be
-\text{Cut}_L(\Delta_R) = \text{Cut}_R(\Delta_L) = \Delta_{LR}
-\ee
-Thus, the double box numerator that simultaneously manifests all of the cut contributing to NLSM are as follows:
-\be
-\boxed{N^{\text{NLSM}}_{\text{2box}} = N^{\text{2box}}_M - (\Delta_{L}+\Delta_{R})+\Delta_{LR}}
-\ee
-Applying the cut relations above, we find that this double box numerator factorizes to the desired expressions:
-\be
-\text{Cut}_{X}(N^{\text{NLSM}}_{\text{2box}} )= N^{\text{2box}}_{X}
-\ee
-The kinematic expressions obtained for the remainder functions are provided below:
-\begin{align}
-\Delta_L &= \frac{1}{2}[61][12]([27]+[67])[4]^2[7] 
-\\
- \Delta_R &= \frac{1}{2}[34][45]([37]+[57])[1]^2[7]
- \\
-\Delta_{LR}&= [1]^2[4]^2[7]^2
-\end{align}
-While these numerators are not functionally automorphic like the one-loop $n$-gon numerators, they do obey color-kinematics when evaluated on-shell and thus should be valid representations for double copy construction.
-
-\subsection{Matching to ZM -- James}
-
-\subsection{Double-copy -- Alex }
-\subsection{YM revisit -- Alex}
-
-\section{Notes}\label{sec:Notes}
-
+Notes to myself: 
 \begin{itemize}
@@
 
+\subsection{Cut construction, graph sym, Jacobi -- James}
+
+Color-dual integrands are typically generated by constructing an ansatz and then imposing various constraints.
+Color-kinematics duality requires writing the integrand in terms of cubic graphs.
+Any theory can be written this way by artificially inserting ratios of propagators (can blow up YM or NLSM).
+Obviously the ansatz must have the correct power counting and external states.
+We will take NLSM as our example theory but later we will discuss YM.
+Since pions are scalars the numerators will not carry any spinors or polarization vectors.
+Every vertex in NLSM scales as $k^2$ so, for example, the numerator of a cubic 2-loop diagram scales as $k^12$.
+There are three conditions that are imposed on the ansatz:  (1) the integrand must have the correct unitarity cuts, (2) numerators must respect graph symmetries, and (3) Jacobi relations amongst graphs must be satisfied.
+The integrand must be written in terms of cubic graphs in order to apply the Jacobi relations.
+This means that there are naively X cubic 4pt 2-loop diagrams.
+However, many of these diagrams are related by Jacobi identities.
+Give an example.
+Through repeated application of the Jacobi identities, all of the cubic diagrams can be written in terms of the double box and penta-triangle.
+The basis choice is not unique.
+For example, any pair of the double box, penta-triangle and crossed box would work.
+So you have to have two numerator ansatze, one for the double box and one for the crossed box.
+What we are describing here is global color-kinematics duality.
+It is possible to give each cubic graph its own numerator and then only impose Jacobi on the cuts (see ...).
+It is not always possible to achieve global CK, but when it is doable, it is typically much easier than doing Jacobi on the cuts because the latter requires far more ansatz parameters.
+Anyway, now the numerator of any diagram can be written in terms of the two basis numerators (double box and crossed box).
+This is part of imposing Jacobi.
+There are additional Jacobi relations that impose actual constraints on the ansatze, for example ASDF.
+We allow BEL graphs to have nonzero numerators since they do not contribute to physical unitarity cuts.
+Jacobi relations involving BEL graphs or tadpoles are simply not solved.
+
+Requiring numerators to respect their graph symmetries is very convenient but is not completely necessary in order to perform the double copy.
+At tree level, finding manifestly color dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
+Nonetheless, for a pure ansatz construction it is very reasonable to impose graph symmetries.
+Note that you impose that the numerator of \emph{every} graph respects its graph automorphisms.
+So the graph syms of the double box impose constraints, but, for example, the crossed box imposes constraints on the ansatz numerators too because the numerator of the crossed box can be written in terms of the two basis numerators.
+
+Finally we have to impose unitarity.
+We only do physical cuts, no aesthetic cuts.
+The two most important cuts for pions (or any EMU) are ...
+However there are other cuts that must be imposed as well.
+
+References for Jacobi, unitarity, etc.
+
+After you've imposed all of the essential stuff you get X free parameters...
+There is lots of generalized gauge freedom, clearly there's room to impose extra constraints.
+For N=4 the extra conditions are things like no triangles, strip off a factor of stAtree (which fails at 5-loops), manifest power counting, etc.
+The obvious choice here is to match to ZM
+There's one known theory that has manifest color-kinematics, manifest Bose sym, and NLSM power counting and that's ZM theory.
+
+\subsection{Pions -- James}
+
+\subsection{Matching to ZM -- James}
+
+\subsection{Double-copy -- Alex }
+\subsection{YM revisit -- Alex}
+
 \section{Discussion}\label{sec:Discussion}

### 2023-08-03 notes/2loopNLSM.tex
diagrams and background

--- 2023-07-31 notes/2loopNLSM.tex
@@
-\documentclass[12pt,letter]{article}
+\documentclass[11pt,letter]{article}
 \usepackage{jheppub}
@@
     colorlinks,
-    linkcolor={hred},
-    citecolor={hgreen},
-    urlcolor={hblue}
+    linkcolor={nhpRed},
+    citecolor={nhpBlue},
+    urlcolor={nhpBlue}
 }
-\tikzset{graviton/.style={decorate, decoration={snake, amplitude=.4mm, segment length=1.5mm, pre length=.5mm, post length=.5mm}, double}}
-\tikzfeynmanset{compat=1.1.0}
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-\usetikzlibrary{external}  
-          %% Load the `external` library
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-\tikzexternalize[                     %% Activate externalization
-  prefix=images/,                    %% Avoid cluttering the directory
- system call={                       %% Use lualatex in system call
-    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
-  },
-]
 
-\definecolor{jaxoblue}{HTML}{0086FF}
-
-\newcommand{\cP}{\rm{cov.}\pi}
-
-\newcommand{\ie}{i.e.~}
-\newcommand{\eg}{e.g.~}
-\usepackage{xspace}
-\newcommand{\Poincare}{Poincar\'e\xspace}
-
-\newcommand{\cC}{g} % -- Crossing Count symbol.
-
-\newcommand{\nkmc}[1][k]{N$^{#1}$MC\xspace}
-
-\def\taua{{{\rm t}}}
-\def\bartaua{{{\bar {\rm t}}}}
-
+\definecolor{nhpRed}{RGB}{161,0,0}
+\definecolor{nhp4}{RGB}{203, 4, 31}
+\definecolor{nhp3}{RGB}{244,99,30}
+\definecolor{nhp2}{RGB}{255,159,0}
+\definecolor{nhp1}{RGB}{48,152,152}
+\definecolor{nhpBlue}{RGB}{0,100,144}
 \definecolor{cutred}{RGB}{219,56,49}
@@
 
+\tikzset{graviton/.style={decorate, decoration={snake, amplitude=.4mm, segment length=1.5mm, pre length=.5mm, post length=.5mm}, double}}
+\tikzfeynmanset{compat=1.1.0}
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\usetikzlibrary{external}  
+          %% Load the `external` library
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\tikzexternalize[                     %% Activate externalization
+  prefix=images/,                    %% Avoid cluttering the directory
+ system call={                       %% Use lualatex in system call
+    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
+  },
+]
+\tikzfeynmanset{
+  fermion2/.style={
+    /tikz/postaction={
+      /tikz/decoration={
+        markings,
+        mark=at position 0.7 with {
+          \arrow{>[length=6pt, width=7pt]};
+        },
+      },
+      /tikz/decorate=true,
+    },
+  },
+}
+
+\definecolor{jaxoblue}{HTML}{0086FF}
+
+\newcommand{\cP}{\rm{cov.}\pi}
+
+\newcommand{\ie}{i.e.~}
+\newcommand{\eg}{e.g.~}
+\usepackage{xspace}
+\newcommand{\Poincare}{Poincar\'e\xspace}
+
+\newcommand{\cC}{g} % -- Crossing Count symbol.
+
+\newcommand{\nkmc}[1][k]{N$^{#1}$MC\xspace}
+
+\def\taua{{{\rm t}}}
+\def\bartaua{{{\bar {\rm t}}}}
+
 \newcommand{\simplebox}{ {
@@
 \vertex (a4) at (-1,-1){1};
-\vertex (mid3) at (.5,.5);
-\vertex (mid4) at (.5,-.5);
-\vertex (mid5) at (-.5,.5);
-\vertex (mid6) at (-.5,-.5);
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid3) --[ultra thick,](mid4),
-(mid5) --[ultra thick,](mid6),
-(mid5) --[ultra thick,](mid3),
-(mid4) --[ultra thick,](mid6),
+\vertex (mid3) at (.35,.35);
+\vertex (mid4) at (.35,-.35);
+\vertex (mid5) at (-.35,.35);
+\vertex (mid6) at (-.35,-.35);
+\diagram{(mid4) --[ultra thick,nhpRed,quarter right](mid3),
+(mid5) --[ultra thick,nhpRed,quarter right](mid6),
+(mid3) --[ultra thick,nhpRed,quarter right](mid5),
+(mid6) --[ultra thick,nhpRed,quarter right](mid4),
+(mid6) --[ultra thick,fermion2](a4),
+(mid3) --[ultra thick,fermion2](a3),
+(mid4) --[ultra thick,fermion2](a2),
+(mid5) --[ultra thick,fermion2](a1),
 };
@@
 
-\newcommand{\xBox}{ {
+\newcommand{\cubic}[7]{ {
 \begin{tikzpicture}[baseline=(current  bounding  box.center)]
 \begin{feynman}
-\vertex (a1) at (-1.5,1){2};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
+\vertex [dot, scale=2.6](mid1) at (0,0){};
+\vertex [dot, scale=2.6](mid2) at (0,0){};
+\vertex [dot, scale=2,#1](mid3) at (0,0){};
+\vertex (a1) at (0,1){3};
+\vertex (a2) at (.85,-.55){2};
+\vertex (a3) at (-.85,-.55){1};
 \diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid4),
+(mid1) --[ultra thick,#2,#3](a3),
+(mid1) --[ultra thick,#4,#5](a2),
+(a1) --[ultra thick,#6,#7](mid1),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+\newcommand{\Acubic}[7]{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (0,1){3};
+\vertex (a2) at (.85,-.55){2};
+\vertex (a3) at (-.85,-.55){1};
+\vertex [dot, scale=2.6](mid1) at (0,0){};
+\vertex [dot, scale=2.6](mid2) at (0,0){};
+\vertex [dot, scale=2,#1](mid3) at (0,0){};
+\diagram{
+(a3) --[ultra thick,#2,#3](mid1),
+(a2) --[ultra thick,#4,#5](mid1),
+(mid1) --[ultra thick,#6,#7](a1),
 };
@@
 
-\title{Color-dual NLSM multi-loop integrands}
+\title{Towards Globally Color-Dual All-Loop Integrands}
 
@@
 
-\section{Tree-level}
+\section{Review}
+The goal is this paper is to compute $D$-dimensional color-dual numerators beyond one-loop.
+To this end compute two-loop color-dual numerators for NLSM that globally satisfy the duality between color and kinematics and elucidate the color-dual structure expected of Yang-Mills at all-loop order.
+To set the stage, it is worth distinguishing between the algebraic properties of functionally symmetric kinematics that satisfy color-kinematics globally, and some of the other constructions that appear in the literature.
 
-\subsection{YZ, j-theory, and ZM -- Nic and James}
+In this work, we will consider three different types of cubic representations, that we define below: 
+\be
+\stackrel{\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}}{\text{Fundamental}}\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
+\ee
+In this review, we will present examples of this distinct kinematic representations that have appeared in the literature.
+Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing.
+The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \cite{}.
+We will briefly review the perturbative construction of this theory below.
+\subsection{ZM-theory} The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:
+\be
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) 
+\ee
+where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $ and $\epsilon_{\mu\nu}$ is the two-dimensional Levi-Civita symbol.
+Expanded out into spacetime components, the momentum space Feynman rule for this theory is simply:
+\be
+\langle ab\rangle \equiv p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle 
+\ee
+ From the interaction part of the Lagrangian, we can see that the three-point vertex is (1) functionally symmetric and (2) the kinematics are completely anti-symmetric: 
+\be
+\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
+\ee
+This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
+In addition to anti-symmetry, the cubic graphs will satisfy jacobi off-shell on any internal edge due to the delta function identity of 2D Levi-Civita symbols:
+\be
+\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle = \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c=0
+\ee
+Theories with this property are the creme de la creme of color-dual gauge theories as they trivially satisfy color-kinematic algebraic relations off-shell.
+This allows one to trivially promote the duality from tree-level to all-loop order by dressing each cubic vertex with its own kinematic structure constant.
 
-\subsection{Attempts in literature -- Nic}
+Later in this section we will show that the interaction vertex is precisely that belonging to self-dual Yang-Mills (SDYM) theory in light-cone gauge.
+However, as we'll see, the kinetic term for these two theories differ -- the SDYM kinetic term transmutes between the holomorphic field $\Phi$, and the anti-holomorphic field, $\bar{\Phi}$, while the ZM scalar leaves the kinematic sector untouched.
+this is a critical distinction between the two theories that has important consequences for their color-dual constructions at loop-level.
 
+While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization.
+Similar to the difficulties of renormalizing chiral fermions \cite{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
+\subsection{YZ-Theory}
+\be
+\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)
+\ee
+\be
+\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i \varepsilon_3 (p_1-p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
+\ee
 We begin with a review of the construction of NLSM numerators at tree-level.
@@
 \end{align}
+\subsection{J-theory}
+\be
+\mathcal{L}^{\text{J}} = \frac{1}{2}(\partial J)(\partial \bar{J}) +g f^{abc} \bar{J}_{\mu\nu}J^\mu J^\nu
+\ee
+where as above, $\bar{J}_{\mu\nu} = \partial_\mu J_\nu - \partial_\nu J_\mu$.
+Subject to the Lorenz gauge condition, $\partial_\mu J^\mu =0$, this Lagrangian produces precisely the EOM for J-theory needed for Berends-Giele recursion at tree-level:
+\be
+\partial^2 J^\mu - gf^{abc} J^\nu \partial_\nu J^\mu = 0 
+\ee
+As such, the single vertex in this theory is the same as for YZ theory: 
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
+\ee
+
+\be
+\mathcal{L}^{\text{SDYM}} = \frac{1}{2}(\partial \bar{\Phi} )^a(\partial  \Phi)^a +g f^{abc} \bar{\Phi} ^a (\partial_u \Phi)^b (\partial_v \Phi)^c
+\ee
+\be
+(\varepsilon^+_1 k_2) - (\varepsilon^+_2 k_1) = [12]\left(\frac{\langle 2 q\rangle}{\langle 1 q\rangle} + \frac{\langle 1 q\rangle}{\langle 2 q\rangle} \right) \sim [12]
+\ee
 Now we are prepared to discuss the one-loop case.
@@
 
+Note from James:  I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.
+\be
+\simplebox = (2 f_\pi^{-1})^4 (l_1 k_1)(l_2 k_2)(l_3 k_3)(l_4 k_4)
+\ee
+where we define sequential loop momenta on the $n$-gon as $l_{i+1}= l_i+k_i$. Given this, the $n$-gon permits a equivalent expression in terms of inverse propagators:
+\be
+\simplebox =f_\pi^{-4} [12][23][34][41]
+\ee
+Where we have define the antisymmetric kinematic variable, $[LR] = l_i^L - l_R^2$
 \subsection{BELs and integration zeros -- Nic}

### 2023-08-06 notes/2loopNLSM.tex
some ZM theory and SDYM additions

@@
 We will briefly review the perturbative construction of this theory below.
+\subsection{Self-dual Yang-Mills}
+\be
+\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
+\ee
+To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
+\be\label{SDcon}
+F_{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
+\ee
+where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength.
+Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
+\be
+u = t+x,\quad v=t-x, \quad w = y+iz
+\ee
+which gives the following expression for the invariant line element:
+\be
+ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
+\ee
+Applying this coordinate transformation to the self-dual condition of \eqn{SDcon}, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the 4D self-dual condition:
+\be
+A_w = 0\,, \qquad \partial_u A_v = \partial_w A_{\bar{w}}\,.
+\ee
+The second equation implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom, which we call $\Psi$.
+This constraint is immediately satisfied with the following definition of the gauge field:
+\be
+A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
+\ee
+Expanding out the equations of motion for the Yang-Mills Lagrangian, yields the following expression in terms of the gauge fields:
+\be
+D^\mu F^{\mu\nu} =0\qquad  \Rightarrow\qquad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
+\ee
+Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
+\be
+\mathcal{L}^{\text{SDYM}} = \frac{1}{2}(\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
+\ee
 \subsection{ZM-theory} The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:

### 2023-08-15 notes/2loopNLSM.tex
Added a gitignore to the notes.  Starting on the YM discussion.

@@
 \def\dj#1{{\color{NUpurple}\it \bf JJ: #1}}
+
+%Comment commands
+\newcommand{\ace}[1]{\textcolor{darkgreen}{\textbf{AE:}{#1}}}
 
@@
 \subsection{Double-copy -- Alex }
+
+\begin{itemize}
+\item  ``Most important'' check of Jacobi -- imposes ``diff'' invariance in the DC numerators
+\item Match against cuts from \cite{Carrasco:2023qgz}: double copy
+  with N=0 \cite{Bern:2015ooa}, N=4, itself
+  \item Whip up a non-jacobi N=0 or $\pi$ to highlight double copy success?
+\end{itemize}
+
 \subsection{YM revisit -- Alex}
+Transition paragraph.....
+
+As part of attemtping to construct a color-kinematics dual
+representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
+Davies, and Nohle (BDN) lay out the following core assumptions for
+integrand numerators (in addition to obeying some form of the
+kinematic Jacobi relations) \cite{Bern:2015ooa}
+\begin{enumerate}
+\item Locality: Diagram ``numerators'' are polynomials in momenta and
+  polarizations, \eg the diagrams only have poles given by the
+  propagators of the diagrams. \emph{We explore a minor breaking of this assumption}
+\item Power-counting: The maximum power of the loop momenta in the
+  numerator is boudned by Feynman-gauge Feynman rules.  \emph{We
+    explore breaking this assumption}.
+\item Cubic diagrams: The only diagrams with nonzero numerators are
+  those with strictly cubic vertices.  This is generally a requirement
+  to properly define the kinematic Jacobi relations.
+\item Relabeling : The diagram numerators are only a function of the
+  diagram's topology and labeling
+\item Symmetries: The diagram numerators are invariant under the
+  automorphisms of the diagrams \emph{including signs that compensate
+    for color-factor sign changes}
+\item Unitarity cuts: The cuts of the ansatz must reproduce the
+  physical unitarity cuts of the theory.
+\end{enumerate}
+They demonstrated that the above assumptions are incompatible with an
+off-shell solution to the kinematic Jacobi relations.  Here, we
+explore two violations of these core assumptions.
+
+First, we analyze the power-counting assumption.  In our labeling of
+the two loop Jacobi-basis diagrams, shown in \ace{Figure out fig}, we
+find that the power counting bound proposed by Bern, Davies, and Nohle
+leads to an initial ansatz with XX terms in the double-box, and YY
+terms for the penta-triangle.  However, recent work by Ben-Shahar,
+Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
+  good examples?} demonstrates that constructing Feynman rules that
+produce manifestly color-dual numerators for the NMHV sector of
+Yang--Mills requires introducing additional auxiliary fields,
+including higher-spin modes, which could shift the expected power
+counting in non-trivial ways.  We therefore attempt to find an
+off-shell color-dual Yang--Mills representation in which all power
+counting restrictions are lifted.
+
+Without power counting restrictions, both the double-box and the
+penta-triangle ansatz have an initial ansatz with 10,010 terms each.
+Imposing diagram automorphisms on the two basis diagrams, we reduce
+the number of terms to XX.  Gauge invariance on support of the maximal
+cuts of the basis diagrams further reduces the remaining freedom to
+YY.  The power-counting restriction of BDN would reduce this count to
+ZZ.  In the original BDN work, they imposed three spanning generalized
+unitarity cuts, shown in [].  Instead of directly imposing the
+spanning cuts, we proceed with the relaxed version of the method of
+maximal cuts used above in the pion construction [\ace{is James going
+  to talk about something along this line in the pions section?}].  We
+find that even with the completely generic ansatz, the representation
+fails to satisfy the next-to-next-to-maximal cut shown in [].
+Notably, imposing the BDN power-counting constraints additionally
+causes a discrepancy with the N$^2$-max cuts show in [].
+
+\begin{itemize}
+\item Recap assumptions of \cite{Bern:2015ooa}
+\item Going beyond ``Feynman-type counting'' $\to$ 10010 initial
+  ansatz.  Compare post-(sym+GI) on BCJ basis.
+\item Discuss which cuts still fail.  Double check these statements
+  \item Attempt at non-local.  Still have problems with cuts+syms+jacobi
+\end{itemize}
 

### 2023-08-15 notes/2loopNLSM.tex
Improved NLSM 2-loop discussion

--- 2023-08-06 notes/2loopNLSM.tex
@@
 \tikzfeynmanset{compat=1.1.0}
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-\usetikzlibrary{external}  
-          %% Load the `external` library
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-\tikzexternalize[                     %% Activate externalization
-  prefix=images/,                    %% Avoid cluttering the directory
- system call={                       %% Use lualatex in system call
-    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
-  },
-]
+%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+%\usetikzlibrary{external}  
+%          %% Load the `external` library
+%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+%\tikzexternalize[                     %% Activate externalization
+%  prefix=images/,                    %% Avoid cluttering the directory
+% system call={                       %% Use lualatex in system call
+%    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
+%  },
+%]
 \tikzfeynmanset{
@@
 \def\bartaua{{{\bar {\rm t}}}}
+
+%%% Jacobi 1 %%%
+
+\newcommand{\JacobiOneDoubleBox}{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-1.5,1){4};
+\vertex (a2) at (1.5,-1){2};
+\vertex (a3) at (1.5,1){3};
+\vertex (a4) at (-1.5,-1){1};
+\vertex (mid1) at (0,-.5);
+\vertex (mid2) at (0,.5);
+\vertex (mid3) at (1,.5) ;
+\vertex (mid4) at (1,-.5) ;
+\vertex (mid5) at (-1,.5);
+\vertex (mid6) at (-1,-.5) ;
+\diagram{
+(a4) --[ultra thick,](mid6),
+(a3) --[ultra thick,](mid3),
+(a2) --[ultra thick,](mid4),
+(a1) --[ultra thick,](mid5),
+(mid1) --[ultra thick,](mid2),
+(mid3) --[ultra thick,](mid2),
+(mid1) --[ultra thick,](mid6),
+(mid1) --[ultra thick,](mid4),
+(mid5) --[ultra thick,red](mid2),
+(mid5) --[ultra thick,](mid6),
+(mid3) --[ultra thick,](mid4),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+\newcommand{\JacobiOneCrossedBox}{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-1.5,1){4};
+\vertex (a2) at (1.5,-1){2};
+\vertex (a3) at (1.5,1){3};
+\vertex (a4) at (-1.5,-1){1};
+\vertex (mid1) at (0,-.5);
+\vertex (mid2) at (0,.5);
+\vertex (mid3) at (1,.5);
+\vertex (mid4) at (1,-.5);
+\vertex (mid5) at (-1,.5);
+\vertex (mid6) at (-1,-.5);
+\vertex (mid7) at (-.5,0) {};
+\diagram{
+(a4) --[ultra thick,](mid6),
+(a3) --[ultra thick,](mid3),
+(a2) --[ultra thick,](mid4),
+(a1) --[ultra thick,](mid5),
+(mid1) --[ultra thick,](mid6),
+(mid3) --[ultra thick,](mid2),
+(mid1) --[ultra thick,](mid4),
+(mid5) --[ultra thick,](mid7),
+(mid7) --[ultra thick,](mid1),
+(mid2) --[ultra thick,](mid6),
+(mid5) --[ultra thick,red](mid2),
+(mid3) --[ultra thick,](mid4),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+\newcommand{\JacobiOnePentaTriangle}{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-1.5,1){4};
+\vertex (a2) at (.5,-1){2};
+\vertex (a3) at (.5,1){3};
+\vertex (a4) at (-1.5,-1){1};
+\vertex (mid1) at (-.5,-.5);
+\vertex (mid2) at (-1,0);
+\vertex (mid3) at (0,.5) ;
+\vertex (mid4) at (0,-.5) ;
+\vertex (mid5) at (-1,.5);
+\vertex (mid6) at (-1,-.5) ;
+\diagram{
+(a4) --[ultra thick,](mid6),
+(a3) --[ultra thick,](mid3),
+(a2) --[ultra thick,](mid4),
+(a1) --[ultra thick,](mid5),
+(mid1) --[ultra thick,](mid2),
+(mid6) --[ultra thick,](mid2),
+(mid1) --[ultra thick,](mid6),
+(mid1) --[ultra thick,](mid4),
+(mid5) --[ultra thick,](mid3),
+(mid5) --[ultra thick,red](mid2),
+(mid3) --[ultra thick,](mid4),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+%%% Jacobi 1 end %%%
+
+%%% Jacobi 2 start %%%
+
+\newcommand{\JacobiTwoCrossedBoxOne}{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-1.5,1){2};
+\vertex (a2) at (1.5,-1){4};
+\vertex (a3) at (1.5,1){3};
+\vertex (a4) at (-1.5,-1){1};
+\vertex (mid1) at (0,-.5);
+\vertex (mid2) at (0,.5);
+\vertex (mid3) at (1,.5);
+\vertex (mid4) at (1,-.5);
+\vertex (mid5) at (-1,.5);
+\vertex (mid6) at (-1,-.5);
+\vertex (mid7) at (-.5,0) {};
+\diagram{
+(a4) --[ultra thick,](mid6),
+(a3) --[ultra thick,](mid3),
+(a2) --[ultra thick,](mid4),
+(a1) --[ultra thick,](mid5),
+(mid1) --[ultra thick,](mid6),
+(mid3) --[ultra thick,](mid2),
+(mid1) --[ultra thick,red](mid4),
+(mid5) --[ultra thick,](mid7),
+(mid7) --[ultra thick,](mid1),
+(mid2) --[ultra thick,](mid6),
+(mid5) --[ultra thick,](mid2),
+(mid3) --[ultra thick,](mid4),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+\newcommand{\JacobiTwoCrossedBoxTwo}{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-1.5,1){3};
+\vertex (a2) at (1.5,-1){4};
+\vertex (a3) at (1.5,1){1};
+\vertex (a4) at (-1.5,-1){2};
+\vertex (mid1) at (0,-.5);
+\vertex (mid2) at (0,.5);
+\vertex (mid3) at (1,.5);
+\vertex (mid4) at (1,-.5);
+\vertex (mid5) at (-1,.5);
+\vertex (mid6) at (-1,-.5);
+\vertex (mid7) at (-.5,0) {};
+\diagram{
+(a4) --[ultra thick,](mid6),
+(a3) --[ultra thick,](mid3),
+(a2) --[ultra thick,](mid4),
+(a1) --[ultra thick,](mid5),
+(mid1) --[ultra thick,](mid6),
+(mid3) --[ultra thick,](mid2),
+(mid1) --[ultra thick,red](mid4),
+(mid5) --[ultra thick,](mid7),
+(mid7) --[ultra thick,](mid1),
+(mid2) --[ultra thick,](mid6),
+(mid5) --[ultra thick,](mid2),
+(mid3) --[ultra thick,](mid4),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+\newcommand{\JacobiTwoCrossedBoxThree}{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-1.5,1){1};
+\vertex (a2) at (1.5,-1){4};
+\vertex (a3) at (1.5,1){2};
+\vertex (a4) at (-1.5,-1){3};
+\vertex (mid1) at (0,-.5);
+\vertex (mid2) at (0,.5);
+\vertex (mid3) at (1,.5);
+\vertex (mid4) at (1,-.5);
+\vertex (mid5) at (-1,.5);
+\vertex (mid6) at (-1,-.5);
+\vertex (mid7) at (-.5,0) {};
+\diagram{
+(a4) --[ultra thick,](mid6),
+(a3) --[ultra thick,](mid3),
+(a2) --[ultra thick,](mid4),
+(a1) --[ultra thick,](mid5),
+(mid1) --[ultra thick,](mid6),
+(mid3) --[ultra thick,](mid2),
+(mid1) --[ultra thick,red](mid4),
+(mid5) --[ultra thick,](mid7),
+(mid7) --[ultra thick,](mid1),
+(mid2) --[ultra thick,](mid6),
+(mid5) --[ultra thick,](mid2),
+(mid3) --[ultra thick,](mid4),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+%%% Jacobi 2 end %%%
 
@@
 \diagram{
-(a4) --[ultra thick,](mid6),
+(a4) --[ultra thick](mid6),
 (a3) --[ultra thick,](mid3),
@@
 \def\dj#1{{\color{NUpurple}\it \bf JJ: #1}}
+
+\newcommand{\draftnoteJM}[1]{\textbf{\color{blue}[#1]}}
 
@@
 \be
-\mathcal{L}^{\text{J}} = \frac{1}{2}(\partial J)(\partial \bar{J}) +g f^{abc} \bar{J}_{\mu\nu}J^\mu J^\nu
+\mathcal{L}^{\text{J}} = \frac{1}{2}\partial_\mu J_\nu \bar{J}^{\mu\nu} +g f^{abc} \bar{J}_{\mu\nu}J^\mu J^\nu
 \ee
@@
 
-Note from James:  I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.
+\draftnoteJM{I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.}
+
 \be
@@
 
-Notes to myself: 
+\subsection{Notes to self}
 \begin{itemize}
+\item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
+\item Are you sure that the SDYM EOM doesn't come from just $F=\epsilon F$?  If $A=\partial \Phi$ then $F$ has the right number of derivatives to give the SDYM EOM but $DF$ has too many.
+\item I believe the j-theory Lagrangian does not lead to the correct EOM as currently written.
+\item Write Lagrangian for j-theory and reiterate the argument about why you know it's pions.
+Reiterate connection to ZM (dualize j and integrate in phi).
+Should probably mention CS somewhere.
+Point out that all of the theories that come from have CK are really some version of YM where you (1) impose some condition like F=0 or some other condition on the field strength and (2) you impose Lorenz gauge.
+\item Explain why you need to take a certain portion of the YZ numerator to get the right answer.
+Basically you can't have a vector particle circle the loop -- NLSM is a scalar theory so only scalar DOF should actually live in cuts.
+If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
+\item Reiterate that the (tree) amplitudes of CS and SDYM are zero.
 \item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
@@
 Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
+\item Explain how matching to ZM is a little silly.
+Check that NLSM and ZM numerator agree on cuts.
+Can't do that or else it becomes subtle.
+Only well defined object is numerator.
 \item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
@@
 I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
+\item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
 \end{itemize}
 
-\subsection{Cut construction, graph sym, Jacobi -- James}
+\subsection{Pions -- James}
 
-Color-dual integrands are typically generated by constructing an ansatz and then imposing various constraints.
-Color-kinematics duality requires writing the integrand in terms of cubic graphs.
-Any theory can be written this way by artificially inserting ratios of propagators (can blow up YM or NLSM).
-Obviously the ansatz must have the correct power counting and external states.
-We will take NLSM as our example theory but later we will discuss YM.
+As we have seen, it is possible to coerce tree numerators into 1-loop numerators at any multiplicity for pions.
+However, these methods cannot be reapplied to generate 2-loop numerators, which begs the question ``is it possible to find globally color-dual numerators beyond 1-loop''.
+By ``global'' we mean that color-kinematics duality is satisfied in any kinematic configuration of the integrand.
+This is a much more stringent condition than absolutely necessary.
+There is reason to believe (cite Zvi et al) that global numerators cannot always be found.
+One resolution to the issue is to only demand color-kinematics duality on the unitarity cuts of the integrand, i.e., in specific kinematic limits.
+Enforcing Jacobi on the cuts is enough to ensure that the squared integrand will correctly cut to gravity (or whatever the squared theory might be).
+When a globally color-dual numerator cannot be found, another alternative explored in the literature is to increase the size of the numerator ansatz by enlarging the numerator from a polynomial to a rational function with spurious singularities (cite Donal et al).
+When global color-kinematics fails, the hope is that it can be restored by enlarging the size of the ansatz, either by giving the numerator of each graph its own ansatz (first option described) or by promoting the numerator to a non-local function (second option described).
+Note that a theory whose Lagrangian has color-kinematics duality would naturally produce a globally color-dual integrand so the quest for a global numerator is closely related to the existence of a Lagrangian exhibiting color-kinematics duality.
+We will begin by tackling the issue of a global 4pt 2-loop numerator for NLSM before moving on to YM.
+Two-loop color-dual integrands for pure YM have been investigated before but only for a limited ansatz that manifests locality (cite Zvi et al paper).
+
+Aside from a few special theories (cite blah), color-dual integrands are constructed from an ansatz.
+Color-kinematics duality is stated in terms of cubic graphs so the first step is to express in the integrand in terms of such graphs.
+Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and bubble on external leg (BEL) graphs.
+It is always possible to express an integrand in terms of cubic graphs, even for an even valency theory like NLSM, by multiplying and dividing the integrand by factors of inverse propagators.
+Next, the ansatz must have the correct power counting and external states.
 Since pions are scalars the numerators will not carry any spinors or polarization vectors.
-Every vertex in NLSM scales as $k^2$ so, for example, the numerator of a cubic 2-loop diagram scales as $k^12$.
-There are three conditions that are imposed on the ansatz:  (1) the integrand must have the correct unitarity cuts, (2) numerators must respect graph symmetries, and (3) Jacobi relations amongst graphs must be satisfied.
-The integrand must be written in terms of cubic graphs in order to apply the Jacobi relations.
-This means that there are naively X cubic 4pt 2-loop diagrams.
-However, many of these diagrams are related by Jacobi identities.
-Give an example.
-Through repeated application of the Jacobi identities, all of the cubic diagrams can be written in terms of the double box and penta-triangle.
-The basis choice is not unique.
-For example, any pair of the double box, penta-triangle and crossed box would work.
-So you have to have two numerator ansatze, one for the double box and one for the crossed box.
-What we are describing here is global color-kinematics duality.
-It is possible to give each cubic graph its own numerator and then only impose Jacobi on the cuts (see ...).
-It is not always possible to achieve global CK, but when it is doable, it is typically much easier than doing Jacobi on the cuts because the latter requires far more ansatz parameters.
-Anyway, now the numerator of any diagram can be written in terms of the two basis numerators (double box and crossed box).
-This is part of imposing Jacobi.
-There are additional Jacobi relations that impose actual constraints on the ansatze, for example ASDF.
-We allow BEL graphs to have nonzero numerators since they do not contribute to physical unitarity cuts.
-Jacobi relations involving BEL graphs or tadpoles are simply not solved.
+Every vertex in NLSM scales as $k^2$ so, for example, the numerator of a cubic 4pt 2-loop diagram scales as $k^{12}$ so there are 8,008 independent dot products of momenta at this mass dimension.
+The numerator is assumed to be manifestly local but one approach to finding color-dual numerators is to relax manifest locality, see (...) for more details.
+After zeroth order considerations like power counting, there are three conditions that are imposed on the ansatz: (1) Jacobi relations amongst graphs must be satisfied, (2) numerators must respect graph symmetries, and (3) the integrand must have the correct unitarity cuts.
 
-Requiring numerators to respect their graph symmetries is very convenient but is not completely necessary in order to perform the double copy.
+\subsubsection{Jacobi relations}
+
+Jacobi relations are the heart of color-kinematics duality.
+The color factors in an integrand obey a set of Jacobi identities.
+Color-kinematics duality states that there exists a way of writing the kinematic numerators of the integrand so that they obey the same set of Jacobi identities.
+(Can trivially read off the adjoint color factors from a cubic graph.)
+So if any triplet of graphs is related by a Jacobi identity, so too must their numerators.
+Broadly speaking there are two kinds of Jacobi identities.
+The first kind relate graphs to a basis.
+For example, the double box, crossed box, and penta-triangle are related to each other as follows
+\be % [[11]]
+\label{eq:TwoLoopJacobiOne}
+\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0.
+\ee
+where the shared propagator is shown in red.
+Using this relation the crossed box can be written in terms of the other two.
+In this way, all of the 14 cubic 4pt 2-loop topologies can be written in terms of a basis of the double box and penta-triangle.
+(Any two of the double box, crossed box, and penta-triangle would have sufficed for a basis but the planar basis was chosen for simplicity.)
+Each of the two basis graphs receives its own numerator ansatz and the numerator of any other graph can be expressed in terms of these.
+As mentioned before, there are 8,008 linearly independent dot products of momenta of the required mass dimension so the total number of free parameters in the system is 16,016.
+As this is too many parameters for \texttt{Mathematica} to reasonably handle, we employ a custom solver suitable for the moderately dense systems appearing in this context.
+(Scalars might generate denser systems since ever dot product can interfere with every other unlike gauge theories which separate based on polarization structure, can cite Nic.)
+
+The second kind of Jacobi relations relate basis elements to themselves.
+For example, the crossed box numerator is related to itself via the following Jacobi relation
+\be % [[19]]
+\label{eq:TwoLoopJacobiTwo}
+\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
+\ee
+where the shared propagator is shown in red as before.
+Each of the crossed box numerators can be represented in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator ansatze.
+The first kind of Jacobi relations simplifies how many numerators require ansatze whereas the second kind of Jacobi relations place constraints on the remaining numerators.
+In principle there could be Jacobi relations involving tadpoles and BEL graphs, which would be subtle to handle.
+One option is to force the numerators of these graphs to zero.
+However, since these graphs will not contribute to physical unitarity cuts, we take a different approach.
+These graphs are allowed to have non-zero numerators but any Jacobi relations involving them are simply not imposed or solved.
+See (4 loop N=4 paper) for a discussion of BELs in the context of color-kinematics duality.
+
+In total, there are 21 Jacobi relations on the 14 cubic 4pt 2-loop graphs where, again, tadpole and BEL graphs are ignored.
+How many constraints fixed.
+
+\subsubsection{Graph symmetries}
+
+The second key constraint in an ansatz construction of color-dual numerators comes from graph symmetries.
+Every numerator is required to respect all of the symmetries (or automorphisms) of its associated graph.
+While it is very convenient to impose graph symmetries, it is not completely necessary in order to perform the double copy.
 At tree level, finding manifestly color dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
 Nonetheless, for a pure ansatz construction it is very reasonable to impose graph symmetries.
-Note that you impose that the numerator of \emph{every} graph respects its graph automorphisms.
-So the graph syms of the double box impose constraints, but, for example, the crossed box imposes constraints on the ansatz numerators too because the numerator of the crossed box can be written in terms of the two basis numerators.
+Note that the graph symmetry constraint is imposed on \emph{every} graph, not just the basis graphs.
+For example, the crossed box, as shown in \eqref{eq:TwoLoopJacobiTwo}, is unchanged upon reflection across the horizontal axis.
+Since the crossed box can be written in terms of the double box and penta-triangle, this imposes non-trivial constraints on the ansatz.
+
+Imposing graph symmetries on the ansatz further reduces the DOF to ...
+
+\subsubsection{Unitarity}
+
+The last key constraint is that the ansatz have the correct unitarity cuts, that is, that the integrand corresponds to the correct theory.
+The essence of generalized unitarity is that when internal lines are placed on-shell, the integrand should factorize into a product of on-shell tree amplitudes.
+Generalized unitarity has been reviewed in many places (cite...) so we will not belabor the details here.
+
+Could mention that it is certainly enough to check $(n-2)!$ color-ordered cuts but you could maybe get away with
 
@@
 The two most important cuts for pions (or any EMU) are ...
-However there are other cuts that must be imposed as well.
+These cuts are the only non-zero cuts.
+However there are other cuts that must be imposed as well like the max cut.
+
+Show the two interesting cuts, mention a max cut
+
+How many DOF left after imposing cuts
+
+Could bake in max cuts to slightly reduce ansatz size.
 
@@
 For N=4 the extra conditions are things like no triangles, strip off a factor of stAtree (which fails at 5-loops), manifest power counting, etc.
-The obvious choice here is to match to ZM
+The obvious choice here is to match to ZM.
 There's one known theory that has manifest color-kinematics, manifest Bose sym, and NLSM power counting and that's ZM theory.
 
-\subsection{Pions -- James}
+\subsubsection{Matching to ZM and loop power counting -- James}
 
-\subsection{Matching to ZM -- James}
+Can simplify the garbage
+
+ZM plagued by (suffers from) IR regulation issues.
+Only one of the two physical/meaningful cuts can be done in a non-subtle way.
+We're using ZM more as a tool to... -- We know ZM has the right kinematic structure to give CK in 2D so we're just matching onto that because we can.  ZM and NLSM can be different at quantum level.
 

### 2023-08-16 notes/2loopNLSM.tex
More changes to 2-loop NLSM

@@
 %%% Jacobi 2 end %%%
+
+%%% Graph sym start %%%
+
+\newcommand{\CrossedBoxGraphSym}{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-1.5,1){};
+\vertex (a2) at (1.5,-1){};
+\vertex (a3) at (1.5,1){};
+\vertex (a4) at (-1.5,-1){};
+\vertex (mid1) at (0,-.5);
+\vertex (mid2) at (0,.5);
+\vertex (mid3) at (1,.5);
+\vertex (mid4) at (1,-.5);
+\vertex (mid5) at (-1,.5);
+\vertex (mid6) at (-1,-.5);
+\vertex (mid7) at (-.5,0) {};
+\vertex (x1) at (-1.5,0);
+\vertex (x2) at (1.5,0);
+\diagram{
+(a4) --[ultra thick,](mid6),
+(a3) --[ultra thick,](mid3),
+(a2) --[ultra thick,](mid4),
+(a1) --[ultra thick,](mid5),
+(mid1) --[ultra thick,](mid6),
+(mid3) --[ultra thick,](mid2),
+(mid1) --[ultra thick,](mid4),
+(mid5) --[ultra thick,](mid7),
+(mid7) --[ultra thick,](mid1),
+(mid2) --[ultra thick,](mid6),
+(mid5) --[ultra thick,](mid2),
+(mid3) --[ultra thick,](mid4),
+(x1) --[ultra thick,dashed,blue](x2),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+%%% Graph sym end %%%
+
+%%% Unitarity cuts begin %%%
+
+\newcommand{\PhysicalCutOne}[4]{ {
+\begin{tikzpicture}[baseline=6]
+\begin{feynman}
+\vertex (a1) at (-1, 1) {#1};
+\vertex (a2) at (1, 1) {#2};
+\vertex [dot,scale=2](mid1) at (0.5,0.5){};
+\vertex [dot,scale=1.5,hgrey0](mid2) at (0.5,0.5){};
+\vertex [dot,scale=2](mid3) at (-0.5,0.5){};
+\vertex [dot,scale=1.5,hgrey0](mid4) at (-0.5,0.5){};
+\vertex [dot,scale=2](mid5) at (0,0){};
+\vertex [dot,scale=1.5,hgrey0](mid6) at (0,0){};
+\vertex (a3) at (-.5, -.5) {#3};
+\vertex (a4) at (.5, -.5) {#4};
+\diagram{
+(mid3) --[ ultra thick](a1),
+(mid1) --[ ultra thick](a2),
+(mid1) --[ ultra thick,out=120,in=60,min distance=0.1cm](mid3),
+(mid1) --[ ultra thick](mid3),
+
+(mid1) --[ ultra thick](mid5),
+(mid3) --[ ultra thick](mid5),
+
+(mid5) --[ ultra thick](a4),
+(mid5) --[ ultra thick,](a3)
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+\newcommand{\PhysicalCutTwo}[4]{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-.6, -0.6) {#1};
+\vertex (a2) at (-.6, 0.6) {#2};
+\vertex [dot,scale=2](mid1) at (0,0){};
+\vertex [dot,scale=1.5,hgrey0](mid2) at (0,0){};
+\vertex [dot,scale=2](mid3) at (.8,0){};
+\vertex [dot,scale=1.5,hgrey0](mid4) at (.8,0){};
+\vertex [dot,scale=2](mid5) at (1.6,0){};
+\vertex [dot,scale=1.5,hgrey0](mid6) at (1.6,0){};
+\vertex (a3) at (2.2, .6) {#3};
+\vertex (a4) at (2.2, -.6) {#4};
+\diagram{
+(mid1) --[ ultra thick,](a1),
+(mid1) --[ ultra thick,](a2),
+(mid1) --[ ultra thick,out=60,in=120,min distance=0.4cm](mid3),
+(mid1) --[ ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
+(mid3) --[ ultra thick,out=60,in=120,min distance=0.4cm](mid5),
+(mid3) --[ ultra thick,out=-60,in=-120,min distance=0.4cm](mid5),
+(mid5) --[ ultra thick](a4),
+(mid5) --[ ultra thick,](a3)
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+\newcommand{\MaxCut}{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-1.2,0.8){};
+\vertex (a2) at (1.2,-0.8){};
+\vertex (a3) at (1.2,0.8){};
+\vertex (a4) at (-1.2,-0.8){};
+\vertex [dot,scale=2] (mid1) at (0,-.4){};
+\vertex [dot,scale=1.5,hgrey0](mid1x) at (0,-.4){};
+\vertex [dot,scale=2] (mid2) at (0,.4){};
+\vertex [dot,scale=1.5,hgrey0] (mid2x) at (0,.4){};
+\vertex [dot,scale=2] (mid3) at (0.8,.4){};
+\vertex [dot,scale=1.5,hgrey0] (mid3x) at (0.8,.4){};
+\vertex [dot,scale=2] (mid4) at (0.8,-.4){};
+\vertex [dot,scale=1.5,hgrey0] (mid4x) at (0.8,-.4){};
+\vertex [dot,scale=2] (mid5) at (-0.8,.4){};
+\vertex [dot,scale=1.5,hgrey0] (mid5x) at (-0.8,.4){};
+\vertex [dot,scale=2] (mid6) at (-0.8,-.4){};
+\vertex [dot,scale=1.5,hgrey0] (mid6x) at (-0.8,-.4){};
+\diagram{
+(a4) --[ultra thick,](mid6),
+(a3) --[ultra thick,](mid3),
+(a2) --[ultra thick,](mid4),
+(a1) --[ultra thick,](mid5),
+(mid1) --[ultra thick,](mid2),
+(mid3) --[ultra thick,](mid2),
+(mid1) --[ultra thick,](mid6),
+(mid1) --[ultra thick,](mid4),
+(mid5) --[ultra thick,](mid2),
+(mid5) --[ultra thick,](mid6),
+(mid3) --[ultra thick,](mid4),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+\newcommand{\SubtleCut}{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (-.8, -0.6) {};
+\vertex (a2) at (-.8, 0.6) {};
+\vertex (a3) at (-1, 0) {};
+\vertex [dot, scale=2](mid1) at (0,0){};
+\vertex [dot, scale=1.5,hgrey0](mid2) at (0,0){};
+\vertex [dot, scale=2](mid3) at (1,0){};
+\vertex [dot, scale=1.5,hgrey0](mid4) at (1,0){};
+\vertex (a4) at (1.8, 0) {};
+\diagram{
+(mid1) --[ultra thick,](a1),
+(mid1) --[ultra thick,](a2),
+(mid1) --[ultra thick,](a3),
+(mid1) --[ultra thick,](mid3),
+(mid1) --[ultra thick,out=60,in=120,min distance=0.4cm](mid3),
+(mid1) --[ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
+(mid3) --[ultra thick](a4),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+%%% Unitarity cuts end %%%
 
@@
 \item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.
+So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\epsilon$ identities.
+Make an ansatz where you do every pairing of $\epsilon$'s.
+This doesn't work.
 \item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
@@
 \item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
+\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4pt, 6pt, and 8pt.
+\item Should probably give the 4pt pion amplitude somewhere to show my conventions.
 \end{itemize}
@@
 Note that the graph symmetry constraint is imposed on \emph{every} graph, not just the basis graphs.
-For example, the crossed box, as shown in \eqref{eq:TwoLoopJacobiTwo}, is unchanged upon reflection across the horizontal axis.
+For example, the crossed box, \be
+\CrossedBoxGraphSym
+\ee
+is unchanged upon reflection across the horizontal axis (shown as a blue dashed line).
 Since the crossed box can be written in terms of the double box and penta-triangle, this imposes non-trivial constraints on the ansatz.
@@
 The last key constraint is that the ansatz have the correct unitarity cuts, that is, that the integrand corresponds to the correct theory.
+Generalized unitarity has been reviewed in many places (cite...) so we will not belabor the details here, in particular see (emu) for a recent treatment of unitarity methods for even multiplicity theories like NLSM.
 The essence of generalized unitarity is that when internal lines are placed on-shell, the integrand should factorize into a product of on-shell tree amplitudes.
-Generalized unitarity has been reviewed in many places (cite...) so we will not belabor the details here.
-
-Could mention that it is certainly enough to check $(n-2)!$ color-ordered cuts but you could maybe get away with
-
-Finally we have to impose unitarity.
-We only do physical cuts, no aesthetic cuts.
-The two most important cuts for pions (or any EMU) are ...
-These cuts are the only non-zero cuts.
-However there are other cuts that must be imposed as well like the max cut.
-
-Show the two interesting cuts, mention a max cut
+The cut to be performed can, itself, be encoded in a graph.
+For example, potential 4pt 2-loop cuts include
+\be
+\label{eq:PotentialCuts}
+\text{(a)} \SubtleCut ~~~~ \text{(b)} \PhysicalCutOne{}{}{}{} ~~~~ \text{(c)} \PhysicalCutTwo{}{}{}{} ~~~~ \text{(d)}  \MaxCut
+\ee
+as well as many more.
+In these graphs, all exposed propagators are understood to be cut/on-shell.
+As an equation, a unitarity cut this looks schematically like
+\be
+\label{eq:SchematicCutEquation}
+\sum \limits_\text{topologies} \frac{n \vert_\text{cut}}{\prod \limits_\text{uncut} k^2} = \sum \limits_\text{states} \prod \limits_\text{blobs} A_\text{tree} .
+\ee
+The right hand side of the equation is a product of on-shell tree amplitudes, represented graphically in \eqref{eq:PotentialCuts} by grey blobs.
+States crossing (or propagating across) the cut must be summed over.
+For scalars this sum is trivial but for spinning particles this is no longer the case and the physical state projector must be inserted (see Dimitrius paper for simplifying this operation).
+The graph topologies appearing in the left hand side of \eqref{eq:SchematicCutEquation} come from blowing up the grey blobs into cubic tree graphs in every conceivable way.
+For each of these topologies, the numerator of the associated graph is subjected to the cut constraints and is then divided by the uncut propagators.
+The right hand side is assumed to be known, which places a constraint on the numerator ansatze in the left hand side.
+
+It is possible to work with either color-dressed cuts or color-ordered cuts.
+For color-dressed cuts the grey blobs are blown up into all possible channels and all color factors $f^{abc}$ are explicitly retained (both in the integrand numerators and in the tree amplitudes).
+For color-ordered cuts the grey blobs are only blown up in color ordered channels, the color factors can be suppressed, and the product of on-shell amplitudes only extends over color-ordered trees.
+We elect to use color-ordered cuts.
+Since these cuts do not contain the full color information of the theory, it is necessary to do multiple color-ordered cuts -- over different orderings of the blob labels -- in order to fully capture all of the cut information.
+For a color dual theory such as NLSM it is enough to do $(n-2)!$ labelings of each blob due to the Kleiss-Kuijf and $U(1)$ decoupling identities (cite KK).
+In this sense color-dressed cuts contain extraneous information that is bypassed when using color-ordered cuts.
+
+In our construction, only well-defined cuts are imposed so, for example, cut (a) of \eqref{eq:PotentialCuts} is not enforced since it is possible to blow up the left blob into a tree amplitude with an on-shell internal propagator.
+Cuts (b) and (c) are the only non-vanishing 4pt 2-loop physical cuts for an even multiplicity theory.
+This means that even at two loops, unitarity cuts are still only probing the on-shell 4pt NLSM amplitude.
+Even though (b) and (c) are the only non-zero cuts, other cuts, for example the maximal cut (d), must also be imposed in order to correctly reproduce NLSM.
+The maximal cut vanishes because only 3pt amplitudes contribute and these amplitudes vanish in any scalar theory.
+It is possible to automatically enforce (or ``bake in'') the double box and penta-triangle max cuts on the ansatz by writing the ansatz in terms of inverse propagators (and remaining irreducible scalar products) and then only keeping terms that involve at least one inverse propagator since those terms will vanish on those max cuts, just as the product of 3pt scalar amplitudes will.
+However, for the sake of simplicity we do not take this route.
 
@@
 
-Could bake in max cuts to slightly reduce ansatz size.
-
 References for Jacobi, unitarity, etc.
 
-After you've imposed all of the essential stuff you get X free parameters...
-There is lots of generalized gauge freedom, clearly there's room to impose extra constraints.
-For N=4 the extra conditions are things like no triangles, strip off a factor of stAtree (which fails at 5-loops), manifest power counting, etc.
-The obvious choice here is to match to ZM.
-There's one known theory that has manifest color-kinematics, manifest Bose sym, and NLSM power counting and that's ZM theory.
-
-\subsubsection{Matching to ZM and loop power counting -- James}
-
-Can simplify the garbage
+Why aren't the two physical cuts spanning?  I know from experience that they're not but I can't easily explain why.
+
+\subsubsection{Matching to ZM -- James}
+
+After imposing all of the three key constraints (Jacobi, graph symmetries, and unitarity), there still remains a plethora of generalized gauge freedom in the X unconstrained ansatz parameters.
+At this point color kinematics duality has been satisfied so the double copy will proceed without issue, but it is possible to enforce additional, more aesthetic, constraints as desired.
+$\mathcal{N}=4$ SYM provides several hints for further conditions to impose on the ansatz.
+For example, for maximally supersymmetric gauge theory it is possible to enforce the no triangle hypothesis, manifest loop power counting, and, at least for 4pt and up to four loops, strip off a factor of $st A_\text{tree}$ from the integrand (I'm not sure I know all of the papers to cite here).
+For the NLSM integrand it is desirable to make color-kinematics duality as manifest as possible.
+One hope would be to factor out some piece of the 1-loop numerator since this at least manifests antisymmetry on some of the legs.
+However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, ZM theory.
 
@@
 We're using ZM more as a tool to... -- We know ZM has the right kinematic structure to give CK in 2D so we're just matching onto that because we can.  ZM and NLSM can be different at quantum level.
+
+Can't match to ZM on all of the physical cuts (one of them is always subtle).  Matching to ZM should be interpreted as just a way to simplify things, not really physical.
+
+Cut (b) is always subtle
+
+Match the $\ell$ structure of ZM
+
+This is the object we include in the ancillary files, maybe with the remaining variables set to zero
 
@@
 
+Figures made with TikZ-Feynman [1601.05437]
+
 \bibliographystyle{JHEP}

### 2023-08-17 notes/2loopNLSM.tex
Added comment command for myself.
review sections and some appendices

--- 2023-08-15 notes/2loopNLSM.tex
@@
 \documentclass[11pt,letter]{article}
+\pdfoutput=1
 \usepackage{jheppub}
@@
 \usepackage{slashed}
+\usepackage{tocloft}
+\renewcommand{\cftdot}{.}
+\renewcommand{\cftsubsecleader}{\cftdotfill{\cftdotsep}}
 \usepackage{diagbox}
@@
 
+\usepackage[framemethod=default]{mdframed}
+\newmdenv[skipabove=7pt,
+skipbelow=7pt,
+rightline=false,
+leftline=false,
+topline=false,
+bottomline=false,
+backgroundcolor=gray!15,
+linecolor=gray,
+innerleftmargin=5pt,
+innerrightmargin=5pt,
+innertopmargin=5pt,
+innerbottommargin=5pt,
+leftmargin=0cm,
+rightmargin=0cm,
+linewidth=4pt]{eBox}
+
 \tikzset{graviton/.style={decorate, decoration={snake, amplitude=.4mm, segment length=1.5mm, pre length=.5mm, post length=.5mm}, double}}
 \tikzfeynmanset{compat=1.1.0}
-%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-%\usetikzlibrary{external}  
-%          %% Load the `external` library
-%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-%\tikzexternalize[                     %% Activate externalization
-%  prefix=images/,                    %% Avoid cluttering the directory
-% system call={                       %% Use lualatex in system call
-%    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
-%  },
-%]
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\usetikzlibrary{external}  
+          %% Load the `external` library
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\tikzexternalize[                     %% Activate externalization
+  prefix=images/,                    %% Avoid cluttering the directory
+ system call={                       %% Use lualatex in system call
+    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
+  },
+]
 \tikzfeynmanset{
@@
         markings,
-        mark=at position 0.7 with {
+        mark=at position 0.8 with {
           \arrow{>[length=6pt, width=7pt]};
@@
 
-%%% Jacobi 1 %%%
-
-\newcommand{\JacobiOneDoubleBox}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){4};
-\vertex (a2) at (1.5,-1){2};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5) ;
-\vertex (mid4) at (1,-.5) ;
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5) ;
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,](mid6),
-(mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,red](mid2),
-(mid5) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\JacobiOneCrossedBox}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){4};
-\vertex (a2) at (1.5,-1){2};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,red](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\JacobiOnePentaTriangle}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){4};
-\vertex (a2) at (.5,-1){2};
-\vertex (a3) at (.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (-.5,-.5);
-\vertex (mid2) at (-1,0);
-\vertex (mid3) at (0,.5) ;
-\vertex (mid4) at (0,-.5) ;
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5) ;
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid2),
-(mid6) --[ultra thick,](mid2),
-(mid1) --[ultra thick,](mid6),
-(mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,](mid3),
-(mid5) --[ultra thick,red](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-%%% Jacobi 1 end %%%
-
-%%% Jacobi 2 start %%%
-
-\newcommand{\JacobiTwoCrossedBoxOne}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){2};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,red](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\JacobiTwoCrossedBoxTwo}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){3};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){1};
-\vertex (a4) at (-1.5,-1){2};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,red](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\JacobiTwoCrossedBoxThree}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){1};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){2};
-\vertex (a4) at (-1.5,-1){3};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,red](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-%%% Jacobi 2 end %%%
-
 \newcommand{\simplebox}{ {
@@
 \vertex (mid6) at (-.35,-.35);
-\diagram{(mid4) --[ultra thick,nhpRed,quarter right](mid3),
-(mid5) --[ultra thick,nhpRed,quarter right](mid6),
-(mid3) --[ultra thick,nhpRed,quarter right](mid5),
-(mid6) --[ultra thick,nhpRed,quarter right](mid4),
+\diagram{(mid4) --[ultra thick,nhpRed](mid3),
+(mid5) --[ultra thick,nhpRed](mid6),
+(mid3) --[ultra thick,nhpRed](mid5),
+(mid6) --[ultra thick,nhpRed](mid4),
 (mid6) --[ultra thick,fermion2](a4),
@@
 };
+\vertex [dot, scale=1.6](mid3a) at (.35,.35){};
+\vertex [dot, scale=1.1,hgrey0](mid3b) at (.35,.35){};
+\vertex [dot, scale=1.6](mid4a) at (-.35,.35){};
+\vertex [dot, scale=1.1,hgrey0](mid4b) at (-.35,.35){};
+\vertex [dot, scale=1.6](mid5a) at (.35,-.35){};
+\vertex [dot, scale=1.1,hgrey0](mid5b) at (.35,-.35){};
+\vertex [dot, scale=1.6](mid6a) at (-.35,-.35){};
+\vertex [dot, scale=1.1,hgrey0](mid6b) at (-.35,-.35){};
 \end{feynman}
@@
 (a1) --[ultra thick,#6,#7](mid1),
+};
+\end{feynman}
+\end{tikzpicture}
+}
+}
+
+\newcommand{\AcubicB}[9]{ {
+\begin{tikzpicture}[baseline=(current  bounding  box.center)]
+\begin{feynman}
+\vertex (a1) at (0,0){};
+\vertex (a2) at (-1.55,.85){2};
+\vertex (a3) at (-1.55,-.85){1};
+\vertex [dot, scale=2.6](mid1) at (-.85,0){};
+\vertex [dot, scale=2.6](mid2) at (-.85,0){};
+\vertex [dot, scale=2,#1](mid3) at (-.85,0){};
+\vertex (a4) at (1.55,.85){3};
+\vertex (a5) at (1.55,-.85){4};
+\vertex [dot, scale=2.6](mid4) at (.85,0){};
+\vertex [dot, scale=2.6](mid5) at (.85,0){};
+\vertex [dot, scale=2,#1](mid6) at (.85,0){};
+\diagram{
+(mid1) --[ultra thick,#2,#3](a3),
+(mid1) --[ultra thick,#4,#5](a2),
+(mid4) --[ultra thick,#8,#9](a4),
+(mid4) --[ultra thick,#8,#9](a5),
+(mid1) --[ultra thick,#6,#7](a1),
+(a1) --[ultra thick,#6,#7](mid4),
 };
@@
 \diagram{
-(a4) --[ultra thick](mid6),
+(a4) --[ultra thick,](mid6),
 (a3) --[ultra thick,](mid3),
@@
 \def\sec#1{section~\ref{#1}}
-\def\eqn#1{eq.~(\ref{#1})}
+\def\eqn#1{(\ref{#1})}
 \def\Eqn#1{Equation~(\ref{#1})}
@@
 
-\def\dj#1{{\color{NUpurple}\it \bf JJ: #1}}
+\author{Alex Edison,}
+\author{James Mangan,}
+\author{and Nicolas H. Pavao}
 
-\newcommand{\draftnoteJM}[1]{\textbf{\color{blue}[#1]}}
-
-\author[1]{Alex Edison,}
-\author[1]{James Mangan,}
-\author[1]{Nicolas H. Pavao}
-
-\affiliation[1]{Department of Physics and Astronomy, Northwestern
+\affiliation{Department of Physics and Astronomy, Northwestern
   University, Evanston, Illinois 60208, USA}
 
-\title{Towards Globally Color-Dual All-Loop Integrands}
+\emailAdd{alexander.edison@northwestern.edu, james.mangan@northwestern.edu, pavao@u.northwestern.edu}
+
+\title{\center Towards Globally Color-Dual All-Loop Integrands}
 
@@
 
-  \newpage
+\makeatletter
+\gdef\@fpheader{\,}
 
@@
 \section{Introduction}
-
-\label{sec:intro} Some refs.
-\cite{BCJreview, Bern:2022wqg, Adamo:2022dcm,Bern:2012uf, Neq44np, GravityFour,Bjerrum-Bohr:2013iza,Edison:2020uzf,Edison:2022jln,Cheung2016prv,He:2017spx,OneTwoLoopPureYMBCJ, Mogull:2015adi, Bern:2015ooa, Geyer:2019hnn,Johansson:2017bfl,Chen:2019ywi,Chen:2021chy,Brandhuber:2021bsf,Cheung:2021zvb,Ben-Shahar:2021zww,Cheung:2022mix, Ben-Shahar:2022ixa,Cachazo:2014xea,Carrasco:2016ldy,Elvang:2020kuj,Bern:2007xj,Carrasco:2013ypa,Craig:2019zkf,Monteiro:2022nqt,Bern:2017tuc,Bern:2017rjw,Bern:2019isl,Goroff:1985sz,Bern:2013uka,Alishahiha:2004eh,Creminelli:2005hu,Fergusson:2008ra,Carrasco:2015pla,Carrasco:2015rva,Carrasco:2015uma,BICEP:2021xfz,Kallosh:2021mnu,Green:1982sw,Mafra:2016mcc,Broedel:2013tta,Carrasco:2016ygv,Azevedo:2018dgo,Anastasiou:2004vj,vonManteuffel:2012np,Smirnov:2014hma,vonManteuffel:2014ixa,Smirnov:2019qkx,Smirnov:2020quc,Usovitsch:2020jrk,Maierhofer:2018gpa,Carrasco:2019yyn,Carrasco:2021ptp,Chi:2021mio,Bonnefoy:2021qgu,Carrasco:2022lbm,Carrasco:2022sck,Pavao:2022kog,Chen:2022shl,Chen:2023dcx,Brown:2023srz,Carrasco:2022jxn,Caron-Huot:2016icg, Chiodaroli:2021eug,Cangemi:2022abk,Cangemi:2022bew,Geiser:2022exp,Cheung:2022mkw,Fonseca:2019yya,Hays:2018zze,Alioli:2022fng}
-
 \section{Review}
-The goal is this paper is to compute $D$-dimensional color-dual numerators beyond one-loop.
-To this end compute two-loop color-dual numerators for NLSM that globally satisfy the duality between color and kinematics and elucidate the color-dual structure expected of Yang-Mills at all-loop order.
  To set the stage, it is worth distinguishing between the algebraic properties of functionally symmetric kinematics that satisfy color-kinematics globally, and some of the other constructions that appear in the literature.
@@
 We will briefly review the perturbative construction of this theory below.
-\subsection{Self-dual Yang-Mills}
+\subsection{Color-dual Amplitudes}
+Review of BCJ relations and Jacobi relations off-shell. Justify kinematic algebra in an off-shell framework by talking about on-shell construction. yada yada yada
+\subsection{Color-dual Lagrangians} In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual.
+As we will show, taking forward limits of tree-level numerators works as long as one can construct an off-shell description with a Lagrangian.
+Here we briefly review the off-shell examples of the kinematic algebra that will be relevant in this paper.
+\paragraph{Self-Dual Yang-Mills} The first example in the literature \cite{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
 \be
@@
 where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength.
+Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
+\be
+D^\mu F^{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
+\ee
+Solutions to \eqn{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills.
+In this paper, we will focus on the perturbative aspects of this constraint.
 Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
@@
 \ee
-Applying this coordinate transformation to the self-dual condition of \eqn{SDcon}, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the 4D self-dual condition:
+Applying this coordinate transformation to the self-dual condition of \eqn{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
+\begin{align} \label{SDLightCone1}
+F_{uw} &=0\,,
+\\
+ \label{SDLightCone2}
+ F_{uv} &= F_{w\bar{w}}\,,
+\\
+ \label{SDLightCone3}
+ F_{v\bar{w}} &= 0\,,
+\end{align}
+Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
 \be
-A_w = 0\,, \qquad \partial_u A_v = \partial_w A_{\bar{w}}\,.
+A_u=0 \text{ and } \eqn{SDLightCone1} \quad\Rightarrow \quad A_w=0
 \ee
-The second equation implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom, which we call $\Psi$.
-This constraint is immediately satisfied with the following definition of the gauge field:
+The second equation \eqn{SDLightCone2}  then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
 \be
+A_w=0\,,\,A_u=0 \text{ and }\eqn{SDLightCone2} \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
+\ee
+This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
+\be\label{SDDef}
 A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
 \ee
-Expanding out the equations of motion for the Yang-Mills Lagrangian, yields the following expression in terms of the gauge fields:
-\be
-D^\mu F^{\mu\nu} =0\qquad  \Rightarrow\qquad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
+Using this definition on the final self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
+\be\label{SDEOM}
+\eqn{SDLightCone1} \text{ and } \eqn{SDDef} \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
 \ee
 Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
+\begin{eBox}
 \be
@@
 \ee
-\subsection{ZM-theory} The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:
+\end{eBox}
+The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
 \be
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) 
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
 \ee
+In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
+In this form, we can see the effect \eqn{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
+Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.
+
+As we will show in \sect{}, the color-dual nature of SDYM can be understood as a direct consequence of isolating the \textit{cubic-sector} of the full Yang-Mills amplitudes by projecting along particular on-shell states.
+For this reason, the color-dual nature depends critically on the loop order of the amplitude and does not hold generically beyond one-loop.
+
+Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \eqn{SDEOM}.
+\paragraph{ZM-theory} The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:
+\begin{eBox}
+\be
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right]
+\ee
+\end{eBox}
 where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $ and $\epsilon_{\mu\nu}$ is the two-dimensional Levi-Civita symbol.
@@
 Similar to the difficulties of renormalizing chiral fermions \cite{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
-\subsection{YZ-Theory}
+As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
+\paragraph{YZ-Theory} Thus far, the two color-dual Lagrangians we have discussed make explicit reference to the spacetime dimension ($D=4$ for SDYM, and $D=2$ for ZM theory).
+This makes them poorly suited for constructing dimensionally regulated integrals in loop-level amplitudes.
+Here we briefly review YZ-theory, which is a honest $D$-dimensional theory first proposed by Cheung and Hsien \cite{Cheung2016prv} for the purpose of describing nonlinear sigma model (NLSM) scattering.
+One can understand YZ-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions.
+
+Starting with the Yang-Mills Lagrangian, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
+\begin{align}
+X_M &= (X_\mu,0,-iX_\mu) 
+\\
+Y_M &= (0,Y,0) 
+\\
+Z_M &= (Z_\mu,0,iZ_\mu) 
+\end{align}
+where $X$ and $Z$ are $d$-vectors and $Y$ is a scalar field.
+Considering the conjugate nature of the X-Z propagator, in this work we will make the replacement $X\rightarrow \bar{Z}$.
+Plugging this redefinition of the gauge fields in, upto cubic order, we thus obtain the following Lagrangian:
+\begin{eBox}
 \be
@@
 \ee
+\end{eBox}
+The Feynman rules for this Lagrangian are simply:
 \be
@@
 \ee
-We begin with a review of the construction of NLSM numerators at tree-level.
-For this work we extend the tree-level construction of $Y\!Z$ model of Cheung and Hsien \cite{Cheung2016prv}.
-In this construction, the generators of the kinematic algebra can be expressed as follows
+Now we review of the construction of NLSM numerators at tree-level. In this construction, we can define generators of the kinematic algebra can be expressed as follows
 \be\label{eq:FeynmanRuleYYZ}
@@
 Indeed, this construction is valid to all orders at tree-level.
-There are only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut :
+One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
 \begin{align}
@@
 \end{align}
-\subsection{J-theory}
+Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
+As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
+Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
+This is essentially what $J$-theory does, as we will show below.
+\paragraph{J-theory} There is an alternative Lagrangian formulation of NLSM constructed by Chueng and one of the authors, that instead starts from the chiral current description of NLSM:
 \be
-\mathcal{L}^{\text{J}} = \frac{1}{2}\partial_\mu J_\nu \bar{J}^{\mu\nu} +g f^{abc} \bar{J}_{\mu\nu}J^\mu J^\nu
+\mathcal{L} = \text{tr}[\partial U \partial U^{-1}] \equiv \text{tr}[J^\mu J_\mu]
 \ee 
+where $J_\mu = U\partial_\mu U^{-1}$.
+To build the J-theory Lagnraigna, we can think of the chiral current $J^\mu$ as a \textit{pure gauge} vector field.
+Thus, the field strength for $J_\mu$ must vanish, this yielding an equivalent on-shell formulation of the EOM:
+\be
+\Box J^\mu +g f^{abc} J^\nu J^{\mu\nu} = 0
+\ee
+where we have applied the gauge condition $\partial_\mu J^\mu = 0$.
+Adding back in a $\bar{J}^\mu$ auxiliary field as a Lagrange multiplier, we obtain the following Lagrangian that is manifestly color-dual:
+\begin{eBox}
+\be
+\mathcal{L}^{\text{J}} = \frac{1}{2}(\partial J)(\partial \bar{J}) +g f^{abc} \bar{J}_{\mu\nu}J^\mu J^\nu
+\ee
+\end{eBox}
 where as above, $\bar{J}_{\mu\nu} = \partial_\mu J_\nu - \partial_\nu J_\mu$.
-Subject to the Lorenz gauge condition, $\partial_\mu J^\mu =0$, this Lagrangian produces precisely the EOM for J-theory needed for Berends-Giele recursion at tree-level:
-\be
-\partial^2 J^\mu - gf^{abc} J^\nu \partial_\nu J^\mu = 0 
-\ee
+Subject to the Lorenz gauge condition, $\partial_\mu J^\mu =0$.
+This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states.
 As such, the single vertex in this theory is the same as for YZ theory:
@@
 \ee
+Now we are prepared to discuss the one-loop case. 
+\subsection{Color-dual Bootstrap}
+Some background here on how we approach color-dual bootstrap. Building an ansatz from irreducible lorentz products (ISPs). Comments about:
+\begin{itemize}
+\item loop momenta weight counting 
+\item polynomial vector spaces 
+\item generalized gauge freedom
+\item functional jacobi constraints and cuts
+\end{itemize} 
+\section{Isolating the cubic sector}
+Here we'll describe the why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
+It has to do with out the vector state sum mixes with the four-point contact.
+In terms of our previously defined Feynman rules, the three-point YM vertex takes the form:
+\be
+\cubic{hgrey0}{gluon}{}{gluon}{}{gluon}{}  =  \cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed} + \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} + \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} +\text{h.c.}
+\ee
+The state-sum between two three-point gluon vertex yields the following expansion in terms of YZ-theory vertices:
+\be
+ \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
+\ee
+All the $(\epsilon\epsilon)^1$ diagram permutations are isolated to the cubic sector and together manifest color-kinematics duality.
+However, the exception of the last diagram which introduces a $(\epsilon\epsilon)^2$ factor, must conspire with the Yang-Mills contact to preserve the duality off-shell
+\be
+\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed} = (s_{13}-s_{12}) \epsilon_{(12)} \epsilon_{(34)}
+\ee
+One was to resolve this is to introduce higher spin modes in order to accomodate the internal index contractions needed to recover the s-channal contract:
+\be
+\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{graviton}{nhpRed}{}{nhpRed} = s_{12 }(\epsilon_{(13)} \epsilon_{(24)} - \epsilon_{(14)} \epsilon_{(23)})
+\ee
+While introducing succesively higher spiin states to the NMHV lagrangian constructed in \cite{} could in principle work at tree level, we will see that it is not consiisntent with what we find at general loop order.
+We will comment on this in \sect{}.
+For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.
+This is easily understood in terms of a polarization decomposition introduced by one of the authors \cite{} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations.
+\subsection{Block Decomposition of Yang-Mills}
+Describe how different orders in $\varepsilon_i\varepsilon_j$ in pure Yang-Mills captures different cubic and contact sectors of the theory.
+All the $D$-dimensional Lagnrangians above can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order.
+Start with reducible amplitude block decomp from Ref.
+\cite:
+\begin{eBox}
+\begin{equation}\label{eq:pureVecRABD}
+A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+\end{equation}
+\end{eBox}
+By a simple mass-dimensioin argument, we know the tree-level cubic sector is simply:
+\be
+A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+\ee
+and likewise at one-loop:
+\be
+A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+\ee
+We can select out both of these manifestly cubic sectors by selecting only $\epsilon^+\epsilon^+$ in light-cone gauge (i.e.
+SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states.
+Indeed, the $D$-dimensional description of $J$ theory is just the following blocks in the RABD expansion of Yang-Mills:
+\be
+A(...,\bar{J}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
+\ee
+and similarly so at one-loop:
+\be
+A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}
+\ee
+To recover NLSM at one-loop, we need to extract out the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars:
+\begin{eBox}
+\be
+A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\epsilon\rightarrow k}
+\ee
+\end{eBox}
+Why must we take the derivative with respect to $D$?
+After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators.
+However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes.
+Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes.
+However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit.
+We will construct these one-loop integrands below in the next section.
+\subsection{One-loop SDYM Integrands}
+\be
+\simplebox = g_{\text{YM}}^4 X(k_1,l_1)X(k_2,l_2)X(k_3,l_3)X(k_4,l_4)
+\ee
+\subsection{One-loop NLSM Integrands}
 
-\be
-\mathcal{L}^{\text{SDYM}} = \frac{1}{2}(\partial \bar{\Phi} )^a(\partial  \Phi)^a +g f^{abc} \bar{\Phi} ^a (\partial_u \Phi)^b (\partial_v \Phi)^c
-\ee
-\be
-(\varepsilon^+_1 k_2) - (\varepsilon^+_2 k_1) = [12]\left(\frac{\langle 2 q\rangle}{\langle 1 q\rangle} + \frac{\langle 1 q\rangle}{\langle 2 q\rangle} \right) \sim [12]
-\ee
-Now we are prepared to discuss the one-loop case.
-
-\section{One-loop}
-
-\subsection{NLSM -- Nic}
-
-\draftnoteJM{I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.}
-
+Note from James:  I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.
 \be
@@
 Where we have define the antisymmetric kinematic variable, $[LR] = l_i^L - l_R^2$
-\subsection{BELs and integration zeros -- Nic}
+\subsection{Two-loop Obstruction}
 
+\section{Bootstrapping two-loop...}
+
+Notes to myself: 
+\begin{itemize}
+\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
+This observation is due to other people but an easy way to see it.
+ZM and 2D NLSM have the same EOM after a field redefinition.
+This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
+\item Forcing pions to match ZM in 2D does funny things.
+The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
+I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
+Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
+For 4pt tree, $z=2/3$ (I matched the half ladder).
+For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
+For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
+For 6pt tree, $z$ is 12/35 (I matched the half ladder).
+So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
+Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
+\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
+At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
+\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.
+\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
+The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
+I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
+\end{itemize}
+
+\subsection{Cut construction, graph sym, Jacobi -- James}
+
+Color-dual integrands are typically generated by constructing an ansatz and then imposing various constraints.
+Color-kinematics duality requires writing the integrand in terms of cubic graphs.
+Any theory can be written this way by artificially inserting ratios of propagators (can blow up YM or NLSM).
+Obviously the ansatz must have the correct power counting and external states.
+We will take NLSM as our example theory but later we will discuss YM.
+Since pions are scalars the numerators will not carry any spinors or polarization vectors.
+Every vertex in NLSM scales as $k^2$ so, for example, the numerator of a cubic 2-loop diagram scales as $k^12$.
+There are three conditions that are imposed on the ansatz:  (1) the integrand must have the correct unitarity cuts, (2) numerators must respect graph symmetries, and (3) Jacobi relations amongst graphs must be satisfied.
+The integrand must be written in terms of cubic graphs in order to apply the Jacobi relations.
+This means that there are naively X cubic 4pt 2-loop diagrams.
+However, many of these diagrams are related by Jacobi identities.
+Give an example.
+Through repeated application of the Jacobi identities, all of the cubic diagrams can be written in terms of the double box and penta-triangle.
+The basis choice is not unique.
+For example, any pair of the double box, penta-triangle and crossed box would work.
+So you have to have two numerator ansatze, one for the double box and one for the crossed box.
+What we are describing here is global color-kinematics duality.
+It is possible to give each cubic graph its own numerator and then only impose Jacobi on the cuts (see ...).
+It is not always possible to achieve global CK, but when it is doable, it is typically much easier than doing Jacobi on the cuts because the latter requires far more ansatz parameters.
+Anyway, now the numerator of any diagram can be written in terms of the two basis numerators (double box and crossed box).
+This is part of imposing Jacobi.
+There are additional Jacobi relations that impose actual constraints on the ansatze, for example ASDF.
+We allow BEL graphs to have nonzero numerators since they do not contribute to physical unitarity cuts.
+Jacobi relations involving BEL graphs or tadpoles are simply not solved.
+
+Requiring numerators to respect their graph symmetries is very convenient but is not completely necessary in order to perform the double copy.
+At tree level, finding manifestly color dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
+Nonetheless, for a pure ansatz construction it is very reasonable to impose graph symmetries.
+Note that you impose that the numerator of \emph{every} graph respects its graph automorphisms.
+So the graph syms of the double box impose constraints, but, for example, the crossed box imposes constraints on the ansatz numerators too because the numerator of the crossed box can be written in terms of the two basis numerators.
+
+Finally we have to impose unitarity.
+We only do physical cuts, no aesthetic cuts.
+The two most important cuts for pions (or any EMU) are ...
+However there are other cuts that must be imposed as well.
+
+References for Jacobi, unitarity, etc.
+
+After you've imposed all of the essential stuff you get X free parameters...
+There is lots of generalized gauge freedom, clearly there's room to impose extra constraints.
+For N=4 the extra conditions are things like no triangles, strip off a factor of stAtree (which fails at 5-loops), manifest power counting, etc.
+The obvious choice here is to match to ZM
+There's one known theory that has manifest color-kinematics, manifest Bose sym, and NLSM power counting and that's ZM theory.
+
+\subsection{Pions -- James}
+
+\subsection{Matching to ZM -- James}
+
+\subsection{Double-copy -- Alex }
+\subsection{YM revisit -- Alex}
+\section{... and Beyond}
+This could be a section about our expectations for all-loop construction requiring non-local color-dual integrands. Lay out contrafactual proof, i,e. define the following statement:
+\be
+ Q_L=\textit{``the $L$-loop numerator is polynomial and color-dual"}. 
+\ee
+Then it is clear that if the kinematic numerator is polynomial and color-dual, evaluating it in kinematic regions where the internal legs are on-shell won't disrupt the kinematic algrebraic relations, and it must still be polynomial.
+Thus we find:
+\be
+Q_L \Rightarrow Q_{L-1}
+\ee
+Or equivalently,
+\be
+\text{not }Q_{L-1}\Rightarrow \text{not }Q_L
+\ee
+We have found that the two-loop integrand for Yang-Mills cannot be constructed from a color-dual polynomial kinematic numerator.
+Thus, if a color-dual representation exists at all-loop order for Yang-Mills it must be a rational function of kinematics.
+\section{Discussion}\label{sec:Discussion}
+
+\paragraph{Acknowledgments} The authors would like to thank ...
+for insightful conversations, related collaboration, and encouragement throughout the completion of this work.
+This work was supported by the DOE under contract DE-SC0015910 and by the Alfred P.
+Sloan Foundation.
+N.H.P.
+additionally acknowledges the Northwestern University Amplitudes and Insight group, the Department of Physics and Astronomy, and Weinberg College for their generous support.
+
+\appendix
+\section{Spinor-Helicity Variables and Conventions}
+Dimensions will generically be away from four, in $D=4-2\epsilon$, with $\epsilon$ arbitrary.
+As noted, it will be convenient to take $D\rightarrow 4$ in certain circumstances after integration.
+In such cases we will employ appropriate spinor-helicity variables.
+Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now.
+For massless momenta, $k_a$ and $k_b$, we have
+\begin{equation}
+s_{ab} = (k_a+k_b)^2= \langle ab \rangle[ba]\,,
+\end{equation}
+the component definition of our spinor bracket that are consistent with the conventions above,
+\begin{align}
+\langle ab \rangle &= \frac{(a_1 + i a_2)(b_0+b_3)-(b_1 + i b_2)(a_0+a_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
+\\
+[ab] &= \frac{(b_1 - i b_2)(a_0+a_3)-(a_1 - i a_2)(b_0+b_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
+\end{align}
+where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
+\begin{equation}\label{eqn:4DPols}
+\begin{aligned}
+k_a \cdot \varepsilon_b^{(+)} &= \frac{\langle q a \rangle[ab]}{\sqrt{2}\langle q b\rangle}\,,
+\qquad\quad \qquad
+k_a \cdot \varepsilon_b^{(-)} = -\frac{[qa]\langle ab\rangle}{\sqrt{2}[qb]}\,,
+\\
+\varepsilon_a^{(-)}\cdot \varepsilon_b^{(+)} &= - \frac{\langle q a\rangle [qb]}{ [qa]\langle q b\rangle} \,,
+\qquad \qquad
+\varepsilon_a^{(\pm)}\cdot \varepsilon_b^{(\pm)} = 0 \,,
+\end{aligned}
+\end{equation}
+Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets.
+In terms of light-cone coordinates that we employed in the text, the angles and squares can be rewritten as follows:
+\begin{align}
+\langle ab \rangle &= \frac{a_w b_u-a_u b_w}{\sqrt{a_ub_u}}\,,
+\\
+[ab] &= \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{\sqrt{a_ub_u}}\,,
+\end{align}
+The conventions we use in the text where the holomorphic spinor cares extra mass dimension essentially amounts to shifting the bracket by the following:
+\begin{align}
+\langle ab \rangle &\rightarrow a_w b_u-a_u b_w \equiv X(a,b)\,,
+\\
+[ab] &\rightarrow \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{a_ub_u}\equiv Q(a,b)\,,
+\end{align}
+With this, we still obtain the same completeness relation for the SDYM spinors:
+\be
+X(a,b)Q(b,a) = \frac{1}{2}s_{ab}
+\ee
+\section{Regulating BEL integrals}
 At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles.
@@
 Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
-
-\section{Two-loop}
-
-\subsection{Notes to self}
-\begin{itemize}
-\item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
-\item Are you sure that the SDYM EOM doesn't come from just $F=\epsilon F$?  If $A=\partial \Phi$ then $F$ has the right number of derivatives to give the SDYM EOM but $DF$ has too many.
-\item I believe the j-theory Lagrangian does not lead to the correct EOM as currently written.
-\item Write Lagrangian for j-theory and reiterate the argument about why you know it's pions.
-Reiterate connection to ZM (dualize j and integrate in phi).
-Should probably mention CS somewhere.
-Point out that all of the theories that come from have CK are really some version of YM where you (1) impose some condition like F=0 or some other condition on the field strength and (2) you impose Lorenz gauge.
-\item Explain why you need to take a certain portion of the YZ numerator to get the right answer.
-Basically you can't have a vector particle circle the loop -- NLSM is a scalar theory so only scalar DOF should actually live in cuts.
-If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
-\item Reiterate that the (tree) amplitudes of CS and SDYM are zero.
-\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
-This observation is due to other people but an easy way to see it.
-ZM and 2D NLSM have the same EOM after a field redefinition.
-This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
-\item Forcing pions to match ZM in 2D does funny things.
-The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
-I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
-Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
-For 4pt tree, $z=2/3$ (I matched the half ladder).
-For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
-For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
-For 6pt tree, $z$ is 12/35 (I matched the half ladder).
-So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
-Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
-\item Explain how matching to ZM is a little silly.
-Check that NLSM and ZM numerator agree on cuts.
-Can't do that or else it becomes subtle.
-Only well defined object is numerator.
-\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
-At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
-\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.
-\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
-The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
-I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
-\item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
-\end{itemize}
-
-\subsection{Pions -- James}
-
-As we have seen, it is possible to coerce tree numerators into 1-loop numerators at any multiplicity for pions.
-However, these methods cannot be reapplied to generate 2-loop numerators, which begs the question ``is it possible to find globally color-dual numerators beyond 1-loop''.
-By ``global'' we mean that color-kinematics duality is satisfied in any kinematic configuration of the integrand.
-This is a much more stringent condition than absolutely necessary.
-There is reason to believe (cite Zvi et al) that global numerators cannot always be found.
-One resolution to the issue is to only demand color-kinematics duality on the unitarity cuts of the integrand, i.e., in specific kinematic limits.
-Enforcing Jacobi on the cuts is enough to ensure that the squared integrand will correctly cut to gravity (or whatever the squared theory might be).
-When a globally color-dual numerator cannot be found, another alternative explored in the literature is to increase the size of the numerator ansatz by enlarging the numerator from a polynomial to a rational function with spurious singularities (cite Donal et al).
-When global color-kinematics fails, the hope is that it can be restored by enlarging the size of the ansatz, either by giving the numerator of each graph its own ansatz (first option described) or by promoting the numerator to a non-local function (second option described).
-Note that a theory whose Lagrangian has color-kinematics duality would naturally produce a globally color-dual integrand so the quest for a global numerator is closely related to the existence of a Lagrangian exhibiting color-kinematics duality.
-We will begin by tackling the issue of a global 4pt 2-loop numerator for NLSM before moving on to YM.
-Two-loop color-dual integrands for pure YM have been investigated before but only for a limited ansatz that manifests locality (cite Zvi et al paper).
-
-Aside from a few special theories (cite blah), color-dual integrands are constructed from an ansatz.
-Color-kinematics duality is stated in terms of cubic graphs so the first step is to express in the integrand in terms of such graphs.
-Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and bubble on external leg (BEL) graphs.
-It is always possible to express an integrand in terms of cubic graphs, even for an even valency theory like NLSM, by multiplying and dividing the integrand by factors of inverse propagators.
-Next, the ansatz must have the correct power counting and external states.
-Since pions are scalars the numerators will not carry any spinors or polarization vectors.
-Every vertex in NLSM scales as $k^2$ so, for example, the numerator of a cubic 4pt 2-loop diagram scales as $k^{12}$ so there are 8,008 independent dot products of momenta at this mass dimension.
-The numerator is assumed to be manifestly local but one approach to finding color-dual numerators is to relax manifest locality, see (...) for more details.
-After zeroth order considerations like power counting, there are three conditions that are imposed on the ansatz: (1) Jacobi relations amongst graphs must be satisfied, (2) numerators must respect graph symmetries, and (3) the integrand must have the correct unitarity cuts.
-
-\subsubsection{Jacobi relations}
-
-Jacobi relations are the heart of color-kinematics duality.
-The color factors in an integrand obey a set of Jacobi identities.
-Color-kinematics duality states that there exists a way of writing the kinematic numerators of the integrand so that they obey the same set of Jacobi identities.
-(Can trivially read off the adjoint color factors from a cubic graph.)
-So if any triplet of graphs is related by a Jacobi identity, so too must their numerators.
-Broadly speaking there are two kinds of Jacobi identities.
-The first kind relate graphs to a basis.
-For example, the double box, crossed box, and penta-triangle are related to each other as follows
-\be % [[11]]
-\label{eq:TwoLoopJacobiOne}
-\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0.
-\ee
-where the shared propagator is shown in red.
-Using this relation the crossed box can be written in terms of the other two.
-In this way, all of the 14 cubic 4pt 2-loop topologies can be written in terms of a basis of the double box and penta-triangle.
-(Any two of the double box, crossed box, and penta-triangle would have sufficed for a basis but the planar basis was chosen for simplicity.)
-Each of the two basis graphs receives its own numerator ansatz and the numerator of any other graph can be expressed in terms of these.
-As mentioned before, there are 8,008 linearly independent dot products of momenta of the required mass dimension so the total number of free parameters in the system is 16,016.
-As this is too many parameters for \texttt{Mathematica} to reasonably handle, we employ a custom solver suitable for the moderately dense systems appearing in this context.
-(Scalars might generate denser systems since ever dot product can interfere with every other unlike gauge theories which separate based on polarization structure, can cite Nic.)
-
-The second kind of Jacobi relations relate basis elements to themselves.
-For example, the crossed box numerator is related to itself via the following Jacobi relation
-\be % [[19]]
-\label{eq:TwoLoopJacobiTwo}
-\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
-\ee
-where the shared propagator is shown in red as before.
-Each of the crossed box numerators can be represented in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator ansatze.
-The first kind of Jacobi relations simplifies how many numerators require ansatze whereas the second kind of Jacobi relations place constraints on the remaining numerators.
-In principle there could be Jacobi relations involving tadpoles and BEL graphs, which would be subtle to handle.
-One option is to force the numerators of these graphs to zero.
-However, since these graphs will not contribute to physical unitarity cuts, we take a different approach.
-These graphs are allowed to have non-zero numerators but any Jacobi relations involving them are simply not imposed or solved.
-See (4 loop N=4 paper) for a discussion of BELs in the context of color-kinematics duality.
-
-In total, there are 21 Jacobi relations on the 14 cubic 4pt 2-loop graphs where, again, tadpole and BEL graphs are ignored.
-How many constraints fixed.
-
-\subsubsection{Graph symmetries}
-
-The second key constraint in an ansatz construction of color-dual numerators comes from graph symmetries.
-Every numerator is required to respect all of the symmetries (or automorphisms) of its associated graph.
-While it is very convenient to impose graph symmetries, it is not completely necessary in order to perform the double copy.
-At tree level, finding manifestly color dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
-Nonetheless, for a pure ansatz construction it is very reasonable to impose graph symmetries.
-Note that the graph symmetry constraint is imposed on \emph{every} graph, not just the basis graphs.
-For example, the crossed box, as shown in \eqref{eq:TwoLoopJacobiTwo}, is unchanged upon reflection across the horizontal axis.
-Since the crossed box can be written in terms of the double box and penta-triangle, this imposes non-trivial constraints on the ansatz.
-
-Imposing graph symmetries on the ansatz further reduces the DOF to ...
-
-\subsubsection{Unitarity}
-
-The last key constraint is that the ansatz have the correct unitarity cuts, that is, that the integrand corresponds to the correct theory.
-The essence of generalized unitarity is that when internal lines are placed on-shell, the integrand should factorize into a product of on-shell tree amplitudes.
-Generalized unitarity has been reviewed in many places (cite...) so we will not belabor the details here.
-
-Could mention that it is certainly enough to check $(n-2)!$ color-ordered cuts but you could maybe get away with
-
-Finally we have to impose unitarity.
-We only do physical cuts, no aesthetic cuts.
-The two most important cuts for pions (or any EMU) are ...
-These cuts are the only non-zero cuts.
-However there are other cuts that must be imposed as well like the max cut.
-
-Show the two interesting cuts, mention a max cut
-
-How many DOF left after imposing cuts
-
-Could bake in max cuts to slightly reduce ansatz size.
-
-References for Jacobi, unitarity, etc.
-
-After you've imposed all of the essential stuff you get X free parameters...
-There is lots of generalized gauge freedom, clearly there's room to impose extra constraints.
-For N=4 the extra conditions are things like no triangles, strip off a factor of stAtree (which fails at 5-loops), manifest power counting, etc.
-The obvious choice here is to match to ZM.
-There's one known theory that has manifest color-kinematics, manifest Bose sym, and NLSM power counting and that's ZM theory.
-
-\subsubsection{Matching to ZM and loop power counting -- James}
-
-Can simplify the garbage
-
-ZM plagued by (suffers from) IR regulation issues.
-Only one of the two physical/meaningful cuts can be done in a non-subtle way.
-We're using ZM more as a tool to... -- We know ZM has the right kinematic structure to give CK in 2D so we're just matching onto that because we can.  ZM and NLSM can be different at quantum level.
-
-\subsection{Double-copy -- Alex }
-\subsection{YM revisit -- Alex}
-
-\section{Discussion}\label{sec:Discussion}
-
-\paragraph{Acknowledgments} The authors would like to thank ...
-for insightful conversations, related collaboration, and encouragement throughout the completion of this work.
-This work was supported by the DOE under contract DE-SC0015910 and by the Alfred P.
-Sloan Foundation.
-N.H.P.
-additionally acknowledges the Northwestern University Amplitudes and Insight group, the Department of Physics and Astronomy, and Weinberg College for their generous support.
-
 \bibliographystyle{JHEP}

### 2023-08-17 notes/2loopNLSM.tex

--- 2023-08-17 notes/2loopNLSM.tex
@@
 
+%Comment commands
+\newcommand{\ace}[1]{\textcolor{darkgreen}{\textbf{AE:}{#1}}}
+
+\usepackage[framemethod=default]{mdframed}
+\newmdenv[skipabove=7pt,
+skipbelow=7pt,
+rightline=false,
+leftline=false,
+topline=false,
+bottomline=false,
+backgroundcolor=gray!15,
+linecolor=gray,
+innerleftmargin=5pt,
+innerrightmargin=5pt,
+innertopmargin=5pt,
+innerbottommargin=5pt,
+leftmargin=0cm,
+rightmargin=0cm,
+linewidth=4pt]{eBox}
+
 \tikzset{graviton/.style={decorate, decoration={snake, amplitude=.4mm, segment length=1.5mm, pre length=.5mm, post length=.5mm}, double}}
 \tikzfeynmanset{compat=1.1.0}
-%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-%\usetikzlibrary{external}  
-%          %% Load the `external` library
-%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-%\tikzexternalize[                     %% Activate externalization
-%  prefix=images/,                    %% Avoid cluttering the directory
-% system call={                       %% Use lualatex in system call
-%    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
-%  },
-%]
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\usetikzlibrary{external}  
+          %% Load the `external` library
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\tikzexternalize[                     %% Activate externalization
+  prefix=images/,                    %% Avoid cluttering the directory
+ system call={                       %% Use lualatex in system call
+    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
+  },
+]
 \tikzfeynmanset{
@@
 
-\def\dj#1{{\color{NUpurple}\it \bf JJ: #1}}
-
 \newcommand{\draftnoteJM}[1]{\textbf{\color{blue}[#1]}}
 
-\author[1]{Alex Edison,}
-\author[1]{James Mangan,}
-\author[1]{Nicolas H. Pavao}
-
-\affiliation[1]{Department of Physics and Astronomy, Northwestern
+\author{Alex Edison,}
+\author{James Mangan,}
+\author{and Nicolas H. Pavao}
+
+\affiliation{Department of Physics and Astronomy, Northwestern
   University, Evanston, Illinois 60208, USA}
 
-\title{Towards Globally Color-Dual All-Loop Integrands}
+\emailAdd{alexander.edison@northwestern.edu, james.mangan@northwestern.edu, pavao@u.northwestern.edu}
+
+\title{\center Towards Globally Color-Dual All-Loop Integrands}
 
@@
 \ee
-Applying this coordinate transformation to the self-dual condition of \eqn{SDcon}, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the 4D self-dual condition:
-\be
-A_w = 0\,, \qquad \partial_u A_v = \partial_w A_{\bar{w}}\,.
-\ee
-The second equation implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom, which we call $\Psi$.
-This constraint is immediately satisfied with the following definition of the gauge field:
-\be
+Applying this coordinate transformation to the self-dual condition of \eqn{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
+\begin{align} \label{SDLightCone1}
+F_{uw} &=0\,,
+\\
+ \label{SDLightCone2}
+ F_{uv} &= F_{w\bar{w}}\,,
+\\
+ \label{SDLightCone3}
+ F_{v\bar{w}} &= 0\,,
+\end{align}
+Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
+\be
+A_u=0 \text{ and } \eqn{SDLightCone1} \quad\Rightarrow \quad A_w=0
+\ee
+The second equation \eqn{SDLightCone2}  then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
+\be
+A_w=0\,,\,A_u=0 \text{ and }\eqn{SDLightCone2} \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
+\ee
+This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
+\be\label{SDDef}
 A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
 \ee
-Expanding out the equations of motion for the Yang-Mills Lagrangian, yields the following expression in terms of the gauge fields:
-\be
-D^\mu F^{\mu\nu} =0\qquad  \Rightarrow\qquad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
+Using this definition on the final self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
+\be\label{SDEOM}
+\eqn{SDLightCone1} \text{ and } \eqn{SDDef} \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
 \ee
 Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
+\begin{eBox}
 \be
@@
 \ee
-\subsection{ZM-theory} The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:
-\be
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) 
-\ee
+\end{eBox}
+The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
+\ee
+In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
+In this form, we can see the effect \eqn{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
+Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.
+
+As we will show in \sect{}, the color-dual nature of SDYM can be understood as a direct consequence of isolating the \textit{cubic-sector} of the full Yang-Mills amplitudes by projecting along particular on-shell states.
+For this reason, the color-dual nature depends critically on the loop order of the amplitude and does not hold generically beyond one-loop.
+
+Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \eqn{SDEOM}.
+\paragraph{ZM-theory} The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:
+\begin{eBox}
+\be
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right]
+\ee
+\end{eBox}
 where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $ and $\epsilon_{\mu\nu}$ is the two-dimensional Levi-Civita symbol.
@@
 \end{align}
-\subsection{J-theory}
-\be
-\mathcal{L}^{\text{J}} = \frac{1}{2}\partial_\mu J_\nu \bar{J}^{\mu\nu} +g f^{abc} \bar{J}_{\mu\nu}J^\mu J^\nu
-\ee
+Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
+As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
+Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
+This is essentially what $J$-theory does, as we will show below.
+\paragraph{J-theory} There is an alternative Lagrangian formulation of NLSM constructed by Chueng and one of the authors, that instead starts from the chiral current description of NLSM:
+\be
+\mathcal{L} = \text{tr}[\partial U \partial U^{-1}] \equiv \text{tr}[J^\mu J_\mu]
+\ee 
+where $J_\mu = U\partial_\mu U^{-1}$.
+To build the J-theory Lagnraigna, we can think of the chiral current $J^\mu$ as a \textit{pure gauge} vector field.
+Thus, the field strength for $J_\mu$ must vanish, this yielding an equivalent on-shell formulation of the EOM:
+\be
+\Box J^\mu +g f^{abc} J^\nu J^{\mu\nu} = 0
+\ee
+where we have applied the gauge condition $\partial_\mu J^\mu = 0$.
+Adding back in a $\bar{J}^\mu$ auxiliary field as a Lagrange multiplier, we obtain the following Lagrangian that is manifestly color-dual:
+\begin{eBox}
+\be
+\mathcal{L}^{\text{J}} = \frac{1}{2}(\partial J)(\partial \bar{J}) +g f^{abc} \bar{J}_{\mu\nu}J^\mu J^\nu
+\ee
+\end{eBox}
 where as above, $\bar{J}_{\mu\nu} = \partial_\mu J_\nu - \partial_\nu J_\mu$.
-Subject to the Lorenz gauge condition, $\partial_\mu J^\mu =0$, this Lagrangian produces precisely the EOM for J-theory needed for Berends-Giele recursion at tree-level:
-\be
-\partial^2 J^\mu - gf^{abc} J^\nu \partial_\nu J^\mu = 0 
-\ee
+Subject to the Lorenz gauge condition, $\partial_\mu J^\mu =0$.
+This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states.
 As such, the single vertex in this theory is the same as for YZ theory:
@@
 \ee
-
-\be
-\mathcal{L}^{\text{SDYM}} = \frac{1}{2}(\partial \bar{\Phi} )^a(\partial  \Phi)^a +g f^{abc} \bar{\Phi} ^a (\partial_u \Phi)^b (\partial_v \Phi)^c
-\ee
-\be
-(\varepsilon^+_1 k_2) - (\varepsilon^+_2 k_1) = [12]\left(\frac{\langle 2 q\rangle}{\langle 1 q\rangle} + \frac{\langle 1 q\rangle}{\langle 2 q\rangle} \right) \sim [12]
-\ee
 Now we are prepared to discuss the one-loop case. 
-
-\section{One-loop}
-
-\subsection{NLSM -- Nic}
-
-\draftnoteJM{I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.}
-
+\subsection{Color-dual Bootstrap}
+Some background here on how we approach color-dual bootstrap. Building an ansatz from irreducible lorentz products (ISPs). Comments about:
+\begin{itemize}
+\item loop momenta weight counting 
+\item polynomial vector spaces 
+\item generalized gauge freedom
+\item functional jacobi constraints and cuts
+\end{itemize} 
+\section{Isolating the cubic sector}
+Here we'll describe the why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
+It has to do with out the vector state sum mixes with the four-point contact.
+In terms of our previously defined Feynman rules, the three-point YM vertex takes the form:
+\be
+\cubic{hgrey0}{gluon}{}{gluon}{}{gluon}{}  =  \cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed} + \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} + \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} +\text{h.c.}
+\ee
+The state-sum between two three-point gluon vertex yields the following expansion in terms of YZ-theory vertices:
+\be
+ \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
+\ee
+All the $(\epsilon\epsilon)^1$ diagram permutations are isolated to the cubic sector and together manifest color-kinematics duality.
+However, the exception of the last diagram which introduces a $(\epsilon\epsilon)^2$ factor, must conspire with the Yang-Mills contact to preserve the duality off-shell
+
+\be
+\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed} = (s_{13}-s_{12}) \epsilon_{(12)} \epsilon_{(34)}
+\ee
+One was to resolve this is to introduce higher spin modes in order to accomodate the internal index contractions needed to recover the s-channal contract:
+\be
+\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{graviton}{nhpRed}{}{nhpRed} = s_{12 }(\epsilon_{(13)} \epsilon_{(24)} - \epsilon_{(14)} \epsilon_{(23)})
+\ee
+While introducing succesively higher spiin states to the NMHV lagrangian constructed in \cite{} could in principle work at tree level, we will see that it is not consiisntent with what we find at general loop order.
+We will comment on this in \sect{}.
+For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.
+This is easily understood in terms of a polarization decomposition introduced by one of the authors \cite{} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations.
+\subsection{Block Decomposition of Yang-Mills}
+Describe how different orders in $\varepsilon_i\varepsilon_j$ in pure Yang-Mills captures different cubic and contact sectors of the theory.
+All the $D$-dimensional Lagnrangians above can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order.
+Start with reducible amplitude block decomp from Ref.
+\cite:
+\begin{eBox}
+\begin{equation}\label{eq:pureVecRABD}
+A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+\end{equation}
+\end{eBox}
+By a simple mass-dimensioin argument, we know the tree-level cubic sector is simply:
+\be
+A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+\ee
+and likewise at one-loop:
+\be
+A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+\ee
+We can select out both of these manifestly cubic sectors by selecting only $\epsilon^+\epsilon^+$ in light-cone gauge (i.e.
+SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states.
+Indeed, the $D$-dimensional description of $J$ theory is just the following blocks in the RABD expansion of Yang-Mills:
+\be
+A(...,\bar{J}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
+\ee
+and similarly so at one-loop:
+\be
+A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}
+\ee
+To recover NLSM at one-loop, we need to extract out the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars:
+\begin{eBox}
+\be
+A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\epsilon\rightarrow k}
+\ee
+\end{eBox}
+Why must we take the derivative with respect to $D$?
+After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators.
+However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes.
+Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes.
+However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit.
+We will construct these one-loop integrands below in the next section.
+\subsection{One-loop SDYM Integrands}
+\be
+\simplebox = g_{\text{YM}}^4 X(k_1,l_1)X(k_2,l_2)X(k_3,l_3)X(k_4,l_4)
+\ee
+\subsection{One-loop NLSM Integrands}
+
+Note from James:  I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.
 \be
@@
 Where we have define the antisymmetric kinematic variable, $[LR] = l_i^L - l_R^2$
-\subsection{BELs and integration zeros -- Nic}
-
-At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles.
-Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.
-Thus, $Y\!Z$ theory gives us the following one-loop $n$-gon numerator:
-\be
-N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+2\, (F^1F^2\cdots F^n)
-\ee
-where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops.
-Plugging in the Feynman rule of \eqn{eq:FeynmanRuleYYZ} and \eqn{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
-\be
-N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
-\ee
-and similarly so for the internal vector contribution:
-\be
- (F^1F^2\cdots F^n) = (D-4)(l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
-\ee
-The dimension dependent factor essentially counts that number of internal vector states.
-While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM.
-However, the scalar contribution, that comes dressed with an overall factor $(D-4)$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts.
-In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality.
-We leave this as a direction of future work.
-
-While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $Y\!Z$ loop alone gives us a desired expression for the $n$-gon.
-The important takeaway is that we now have a guess for the form of the off-shell three-point vertex that has a chance of manifesting the duality off-shell.
-The $n$-gon numerator above has scalar insertions of the following kinematic vertex:
-\be
-T^{a}_{LR} = k_a(l_L-l_{R}) = (l_L+l_{R}) (l_L-l_{R})  = l_L^2-l_{R}^2 
-\ee
-Given this structure, in the next section we will attempt to construct two-loop basis diagrams from these cubic vertex assignments and try to reverse engineer the particle content that produces these master numerators.
-
-Before proceeding, we note a strange property of the $n$-gon numerator for the pions.
-In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs).
-However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble.
-The BEL diagram can be reconstructed from the $n$-gon as follows:
-\be
-N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
-\ee
-where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
-\be
-N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
-\ee
-Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
-\be
-\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
-\ee
-where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$.
-Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
-
-\section{Two-loop}
+\subsection{Two-loop Obstruction}
+
+\section{Bootstrapping two-loop...}
 
@@
 \section{Discussion}\label{sec:Discussion}
+\section{... and Beyond}
+This could be a section about our expectations for all-loop construction requiring non-local color-dual integrands. Lay out contrafactual proof, i,e. define the following statement:
+\be
+ Q_L=\textit{``the $L$-loop numerator is polynomial and color-dual"}. 
+\ee
+Then it is clear that if the kinematic numerator is polynomial and color-dual, evaluating it in kinematic regions where the internal legs are on-shell won't disrupt the kinematic algrebraic relations, and it must still be polynomial.
+Thus we find:
+\be
+Q_L \Rightarrow Q_{L-1}
+\ee
+Or equivalently,
+\be
+\text{not }Q_{L-1}\Rightarrow \text{not }Q_L
+\ee
+We have found that the two-loop integrand for Yang-Mills cannot be constructed from a color-dual polynomial kinematic numerator.
+Thus, if a color-dual representation exists at all-loop order for Yang-Mills it must be a rational function of kinematics.
 
@@
 
+\appendix
+\section{Spinor-Helicity Variables and Conventions}
+Dimensions will generically be away from four, in $D=4-2\epsilon$, with $\epsilon$ arbitrary.
+As noted, it will be convenient to take $D\rightarrow 4$ in certain circumstances after integration.
+In such cases we will employ appropriate spinor-helicity variables.
+Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now.
+For massless momenta, $k_a$ and $k_b$, we have
+\begin{equation}
+s_{ab} = (k_a+k_b)^2= \langle ab \rangle[ba]\,,
+\end{equation}
+the component definition of our spinor bracket that are consistent with the conventions above,
+\begin{align}
+\langle ab \rangle &= \frac{(a_1 + i a_2)(b_0+b_3)-(b_1 + i b_2)(a_0+a_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
+\\
+[ab] &= \frac{(b_1 - i b_2)(a_0+a_3)-(a_1 - i a_2)(b_0+b_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
+\end{align}
+where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
+\begin{equation}\label{eqn:4DPols}
+\begin{aligned}
+k_a \cdot \varepsilon_b^{(+)} &= \frac{\langle q a \rangle[ab]}{\sqrt{2}\langle q b\rangle}\,,
+\qquad\quad \qquad
+k_a \cdot \varepsilon_b^{(-)} = -\frac{[qa]\langle ab\rangle}{\sqrt{2}[qb]}\,,
+\\
+\varepsilon_a^{(-)}\cdot \varepsilon_b^{(+)} &= - \frac{\langle q a\rangle [qb]}{ [qa]\langle q b\rangle} \,,
+\qquad \qquad
+\varepsilon_a^{(\pm)}\cdot \varepsilon_b^{(\pm)} = 0 \,,
+\end{aligned}
+\end{equation}
+Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets.
+In terms of light-cone coordinates that we employed in the text, the angles and squares can be rewritten as follows:
+\begin{align}
+\langle ab \rangle &= \frac{a_w b_u-a_u b_w}{\sqrt{a_ub_u}}\,,
+\\
+[ab] &= \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{\sqrt{a_ub_u}}\,,
+\end{align}
+The conventions we use in the text where the holomorphic spinor cares extra mass dimension essentially amounts to shifting the bracket by the following:
+\begin{align}
+\langle ab \rangle &\rightarrow a_w b_u-a_u b_w \equiv X(a,b)\,,
+\\
+[ab] &\rightarrow \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{a_ub_u}\equiv Q(a,b)\,,
+\end{align}
+With this, we still obtain the same completeness relation for the SDYM spinors:
+\be
+X(a,b)Q(b,a) = \frac{1}{2}s_{ab}
+\ee
+\section{Regulating BEL integrals}
+At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles.
+Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.
+Thus, $Y\!Z$ theory gives us the following one-loop $n$-gon numerator:
+\be
+N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+2\, (F^1F^2\cdots F^n)
+\ee
+where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops.
+Plugging in the Feynman rule of \eqn{eq:FeynmanRuleYYZ} and \eqn{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
+\be
+N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
+\ee
+and similarly so for the internal vector contribution:
+\be
+ (F^1F^2\cdots F^n) = (D-4)(l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
+\ee
+The dimension dependent factor essentially counts that number of internal vector states.
+While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM.
+However, the scalar contribution, that comes dressed with an overall factor $(D-4)$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts.
+In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality.
+We leave this as a direction of future work.
+
+While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $Y\!Z$ loop alone gives us a desired expression for the $n$-gon.
+The important takeaway is that we now have a guess for the form of the off-shell three-point vertex that has a chance of manifesting the duality off-shell.
+The $n$-gon numerator above has scalar insertions of the following kinematic vertex:
+\be
+T^{a}_{LR} = k_a(l_L-l_{R}) = (l_L+l_{R}) (l_L-l_{R})  = l_L^2-l_{R}^2 
+\ee
+Given this structure, in the next section we will attempt to construct two-loop basis diagrams from these cubic vertex assignments and try to reverse engineer the particle content that produces these master numerators.
+
+Before proceeding, we note a strange property of the $n$-gon numerator for the pions.
+In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs).
+However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble.
+The BEL diagram can be reconstructed from the $n$-gon as follows:
+\be
+N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
+\ee
+where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
+\be
+N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
+\ee
+Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
+\be
+\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
+\ee
+where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$.
+Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
 \bibliographystyle{JHEP}
@@
 \end{document}
+
+%%% Local Variables: 
+%%% TeX-command-extra-options: "-shell-escape"
+%%% End:

### 2023-08-17 notes/2loopNLSM.tex
Rearranged subsections in Review slightly

@@
 \end{eBox}
+\draftnoteJM{I don't think there should be a factor of 1/2 in the kinetic term.}
 The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
@@
 Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \eqn{SDEOM}.
-\paragraph{ZM-theory} The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:
-\begin{eBox}
-\be
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right]
-\ee
-\end{eBox}
-where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $ and $\epsilon_{\mu\nu}$ is the two-dimensional Levi-Civita symbol.
-Expanded out into spacetime components, the momentum space Feynman rule for this theory is simply:
-\be
-\langle ab\rangle \equiv p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle 
-\ee
- From the interaction part of the Lagrangian, we can see that the three-point vertex is (1) functionally symmetric and (2) the kinematics are completely anti-symmetric: 
-\be
-\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
-\ee
-This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
-In addition to anti-symmetry, the cubic graphs will satisfy jacobi off-shell on any internal edge due to the delta function identity of 2D Levi-Civita symbols:
-\be
-\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle = \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c=0
-\ee
-Theories with this property are the creme de la creme of color-dual gauge theories as they trivially satisfy color-kinematic algebraic relations off-shell.
-This allows one to trivially promote the duality from tree-level to all-loop order by dressing each cubic vertex with its own kinematic structure constant.
-
-Later in this section we will show that the interaction vertex is precisely that belonging to self-dual Yang-Mills (SDYM) theory in light-cone gauge.
-However, as we'll see, the kinetic term for these two theories differ -- the SDYM kinetic term transmutes between the holomorphic field $\Phi$, and the anti-holomorphic field, $\bar{\Phi}$, while the ZM scalar leaves the kinematic sector untouched.
-this is a critical distinction between the two theories that has important consequences for their color-dual constructions at loop-level.
-
-While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization.
-Similar to the difficulties of renormalizing chiral fermions \cite{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
-As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
+
 \paragraph{YZ-Theory} Thus far, the two color-dual Lagrangians we have discussed make explicit reference to the spacetime dimension ($D=4$ for SDYM, and $D=2$ for ZM theory).
@@
 Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
-This is essentially what $J$-theory does, as we will show below.
-\paragraph{J-theory} There is an alternative Lagrangian formulation of NLSM constructed by Chueng and one of the authors, that instead starts from the chiral current description of NLSM:
-\be
-\mathcal{L} = \text{tr}[\partial U \partial U^{-1}] \equiv \text{tr}[J^\mu J_\mu]
-\ee 
-where $J_\mu = U\partial_\mu U^{-1}$.
-To build the J-theory Lagnraigna, we can think of the chiral current $J^\mu$ as a \textit{pure gauge} vector field.
-Thus, the field strength for $J_\mu$ must vanish, this yielding an equivalent on-shell formulation of the EOM:
-\be
-\Box J^\mu +g f^{abc} J^\nu J^{\mu\nu} = 0
-\ee
-where we have applied the gauge condition $\partial_\mu J^\mu = 0$.
-Adding back in a $\bar{J}^\mu$ auxiliary field as a Lagrange multiplier, we obtain the following Lagrangian that is manifestly color-dual:
+This is essentially what $J$-thepory does, as we will show below.
+\paragraph{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
+For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
+The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
+First order formulation of NLSM in terms of chiral current $J^\mu$.
+Two equations.
+Two constraints, the field strength should vanish
+\be
+\label{eq:FieldStrengthJ}
+F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
+\ee
+which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
+The second condition is that the chiral current should be in Lorenz gauge
+\be
+\label{eq:LorenzGaugeJ}
+\partial_\mu J^\mu=0
+\ee
+which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
+Taking a linear combination of \eqref{eq:FieldStrengthJ} and \eqref{eq:LorenzGaugeJ} yields
+\be
+\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
+\ee
+Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian
 \begin{eBox}
 \be
-\mathcal{L}^{\text{J}} = \frac{1}{2}(\partial J)(\partial \bar{J}) +g f^{abc} \bar{J}_{\mu\nu}J^\mu J^\nu
+\mathcal{L}^{\text{J}} =\bar{J}^\mu \Box J_\mu +g f^{abc} \bar{J}^\mu J^\nu \partial_\nu J^\mu .
 \ee
 \end{eBox}
-where as above, $\bar{J}_{\mu\nu} = \partial_\mu J_\nu - \partial_\nu J_\mu$.
-Subject to the Lorenz gauge condition, $\partial_\mu J^\mu =0$.
-This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states.
-As such, the single vertex in this theory is the same as for YZ theory:
+By calculating an off-shell 4pt correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
+Kinematic algebra is diff algebra (as usual).
+How to extract physical states... (longitudinal J, weird J bar, restores broken Bose).
+
+This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states. As such, the single vertex in this theory is the same as for YZ theory: 
 \be
@@
 \ee
+
+\paragraph{ZM-theory}
+While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
+Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$.
+This trivially enforces Lorenz gauge while the vanishing field strength condition...
+
+The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:
+\begin{eBox}
+\be
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right]
+\ee
+\end{eBox}
+where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $ and $\epsilon_{\mu\nu}$ is the two-dimensional Levi-Civita symbol.
+Expanded out into spacetime components, the momentum space Feynman rule for this theory is simply:
+\be
+\langle ab\rangle \equiv p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle 
+\ee
+ From the interaction part of the Lagrangian, we can see that the three-point vertex is (1) functionally symmetric and (2) the kinematics are completely anti-symmetric: 
+\be
+\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
+\ee
+This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
+In addition to anti-symmetry, the cubic graphs will satisfy jacobi off-shell on any internal edge due to the delta function identity of 2D Levi-Civita symbols (TODO:  show the identity, say that the following is Schouten, cite Schouten?, comment on addition of masses):
+\be
+\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle = \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c=0
+\ee
+Theories with this property are the creme de la creme of color-dual gauge theories as they trivially satisfy color-kinematic algebraic relations off-shell.
+This allows one to trivially promote the duality from tree-level to all-loop order by dressing each cubic vertex with its own kinematic structure constant.
+
+Later in this section we will show that the interaction vertex is precisely that belonging to self-dual Yang-Mills (SDYM) theory in light-cone gauge.
+However, as we'll see, the kinetic term for these two theories differ -- the SDYM kinetic term transmutes between the holomorphic field $\Phi$, and the anti-holomorphic field, $\bar{\Phi}$, while the ZM scalar leaves the kinematic sector untouched.
+this is a critical distinction between the two theories that has important consequences for their color-dual constructions at loop-level.
+
+While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization.
+Similar to the difficulties of renormalizing chiral fermions \cite{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
+As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
+
 Now we are prepared to discuss the one-loop case.
+
 \subsection{Color-dual Bootstrap}
@@
 \begin{itemize}
+\item Mention NANS after j theory.  Color kinematics duality doesn't care about the propagator but using a funny one might mess up locality in the double copied theory.
 \item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
@@
 Point out that all of the theories that come from have CK are really some version of YM where you (1) impose some condition like F=0 or some other condition on the field strength and (2) you impose Lorenz gauge.
+Point out that the kinematic algebra is always diffs.
+\item Cite papers arguing about whether NLSM in 2D is non-trivial or not.
 \item Explain why you need to take a certain portion of the YZ numerator to get the right answer.
@@
 This is the object we include in the ancillary files, maybe with the remaining variables set to zero
+
+For 4pt on-shell ZM, the LRLR configuration is zero and for every other configuration of external states the on-shell amplitude is subtle because of IR poles.
+Note that the (on-shell) kinematic numerators are always unambiguous and never suffer from any of these subtleties in any kinematic configuration.
+So when you compare against ZM, you either comparing against zero or something subtle.
+This is why you can't really take cuts of the NLSM and ZM integrands and meaningfully compare them even though you can compare their numerators.
 

### 2023-08-17 notes/2loopNLSM.tex
Added to Review section

@@
 
-\paragraph{YZ-Theory} Thus far, the two color-dual Lagrangians we have discussed make explicit reference to the spacetime dimension ($D=4$ for SDYM, and $D=2$ for ZM theory).
-This makes them poorly suited for constructing dimensionally regulated integrals in loop-level amplitudes.
-Here we briefly review YZ-theory, which is a honest $D$-dimensional theory first proposed by Cheung and Hsien \cite{Cheung2016prv} for the purpose of describing nonlinear sigma model (NLSM) scattering.
+\paragraph{YZ-Theory}
+SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \sect{sec:ZMTheory}, does as well.
+This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
+On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung2016prv}.
+
 One can understand YZ-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions. 
-
 Starting with the Yang-Mills Lagrangian, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
@@
 \be
+\label{eq:JTheoryEOM}
 \Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
@@
 
+\draftnoteJM{Put comment about the fact that you can use funny propagators without affecting CK earlier.  Mention NANS as modification of J-theory.}
+
 \paragraph{ZM-theory}
+\label{sec:ZMTheory}
 While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
-Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$.
-This trivially enforces Lorenz gauge while the vanishing field strength condition...
-
-The Lagrangian for Zakharov-Mikhailov (ZM) theory is a simple $SU(N)$ scalar theory defined in two spacetime dimensions:
+Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
+After plugging $\varphi$ into \eqref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
 \begin{eBox}
@@
 \end{eBox}
-where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $ and $\epsilon_{\mu\nu}$ is the two-dimensional Levi-Civita symbol.
-Expanded out into spacetime components, the momentum space Feynman rule for this theory is simply:
-\be
-\langle ab\rangle \equiv p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle 
-\ee
- From the interaction part of the Lagrangian, we can see that the three-point vertex is (1) functionally symmetric and (2) the kinematics are completely anti-symmetric: 
+where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $.
+This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
+The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian, giving
+\be
+\langle ab\rangle \equiv p_a^\mu \epsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
+\ee
+The vertex is (1) functionally symmetric and (2) the kinematic portion of the vertex is completely anti-symmetric: 
 \be
@@
 This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
-In addition to anti-symmetry, the cubic graphs will satisfy jacobi off-shell on any internal edge due to the delta function identity of 2D Levi-Civita symbols (TODO:  show the identity, say that the following is Schouten, cite Schouten?, comment on addition of masses):
-\be
-\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle = \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c=0
-\ee
-Theories with this property are the creme de la creme of color-dual gauge theories as they trivially satisfy color-kinematic algebraic relations off-shell.
-This allows one to trivially promote the duality from tree-level to all-loop order by dressing each cubic vertex with its own kinematic structure constant.
+To prove off-shell color kinematics duality for any multiplicity and loop order it is enough to observe that the sum of the off-shell $s$-, $t$-, and $u$-channel numerators sum to zero
+\be
+\label{eq:ZMJacobi}
+\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
+\ee
+by virtue of the 2D Levi-Civita identity $\epsilon_{\mu\nu}\epsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
+Amusingly, \eqref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.
+
+Since ZM theory manifested color-kinematics duality without any reference to the on-shell condition, a mass term can be added to ZM theory without spoiling color-kinematics duality.
+In fact, the kinetic term could be dramatically altered.
+In general, if the on-shell conditions are not used, color-kinematics duality admits any kinetic term but the choice of propagator might spoil locality in the double-coppied theory.
 
@@
 Now we are prepared to discuss the one-loop case.
+
+\paragraph{Generalities of known color-dual theories -- James (I'll come back to this later)}
+\begin{itemize}
+\item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
+\item All of the theories described above have diff as kinematic algebra
+\item All of the theories choose a simple gauge like Lorenz or lightcone
+\item All of the theories place some constraint on the field strength directly and get their equations of motion directly from that constraint, not the YM EOM.
+\item (Almost all of the theories (aside from NLSM) have trivial amplitudes at least at tree level)
+\item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
+\end{itemize}
 
@@
 \item Are you sure that the SDYM EOM doesn't come from just $F=\epsilon F$?  If $A=\partial \Phi$ then $F$ has the right number of derivatives to give the SDYM EOM but $DF$ has too many.
-\item I believe the j-theory Lagrangian does not lead to the correct EOM as currently written.
 \item Write Lagrangian for j-theory and reiterate the argument about why you know it's pions.

### 2023-08-21 notes/2loopNLSM.tex
small edits -- giving back to james

@@
 \usepackage{slashed}
+\usepackage{anyfontsize}
 \usepackage{tocloft}
@@
 \newcommand{\ace}[1]{\textcolor{darkgreen}{\textbf{AE:}{#1}}}
+\newcommand{\nhp}[1]{\textcolor{nhpRed}{\textbf{NHP:}{#1}}}
 
@@
 
-\tikzset{graviton/.style={decorate, decoration={snake, amplitude=.4mm, segment length=1.5mm, pre length=.5mm, post length=.5mm}, double}}
+\tikzset{Bfield/.style={decorate, double}}
+
+\iffalse
 \tikzfeynmanset{compat=1.1.0}
@@
 ]
+\fi
 \tikzfeynmanset{
@@
 (mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,red](mid2),
+(mid5) --[ultra thick,nhp4](mid2),
 (mid5) --[ultra thick,](mid6),
@@
 (mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,red](mid2),
+(mid5) --[ultra thick,nhp4](mid2),
 (mid3) --[ultra thick,](mid4),
@@
 (mid5) --[ultra thick,](mid3),
-(mid5) --[ultra thick,red](mid2),
+(mid5) --[ultra thick,nhp4](mid2),
 (mid3) --[ultra thick,](mid4),
@@
 (mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,red](mid4),
+(mid1) --[ultra thick,nhp4](mid4),
 (mid5) --[ultra thick,](mid7),
@@
 (mid3) --[ultra thick,](mid4),
-(x1) --[ultra thick,dashed,blue](x2),
+(x1) --[ultra thick,dashed,nhp4](x2),
 };
@@
 
-\author{Alex Edison,}
-\author{James Mangan,}
-\author{and Nicolas H. Pavao}
+\author{\large Alex Edison,}
+\author{\large James Mangan,}
+\author{\large and Nicolas H. Pavao}
 
@@
 
-\title{\center Towards Globally Color-Dual All-Loop Integrands}
+\title{\center  \fontsize{18.8}{20} \selectfont  Towards Globally Color-Dual All-Loop Integrands}
 
@@
 Here we briefly review the off-shell examples of the kinematic algebra that will be relevant in this paper.
+\be
+\mathcal{L}^{\text{semi-YM}} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} - \frac{g}{2} G_{\mu\nu} [A_\mu, A_\nu]
+\ee
 \paragraph{Self-Dual Yang-Mills} The first example in the literature \cite{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
@@
 \be
-\mathcal{L}^{\text{SDYM}} = \frac{1}{2}(\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
+\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
 \ee
 \end{eBox}
-\draftnoteJM{I don't think there should be a factor of 1/2 in the kinetic term.}
 The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
@@
 \subsection{Color-dual Bootstrap}
-Some background here on how we approach color-dual bootstrap. Building an ansatz from irreducible lorentz products (ISPs). Comments about:
+Some background here on how we approach color-dual bootstrap (as we will utilize in our two-loop construction). Building an ansatz from irreducible lorentz products (ISPs). Comments about:
 \begin{itemize}
@@
 \end{itemize} 
+I suggest we put this all here in the intro/review so that people who know can skip, and then people who don't can read it and then be prepared to understand our approach before getting to the two-loop section.
 \section{Isolating the cubic sector}
@@
 \be
-\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{graviton}{nhpRed}{}{nhpRed} = s_{12 }(\epsilon_{(13)} \epsilon_{(24)} - \epsilon_{(14)} \epsilon_{(23)})
+\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{Bfield}{nhpRed}{}{nhpRed} = s_{12 }(\epsilon_{(13)} \epsilon_{(24)} - \epsilon_{(14)} \epsilon_{(23)})
 \ee
@@
 As this is too many parameters for \texttt{Mathematica} to reasonably handle, we employ a custom solver suitable for the moderately dense systems appearing in this context.
-(Scalars might generate denser systems since ever dot product can interfere with every other unlike gauge theories which separate based on polarization structure, can cite Nic.)
+(Scalars might generate denser systems since ever dot product can interfere with every other unlike gauge theories which separate based on polarization structure, can cite Nic.
+\nhp{ distinguish between NLSM and YM ansatz -- i.e.
+why is 10,010 per diagram solvable for YM, but 8,008 per diagram runs into issues for NLSM.
+As you said, emphasize the density of NLSM matrix inversion due to generalized gauge freedom vs.
+independent polarization structures for YM.})
 
@@
 
-\subsection{YM revisit -- Alex}
+\subsection{Yang-Mills revisited -- Alex}
 Transition paragraph.....
@@
 
-\section{Discussion}\label{sec:Discussion}
 \section{... and Beyond}
@@
 
+\section{Discussion}\label{sec:Discussion}
 \paragraph{Acknowledgments} The authors would like to thank ...
@@
 \appendix
-\section{Spinor-Helicity Variables and Conventions}
+\section{Spinor-Helicity and Conventions}
 Dimensions will generically be away from four, in $D=4-2\epsilon$, with $\epsilon$ arbitrary.

### 2023-08-21 notes/2loopNLSM.tex
About to rearrange color dual bootstrap sections

@@
 \ee
-\paragraph{Self-Dual Yang-Mills} The first example in the literature \cite{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
+\draftnoteJM{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
+\subsubsection{Self-Dual Yang-Mills} The first example in the literature \cite{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
 \be
@@
 \ee
-Using this definition on the final self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
+Using this definition on the final \draftnoteJM{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
 \be\label{SDEOM}
@@
 
-\paragraph{YZ-Theory}
+\subsubsection{YZ-Theory}
 SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \sect{sec:ZMTheory}, does as well.
@@
 This is essentially what $J$-thepory does, as we will show below.
-\paragraph{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
+
+\subsubsection{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
 For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
@@
 
-\draftnoteJM{Put comment about the fact that you can use funny propagators without affecting CK earlier.  Mention NANS as modification of J-theory.}
-
-\paragraph{ZM-theory}
+\subsubsection{Zakharov-Mikhailov theory}
 \label{sec:ZMTheory}
@@
 \be
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right]
+\label{eq:ZMLagrangian}
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
 \ee
 \end{eBox}
-where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $.
 This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
-The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian, giving
+ZM theory can also be tenuously motivated from SDYM theory.
+The power counting of the interaction term in the SDYM equation of motion \eqref{SDEOM} makes it clear that the theory is critical in 2D.
+This suggests that the two lightcone coordinates $u$ and $w$ should be identified as the coordinates of the 2D space.
+The 4D d'Alembertian in lightcone coordinates, $\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$, cannot be interpreted as the 2D equivalent, so the kinetic term of SDYM must be scrapped and replaced with the correct 2D version.
+This argument should be understood purely as an alternative route to ZM theory.
+While NLSM and ZM are the same theory classically when restricted to 2D, SDYM and ZM are not because, for example, the tree amplitudes of SDYM vanish but those of ZM do not (cite argumentative papers).
+
+The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \eqref{eq:ZMLagrangian}, giving
 \be
@@
 In fact, the kinetic term could be dramatically altered.
-In general, if the on-shell conditions are not used, color-kinematics duality admits any kinetic term but the choice of propagator might spoil locality in the double-coppied theory.
-
-Later in this section we will show that the interaction vertex is precisely that belonging to self-dual Yang-Mills (SDYM) theory in light-cone gauge.
-However, as we'll see, the kinetic term for these two theories differ -- the SDYM kinetic term transmutes between the holomorphic field $\Phi$, and the anti-holomorphic field, $\bar{\Phi}$, while the ZM scalar leaves the kinematic sector untouched.
-this is a critical distinction between the two theories that has important consequences for their color-dual constructions at loop-level.
+In general, if the on-shell conditions are not used, color-kinematics duality is unaffected by the details of the propagator structure.
+Of course, dramatically altering the pole structure could spoil locality in the double-coppied theory.
+As already mentioned, the only difference classically between ZM and SDYM is the propagator structure.
+While both theories are color dual for the same reason, altering the propagators has profound consequences since SDYM tree amplitudes vanish and manifest color-kinematics does not persist to all loop orders.
+Color dual theories with the same interactions but different kinetic terms have appeared in the literature before.
+For example, J-theory and the theory of non-Abelian fluids presented in \cite{Cheung:2020djz} differ only in their propagators.
+Specifically, taking the static limit of the fluid's $(D+1)$-dimensional kinetic term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates yields the relativistic d'Alembertian of $D$-dimensional J-theory.
 
@@
 
-Now we are prepared to discuss the one-loop case.
-
-\paragraph{Generalities of known color-dual theories -- James (I'll come back to this later)}
+\subsubsection{Wess-Zumino-Witten theory -- James}
+I want to write this down or I'm going to completely forget it
+
+\subsubsection{Chern-Simons theory -- James}
+We won't use this but it's useful to treat all of the CK theories in one place
+Cite Henrik Maor
+Again you place some constraint on the field strength and use Lorenz gauge
+
+\subsubsection{Generalities of known color-dual theories -- James}
+Should this section maybe go first?
+
 \begin{itemize}
@@
 \item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
+\item For off-shell CK, the kinetic term is relatively unimportant so long as the poles are correctly/consistently identified (what do you mean by s,t,u channel poles).
+This might screw up locality in the squared theory.
 \end{itemize}
+
+Now we are prepared to discuss the one-loop case.
 
@@
 \begin{itemize}
-\item Mention NANS after j theory.  Color kinematics duality doesn't care about the propagator but using a funny one might mess up locality in the double copied theory.
 \item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
-\item Are you sure that the SDYM EOM doesn't come from just $F=\epsilon F$?  If $A=\partial \Phi$ then $F$ has the right number of derivatives to give the SDYM EOM but $DF$ has too many.
-\item Write Lagrangian for j-theory and reiterate the argument about why you know it's pions.
-Reiterate connection to ZM (dualize j and integrate in phi).
-Should probably mention CS somewhere.
-Point out that all of the theories that come from have CK are really some version of YM where you (1) impose some condition like F=0 or some other condition on the field strength and (2) you impose Lorenz gauge.
-Point out that the kinematic algebra is always diffs.
 \item Cite papers arguing about whether NLSM in 2D is non-trivial or not.

### 2023-08-21 notes/2loopNLSM.tex
Moved 2-loop bootstrap review to 'Review' section

@@
 Review of BCJ relations and Jacobi relations off-shell. Justify kinematic algebra in an off-shell framework by talking about on-shell construction. yada yada yada
-\subsection{Color-dual Lagrangians} In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual.
+
+\subsection{Color-dual Lagrangians}
+\label{sec:CKLagrangians}
+In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual.
 As we will show, taking forward limits of tree-level numerators works as long as one can construct an off-shell description with a Lagrangian.
@@
 
+Should probably also mention that BAS has CK at Lagrangian level (duh).
+
+Cubic 2-form theory also has trivial CK.
+
 \subsubsection{Chern-Simons theory -- James}
@@
 \item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
-\item All of the theories described above have diff as kinematic algebra
+\item All of the theories described above have diff as kinematic algebra, SU(N) for BAS, or rigid/spin Lorenz for cubic 2-form theory
 \item All of the theories choose a simple gauge like Lorenz or lightcone
@@
 \end{itemize}
-I suggest we put this all here in the intro/review so that people who know can skip, and then people who don't can read it and then be prepared to understand our approach before getting to the two-loop section.
+
+References for Jacobi, unitarity, etc.
+
+Aside from the few special theories mentioned in \sect{sec:CKLagrangians}, color-dual integrands are constructed from an ansatz.
+
+Different kinds of CK.
+We want global.
+Global is the simplest option, it is also the option that you would automatically get if you had a color-dual Lagrangian.
+By ``global'' we mean that color-kinematics duality is satisfied in any kinematic configuration of the integrand.
+This is a much more stringent condition than absolutely necessary.
+There is reason to believe (cite Zvi et al) that global numerators cannot always be found.
+One resolution to the issue is to only demand color-kinematics duality on the unitarity cuts of the integrand, i.e., in specific kinematic limits.
+Enforcing Jacobi on the cuts is enough to ensure that the squared integrand will correctly cut to gravity (or whatever the squared theory might be).
+When a globally color-dual numerator cannot be found, another alternative explored in the literature is to increase the size of the numerator ansatz by enlarging the numerator from a polynomial to a rational function with spurious singularities (cite Donal et al).
+When global color-kinematics fails, the hope is that it can be restored by enlarging the size of the ansatz, either by giving the numerator of each graph its own ansatz (first option described) or by promoting the numerator to a non-local function (second option described).
+Note that a theory whose Lagrangian has color-kinematics duality would naturally produce a globally color-dual integrand so the quest for a global numerator is closely related to the existence of a Lagrangian exhibiting color-kinematics duality.
+Section X is devoted to color-dual representations of the 4pt 2-loop NLSM integrand and the analogous integrand for YM is treated in section Y.
+Two-loop color-dual integrands for pure YM have been investigated before but only for a limited ansatz that manifests locality (cite Zvi et al paper).
+All of the N=4 SYM constructions below 5-loop are local.
+Mention generalized double copy.
+
+Color-kinematics duality is stated in terms of cubic graphs so the first step is to express in the integrand in terms of such graphs.
+As an example we will focus on the 4pt 2-loop integrand of some color-dual theory like NLSM or YM.
+The 4pt 1-loop integrand is not a sufficiently illustrative example because, for instance, it lacks any self Jacobi like \eqref{eq:TwoLoopJacobiTwo} to be discussed shortly.
+Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and bubble on external leg (BEL) graphs.
+It is always possible to express an integrand in terms of cubic graphs, even for an even valency theory like NLSM, by multiplying and dividing the integrand by factors of inverse propagators.
+Next, the ansatz must have the correct power counting and external states, \emph{e.g.}, polarization vectors for YM.
+The numerator is assumed to be manifestly local but one approach to finding color-dual numerators is to relax manifest locality, see (...) for more details.
+After zeroth order considerations like power counting, there are three conditions that are imposed on the ansatz: (1) Jacobi relations amongst graphs must be satisfied, (2) numerators must respect graph symmetries, and (3) the integrand must have the correct unitarity cuts.
+
+(These three constraints can be solved in any order and my guess is that Alex and I did solve them in different orders.)
+
+\subsubsection{Jacobi relations}
+
+Jacobi relations are the heart of color-kinematics duality.
+The color factors in an integrand obey a set of Jacobi identities.
+Color-kinematics duality states that there exists a way of writing the kinematic numerators of the integrand so that they obey the same set of Jacobi identities.
+(Can trivially read off the adjoint color factors from a cubic graph.)
+So if any triplet of graphs is related by a Jacobi identity, so too must their numerators.
+Broadly speaking there are two kinds of Jacobi identities.
+The first kind relate graphs to a basis.
+For example, the double box, crossed box, and penta-triangle are related to each other as follows
+\be % [[11]]
+\label{eq:TwoLoopJacobiOne}
+\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0.
+\ee
+where the shared propagator is shown in red.
+Using this relation the crossed box can be written in terms of the other two.
+In this way, all of the 14 cubic 4pt 2-loop topologies can be written in terms of a basis of the double box and penta-triangle.
+(Any two of the double box, crossed box, and penta-triangle would suffice for a basis but the planar basis is chosen for simplicity in this work.)
+For global color-kinematics duality each of the two basis graphs receives its own numerator ansatz and the numerator of any other graph can be expressed in terms of these.
+
+The second kind of Jacobi relations relate basis elements to themselves.
+For example, the crossed box numerator is related to itself via the following Jacobi relation
+\be % [[19]]
+\label{eq:TwoLoopJacobiTwo}
+\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
+\ee
+where the shared propagator is shown in red as before.
+Each of the crossed box numerators can be represented in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator ansatze.
+The first kind of Jacobi relations simplifies how many numerators require ansatze whereas the second kind of Jacobi relations place constraints on the remaining numerators.
+In principle there could be Jacobi relations involving tadpoles and BEL graphs, which would be subtle to handle.
+One option is to force the numerators of these graphs to zero.
+However, since these graphs will not contribute to physical unitarity cuts, we take a different approach.
+These graphs are allowed to have non-zero numerators but any Jacobi relations involving them are simply not imposed or solved.
+See (4 loop N=4 paper) for a discussion of BELs in the context of color-kinematics duality.
+
+In total, there are 21 Jacobi relations on the 14 cubic 4pt 2-loop graphs where, again, tadpole and BEL graphs are ignored.
+
+\subsubsection{Graph symmetries}
+
+The second key constraint in an ansatz construction of color-dual numerators comes from graph symmetries.
+Every numerator is required to respect all of the symmetries (or automorphisms) of its associated graph.
+While it is very convenient to impose graph symmetries, it is not completely necessary in order to perform the double copy.
+At tree level, finding manifestly color dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
+Nonetheless, for a pure ansatz construction it is very reasonable to impose graph symmetries.
+Note that the graph symmetry constraint is imposed on \emph{every} graph, not just the basis graphs.
+For example, the crossed box,
+\be
+\CrossedBoxGraphSym ,
+\ee
+is unchanged upon reflection across the horizontal axis (shown as a red dashed line).
+Since the crossed box can be written in terms of the double box and penta-triangle, this imposes non-trivial constraints on the ansatz.
+
+\subsubsection{Unitarity}
+
+The last key constraint is that the ansatz have the correct unitarity cuts, that is, that the integrand corresponds to the correct theory.
+Generalized unitarity has been reviewed in many places (cite...) so we will not belabor the details here, in particular see (emu) for a recent treatment of unitarity methods for even multiplicity theories like NLSM.
+The essence of generalized unitarity is that when internal lines are placed on-shell, the integrand should factorize into a product of on-shell tree amplitudes.
+The cut to be performed can, itself, be encoded in a graph.
+For example, potential 4pt 2-loop cuts include
+\be
+\label{eq:PotentialCuts}
+\text{(a)} \SubtleCut ~~~~ \text{(b)} \PhysicalCutOne{}{}{}{} ~~~~ \text{(c)} \PhysicalCutTwo{}{}{}{} ~~~~ \text{(d)}  \MaxCut
+\ee
+as well as many more.
+In these graphs, all exposed propagators are understood to be cut/on-shell.
+As an equation, a unitarity cut this looks schematically like
+\be
+\label{eq:SchematicCutEquation}
+\sum \limits_\text{topologies} \frac{n \vert_\text{cut}}{\prod \limits_\text{uncut} k^2} = \sum \limits_\text{states} \prod \limits_\text{blobs} A_\text{tree} .
+\ee
+The right hand side of the equation is a product of on-shell tree amplitudes, represented graphically in \eqref{eq:PotentialCuts} by grey blobs.
+States crossing (or propagating across) the cut must be summed over.
+For scalars this sum is trivial but for spinning particles this is no longer the case and the physical state projector must be inserted (see Dimitrius paper for simplifying this operation).
+The graph topologies appearing in the left hand side of \eqref{eq:SchematicCutEquation} come from blowing up the grey blobs into cubic tree graphs in every conceivable way.
+For each of these topologies, the numerator of the associated graph is subjected to the cut constraints and is then divided by the uncut propagators.
+The right hand side is assumed to be known, which places a constraint on the numerator ansatz in the left hand side.
+
+It is possible to work with either color-dressed cuts or color-ordered cuts.
+For color-dressed cuts the grey blobs are blown up into all possible channels and all color factors $f^{abc}$ are explicitly retained on both sides of the unitarity equation \eqref{eq:SchematicCutEquation}.
+For color-ordered cuts the grey blobs are only blown up in color ordered channels, all color factors in \eqref{eq:SchematicCutEquation} are suppressed, and the product of on-shell amplitudes only extends over color-ordered trees.
+Since color-ordered cuts do not contain the full color information of the theory, it is necessary to do multiple color-ordered cuts -- over different orderings of the blob labels -- in order to fully capture all of the cut information.
+For a color dual theory such as NLSM or YM it is enough to do $(n-2)!$ labelings of each blob due to the Kleiss-Kuijf and $U(1)$ decoupling identities (cite KK).
+In this sense color-dressed cuts contain extraneous information that is bypassed when using color-ordered cuts.
+
+In our construction, only well-defined cuts are imposed so, for example, cut (a) of \eqref{eq:PotentialCuts} is not enforced since it is possible to blow up the left blob into a tree amplitude with an on-shell internal propagator.
+Cuts (b), (c), and (d) represent physical cuts where (d) is known as a maximal cut since the maximal number of propagators have been put on shell.
+
+After imposing all of the conditions above, any remaining free parameters represent ``generalized gauge freedom'' meaning that the freedom does not affect the physical integrand or its double copy.
+
 \section{Isolating the cubic sector}
@@
 
-\subsection{Notes to self}
+\subsection{Notes to self -- James}
 \begin{itemize}
@@
 However, these methods cannot be reapplied to generate 2-loop numerators, which begs the question ``is it possible to find globally color-dual numerators beyond 1-loop''.
-By ``global'' we mean that color-kinematics duality is satisfied in any kinematic configuration of the integrand.
-This is a much more stringent condition than absolutely necessary.
-There is reason to believe (cite Zvi et al) that global numerators cannot always be found.
-One resolution to the issue is to only demand color-kinematics duality on the unitarity cuts of the integrand, i.e., in specific kinematic limits.
-Enforcing Jacobi on the cuts is enough to ensure that the squared integrand will correctly cut to gravity (or whatever the squared theory might be).
-When a globally color-dual numerator cannot be found, another alternative explored in the literature is to increase the size of the numerator ansatz by enlarging the numerator from a polynomial to a rational function with spurious singularities (cite Donal et al).
-When global color-kinematics fails, the hope is that it can be restored by enlarging the size of the ansatz, either by giving the numerator of each graph its own ansatz (first option described) or by promoting the numerator to a non-local function (second option described).
-Note that a theory whose Lagrangian has color-kinematics duality would naturally produce a globally color-dual integrand so the quest for a global numerator is closely related to the existence of a Lagrangian exhibiting color-kinematics duality.
-We will begin by tackling the issue of a global 4pt 2-loop numerator for NLSM before moving on to YM.
-Two-loop color-dual integrands for pure YM have been investigated before but only for a limited ansatz that manifests locality (cite Zvi et al paper).
-
-Aside from a few special theories (cite blah), color-dual integrands are constructed from an ansatz.
-Color-kinematics duality is stated in terms of cubic graphs so the first step is to express in the integrand in terms of such graphs.
-Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and bubble on external leg (BEL) graphs.
-It is always possible to express an integrand in terms of cubic graphs, even for an even valency theory like NLSM, by multiplying and dividing the integrand by factors of inverse propagators.
-Next, the ansatz must have the correct power counting and external states.
-Since pions are scalars the numerators will not carry any spinors or polarization vectors.
+We will tackle this question for NLSM before moving on to YM
+
 Every vertex in NLSM scales as $k^2$ so, for example, the numerator of a cubic 4pt 2-loop diagram scales as $k^{12}$ so there are 8,008 independent dot products of momenta at this mass dimension.
-The numerator is assumed to be manifestly local but one approach to finding color-dual numerators is to relax manifest locality, see (...) for more details.
-After zeroth order considerations like power counting, there are three conditions that are imposed on the ansatz: (1) Jacobi relations amongst graphs must be satisfied, (2) numerators must respect graph symmetries, and (3) the integrand must have the correct unitarity cuts.
-
-\subsubsection{Jacobi relations}
-
-Jacobi relations are the heart of color-kinematics duality.
-The color factors in an integrand obey a set of Jacobi identities.
-Color-kinematics duality states that there exists a way of writing the kinematic numerators of the integrand so that they obey the same set of Jacobi identities.
-(Can trivially read off the adjoint color factors from a cubic graph.)
-So if any triplet of graphs is related by a Jacobi identity, so too must their numerators.
-Broadly speaking there are two kinds of Jacobi identities.
-The first kind relate graphs to a basis.
-For example, the double box, crossed box, and penta-triangle are related to each other as follows
-\be % [[11]]
-\label{eq:TwoLoopJacobiOne}
-\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0.
-\ee
-where the shared propagator is shown in red.
-Using this relation the crossed box can be written in terms of the other two.
-In this way, all of the 14 cubic 4pt 2-loop topologies can be written in terms of a basis of the double box and penta-triangle.
-(Any two of the double box, crossed box, and penta-triangle would have sufficed for a basis but the planar basis was chosen for simplicity.)
-Each of the two basis graphs receives its own numerator ansatz and the numerator of any other graph can be expressed in terms of these.
+
+NLSM scalar theory, no external state information stuff.
+
 As mentioned before, there are 8,008 linearly independent dot products of momenta of the required mass dimension so the total number of free parameters in the system is 16,016.
@@
 
-The second kind of Jacobi relations relate basis elements to themselves.
-For example, the crossed box numerator is related to itself via the following Jacobi relation
-\be % [[19]]
-\label{eq:TwoLoopJacobiTwo}
-\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
-\ee
-where the shared propagator is shown in red as before.
-Each of the crossed box numerators can be represented in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator ansatze.
-The first kind of Jacobi relations simplifies how many numerators require ansatze whereas the second kind of Jacobi relations place constraints on the remaining numerators.
-In principle there could be Jacobi relations involving tadpoles and BEL graphs, which would be subtle to handle.
-One option is to force the numerators of these graphs to zero.
-However, since these graphs will not contribute to physical unitarity cuts, we take a different approach.
-These graphs are allowed to have non-zero numerators but any Jacobi relations involving them are simply not imposed or solved.
-See (4 loop N=4 paper) for a discussion of BELs in the context of color-kinematics duality.
-
-In total, there are 21 Jacobi relations on the 14 cubic 4pt 2-loop graphs where, again, tadpole and BEL graphs are ignored.
-How many constraints fixed.
-
-\subsubsection{Graph symmetries}
-
-The second key constraint in an ansatz construction of color-dual numerators comes from graph symmetries.
-Every numerator is required to respect all of the symmetries (or automorphisms) of its associated graph.
-While it is very convenient to impose graph symmetries, it is not completely necessary in order to perform the double copy.
-At tree level, finding manifestly color dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
-Nonetheless, for a pure ansatz construction it is very reasonable to impose graph symmetries.
-Note that the graph symmetry constraint is imposed on \emph{every} graph, not just the basis graphs.
-For example, the crossed box, \be
-\CrossedBoxGraphSym
-\ee
-is unchanged upon reflection across the horizontal axis (shown as a blue dashed line).
-Since the crossed box can be written in terms of the double box and penta-triangle, this imposes non-trivial constraints on the ansatz.
-
-Imposing graph symmetries on the ansatz further reduces the DOF to ...
-
-\subsubsection{Unitarity}
-
-The last key constraint is that the ansatz have the correct unitarity cuts, that is, that the integrand corresponds to the correct theory.
-Generalized unitarity has been reviewed in many places (cite...) so we will not belabor the details here, in particular see (emu) for a recent treatment of unitarity methods for even multiplicity theories like NLSM.
-The essence of generalized unitarity is that when internal lines are placed on-shell, the integrand should factorize into a product of on-shell tree amplitudes.
-The cut to be performed can, itself, be encoded in a graph.
-For example, potential 4pt 2-loop cuts include
-\be
-\label{eq:PotentialCuts}
-\text{(a)} \SubtleCut ~~~~ \text{(b)} \PhysicalCutOne{}{}{}{} ~~~~ \text{(c)} \PhysicalCutTwo{}{}{}{} ~~~~ \text{(d)}  \MaxCut
-\ee
-as well as many more.
-In these graphs, all exposed propagators are understood to be cut/on-shell.
-As an equation, a unitarity cut this looks schematically like
-\be
-\label{eq:SchematicCutEquation}
-\sum \limits_\text{topologies} \frac{n \vert_\text{cut}}{\prod \limits_\text{uncut} k^2} = \sum \limits_\text{states} \prod \limits_\text{blobs} A_\text{tree} .
-\ee
-The right hand side of the equation is a product of on-shell tree amplitudes, represented graphically in \eqref{eq:PotentialCuts} by grey blobs.
-States crossing (or propagating across) the cut must be summed over.
-For scalars this sum is trivial but for spinning particles this is no longer the case and the physical state projector must be inserted (see Dimitrius paper for simplifying this operation).
-The graph topologies appearing in the left hand side of \eqref{eq:SchematicCutEquation} come from blowing up the grey blobs into cubic tree graphs in every conceivable way.
-For each of these topologies, the numerator of the associated graph is subjected to the cut constraints and is then divided by the uncut propagators.
-The right hand side is assumed to be known, which places a constraint on the numerator ansatze in the left hand side.
-
-It is possible to work with either color-dressed cuts or color-ordered cuts.
-For color-dressed cuts the grey blobs are blown up into all possible channels and all color factors $f^{abc}$ are explicitly retained (both in the integrand numerators and in the tree amplitudes).
-For color-ordered cuts the grey blobs are only blown up in color ordered channels, the color factors can be suppressed, and the product of on-shell amplitudes only extends over color-ordered trees.
-We elect to use color-ordered cuts.
-Since these cuts do not contain the full color information of the theory, it is necessary to do multiple color-ordered cuts -- over different orderings of the blob labels -- in order to fully capture all of the cut information.
-For a color dual theory such as NLSM it is enough to do $(n-2)!$ labelings of each blob due to the Kleiss-Kuijf and $U(1)$ decoupling identities (cite KK).
-In this sense color-dressed cuts contain extraneous information that is bypassed when using color-ordered cuts.
-
-In our construction, only well-defined cuts are imposed so, for example, cut (a) of \eqref{eq:PotentialCuts} is not enforced since it is possible to blow up the left blob into a tree amplitude with an on-shell internal propagator.
+How many constraints fixed by Jacobi, then graph sym, then cuts
+
 Cuts (b) and (c) are the only non-vanishing 4pt 2-loop physical cuts for an even multiplicity theory.
@@
 
-References for Jacobi, unitarity, etc.
-
 Why aren't the two physical cuts spanning?  I know from experience that they're not but I can't easily explain why.
-
-\subsubsection{Matching to ZM -- James}
 

### 2023-08-21 notes/2loopNLSM.tex
Added actual numbers into YM discussion.

--- 2023-08-21 notes/2loopNLSM.tex
@@
 \def\mystrut{\rule[-2ex]{0ex}{6ex}}
+
+\usepackage{showkeys}
 
@@
 find that the power counting bound proposed by Bern, Davies, and Nohle
-leads to an initial ansatz with XX terms in the double-box, and YY
+leads to an initial ansatz with 10,000 terms in the double-box, and 9,849
 terms for the penta-triangle.  However, recent work by Ben-Shahar,
@@
 penta-triangle ansatz have an initial ansatz with 10,010 terms each.
-Imposing diagram automorphisms on the two basis diagrams, we reduce
-the number of terms to XX.  Gauge invariance on support of the maximal
-cuts of the basis diagrams further reduces the remaining freedom to
-YY.  The power-counting restriction of BDN would reduce this count to
-ZZ.  In the original BDN work, they imposed three spanning generalized
-unitarity cuts, shown in [].  Instead of directly imposing the
-spanning cuts, we proceed with the relaxed version of the method of
-maximal cuts used above in the pion construction [\ace{is James going
-  to talk about something along this line in the pions section?}].  We
-find that even with the completely generic ansatz, the representation
-fails to satisfy the next-to-next-to-maximal cut shown in [].
-Notably, imposing the BDN power-counting constraints additionally
-causes a discrepancy with the N$^2$-max cuts show in [].
+Imposing both diagram automorphisms and maximal-cut gauge invariance
+on both of the basis diagrams reduces the ansatz to 2,235 terms in the
+double-box and 4,133 terms in the penta-triangle.  The power-counting
+restriction of BDN would reduce the counts to 2232 and 4072,
+respectively.  In the original BDN work, they imposed three spanning
+generalized unitarity cuts, shown in [].  Instead of directly imposing
+the spanning cuts, we proceed with a relaxed version of the method of
+maximal cuts [] in order to more-directly identify the location of
+tension between kinematic Jacobi relations and unitarity constraints.
+We find that even with the completely generic ansatz,
+the representation fails to satisfy the next-to-next-to-maximal cut
+shown in [].  Notably, imposing the BDN power-counting constraints
+additionally causes a discrepancy with the N$^2$-max cuts show in [].
 

### 2023-08-21 notes/2loopNLSM.tex
Reminder to myself on B^3 theory
Fixed showkeys
Switched to cref and factored out all of the tikz code to clean up preamble.

--- 2023-08-21 notes/2loopNLSM.tex
@@
 \usepackage{stackengine}
+\usepackage{cleveref}
+
 \def\RA{\rlap{\scalebox{1.6}{$\leftrightarrow$}}}
@@
 
+\usepackage[notcite]{showkeys}
 \usepackage{tikz-feynman} 
@@
 \newcommand{\nhp}[1]{\textcolor{nhpRed}{\textbf{NHP:}{#1}}}
+\newcommand{\draftnoteJM}[1]{\textbf{\textcolor{blue}{#1}}}
 
@@
 
-\tikzset{Bfield/.style={decorate, double}}
-
-\iffalse
-\tikzfeynmanset{compat=1.1.0}
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-\usetikzlibrary{external}  
-          %% Load the `external` library
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-\tikzexternalize[                     %% Activate externalization
-  prefix=images/,                    %% Avoid cluttering the directory
- system call={                       %% Use lualatex in system call
-    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
-  },
-]
-\fi
-\tikzfeynmanset{
-  fermion2/.style={
-    /tikz/postaction={
-      /tikz/decoration={
-        markings,
-        mark=at position 0.7 with {
-          \arrow{>[length=6pt, width=7pt]};
-        },
-      },
-      /tikz/decorate=true,
-    },
-  },
-}
-
-\definecolor{jaxoblue}{HTML}{0086FF}
+\input{tikz_nonsense.tex}
 
@@
 
-\newcommand{\cC}{g} % -- Crossing Count symbol.
-
 \newcommand{\nkmc}[1][k]{N$^{#1}$MC\xspace}
@@
 
-%%% Jacobi 1 %%%
-
-\newcommand{\JacobiOneDoubleBox}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){4};
-\vertex (a2) at (1.5,-1){2};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5) ;
-\vertex (mid4) at (1,-.5) ;
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5) ;
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,](mid6),
-(mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,nhp4](mid2),
-(mid5) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\JacobiOneCrossedBox}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){4};
-\vertex (a2) at (1.5,-1){2};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,nhp4](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\JacobiOnePentaTriangle}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){4};
-\vertex (a2) at (.5,-1){2};
-\vertex (a3) at (.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (-.5,-.5);
-\vertex (mid2) at (-1,0);
-\vertex (mid3) at (0,.5) ;
-\vertex (mid4) at (0,-.5) ;
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5) ;
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid2),
-(mid6) --[ultra thick,](mid2),
-(mid1) --[ultra thick,](mid6),
-(mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,](mid3),
-(mid5) --[ultra thick,nhp4](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-%%% Jacobi 1 end %%%
-
-%%% Jacobi 2 start %%%
-
-\newcommand{\JacobiTwoCrossedBoxOne}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){2};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,nhp4](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\JacobiTwoCrossedBoxTwo}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){3};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){1};
-\vertex (a4) at (-1.5,-1){2};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,nhp4](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\JacobiTwoCrossedBoxThree}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){1};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){2};
-\vertex (a4) at (-1.5,-1){3};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,nhp4](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-%%% Jacobi 2 end %%%
-
-%%% Graph sym start %%%
-
-\newcommand{\CrossedBoxGraphSym}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){};
-\vertex (a2) at (1.5,-1){};
-\vertex (a3) at (1.5,1){};
-\vertex (a4) at (-1.5,-1){};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5);
-\vertex (mid4) at (1,-.5);
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5);
-\vertex (mid7) at (-.5,0) {};
-\vertex (x1) at (-1.5,0);
-\vertex (x2) at (1.5,0);
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,](mid7),
-(mid7) --[ultra thick,](mid1),
-(mid2) --[ultra thick,](mid6),
-(mid5) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid4),
-(x1) --[ultra thick,dashed,nhp4](x2),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-%%% Graph sym end %%%
-
-%%% Unitarity cuts begin %%%
-
-\newcommand{\PhysicalCutOne}[4]{ {
-\begin{tikzpicture}[baseline=6]
-\begin{feynman}
-\vertex (a1) at (-1, 1) {#1};
-\vertex (a2) at (1, 1) {#2};
-\vertex [dot,scale=2](mid1) at (0.5,0.5){};
-\vertex [dot,scale=1.5,hgrey0](mid2) at (0.5,0.5){};
-\vertex [dot,scale=2](mid3) at (-0.5,0.5){};
-\vertex [dot,scale=1.5,hgrey0](mid4) at (-0.5,0.5){};
-\vertex [dot,scale=2](mid5) at (0,0){};
-\vertex [dot,scale=1.5,hgrey0](mid6) at (0,0){};
-\vertex (a3) at (-.5, -.5) {#3};
-\vertex (a4) at (.5, -.5) {#4};
-\diagram{
-(mid3) --[ ultra thick](a1),
-(mid1) --[ ultra thick](a2),
-(mid1) --[ ultra thick,out=120,in=60,min distance=0.1cm](mid3),
-(mid1) --[ ultra thick](mid3),
-
-(mid1) --[ ultra thick](mid5),
-(mid3) --[ ultra thick](mid5),
-
-(mid5) --[ ultra thick](a4),
-(mid5) --[ ultra thick,](a3)
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\PhysicalCutTwo}[4]{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-.6, -0.6) {#1};
-\vertex (a2) at (-.6, 0.6) {#2};
-\vertex [dot,scale=2](mid1) at (0,0){};
-\vertex [dot,scale=1.5,hgrey0](mid2) at (0,0){};
-\vertex [dot,scale=2](mid3) at (.8,0){};
-\vertex [dot,scale=1.5,hgrey0](mid4) at (.8,0){};
-\vertex [dot,scale=2](mid5) at (1.6,0){};
-\vertex [dot,scale=1.5,hgrey0](mid6) at (1.6,0){};
-\vertex (a3) at (2.2, .6) {#3};
-\vertex (a4) at (2.2, -.6) {#4};
-\diagram{
-(mid1) --[ ultra thick,](a1),
-(mid1) --[ ultra thick,](a2),
-(mid1) --[ ultra thick,out=60,in=120,min distance=0.4cm](mid3),
-(mid1) --[ ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
-(mid3) --[ ultra thick,out=60,in=120,min distance=0.4cm](mid5),
-(mid3) --[ ultra thick,out=-60,in=-120,min distance=0.4cm](mid5),
-(mid5) --[ ultra thick](a4),
-(mid5) --[ ultra thick,](a3)
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\MaxCut}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.2,0.8){};
-\vertex (a2) at (1.2,-0.8){};
-\vertex (a3) at (1.2,0.8){};
-\vertex (a4) at (-1.2,-0.8){};
-\vertex [dot,scale=2] (mid1) at (0,-.4){};
-\vertex [dot,scale=1.5,hgrey0](mid1x) at (0,-.4){};
-\vertex [dot,scale=2] (mid2) at (0,.4){};
-\vertex [dot,scale=1.5,hgrey0] (mid2x) at (0,.4){};
-\vertex [dot,scale=2] (mid3) at (0.8,.4){};
-\vertex [dot,scale=1.5,hgrey0] (mid3x) at (0.8,.4){};
-\vertex [dot,scale=2] (mid4) at (0.8,-.4){};
-\vertex [dot,scale=1.5,hgrey0] (mid4x) at (0.8,-.4){};
-\vertex [dot,scale=2] (mid5) at (-0.8,.4){};
-\vertex [dot,scale=1.5,hgrey0] (mid5x) at (-0.8,.4){};
-\vertex [dot,scale=2] (mid6) at (-0.8,-.4){};
-\vertex [dot,scale=1.5,hgrey0] (mid6x) at (-0.8,-.4){};
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,](mid2),
-(mid3) --[ultra thick,](mid2),
-(mid1) --[ultra thick,](mid6),
-(mid1) --[ultra thick,](mid4),
-(mid5) --[ultra thick,](mid2),
-(mid5) --[ultra thick,](mid6),
-(mid3) --[ultra thick,](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\SubtleCut}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-.8, -0.6) {};
-\vertex (a2) at (-.8, 0.6) {};
-\vertex (a3) at (-1, 0) {};
-\vertex [dot, scale=2](mid1) at (0,0){};
-\vertex [dot, scale=1.5,hgrey0](mid2) at (0,0){};
-\vertex [dot, scale=2](mid3) at (1,0){};
-\vertex [dot, scale=1.5,hgrey0](mid4) at (1,0){};
-\vertex (a4) at (1.8, 0) {};
-\diagram{
-(mid1) --[ultra thick,](a1),
-(mid1) --[ultra thick,](a2),
-(mid1) --[ultra thick,](a3),
-(mid1) --[ultra thick,](mid3),
-(mid1) --[ultra thick,out=60,in=120,min distance=0.4cm](mid3),
-(mid1) --[ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
-(mid3) --[ultra thick](a4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-%%% Unitarity cuts end %%%
-
-\newcommand{\simplebox}{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1,1){2};
-\vertex (a2) at (1,-1){4};
-\vertex (a3) at (1,1){3};
-\vertex (a4) at (-1,-1){1};
-\vertex (mid3) at (.35,.35);
-\vertex (mid4) at (.35,-.35);
-\vertex (mid5) at (-.35,.35);
-\vertex (mid6) at (-.35,-.35);
-\diagram{(mid4) --[ultra thick,nhpRed](mid3),
-(mid5) --[ultra thick,nhpRed](mid6),
-(mid3) --[ultra thick,nhpRed](mid5),
-(mid6) --[ultra thick,nhpRed](mid4),
-(mid6) --[ultra thick,fermion2](a4),
-(mid3) --[ultra thick,fermion2](a3),
-(mid4) --[ultra thick,fermion2](a2),
-(mid5) --[ultra thick,fermion2](a1),
-};
-\vertex [dot, scale=1.6](mid3a) at (.35,.35){};
-\vertex [dot, scale=1.1,hgrey0](mid3b) at (.35,.35){};
-\vertex [dot, scale=1.6](mid4a) at (-.35,.35){};
-\vertex [dot, scale=1.1,hgrey0](mid4b) at (-.35,.35){};
-\vertex [dot, scale=1.6](mid5a) at (.35,-.35){};
-\vertex [dot, scale=1.1,hgrey0](mid5b) at (.35,-.35){};
-\vertex [dot, scale=1.6](mid6a) at (-.35,-.35){};
-\vertex [dot, scale=1.1,hgrey0](mid6b) at (-.35,-.35){};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\cubic}[7]{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex [dot, scale=2.6](mid1) at (0,0){};
-\vertex [dot, scale=2.6](mid2) at (0,0){};
-\vertex [dot, scale=2,#1](mid3) at (0,0){};
-\vertex (a1) at (0,1){3};
-\vertex (a2) at (.85,-.55){2};
-\vertex (a3) at (-.85,-.55){1};
-\diagram{
-(mid1) --[ultra thick,#2,#3](a3),
-(mid1) --[ultra thick,#4,#5](a2),
-(a1) --[ultra thick,#6,#7](mid1),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\AcubicB}[9]{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (0,0){};
-\vertex (a2) at (-1.55,.85){2};
-\vertex (a3) at (-1.55,-.85){1};
-\vertex [dot, scale=2.6](mid1) at (-.85,0){};
-\vertex [dot, scale=2.6](mid2) at (-.85,0){};
-\vertex [dot, scale=2,#1](mid3) at (-.85,0){};
-\vertex (a4) at (1.55,.85){3};
-\vertex (a5) at (1.55,-.85){4};
-\vertex [dot, scale=2.6](mid4) at (.85,0){};
-\vertex [dot, scale=2.6](mid5) at (.85,0){};
-\vertex [dot, scale=2,#1](mid6) at (.85,0){};
-\diagram{
-(mid1) --[ultra thick,#2,#3](a3),
-(mid1) --[ultra thick,#4,#5](a2),
-(mid4) --[ultra thick,#8,#9](a4),
-(mid4) --[ultra thick,#8,#9](a5),
-(mid1) --[ultra thick,#6,#7](a1),
-(a1) --[ultra thick,#6,#7](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\Acubic}[7]{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (0,1){3};
-\vertex (a2) at (.85,-.55){2};
-\vertex (a3) at (-.85,-.55){1};
-\vertex [dot, scale=2.6](mid1) at (0,0){};
-\vertex [dot, scale=2.6](mid2) at (0,0){};
-\vertex [dot, scale=2,#1](mid3) at (0,0){};
-\diagram{
-(a3) --[ultra thick,#2,#3](mid1),
-(a2) --[ultra thick,#4,#5](mid1),
-(mid1) --[ultra thick,#6,#7](a1),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\dBox}[7]{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){2};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5) ;
-\vertex (mid4) at (1,-.5) ;
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5) ;
-\diagram{
-(a4) --[ultra thick](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,#1](mid2),
-(mid3) --[ultra thick,#2](mid2),
-(mid1) --[ultra thick,#3](mid6),
-(mid1) --[ultra thick,#4](mid4),
-(mid5) --[ultra thick,#5](mid2),
-(mid5) --[ultra thick,#6](mid6),
-(mid3) --[ultra thick,#7](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\dBoxR}[7]{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){2};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5) ;
-\vertex (mid4) at (1,-.5) ;
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5) ;
-\diagram{
-(a4) --[ultra thick,](mid6),
-(a3) --[ultra thick,hred](mid3),
-(a2) --[ultra thick,hred](mid4),
-(a1) --[ultra thick,](mid5),
-(mid1) --[ultra thick,#1](mid2),
-(mid3) --[ultra thick,#2](mid2),
-(mid1) --[ultra thick,#3](mid6),
-(mid1) --[ultra thick,#4](mid4),
-(mid5) --[ultra thick,#5](mid2),
-(mid5) --[ultra thick,#6](mid6),
-(mid3) --[ultra thick,#7](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
-\newcommand{\dBoxL}[7]{ {
-\begin{tikzpicture}[baseline=(current  bounding  box.center)]
-\begin{feynman}
-\vertex (a1) at (-1.5,1){2};
-\vertex (a2) at (1.5,-1){4};
-\vertex (a3) at (1.5,1){3};
-\vertex (a4) at (-1.5,-1){1};
-\vertex (mid1) at (0,-.5);
-\vertex (mid2) at (0,.5);
-\vertex (mid3) at (1,.5) ;
-\vertex (mid4) at (1,-.5) ;
-\vertex (mid5) at (-1,.5);
-\vertex (mid6) at (-1,-.5) ;
-\diagram{
-(a4) --[ultra thick,hred](mid6),
-(a3) --[ultra thick,](mid3),
-(a2) --[ultra thick,](mid4),
-(a1) --[ultra thick,hred](mid5),
-(mid1) --[ultra thick,#1](mid2),
-(mid3) --[ultra thick,#2](mid2),
-(mid1) --[ultra thick,#3](mid6),
-(mid1) --[ultra thick,#4](mid4),
-(mid5) --[ultra thick,#5](mid2),
-(mid5) --[ultra thick,#6](mid6),
-(mid3) --[ultra thick,#7](mid4),
-};
-\end{feynman}
-\end{tikzpicture}
-}
-}
-
 \DeclareMathOperator{\cut}{\mathcal{C}}
-
- \def\draftnote#1{{\color{red}\it #1}} 
-\iffalse \def\draftnote#1{{\color{red}\it}} \fi
-
-\def\sect#1{section~\ref{#1}}
-\def\Fig#1{fig.~{\ref{#1}}}
-\def\Fig#1{Fig.~{\ref{#1}}}
-\def\Figs#1#2{figs.~{\ref{#1}} and {\ref{#2}}}
-\def\Figs#1#2{Figs.~{\ref{#1}} and {\ref{#2}}}
-
-\def\tab#1{table~{\ref{#1}}}
-\def\Tab#1{Table~{\ref{#1}}}
-\def\tabs#1#2{tables~{\ref{#1}} and {\ref{#2}}}
-\def\Tabs#1#2{TablesnFigs.~{\ref{#1}} and {\ref{#2}}}
 
@@
 \def\nn{\nonumber}
-\def\sec#1{section~\ref{#1}}
-\def\eqn#1{(\ref{#1})}
-\def\Eqn#1{Equation~(\ref{#1})}
-\def\eqns#1#2{eqs.~(\ref{#1}) and~(\ref{#2})}
-\def\Eqns#1#2{Eqs.~(\ref{#1}) and~(\ref{#2})}
-\def\Figref#1{Fig.~\ref{#1}}
-\def\secref#1{section~\ref{#1}}
 \def\Neqfour{{{\cal N}=4}}
@@
 
+%TODO-type commands
 \newcommand\citepls{{\bf\color{red}[[Cite Needed]]}}
+\newcommand{\sect}{\textbf{\textcolor{red}{RefSec}}}
 
@@
 \definecolor{NUpurple}{RGB}{078,042,132}
-
-\newcommand{\draftnoteJM}[1]{\textbf{\color{blue}[#1]}}
 
@@
 \ee
-Solutions to \eqn{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills.
+Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills.
 In this paper, we will focus on the perturbative aspects of this constraint.
@@
 \ee
-Applying this coordinate transformation to the self-dual condition of \eqn{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
+Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
 \begin{align} \label{SDLightCone1}
@@
 \be
-A_u=0 \text{ and } \eqn{SDLightCone1} \quad\Rightarrow \quad A_w=0
-\ee
-The second equation \eqn{SDLightCone2}  then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
-\be
-A_w=0\,,\,A_u=0 \text{ and }\eqn{SDLightCone2} \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
+A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
+\ee
+The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
+\be
+A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
 \ee
@@
 \be\label{SDEOM}
-\eqn{SDLightCone1} \text{ and } \eqn{SDDef} \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
+(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
 \ee
@@
 In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
-In this form, we can see the effect \eqn{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
+In this form, we can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
 Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.
@@
 
-Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \eqn{SDEOM}.
+Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \cref{SDEOM}.
 
 \subsubsection{YZ-Theory}
-SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \sect{sec:ZMTheory}, does as well.
+SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \cref{sec:ZMTheory}, does as well.
 This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
@@
 \ee
-Plugging in the on-shell polarizatoin of the conjugate field in \eqn{eq:onShellZStates} produces precisely the desired result of \eqn{eq:NLSMYZ4point}.
+Plugging in the on-shell polarizatoin of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
 Indeed, this construction is valid to all orders at tree-level.
@@
 which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
-Taking a linear combination of \eqref{eq:FieldStrengthJ} and \eqref{eq:LorenzGaugeJ} yields
+Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
 \be
@@
 Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
-After plugging $\varphi$ into \eqref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
+After plugging $\varphi$ into \cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
 \begin{eBox}
@@
 ZM theory can also be tenuously motivated from SDYM theory.
-The power counting of the interaction term in the SDYM equation of motion \eqref{SDEOM} makes it clear that the theory is critical in 2D.
+The power counting of the interaction term in the SDYM equation of motion \cref{SDEOM} makes it clear that the theory is critical in 2D.
 This suggests that the two lightcone coordinates $u$ and $w$ should be identified as the coordinates of the 2D space.
@@
 
-The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \eqref{eq:ZMLagrangian}, giving
+The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \cref{eq:ZMLagrangian}, giving
 \be
@@
 by virtue of the 2D Levi-Civita identity $\epsilon_{\mu\nu}\epsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
-Amusingly, \eqref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.
+Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.
 
@@
 
+\subsubsection{Cubic 2-form theory -- James}
+
 Cubic 2-form theory also has trivial CK.
+If you change the propagator (this trick is a theme) then you get YM at least classically.
+This is the nonsense ``covariant'' DC.
 
@@
 
-Aside from the few special theories mentioned in \sect{sec:CKLagrangians}, color-dual integrands are constructed from an ansatz.
+Aside from the few special theories mentioned in \cref{sec:CKLagrangians}, color-dual integrands are constructed from an ansatz.
 
@@
 As an example we will focus on the 4pt 2-loop integrand of some color-dual theory like NLSM or YM.
-The 4pt 1-loop integrand is not a sufficiently illustrative example because, for instance, it lacks any self Jacobi like \eqref{eq:TwoLoopJacobiTwo} to be discussed shortly.
+The 4pt 1-loop integrand is not a sufficiently illustrative example because, for instance, it lacks any self Jacobi like \cref{eq:TwoLoopJacobiTwo} to be discussed shortly.
 Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and bubble on external leg (BEL) graphs.
@@
 \ee
-The right hand side of the equation is a product of on-shell tree amplitudes, represented graphically in \eqref{eq:PotentialCuts} by grey blobs.
+The right hand side of the equation is a product of on-shell tree amplitudes, represented graphically in \cref{eq:PotentialCuts} by grey blobs.
 States crossing (or propagating across) the cut must be summed over.
 For scalars this sum is trivial but for spinning particles this is no longer the case and the physical state projector must be inserted (see Dimitrius paper for simplifying this operation).
-The graph topologies appearing in the left hand side of \eqref{eq:SchematicCutEquation} come from blowing up the grey blobs into cubic tree graphs in every conceivable way.
+The graph topologies appearing in the left hand side of \cref{eq:SchematicCutEquation} come from blowing up the grey blobs into cubic tree graphs in every conceivable way.
 For each of these topologies, the numerator of the associated graph is subjected to the cut constraints and is then divided by the uncut propagators.
@@
 It is possible to work with either color-dressed cuts or color-ordered cuts.
-For color-dressed cuts the grey blobs are blown up into all possible channels and all color factors $f^{abc}$ are explicitly retained on both sides of the unitarity equation \eqref{eq:SchematicCutEquation}.
-For color-ordered cuts the grey blobs are only blown up in color ordered channels, all color factors in \eqref{eq:SchematicCutEquation} are suppressed, and the product of on-shell amplitudes only extends over color-ordered trees.
+For color-dressed cuts the grey blobs are blown up into all possible channels and all color factors $f^{abc}$ are explicitly retained on both sides of the unitarity equation \cref{eq:SchematicCutEquation}.
+For color-ordered cuts the grey blobs are only blown up in color ordered channels, all color factors in \cref{eq:SchematicCutEquation} are suppressed, and the product of on-shell amplitudes only extends over color-ordered trees.
 Since color-ordered cuts do not contain the full color information of the theory, it is necessary to do multiple color-ordered cuts -- over different orderings of the blob labels -- in order to fully capture all of the cut information.
@@
 
-In our construction, only well-defined cuts are imposed so, for example, cut (a) of \eqref{eq:PotentialCuts} is not enforced since it is possible to blow up the left blob into a tree amplitude with an on-shell internal propagator.
+In our construction, only well-defined cuts are imposed so, for example, cut (a) of \cref{eq:PotentialCuts} is not enforced since it is possible to blow up the left blob into a tree amplitude with an on-shell internal propagator.
 Cuts (b), (c), and (d) represent physical cuts where (d) is known as a maximal cut since the maximal number of propagators have been put on shell.
@@
 where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
-\begin{equation}\label{eqn:4DPols}
+\begin{equation}\label{eq:4DPols}
 \begin{aligned}
@@
 where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops.
-Plugging in the Feynman rule of \eqn{eq:FeynmanRuleYYZ} and \eqn{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
+Plugging in the Feynman rule of \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
 \be

### 2023-08-21 notes/2loopNLSM.tex
Added BDN assumptions to review.

@@
 
+As part of attemtping to construct a color-kinematics dual
+representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
+Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
+assumptions for integrand numerators (ordered accoring to the
+reference):
+\begin{enumerate}
+\item Locality: Diagram ``numerators'' are polynomials in momenta and
+  polarizations, \eg the diagrams only have poles given by the
+  propagators of the diagrams.
+\item Power-counting: The maximum power of the loop momenta in the
+  numerator is bounded by Feynman-gauge Feynman rules.
+\item Cubic diagrams: The only diagrams with nonzero numerators are
+  those with strictly cubic vertices.  This is generally a requirement
+  to properly define the kinematic Jacobi relations.
+\item Relabeling : The diagram numerators are only a function of the
+  diagram's topology and labeling.
+\item Symmetries: The diagram numerators are invariant under the
+  automorphisms of the diagrams \emph{including signs that compensate
+    for color-factor sign changes}.
+\item Unitarity cuts: The cuts of the ansatz must reproduce the
+  physical unitarity cuts of the theory.
+\item Color-kinematics duality: The numerators obey some form of the
+  kinematic Jacobi relations.
+\end{enumerate}
+
 References for Jacobi, unitarity, etc.
@@
 \subsubsection{Jacobi relations}
+\ace{I like (and have previously used) the terms \emph{defining} and \emph{boundary} relations for the two types of Jacobi}
 

### 2023-08-21 notes/2loopNLSM.tex
Starting to add commentary to points.

@@
 \subsection{Color-dual Bootstrap}
+\label{sec:bootstrap}
 Some background here on how we approach color-dual bootstrap (as we will utilize in our two-loop construction). Building an ansatz from irreducible lorentz products (ISPs). Comments about:
@@
 Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
-assumptions for integrand numerators (ordered accoring to the
+assumptions in searching for double-copyable integrand numerators (ordered accoring to the
 reference):
@@
 \end{enumerate}
+Point 1 is generally a matter of convenience: there are many examples
+in which ``numerators'' with controlled rational contributions have
+been found \citepls{}.  However, without a guiding principle about
+what types of rational terms to use, the size of ans\"{a}tze quickly
+get out of hand.  Point 2 was motivated at the time by the hope that
+color-dual numerators could arise naturally out of a special gauge
+choice.  However, recent work by Ben-Shahar, Garozzo, and Johansson
+\cite{Ben-Shahar:2022ixa} \ace{Are there other good examples?}
+demonstrates that constructing Feynman rules which produce manifestly
+color-dual numerators for the NMHV sector of Yang--Mills requires
+introducing additional auxiliary fields, including higher-spin modes,
+which could shift the expected power counting in non-trivial ways.
+Point 3 is a requirement of the BCJ double-copy: currently there is no
+known way of incorporating non-cubic diagrams into the kinematic
+Jacobi relations.  Points 4 and 5 will be elaborated on in
+\cref{sec:syms}, Point 6 in \cref{sec:unitarity}, and Point 7 in
+\cref{sec:jac-rels}.
 
@@
 \subsubsection{Jacobi relations}
+\label{sec:jac-rels}
 \ace{I like (and have previously used) the terms \emph{defining} and \emph{boundary} relations for the two types of Jacobi}
@@
 \subsubsection{Graph symmetries}
+\label{sec:syms}
 
@@
 \subsubsection{Unitarity}
+\label{sec:unitarity}
 

### 2023-08-24 notes/2loopNLSM.tex
Fixed broken cites, slightly improved \citepls

@@
 %TODO-type commands
-\newcommand\citepls{{\bf\color{red}[[Cite Needed]]}}
+\newcommand{\citepls}[1]{{\bf\color{red}[[Cite Needed:#1]]}}
 \newcommand{\sect}{\textbf{\textcolor{red}{RefSec}}}
@@
 Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing.
-The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \cite{}.
+The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \citepls{}.
 We will briefly review the perturbative construction of this theory below.
@@
 \draftnoteJM{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
-\subsubsection{Self-Dual Yang-Mills} The first example in the literature \cite{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
+\subsubsection{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
 \be
@@
 This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
-On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung2016prv}.
+On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung:2016prv}.
 
@@
 While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization.
-Similar to the difficulties of renormalizing chiral fermions \cite{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
+Similar to the difficulties of renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
 As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
@@
 \ee
-While introducing succesively higher spiin states to the NMHV lagrangian constructed in \cite{} could in principle work at tree level, we will see that it is not consiisntent with what we find at general loop order.
+While introducing succesively higher spiin states to the NMHV lagrangian constructed in \citepls{} could in principle work at tree level, we will see that it is not consiisntent with what we find at general loop order.
 We will comment on this in \sect{}.
 For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.
-This is easily understood in terms of a polarization decomposition introduced by one of the authors \cite{} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations.
+This is easily understood in terms of a polarization decomposition introduced by one of the authors \citepls{} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations.
 \subsection{Block Decomposition of Yang-Mills}
@@
 Start with reducible amplitude block decomp from Ref.
-\cite:
+\citepls{}:
 \begin{eBox}

### 2023-08-24 notes/2loopNLSM.tex
Rework of intro to YangMills revisited.

@@
 %Comment commands
-\newcommand{\ace}[1]{\textcolor{darkgreen}{\textbf{AE:}{#1}}}
+\newcommand{\ace}[1]{\textcolor{darkgreen}{\textbf{AE:}{ #1}}}
 \newcommand{\nhp}[1]{\textcolor{nhpRed}{\textbf{NHP:}{#1}}}
@@
 in which ``numerators'' with controlled rational contributions have
-been found \citepls{}.  However, without a guiding principle about
-what types of rational terms to use, the size of ans\"{a}tze quickly
-get out of hand.  Point 2 was motivated at the time by the hope that
-color-dual numerators could arise naturally out of a special gauge
-choice.  However, recent work by Ben-Shahar, Garozzo, and Johansson
-\cite{Ben-Shahar:2022ixa} \ace{Are there other good examples?}
-demonstrates that constructing Feynman rules which produce manifestly
-color-dual numerators for the NMHV sector of Yang--Mills requires
-introducing additional auxiliary fields, including higher-spin modes,
-which could shift the expected power counting in non-trivial ways.
-Point 3 is a requirement of the BCJ double-copy: currently there is no
-known way of incorporating non-cubic diagrams into the kinematic
-Jacobi relations.  Points 4 and 5 will be elaborated on in
-\cref{sec:syms}, Point 6 in \cref{sec:unitarity}, and Point 7 in
-\cref{sec:jac-rels}.
+been found
+\cite{Square,WeinzierlBCJLagrangian,Mogull:2015adi,FivePointN4BCJ,Johansson:2017bfl}.
+However, without a guiding principle about what types of rational
+terms to use, the size of ans\"{a}tze quickly get out of hand.  Point
+2 was motivated at the time by the hope that color-dual numerators
+could arise naturally out of a special gauge choice.  On the other hand, recent
+work by Ben-Shahar, Garozzo, and Johansson \cite{Ben-Shahar:2022ixa}
+\ace{Are there other good examples?}  demonstrates that constructing
+Feynman rules which produce manifestly color-dual numerators for the
+NMHV sector of Yang--Mills requires introducing additional auxiliary
+fields, including higher-spin modes, which could shift the expected
+power counting in non-trivial ways.  Point 3 is a requirement of the
+BCJ double-copy: currently there is no known way of incorporating
+non-cubic diagrams into the kinematic Jacobi relations.  Points 4 and
+5 will be elaborated on in \cref{sec:syms}, Point 6 in
+\cref{sec:unitarity}, and Point 7 in \cref{sec:jac-rels}.
 
@@
 
-Different kinds of CK.
-We want global.
-Global is the simplest option, it is also the option that you would automatically get if you had a color-dual Lagrangian.
-By ``global'' we mean that color-kinematics duality is satisfied in any kinematic configuration of the integrand.
-This is a much more stringent condition than absolutely necessary.
-There is reason to believe (cite Zvi et al) that global numerators cannot always be found.
-One resolution to the issue is to only demand color-kinematics duality on the unitarity cuts of the integrand, i.e., in specific kinematic limits.
-Enforcing Jacobi on the cuts is enough to ensure that the squared integrand will correctly cut to gravity (or whatever the squared theory might be).
-When a globally color-dual numerator cannot be found, another alternative explored in the literature is to increase the size of the numerator ansatz by enlarging the numerator from a polynomial to a rational function with spurious singularities (cite Donal et al).
-When global color-kinematics fails, the hope is that it can be restored by enlarging the size of the ansatz, either by giving the numerator of each graph its own ansatz (first option described) or by promoting the numerator to a non-local function (second option described).
-Note that a theory whose Lagrangian has color-kinematics duality would naturally produce a globally color-dual integrand so the quest for a global numerator is closely related to the existence of a Lagrangian exhibiting color-kinematics duality.
-Section X is devoted to color-dual representations of the 4pt 2-loop NLSM integrand and the analogous integrand for YM is treated in section Y.
-Two-loop color-dual integrands for pure YM have been investigated before but only for a limited ansatz that manifests locality (cite Zvi et al paper).
-All of the N=4 SYM constructions below 5-loop are local.
+Different kinds of CK.  We want global.  Global is the simplest
+option, it is also the option that you would automatically get if you
+had a color-dual Lagrangian.  By ``global'' we mean that
+color-kinematics duality is satisfied in any kinematic configuration
+of the integrand.  This is a much more stringent condition than
+absolutely necessary.  There is reason to believe \cite{Bern:2015ooa}
+\ace{Is this the cite you wanted?}  that global numerators cannot
+always be found.  One resolution to the issue is to only demand
+color-kinematics duality on the unitarity cuts of the integrand, i.e.,
+in specific kinematic limits.  Enforcing Jacobi on the cuts is enough
+to ensure that the squared integrand will correctly cut to gravity (or
+whatever the squared theory might be).  When a globally color-dual
+numerator cannot be found, another alternative explored in the
+literature is to increase the size of the numerator ansatz by
+enlarging the numerator from a polynomial to a rational function with
+spurious singularities (cite Donal et al).  When global
+color-kinematics fails, the hope is that it can be restored by
+enlarging the size of the ansatz, either by giving the numerator of
+each graph its own ansatz (first option described) or by promoting the
+numerator to a non-local function (second option described).  Note
+that a theory whose Lagrangian has color-kinematics duality would
+naturally produce a globally color-dual integrand so the quest for a
+global numerator is closely related to the existence of a Lagrangian
+exhibiting color-kinematics duality.  Section X is devoted to
+color-dual representations of the 4pt 2-loop NLSM integrand and the
+analogous integrand for YM is treated in section Y.  Two-loop
+color-dual integrands for pure YM have been investigated before but
+only for a limited ansatz that manifests locality (cite Zvi et al
+paper).  All of the N=4 SYM constructions below 5-loop are local.
 Mention generalized double copy.
 
-Color-kinematics duality is stated in terms of cubic graphs so the first step is to express in the integrand in terms of such graphs.
-As an example we will focus on the 4pt 2-loop integrand of some color-dual theory like NLSM or YM.
-The 4pt 1-loop integrand is not a sufficiently illustrative example because, for instance, it lacks any self Jacobi like \cref{eq:TwoLoopJacobiTwo} to be discussed shortly.
-Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and bubble on external leg (BEL) graphs.
-It is always possible to express an integrand in terms of cubic graphs, even for an even valency theory like NLSM, by multiplying and dividing the integrand by factors of inverse propagators.
-Next, the ansatz must have the correct power counting and external states, \emph{e.g.}, polarization vectors for YM.
-The numerator is assumed to be manifestly local but one approach to finding color-dual numerators is to relax manifest locality, see (...) for more details.
-After zeroth order considerations like power counting, there are three conditions that are imposed on the ansatz: (1) Jacobi relations amongst graphs must be satisfied, (2) numerators must respect graph symmetries, and (3) the integrand must have the correct unitarity cuts.
+Color-kinematics duality is stated in terms of cubic graphs so the
+first step is to express in the integrand in terms of such graphs.  As
+an example we will focus on the 4pt 2-loop integrand of some
+color-dual theory like NLSM or YM.  The 4pt 1-loop integrand is not a
+sufficiently illustrative example because, for instance, it lacks any
+self Jacobi like \cref{eq:TwoLoopJacobiTwo} to be discussed shortly.
+Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and
+bubble on external leg (BEL) graphs.  It is always possible to express
+an integrand in terms of cubic graphs, even for an even valency theory
+like NLSM, by multiplying and dividing the integrand by factors of
+inverse propagators.  Next, the ansatz must have the correct power
+counting and external states, \emph{e.g.}, polarization vectors for
+YM.  The numerator is assumed to be manifestly local but one approach
+to finding color-dual numerators is to relax manifest locality, see
+(...) for more details.  After zeroth order considerations like power
+counting, there are three conditions that are imposed on the ansatz:
+(1) Jacobi relations amongst graphs must be satisfied, (2) numerators
+must respect graph symmetries, and (3) the integrand must have the
+correct unitarity cuts.
 
@@
 
-For 4pt on-shell ZM, the LRLR configuration is zero and for every other configuration of external states the on-shell amplitude is subtle because of IR poles.
-Note that the (on-shell) kinematic numerators are always unambiguous and never suffer from any of these subtleties in any kinematic configuration.
-So when you compare against ZM, you either comparing against zero or something subtle.
-This is why you can't really take cuts of the NLSM and ZM integrands and meaningfully compare them even though you can compare their numerators.
+For 4pt on-shell ZM, the LRLR configuration is zero and for every
+other configuration of external states the on-shell amplitude is
+subtle because of IR poles.  Note that the (on-shell) kinematic
+numerators are always unambiguous and never suffer from any of these
+subtleties in any kinematic configuration.  So when you compare
+against ZM, you either comparing against zero or something subtle.
+This is why you can't really take cuts of the NLSM and ZM integrands
+and meaningfully compare them even though you can compare their
+numerators.
 
@@
 \subsection{Yang-Mills revisited -- Alex}
-Transition paragraph.....
-
-As part of attemtping to construct a color-kinematics dual
-representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
-Davies, and Nohle (BDN) lay out the following core assumptions for
-integrand numerators (in addition to obeying some form of the
-kinematic Jacobi relations) \cite{Bern:2015ooa}
-\begin{enumerate}
-\item Locality: Diagram ``numerators'' are polynomials in momenta and
-  polarizations, \eg the diagrams only have poles given by the
-  propagators of the diagrams. \emph{We explore a minor breaking of this assumption}
-\item Power-counting: The maximum power of the loop momenta in the
-  numerator is boudned by Feynman-gauge Feynman rules.  \emph{We
-    explore breaking this assumption}.
-\item Cubic diagrams: The only diagrams with nonzero numerators are
-  those with strictly cubic vertices.  This is generally a requirement
-  to properly define the kinematic Jacobi relations.
-\item Relabeling : The diagram numerators are only a function of the
-  diagram's topology and labeling
-\item Symmetries: The diagram numerators are invariant under the
-  automorphisms of the diagrams \emph{including signs that compensate
-    for color-factor sign changes}
-\item Unitarity cuts: The cuts of the ansatz must reproduce the
-  physical unitarity cuts of the theory.
-\end{enumerate}
-They demonstrated that the above assumptions are incompatible with an
-off-shell solution to the kinematic Jacobi relations.  Here, we
-explore two violations of these core assumptions.
-
-First, we analyze the power-counting assumption.  In our labeling of
-the two loop Jacobi-basis diagrams, shown in \ace{Figure out fig}, we
-find that the power counting bound proposed by Bern, Davies, and Nohle
-leads to an initial ansatz with XX terms in the double-box, and YY
-terms for the penta-triangle.  However, recent work by Ben-Shahar,
-Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
-  good examples?} demonstrates that constructing Feynman rules that
-produce manifestly color-dual numerators for the NMHV sector of
-Yang--Mills requires introducing additional auxiliary fields,
-including higher-spin modes, which could shift the expected power
-counting in non-trivial ways.  We therefore attempt to find an
-off-shell color-dual Yang--Mills representation in which all power
-counting restrictions are lifted.
+Given the close ties between pion and gluon scattering for trees and
+at one loop, the success of a globally color-dual solution for pions
+at two loops warrants a reexamination of the two-loop pure Yang--Mills
+problem.  As discussed above in \cref{sec:bootstrap}, BDN failed at
+finding an off-shell color-dual representation satisfying 7
+assumptions, and were forced to develop an on-shell notion of
+color-kinematics duality \cite{Bern:2015ooa}.  Thus we must decide
+which assumption(s) to break.  From both a motivation and
+implementation standpoint, the simplest assumption to break is the
+``power-counting'' statement, which we analyze first.
+
+In our labeling of the two loop Jacobi-basis diagrams, shown in
+\ace{Figure out fig}, we find that the power counting bound proposed
+by Bern, Davies, and Nohle leads to an initial ansatz with 10,000
+terms in the double-box, and 9849 terms for the penta-triangle.
+However, recent work by Ben-Shahar, Garozzo, and Johansson
+\cite{Ben-Shahar:2022ixa} \ace{Are there other good examples?}
+demonstrates that constructing Feynman rules that produce manifestly
+color-dual numerators for the NMHV sector of Yang--Mills requires
+introducing additional auxiliary fields, including higher-spin modes,
+which could shift the expected power counting in non-trivial ways.  We
+therefore attempt to find an off-shell color-dual Yang--Mills
+representation in which all power counting restrictions are lifted.
 

### 2023-08-24 notes/2loopNLSM.tex
Sprused up some of the tikz code, put together some diagrams for the YM section.

@@
 \usepackage{stackengine}
+\usepackage{subcaption}
 \usepackage{cleveref}
@@
 terms in the double-box, and 9849 terms for the penta-triangle.
-However, recent work by Ben-Shahar, Garozzo, and Johansson
-\cite{Ben-Shahar:2022ixa} \ace{Are there other good examples?}
-demonstrates that constructing Feynman rules that produce manifestly
-color-dual numerators for the NMHV sector of Yang--Mills requires
-introducing additional auxiliary fields, including higher-spin modes,
-which could shift the expected power counting in non-trivial ways.  We
-therefore attempt to find an off-shell color-dual Yang--Mills
-representation in which all power counting restrictions are lifted.
-
 Without power counting restrictions, both the double-box and the
-penta-triangle ansatz have an initial ansatz with 10,010 terms each.
-Imposing diagram automorphisms on the two basis diagrams, we reduce
-the number of terms to XX.  Gauge invariance on support of the maximal
-cuts of the basis diagrams further reduces the remaining freedom to
-YY.  The power-counting restriction of BDN would reduce this count to
-ZZ.  In the original BDN work, they imposed three spanning generalized
-unitarity cuts, shown in [].  Instead of directly imposing the
-spanning cuts, we proceed with the relaxed version of the method of
+penta-triangle ansatz have an ansatz with 10,010 terms each.  Imposing
+diagram automorphisms and maximal-cut gauge invariance on the two
+basis diagrams, we reduce the number of terms to XX for the
+double-box, and YY for the penta-triangle.  The power-counting
+restriction of BDN would further reduce these counts to 2232 and 4072.
+In Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
+imposed using a spanning set of minimal physical cuts, shown in
+\cref{fig:ym-spanning}.  Instead of also directly going to the
+spanning cuts, we work within the framework of the Method of Maximal
+Cuts \citepls{} in order to identify the simplest cut that is in
+tension with the kinematic Jacobi relations.
+
+\begin{figure}
+  \begin{center}
+    \begin{subfigure}{0.3\textwidth}
+      \begin{center}
+        \LMCut
+      \end{center}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+      \begin{center}
+        \PhysicalCutOne{}{}{}{}
+      \end{center}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+      \begin{center}
+        \PhysicalCutTwo{}{}{}{}
+      \end{center}
+    \end{subfigure}
+  \end{center}
+  \caption{The three spanning physical unitarity cuts of pure
+    Yang--Mills at 2 loops}
+  \label{fig:ym-spanning}
+\end{figure}
+
+we proceed with the relaxed version of the method of
 maximal cuts used above in the pion construction [\ace{is James going
@@
 causes a discrepancy with the N$^2$-max cuts show in [].
+
+\KissingTriangles
 

### 2023-08-24 notes/2loopNLSM.tex
More tikz stuff.  Progress on YM writeup.

@@
 \subsection{Pions -- James}
+\label{sec:pions}
 
@@
 
-we proceed with the relaxed version of the method of
-maximal cuts used above in the pion construction [\ace{is James going
-  to talk about something along this line in the pions section?}].  We
-find that even with the completely generic ansatz, the representation
-fails to satisfy the next-to-next-to-maximal cut shown in [].
-Notably, imposing the BDN power-counting constraints additionally
-causes a discrepancy with the N$^2$-max cuts show in [].
-
-\KissingTriangles
+Similar to the pion construction in \cref{sec:pions}, we use the
+kinematic Jacobi relations to define the numerators for all cubic
+graphs in terms of the two basis graphs, including allowing nontrivial
+numerators on BEL diagrams.  We will simply avoid imposing
+constraints that directly involve such pathological diagrams.  That
+leaves us with 14 non-pathological cubic diagrams on which to impose
+maximal cuts and symmetries. \ace{Do we want the graphs for these?
+  Doable in tikz, but would take some time, or I can dump nice-ish
+  versions from mathematica}.  Doing so, we are left with AA total
+parameters in the unrestricted ansatz and BB total in the
+BDN-restricted ansatz.
+
+Proceeding to the next-to-maximal cuts, we continue to avoid BEL
+diagrams.  Additionally, now that we have higher-point vertices, we
+avoid diagrams in which the higher-point vertex could contain an
+off-shell propagator that carries the same momenta as one of the cut
+propagators, \eg \ace{Any feedback on how this looks, especially with
+  the dashed lines?}
+\begin{equation*}
+  \begin{tikzpicture}
+    \pgfmathsetmacro{\ri}{1};
+    \pgfmathsetmacro{\re}{0.6};
+    \pgfmathsetmacro{\ang}{35};
+    \begin{feynman}
+      \blob{i1}{\ang:\ri};
+      \blob{i2}{180-\ang:\ri};
+      \blob{i3}{180+\ang:\ri};
+      \blob{i4}{-\ang:\ri};
+      \blob{i5}{ $(i1)!0.5!(i2)$ };
+      \ver{e1}{45:\ri+\re};
+      \ver{e2}{135:\ri+\re};
+      \ver{e3}{225:\ri+\re};
+      \ver{e4}{-45:\ri+\re};
+
+      \diagram{
+        {[edges={ultra thick}] (e1)--(i1),
+          (e2)--(i2),
+          (e3)--(i3),
+          (e4)--(i4),
+          (i5)--(i1)--(i4)--(i3)--(i2),
+          (i2) --[out=60,in=180-60] (i5),
+          (i2) --[out=-60,in=180+60] (i5)
+        };
+      };
+    \end{feynman}
+  \end{tikzpicture}
+  \text{ contains a contribution from }
+  \begin{tikzpicture}
+    \pgfmathsetmacro{\ri}{1};
+    \pgfmathsetmacro{\re}{0.6};
+    \pgfmathsetmacro{\ang}{35};
+    \pgfmathsetmacro{\cang}{90};
+    \pgfmathsetmacro{\cl}{1.1};
+      \ver{i1}{\ang:\ri};
+      \ver{i2}{180-\ang:\ri};
+      \ver{i3}{180+\ang:\ri};
+      \ver{i4}{-\ang:\ri};
+      \ver{i5}{ $(i1)!0.25!(i2)$ };
+      \ver{i6}{ $(i1)!0.75!(i2)$ };
+
+      \ver{e1}{45:\ri+\re};
+      \ver{e2}{135:\ri+\re};
+      \ver{e3}{225:\ri+\re};
+      \ver{e4}{-45:\ri+\re};
+
+      \ver{c1}{0:\cl};
+      \ver{c2}{\cang:\cl};
+      \ver{c3}{2*\cang:\cl};
+      \ver{c4}{3*\cang:\cl};
+      \ver{ci}{$(i5)!0.5!(i1)$};
+      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
+      \draw[ultra thick] (e1)--(i1);
+      \draw[ultra thick] (e2)--(i2);
+      \draw[ultra thick] (e3)--(i3);
+      \draw[ultra thick] (e4)--(i4);
+      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
+      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
+      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
+      \draw[dashed,ultra thick,blue] (0,0) -- (c1);
+      \draw[dashed,ultra thick,blue] (0,0) -- (c2);
+      \draw[dashed,ultra thick,blue] (0,0) -- (c3);
+      \draw[dashed,ultra thick,blue] (0,0) -- (c4);
+      \draw[dashed,ultra thick,blue] (c5) -- ++(90:0.7*\cl);
+
+  \end{tikzpicture},
+\end{equation*}
+as it is non-trivial and beyond the scope of this paper to define
+exactly what such a cut and cut contribution means.  After discarding
+these types of cuts, we are left with 8 unique cut topologies to
+check.  Seven of these next-to-maximal cuts are consistent with the
+kinematic Jacobi relations and symmetries.  Interestingly, the
+``kissing triangles'' cut,
+\begin{equation*}
+  \KissingTriangles \,,
+\end{equation*}
+cannot be satisfied by either the unrestricted or the BDN-restricted
+ansatz with Jacobi relations and symmetries applied.
 

### 2023-08-28 notes/2loopNLSM.tex
Rearranged to prepare \bar{F}F discussion

@@
 \subsection{Color-dual Lagrangians}
-\label{sec:CKLagrangians}
-In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual.
-As we will show, taking forward limits of tree-level numerators works as long as one can construct an off-shell description with a Lagrangian.
-Here we briefly review the off-shell examples of the kinematic algebra that will be relevant in this paper.
-\be
-\mathcal{L}^{\text{semi-YM}} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} - \frac{g}{2} G_{\mu\nu} [A_\mu, A_\nu]
-\ee
-\draftnoteJM{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
-\subsubsection{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
-\be
-\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
-\ee
-To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
-\be\label{SDcon}
-F_{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
-\ee
-where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength.
-Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
-\be
-D^\mu F^{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
-\ee
-Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills.
-In this paper, we will focus on the perturbative aspects of this constraint.
-Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
-\be
-u = t+x,\quad v=t-x, \quad w = y+iz
-\ee
-which gives the following expression for the invariant line element:
-\be
-ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
-\ee
-Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
-\begin{align} \label{SDLightCone1}
-F_{uw} &=0\,,
-\\
- \label{SDLightCone2}
- F_{uv} &= F_{w\bar{w}}\,,
-\\
- \label{SDLightCone3}
- F_{v\bar{w}} &= 0\,,
-\end{align}
-Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
-\be
-A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
-\ee
-The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
-\be
-A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
-\ee
-This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
-\be\label{SDDef}
-A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
-\ee
-Using this definition on the final \draftnoteJM{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
-\be\label{SDEOM}
-(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
-\ee
-Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
-\begin{eBox}
-\be
-\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
-\ee
-\end{eBox}
-The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
-\be
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
-\ee
-In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
-In this form, we can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
-Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.
-
-As we will show in \sect{}, the color-dual nature of SDYM can be understood as a direct consequence of isolating the \textit{cubic-sector} of the full Yang-Mills amplitudes by projecting along particular on-shell states.
-For this reason, the color-dual nature depends critically on the loop order of the amplitude and does not hold generically beyond one-loop.
-
-Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \cref{SDEOM}.
-
-\subsubsection{YZ-Theory}
-SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \cref{sec:ZMTheory}, does as well.
-This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
-On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung:2016prv}.
-
-One can understand YZ-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions. 
-Starting with the Yang-Mills Lagrangian, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
-\begin{align}
-X_M &= (X_\mu,0,-iX_\mu) 
-\\
-Y_M &= (0,Y,0) 
-\\
-Z_M &= (Z_\mu,0,iZ_\mu) 
-\end{align}
-where $X$ and $Z$ are $d$-vectors and $Y$ is a scalar field.
-Considering the conjugate nature of the X-Z propagator, in this work we will make the replacement $X\rightarrow \bar{Z}$.
-Plugging this redefinition of the gauge fields in, upto cubic order, we thus obtain the following Lagrangian:
-\begin{eBox}
-\be
-\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)
-\ee
-\end{eBox}
-The Feynman rules for this Lagrangian are simply:
-\be
-\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i \varepsilon_3 (p_1-p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
-\ee
-Now we review of the construction of NLSM numerators at tree-level. In this construction, we can define generators of the kinematic algebra can be expressed as follows
-\be\label{eq:FeynmanRuleYYZ}
-T^a_{ij}= i \varepsilon_a(p_i-p_j)
-\ee
-where momentum conservation requires
-\be
-p_a + p_i + p_j =0
-\ee
-The kinematic half-ladder diagrams then takes on the following concise definition:
-\be
-n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
-\ee
-Since there are on pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the chiral current algebra is manifestly cubic.
-Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom.
-They can be defined implicitly below:
-\be
-[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}
-\ee
-Given this definition, the Feynman rule associated with kinematic structure constant is simply:
-\be\label{eq:FeynmanRuleXZZ}
-i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c) 
-\ee
-where $p_{ab}=p_a+p_b$ and $\epsilon$ and $\bar{\epsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
-The on-shell state sum for the polarization vectors is simply:
-\be
-\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}
-\ee
-Notice that the vector state sum is gauge fixed since the $Y\,Z$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$.
-To recover NLSM amplitudes from this these kinematic structure constants at tree-level, we simply plug in the following on-shell polarizations for the $Z$ and $\bar{Z}$ particles:
-\be\label{eq:onShellZStates}
-\varepsilon^\mu_{(p)} = p^\mu \qquad \bar{\varepsilon}^\mu_{(p)} = \frac{q^\mu}{pq}
-\ee
-where $q^2=0$ is some null reference momentum. With this, we can define tree-level pion scattering in two equivalent ways:
-\be
-A^{\text{NLSM}} = A(...,Y,...,Y,...) = A(...,\bar{Z},...) 
-\ee
-where the ellipses denote additional on-shell $Z$-particles.
-Subject to a particular gauge choice, the kinematic numerators in latter definition for pion scattering is equivalent to those $J$-theory, first written down by Cheung and one of the authors \cite{Cheung:2021zvb}.
-In this paradigm, the on-shell $\bar{Z}$ state is equivalent to the root leg appearing in the color-dual $J$-theory numerators.
-
-It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion.
-First we'll start with two $Y$ particles on legs 1 and 4.
-Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
-\begin{align}
-n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
-\\
- n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
-\end{align}
-Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
-\be\label{eq:NLSMYZ4point}
-A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
-\ee
-Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration.
-Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free.
-This produces the following numerators:
-\begin{align}
-n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
-\\
- n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
-\end{align}
-where we have defined the short hand notation:
-\be
-{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
-\ee
-Similarly, we find the following ordered amplitude when plugging in these numerators:
-\be
-A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
-\ee
-Plugging in the on-shell polarizatoin of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
-Indeed, this construction is valid to all orders at tree-level.
-One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
-\begin{align}
-A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
-\\
-&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
-\end{align}
-Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
-As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
-Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
-This is essentially what $J$-thepory does, as we will show below.
-
-\subsubsection{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
-For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
-The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
-First order formulation of NLSM in terms of chiral current $J^\mu$.
-Two equations.
-Two constraints, the field strength should vanish
-\be
-\label{eq:FieldStrengthJ}
-F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
-\ee
-which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
-The second condition is that the chiral current should be in Lorenz gauge
-\be
-\label{eq:LorenzGaugeJ}
-\partial_\mu J^\mu=0
-\ee
-which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
-Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
-\be
-\label{eq:JTheoryEOM}
-\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
-\ee
-Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian
-\begin{eBox}
-\be
-\mathcal{L}^{\text{J}} =\bar{J}^\mu \Box J_\mu +g f^{abc} \bar{J}^\mu J^\nu \partial_\nu J^\mu .
-\ee
-\end{eBox}
-By calculating an off-shell 4pt correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
-Kinematic algebra is diff algebra (as usual).
-How to extract physical states... (longitudinal J, weird J bar, restores broken Bose).
-
-This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states. As such, the single vertex in this theory is the same as for YZ theory: 
-\be
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
-\ee
-
-\subsubsection{Zakharov-Mikhailov theory}
-\label{sec:ZMTheory}
-While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
-Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
-After plugging $\varphi$ into \cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
-\begin{eBox}
-\be
-\label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
-\ee
-\end{eBox}
-This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
-ZM theory can also be tenuously motivated from SDYM theory.
-The power counting of the interaction term in the SDYM equation of motion \cref{SDEOM} makes it clear that the theory is critical in 2D.
-This suggests that the two lightcone coordinates $u$ and $w$ should be identified as the coordinates of the 2D space.
-The 4D d'Alembertian in lightcone coordinates, $\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$, cannot be interpreted as the 2D equivalent, so the kinetic term of SDYM must be scrapped and replaced with the correct 2D version.
-This argument should be understood purely as an alternative route to ZM theory.
-While NLSM and ZM are the same theory classically when restricted to 2D, SDYM and ZM are not because, for example, the tree amplitudes of SDYM vanish but those of ZM do not (cite argumentative papers).
-
-The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \cref{eq:ZMLagrangian}, giving
-\be
-\langle ab\rangle \equiv p_a^\mu \epsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
-\ee
-The vertex is (1) functionally symmetric and (2) the kinematic portion of the vertex is completely anti-symmetric: 
-\be
-\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
-\ee
-This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
-To prove off-shell color kinematics duality for any multiplicity and loop order it is enough to observe that the sum of the off-shell $s$-, $t$-, and $u$-channel numerators sum to zero
-\be
-\label{eq:ZMJacobi}
-\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
-\ee
-by virtue of the 2D Levi-Civita identity $\epsilon_{\mu\nu}\epsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
-Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.
-
-Since ZM theory manifested color-kinematics duality without any reference to the on-shell condition, a mass term can be added to ZM theory without spoiling color-kinematics duality.
-In fact, the kinetic term could be dramatically altered.
-In general, if the on-shell conditions are not used, color-kinematics duality is unaffected by the details of the propagator structure.
-Of course, dramatically altering the pole structure could spoil locality in the double-coppied theory.
-As already mentioned, the only difference classically between ZM and SDYM is the propagator structure.
-While both theories are color dual for the same reason, altering the propagators has profound consequences since SDYM tree amplitudes vanish and manifest color-kinematics does not persist to all loop orders.
-Color dual theories with the same interactions but different kinetic terms have appeared in the literature before.
-For example, J-theory and the theory of non-Abelian fluids presented in \cite{Cheung:2020djz} differ only in their propagators.
-Specifically, taking the static limit of the fluid's $(D+1)$-dimensional kinetic term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates yields the relativistic d'Alembertian of $D$-dimensional J-theory.
-
-While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization.
-Similar to the difficulties of renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
-As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
-
-\subsubsection{Wess-Zumino-Witten theory -- James}
-I want to write this down or I'm going to completely forget it
-
-Should probably also mention that BAS has CK at Lagrangian level (duh).
-
-\subsubsection{Cubic 2-form theory -- James}
-
-Cubic 2-form theory also has trivial CK.
-If you change the propagator (this trick is a theme) then you get YM at least classically.
-This is the nonsense ``covariant'' DC.
-
-\subsubsection{Chern-Simons theory -- James}
-We won't use this but it's useful to treat all of the CK theories in one place
-Cite Henrik Maor
-Again you place some constraint on the field strength and use Lorenz gauge
-
-\subsubsection{Generalities of known color-dual theories -- James}
-Should this section maybe go first?
-
-\begin{itemize}
-\item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
-\item All of the theories described above have diff as kinematic algebra, SU(N) for BAS, or rigid/spin Lorenz for cubic 2-form theory
-\item All of the theories choose a simple gauge like Lorenz or lightcone
-\item All of the theories place some constraint on the field strength directly and get their equations of motion directly from that constraint, not the YM EOM.
-\item (Almost all of the theories (aside from NLSM) have trivial amplitudes at least at tree level)
-\item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
-\item For off-shell CK, the kinetic term is relatively unimportant so long as the poles are correctly/consistently identified (what do you mean by s,t,u channel poles).
-This might screw up locality in the squared theory.
-\end{itemize}
-
-Now we are prepared to discuss the one-loop case.
+
+BCJ loves $\mathcal{L} = \bar{F} F$.
+How this connects to SDYM, NLSM.
+You can do tree and 1-loop.
+Why the bowtie is so important.
 
@@
 of the integrand.  This is a much more stringent condition than
-absolutely necessary.  There is reason to believe \cite{Bern:2015ooa}
-\ace{Is this the cite you wanted?}  that global numerators cannot
+absolutely necessary.  There is reason to believe \cite{Bern:2015ooa} that global numerators cannot
 always be found.  One resolution to the issue is to only demand
@@
 Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
+
+\section{Review of known theories}
+\label{sec:CKLagrangians}
+In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual.
+As we will show, taking forward limits of tree-level numerators works as long as one can construct an off-shell description with a Lagrangian.
+Here we briefly review the off-shell examples of the kinematic algebra that will be relevant in this paper.
+\be
+\mathcal{L}^{\text{semi-YM}} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} - \frac{g}{2} G_{\mu\nu} [A_\mu, A_\nu]
+\ee
+\draftnoteJM{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
+\subsubsection{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
+\be
+\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
+\ee
+To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
+\be\label{SDcon}
+F_{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
+\ee
+where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength.
+Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
+\be
+D^\mu F^{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
+\ee
+Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills.
+In this paper, we will focus on the perturbative aspects of this constraint.
+Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
+\be
+u = t+x,\quad v=t-x, \quad w = y+iz
+\ee
+which gives the following expression for the invariant line element:
+\be
+ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
+\ee
+Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
+\begin{align} \label{SDLightCone1}
+F_{uw} &=0\,,
+\\
+ \label{SDLightCone2}
+ F_{uv} &= F_{w\bar{w}}\,,
+\\
+ \label{SDLightCone3}
+ F_{v\bar{w}} &= 0\,,
+\end{align}
+Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
+\be
+A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
+\ee
+The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
+\be
+A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
+\ee
+This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
+\be\label{SDDef}
+A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
+\ee
+Using this definition on the final \draftnoteJM{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
+\be\label{SDEOM}
+(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
+\ee
+Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
+\begin{eBox}
+\be
+\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
+\ee
+\end{eBox}
+The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
+\ee
+In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
+In this form, we can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
+Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.
+
+As we will show in \sect{}, the color-dual nature of SDYM can be understood as a direct consequence of isolating the \textit{cubic-sector} of the full Yang-Mills amplitudes by projecting along particular on-shell states.
+For this reason, the color-dual nature depends critically on the loop order of the amplitude and does not hold generically beyond one-loop.
+
+Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \cref{SDEOM}.
+
+\subsubsection{YZ-Theory}
+SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \cref{sec:ZMTheory}, does as well.
+This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
+On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung:2016prv}.
+
+One can understand YZ-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions. 
+Starting with the Yang-Mills Lagrangian, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
+\begin{align}
+X_M &= (X_\mu,0,-iX_\mu) 
+\\
+Y_M &= (0,Y,0) 
+\\
+Z_M &= (Z_\mu,0,iZ_\mu) 
+\end{align}
+where $X$ and $Z$ are $d$-vectors and $Y$ is a scalar field.
+Considering the conjugate nature of the X-Z propagator, in this work we will make the replacement $X\rightarrow \bar{Z}$.
+Plugging this redefinition of the gauge fields in, upto cubic order, we thus obtain the following Lagrangian:
+\begin{eBox}
+\be
+\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)
+\ee
+\end{eBox}
+The Feynman rules for this Lagrangian are simply:
+\be
+\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i \varepsilon_3 (p_1-p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
+\ee
+Now we review of the construction of NLSM numerators at tree-level. In this construction, we can define generators of the kinematic algebra can be expressed as follows
+\be\label{eq:FeynmanRuleYYZ}
+T^a_{ij}= i \varepsilon_a(p_i-p_j)
+\ee
+where momentum conservation requires
+\be
+p_a + p_i + p_j =0
+\ee
+The kinematic half-ladder diagrams then takes on the following concise definition:
+\be
+n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
+\ee
+Since there are on pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the chiral current algebra is manifestly cubic.
+Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom.
+They can be defined implicitly below:
+\be
+[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}
+\ee
+Given this definition, the Feynman rule associated with kinematic structure constant is simply:
+\be\label{eq:FeynmanRuleXZZ}
+i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c) 
+\ee
+where $p_{ab}=p_a+p_b$ and $\epsilon$ and $\bar{\epsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
+The on-shell state sum for the polarization vectors is simply:
+\be
+\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}
+\ee
+Notice that the vector state sum is gauge fixed since the $Y\,Z$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$.
+To recover NLSM amplitudes from this these kinematic structure constants at tree-level, we simply plug in the following on-shell polarizations for the $Z$ and $\bar{Z}$ particles:
+\be\label{eq:onShellZStates}
+\varepsilon^\mu_{(p)} = p^\mu \qquad \bar{\varepsilon}^\mu_{(p)} = \frac{q^\mu}{pq}
+\ee
+where $q^2=0$ is some null reference momentum. With this, we can define tree-level pion scattering in two equivalent ways:
+\be
+A^{\text{NLSM}} = A(...,Y,...,Y,...) = A(...,\bar{Z},...) 
+\ee
+where the ellipses denote additional on-shell $Z$-particles.
+Subject to a particular gauge choice, the kinematic numerators in latter definition for pion scattering is equivalent to those $J$-theory, first written down by Cheung and one of the authors \cite{Cheung:2021zvb}.
+In this paradigm, the on-shell $\bar{Z}$ state is equivalent to the root leg appearing in the color-dual $J$-theory numerators.
+
+It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion.
+First we'll start with two $Y$ particles on legs 1 and 4.
+Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
+\begin{align}
+n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
+\\
+ n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
+\end{align}
+Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
+\be\label{eq:NLSMYZ4point}
+A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
+\ee
+Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration.
+Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free.
+This produces the following numerators:
+\begin{align}
+n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
+\\
+ n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
+\end{align}
+where we have defined the short hand notation:
+\be
+{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
+\ee
+Similarly, we find the following ordered amplitude when plugging in these numerators:
+\be
+A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
+\ee
+Plugging in the on-shell polarizatoin of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
+Indeed, this construction is valid to all orders at tree-level.
+One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
+\begin{align}
+A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
+\\
+&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
+\end{align}
+Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
+As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
+Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
+This is essentially what $J$-thepory does, as we will show below.
+
+\subsubsection{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
+For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
+The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
+First order formulation of NLSM in terms of chiral current $J^\mu$.
+Two equations.
+Two constraints, the field strength should vanish
+\be
+\label{eq:FieldStrengthJ}
+F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
+\ee
+which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
+The second condition is that the chiral current should be in Lorenz gauge
+\be
+\label{eq:LorenzGaugeJ}
+\partial_\mu J^\mu=0
+\ee
+which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
+Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
+\be
+\label{eq:JTheoryEOM}
+\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
+\ee
+Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian
+\begin{eBox}
+\be
+\mathcal{L}^{\text{J}} =\bar{J}^\mu \Box J_\mu +g f^{abc} \bar{J}^\mu J^\nu \partial_\nu J^\mu .
+\ee
+\end{eBox}
+By calculating an off-shell 4pt correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
+Kinematic algebra is diff algebra (as usual).
+How to extract physical states... (longitudinal J, weird J bar, restores broken Bose).
+
+This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states. As such, the single vertex in this theory is the same as for YZ theory: 
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
+\ee
+
+\subsubsection{Zakharov-Mikhailov theory}
+\label{sec:ZMTheory}
+While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
+Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
+After plugging $\varphi$ into \cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
+\begin{eBox}
+\be
+\label{eq:ZMLagrangian}
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
+\ee
+\end{eBox}
+This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
+ZM theory can also be tenuously motivated from SDYM theory.
+The power counting of the interaction term in the SDYM equation of motion \cref{SDEOM} makes it clear that the theory is critical in 2D.
+This suggests that the two lightcone coordinates $u$ and $w$ should be identified as the coordinates of the 2D space.
+The 4D d'Alembertian in lightcone coordinates, $\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$, cannot be interpreted as the 2D equivalent, so the kinetic term of SDYM must be scrapped and replaced with the correct 2D version.
+This argument should be understood purely as an alternative route to ZM theory.
+While NLSM and ZM are the same theory classically when restricted to 2D, SDYM and ZM are not because, for example, the tree amplitudes of SDYM vanish but those of ZM do not (cite argumentative papers).
+
+The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \cref{eq:ZMLagrangian}, giving
+\be
+\langle ab\rangle \equiv p_a^\mu \epsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
+\ee
+The vertex is (1) functionally symmetric and (2) the kinematic portion of the vertex is completely anti-symmetric: 
+\be
+\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
+\ee
+This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
+To prove off-shell color kinematics duality for any multiplicity and loop order it is enough to observe that the sum of the off-shell $s$-, $t$-, and $u$-channel numerators sum to zero
+\be
+\label{eq:ZMJacobi}
+\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
+\ee
+by virtue of the 2D Levi-Civita identity $\epsilon_{\mu\nu}\epsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
+Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.
+
+Since ZM theory manifested color-kinematics duality without any reference to the on-shell condition, a mass term can be added to ZM theory without spoiling color-kinematics duality.
+In fact, the kinetic term could be dramatically altered.
+In general, if the on-shell conditions are not used, color-kinematics duality is unaffected by the details of the propagator structure.
+Of course, dramatically altering the pole structure could spoil locality in the double-coppied theory.
+As already mentioned, the only difference classically between ZM and SDYM is the propagator structure.
+While both theories are color dual for the same reason, altering the propagators has profound consequences since SDYM tree amplitudes vanish and manifest color-kinematics does not persist to all loop orders.
+Color dual theories with the same interactions but different kinetic terms have appeared in the literature before.
+For example, J-theory and the theory of non-Abelian fluids presented in \cite{Cheung:2020djz} differ only in their propagators.
+Specifically, taking the static limit of the fluid's $(D+1)$-dimensional kinetic term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates yields the relativistic d'Alembertian of $D$-dimensional J-theory.
+
+While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization.
+Similar to the difficulties of renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
+As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
+
+\subsubsection{Wess-Zumino-Witten theory -- James}
+I want to write this down or I'm going to completely forget it
+
+Should probably also mention that BAS has CK at Lagrangian level (duh).
+
+\subsubsection{Cubic 2-form theory -- James}
+
+Cubic 2-form theory also has trivial CK.
+If you change the propagator (this trick is a theme) then you get YM at least classically.
+This is the nonsense ``covariant'' DC.
+
+\subsubsection{Chern-Simons theory -- James}
+We won't use this but it's useful to treat all of the CK theories in one place
+Cite Henrik Maor
+Again you place some constraint on the field strength and use Lorenz gauge
+
+\subsubsection{Generalities of known color-dual theories -- James}
+Should this section maybe go first?
+
+\begin{itemize}
+\item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
+\item All of the theories described above have diff as kinematic algebra, SU(N) for BAS, or rigid/spin Lorenz for cubic 2-form theory
+\item All of the theories choose a simple gauge like Lorenz or lightcone
+\item All of the theories place some constraint on the field strength directly and get their equations of motion directly from that constraint, not the YM EOM.
+\item (Almost all of the theories (aside from NLSM) have trivial amplitudes at least at tree level)
+\item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
+\item For off-shell CK, the kinetic term is relatively unimportant so long as the poles are correctly/consistently identified (what do you mean by s,t,u channel poles).
+This might screw up locality in the squared theory.
+\end{itemize}
+
 \bibliographystyle{JHEP}

### 2023-08-28 notes/2loopNLSM.tex
Updates to 2-loop NLSM

@@
 However, these methods cannot be reapplied to generate 2-loop numerators, which begs the question ``is it possible to find globally color-dual numerators beyond 1-loop''.
-We will tackle this question for NLSM before moving on to YM
-
-Every vertex in NLSM scales as $k^2$ so, for example, the numerator of a cubic 4pt 2-loop diagram scales as $k^{12}$ so there are 8,008 independent dot products of momenta at this mass dimension.
-
-NLSM scalar theory, no external state information stuff.
-
-As mentioned before, there are 8,008 linearly independent dot products of momenta of the required mass dimension so the total number of free parameters in the system is 16,016.
-As this is too many parameters for \texttt{Mathematica} to reasonably handle, we employ a custom solver suitable for the moderately dense systems appearing in this context.
-(Scalars might generate denser systems since ever dot product can interfere with every other unlike gauge theories which separate based on polarization structure, can cite Nic.
-\nhp{ distinguish between NLSM and YM ansatz -- i.e.
-why is 10,010 per diagram solvable for YM, but 8,008 per diagram runs into issues for NLSM.
-As you said, emphasize the density of NLSM matrix inversion due to generalized gauge freedom vs.
-independent polarization structures for YM.})
+We will tackle this question for NLSM before moving on to YM.
+
+Every vertex in NLSM scales as $k^2$ so the numerator of a cubic 4pt 2-loop diagram scales as $k^{12}$.
+There are 8,008 independent dot products of momenta at this mass dimension.
+Since there are two basis numerators, double box and penta-triangle, the entire calculation involves 16,016 degrees of freedom.\footnote{A custom solver is needed for the pion ansatz since \texttt{Mathematica} cannot reasonably handle sixteen thousand parameters.
+One alternative might be to use a large linear system solver designed for integral reduction.
+However, these solvers assume that the matrix under consideration has a very low density.
+This is not the case for pions where the equations naturally have a density of a few percent.
+The YM equations have a lower density because the theory separates into different ``helicity'' or $e_i\cdot e_j$ sectors.
+Since pions are scalars there is no such separation into sectors, resulting in denser equations.}
 
@@
 
-Cuts (b) and (c) are the only non-vanishing 4pt 2-loop physical cuts for an even multiplicity theory.
+Move some of the cut pictures here.
+
+Cuts (b) and (c) of \cref{eq:PotentialCuts} are the only non-vanishing 4pt 2-loop physical cuts for an even multiplicity theory.
 This means that even at two loops, unitarity cuts are still only probing the on-shell 4pt NLSM amplitude.

### 2023-08-28 notes/2loopNLSM.tex
First paragraph on DC.

@@
 
+\begin{figure}
+  \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+      \begin{center}
+        \PhysicalCutOne{}{}{}{}
+      \end{center}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+      \begin{center}
+        \PhysicalCutTwo{}{}{}{}
+      \end{center}
+    \end{subfigure}
+  \end{center}
+  \caption{The two physical cut topologies shared by sGal, BI, and DBIVA}
+  \label{fig:emu}
+\end{figure}
+
+With a cubic color-dual pion representation in hand, we can perfrom
+double copies with many theories to extract ``gravitational''
+amplitudes.  Such double-copy constructions are important nontrivial
+checks on the underlying single-copy theories: the Jacobi relations in
+the single copy conspire to produce the double-copy theory's version
+of ``diff. invariance'' \citepls{}.  With pions as one of our single
+copies, we will look at producing numerators for special Gallileons,
+Born-Infeld theory, and DBIVA by double-copying against pions,
+$\mathcal{N}=0$ YM, and $\mathcal{N}=4$ sYM respectively \citepls{}.
+These output theories were recently studied extensively by one of the
+authors and Carrasco from the perspective of direct unitarity cut
+construction \cite{Carrasco:2023qgz}.  One of the shared features of
+these 3 theories is that they all have the same physical cut
+topologies in 4D: the two diagrams shown in \cref{fig:emu} which are
+only composed of even-point amplitudes.
+
 \begin{itemize}

### 2023-08-29 notes/2loopNLSM.tex
Added paragraph about hypothetical minimal failure state.  Need to check it.

@@
 
+\ace{I need to check this.  For now it is a standing hypothesis:} In
+fact, we can make the failure extremely precise.  Start with the
+diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
+the double-box, crossed-box, and penta-triangle.  For each of the
+three diagrams, write down the most generic parity-even local ansatz
+involving four polarizations and six momenta (any combination of external or loop).  Each ansatz will be
+10,010 terms initially.  Next impose the symmetry constraints on each
+of the three diagrams, leaving XX free parameters on the double-box,
+YY free parameters on the crossed-box, and ZZ free paramters on the
+penta-triangle.  Then impose the ``kissing triangle'' next-to-maximal
+cut, which in the \emph{non-planar} color channel only recieves
+contributions from the double-box
+\begin{equation}
+  \KissingTriangles
+  =
+  \frac{1}{(\textcolor{nhp4}{\ell_1})^2} \
+  n \left[
+    \DoubleBoxLabeled{1}{2}{3}{4}
+  \right]
+  +
+  \frac{1}{(\textcolor{nhp4}{\ell_2})^2} \
+  n\left[\DoubleBoxLabeled{1}{3}{2}{4}\right]
+\end{equation}
+After imposing this cut, we find that the original Jacobi relation,
+\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
+\begin{equation}
+  \KissingTriangles
+  \Rightarrow
+  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0
+\end{equation}
+
 \begin{itemize}

### 2023-08-29 notes/2loopNLSM.tex
Added some more blurbs in DC and YM.

@@
 these 3 theories is that they all have the same physical cut
-topologies in 4D: the two diagrams shown in \cref{fig:emu} which are
+topologies in 4D: the two diagrams shown in \cref{fig:emu}, which are
 only composed of even-point amplitudes.
+
+To construct the double-copy theories, we source the cubic
+$\mathcal{N}=0$ YM numerators from Ref.~\cite{Bern:2015ooa} (which
+additionally satisfies a relaxed form of color-kinematics duality),
+and the cubic $\mathcal{N}=4$ sYM representation from the well-known
+$n_{\text{DB}} = n_{\text{CB}} = s (st\, A_{\text{tree}})$ \citepls{}.
+
+Using the methods of Ref.~\cite{Carrasco:2023qgz}, we can directly
+compute the needed basis cuts in all 3 theories without relying on a
+color-dual pion representation.
 

### 2023-08-30 notes/2loopNLSM.tex
2-loop pion section

@@
 \newcommand{\nhp}[1]{\textcolor{nhpRed}{\textbf{NHP:}{#1}}}
-\newcommand{\draftnoteJM}[1]{\textbf{\textcolor{blue}{#1}}}
+\newcommand{\jm}[1]{\textcolor{blue}{\textbf{JM: }{#1}}}
 
@@
 Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
-assumptions in searching for double-copyable integrand numerators (ordered accoring to the
+assumptions in searching for double-copyable integrand numerators (ordered according to the
 reference):
@@
 However, without a guiding principle about what types of rational
-terms to use, the size of ans\"{a}tze quickly get out of hand.  Point
-2 was motivated at the time by the hope that color-dual numerators
-could arise naturally out of a special gauge choice.  On the other hand, recent
-work by Ben-Shahar, Garozzo, and Johansson \cite{Ben-Shahar:2022ixa}
+terms to use, the size of ans\"{a}tze quickly get out of hand.
+Point 2 was motivated at the time by the hope that color-dual numerators
+could arise naturally out of a special gauge choice.
+\jm{I'm not sure that we should bring up point 2.
+I don't follow it and I don't think Alex did either since this wouldn't be the most general ansatz.
+Also, why doesn't point 5 cover point 4?}
+On the other hand, recent work by Ben-Shahar, Garozzo, and Johansson \cite{Ben-Shahar:2022ixa}
 \ace{Are there other good examples?}  demonstrates that constructing
@@
 \label{sec:jac-rels}
-\ace{I like (and have previously used) the terms \emph{defining} and \emph{boundary} relations for the two types of Jacobi}
 
@@
 (Can trivially read off the adjoint color factors from a cubic graph.)
-So if any triplet of graphs is related by a Jacobi identity, so too must their numerators.
-Broadly speaking there are two kinds of Jacobi identities.
-The first kind relate graphs to a basis.
+If any triplet of graphs is related by a Jacobi identity, so too must their numerators.
+Broadly speaking there are two kinds of Jacobi identities:  \emph{defining} relations and \emph{boundary} relations.
+Defining Jacobi relations can be used to express any graph in terms of a basis.
 For example, the double box, crossed box, and penta-triangle are related to each other as follows
@@
 where the shared propagator is shown in red.
-Using this relation the crossed box can be written in terms of the other two.
+Using this relation the crossed box can be written (or \emph{defined}) in terms of the other two.
 In this way, all of the 14 cubic 4pt 2-loop topologies can be written in terms of a basis of the double box and penta-triangle.
@@
 
-The second kind of Jacobi relations relate basis elements to themselves.
+After using the defining Jacobi relations to relate any graph to the basis, we will refer to any remaining Jacobi relations as boundary relations.
+In other words, boundary relations (indirectly) relate basis elements to themselves.
 For example, the crossed box numerator is related to itself via the following Jacobi relation
@@
 Each of the crossed box numerators can be represented in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator ansatze.
-The first kind of Jacobi relations simplifies how many numerators require ansatze whereas the second kind of Jacobi relations place constraints on the remaining numerators.
+While defining Jacobi relations simplify how many numerators require ansatze, boundary relations place restrictions on those ansatze.
 In principle there could be Jacobi relations involving tadpoles and BEL graphs, which would be subtle to handle.
@@
 
-In total, there are 21 Jacobi relations on the 14 cubic 4pt 2-loop graphs where, again, tadpole and BEL graphs are ignored.
-
 \subsubsection{Graph symmetries}
@@
 While it is very convenient to impose graph symmetries, it is not completely necessary in order to perform the double copy.
-At tree level, finding manifestly color dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
+At tree level, finding manifestly color-dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
 Nonetheless, for a pure ansatz construction it is very reasonable to impose graph symmetries.
@@
 In these graphs, all exposed propagators are understood to be cut/on-shell.
-As an equation, a unitarity cut this looks schematically like
+As an equation, a unitarity cut looks schematically like
 \be
@@
 The graph topologies appearing in the left hand side of \cref{eq:SchematicCutEquation} come from blowing up the grey blobs into cubic tree graphs in every conceivable way.
+The numerator of each graph is related back to the basis numerators via Jacobi relations.
 For each of these topologies, the numerator of the associated graph is subjected to the cut constraints and is then divided by the uncut propagators.
@@
 For color-dressed cuts the grey blobs are blown up into all possible channels and all color factors $f^{abc}$ are explicitly retained on both sides of the unitarity equation \cref{eq:SchematicCutEquation}.
-For color-ordered cuts the grey blobs are only blown up in color ordered channels, all color factors in \cref{eq:SchematicCutEquation} are suppressed, and the product of on-shell amplitudes only extends over color-ordered trees.
+For color-ordered cuts the grey blobs are only blown up in color-ordered channels, all color factors in \cref{eq:SchematicCutEquation} are suppressed, and the product of on-shell amplitudes only extends over color-ordered trees.
 Since color-ordered cuts do not contain the full color information of the theory, it is necessary to do multiple color-ordered cuts -- over different orderings of the blob labels -- in order to fully capture all of the cut information.
@@
 
-\subsection{Notes to self -- James}
-\begin{itemize}
-\item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
-\item Cite papers arguing about whether NLSM in 2D is non-trivial or not.
-\item Explain why you need to take a certain portion of the YZ numerator to get the right answer.
-Basically you can't have a vector particle circle the loop -- NLSM is a scalar theory so only scalar DOF should actually live in cuts.
-If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
-\item Reiterate that the (tree) amplitudes of CS and SDYM are zero.
-\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
-This observation is due to other people but an easy way to see it.
-ZM and 2D NLSM have the same EOM after a field redefinition.
-This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
-\item Forcing pions to match ZM in 2D does funny things.
-The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
-I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
-Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
-For 4pt tree, $z=2/3$ (I matched the half ladder).
-For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
-For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
-For 6pt tree, $z$ is 12/35 (I matched the half ladder).
-So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
-Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
-\item Explain how matching to ZM is a little silly.
-Check that NLSM and ZM numerator agree on cuts.
-Can't do that or else it becomes subtle.
-Only well defined object is numerator.
-\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
-At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
-\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.
-So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\epsilon$ identities.
-Make an ansatz where you do every pairing of $\epsilon$'s.
-This doesn't work.
-\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
-The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
-I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
-\item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
-\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4pt, 6pt, and 8pt.
-\item Should probably give the 4pt pion amplitude somewhere to show my conventions.
-\end{itemize}
-
-\subsection{Pions -- James}
+\subsection{Two-loop NLSM}
 \label{sec:pions}
@@
 
-Every vertex in NLSM scales as $k^2$ so the numerator of a cubic 4pt 2-loop diagram scales as $k^{12}$.
-There are 8,008 independent dot products of momenta at this mass dimension.
-Since there are two basis numerators, double box and penta-triangle, the entire calculation involves 16,016 degrees of freedom.\footnote{A custom solver is needed for the pion ansatz since \texttt{Mathematica} cannot reasonably handle sixteen thousand parameters.
-One alternative might be to use a large linear system solver designed for integral reduction.
-However, these solvers assume that the matrix under consideration has a very low density.
-This is not the case for pions where the equations naturally have a density of a few percent.
-The YM equations have a lower density because the theory separates into different ``helicity'' or $e_i\cdot e_j$ sectors.
-Since pions are scalars there is no such separation into sectors, resulting in denser equations.}
-
-How many constraints fixed by Jacobi, then graph sym, then cuts
-
-Move some of the cut pictures here.
-
-Cuts (b) and (c) of \cref{eq:PotentialCuts} are the only non-vanishing 4pt 2-loop physical cuts for an even multiplicity theory.
+Every vertex in NLSM scales as $k^2$ so the numerator of a 4pt 2-loop diagram diagram scales as $k^{12}$.
+At this mass dimension there are 8,008 independent dot products of momenta.
+Ignoring tadpoles and BEL graphs, there are 14 cubic 4pt 2-loop graphs, but they are related to one another via 21 distinct Jacobi relations.
+As mentioned in (review section), this means that the numerator of every graph can be expressed in terms of the double box and penta-triangle.
+With two basis graphs there is a total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is not suited to equations with sixteen thousand parameters so a different method is desirable.
+One possibility is to use a solver designed for integral reduction.
+However, these solvers typically assume that the matrix has a very low density which is not the case for equations coming from NLSM which typically have a density of a few percent.
+While the equations in YM naturally separate into different ``helicity'' sectors (or $e_i \cdot e_j$ and $e_i \cdot k_j$ sectors in $D$ dimensions), there is no such separation of sectors in a scalar theory where any product of momenta can interfere with any other.
+The NLSM constraint equations were solved using a custom solver, \texttt{FiniteFieldSolve}, designed to solve large linear systems of arbitrary density.
+\texttt{FiniteFieldSolve} will be released publicly shortly.}
+Imposing all of the Jacobi relations eliminates all but 4,473 of the original free parameters.
+Further imposing graph symmetries reduces the number of free parameters to 1,243.
+
+The final essential constraint is unitarity.
+Cuts (b) and (c) of \cref{eq:PotentialCuts} are the only non-vanishing cuts that need to be enforced.  \jm{Move some of the cut pictures here?}
 This means that even at two loops, unitarity cuts are still only probing the on-shell 4pt NLSM amplitude.
@@
 The maximal cut vanishes because only 3pt amplitudes contribute and these amplitudes vanish in any scalar theory.
-It is possible to automatically enforce (or ``bake in'') the double box and penta-triangle max cuts on the ansatz by writing the ansatz in terms of inverse propagators (and remaining irreducible scalar products) and then only keeping terms that involve at least one inverse propagator since those terms will vanish on those max cuts, just as the product of 3pt scalar amplitudes will.
-However, for the sake of simplicity we do not take this route.
-
-How many DOF left after imposing cuts
-
-Why aren't the two physical cuts spanning?  I know from experience that they're not but I can't easily explain why.
-
-After imposing all of the three key constraints (Jacobi, graph symmetries, and unitarity), there still remains a plethora of generalized gauge freedom in the X unconstrained ansatz parameters.
-At this point color kinematics duality has been satisfied so the double copy will proceed without issue, but it is possible to enforce additional, more aesthetic, constraints as desired.
+%It is possible to automatically enforce (or ``bake in'') the double box and penta-triangle max cuts on the ansatz by writing the ansatz in terms of inverse propagators (and remaining irreducible scalar products) and then only keeping terms that involve at least one inverse propagator since those terms will vanish on those max cuts, just as the product of 3pt scalar amplitudes will.
+%However, for the sake of simplicity we do not take this route.
+Imposing all relevant cuts leaves 765 free parameters representing the generalized gauge freedom in the answer.
+
+\jm{Why aren't the two physical cuts spanning?  I know from experience that they're not but I can't easily explain why.}
+
+At this point color-kinematics duality has been satisfied, so the double copy will proceed without issue.
+However, the plethora of generalized gauge freedom parameters leaves the option for enforcing additional aesthetic constraints.
 $\mathcal{N}=4$ SYM provides several hints for further conditions to impose on the ansatz.
@@
 For the NLSM integrand it is desirable to make color-kinematics duality as manifest as possible.
-One hope would be to factor out some piece of the 1-loop numerator since this at least manifests antisymmetry on some of the legs.
-However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, ZM theory.
-
-ZM plagued by (suffers from) IR regulation issues.
-Only one of the two physical/meaningful cuts can be done in a non-subtle way.
-We're using ZM more as a tool to... -- We know ZM has the right kinematic structure to give CK in 2D so we're just matching onto that because we can.  ZM and NLSM can be different at quantum level.
-
-Can't match to ZM on all of the physical cuts (one of them is always subtle).  Matching to ZM should be interpreted as just a way to simplify things, not really physical.
-
-Cut (b) is always subtle
-
-Match the $\ell$ structure of ZM
-
-This is the object we include in the ancillary files, maybe with the remaining variables set to zero
-
-For 4pt on-shell ZM, the LRLR configuration is zero and for every
-other configuration of external states the on-shell amplitude is
-subtle because of IR poles.  Note that the (on-shell) kinematic
-numerators are always unambiguous and never suffer from any of these
-subtleties in any kinematic configuration.  So when you compare
-against ZM, you either comparing against zero or something subtle.
-This is why you can't really take cuts of the NLSM and ZM integrands
-and meaningfully compare them even though you can compare their
-numerators.
+One hope would be to factor out some piece of the 1-loop numerator since this at least manifests antisymmetry for the vertices involving external legs.
+However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov theory (cite ZM, James).
+
+Why don't you just set all of the generalized gauge freedom parameters to zero?
+You can learn useful things by not doing this (see N=4), this allows us to introduce more physics into the problem, and, unsurprisingly, setting them to zero produces more a more complex answer with more unwieldy rational numbers than using physics.
+
+ZM theory is governed by the Lagrangian
+\be
+\label{eq:ZMLagrangian}
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) .
+\ee
+The color-stripped Feynman rule for the vertex is simply $V(k_1, k_2, k_3) \propto \epsilon_{\mu\nu}k_1^\mu k_2^\nu$ where off-shell color-kinematics duality to all orders in perturbation theory simply follows from the Schouten identity.
+Since the theory only has a cubic vertex and the theory has manifest off-shell color-kinematics duality, it is trivial to read off the color-dual numerator for any graph.
+From the presence of the Levi-Civita tensor $\epsilon^{\mu\nu}$, the theory clearly resides in two spacetime dimensions where scattering is notoriously plagued by infrared regulation issues.
+Every on-shell particle is either a right mover, with momentum proportional to $k_R^\mu \equiv (1,1)$, or a left mover, with momentum proportional to $k_L^\mu \equiv (1,-1)$.
+On-shell ZM amplitudes naturally divide into sectors corresponding to the configuration of left and right movers, where the scattering in many sectors is rather subtle.
+Only \emph{ordered} amplitudes can be defined unambiguously from the Feynman rules.
+At 4pt, only the alternating sector is free of subtleties and the amplitude for this process vanishes.
+In equations, $A[LRLR]=0$ where $R$ corresponds to a right mover and $L$ corresponds to a left mover.
+In every other configuration of right and left movers, such as $A[RRRR]$, one of the internal propagators is incidentally on-shell since $k_R^2=k_L^2=0$.
+
+It is tempting to try to match the pion 4pt 2-loop integrand to ZM on the cuts, but given that the cuts only probe the on-shell 4pt amplitude, which is either subtle or vanishes for ZM, it is better to compare the off-shell numerators directly.
+As local functions, the numerators never suffer from any of the subtleties of on-shell 2D kinematics.
+Since the physical cuts are difficult to compare, ZM theory is being used here simply as a tool to eliminate generalized gauge freedom; ZM theory has the right power counting and kinematic structure in 2D to compare against.
+Since ZM theory is only being used for the kinematical structure of its numerators, it is natural to introduce a proportionality constant $z$ between the NLSM and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.
+The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically \citepls{Nappi}.}
+This introduces an extra degree of freedom into the problem.
+Mechanically, the pion numerator is matched to ZM by first taking every possible assignment of right and left movers for the external particles and then restricting the pion numerator to 2D.
+The loop momenta are restricted to 2D but left off-shell.
+After performing the 2D matching, there are only 365 parameters of generalized gauge freedom.
+
+The loop momentum structure of ZM theory provides one final hint for simplifying the pion numerators.
+Both loop momenta $\ell_1$ and $\ell_2$ appear in the ZM numerators but only 5 to 8 powers appear in any term, that is, each term in the ZM numerator scales as either $\ell^5$, $\ell^6$, $\ell^7$, or $\ell^8$ where $\ell$ here refers to any combination of $\ell_1$ or $\ell_2$.
+When the pion numerator is also forced to have this loop power counting, the number of generalized gauge freedom parameters reduces to 58.
+The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4pt pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \epsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}
 
@@
 propagators, \eg \ace{Any feedback on how this looks, especially with
-  the dashed lines?}
+  the dashed lines?} \jm{It looks good!  Can you omit the part where the blue lines actually cross?}
 \begin{equation*}
@@
 \ee
-\draftnoteJM{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
+\jm{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
 \subsubsection{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
@@
 \ee
-Using this definition on the final \draftnoteJM{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
+Using this definition on the final \jm{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
 \be\label{SDEOM}
@@
 
+\section{Notes to self -- James}
+\begin{itemize}
+\item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
+\item Cite papers arguing about whether NLSM in 2D is non-trivial or not.
+\item Explain why you need to take a certain portion of the YZ numerator to get the right answer.
+Basically you can't have a vector particle circle the loop -- NLSM is a scalar theory so only scalar DOF should actually live in cuts.
+If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
+\item Reiterate that the (tree) amplitudes of CS and SDYM are zero.
+\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
+This observation is due to other people but an easy way to see it.
+ZM and 2D NLSM have the same EOM after a field redefinition.
+This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
+\item Forcing pions to match ZM in 2D does funny things.
+The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
+I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
+Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
+For 4pt tree, $z=2/3$ (I matched the half ladder).
+For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
+For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
+For 6pt tree, $z$ is 12/35 (I matched the half ladder).
+So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
+Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
+\item Explain how matching to ZM is a little silly.
+Check that NLSM and ZM numerator agree on cuts.
+Can't do that or else it becomes subtle.
+Only well defined object is numerator.
+\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
+At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
+\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.
+So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\epsilon$ identities.
+Make an ansatz where you do every pairing of $\epsilon$'s.
+This doesn't work.
+\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
+The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
+I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
+\item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
+\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4pt, 6pt, and 8pt.
+\item Should probably give the 4pt pion amplitude somewhere to show my conventions.
+\end{itemize}
+
 \bibliographystyle{JHEP}

### 2023-08-30 mma/yang-mills/ym-fail-hypoth.m
Added YM failure hypothesis test.

@@ -1,0 +1,316 @@
+(* ::Package:: *)
+
+<<AmpToolsM`RecycleCuts`
+<<AmpToolsM`Integrands`
+<<AmpToolsM`MaschkeAll`
+<<AmpToolsM`SingularInterface`
+<<AmpToolsM`IsecIdeals`
+
+
+<<AmpToolsM`BasisConstruction`
+<<AmpToolsM`CKDual`
+
+
+<<AmpToolsM`Grassmania`
+
+
+<<AmpToolsM`FourDNumerics`
+
+
+<<TetanusLink`
+(*Define some convenient defaults*)
+WorkingGF = 2^MersennePrimeExponent[7] - 1;
+(*WorkingGF = 107;*)
+tetanusSolve[system_]:=tetanusSolveFull[system,a,a[1000,0],{-#[[1]]&,-#[[2]]&},GroundField->WorkingGF]
+tetanusSolveNP[system_]:=tetanusSolveFull[system,a,a[1000,0],{-#[[1]]&,-#[[2]]&},PrintStatusQ->False,GroundField->WorkingGF]
+
+
+ffSolver = tetanusSolveNP;
+(*ffSolver = spasmSolveNP;*)
+
+
+loadNPointAnalytics[4];
+
+
+(* ::Section:: *)
+(*Build the two-loop rep*)
+
+
+(* ::Subsection::Closed:: *)
+(*New Construction/Constraint functions*)
+
+
+makeAnsatzViaDioph[diag_List,totalDeg_Integer,pcData_List,maxTotalPC_Integer,desiredPols_List]:=Block[
+	{polQ = desiredPols!={},loopMom = pcData[[All,2]],polWeights,v},
+	theCutBasis = makeZBasis[diag,0,ColorSignsQ->True,Polarizations->polQ]["ZtoD"];
+	baseVars = theCutBasis[[All,1]];
+	loopMom = pcData[[All,2]];
+	If[polQ,polWeights = Exponent[#,e/@Range[4]]&/@
+	(baseVars/.{EP[i_,j_]:>e[i]EP[i,j],EE[i_,j_]:>EE[i,j]e[i]e[j]})];
+	
+	loopWeights = Boole[#>0]&/@Exponent[#,\[Alpha]@@@loopMom]&/@(theCutBasis[[All,2]]/.l[i_]:>\[Alpha][i]l[i]);
+	
+	conditions = Join[Thread[#>=0],{Total[#]==totalDeg},
[…]

### 2023-08-30 notes/2loopNLSM.tex
Cleaned up diagrams for YM failure.

@@
 \usepackage{cleveref}
+\usepackage[normalem]{ulem}
 
@@
 \definecolor{darkgreen}{RGB}{59,126,108}
+\definecolor{nu-80}{RGB}{104, 076, 150}
+\definecolor{nu-40}{RGB}{164, 149, 195}
+\colorlet{ucp-color}{nu-40}
 
@@
 However, without a guiding principle about what types of rational
-terms to use, the size of ans\"{a}tze quickly get out of hand.
-Point 2 was motivated at the time by the hope that color-dual numerators
-could arise naturally out of a special gauge choice.
-\jm{I'm not sure that we should bring up point 2.
-I don't follow it and I don't think Alex did either since this wouldn't be the most general ansatz.
-Also, why doesn't point 5 cover point 4?}
-On the other hand, recent work by Ben-Shahar, Garozzo, and Johansson \cite{Ben-Shahar:2022ixa}
-\ace{Are there other good examples?}  demonstrates that constructing
-Feynman rules which produce manifestly color-dual numerators for the
-NMHV sector of Yang--Mills requires introducing additional auxiliary
-fields, including higher-spin modes, which could shift the expected
-power counting in non-trivial ways.  Point 3 is a requirement of the
-BCJ double-copy: currently there is no known way of incorporating
+terms to use, the size of ans\"{a}tze quickly get out of hand.  Point
+2 was motivated at the time by the hope that color-dual numerators
+could arise naturally out of a special gauge choice. \jm{I'm not sure
+  that we should bring up point 2.  I don't follow it and I don't
+  think Alex did either since this wouldn't be the most general
+  ansatz.  Also, why doesn't point 5 cover point 4?}\ace{I paraphrased
+  these out of \cite{Bern:2015ooa}, thus the inclusion of Point 2.
+  For Points 4 and 5, definitely 4 $\not \Rightarrow$ 5.  In the other
+  direction, I could imagine a situation in which we violate 4 (eg we
+  need to specify a reference ordering) but that symmetries are still
+  respected as long as you also perform the correct actions on the
+  auxiliary data.} On the other hand, recent work by Ben-Shahar,
+Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
+  good examples?}  demonstrates that constructing Feynman rules which
+produce manifestly color-dual numerators for the NMHV sector of
+Yang--Mills requires introducing additional auxiliary fields,
+including higher-spin modes, which could shift the expected power
+counting in non-trivial ways.  Point 3 is a requirement of the BCJ
+double-copy: currently there is no known way of incorporating
 non-cubic diagrams into the kinematic Jacobi relations.  Points 4 and
@@
 \subsection{Double-copy -- Alex }
+\ace{I'm punting a lot of discussion to Ref \cite{Carrasco:2023qgz}.
+  Do we think that is a problem?}
 
@@
 $n_{\text{DB}} = n_{\text{CB}} = s (st\, A_{\text{tree}})$ \citepls{}.
-
-Using the methods of Ref.~\cite{Carrasco:2023qgz}, we can directly
-compute the needed basis cuts in all 3 theories without relying on a
-color-dual pion representation.
-
-\begin{itemize}
-\item  ``Most important'' check of Jacobi -- imposes ``diff'' invariance in the DC numerators
-\item Match against cuts from \cite{Carrasco:2023qgz}: double copy
-  with N=0 \cite{Bern:2015ooa}, N=4, itself
-  \item Whip up a non-jacobi N=0 or $\pi$ to highlight double copy success?
-\end{itemize}
+On the other hand, we use the methods of Ref.~\cite{Carrasco:2023qgz}
+to directly compute the needed basis cuts in all 3 theories without
+relying on a color-dual pion representation.  We find exact agreement
+in each of the three theories for both physical cuts.  Since
+Ref.~\cite{Carrasco:2023qgz} has already exhaustively explored the
+properties of four-point loop amplitudes in these theories, we direct
+interested readers there for more information.
 
@@
 propagators, \eg \ace{Any feedback on how this looks, especially with
-  the dashed lines?} \jm{It looks good!  Can you omit the part where the blue lines actually cross?}
+  the dashed lines?} \jm{It looks good!  Can you omit the part where the blue lines actually cross?}\ace{Like so?}
 \begin{equation*}
@@
       \draw[dashed,ultra thick,blue] (c5) -- ++(90:0.7*\cl);
+      \node[fill=white,circle] (c) at (0,0) {};
 
@@
 
-\ace{I need to check this.  For now it is a standing hypothesis:} In
-fact, we can make the failure extremely precise.  Start with the
-diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
-the double-box, crossed-box, and penta-triangle.  For each of the
-three diagrams, write down the most generic parity-even local ansatz
-involving four polarizations and six momenta (any combination of external or loop).  Each ansatz will be
-10,010 terms initially.  Next impose the symmetry constraints on each
-of the three diagrams, leaving XX free parameters on the double-box,
-YY free parameters on the crossed-box, and ZZ free paramters on the
-penta-triangle.  Then impose the ``kissing triangle'' next-to-maximal
-cut, which in the \emph{non-planar} color channel only recieves
-contributions from the double-box
+\ace{\sout{I need to check this.  For now it is a standing
+    hypothesis:} Checked.  The failure works as stated.} In fact, we can make the
+failure extremely precise.  Start with the diagrams shown in the
+Jacobi relation from \cref{eq:TwoLoopJacobiOne}: the double-box,
+crossed-box, and penta-triangle.  For each of the three diagrams,
+write down the most generic parity-even local ansatz involving four
+polarizations and six momenta (any combination of external or loop).
+Each ansatz will be 10,010 terms initially.  Next impose the symmetry
+constraints on each of the three diagrams, leaving 2761 free
+parameters on the double-box, 2576 free parameters on the crossed-box,
+and 5040 free paramters on the penta-triangle.  Then impose the
+``kissing triangle'' next-to-maximal cut, which in the
+\emph{non-planar} $t$-$u$ color channel only recieves contributions from the
+double-box
 \begin{equation}
@@
   =
-  \frac{1}{(\textcolor{nhp4}{\ell_1})^2} \
+  \frac{1}{(\textcolor{ucp-color}{\ell_1})^2} \
   n \left[
-    \DoubleBoxLabeled{1}{2}{3}{4}
+    \KTDBContrib{1}{2}{3}{4}
   \right]
   +
-  \frac{1}{(\textcolor{nhp4}{\ell_2})^2} \
-  n\left[\DoubleBoxLabeled{1}{3}{2}{4}\right]
+  \frac{1}{(\textcolor{ucp-color}{\ell_2})^2} \
+  n\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
 \end{equation}
@@
   \Rightarrow
-  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0
+  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
 \end{equation}
+Thus we have identified the minimal failure state for a
+globally-color-dual two-loop Yang--Mills representation: locality,
+symmetry, and the ``kissing triangle'' cut are incompatible with the
+kinematic Jacobi relations.
 

### 2023-08-30 mma/yang-mills/ym-fail-hypoth.m

@@ -19,7 +19,9 @@
 
 <<TetanusLink`
 (*Define some convenient defaults*)
+WorkingGF = 2^MersennePrimeExponent[6] - 1;
 WorkingGF = 2^MersennePrimeExponent[7] - 1;
+WorkingGF = 2^MersennePrimeExponent[8] - 1;
 (*WorkingGF = 107;*)
 tetanusSolve[system_]:=tetanusSolveFull[system,a,a[1000,0],{-#[[1]]&,-#[[2]]&},GroundField->WorkingGF]
 tetanusSolveNP[system_]:=tetanusSolveFull[system,a,a[1000,0],{-#[[1]]&,-#[[2]]&},PrintStatusQ->False,GroundField->WorkingGF]

### 2023-08-30 notes/2loopNLSM.tex
Starting blurb about nonlocal.

@@
 
+We now turn to exploring the use of non-local numerators to skirt the
+incompatibility.  We expect that promoting the numerators to
+sufficiently complicated rational functions of the momenta will
+eventually produce a color-dual representation.  At worst one could
+imagine diagram ``numerator'' functions where all possible propagators
+of all diagrams appear in each diagram ``numerator's'' denominator, at
+which point required contributions could be arbitrarily rearranged
+between diagrams.  However, given the success of non-local loop
+numerators in other contexts \cite{Square, WeinzierlBCJLagrangian,
+  Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl}, we hope that
+only relatively tame additional denominators are required.
+
+As a first attempt at such a tame non-local representation,
+
 \begin{itemize}

### 2023-08-30 notes/2loopNLSM.tex
small edits

@@
 
-\subsubsection{Jacobi relations}
+\paragraph{Jacobi relations}
 \label{sec:jac-rels}
@@
 
-\subsubsection{Graph symmetries}
+\paragraph{Graph symmetries}
 \label{sec:syms}
@@
 
-\subsubsection{Unitarity}
+\paragraph{Unitarity}
 \label{sec:unitarity}
@@
 
-\section{Isolating the cubic sector}
+\section{One-loop cubic construction}
 Here we'll describe the why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
@@
 We will construct these one-loop integrands below in the next section.
-\subsection{One-loop SDYM Integrands}
+\subsection{Semi-abelian Yang-Mills theory}
+\subsection{One-loop SDYM integrands}
 \be
@@
 Where we have define the antisymmetric kinematic variable, $[LR] = l_i^L - l_R^2$
-\subsection{Two-loop Obstruction}
-
-\section{Bootstrapping two-loop...}
+\subsection{Two-loop obstruction}
+
+\section{Two-loop bootstrap}
 
@@
 
-\subsection{Double-copy -- Alex }
+\subsection{Double-copy verification}
 \ace{I'm punting a lot of discussion to Ref \cite{Carrasco:2023qgz}.
@@
   \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-      \begin{center}
-        \PhysicalCutOne{}{}{}{}
-      \end{center}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-      \begin{center}
-        \PhysicalCutTwo{}{}{}{}
-      \end{center}
-    \end{subfigure}
+	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
   \end{center}
@@
 
-\subsection{Yang-Mills revisited -- Alex}
+\subsection{Two-loop Yang-Mills revisited}
 Given the close ties between pion and gluon scattering for trees and
@@
       \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
-      \draw[dashed,ultra thick,blue] (0,0) -- (c1);
-      \draw[dashed,ultra thick,blue] (0,0) -- (c2);
-      \draw[dashed,ultra thick,blue] (0,0) -- (c3);
-      \draw[dashed,ultra thick,blue] (0,0) -- (c4);
-      \draw[dashed,ultra thick,blue] (c5) -- ++(90:0.7*\cl);
+      \draw[dashed,ultra thick,nhp4] (0,0) -- (c1);
+      \draw[dashed,ultra thick,nhp4] (0,0) -- (c2);
+      \draw[dashed,ultra thick,nhp4] (0,0) -- (c3);
+      \draw[dashed,ultra thick,nhp4] (0,0) -- (c4);
+      \draw[dashed,ultra thick,nhp4] (c5) -- ++(90:0.7*\cl);
       \node[fill=white,circle] (c) at (0,0) {};
@@
   =
-  \frac{1}{(\textcolor{ucp-color}{\ell_1})^2} \
+  \frac{1}{(\textcolor{nhpBlue}{\ell_1})^2} \
   n \left[
@@
   +
-  \frac{1}{(\textcolor{ucp-color}{\ell_2})^2} \
+  \frac{1}{(\textcolor{nhpBlue}{\ell_2})^2} \
   n\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
@@
 
-\section{... and Beyond}
-This could be a section about our expectations for all-loop construction requiring non-local color-dual integrands. Lay out contrafactual proof, i,e. define the following statement:
+\section{All-loop no-go theorem}
+This could be a section about our expectations for all-loop construction requiring non-local color-dual integrands. Lay out counterfactual proof, i,e. define the following statement:
 \be
@@
 \appendix
-\section{Spinor-Helicity and Conventions}
+\section{Catalog of color-dual theories}
+\label{sec:CKLagrangians}
+In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual.
+As we will show, taking forward limits of tree-level numerators works as long as one can construct an off-shell description with a Lagrangian.
+Here we briefly review the off-shell examples of the kinematic algebra that will be relevant in this paper.
+\be
+\mathcal{L}^{\text{semi-YM}} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} - \frac{g}{2} G_{\mu\nu} [A_\mu, A_\nu]
+\ee
+\jm{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
+\paragraph{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
+\be
+\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
+\ee
+To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
+\be\label{SDcon}
+F_{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
+\ee
+where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength.
+Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
+\be
+D^\mu F^{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
+\ee
+Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills.
+In this paper, we will focus on the perturbative aspects of this constraint.
+Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
+\be
+u = t+x,\quad v=t-x, \quad w = y+iz
+\ee
+which gives the following expression for the invariant line element:
+\be
+ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
+\ee
+Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
+\begin{align} \label{SDLightCone1}
+F_{uw} &=0\,,
+\\
+ \label{SDLightCone2}
+ F_{uv} &= F_{w\bar{w}}\,,
+\\
+ \label{SDLightCone3}
+ F_{v\bar{w}} &= 0\,,
+\end{align}
+Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
+\be
+A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
+\ee
+The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
+\be
+A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
+\ee
+This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
+\be\label{SDDef}
+A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
+\ee
+Using this definition on the final \jm{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
+\be\label{SDEOM}
+(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
+\ee
+Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
+\begin{eBox}
+\be
+\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
+\ee
+\end{eBox}
+The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
+\ee
+In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
+In this form, we can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
+Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.
+
+As we will show in \sect{}, the color-dual nature of SDYM can be understood as a direct consequence of isolating the \textit{cubic-sector} of the full Yang-Mills amplitudes by projecting along particular on-shell states.
+For this reason, the color-dual nature depends critically on the loop order of the amplitude and does not hold generically beyond one-loop.
+
+Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \cref{SDEOM}.
+
+\paragraph{YZ-Theory}
+SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \cref{sec:ZMTheory}, does as well.
+This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
+On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung:2016prv}.
+
+One can understand YZ-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions. 
+Starting with the Yang-Mills Lagrangian, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
+\begin{align}
+X_M &= (X_\mu,0,-iX_\mu) 
+\\
+Y_M &= (0,Y,0) 
+\\
+Z_M &= (Z_\mu,0,iZ_\mu) 
+\end{align}
+where $X$ and $Z$ are $d$-vectors and $Y$ is a scalar field.
+Considering the conjugate nature of the X-Z propagator, in this work we will make the replacement $X\rightarrow \bar{Z}$.
+Plugging this redefinition of the gauge fields in, upto cubic order, we thus obtain the following Lagrangian:
+\begin{eBox}
+\be
+\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)
+\ee
+\end{eBox}
+The Feynman rules for this Lagrangian are simply:
+\be
+\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i \varepsilon_3 (p_1-p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
+\ee
+Now we review of the construction of NLSM numerators at tree-level. In this construction, we can define generators of the kinematic algebra can be expressed as follows
+\be\label{eq:FeynmanRuleYYZ}
+T^a_{ij}= i \varepsilon_a(p_i-p_j)
+\ee
+where momentum conservation requires
+\be
+p_a + p_i + p_j =0
+\ee
+The kinematic half-ladder diagrams then takes on the following concise definition:
+\be
+n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
+\ee
+Since there are on pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the chiral current algebra is manifestly cubic.
+Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom.
+They can be defined implicitly below:
+\be
+[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}
+\ee
+Given this definition, the Feynman rule associated with kinematic structure constant is simply:
+\be\label{eq:FeynmanRuleXZZ}
+i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c) 
+\ee
+where $p_{ab}=p_a+p_b$ and $\epsilon$ and $\bar{\epsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
+The on-shell state sum for the polarization vectors is simply:
+\be
+\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}
+\ee
+Notice that the vector state sum is gauge fixed since the $Y\,Z$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$.
+To recover NLSM amplitudes from this these kinematic structure constants at tree-level, we simply plug in the following on-shell polarizations for the $Z$ and $\bar{Z}$ particles:
+\be\label{eq:onShellZStates}
+\varepsilon^\mu_{(p)} = p^\mu \qquad \bar{\varepsilon}^\mu_{(p)} = \frac{q^\mu}{pq}
+\ee
+where $q^2=0$ is some null reference momentum. With this, we can define tree-level pion scattering in two equivalent ways:
+\be
+A^{\text{NLSM}} = A(...,Y,...,Y,...) = A(...,\bar{Z},...) 
+\ee
+where the ellipses denote additional on-shell $Z$-particles.
+Subject to a particular gauge choice, the kinematic numerators in latter definition for pion scattering is equivalent to those $J$-theory, first written down by Cheung and one of the authors \cite{Cheung:2021zvb}.
+In this paradigm, the on-shell $\bar{Z}$ state is equivalent to the root leg appearing in the color-dual $J$-theory numerators.
+
+It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion.
+First we'll start with two $Y$ particles on legs 1 and 4.
+Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
+\begin{align}
+n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
+\\
+ n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
+\end{align}
+Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
+\be\label{eq:NLSMYZ4point}
+A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
+\ee
+Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration.
+Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free.
+This produces the following numerators:
+\begin{align}
+n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
+\\
+ n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
+\end{align}
+where we have defined the short hand notation:
+\be
+{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
+\ee
+Similarly, we find the following ordered amplitude when plugging in these numerators:
+\be
+A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
+\ee
+Plugging in the on-shell polarizatoin of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
+Indeed, this construction is valid to all orders at tree-level.
+One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
+\begin{align}
+A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
+\\
+&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
+\end{align}
+Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
+As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
+Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
+This is essentially what $J$-thepory does, as we will show below.
+
+\paragraph{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
+For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
+The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
+First order formulation of NLSM in terms of chiral current $J^\mu$.
+Two equations.
+Two constraints, the field strength should vanish
+\be
+\label{eq:FieldStrengthJ}
+F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
+\ee
+which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
+The second condition is that the chiral current should be in Lorenz gauge
+\be
+\label{eq:LorenzGaugeJ}
+\partial_\mu J^\mu=0
+\ee
+which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
+Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
+\be
+\label{eq:JTheoryEOM}
+\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
+\ee
+Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian
+\begin{eBox}
+\be
+\mathcal{L}^{\text{J}} =\bar{J}^\mu \Box J_\mu +g f^{abc} \bar{J}^\mu J^\nu \partial_\nu J^\mu .
+\ee
+\end{eBox}
+By calculating an off-shell 4pt correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
+Kinematic algebra is diff algebra (as usual).
+How to extract physical states... (longitudinal J, weird J bar, restores broken Bose).
+
+This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states. As such, the single vertex in this theory is the same as for YZ theory: 
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
+\ee
+
+\paragraph{Zakharov-Mikhailov theory}
+\label{sec:ZMTheory}
+While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
+Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
+After plugging $\varphi$ into \cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
+\begin{eBox}
+\be
+\label{eq:ZMLagrangian}
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
+\ee
+\end{eBox}
+This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
+ZM theory can also be tenuously motivated from SDYM theory.
+The power counting of the interaction term in the SDYM equation of motion \cref{SDEOM} makes it clear that the theory is critical in 2D.
+This suggests that the two lightcone coordinates $u$ and $w$ should be identified as the coordinates of the 2D space.
+The 4D d'Alembertian in lightcone coordinates, $\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$, cannot be interpreted as the 2D equivalent, so the kinetic term of SDYM must be scrapped and replaced with the correct 2D version.
+This argument should be understood purely as an alternative route to ZM theory.
+While NLSM and ZM are the same theory classically when restricted to 2D, SDYM and ZM are not because, for example, the tree amplitudes of SDYM vanish but those of ZM do not (cite argumentative papers).
+
+The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \cref{eq:ZMLagrangian}, giving
+\be
+\langle ab\rangle \equiv p_a^\mu \epsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
+\ee
+The vertex is (1) functionally symmetric and (2) the kinematic portion of the vertex is completely anti-symmetric: 
+\be
+\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
+\ee
+This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
+To prove off-shell color kinematics duality for any multiplicity and loop order it is enough to observe that the sum of the off-shell $s$-, $t$-, and $u$-channel numerators sum to zero
+\be
+\label{eq:ZMJacobi}
+\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
+\ee
+by virtue of the 2D Levi-Civita identity $\epsilon_{\mu\nu}\epsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
+Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.
+
+Since ZM theory manifested color-kinematics duality without any reference to the on-shell condition, a mass term can be added to ZM theory without spoiling color-kinematics duality.
+In fact, the kinetic term could be dramatically altered.
+In general, if the on-shell conditions are not used, color-kinematics duality is unaffected by the details of the propagator structure.
+Of course, dramatically altering the pole structure could spoil locality in the double-coppied theory.
+As already mentioned, the only difference classically between ZM and SDYM is the propagator structure.
+While both theories are color dual for the same reason, altering the propagators has profound consequences since SDYM tree amplitudes vanish and manifest color-kinematics does not persist to all loop orders.
+Color dual theories with the same interactions but different kinetic terms have appeared in the literature before.
+For example, J-theory and the theory of non-Abelian fluids presented in \cite{Cheung:2020djz} differ only in their propagators.
+Specifically, taking the static limit of the fluid's $(D+1)$-dimensional kinetic term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates yields the relativistic d'Alembertian of $D$-dimensional J-theory.
+
+While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization.
+Similar to the difficulties of renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
+As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
+
+\paragraph{Wess-Zumino-Witten theory -- James}
+I want to write this down or I'm going to completely forget it
+
+Should probably also mention that BAS has CK at Lagrangian level (duh).
+
+\paragraph{Cubic 2-form theory -- James}
+
+Cubic 2-form theory also has trivial CK.
+If you change the propagator (this trick is a theme) then you get YM at least classically.
+This is the nonsense ``covariant'' DC.
+
+\paragraph{Chern-Simons theory -- James}
+We won't use this but it's useful to treat all of the CK theories in one place
+Cite Henrik Maor
+Again you place some constraint on the field strength and use Lorenz gauge
+
+\paragraph{Generalities of known color-dual theories -- James}
+Should this section maybe go first?
+
+\begin{itemize}
+\item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
+\item All of the theories described above have diff as kinematic algebra, SU(N) for BAS, or rigid/spin Lorenz for cubic 2-form theory
+\item All of the theories choose a simple gauge like Lorenz or lightcone
+\item All of the theories place some constraint on the field strength directly and get their equations of motion directly from that constraint, not the YM EOM.
+\item (Almost all of the theories (aside from NLSM) have trivial amplitudes at least at tree level)
+\item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
+\item For off-shell CK, the kinetic term is relatively unimportant so long as the poles are correctly/consistently identified (what do you mean by s,t,u channel poles).
+This might screw up locality in the squared theory.
+\end{itemize}
+\section{Spinor-helicity and conventions}
 Dimensions will generically be away from four, in $D=4-2\epsilon$, with $\epsilon$ arbitrary.
@@
 Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
-
-\section{Review of known theories}
-\label{sec:CKLagrangians}
-In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual.
-As we will show, taking forward limits of tree-level numerators works as long as one can construct an off-shell description with a Lagrangian.
-Here we briefly review the off-shell examples of the kinematic algebra that will be relevant in this paper.
-\be
-\mathcal{L}^{\text{semi-YM}} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} - \frac{g}{2} G_{\mu\nu} [A_\mu, A_\nu]
-\ee
-\jm{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
-\subsubsection{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
-\be
-\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
-\ee
-To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
-\be\label{SDcon}
-F_{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
-\ee
-where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength.
-Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
-\be
-D^\mu F^{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
-\ee
-Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills.
-In this paper, we will focus on the perturbative aspects of this constraint.
-Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
-\be
-u = t+x,\quad v=t-x, \quad w = y+iz
-\ee
-which gives the following expression for the invariant line element:
-\be
-ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
-\ee
-Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
-\begin{align} \label{SDLightCone1}
-F_{uw} &=0\,,
-\\
- \label{SDLightCone2}
- F_{uv} &= F_{w\bar{w}}\,,
-\\
- \label{SDLightCone3}
- F_{v\bar{w}} &= 0\,,
-\end{align}
-Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
-\be
-A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
-\ee
-The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
-\be
-A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
-\ee
-This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
-\be\label{SDDef}
-A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
-\ee
-Using this definition on the final \jm{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
-\be\label{SDEOM}
-(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
-\ee
-Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
-\begin{eBox}
-\be
-\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
-\ee
-\end{eBox}
-The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
-\be
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
-\ee
-In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
-In this form, we can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
-Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.
-
-As we will show in \sect{}, the color-dual nature of SDYM can be understood as a direct consequence of isolating the \textit{cubic-sector} of the full Yang-Mills amplitudes by projecting along particular on-shell states.
-For this reason, the color-dual nature depends critically on the loop order of the amplitude and does not hold generically beyond one-loop.
-
-Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \cref{SDEOM}.
-
-\subsubsection{YZ-Theory}
-SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \cref{sec:ZMTheory}, does as well.
-This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
-On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung:2016prv}.
-
-One can understand YZ-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions. 
-Starting with the Yang-Mills Lagrangian, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
-\begin{align}
-X_M &= (X_\mu,0,-iX_\mu) 
-\\
-Y_M &= (0,Y,0) 
-\\
-Z_M &= (Z_\mu,0,iZ_\mu) 
-\end{align}
-where $X$ and $Z$ are $d$-vectors and $Y$ is a scalar field.
-Considering the conjugate nature of the X-Z propagator, in this work we will make the replacement $X\rightarrow \bar{Z}$.
-Plugging this redefinition of the gauge fields in, upto cubic order, we thus obtain the following Lagrangian:
-\begin{eBox}
-\be
-\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)
-\ee
-\end{eBox}
-The Feynman rules for this Lagrangian are simply:
-\be
-\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i \varepsilon_3 (p_1-p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
-\ee
-Now we review of the construction of NLSM numerators at tree-level. In this construction, we can define generators of the kinematic algebra can be expressed as follows
-\be\label{eq:FeynmanRuleYYZ}
-T^a_{ij}= i \varepsilon_a(p_i-p_j)
-\ee
-where momentum conservation requires
-\be
-p_a + p_i + p_j =0
-\ee
-The kinematic half-ladder diagrams then takes on the following concise definition:
-\be
-n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
-\ee
-Since there are on pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the chiral current algebra is manifestly cubic.
-Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom.
-They can be defined implicitly below:
-\be
-[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}
-\ee
-Given this definition, the Feynman rule associated with kinematic structure constant is simply:
-\be\label{eq:FeynmanRuleXZZ}
-i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c) 
-\ee
-where $p_{ab}=p_a+p_b$ and $\epsilon$ and $\bar{\epsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
-The on-shell state sum for the polarization vectors is simply:
-\be
-\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}
-\ee
-Notice that the vector state sum is gauge fixed since the $Y\,Z$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$.
-To recover NLSM amplitudes from this these kinematic structure constants at tree-level, we simply plug in the following on-shell polarizations for the $Z$ and $\bar{Z}$ particles:
-\be\label{eq:onShellZStates}
-\varepsilon^\mu_{(p)} = p^\mu \qquad \bar{\varepsilon}^\mu_{(p)} = \frac{q^\mu}{pq}
-\ee
-where $q^2=0$ is some null reference momentum. With this, we can define tree-level pion scattering in two equivalent ways:
-\be
-A^{\text{NLSM}} = A(...,Y,...,Y,...) = A(...,\bar{Z},...) 
-\ee
-where the ellipses denote additional on-shell $Z$-particles.
-Subject to a particular gauge choice, the kinematic numerators in latter definition for pion scattering is equivalent to those $J$-theory, first written down by Cheung and one of the authors \cite{Cheung:2021zvb}.
-In this paradigm, the on-shell $\bar{Z}$ state is equivalent to the root leg appearing in the color-dual $J$-theory numerators.
-
-It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion.
-First we'll start with two $Y$ particles on legs 1 and 4.
-Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
-\begin{align}
-n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
-\\
- n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
-\end{align}
-Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
-\be\label{eq:NLSMYZ4point}
-A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
-\ee
-Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration.
-Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free.
-This produces the following numerators:
-\begin{align}
-n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
-\\
- n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
-\end{align}
-where we have defined the short hand notation:
-\be
-{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
-\ee
-Similarly, we find the following ordered amplitude when plugging in these numerators:
-\be
-A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
-\ee
-Plugging in the on-shell polarizatoin of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
-Indeed, this construction is valid to all orders at tree-level.
-One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
-\begin{align}
-A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
-\\
-&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
-\end{align}
-Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
-As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
-Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
-This is essentially what $J$-thepory does, as we will show below.
-
-\subsubsection{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
-For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
-The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
-First order formulation of NLSM in terms of chiral current $J^\mu$.
-Two equations.
-Two constraints, the field strength should vanish
-\be
-\label{eq:FieldStrengthJ}
-F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
-\ee
-which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
-The second condition is that the chiral current should be in Lorenz gauge
-\be
-\label{eq:LorenzGaugeJ}
-\partial_\mu J^\mu=0
-\ee
-which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
-Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
-\be
-\label{eq:JTheoryEOM}
-\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
-\ee
-Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian
-\begin{eBox}
-\be
-\mathcal{L}^{\text{J}} =\bar{J}^\mu \Box J_\mu +g f^{abc} \bar{J}^\mu J^\nu \partial_\nu J^\mu .
-\ee
-\end{eBox}
-By calculating an off-shell 4pt correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
-Kinematic algebra is diff algebra (as usual).
-How to extract physical states... (longitudinal J, weird J bar, restores broken Bose).
-
-This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states. As such, the single vertex in this theory is the same as for YZ theory: 
-\be
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
-\ee
-
-\subsubsection{Zakharov-Mikhailov theory}
-\label{sec:ZMTheory}
-While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
-Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
-After plugging $\varphi$ into \cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
-\begin{eBox}
-\be
-\label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
-\ee
-\end{eBox}
-This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
-ZM theory can also be tenuously motivated from SDYM theory.
-The power counting of the interaction term in the SDYM equation of motion \cref{SDEOM} makes it clear that the theory is critical in 2D.
-This suggests that the two lightcone coordinates $u$ and $w$ should be identified as the coordinates of the 2D space.
-The 4D d'Alembertian in lightcone coordinates, $\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$, cannot be interpreted as the 2D equivalent, so the kinetic term of SDYM must be scrapped and replaced with the correct 2D version.
-This argument should be understood purely as an alternative route to ZM theory.
-While NLSM and ZM are the same theory classically when restricted to 2D, SDYM and ZM are not because, for example, the tree amplitudes of SDYM vanish but those of ZM do not (cite argumentative papers).
-
-The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \cref{eq:ZMLagrangian}, giving
-\be
-\langle ab\rangle \equiv p_a^\mu \epsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
-\ee
-The vertex is (1) functionally symmetric and (2) the kinematic portion of the vertex is completely anti-symmetric: 
-\be
-\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
-\ee
-This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
-To prove off-shell color kinematics duality for any multiplicity and loop order it is enough to observe that the sum of the off-shell $s$-, $t$-, and $u$-channel numerators sum to zero
-\be
-\label{eq:ZMJacobi}
-\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
-\ee
-by virtue of the 2D Levi-Civita identity $\epsilon_{\mu\nu}\epsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
-Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.
-
-Since ZM theory manifested color-kinematics duality without any reference to the on-shell condition, a mass term can be added to ZM theory without spoiling color-kinematics duality.
-In fact, the kinetic term could be dramatically altered.
-In general, if the on-shell conditions are not used, color-kinematics duality is unaffected by the details of the propagator structure.
-Of course, dramatically altering the pole structure could spoil locality in the double-coppied theory.
-As already mentioned, the only difference classically between ZM and SDYM is the propagator structure.
-While both theories are color dual for the same reason, altering the propagators has profound consequences since SDYM tree amplitudes vanish and manifest color-kinematics does not persist to all loop orders.
-Color dual theories with the same interactions but different kinetic terms have appeared in the literature before.
-For example, J-theory and the theory of non-Abelian fluids presented in \cite{Cheung:2020djz} differ only in their propagators.
-Specifically, taking the static limit of the fluid's $(D+1)$-dimensional kinetic term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates yields the relativistic d'Alembertian of $D$-dimensional J-theory.
-
-While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization.
-Similar to the difficulties of renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
-As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
-
-\subsubsection{Wess-Zumino-Witten theory -- James}
-I want to write this down or I'm going to completely forget it
-
-Should probably also mention that BAS has CK at Lagrangian level (duh).
-
-\subsubsection{Cubic 2-form theory -- James}
-
-Cubic 2-form theory also has trivial CK.
-If you change the propagator (this trick is a theme) then you get YM at least classically.
-This is the nonsense ``covariant'' DC.
-
-\subsubsection{Chern-Simons theory -- James}
-We won't use this but it's useful to treat all of the CK theories in one place
-Cite Henrik Maor
-Again you place some constraint on the field strength and use Lorenz gauge
-
-\subsubsection{Generalities of known color-dual theories -- James}
-Should this section maybe go first?
-
-\begin{itemize}
-\item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
-\item All of the theories described above have diff as kinematic algebra, SU(N) for BAS, or rigid/spin Lorenz for cubic 2-form theory
-\item All of the theories choose a simple gauge like Lorenz or lightcone
-\item All of the theories place some constraint on the field strength directly and get their equations of motion directly from that constraint, not the YM EOM.
-\item (Almost all of the theories (aside from NLSM) have trivial amplitudes at least at tree level)
-\item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
-\item For off-shell CK, the kinetic term is relatively unimportant so long as the poles are correctly/consistently identified (what do you mean by s,t,u channel poles).
-This might screw up locality in the squared theory.
-\end{itemize}
-
 \section{Notes to self -- James}

### 2023-08-30 notes/2loopNLSM.tex
A few more sentences on nonlocal.

--- 2023-08-30 notes/2loopNLSM.tex
@@
 
-As a first attempt at such a tame non-local representation,
+As a first attempt at such a non-local representation, we consider
+allowing one factor each of $s$,$t$, or $u$ in the denominator of each
+of the double-box and penta-triangle numerators, in addition to the
+standard local ansatze.  In order to not over-count the local terms,
+we restrict the non-local ansatze to only truly rational terms, \eg
+for the term $n_{\text{nl}}\sim \frac{x}{s}$ we drop all terms with
+$x \propto s$.  Thus each basis diagram ansatz contains 114,422 terms
+to start, 10,010 from the local terms and 34,804 from each of the
+three non-local pieces.
 
 \begin{itemize}
-\item Recap assumptions of \cite{Bern:2015ooa}
-\item Going beyond ``Feynman-type counting'' $\to$ 10010 initial
-  ansatz.  Compare post-(sym+GI) on BCJ basis.
-\item Discuss which cuts still fail.  Double check these statements
   \item Attempt at non-local.  Still have problems with cuts+syms+jacobi

### 2023-08-31 notes/2loopNLSM.tex
Added basic figs for the YM discussion.  Added color aliases for different colors (even though some of the names currently point to the same color).

@@
 \definecolor{nu-40}{RGB}{164, 149, 195}
-\colorlet{ucp-color}{nu-40}
+\colorlet{ucp-color}{nhpBlue}
+\colorlet{cut-color}{nhp4}
+\colorlet{jacobi-color}{nhp4}
+\colorlet{refl-color}{nhp4}
 
@@
 \item How can bubble on external legs that are zero by IBP inform generalizations beyond pions?
+\item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
+    , \textcolor{cut-color}{\texttt{cut-color}},
+    \textcolor{refl-color}{\texttt{refl-color}},and
+    \textcolor{jacobi-color}{\texttt{jacobi-color}} as aliases for
+    other colors so that we don't have to keep changing colors in
+    multiple locations when we want to change diagram color schemes.
+    I think I have updated all of the diagrams to use the
+    correctly-named color, but haven't changed any of the backing
+    colors for the names.}
 \end{enumerate}
@@
 constraints that directly involve such pathological diagrams.  That
-leaves us with 14 non-pathological cubic diagrams on which to impose
+leaves us with 14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc} on which to impose
 maximal cuts and symmetries. \ace{Do we want the graphs for these?
@@
 BDN-restricted ansatz.
+
+\begin{figure}
+  \foreach \x in {1,...,14}
+  {
+    \begin{minipage}{0.32\textwidth}
+      \includegraphics[width=\textwidth]{temp-figs/nonpath-mc-\x.pdf}
+    \end{minipage}
+  }
+  \caption{The 14 non-pathological maximal-cut diagrams}
+  \label{fig:ym-mc}
+\end{figure}
 
@@
       \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
-      \draw[dashed,ultra thick,nhp4] (0,0) -- (c1);
-      \draw[dashed,ultra thick,nhp4] (0,0) -- (c2);
-      \draw[dashed,ultra thick,nhp4] (0,0) -- (c3);
-      \draw[dashed,ultra thick,nhp4] (0,0) -- (c4);
-      \draw[dashed,ultra thick,nhp4] (c5) -- ++(90:0.7*\cl);
+      \draw[dashed,ultra thick,cut-color] (0,0) -- (c1);
+      \draw[dashed,ultra thick,cut-color] (0,0) -- (c2);
+      \draw[dashed,ultra thick,cut-color] (0,0) -- (c3);
+      \draw[dashed,ultra thick,cut-color] (0,0) -- (c4);
+      \draw[dashed,ultra thick,cut-color] (c5) -- ++(90:0.7*\cl);
       \node[fill=white,circle] (c) at (0,0) {};
@@
 exactly what such a cut and cut contribution means.  After discarding
-these types of cuts, we are left with 8 unique cut topologies to
-check.  Seven of these next-to-maximal cuts are consistent with the
-kinematic Jacobi relations and symmetries.  Interestingly, the
-``kissing triangles'' cut,
+these types of cuts, we are left with 8 unique cut topologies, shown
+in \cref{fig:ym-nmc}, to check.  Seven of these next-to-maximal cuts
+are consistent with the kinematic Jacobi relations and symmetries.
+Interestingly, the ``kissing triangles'' cut,
 \begin{equation*}
@@
 ansatz with Jacobi relations and symmetries applied.
+
+\begin{figure}
+  \foreach \x in {1,...,8}
+  {
+    \begin{minipage}{0.32\textwidth}
+      \includegraphics[width=\textwidth]{temp-figs/nonpath-nmc-\x.pdf}
+    \end{minipage}
+  }
+  \caption{The 8 non-pathological next-to-maximal-cut diagrams}
+  \label{fig:ym-nmc}
+\end{figure}
 
@@
 
+\iffalse
 We now turn to exploring the use of non-local numerators to skirt the
@@
 three non-local pieces.
-
-\begin{itemize}
-  \item Attempt at non-local.  Still have problems with cuts+syms+jacobi
-  \end{itemize}
+\fi
 

### 2023-08-31 notes/2loopNLSM.tex
Added first gen unit example.

@@
  \newcommand{\cblue}{\color{blue}}
- \definecolor{MattOrange}{rgb}{1.0,0.4,0.2}
-\newcommand{\cob}{ \bf \color{MattOrange}}
 \newcommand{\andd}{\ , \quad \text{and}  \quad}
@@
 
+\newcommand{\atree}{\ensuremath{A^{\text{tree}}}}
 \newcommand{\afour}{\ensuremath{A_4^{\text{tree}}}}
@@
 \label{sec:unitarity}
-
-The last key constraint is that the ansatz have the correct unitarity cuts, that is, that the integrand corresponds to the correct theory.
-Generalized unitarity has been reviewed in many places (cite...) so we will not belabor the details here, in particular see (emu) for a recent treatment of unitarity methods for even multiplicity theories like NLSM.
-The essence of generalized unitarity is that when internal lines are placed on-shell, the integrand should factorize into a product of on-shell tree amplitudes.
-The cut to be performed can, itself, be encoded in a graph.
-For example, potential 4pt 2-loop cuts include
-\be
+The last key source of constraints comes from ensuring that the ansatz
+correctly reproduces the generalized unitarity cuts of the theory.
+Matching the unitarity cuts provides the vast majority of
+theory-dependent information for the ansatz by ensuring that the
+numerators under construction are actually a valid representation of
+the theory being considered.  Generalized unitarity methods has been
+reviewed in many places \cite{BCFUnitarity, BernHuangReview,
+  Bern:2015ooa, Bourjaily:2017wjl, JJHenrikReview, FivePointN4BCJ,
+  Bern:2012uf, BCJreview, Edison:2022jln} \ace{Here is a semi-random
+  collection of unitarity-related citations.  Probably want to bulk it
+  up a bit more} so we will be light on details here. We also want to
+call special attention to Ref.~\cite{Carrasco:2023qgz} for a recent
+treatment of unitarity methods optimized for even multiplicity
+theories like NLSM.
+
+In the context of loop integrand construction, generalized unitarity
+allows us to equate products of on-shell tree amplitudes encoded via
+graphs, \eg
+\begin{equation}
+  \label{eq:example-cut-prod}
+  \ExCutLabeled{1}{2}{3}{4} = \!\!\!\!\! \sum_{\substack{\text{states of }\\ \{\ell_1, \ell_2, \ell_3, \ell_4\}}} \!\!\!\!\!\!\!
+  \atree(1,2,\ell_1,\ell_2) \atree(-\ell_1,-\ell_2,\ell_3,\ell_4) \atree(-\ell_3,-\ell_4,3,4) \,,
+\end{equation}
+to sums over compatible\footnote{A diagram $g$ is compatible with the
+  cut diagram $\gamma$ if $g$ is isomorphic to $\gamma$ or to any of
+  the additional factorization channels of $\gamma$. } diagram
+numerators evaluated on the support of the on-shell conditions and
+weighted by their uncut propagators, \eg
+\begin{align}
+  \label{eq:example-cut-sum}
+  \ExCutLabeled{1}{2}{3}{4} &=
+  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
+    \delta(\textcolor{cut-color}{\ell_2^2})
+    \delta(\textcolor{cut-color}{\ell_3^2})
+    \delta(\textcolor{cut-color}{\ell_4^2})}{(\textcolor{ucp-color}{\ell_5})^2
+    (\textcolor{ucp-color}{\ell_6})^2
+    (\textcolor{ucp-color}{\ell_7})^2}
+  \ n\left[
+    \IUCContrib{1}{4}{3}{2}
+                              \right] \notag \\
+  &\quad + 
+  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
+    \delta(\textcolor{cut-color}{\ell_2^2})
+    \delta(\textcolor{cut-color}{\ell_3^2})
+    \delta(\textcolor{cut-color}{\ell_4^2})}
+    {(\textcolor{ucp-color}{\ell_5})^2
+    (\textcolor{ucp-color}{\ell_6})^2
+    (\textcolor{ucp-color}{\ell_7'})^2}
+  \ n\left[
+    \IUCContrib{1}{3}{4}{2}
+    \right] + \text{others}
+\end{align}
+When drawing cut diagrams, we will use gray blobs as in the left-hand
+sides of \cref{eq:example-cut-prod,eq:example-cut-sum} and all drawn
+legs are assumed to be on-shell.  When drawing numerator contributions
+to cuts, we will not use blobs on vertices, and will use
+\textcolor{cut-color}{dashed lines} bisecting edges to denote cut
+lines and highlight the \textcolor{ucp-color}{uncut edges}.  From now
+on we will leave the cut $\delta(\ell^2)$s implicit.
+
+The essence of generalized unitarity is that when internal lines are
+placed on-shell, the integrand should factorize into a product of
+on-shell tree amplitudes.  The cut to be performed can, itself, be
+encoded in a graph.  For example, potential 4pt 2-loop cuts include
+\begin{equation}
 \label{eq:PotentialCuts}
 \text{(a)} \SubtleCut ~~~~ \text{(b)} \PhysicalCutOne{}{}{}{} ~~~~ \text{(c)} \PhysicalCutTwo{}{}{}{} ~~~~ \text{(d)}  \MaxCut
-\ee
+\end{equation}
 as well as many more.
@@
 As an equation, a unitarity cut looks schematically like
-\be
+\begin{equation}
 \label{eq:SchematicCutEquation}
-\sum \limits_\text{topologies} \frac{n \vert_\text{cut}}{\prod \limits_\text{uncut} k^2} = \sum \limits_\text{states} \prod \limits_\text{blobs} A_\text{tree} .
-\ee
-The right hand side of the equation is a product of on-shell tree amplitudes, represented graphically in \cref{eq:PotentialCuts} by grey blobs.
-States crossing (or propagating across) the cut must be summed over.
-For scalars this sum is trivial but for spinning particles this is no longer the case and the physical state projector must be inserted (see Dimitrius paper for simplifying this operation).
-The graph topologies appearing in the left hand side of \cref{eq:SchematicCutEquation} come from blowing up the grey blobs into cubic tree graphs in every conceivable way.
-The numerator of each graph is related back to the basis numerators via Jacobi relations.
-For each of these topologies, the numerator of the associated graph is subjected to the cut constraints and is then divided by the uncut propagators.
-The right hand side is assumed to be known, which places a constraint on the numerator ansatz in the left hand side.
-
-It is possible to work with either color-dressed cuts or color-ordered cuts.
-For color-dressed cuts the grey blobs are blown up into all possible channels and all color factors $f^{abc}$ are explicitly retained on both sides of the unitarity equation \cref{eq:SchematicCutEquation}.
-For color-ordered cuts the grey blobs are only blown up in color-ordered channels, all color factors in \cref{eq:SchematicCutEquation} are suppressed, and the product of on-shell amplitudes only extends over color-ordered trees.
-Since color-ordered cuts do not contain the full color information of the theory, it is necessary to do multiple color-ordered cuts -- over different orderings of the blob labels -- in order to fully capture all of the cut information.
-For a color dual theory such as NLSM or YM it is enough to do $(n-2)!$ labelings of each blob due to the Kleiss-Kuijf and $U(1)$ decoupling identities (cite KK).
-In this sense color-dressed cuts contain extraneous information that is bypassed when using color-ordered cuts.
-
-In our construction, only well-defined cuts are imposed so, for example, cut (a) of \cref{eq:PotentialCuts} is not enforced since it is possible to blow up the left blob into a tree amplitude with an on-shell internal propagator.
-Cuts (b), (c), and (d) represent physical cuts where (d) is known as a maximal cut since the maximal number of propagators have been put on shell.
-
-After imposing all of the conditions above, any remaining free parameters represent ``generalized gauge freedom'' meaning that the freedom does not affect the physical integrand or its double copy.
+\sum \limits_\text{topologies} \frac{n \vert_\text{cut}}{\prod \limits_\text{uncut} k^2} = \sum \limits_\text{states} \prod \limits_\text{blobs} A_\text{tree} \, .
+\end{equation}
+The right hand side of the equation is a product of on-shell tree
+amplitudes, represented graphically in \cref{eq:PotentialCuts} by grey
+blobs.  States crossing (or propagating across) the cut must be summed
+over.  For scalars this sum is trivial but for spinning particles this
+is no longer the case and the physical state projector must be
+inserted (see Dimitrius paper for simplifying this operation).  The
+graph topologies appearing in the left hand side of
+\cref{eq:SchematicCutEquation} come from blowing up the grey blobs
+into cubic tree graphs in every conceivable way.  The numerator of
+each graph is related back to the basis numerators via Jacobi
+relations.  For each of these topologies, the numerator of the
+associated graph is subjected to the cut constraints and is then
+divided by the uncut propagators.  The right hand side is assumed to
+be known, which places a constraint on the numerator ansatz in the
+left hand side.
+
+It is possible to work with either color-dressed cuts or color-ordered
+cuts.  For color-dressed cuts the grey blobs are blown up into all
+possible channels and all color factors $f^{abc}$ are explicitly
+retained on both sides of the unitarity equation
+\cref{eq:SchematicCutEquation}.  For color-ordered cuts the grey blobs
+are only blown up in color-ordered channels, all color factors in
+\cref{eq:SchematicCutEquation} are suppressed, and the product of
+on-shell amplitudes only extends over color-ordered trees.  Since
+color-ordered cuts do not contain the full color information of the
+theory, it is necessary to do multiple color-ordered cuts -- over
+different orderings of the blob labels -- in order to fully capture
+all of the cut information.  For a color dual theory such as NLSM or
+YM it is enough to do $(n-2)!$ labelings of each blob due to the
+Kleiss-Kuijf and $U(1)$ decoupling identities (cite KK).  In this
+sense color-dressed cuts contain extraneous information that is
+bypassed when using color-ordered cuts.
+
+In our construction, only well-defined cuts are imposed so, for
+example, cut (a) of \cref{eq:PotentialCuts} is not enforced since it
+is possible to blow up the left blob into a tree amplitude with an
+on-shell internal propagator.  Cuts (b), (c), and (d) represent
+physical cuts where (d) is known as a maximal cut since the maximal
+number of propagators have been put on shell.
+
+After imposing all of the conditions above, any remaining free
+parameters represent ``generalized gauge freedom'' meaning that the
+freedom does not affect the physical integrand or its double copy.
 
@@
   }
-  \caption{The 8 non-pathological next-to-maximal-cut diagrams}
+  \caption{The 8 non-pathological next-to-maximal-cut diagrams.
+    \ace{Note that Mathematica drew the bottom-left diagram with two
+      legs stacked on top of each other which eventually meet in a
+      3pt.  One leg is on the ``bottom level'' and connects with a 3pt
+      to the two legs coming off to the side, and the other is on the
+      ``top level'' and connects to the 4pt.}}
   \label{fig:ym-nmc}
@@
   =
-  \frac{1}{(\textcolor{nhpBlue}{\ell_1})^2} \
+  \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
   n \left[
@@
   +
-  \frac{1}{(\textcolor{nhpBlue}{\ell_2})^2} \
+  \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
   n\left[\KTDBContrib{1}{3}{2}{4}\right] \,.

### 2023-08-31 notes/2loopNLSM.tex
Starting cleanup of unitarity section.

@@
 In the context of loop integrand construction, generalized unitarity
-allows us to equate products of on-shell tree amplitudes encoded via
-graphs, \eg
+allows us to equate products of on-shell tree amplitudes, encoded via
+a graph $\gamma$, to sums over compatible\footnote{A diagram $g$ is compatible with the
+  cut diagram $\gamma$ if $g$ is isomorphic to $\gamma$ or to any of
+  the additional factorization channels of $\gamma$. } diagram
+numerators evaluated on the support of the on-shell conditions and
+weighted by their uncut propagators
+\begin{equation}
+\label{eq:SchematicCutEquation}
+\text{Cut}[\gamma]= \sum_{\substack{\text{states}\\\text{crossing } E(\gamma)}} \prod_{v \in V(\gamma)} \atree(v)
+= \sum_{g \text{ compat } \gamma}
+\frac{n[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
+ \, ,
+\end{equation}
+where $V(\gamma)$ are the vertices of $\gamma$ and $E(\gamma)$ its
+edges.  The sum over states hides much of the complexity of cut
+construction: for scalars the process is trivial while spinning states
+greatly complicate matters (see
+Refs.~\cite{Kosmopoulos:2020pcd,Edison:2022jln} for recent discussion
+and detailed examples of evaluating state sums).  It is useful to
+provide some examples of the two types of expressions appearing in
+\cref{eq:SchematicCutEquation}.  First the so-called
+iterated unitarity cut, which can be written in the product-of-trees
+representation as
 \begin{equation}
@@
 \end{equation}
-to sums over compatible\footnote{A diagram $g$ is compatible with the
-  cut diagram $\gamma$ if $g$ is isomorphic to $\gamma$ or to any of
-  the additional factorization channels of $\gamma$. } diagram
-numerators evaluated on the support of the on-shell conditions and
-weighted by their uncut propagators, \eg
+or in reference to a collection of diagram numerators as
 \begin{align}
@@
     \IUCContrib{1}{3}{4}{2}
-    \right] + \text{others}
+    \right] + 25\text{ others.}
 \end{align}
@@
 on we will leave the cut $\delta(\ell^2)$s implicit.
+
+In color-charged theories, both sides of the cut can be further
+decomposed according to the color algebra.  For theories charged under
+the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes
+
+It is possible to work with either color-dressed cuts or color-ordered
+cuts.  For color-dressed cuts the grey blobs are blown up into all
+possible channels and all color factors $f^{abc}$ are explicitly
+retained on both sides of the unitarity equation
+\cref{eq:SchematicCutEquation}.  For color-ordered cuts the grey blobs
+are only blown up in color-ordered channels, all color factors in
+\cref{eq:SchematicCutEquation} are suppressed, and the product of
+on-shell amplitudes only extends over color-ordered trees.  Since
+color-ordered cuts do not contain the full color information of the
+theory, it is necessary to do multiple color-ordered cuts -- over
+different orderings of the blob labels -- in order to fully capture
+all of the cut information.  For a color dual theory such as NLSM or
+YM it is enough to do $(n-2)!$ labelings of each blob due to the
+Kleiss-Kuijf and $U(1)$ decoupling identities (cite KK).  In this
+sense color-dressed cuts contain extraneous information that is
+bypassed when using color-ordered cuts.
 

### 2023-08-31 notes/2loopNLSM.tex
Working on pathological def.

@@
 \textcolor{cut-color}{dashed lines} bisecting edges to denote cut
-lines and highlight the \textcolor{ucp-color}{uncut edges}.  From now
-on we will leave the cut $\delta(\ell^2)$s implicit.
+lines and use colored edges to highlight the
+\textcolor{ucp-color}{uncut propagators}.  From now on we will leave
+the cut $\delta(\ell^2)$s implicit.
 
@@
 decomposed according to the color algebra.  For theories charged under
-the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes
-
-It is possible to work with either color-dressed cuts or color-ordered
-cuts.  For color-dressed cuts the grey blobs are blown up into all
-possible channels and all color factors $f^{abc}$ are explicitly
-retained on both sides of the unitarity equation
-\cref{eq:SchematicCutEquation}.  For color-ordered cuts the grey blobs
-are only blown up in color-ordered channels, all color factors in
-\cref{eq:SchematicCutEquation} are suppressed, and the product of
-on-shell amplitudes only extends over color-ordered trees.  Since
-color-ordered cuts do not contain the full color information of the
-theory, it is necessary to do multiple color-ordered cuts -- over
-different orderings of the blob labels -- in order to fully capture
-all of the cut information.  For a color dual theory such as NLSM or
-YM it is enough to do $(n-2)!$ labelings of each blob due to the
-Kleiss-Kuijf and $U(1)$ decoupling identities (cite KK).  In this
-sense color-dressed cuts contain extraneous information that is
-bypassed when using color-ordered cuts.
+the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes, it is
+convenient to project onto a specific basis of the Del
+Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
+inserting color-ordered amplitudes in the product of trees, and
+restricting the set of compatible diagrams to those whose color
+factors reduce to the appropriate DDM element when summing over
+\emph{only the uncut color contractions}.  In this situation, the
+color becomes an overall factor on the entire equality and thus can be
+ignored.  Cuts that are organized in this manner are known as
+``color-ordered'' cuts, in the same sense as color-ordered tree
+amplitudes.  Since the DDM basis (and dual Kleiss-Kuijf amplitude
+basis \cite{Kleiss:1988ne}) have $(n-2)!$ elements, one generally
+needs to evaluate that many separate color-orderings of the same cut.
+As an example, consider the ``kissing triangle'' cut topology, one of
+the factorization channels of the iterated unitarity cut, which has
+two topologically distinct color-ordered expansions
+\begin{equation}
+  \label{eq:kt-color-ord}
+  \KissingTriangles =
+  \begin{cases}
+     s\text{-}t \text{ channel}
+    &
+      \frac{1}{\textcolor{ucp-color}{s_{12}}}
+      n \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
+      \right]
+      +
+      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
+      n \left[
+      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
+      \right]\\
+    t\text{-}u \text{ channel}
+    & 
+      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
+      n \left[
+      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
+      \right]
+      +
+      \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
+      n\left[
+      \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
+      \right]
+  \end{cases}
+\end{equation}
+which serve as a complete basis for the full cut.
+
+Even beginning at one loop, we will encounter types of cuts that are
+difficult to properly define due to hidden non-physical singularities.
+The quintessential example of such a ``pathological'' cut is the 3-1
+two-particle cut at one loop which hides a bubble-on-external-leg
+singularity
+\begin{equation}
+  \begin{tikzpicture}
+\begin{feynman}
+\vertex (a1) at (-.8, -0.6) {};
+\vertex (a2) at (-.8, 0.6) {};
+\vertex (a3) at (-1, 0) {};
+\vertex [dot, scale=2](mid1) at (0,0){};
+\vertex [dot, scale=1.5,hgrey0](mid2) at (0,0){};
+\vertex [dot, scale=2](mid3) at (1,0){};
+\vertex [dot, scale=1.5,hgrey0](mid4) at (1,0){};
+\vertex (a4) at (1.8, 0) {};
+\diagram{
+(mid1) --[ultra thick,](a1),
+(mid1) --[ultra thick,](a2),
+(mid1) --[ultra thick,](a3),
+%(mid1) --[ultra thick,](mid3),
+(mid1) --[ultra thick,out=60,in=120,min distance=0.4cm](mid3),
+(mid1) --[ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
+(mid3) --[ultra thick](a4),
+};
+\end{feynman}
+\end{tikzpicture}
+\ni
+\frac{\delta(\textcolor{cut-color}{k_1^2})}{\textcolor{ucp-color}{k_1^2}}
+n \left[
+  \begin{tikzpicture}
+    \ver{e1}{-1,0};
+    \ver{e2}{-0.6,0.4};
+    \ver{e3}{-0.3,0.4};
+    \ver{i1}{-0.6,0};
+    \ver{i2}{-0.3,0};
+    \ver{i3}{0,0};
+    \ver{i4}{0.8,0};
+    \ver{co}{$(i3)!0.5!(i4)$};
+    \ver{e4}{1.2,0};
+    \draw[ultra thick] (e1)--(i1)--(i2)--(i3) to [out=80,in=100,min distance=0.4cm](i4)--(e4);
+    \draw[ultra thick,ucp-color](i1)--(i2)--(i3);
+    \draw[ultra thick,cut-color](i4)--(e4);
+    \draw[ultra thick] (i3) to [out=-80,in=-100,min distance=0.4cm](i4);
+    \draw[ultra thick] (e2) -- (i1);
+    \draw[ultra thick] (e3)--(i2);
+    \draw[ultra thick,dashed,cut-color] (co)--++(90:0.5);
+    \draw[ultra thick,dashed,cut-color] (co)--++(-90:0.5);
+  \end{tikzpicture}
+  \right]
+\end{equation}
 

### 2023-08-31 notes/2loopNLSM.tex
Finished first pass on unitarity rework.

@@
 the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes, it is
-convenient to project onto a specific basis of the Del
+convenient to project onto a specific element of the Del
 Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
@@
 
-Even beginning at one loop, we will encounter types of cuts that are
+Even beginning at one loop, we encounter classes of cuts that are
 difficult to properly define due to hidden non-physical singularities.
@@
 \begin{feynman}
-\vertex (a1) at (-.8, -0.6) {};
-\vertex (a2) at (-.8, 0.6) {};
-\vertex (a3) at (-1, 0) {};
+\vertex (a1) at (-.8, -0.6) {1};
+\vertex (a2) at (-.8, 0.6) {3};
+\vertex (a3) at (-1, 0) {2};
 \vertex [dot, scale=2](mid1) at (0,0){};
@@
 \vertex [dot, scale=1.5,hgrey0](mid4) at (1,0){};
-\vertex (a4) at (1.8, 0) {};
+\vertex (a4) at (1.8, 0) {4};
 \diagram{
@@
 \ni
-\frac{\delta(\textcolor{cut-color}{k_1^2})}{\textcolor{ucp-color}{k_1^2}}
+\frac{\delta(\textcolor{cut-color}{k_4^2})}{\textcolor{ucp-color}{s\, k_4^2}}
 n \left[
@@
 \end{equation}
-
+in which one of the uncut propagators is set equal to an external
+on-shell propagator.  Discussions about how to resolve these types of
+singularities can be found in Refs.~\cite{Edison:2022jln,
+  Edison:2022smn, Edison:2020uzf, Geyer:2015bja, Bern:2012uf}
+\citepls{Minahan}.  In addition to the bubble-on-external-leg cuts,
+there is a related class of cuts in which an uncut propagator is set
+to zero by an \emph{internal cut condition}, for instance,
+\begin{equation*}
+  \begin{tikzpicture}
+    \pgfmathsetmacro{\ri}{1};
+    \pgfmathsetmacro{\re}{0.6};
+    \pgfmathsetmacro{\ang}{35};
+    \begin{feynman}
+      \blob{i1}{\ang:\ri};
+      \blob{i2}{180-\ang:\ri};
+      \blob{i3}{180+\ang:\ri};
+      \blob{i4}{-\ang:\ri};
+      \blob{i5}{ $(i1)!0.5!(i2)$ };
+      \ver{e1}{45:\ri+\re};
+      \ver{e2}{135:\ri+\re};
+      \ver{e3}{225:\ri+\re};
+      \ver{e4}{-45:\ri+\re};
+
+      \diagram{
+        {[edges={ultra thick}] (e1)--(i1),
+          (e2)--(i2),
+          (e3)--(i3),
+          (e4)--(i4),
+          (i5)--(i1)--(i4)--(i3)--(i2),
+          (i2) --[out=60,in=180-60] (i5),
+          (i2) --[out=-60,in=180+60] (i5)
+        };
+      };
+    \end{feynman}
+  \end{tikzpicture}
+  \text{ contains a contribution from }
+  \begin{tikzpicture}
+    \pgfmathsetmacro{\ri}{1};
+    \pgfmathsetmacro{\re}{0.6};
+    \pgfmathsetmacro{\ang}{35};
+    \pgfmathsetmacro{\cang}{90};
+    \pgfmathsetmacro{\cl}{1.1};
+      \ver{i1}{\ang:\ri};
+      \ver{i2}{180-\ang:\ri};
+      \ver{i3}{180+\ang:\ri};
+      \ver{i4}{-\ang:\ri};
+      \ver{i5}{ $(i1)!0.25!(i2)$ };
+      \ver{i6}{ $(i1)!0.75!(i2)$ };
+
+      \ver{e1}{45:\ri+\re};
+      \ver{e2}{135:\ri+\re};
+      \ver{e3}{225:\ri+\re};
+      \ver{e4}{-45:\ri+\re};
+
+      \ver{c1}{0:\cl};
+      \ver{c2}{\cang:\cl};
+      \ver{c3}{2*\cang:\cl};
+      \ver{c4}{3*\cang:\cl};
+      \ver{ci}{$(i5)!0.5!(i1)$};
+      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
+      \draw[ultra thick] (e1)--(i1);
+      \draw[ultra thick] (e2)--(i2);
+      \draw[ultra thick] (e3)--(i3);
+      \draw[ultra thick] (e4)--(i4);
+      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
+      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
+      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
+      \draw[dashed,ultra thick,cut-color] (0,0) -- (c1);
+      \draw[dashed,ultra thick,cut-color] (0,0) -- (c2);
+      \draw[dashed,ultra thick,cut-color] (0,0) -- (c3);
+      \draw[dashed,ultra thick,cut-color] (0,0) -- (c4);
+      \draw[dashed,ultra thick,cut-color] (c5) -- ++(90:0.7*\cl);
+      \node[fill=white,circle] (c) at (0,0) {};
+  \end{tikzpicture}.
+\end{equation*}
+Fully resolving both of these problems is beyond the scope of the
+current work, so we will simply not impose any constraints that
+require handling these type of cuts.
+
+\iffalse
 The essence of generalized unitarity is that when internal lines are
@@
 number of propagators have been put on shell.
+\fi
 
@@
   the dashed lines?} \jm{It looks good!  Can you omit the part where the blue lines actually cross?}\ace{Like so?}
-\begin{equation*}
-  \begin{tikzpicture}
-    \pgfmathsetmacro{\ri}{1};
-    \pgfmathsetmacro{\re}{0.6};
-    \pgfmathsetmacro{\ang}{35};
-    \begin{feynman}
-      \blob{i1}{\ang:\ri};
-      \blob{i2}{180-\ang:\ri};
-      \blob{i3}{180+\ang:\ri};
-      \blob{i4}{-\ang:\ri};
-      \blob{i5}{ $(i1)!0.5!(i2)$ };
-      \ver{e1}{45:\ri+\re};
-      \ver{e2}{135:\ri+\re};
-      \ver{e3}{225:\ri+\re};
-      \ver{e4}{-45:\ri+\re};
-
-      \diagram{
-        {[edges={ultra thick}] (e1)--(i1),
-          (e2)--(i2),
-          (e3)--(i3),
-          (e4)--(i4),
-          (i5)--(i1)--(i4)--(i3)--(i2),
-          (i2) --[out=60,in=180-60] (i5),
-          (i2) --[out=-60,in=180+60] (i5)
-        };
-      };
-    \end{feynman}
-  \end{tikzpicture}
-  \text{ contains a contribution from }
-  \begin{tikzpicture}
-    \pgfmathsetmacro{\ri}{1};
-    \pgfmathsetmacro{\re}{0.6};
-    \pgfmathsetmacro{\ang}{35};
-    \pgfmathsetmacro{\cang}{90};
-    \pgfmathsetmacro{\cl}{1.1};
-      \ver{i1}{\ang:\ri};
-      \ver{i2}{180-\ang:\ri};
-      \ver{i3}{180+\ang:\ri};
-      \ver{i4}{-\ang:\ri};
-      \ver{i5}{ $(i1)!0.25!(i2)$ };
-      \ver{i6}{ $(i1)!0.75!(i2)$ };
-
-      \ver{e1}{45:\ri+\re};
-      \ver{e2}{135:\ri+\re};
-      \ver{e3}{225:\ri+\re};
-      \ver{e4}{-45:\ri+\re};
-
-      \ver{c1}{0:\cl};
-      \ver{c2}{\cang:\cl};
-      \ver{c3}{2*\cang:\cl};
-      \ver{c4}{3*\cang:\cl};
-      \ver{ci}{$(i5)!0.5!(i1)$};
-      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
-      \draw[ultra thick] (e1)--(i1);
-      \draw[ultra thick] (e2)--(i2);
-      \draw[ultra thick] (e3)--(i3);
-      \draw[ultra thick] (e4)--(i4);
-      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
-      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
-      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c1);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c2);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c3);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c4);
-      \draw[dashed,ultra thick,cut-color] (c5) -- ++(90:0.7*\cl);
-      \node[fill=white,circle] (c) at (0,0) {};
-
-  \end{tikzpicture},
-\end{equation*}
+
 as it is non-trivial and beyond the scope of this paper to define

### 2023-08-31 notes/2loopNLSM.tex
More 2-loop NLSM and figures.

--- 2023-08-31 notes/2loopNLSM.tex
@@
 Note that the graph symmetry constraint is imposed on \emph{every} graph, not just the basis graphs.
-For example, the crossed box,
-\be
-\CrossedBoxGraphSym ,
-\ee
-is unchanged upon reflection across the horizontal axis (shown as a red dashed line).
-Since the crossed box can be written in terms of the double box and penta-triangle, this imposes non-trivial constraints on the ansatz.
+%For example, the symmetries of the crossed box are spanned by
+%\be
+%\CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{3}{4} \text{ and } \CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{4}{3}
+%\ee
+For example, the symmetries of the crossed box
+\be
+\CrossedBoxGraphSym{1}{2}{3}{4}
+\ee
+are spanned by $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
+In general, internal edge labels will have to be tracked as well.
+Care must be taken with the signs in a symmetry relation.
+To compensate for the antisymmetric structure of $f^{abc}$, the vertices are all totally antisymmetric and hence have signs built into their orientations.
+Once the signs are included in the symmetry relations, the crossed box can be expressed in terms of the double box and penta-triangle, thus imposing non-trivial constraints on the ansatz.
 
@@
 As we have seen, it is possible to coerce tree numerators into 1-loop numerators at any multiplicity for pions.
-However, these methods cannot be reapplied to generate 2-loop numerators, which begs the question ``is it possible to find globally color-dual numerators beyond 1-loop''.
-We will tackle this question for NLSM before moving on to YM.
-
-Every vertex in NLSM scales as $k^2$ so the numerator of a 4pt 2-loop diagram diagram scales as $k^{12}$.
+However, these methods cannot be reapplied to generate higher-loop numerators, which begs the question ``is it possible to find globally color-dual numerators beyond 1-loop''.
+We will tackle this question for N$^2$LO 2-to-2 scattering in NLSM before moving on to the same process in YM.
+
+Ignoring tadpoles and BEL graphs, there are 14 cubic 4pt 2-loop graphs (see later picture) which are related to each other via 21 Jacobi relations.
+As mentioned in (review section), color-kinematics duality ensures that the numerator of every graph can be expressed in terms of a basis of the double box and penta-triangle,
+\be 
+\NLSMBasisDoubleBox \text{ and } \NLSMBasisPentaTriangle .
+\ee
+For a scalar theory like NLSM the numerator only depends on dot products of momenta.
+The basis of Mandelstam invariants for both of these graphs can be taken to be
+\be
+\{ k_{13}, k_{23}, k_{15}, k_{16}, k_{25}, k_{26}, k_{35}, k_{36}, k_{55}, k_{56}, k_{66} \},
+\ee
+where $k_{ij}$ means $k_i \cdot k_j$, $k_5=\ell_1$, and $k_5 = \ell_2$.
+%%%%
+% Basis for both diagrams
+% {d[p[1], p[3]], d[p[1], p[6]], d[p[1], p[7]], d[p[2], p[3]],  d[p[2], p[6]], d[p[2], p[7]], d[p[3], p[6]], d[p[3], p[7]],  d[p[6], p[6]], d[p[6], p[7]], d[p[7], p[7]]}
+%%%%
+Every vertex in NLSM scales as $k^2$ so the numerator of each diagram scales as $k^{12}$.
 At this mass dimension there are 8,008 independent dot products of momenta.
-Ignoring tadpoles and BEL graphs, there are 14 cubic 4pt 2-loop graphs, but they are related to one another via 21 distinct Jacobi relations.
-As mentioned in (review section), this means that the numerator of every graph can be expressed in terms of the double box and penta-triangle.
 With two basis graphs there is a total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is not suited to equations with sixteen thousand parameters so a different method is desirable.
@@
 Imposing all relevant cuts leaves 765 free parameters representing the generalized gauge freedom in the answer.
+Again, ambiguous non-physical cuts are not imposed.
 
@@
 One hope would be to factor out some piece of the 1-loop numerator since this at least manifests antisymmetry for the vertices involving external legs.
-However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov theory (cite ZM, James).
+However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov theory \citepls{Original ZM paper, ZM CK paper}.
 
@@
 The loop momentum structure of ZM theory provides one final hint for simplifying the pion numerators.
-Both loop momenta $\ell_1$ and $\ell_2$ appear in the ZM numerators but only 5 to 8 powers appear in any term, that is, each term in the ZM numerator scales as either $\ell^5$, $\ell^6$, $\ell^7$, or $\ell^8$ where $\ell$ here refers to any combination of $\ell_1$ or $\ell_2$.
+A generic term in the ZM numerator (of either basis graph) looks schematically like
+\be
+\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8.
+\ee
+In other words, every term contains between 5 and 8 powers of loop momenta, as one would expect from a set of local, cubic Feynman rules.
+\jm{I believe this is true but I need to check it.}
 When the pion numerator is also forced to have this loop power counting, the number of generalized gauge freedom parameters reduces to 58.

### 2023-09-01 notes/2loopNLSM.tex
Test, just added whitespace
Small edits about NLSM cuts

@@
 \begin{enumerate}
-\item Does our construction manifest all the cuts for the two-loop n-gon?
-\item What is the physics story here? Perturbative corrections to special Galilon, DBI for inflation? 
-\item How can bubble on external legs that are zero by IBP inform generalizations beyond pions?
 \item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
@@
 The final essential constraint is unitarity.
-Cuts (b) and (c) of \cref{eq:PotentialCuts} are the only non-vanishing cuts that need to be enforced.  \jm{Move some of the cut pictures here?}
-This means that even at two loops, unitarity cuts are still only probing the on-shell 4pt NLSM amplitude.
-Even though (b) and (c) are the only non-zero cuts, other cuts, for example the maximal cut (d), must also be imposed in order to correctly reproduce NLSM.
-The maximal cut vanishes because only 3pt amplitudes contribute and these amplitudes vanish in any scalar theory.
+Cuts (b) and (c) of \cref{eq:PotentialCuts} are the only physical cuts that need to be enforced.  \jm{Move some of the cut pictures here?}
+This means that even at two loops, unitarity is still only probing the on-shell 4pt NLSM amplitude.
+The other cuts besides (b) and (c) are either pathological or vanish because they involve a 3pt point on-shell amplitude (which vanishes in any scalar theory).
+In order to manifest the $\mathbb{Z}_2$ symmetry of NLSM at the integrand level, we enforce that all non-pathological cuts containing a 3pt vertex (such as the maximal cut) vanish.
+Imposing all relevant cuts leaves 765 free parameters representing the generalized gauge freedom in the answer.
+
 %It is possible to automatically enforce (or ``bake in'') the double box and penta-triangle max cuts on the ansatz by writing the ansatz in terms of inverse propagators (and remaining irreducible scalar products) and then only keeping terms that involve at least one inverse propagator since those terms will vanish on those max cuts, just as the product of 3pt scalar amplitudes will.
 %However, for the sake of simplicity we do not take this route.
-Imposing all relevant cuts leaves 765 free parameters representing the generalized gauge freedom in the answer.
-Again, ambiguous non-physical cuts are not imposed.
-
-\jm{Why aren't the two physical cuts spanning?  I know from experience that they're not but I can't easily explain why.}
 
@@
 off-shell propagator that carries the same momenta as one of the cut
-propagators, \eg \ace{Any feedback on how this looks, especially with
-  the dashed lines?} \jm{It looks good!  Can you omit the part where the blue lines actually cross?}\ace{Like so?}
+propagators, \eg 
 \begin{equation*}

### 2023-09-01 notes/2loopNLSM.tex
A few polishing touches on my sections.

--- 2023-09-01 notes/2loopNLSM.tex
@@
 
-\abstract{ For now, let's put the things we need to check/compute here in the abstract. 
+\abstract{
+\ace{I will start working here over the weekendish}
+
+TODO:\\
+For now, let's put the things we need to check/compute here in the abstract. 
 \begin{enumerate}
@@
     , \textcolor{cut-color}{\texttt{cut-color}},
-    \textcolor{refl-color}{\texttt{refl-color}},and
+    \textcolor{refl-color}{\texttt{refl-color}}, and
     \textcolor{jacobi-color}{\texttt{jacobi-color}} as aliases for
@@
 to zero by an \emph{internal cut condition}, for instance,
-\begin{equation*}
+\begin{equation}
+  \label{eq:other-path}
   \begin{tikzpicture}
@@
   \end{tikzpicture}.
-\end{equation*}
+\end{equation}
 Fully resolving both of these problems is beyond the scope of the
@@
 and the cubic $\mathcal{N}=4$ sYM representation from the well-known
-$n_{\text{DB}} = n_{\text{CB}} = s (st\, A_{\text{tree}})$ \citepls{}.
+$n_{\text{DB}} = n_{\text{CB}} = s^2t\, \atree)$ \citepls{}.
 On the other hand, we use the methods of Ref.~\cite{Carrasco:2023qgz}
@@
 implementation standpoint, the simplest assumption to break is the
-``power-counting'' statement, which we analyze first.
-
+``power-counting'' statement, which we now analyze.
+
+We follow the same general procedure as outlined above, again
+identifying the double-box and penta-triangle as the Jacobi basis
+graphs and building a generic ansatz for each of their numerators.
+Because we are now considering pure Yang--Mills, each monomial in the
+local ansatz must consist of five Lorentz scalar dot products instead
+of the six for NLSM, and each monomial must be linear in each of the
+four external gluon polarizations.  Thus, the ansatz will be built
+from terms of the form
+\begin{align}
+  \pol_1 \cdot k_2, \quad \pol_1 \cdot k_3, \quad& \pol_1 \cdot \ell_1, \quad \pol_1 \cdot \ell_2, \notag \\
+  \pol_2 \cdot k_1, \quad \pol_2 \cdot k_3, \quad& \pol_2 \cdot \ell_1, \quad \pol_2 \cdot \ell_2, \notag \\
+  \pol_3 \cdot k_1, \quad \pol_3 \cdot k_2, \quad& \pol_3 \cdot \ell_1, \quad \pol_3 \cdot \ell_2,  \\
+  \pol_4 \cdot k_1, \quad \pol_4 \cdot k_2, \quad& \pol_4 \cdot \ell_1, \quad \pol_4 \cdot \ell_2, \notag \\
+  \pol_1 \cdot \pol_2, \quad \pol_1 \cdot \pol_3, \quad& \pol_1 \cdot \pol_4, \quad \pol_2 \cdot \pol_3, \notag \\
+  \pol_2 \cdot \pol_4, \quad& \pol_3 \cdot \pol_4  \notag
+\end{align}
+in addition to the purely momentum-dependent terms show in \sect{}.
 In our labeling of the two loop Jacobi-basis diagrams, shown in
@@
 graphs in terms of the two basis graphs, including allowing nontrivial
-numerators on BEL diagrams.  We will simply avoid imposing
-constraints that directly involve such pathological diagrams.  That
-leaves us with 14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc} on which to impose
-maximal cuts and symmetries. \ace{Do we want the graphs for these?
-  Doable in tikz, but would take some time, or I can dump nice-ish
-  versions from mathematica}.  Doing so, we are left with AA total
-parameters in the unrestricted ansatz and BB total in the
-BDN-restricted ansatz.
+numerators on BEL diagrams.  We will simply avoid imposing constraints
+that directly involve such pathological diagrams.  That leaves us with
+14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc}, on
+which to impose maximal cuts and symmetries.  Doing so, we are left
+with AA total parameters in the unrestricted ansatz and BB total in
+the BDN-restricted ansatz.
 
@@
 
-Proceeding to the next-to-maximal cuts, we continue to avoid BEL
-diagrams.  Additionally, now that we have higher-point vertices, we
-avoid diagrams in which the higher-point vertex could contain an
-off-shell propagator that carries the same momenta as one of the cut
-propagators, \eg \ace{Any feedback on how this looks, especially with
-  the dashed lines?} \jm{It looks good!  Can you omit the part where the blue lines actually cross?}\ace{Like so?}
-\begin{equation*}
-  \begin{tikzpicture}
-    \pgfmathsetmacro{\ri}{1};
-    \pgfmathsetmacro{\re}{0.6};
-    \pgfmathsetmacro{\ang}{35};
-    \begin{feynman}
-      \blob{i1}{\ang:\ri};
-      \blob{i2}{180-\ang:\ri};
-      \blob{i3}{180+\ang:\ri};
-      \blob{i4}{-\ang:\ri};
-      \blob{i5}{ $(i1)!0.5!(i2)$ };
-      \ver{e1}{45:\ri+\re};
-      \ver{e2}{135:\ri+\re};
-      \ver{e3}{225:\ri+\re};
-      \ver{e4}{-45:\ri+\re};
-
-      \diagram{
-        {[edges={ultra thick}] (e1)--(i1),
-          (e2)--(i2),
-          (e3)--(i3),
-          (e4)--(i4),
-          (i5)--(i1)--(i4)--(i3)--(i2),
-          (i2) --[out=60,in=180-60] (i5),
-          (i2) --[out=-60,in=180+60] (i5)
-        };
-      };
-    \end{feynman}
-  \end{tikzpicture}
-  \text{ contains a contribution from }
-  \begin{tikzpicture}
-    \pgfmathsetmacro{\ri}{1};
-    \pgfmathsetmacro{\re}{0.6};
-    \pgfmathsetmacro{\ang}{35};
-    \pgfmathsetmacro{\cang}{90};
-    \pgfmathsetmacro{\cl}{1.1};
-      \ver{i1}{\ang:\ri};
-      \ver{i2}{180-\ang:\ri};
-      \ver{i3}{180+\ang:\ri};
-      \ver{i4}{-\ang:\ri};
-      \ver{i5}{ $(i1)!0.25!(i2)$ };
-      \ver{i6}{ $(i1)!0.75!(i2)$ };
-
-      \ver{e1}{45:\ri+\re};
-      \ver{e2}{135:\ri+\re};
-      \ver{e3}{225:\ri+\re};
-      \ver{e4}{-45:\ri+\re};
-
-      \ver{c1}{0:\cl};
-      \ver{c2}{\cang:\cl};
-      \ver{c3}{2*\cang:\cl};
-      \ver{c4}{3*\cang:\cl};
-      \ver{ci}{$(i5)!0.5!(i1)$};
-      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
-      \draw[ultra thick] (e1)--(i1);
-      \draw[ultra thick] (e2)--(i2);
-      \draw[ultra thick] (e3)--(i3);
-      \draw[ultra thick] (e4)--(i4);
-      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
-      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
-      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c1);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c2);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c3);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c4);
-      \draw[dashed,ultra thick,cut-color] (c5) -- ++(90:0.7*\cl);
-      \node[fill=white,circle] (c) at (0,0) {};
-
-  \end{tikzpicture},
-\end{equation*}
-as it is non-trivial and beyond the scope of this paper to define
-exactly what such a cut and cut contribution means.  After discarding
-these types of cuts, we are left with 8 unique cut topologies, shown
-in \cref{fig:ym-nmc}, to check.  Seven of these next-to-maximal cuts
-are consistent with the kinematic Jacobi relations and symmetries.
-Interestingly, the ``kissing triangles'' cut,
+Proceeding to the next-to-maximal cuts, we continue to avoid
+pathological diagrams including the newly-appearing type discussed in
+\cref{eq:other-path}. After discarding these types of cuts, we are
+left with 8 \ace{(maybe a few more to account for dangling trees)}
+unique cut topologies, shown in \cref{fig:ym-nmc}, to check.  Seven of
+these next-to-maximal cuts are consistent with the kinematic Jacobi
+relations and symmetries.  Interestingly, the ``kissing triangles''
+cut,
 \begin{equation*}
@@
 
-\ace{\sout{I need to check this.  For now it is a standing
-    hypothesis:} Checked.  The failure works as stated.} In fact, we can make the
-failure extremely precise.  Start with the diagrams shown in the
-Jacobi relation from \cref{eq:TwoLoopJacobiOne}: the double-box,
-crossed-box, and penta-triangle.  For each of the three diagrams,
-write down the most generic parity-even local ansatz involving four
-polarizations and six momenta (any combination of external or loop).
-Each ansatz will be 10,010 terms initially.  Next impose the symmetry
-constraints on each of the three diagrams, leaving 2761 free
-parameters on the double-box, 2576 free parameters on the crossed-box,
-and 5040 free paramters on the penta-triangle.  Then impose the
-``kissing triangle'' next-to-maximal cut, which in the
-\emph{non-planar} $t$-$u$ color channel only recieves contributions from the
-double-box
+In fact, we can make the failure extremely precise.  Start with the
+diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
+the double-box, crossed-box, and penta-triangle.  For each of the
+three diagrams, write down the most generic parity-even local ansatz
+involving four polarizations and six momenta (any combination of
+external or loop).  Each ansatz will be 10,010 terms initially.  Next
+impose the symmetry constraints on each of the three diagrams, leaving
+2761 free parameters on the double-box, 2576 free parameters on the
+crossed-box, and 5040 free paramters on the penta-triangle.  Then
+impose the ``kissing triangle'' next-to-maximal cut, which in the
+\emph{non-planar} $t$-$u$ color channel only recieves contributions
+from the double-box
 \begin{equation}
@@
 globally-color-dual two-loop Yang--Mills representation: locality,
-symmetry, and the ``kissing triangle'' cut are incompatible with the
-kinematic Jacobi relations.
+symmetry, and the kinematic Jacobi relations for just three diagrams
+are incompatible with the ``kissing triangle'' cut.
 

### 2023-09-05 notes/2loopNLSM.tex
Added some color and a few equation labels.

@@
 \end{equation}
-in which one of the uncut propagators is set equal to an external
-on-shell propagator.  Discussions about how to resolve these types of
-singularities can be found in Refs.~\cite{Edison:2022jln,
-  Edison:2022smn, Edison:2020uzf, Geyer:2015bja, Bern:2012uf}
-\citepls{Minahan}.  In addition to the bubble-on-external-leg cuts,
-there is a related class of cuts in which an uncut propagator is set
-to zero by an \emph{internal cut condition}, for instance,
+in which one of the \textcolor{ucp-color}{uncut propagators} is set
+equal to an \textcolor{cut-color}{external on-shell propagator}.
+Discussions about how to resolve these types of singularities can be
+found in Refs.~\cite{Edison:2022jln, Edison:2022smn, Edison:2020uzf,
+  Geyer:2015bja, Bern:2012uf} \citepls{Minahan}.  In addition to the
+bubble-on-external-leg cuts, there is a related class of cuts in which
+an uncut propagator is set to zero by an \emph{internal cut
+  condition}, for instance,
 \begin{equation}
@@
 As mentioned in (review section), color-kinematics duality ensures that the numerator of every graph can be expressed in terms of a basis of the double box and penta-triangle,
-\be 
+\begin{equation}
+\label{eq:jacobi-basis}
 \NLSMBasisDoubleBox \text{ and } \NLSMBasisPentaTriangle .
-\ee
+\end{equation}
 For a scalar theory like NLSM the numerator only depends on dot products of momenta.
 The basis of Mandelstam invariants for both of these graphs can be taken to be
-\be
+\begin{equation}
+\label{eq:scalar-basis}
 \{ k_{13}, k_{23}, k_{15}, k_{16}, k_{25}, k_{26}, k_{35}, k_{36}, k_{55}, k_{56}, k_{66} \},
-\ee
-where $k_{ij}$ means $k_i \cdot k_j$, $k_5=\ell_1$, and $k_5 = \ell_2$.
+\end{equation}
+where $k_{ij}$ means $k_i \cdot k_j$, $k_5=\ell_1$, and $k_6 = \ell_2$.
 %%%%
@@
 \end{align}
-in addition to the purely momentum-dependent terms show in \sect{}.
-In our labeling of the two loop Jacobi-basis diagrams, shown in
-\ace{Figure out fig}, we find that the power counting bound proposed
-by Bern, Davies, and Nohle leads to an initial ansatz with 10,000
-terms in the double-box, and 9849 terms for the penta-triangle.
-Without power counting restrictions, both the double-box and the
-penta-triangle ansatz have an ansatz with 10,010 terms each.  Imposing
-diagram automorphisms and maximal-cut gauge invariance on the two
-basis diagrams, we reduce the number of terms to XX for the
-double-box, and YY for the penta-triangle.  The power-counting
-restriction of BDN would further reduce these counts to 2232 and 4072.
-In Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
-imposed using a spanning set of minimal physical cuts, shown in
-\cref{fig:ym-spanning}.  Instead of also directly going to the
-spanning cuts, we work within the framework of the Method of Maximal
-Cuts \citepls{} in order to identify the simplest cut that is in
-tension with the kinematic Jacobi relations.
+in addition to the purely momentum-dependent terms show in
+\cref{eq:scalar-basis}.  In our labeling of the two loop Jacobi-basis
+diagrams, shown in \cref{eq:jacobi-basis}, we find that the power
+counting bound proposed by Bern, Davies, and Nohle leads to an initial
+ansatz with 10,000 terms in the double-box, and 9849 terms for the
+penta-triangle.  Without power counting restrictions, both the
+double-box and the penta-triangle ansatz have an ansatz with 10,010
+terms each.  Imposing diagram automorphisms and maximal-cut gauge
+invariance on the two basis diagrams, we reduce the number of terms to
+XX for the double-box, and YY for the penta-triangle.  The
+power-counting restriction of BDN would further reduce these counts to
+2232 and 4072.  In Ref.~\cite{Bern:2015ooa}, the unitarity matching
+constraints were imposed using a spanning set of minimal physical
+cuts, shown in \cref{fig:ym-spanning}.  Instead of also directly going
+to the spanning cuts, we work within the framework of the Method of
+Maximal Cuts \citepls{} in order to identify the simplest cut that is
+in tension with the kinematic Jacobi relations.
 

### 2023-09-06 notes/2loopNLSM.tex
Updated color-dual amp section

@@
 We will briefly review the perturbative construction of this theory below.
+
 \subsection{Color-dual Amplitudes}
-Review of BCJ relations and Jacobi relations off-shell. Justify kinematic algebra in an off-shell framework by talking about on-shell construction. yada yada yada
+
+I think this belongs in another section...
+Why DC is cool:
+1) Reduction in computational complexity.
+Off-shell high spin is terrible.
+Gravity has infinitely many very complex Feynman rules as a result of gauge redundancy but YM only has two relatively simple Feynman rules.
+2) DC points to deep structure hidden in Lagrangian formulation.
+
+Color-kinematics duality is a statement about amplitude integrands.
+Ignoring factors of $i$ and the coupling constant, a generic $m$-point $L$-loop amplitude in a color-dual theory -- such as NLSM, YM, or bi-adjoint scalar theory -- can be written as
+\be
+\mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma n_\Gamma}{d_\Gamma} .
+\ee
+Here the spacetime dimension is $D$.
+Even though the underlying theory may have quartic (or higher multiplicity) vertices, it is possible to multiply and divide by propagators so that the sum runs over only purely cubic graphs $\Gamma$.
+Overcounting is removed by the internal symmetry factor $S_\Gamma$, which tracks the number of graph symmetries with external legs held fixed.
+The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.
+However, the double copy can be applied to a far more diverse set of theories, see for example \citepls{$DF^2$, fundamental fermions, anything else anyone wants to mention}.}
+the denominator $d_\Gamma$ is the product of propagators associated with the graph $\Gamma$, and the numerator $n_\Gamma$ is all of the remaining kinematic factors including dot products of momenta and polarization vectors.
+
+The color factors $c_\Gamma$ are not independent and are related to one another via a set of Jacobi identities that look schematically like
+\be
+c_i+c_j+c_k=0,
+\ee
+where $i$, $j$, and $k$ are three graphs.
+An example Jacobi relation will be presented in \sect{}.
+Color-kinematics duality states that there exists a way to rearrange factors between the various kinematic numerators $n_\Gamma$ such that the numerators obey all of the same Jacobi identities as the color factors
+\be
+n_i +n_j +n_k=0.
+\ee
+If color-kinematics duality can be achieved at the off-shell level, then the kinematic numerators should satisfy an algebra just like the color factors.
+In theories where the kinematic algebra is known, it is often the algebra of volume preserving diffeomorphisms \citepls{Donal Ricardo SDYM, Henrik Maor CS, Cliff James NLSM, Cliff et al ZM}.
+
+Once color-dual numerators $n_\Gamma$ have been found, they can be used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a \emph{different} amplitude to produce the corresponding amplitude in the double-copy theory
+\be
+\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)} ~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma \tilde{n}_\Gamma}{d_\Gamma}.
+\ee
+Importantly, the $\tilde{n}_\Gamma$ do not need to respect color-kinematics duality.
+The prototypical example of the double-copy is that YM double copied with YM results in gravity where the gauge invariance of each separate gluon produces the diffeomorphism invariance of the graviton.
+The double copy can be proven at tree level using the KLT relations but there is significant evidence that the double copy persists to all loop orders \citepls{KLT, ``M.
+Kiermaier, Gravity as the square of gauge theory, in Amplitudes 2010, Queen Mary,
+University of London,
+https://strings.ph.qmul.ac.uk/?theory/Amplitudes2010/Talks/MK2010.pdf '',
+any loop papers we want}.
+
+Many of the 1-loop results presented in \sect{} are informed by the tree-level double-copy so we will review the tree case here.
+The color structure of tree-level amplitudes is particularly simple.
+A fully color dressed tree amplitude $\mathcal{A}$ in YM or NLSM can be decomposed in terms of the trace basis
+\be
+\mathcal{A}_m = \sum Tr(...) A[]
+\ee
+where, because of the cyclicity of the trace, $(n-1)!$ of the color-ordered partial amplitudes $A$ form a basis.
+Any color factor can be written in terms of the basis of $(n-2)!$ DDM half ladders, indicating that there are further linear relations (the KK relations) amongst the partial amplitudes (cite DDM, KK).
+The KLT relations (or tree-level color-kinematics duality) means that there are even more linear relations among the partial amplitudes, meaning that you can go to a basis of $(n-3)!$.
+At tree level, it is enough to specify the numerators of the half ladder topologies.
+By repeated application of the Jacobi identity, any other topology can be obtained from the half ladder.
+The same is true for 1-loop and the $n$-gon.
+
+Do 4pt tree example
+$c_s+c_t+c_u=0$ and $n_s+n_t+n_u=0$
+NLSM 4pt CK numerators and DC to sGal
 

### 2023-09-07 notes/2loopNLSM.tex
Revised color-dual amp section

@@
 The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.
-However, the double copy can be applied to a far more diverse set of theories, see for example \citepls{$DF^2$, fundamental fermions, anything else anyone wants to mention}.}
+However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu} \jm{I cited DF$^2$ and fundamental fermions.
+Is there anything else anyone wants to mention?}.}
 the denominator $d_\Gamma$ is the product of propagators associated with the graph $\Gamma$, and the numerator $n_\Gamma$ is all of the remaining kinematic factors including dot products of momenta and polarization vectors.
@@
 where $i$, $j$, and $k$ are three graphs.
-An example Jacobi relation will be presented in \sect{}.
+Example Jacobi relations are presented in detail in \cref{sec:bootstrap}.
 Color-kinematics duality states that there exists a way to rearrange factors between the various kinematic numerators $n_\Gamma$ such that the numerators obey all of the same Jacobi identities as the color factors
@@
 If color-kinematics duality can be achieved at the off-shell level, then the kinematic numerators should satisfy an algebra just like the color factors.
-In theories where the kinematic algebra is known, it is often the algebra of volume preserving diffeomorphisms \citepls{Donal Ricardo SDYM, Henrik Maor CS, Cliff James NLSM, Cliff et al ZM}.
+In theories where the kinematic algebra is known, it is often the algebra of volume preserving diffeomorphisms \cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz, Cheung:2021zvb, Cheung:2022mix}.
 
@@
 The prototypical example of the double-copy is that YM double copied with YM results in gravity where the gauge invariance of each separate gluon produces the diffeomorphism invariance of the graviton.
-The double copy can be proven at tree level using the KLT relations but there is significant evidence that the double copy persists to all loop orders \citepls{KLT, ``M.
-Kiermaier, Gravity as the square of gauge theory, in Amplitudes 2010, Queen Mary,
-University of London,
-https://strings.ph.qmul.ac.uk/?theory/Amplitudes2010/Talks/MK2010.pdf '',
-any loop papers we want}.
+The double copy can be proven at tree level using the KLT relations but there is significant evidence that the double copy persists to all loop orders \cite{KLT, KiermaierTalk} \citepls{Any loop papers we want?}.
 
@@
 The color structure of tree-level amplitudes is particularly simple.
-A fully color dressed tree amplitude $\mathcal{A}$ in YM or NLSM can be decomposed in terms of the trace basis
-\be
-\mathcal{A}_m = \sum Tr(...) A[]
-\ee
-where, because of the cyclicity of the trace, $(n-1)!$ of the color-ordered partial amplitudes $A$ form a basis.
-Any color factor can be written in terms of the basis of $(n-2)!$ DDM half ladders, indicating that there are further linear relations (the KK relations) amongst the partial amplitudes (cite DDM, KK).
-The KLT relations (or tree-level color-kinematics duality) means that there are even more linear relations among the partial amplitudes, meaning that you can go to a basis of $(n-3)!$.
-At tree level, it is enough to specify the numerators of the half ladder topologies.
-By repeated application of the Jacobi identity, any other topology can be obtained from the half ladder.
-The same is true for 1-loop and the $n$-gon.
-
-Do 4pt tree example
-$c_s+c_t+c_u=0$ and $n_s+n_t+n_u=0$
-NLSM 4pt CK numerators and DC to sGal
+A fully color dressed tree amplitude $\mathcal{A}_n$ in YM, NLSM, or bi-adjoint scalar theory can be decomposed in terms of the trace basis
+\be
+\mathcal{A}_n = \sum \limits_{\sigma\in S_{n-1}} \text{Tr}(T^{a_{\sigma_1}} T^{a_{\sigma_2}}...T^{a_{\sigma_{n-1}}} T^{a_n}) A_n[\sigma_1, \sigma_2,...\sigma_{n-1}, n],
+\ee
+where $T^a$ are generators of the gauge group and, because of the cyclicity of the trace, one of the legs is held fixed so that the sum runs over the $(n-1)!$ permutations of the remaining external legs.
+The coefficients of the color factors are the color-ordered partial amplitudes $A_n[...]$.
+Any tree-level color factor can be converted into a linear combination of Del Duca-Dixon-Maltoni (DDM) half-ladder color factors
+\be
+\text{DDM}[a_1, a_2,... a_n] \equiv f^{a_1 a_2 b_1} f^{b_1 a_3 b_2} f^{b_2 a_4 b_3}...f^{b_{n-3} a_{n-1} a_n}
+\ee
+associated with the graph
+\be
+\HalfLadder
+\ee
+by repeated application of the Jacobi identity \cite{DixonMaltoni}.
+The fully color-dressed tree amplitude can then be re-expressed as
+\be
+\mathcal{A}_n = \sum \limits_{\sigma\in S_{n-2}} \text{DDM}[a_1, a_{\sigma_2}, a_{\sigma_3}, a_{\sigma_{n-1}}, a_n]  A_n[1, \sigma_2,...\sigma_{n-1}, n]
+\ee
+with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$ terms, indicating that there are additional relations (the Kleiss-Kuijf relations) amongst the partial amplitudes \cite{Kleiss:1988ne}.\footnote{The fundamental BCJ relations further reduce the basis of partial amplitudes down to $(n-3)!$ \cite{BCJ}.}
+Since the Jacobi identity can be used to express any tree-level color factor in terms of the half ladders, it is enough to specify the numerators of the half ladder diagrams in order to satisfy color-kinematics duality at tree level.
+At 1-loop, every diagram can be related to one topology as well, in this case the $n$-gon, but the pattern does not persist to 2-loops.
+
+\jm{Should we do some example like 4pt NLSM or 4pt YM and say that it's simpler than GR?  I don't think it would add much.}
 

### 2023-09-11 notes/2loopNLSM.tex
some changes
cut graphs

@@
 \section{Introduction}
-\section{Review}
+\section{Background}
  To set the stage, it is worth distinguishing between the algebraic properties of functionally symmetric kinematics that satisfy color-kinematics globally, and some of the other constructions that appear in the literature.
@@
 \be
-\HalfLadder
+\halfLadder
 \ee
@@
 \begin{enumerate}
-\item Locality: Diagram ``numerators'' are polynomials in momenta and
+\item \textbf{Locality}: Diagram ``numerators'' are polynomials in momenta and
   polarizations, \eg the diagrams only have poles given by the
   propagators of the diagrams.
-\item Power-counting: The maximum power of the loop momenta in the
+\item  \textbf{Power-counting:} The maximum power of the loop momenta in the
   numerator is bounded by Feynman-gauge Feynman rules.
-\item Cubic diagrams: The only diagrams with nonzero numerators are
+\item  \textbf{Cubic diagrams}: The only diagrams with nonzero numerators are
   those with strictly cubic vertices.  This is generally a requirement
   to properly define the kinematic Jacobi relations.
-\item Relabeling : The diagram numerators are only a function of the
+\item  \textbf{Relabeling}: The diagram numerators are only a function of the
   diagram's topology and labeling.
-\item Symmetries: The diagram numerators are invariant under the
+\item  \textbf{Symmetries}: The diagram numerators are invariant under the
   automorphisms of the diagrams \emph{including signs that compensate
     for color-factor sign changes}.
-\item Unitarity cuts: The cuts of the ansatz must reproduce the
+\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the
   physical unitarity cuts of the theory.
-\item Color-kinematics duality: The numerators obey some form of the
+\item  \textbf{Color-kinematics duality}: The numerators obey some form of the
   kinematic Jacobi relations.
@@
   \label{eq:kt-color-ord}
-  \KissingTriangles =
+   \NMCutC =
   \begin{cases}
@@
 \begin{equation}
-  \begin{tikzpicture}
-\begin{feynman}
-\vertex (a1) at (-.8, -0.6) {1};
-\vertex (a2) at (-.8, 0.6) {3};
-\vertex (a3) at (-1, 0) {2};
-\vertex [dot, scale=2](mid1) at (0,0){};
-\vertex [dot, scale=1.5,hgrey0](mid2) at (0,0){};
-\vertex [dot, scale=2](mid3) at (1,0){};
-\vertex [dot, scale=1.5,hgrey0](mid4) at (1,0){};
-\vertex (a4) at (1.8, 0) {4};
-\diagram{
-(mid1) --[ultra thick,](a1),
-(mid1) --[ultra thick,](a2),
-(mid1) --[ultra thick,](a3),
-%(mid1) --[ultra thick,](mid3),
-(mid1) --[ultra thick,out=60,in=120,min distance=0.4cm](mid3),
-(mid1) --[ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
-(mid3) --[ultra thick](a4),
-};
-\end{feynman}
-\end{tikzpicture}
-\ni
 \frac{\delta(\textcolor{cut-color}{k_4^2})}{\textcolor{ucp-color}{s\, k_4^2}}
@@
   \right]
+  \in   \begin{tikzpicture}
+\begin{feynman}
+\vertex (a1) at (-.8, -0.6) {1};
+\vertex (a2) at (-.8, 0.6) {3};
+\vertex (a3) at (-1, 0) {2};
+\vertex [dot, scale=2](mid1) at (0,0){};
+\vertex [dot, scale=1.5,hgrey0](mid2) at (0,0){};
+\vertex [dot, scale=2](mid3) at (1,0){};
+\vertex [dot, scale=1.5,hgrey0](mid4) at (1,0){};
+\vertex (a4) at (1.8, 0) {4};
+\diagram{
+(mid1) --[ultra thick,](a1),
+(mid1) --[ultra thick,](a2),
+(mid1) --[ultra thick,](a3),
+%(mid1) --[ultra thick,](mid3),
+(mid1) --[ultra thick,out=60,in=120,min distance=0.4cm](mid3),
+(mid1) --[ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
+(mid3) --[ultra thick](a4),
+};
+\end{feynman}
+\end{tikzpicture}
 \end{equation}
@@
 \subsection{Semi-abelian Yang-Mills theory}
-\subsection{One-loop SDYM integrands}
+\subsection{One-loop color-dual integrands}
 \be
@@
 \ee
-\subsection{One-loop NLSM Integrands}
-
+\be
+\nGonScalar
+\ee
 Note from James:  I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.
@@
 the BDN-restricted ansatz.
-
 \begin{figure}
-  \foreach \x in {1,...,14}
-  {
-    \begin{minipage}{0.32\textwidth}
-      \includegraphics[width=\textwidth]{temp-figs/nonpath-mc-\x.pdf}
-    \end{minipage}
+\centering
+{\MCutC, \MCutD, \sumoCut, \MCutJ,  
+ \\
+  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
+\\
+\MCutI,  \MCutE, \MCutK, 
+\\
+ \MCutL, \MCutG,  \MCutH,
 }
   \caption{The 14 non-pathological maximal-cut diagrams}
-  \label{fig:ym-mc}
   \end{figure}
@@
 \begin{equation*}
-  \KissingTriangles \,,
+   \NMCutC \,,
 \end{equation*}
@@
 ansatz with Jacobi relations and symmetries applied.
-
 \begin{figure}
-  \foreach \x in {1,...,8}
-  {
-    \begin{minipage}{0.32\textwidth}
-      \includegraphics[width=\textwidth]{temp-figs/nonpath-nmc-\x.pdf}
-    \end{minipage}
-  }
-  \caption{The 8 non-pathological next-to-maximal-cut diagrams.
-    \ace{Note that Mathematica drew the bottom-left diagram with two
-      legs stacked on top of each other which eventually meet in a
-      3pt.  One leg is on the ``bottom level'' and connects with a 3pt
-      to the two legs coming off to the side, and the other is on the
-      ``top level'' and connects to the 4pt.}}
+\centering
+ { \NMCutH, \NMCutG,  \NMCutD,\NMCutB, 
+ \\
+ \NMCutE, \NMCutF, \NMCutA, \NMCutC,  }
+  \caption{The 8 non-pathological next-to-maximal-cut diagrams.}
   \label{fig:ym-nmc}
@@
 \begin{equation}
-  \KissingTriangles
+   \NMCutC
   =
@@
 \begin{equation}
-  \KissingTriangles
+   \NMCutC
   \Rightarrow
@@
 
-\section{All-loop no-go theorem}
+\section{Conclusions and Outlook}
+\subsection{All-loop No-Go Theorem}
 This could be a section about our expectations for all-loop construction requiring non-local color-dual integrands. Lay out counterfactual proof, i,e. define the following statement:
@@
 Thus, if a color-dual representation exists at all-loop order for Yang-Mills it must be a rational function of kinematics.
-
-\section{Discussion}\label{sec:Discussion}
+\subsection{Future Directions}\label{sec:Discussion}
 \paragraph{Acknowledgments} The authors would like to thank ...

### 2023-09-11 notes/2loopNLSM.tex
Added some references

@@
 Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing.
-The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \citepls{}.
+The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \cite{Zakharov:1973pp, Cheung:2022mix}.
 We will briefly review the perturbative construction of this theory below.
@@
 \ee
-While introducing succesively higher spiin states to the NMHV lagrangian constructed in \citepls{} could in principle work at tree level, we will see that it is not consiisntent with what we find at general loop order.
+While introducing succesively higher spin states to the NMHV Lagrangian constructed in \cite{Ben-Shahar:2022ixa} could in principle work at tree level, we will see that it is not consistent with what we find at general loop order.
 We will comment on this in \sect{}.
 For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.
-This is easily understood in terms of a polarization decomposition introduced by one of the authors \citepls{} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations.
+This is easily understood in terms of a polarization decomposition introduced by one of the authors \cite{Pavao:2022kog} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations.
 \subsection{Block Decomposition of Yang-Mills}
@@
 Start with reducible amplitude block decomp from Ref.
-\citepls{}:
+\cite{Pavao:2022kog}:
 \begin{eBox}
@@
 One hope would be to factor out some piece of the 1-loop numerator since this at least manifests antisymmetry for the vertices involving external legs.
-However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov theory \citepls{Original ZM paper, ZM CK paper}.
+However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov theory \cite{Zakharov:1973pp, Cheung:2022mix}.
 
@@
 Since ZM theory is only being used for the kinematical structure of its numerators, it is natural to introduce a proportionality constant $z$ between the NLSM and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.
-The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically \citepls{Nappi}.}
+The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically \cite{Nappi:1979ig}.}
 This introduces an extra degree of freedom into the problem.
@@
 additionally acknowledges the Northwestern University Amplitudes and Insight group, the Department of Physics and Astronomy, and Weinberg College for their generous support.
-
-Figures made with TikZ-Feynman [1601.05437]
+Feynman diagrams were typeset using TikZ-Feynman \cite{Ellis:2016jkw}.
 

### 2023-09-11 notes/2loopNLSM.tex
Corrected a power counting statment

@@
 color-dual integrands for pure YM have been investigated before but
-only for a limited ansatz that manifests locality (cite Zvi et al
-paper).  All of the N=4 SYM constructions below 5-loop are local.
+only for a limited ansatz that manifests locality \cite{Bern:2015ooa}.  All of the N=4 SYM constructions below 5-loop are local.
 Mention generalized double copy.
@@
 This means that even at two loops, unitarity is still only probing the on-shell 4pt NLSM amplitude.
-The other cuts besides (b) and (c) are either pathological or vanish because they involve a 3pt point on-shell amplitude (which vanishes in any scalar theory).
+The other cuts besides (b) and (c) are either pathological or vanish because they involve a 3pt point on-shell amplitude (which vanishes on general grounds for scalar theories).
 In order to manifest the $\mathbb{Z}_2$ symmetry of NLSM at the integrand level, we enforce that all non-pathological cuts containing a 3pt vertex (such as the maximal cut) vanish.
@@
 \be
-\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8.
-\ee
-In other words, every term contains between 5 and 8 powers of loop momenta, as one would expect from a set of local, cubic Feynman rules.
-\jm{I believe this is true but I need to check it.}
-When the pion numerator is also forced to have this loop power counting, the number of generalized gauge freedom parameters reduces to 58.
+\label{eq:ZMLoopPowCount}
+\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
+\ee
+whereas a generic set of local, cubic Feynman rules could have produced terms with up to $m+n=12$ powers of loop momenta.
+When the pion numerator is forced to have the loop power counting structure in \cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge freedom parameters reduces to 58.
 The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4pt pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \epsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}

### 2023-09-12 notes/2loopNLSM.tex
Update 2loopNLSM.tex

--- 2023-09-11 notes/2loopNLSM.tex
@@
 \be
-\stackrel{\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}}{\text{Fundamental}}\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
+\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
 \ee
@@
   to properly define the kinematic Jacobi relations.
-\item  \textbf{Relabeling}: The diagram numerators are only a function of the
-  diagram's topology and labeling.
-\item  \textbf{Symmetries}: The diagram numerators are invariant under the
+\item  \textbf{Symmetries}: The diagram numerators are only a function of the
+  diagram's topology and labeling. The diagram numerators are invariant under the
   automorphisms of the diagrams \emph{including signs that compensate
@@
 Here we'll describe the why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
-It has to do with out the vector state sum mixes with the four-point contact.
-In terms of our previously defined Feynman rules, the three-point YM vertex takes the form:
+It has to do with how the vector state sum mixes with the four-point contact.
+
+This is most easily seen by decomposing the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
+\be \label{YMSvert}
+\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = (\varepsilon_1\varepsilon_2)(\varepsilon_3 k_1)
+\ee
+With this, the full vector interaction can be expressed as a sum over cyclic permutations:
 \be
@@
  \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
+\ee
+where we have defined a new oriented vertex in terms of our scalar-vector building block of \ref{YMSvert},
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} = \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} +\cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed}\,.
 \ee
@@
 \subsection{Semi-abelian Yang-Mills theory}
+\begin{eBox}
+\be
+\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
+\ee
+\end{eBox}
+where,
+\be
+\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
+\ee
+\be
+F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a
+\ee
 \subsection{One-loop color-dual integrands}
@@
 \label{sec:CKLagrangians}
-In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual.
-As we will show, taking forward limits of tree-level numerators works as long as one can construct an off-shell description with a Lagrangian.
-Here we briefly review the off-shell examples of the kinematic algebra that will be relevant in this paper.
-\be
-\mathcal{L}^{\text{semi-YM}} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} - \frac{g}{2} G_{\mu\nu} [A_\mu, A_\nu]
-\ee
-\jm{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
 \paragraph{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
@@
 \section{Spinor-helicity and conventions}
-Dimensions will generically be away from four, in $D=4-2\epsilon$, with $\epsilon$ arbitrary.
-As noted, it will be convenient to take $D\rightarrow 4$ in certain circumstances after integration.
-In such cases we will employ appropriate spinor-helicity variables.
-Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now.
-For massless momenta, $k_a$ and $k_b$, we have
+Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. For massless momenta, $k_a$ and $k_b$, we have 
 \begin{equation}
@@
 Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
+
 \section{Notes to self -- James}
+\jm{Notes to self -- James}
 \begin{itemize}

### 2023-09-12 notes/2loopNLSM.tex
Edited color dual boostrap section

@@
 \label{sec:bootstrap}
-Some background here on how we approach color-dual bootstrap (as we will utilize in our two-loop construction). Building an ansatz from irreducible lorentz products (ISPs). Comments about:
-\begin{itemize}
-\item loop momenta weight counting 
-\item polynomial vector spaces 
-\item generalized gauge freedom
-\item functional jacobi constraints and cuts
-\end{itemize}
-
-As part of attemtping to construct a color-kinematics dual
-representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
-Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
-assumptions in searching for double-copyable integrand numerators (ordered according to the
-reference):
+
+Aside from a few special theories \citepls{}, color-dual integrands are constructed from an ansatz.
+The four conditions imposed on the ansatz are summarized here and elaborated on below.
 \begin{enumerate}
@@
   propagators of the diagrams.
-\item  \textbf{Power-counting:} The maximum power of the loop momenta in the
-  numerator is bounded by Feynman-gauge Feynman rules.
-\item  \textbf{Cubic diagrams}: The only diagrams with nonzero numerators are
-  those with strictly cubic vertices.  This is generally a requirement
-  to properly define the kinematic Jacobi relations.
-\item  \textbf{Symmetries}: The diagram numerators are only a function of the
-  diagram's topology and labeling. The diagram numerators are invariant under the
-  automorphisms of the diagrams \emph{including signs that compensate
-    for color-factor sign changes}.
-\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the
-  physical unitarity cuts of the theory.
-\item  \textbf{Color-kinematics duality}: The numerators obey some form of the
-  kinematic Jacobi relations.
+  \item  \textbf{Color-kinematics duality}: The numerators obey the same Jacobi identities as the color factors.
+This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
+\item  \textbf{Graph symmetries}: The diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
+The diagram numerators are only a function of the diagram's topology and labeling.
+\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory.
 \end{enumerate}
-Point 1 is generally a matter of convenience: there are many examples
-in which ``numerators'' with controlled rational contributions have
-been found
-\cite{Square,WeinzierlBCJLagrangian,Mogull:2015adi,FivePointN4BCJ,Johansson:2017bfl}.
-However, without a guiding principle about what types of rational
-terms to use, the size of ans\"{a}tze quickly get out of hand.  Point
-2 was motivated at the time by the hope that color-dual numerators
-could arise naturally out of a special gauge choice. \jm{I'm not sure
-  that we should bring up point 2.  I don't follow it and I don't
-  think Alex did either since this wouldn't be the most general
-  ansatz.  Also, why doesn't point 5 cover point 4?}\ace{I paraphrased
-  these out of \cite{Bern:2015ooa}, thus the inclusion of Point 2.
-  For Points 4 and 5, definitely 4 $\not \Rightarrow$ 5.  In the other
-  direction, I could imagine a situation in which we violate 4 (eg we
-  need to specify a reference ordering) but that symmetries are still
-  respected as long as you also perform the correct actions on the
-  auxiliary data.} On the other hand, recent work by Ben-Shahar,
-Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
-  good examples?}  demonstrates that constructing Feynman rules which
-produce manifestly color-dual numerators for the NMHV sector of
-Yang--Mills requires introducing additional auxiliary fields,
-including higher-spin modes, which could shift the expected power
-counting in non-trivial ways.  Point 3 is a requirement of the BCJ
-double-copy: currently there is no known way of incorporating
-non-cubic diagrams into the kinematic Jacobi relations.  Points 4 and
-5 will be elaborated on in \cref{sec:syms}, Point 6 in
-\cref{sec:unitarity}, and Point 7 in \cref{sec:jac-rels}.
-
-References for Jacobi, unitarity, etc.
-
-Aside from the few special theories mentioned in \cref{sec:CKLagrangians}, color-dual integrands are constructed from an ansatz.
+
+\paragraph{Locality}
+
+The kinematic numerators need to be $D$-dimensional, Lorentz invariant, local (polynomial) functions of the graph kinematics with the correct power counting and external states.
+Insisting on a local numerator is partly a matter of convenience as the ansatz for a rational function would quickly grow out of control without a guiding principle for what terms to include.
+Locality is also physically motivated since Feynman rules typically produce polynomial numerators.
+While locality is well motivated from a physical and computational standpoint, the literature has featured numerators that violate locality, break manifest Lorentz invariance, and modify naive power counting through the presence of higher spin modes \cite{Square, WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv, Cheung:2021zvb}.
+\jm{Alex wrote some of this citation.
+I'm not sure why it broke.}
+These developments suggest that relaxing locality is a viable option when the condition proves too stringent for an ansatz.
+We will comment more on locality in \sect{}.
+
+\paragraph{Color-kinematics duality}
+
+Somewhere emphasize that Zvi et al didn't do the most general ansatz, imposed extra loop power counting constraints.
 
@@
 to finding color-dual numerators is to relax manifest locality, see
-(...) for more details.  After zeroth order considerations like power
-counting, there are three conditions that are imposed on the ansatz:
-(1) Jacobi relations amongst graphs must be satisfied, (2) numerators
-must respect graph symmetries, and (3) the integrand must have the
-correct unitarity cuts.
-
-(These three constraints can be solved in any order and my guess is that Alex and I did solve them in different orders.)
-
-\paragraph{Jacobi relations}
-\label{sec:jac-rels}
+(...) for more details.
 
@@
 \paragraph{Graph symmetries}
-\label{sec:syms}
+
+Want explicit Bose sym, broken in many cases.
 
@@
 \paragraph{Unitarity}
-\label{sec:unitarity}
+
 The last key source of constraints comes from ensuring that the ansatz

### 2023-09-13 notes/2loopNLSM.tex
Finished CK boostrap 2nd pass

@@
 \newcommand{\forr}{\ , \quad \text{for}  \quad}
+\newcommand{\ansatze}{ans\"atze} %Because words are hard
 
 %TODO-type commands
-\newcommand{\citepls}[1]{{\bf\color{red}[[Cite Needed:#1]]}}
+\newcommand{\citepls}[1]{{\bf\color{red}[[Cite Needed: #1]]}}
 \newcommand{\sect}{\textbf{\textcolor{red}{RefSec}}}
@@
 Aside from a few special theories \citepls{}, color-dual integrands are constructed from an ansatz.
-The four conditions imposed on the ansatz are summarized here and elaborated on below.
+The four conditions we impose on an ansatz are summarized here and elaborated on below.\footnote{The four ansatz conditions are similar to those of Ref.~\cite{Bern:2015ooa} except that the authors demand that the numerators have the same loop power counting as Feynman gauge Feynman rules.
+This is an additional assumption that is most emphatically not made here.}
 \begin{enumerate}
-\item \textbf{Locality}: Diagram ``numerators'' are polynomials in momenta and
+\item \textbf{Locality}: Diagram numerators are polynomials in momenta and
   polarizations, \eg the diagrams only have poles given by the
@@
 This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
-\item  \textbf{Graph symmetries}: The diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
-The diagram numerators are only a function of the diagram's topology and labeling.
+\item  \textbf{Graph symmetries}: The diagram numerators are only a function of the diagram's topology and labeling.
+Furthermore, the diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
 \item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory.
@@
 
+In order to clarify general statements, the following subsections include examples from a 4pt 2-loop integrand for some color-dual theory like YM or NLSM.
+This is the simplest integrand that demonstrates the full machinery of the color-dual bootstrap.
+All tree and 1-loop processes are generated by single basis diagrams (the half ladder and $n$-gon respectively) so they lack examples of the ``boundary'' Jacobi relations to be described shortly.
+Choosing the 4pt 2-loop integrand also has the advantage that this process appears prominently in this paper.
+
 \paragraph{Locality}
 
-The kinematic numerators need to be $D$-dimensional, Lorentz invariant, local (polynomial) functions of the graph kinematics with the correct power counting and external states.
+The kinematic numerators must be $D$-dimensional, Lorentz invariant, local (polynomial) functions of the graph kinematics with the correct power counting and external states.
 Insisting on a local numerator is partly a matter of convenience as the ansatz for a rational function would quickly grow out of control without a guiding principle for what terms to include.
 Locality is also physically motivated since Feynman rules typically produce polynomial numerators.
-While locality is well motivated from a physical and computational standpoint, the literature has featured numerators that violate locality, break manifest Lorentz invariance, and modify naive power counting through the presence of higher spin modes \cite{Square, WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv, Cheung:2021zvb}.
-\jm{Alex wrote some of this citation.
-I'm not sure why it broke.}
-These developments suggest that relaxing locality is a viable option when the condition proves too stringent for an ansatz.
+While these assumptions are well motivated from a physical and complexity standpoint, the literature has featured numerators that violate locality, modify naive power counting through the inclusion of higher spin modes, and break manifest Lorentz invariance \cite{Square, WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv, Cheung:2021zvb}.
+These developments suggest that relaxing locality is a viable alternative when the condition proves too stringent for an ansatz.
 We will comment more on locality in \sect{}.
 
+\jm{The next section feels a little redundant and silly sometimes because the integrand, color factors, kinematic numerators, etc.
+were defined a while ago.
+I'm not sure how to merge the two sections though.}
+
 \paragraph{Color-kinematics duality}
 
-Somewhere emphasize that Zvi et al didn't do the most general ansatz, imposed extra loop power counting constraints.
-
-Different kinds of CK.  We want global.  Global is the simplest
-option, it is also the option that you would automatically get if you
-had a color-dual Lagrangian.  By ``global'' we mean that
-color-kinematics duality is satisfied in any kinematic configuration
-of the integrand.  This is a much more stringent condition than
-absolutely necessary.  There is reason to believe \cite{Bern:2015ooa} that global numerators cannot
-always be found.  One resolution to the issue is to only demand
-color-kinematics duality on the unitarity cuts of the integrand, i.e.,
-in specific kinematic limits.  Enforcing Jacobi on the cuts is enough
-to ensure that the squared integrand will correctly cut to gravity (or
-whatever the squared theory might be).  When a globally color-dual
-numerator cannot be found, another alternative explored in the
-literature is to increase the size of the numerator ansatz by
-enlarging the numerator from a polynomial to a rational function with
-spurious singularities (cite Donal et al).  When global
-color-kinematics fails, the hope is that it can be restored by
-enlarging the size of the ansatz, either by giving the numerator of
-each graph its own ansatz (first option described) or by promoting the
-numerator to a non-local function (second option described).  Note
-that a theory whose Lagrangian has color-kinematics duality would
-naturally produce a globally color-dual integrand so the quest for a
-global numerator is closely related to the existence of a Lagrangian
-exhibiting color-kinematics duality.  Section X is devoted to
-color-dual representations of the 4pt 2-loop NLSM integrand and the
-analogous integrand for YM is treated in section Y.  Two-loop
-color-dual integrands for pure YM have been investigated before but
-only for a limited ansatz that manifests locality \cite{Bern:2015ooa}.  All of the N=4 SYM constructions below 5-loop are local.
-Mention generalized double copy.
-
-Color-kinematics duality is stated in terms of cubic graphs so the
-first step is to express in the integrand in terms of such graphs.  As
-an example we will focus on the 4pt 2-loop integrand of some
-color-dual theory like NLSM or YM.  The 4pt 1-loop integrand is not a
-sufficiently illustrative example because, for instance, it lacks any
-self Jacobi like \cref{eq:TwoLoopJacobiTwo} to be discussed shortly.
-Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and
-bubble on external leg (BEL) graphs.  It is always possible to express
-an integrand in terms of cubic graphs, even for an even valency theory
-like NLSM, by multiplying and dividing the integrand by factors of
-inverse propagators.  Next, the ansatz must have the correct power
-counting and external states, \emph{e.g.}, polarization vectors for
-YM.  The numerator is assumed to be manifestly local but one approach
-to finding color-dual numerators is to relax manifest locality, see
-(...) for more details.
-
-Jacobi relations are the heart of color-kinematics duality.
+Color-kinematics duality is a statement about color factors, kinematic numerators, and the accompanying Jacobi relations.
+Adjoint-type color factors are associated with cubic graphs, so satisfying color-kinematics duality implicitly requires expressing the integrand in terms of such graphs.
+As mentioned earlier, this is possible to do even for a theory with quartic (or higher multiplicity) vertices by multiplying and dividing by propagators.
+In the case of the 4pt 2-loop example promised above, there are 14 cubic graph topologies (shown in Fig \sect{}) ignoring tadpoles and bubble on external leg (BEL) graphs.
+
+With the integrand expressed in terms of cubic graphs, it is possible to discuss the main ingredient in color-kinematics duality -- the Jacobi relations.
 The color factors in an integrand obey a set of Jacobi identities.
-Color-kinematics duality states that there exists a way of writing the kinematic numerators of the integrand so that they obey the same set of Jacobi identities.
-(Can trivially read off the adjoint color factors from a cubic graph.)
-If any triplet of graphs is related by a Jacobi identity, so too must their numerators.
-Broadly speaking there are two kinds of Jacobi identities:  \emph{defining} relations and \emph{boundary} relations.
+Color-kinematics duality states that there \emph{exists} a way of writing the kinematic numerators of the integrand so that they obey the same set of Jacobi identities.
+The Jacobi identities can be divided into two categories:  \emph{defining} relations and \emph{boundary} relations.
 Defining Jacobi relations can be used to express any graph in terms of a basis.
@@
 \label{eq:TwoLoopJacobiOne}
-\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0.
+\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0,
 \ee
@@
 (Any two of the double box, crossed box, and penta-triangle would suffice for a basis but the planar basis is chosen for simplicity in this work.)
-For global color-kinematics duality each of the two basis graphs receives its own numerator ansatz and the numerator of any other graph can be expressed in terms of these.
-
-After using the defining Jacobi relations to relate any graph to the basis, we will refer to any remaining Jacobi relations as boundary relations.
+The numerator of each of the two basis graphs receives its own ansatz and the numerator of any other graph can be expressed in terms of these two.
+
+After using the defining Jacobi relations to relate every graph to the basis, any remaining Jacobi relations will be referred to as boundary relations.
 In other words, boundary relations (indirectly) relate basis elements to themselves.
@@
 where the shared propagator is shown in red as before.
-Each of the crossed box numerators can be represented in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator ansatze.
-While defining Jacobi relations simplify how many numerators require ansatze, boundary relations place restrictions on those ansatze.
+Each of the crossed box numerators can be written in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator \ansatze{}.
+While defining Jacobi relations simplify how many numerators require \ansatze{}, boundary relations place restrictions on those \ansatze{}.
 In principle there could be Jacobi relations involving tadpoles and BEL graphs, which would be subtle to handle.
@@
 These graphs are allowed to have non-zero numerators but any Jacobi relations involving them are simply not imposed or solved.
-See (4 loop N=4 paper) for a discussion of BELs in the context of color-kinematics duality.
+See Ref.~\cite{Bern:2012uf} for a discussion of BELs in the context of color-kinematics duality.
+
+What has just been described is sometimes referred to as ``global'' color-kinematics duality because the Jacobi identities are solved by a single (global) integrand with off-shell internal lines.
+In order to perform the double copy it is enough to simply satisfy the Jacobi identities on the generalized unitarity cuts, meaning that each graph can be assigned its own ansatz \cite{Bern:2015ooa}.
+If a global solution cannot be found, this is one way to enlarge the ansatz where the other option described above was to incorporate non-local terms in the ``numerators''.
+A globally color-dual integrand is desirable because of its simplicity and because a color-dual Lagrangian would naively produce precisely this object.
 
@@
 
-Want explicit Bose sym, broken in many cases.
-
-The second key constraint in an ansatz construction of color-dual numerators comes from graph symmetries.
 Every numerator is required to respect all of the symmetries (or automorphisms) of its associated graph.
-While it is very convenient to impose graph symmetries, it is not completely necessary in order to perform the double copy.
-At tree level, finding manifestly color-dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
-Nonetheless, for a pure ansatz construction it is very reasonable to impose graph symmetries.
-Note that the graph symmetry constraint is imposed on \emph{every} graph, not just the basis graphs.
+Graph symmetries are an avatar of Bose symmetry.
+For a pure ansatz construction it is very reasonable to impose graph symmetries, but color-kinematics duality at tree-level is often achieved at the expense of manifest Bose symmetry \cite{Cheung:2016prv, Cheung:2021zvb, Brandhuber:2021bsf} \citepls{Alex numerators from CHY}.
+In an ansatz construction graph symmetries are imposed for \emph{every} graph, not just the basis graphs.
 %For example, the symmetries of the crossed box are spanned by
@@
 are spanned by $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
-In general, internal edge labels will have to be tracked as well.
-Care must be taken with the signs in a symmetry relation.
-To compensate for the antisymmetric structure of $f^{abc}$, the vertices are all totally antisymmetric and hence have signs built into their orientations.
+In general, internal edge labels must be tracked as well.
+Furthermore, care must be taken with the signs in a symmetry relation.
+To compensate for the antisymmetric color factors, $f^{abc}$, graph vertices are all totally antisymmetric and hence have signs built into their orientations.
 Once the signs are included in the symmetry relations, the crossed box can be expressed in terms of the double box and penta-triangle, thus imposing non-trivial constraints on the ansatz.
@@
 
-The last key source of constraints comes from ensuring that the ansatz
-correctly reproduces the generalized unitarity cuts of the theory.
-Matching the unitarity cuts provides the vast majority of
-theory-dependent information for the ansatz by ensuring that the
-numerators under construction are actually a valid representation of
-the theory being considered.  Generalized unitarity methods has been
-reviewed in many places \cite{BCFUnitarity, BernHuangReview,
-  Bern:2015ooa, Bourjaily:2017wjl, JJHenrikReview, FivePointN4BCJ,
-  Bern:2012uf, BCJreview, Edison:2022jln} \ace{Here is a semi-random
-  collection of unitarity-related citations.  Probably want to bulk it
-  up a bit more} so we will be light on details here. We also want to
-call special attention to Ref.~\cite{Carrasco:2023qgz} for a recent
-treatment of unitarity methods optimized for even multiplicity
-theories like NLSM.
-
-In the context of loop integrand construction, generalized unitarity
-allows us to equate products of on-shell tree amplitudes, encoded via
+The final constraints comes from ensuring that the ansatz correctly reproduces the generalized unitarity cuts of the desired theory, thus guaranteeing that the numerators encode the correct physical, theory-dependent information.
+Generalized unitarity methods has been reviewed in many places so we will be light on details here \cite{BCFUnitarity, BernHuangReview, Bern:2015ooa, Bourjaily:2017wjl, JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview, Edison:2022jln}.
+\ace{Here is a semi-random collection of unitarity-related citations.  Probably want to bulk it up a bit more.}
+Recently, generalized unitarity was optimized for even-multiplicity theories like NLSM \cite{Carrasco:2023qgz}.
+
+Generalized unitarity equates products of on-shell tree amplitudes, encoded via
 a graph $\gamma$, to sums over compatible\footnote{A diagram $g$ is compatible with the
@@
 Refs.~\cite{Kosmopoulos:2020pcd,Edison:2022jln} for recent discussion
-and detailed examples of evaluating state sums).  It is useful to
-provide some examples of the two types of expressions appearing in
-\cref{eq:SchematicCutEquation}.  First the so-called
-iterated unitarity cut, which can be written in the product-of-trees
-representation as
+and detailed examples of evaluating state sums).
+As an example of the two types of expressions appearing in \cref{eq:SchematicCutEquation}, consider the so-called iterated two-particle cut which can be represented as a product of trees via
 \begin{equation}
@@
   \ExCutLabeled{1}{2}{3}{4} = \!\!\!\!\! \sum_{\substack{\text{states of }\\ \{\ell_1, \ell_2, \ell_3, \ell_4\}}} \!\!\!\!\!\!\!
-  \atree(1,2,\ell_1,\ell_2) \atree(-\ell_1,-\ell_2,\ell_3,\ell_4) \atree(-\ell_3,-\ell_4,3,4) \,,
+  \atree(1,2,\ell_1,\ell_2) \atree(-\ell_1,-\ell_2,\ell_3,\ell_4) \atree(-\ell_3,-\ell_4,3,4)
 \end{equation}
-or in reference to a collection of diagram numerators as
+or as a collection of diagram numerators via
 \begin{align}
@@
 the cut $\delta(\ell^2)$s implicit.
+\jm{Again, I love the colors!  Would it be possible to add $\ell$ labels to the RHS of \cref{eq:example-cut-sum} to show what $\ell_5$, $\ell_6$... are?}
 
@@
 needs to evaluate that many separate color-orderings of the same cut.
-As an example, consider the ``kissing triangle'' cut topology, one of
-the factorization channels of the iterated unitarity cut, which has
+\jm{Don't you need $(n-2)!$ for each blob in the cut?
+So you need to evaluate $(n_1-2)!
+(n_2-2)!...$ cuts where $n_1$, $n_2$...
+are the multiplicities of the blobs.}
+As an example, consider the ``kissing triangle'' cut topology -- one of
+the factorization channels of the iterated unitarity cut -- which has
 two topologically distinct color-ordered expansions
@@
 
-Even beginning at one loop, we encounter classes of cuts that are
+Even though unitarity methods aim to generate loop-level data from well-defined on-shell information, the procedure can encounter subtleties.
+Beginning at one loop, there are classes of cuts that are
 difficult to properly define due to hidden non-physical singularities.
@@
 in which one of the \textcolor{ucp-color}{uncut propagators} is set
-equal to an \textcolor{cut-color}{external on-shell propagator}.
+equal to an \textcolor{cut-color}{external on-shell propagator}. \jm{I think the blue line might extend too far to the left in the picture.}
 Discussions about how to resolve these types of singularities can be
@@
 current work, so we will simply not impose any constraints that
-require handling these type of cuts.
+require handling these types of cuts.
 
@@
 
-After imposing all of the conditions above, any remaining free
+After imposing all four of the conditions above, any remaining free
 parameters represent ``generalized gauge freedom'' meaning that the
@@
 \subsection{Two-loop Yang-Mills revisited}
+
+Two-loop color-dual integrands for non-supersymmetric YM have been investigated before but only for a limited ansatz that manifests locality \cite{Bern:2015ooa}.
+
 Given the close ties between pion and gluon scattering for trees and
@@
 of the double-box and penta-triangle numerators, in addition to the
-standard local ansatze.  In order to not over-count the local terms,
-we restrict the non-local ansatze to only truly rational terms, \eg
+standard local \ansatze{}.  In order to not over-count the local terms,
+we restrict the non-local \ansatze{} to only truly rational terms, \eg
 for the term $n_{\text{nl}}\sim \frac{x}{s}$ we drop all terms with
@@
 \begin{itemize}
+\item This paper kills all ``simple'' color-dual, loop-level Lagrangians for YM but it remains possible that one exists for NLSM.
 \item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)

### 2023-09-18 notes/2loopNLSM.tex
need to write intro -- here's everything else

@@
 \def\mystrut{\rule[-2ex]{0ex}{6ex}}
+
+\usepackage{tikz-feynman}
+
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\usetikzlibrary{external}  
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\tikzexternalize[                     %% Activate externalization
+ prefix=images/,                    %% Avoid cluttering the directory
+ system call={                       %% Use lualatex in system call
+    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
+ },
+]
 
@@
 \section{Background}
- To set the stage, it is worth distinguishing between the algebraic properties of functionally symmetric kinematics that satisfy color-kinematics globally, and some of the other constructions that appear in the literature.
-
-In this work, we will consider three different types of cubic representations, that we define below: 
-\be
-\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
-\ee
-In this review, we will present examples of this distinct kinematic representations that have appeared in the literature.
-Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing.
-The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \cite{Zakharov:1973pp, Cheung:2022mix}.
-We will briefly review the perturbative construction of this theory below.
-
+To set the stage, in this section we will provide an overview of color-kinematics duality -- both the on-shell and off-shell construction.
+We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM.
 \subsection{Color-dual Amplitudes}
@@
 
-Color-kinematics duality is a statement about amplitude integrands.
+Color-kinematics duality is a statement about the off-shell graphical simplicity that manifest redundancy in the on-shell observables of gauge and gravity theories.
 Ignoring factors of $i$ and the coupling constant, a generic $m$-point $L$-loop amplitude in a color-dual theory -- such as NLSM, YM, or bi-adjoint scalar theory -- can be written as
@@
 The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.
-However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu} \jm{I cited DF$^2$ and fundamental fermions.
+However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu} ref[Ingrid+JJ, Aslan+JJ] \jm{I cited DF$^2$ and fundamental fermions.
 Is there anything else anyone wants to mention?}.}
@@
 Once color-dual numerators $n_\Gamma$ have been found, they can be used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a \emph{different} amplitude to produce the corresponding amplitude in the double-copy theory
-\be
+\be\label{DCconstruction}
 \tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)} ~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma \tilde{n}_\Gamma}{d_\Gamma}.
@@
 \subsection{Color-dual Lagrangians}
-
-BCJ loves $\mathcal{L} = \bar{F} F$.
-How this connects to SDYM, NLSM.
-You can do tree and 1-loop.
-Why the bowtie is so important.
-
+While BCJ relations is an on-shell statement about the color-dual nature of scattering amplitudes, one might aspire to hard code color-kinematics duality by realizing an off-shell Lagrangian description of the theory.
+The double-copy construction of \ref{DCconstruction} would suggest a manifestly cubic Lagrangian of the form:
+\be
+\mathcal{L} = P_V^{ab}P_W^{ij}\mathcal{O}^a_i \Box \mathcal{O}^b_j +  V^{abc} W^{ijk}\mathcal{O}^a_i \mathcal{O}^b_j \mathcal{O}^c_k
+\ee
+where $V^{abc}$ and $W^{ijk}$ are cubic Feynman rules mixing field operators $\mathcal{O}^{a}_i$ indexed by quantum numbers $a$ and $i$.
+We have introduced $P_V^{ab}$ and $P_W^{ij}$ projection operators to encode non-local kinetic structure that could in principle participate in the construction.
+Should the off-shell Feynman rules of this cubic theory be antisymmetric and satisfy Jacobi identities on all internal edges,
+\begin{align}
+\textit{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0\,,
+\\
+\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\,,
+\end{align}
+where 
+\be
+{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}V^{b_1a_3b_2}\cdots V^{b_{n-3} a_{n-2}a_n}\,.
+\ee
+This is a sufficient condition of the amplitudes to obey BCJ relations.
+Off-shell desciription of color-dual theories are rare, and only a few examples are available in the literature.
+Typically when one goes about construction color-dual theories directly from a set of cubic interactions, higher point Jacobi and antisymmetry constraints require introducing additional operators.
+See refs \cite{} for some recent examples.
+Indeed, as we'll show in \ref{cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point.
+Absent information about the kinematic algebra, one can make progress in the construction of loop-level color-dual amplitudes by employing a color-dual bootstrap.
 \subsection{Color-dual Bootstrap}
@@
 
-Aside from a few special theories \citepls{}, color-dual integrands are constructed from an ansatz.
+Aside from a few special theories that permit an off-shell Lagrangian description \citepls{}, color-dual integrands are constructed from an ansatz.
 The four conditions we impose on an ansatz are summarized here and elaborated on below.\footnote{The four ansatz conditions are similar to those of Ref.~\cite{Bern:2015ooa} except that the authors demand that the numerators have the same loop power counting as Feynman gauge Feynman rules.
@@
 
-\section{One-loop cubic construction}
-Here we'll describe the why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
+\section{One-loop cubic construction} \label{cubic}
+Here we'll describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
 It has to do with how the vector state sum mixes with the four-point contact.
-
-This is most easily seen by decomposing the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
-\be \label{YMSvert}
-\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = (\varepsilon_1\varepsilon_2)(\varepsilon_3 k_1)
-\ee
-With this, the full vector interaction can be expressed as a sum over cyclic permutations:
-\be
-\cubic{hgrey0}{gluon}{}{gluon}{}{gluon}{}  =  \cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed} + \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} + \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} +\text{h.c.}
-\ee
-The state-sum between two three-point gluon vertex yields the following expansion in terms of YZ-theory vertices:
-\be
- \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
-\ee
-where we have defined a new oriented vertex in terms of our scalar-vector building block of \ref{YMSvert},
-\be
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} = \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} +\cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed}\,.
-\ee
-All the $(\epsilon\epsilon)^1$ diagram permutations are isolated to the cubic sector and together manifest color-kinematics duality.
-However, the exception of the last diagram which introduces a $(\epsilon\epsilon)^2$ factor, must conspire with the Yang-Mills contact to preserve the duality off-shell
-
-\be
-\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed} = (s_{13}-s_{12}) \epsilon_{(12)} \epsilon_{(34)}
-\ee
-One was to resolve this is to introduce higher spin modes in order to accomodate the internal index contractions needed to recover the s-channal contract:
-\be
-\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{Bfield}{nhpRed}{}{nhpRed} = s_{12 }(\epsilon_{(13)} \epsilon_{(24)} - \epsilon_{(14)} \epsilon_{(23)})
-\ee
-While introducing succesively higher spin states to the NMHV Lagrangian constructed in \cite{Ben-Shahar:2022ixa} could in principle work at tree level, we will see that it is not consistent with what we find at general loop order.
+Starting with the Yang-Mills Lagrangian,
+\be
+\mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2 + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
+\ee
+We can express the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
+\be
+T^k_{ij} = (\varepsilon_i\varepsilon_j)(\varepsilon_k p_i)
+\ee
+This kinematic generator is anti-symmetric in $1\leftrightarrow 2$ exchange, and from it we can construct the full Lorenz gauge Yang-Mills vertex by summing over cyclic permutations:
+\be
+V^{(123)}_{\text{YM}} = T^3_{12} +\text{cyc}(123)
+\ee
+Contracting this with the vector state sum, we can see that the cubic Yang-Mills vertex does not alone satisfy the four-point Jacobi identity:
+\be\label{cubicJac}
+{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4+\text{cyc}(234) = \varepsilon_{(12)}  \varepsilon_{(34)} (s_{13}-s_{23}) +\text{cyc}(234) \neq 0
+\ee
+where $ \varepsilon_{(ij)} =  \varepsilon_{i}\cdot  \varepsilon_{j}$.
+Of course, it is not hard to see that one can simply absorb the remaining terms into the definition of the four-point kinematic numerators:
+\be
+{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4 = {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4 + s_{12} (\varepsilon_{(13)}\varepsilon_{(24)}-\varepsilon_{(14)}\varepsilon_{(23)})
+\ee
+where $V_{\text{YM}+B}$ indicates the introduction of an additional two-form studied in \cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian. 
+\be
+{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
+\ee
+where the new cubic Lagrangian is of the form:
+\be
+\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 - B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu A^c_\nu
+\ee
+Of course, higher multiplicity would require further redefinition of the three-point vertex to satisfy Jacobi identites on all internal edges.
+While introducing successively higher spin states could in principle work at tree level, we will see that it is not consistent with what we find at general loop order.
 We will comment on this in \sect{}.
 For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.
-This is easily understood in terms of a polarization decomposition introduced by one of the authors \cite{Pavao:2022kog} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations.
+
+As one can see above, the Jacobi identity of \ref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$.
+Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
+\be
+{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0
+\ee
+Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form.
+The organizational principle underlying this construction can be easily understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog}, which we summarize briefly below.
 \subsection{Block Decomposition of Yang-Mills}
-Describe how different orders in $\varepsilon_i\varepsilon_j$ in pure Yang-Mills captures different cubic and contact sectors of the theory.
-All the $D$-dimensional Lagnrangians above can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order.
+The $D$-dimensional Lagrangians of \ref{} can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order.
 Start with reducible amplitude block decomp from Ref.
 \cite{Pavao:2022kog}:
+\begin{equation}\label{eq:pureVecRABD}
+A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+\end{equation}
+By a simple mass-dimensioin argument, we know the tree-level cubic sector must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
+\be
+A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+\ee
+while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products:
+\be
+A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+\ee
+When decomposed in this way, in order for the full amplitude to be gauge invariant, the polarization stripped building blocks, must obey a set of Ward-Identities between different helicity sectors:
+ \begin{equation}\label{eq:GIrelA}
+\Delta_{(\sigma)}^{(\rho)}\Big|_{\epsilon_i\rightarrow k_i} =-
+\sum_{j \in \rho^c} (k_i \varepsilon_j)\Delta_{(\sigma )}^{(\rho\cup (ij))} \,.
+\end{equation}
+With this in hand, we can construct a Lagrangian description of the of the cubic sector for Yang-Mills, and will demonstrate that the resulting amplitudes with manifestly color-dual Feynman rules are equivalent to both SDYM and NLSM through one-loop.
+\subsection{Semi-abelian Yang-Mills theory}
+As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell.
+However, the contrapositive is also true -- if we get rid of the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.
+
+We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G \rightarrow G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$.
+However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$, and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preffered $U(1)$-directions.
+We call this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
 \begin{eBox}
-\begin{equation}\label{eq:pureVecRABD}
-A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
-\end{equation}
+\be
+\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
+\ee
 \end{eBox}
-By a simple mass-dimensioin argument, we know the tree-level cubic sector is simply:
-\be
-A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
-\ee
-and likewise at one-loop:
-\be
-A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
-\ee
-We can select out both of these manifestly cubic sectors by selecting only $\epsilon^+\epsilon^+$ in light-cone gauge (i.e.
+where,
+\be
+\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
+\ee
+\be
+F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
+\ee
+Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents.
+Indeed, as we describe in the Appendix \ref{}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{}, J-theory \cite{}, and self-dual Yang-Mills \cite{}.
+We can use the Ward identity of \ref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant with the abelian polarizations are taken on-shell, $\bar{\varepsilon} \rightarrow k$.
+
+We can select out both of these manifestly cubic sectors by selecting only $\varepsilon^+\varepsilon^+$ in light-cone gauge (i.e.
 SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states.
@@
 \be
-A(...,\bar{J}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
+A(...,\bar{A}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
 \ee
@@
 \be
-A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\epsilon\rightarrow k}
+A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}
 \ee
@@
 We will construct these one-loop integrands below in the next section.
-\subsection{Semi-abelian Yang-Mills theory}
-\begin{eBox}
-\be
-\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
-\ee
-\end{eBox}
-where,
-\be
-\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
-\ee
-\be
-F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a
-\ee
+
 \subsection{One-loop color-dual integrands}
-\be
-\simplebox = g_{\text{YM}}^4 X(k_1,l_1)X(k_2,l_2)X(k_3,l_3)X(k_4,l_4)
-\ee
-\be
-\nGonScalar
+Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM).
+At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{}:
+\be
+X(p,k) = p_u k_w-p_w k_u
+\ee
+At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop.
+This can be done using the cubic semi-YM vertices of the previous section:
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
+\ee
+Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase.
+Of course, this has the advantage of permitting a $D$-dimensional construction of the one-loop integrand.
+Below we provide a four-point example:
+\be
+\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
+\ee
+where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
+\be
+\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
+\ee
+Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$.
+By taking a derivative, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
+\be
 \ee
@@
 \be
-\simplebox = (2 f_\pi^{-1})^4 (l_1 k_1)(l_2 k_2)(l_3 k_3)(l_4 k_4)
-\ee
-where we define sequential loop momenta on the $n$-gon as $l_{i+1}= l_i+k_i$. Given this, the $n$-gon permits a equivalent expression in terms of inverse propagators:
-\be
-\simplebox =f_\pi^{-4} [12][23][34][41]
-\ee
-Where we have define the antisymmetric kinematic variable, $[LR] = l_i^L - l_R^2$
+\nGonScalar \equiv \frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}} = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
+\ee
+This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop.
+For more background, we refer the reader to appendix \ref{}.
+\be
+\left[\nGonScalar\right]_{\epsilon \rightarrow k} =  f_\pi^{-n} [12][23]\cdots [n1]
+\ee
+Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
 \subsection{Two-loop obstruction}
-
+At two-loop, introducing terms that conspire with four-point contacts is unavoidable. Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
 \section{Two-loop bootstrap}
@@
 \label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) .
-\ee
-The color-stripped Feynman rule for the vertex is simply $V(k_1, k_2, k_3) \propto \epsilon_{\mu\nu}k_1^\mu k_2^\nu$ where off-shell color-kinematics duality to all orders in perturbation theory simply follows from the Schouten identity.
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) .
+\ee
+The color-stripped Feynman rule for the vertex is simply $V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where off-shell color-kinematics duality to all orders in perturbation theory simply follows from the Schouten identity.
 Since the theory only has a cubic vertex and the theory has manifest off-shell color-kinematics duality, it is trivial to read off the color-dual numerator for any graph.
-From the presence of the Levi-Civita tensor $\epsilon^{\mu\nu}$, the theory clearly resides in two spacetime dimensions where scattering is notoriously plagued by infrared regulation issues.
+From the presence of the Levi-Civita tensor $\varepsilon^{\mu\nu}$, the theory clearly resides in two spacetime dimensions where scattering is notoriously plagued by infrared regulation issues.
 Every on-shell particle is either a right mover, with momentum proportional to $k_R^\mu \equiv (1,1)$, or a left mover, with momentum proportional to $k_L^\mu \equiv (1,-1)$.
@@
 When the pion numerator is forced to have the loop power counting structure in \cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge freedom parameters reduces to 58.
-The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4pt pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \epsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}
+The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4pt pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}
 
@@
 four external gluon polarizations.  Thus, the ansatz will be built
-from terms of the form
-\begin{align}
-  \pol_1 \cdot k_2, \quad \pol_1 \cdot k_3, \quad& \pol_1 \cdot \ell_1, \quad \pol_1 \cdot \ell_2, \notag \\
-  \pol_2 \cdot k_1, \quad \pol_2 \cdot k_3, \quad& \pol_2 \cdot \ell_1, \quad \pol_2 \cdot \ell_2, \notag \\
-  \pol_3 \cdot k_1, \quad \pol_3 \cdot k_2, \quad& \pol_3 \cdot \ell_1, \quad \pol_3 \cdot \ell_2,  \\
-  \pol_4 \cdot k_1, \quad \pol_4 \cdot k_2, \quad& \pol_4 \cdot \ell_1, \quad \pol_4 \cdot \ell_2, \notag \\
-  \pol_1 \cdot \pol_2, \quad \pol_1 \cdot \pol_3, \quad& \pol_1 \cdot \pol_4, \quad \pol_2 \cdot \pol_3, \notag \\
-  \pol_2 \cdot \pol_4, \quad& \pol_3 \cdot \pol_4  \notag
-\end{align}
+from terms of the form:
+\be
+\mathcal{N}_{\text{2box}},\mathcal{N}_{\text{pt}}\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
+\ee
 in addition to the purely momentum-dependent terms show in
@@
 Thus, if a color-dual representation exists at all-loop order for Yang-Mills it must be a rational function of kinematics.
+
+Much of the complexity for $D$-dimensional vector theories at loop-level arises due to the mixing between external polarization and internal loop momenta.
+One advantage of expanding ansatz construction towards functions of rational kinematics is the prospect of stripping out overall factors of gauge invariant tensors.
+For example, consider the simple four-point example of a color-dual representation of Yang-Mills theory.
+\be
+\mathcal{N}_{(12|34)}^{\text{YM}} = \frac{1}{3}\left[\frac{t_8F^4}{s_{23}} -  \frac{t_8F^4}{s_{13}}\right]
+\ee
+\be
+\mathcal{N}_{(12|34)}^{\text{YM}} + \mathcal{N}_{(13|42)}^{\text{YM}} +\mathcal{N}_{(14|23)}^{\text{YM}} = 0
+\ee
+\be
+\text{Res}\left[\frac{c_s \mathcal{N}_{s}^{\text{YM}} }{s}\right]^{s=0}= \frac{2}{3} \frac{t_8F^4}{t} \qquad 
+\text{Res}\left[\frac{\mathcal{N}_{t}^{\text{YM}} }{t}\right]^{s=0}= \frac{1}{3} \frac{t_8F^4}{t}
+\ee
+\be
+A^{\text{YM}}_{(1234)} = \frac{t_8F^4}{s_{12}s_{23}}
+\ee
 \subsection{Future Directions}\label{sec:Discussion}
@@
 \be\label{SDcon}
-F_{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
+F_{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
 \ee
@@
 \be
-D^\mu F^{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
+D^\mu F^{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
 \ee
@@
 \be
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =\mathcal{X}(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
 \ee
@@
 \ee
-where $p_{ab}=p_a+p_b$ and $\epsilon$ and $\bar{\epsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
+where $p_{ab}=p_a+p_b$ and $\varepsilon$ and $\bar{\varepsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
 The on-shell state sum for the polarization vectors is simply:
@@
 While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
-Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
+Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \varepsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
 After plugging $\varphi$ into \cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
@@
 \label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
 \ee
@@
 \be
-\langle ab\rangle \equiv p_a^\mu \epsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
+\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
 \ee
@@
 \ee
-by virtue of the 2D Levi-Civita identity $\epsilon_{\mu\nu}\epsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
+by virtue of the 2D Levi-Civita identity $\varepsilon_{\mu\nu}\varepsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
 Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.
@@
 \item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.
-So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\epsilon$ identities.
-Make an ansatz where you do every pairing of $\epsilon$'s.
+So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\varepsilon$ identities.
+Make an ansatz where you do every pairing of $\varepsilon$'s.
 This doesn't work.
@@
 \end{itemize}
+\be \label{YMSvert}
+\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} =T^3_{12}
+\ee
+\be
+V^{c}_{ab} = (\varepsilon_a\varepsilon_b)(\varepsilon_c k_a)
+\ee
+With this, the full vector interaction can be expressed as a sum over cyclic permutations:
+\be
+\cubic{hgrey0}{gluon}{}{gluon}{}{gluon}{}  =  \cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed} + \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} + \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} +\text{h.c.}
+\ee
+The state-sum between two three-point gluon vertex yields the following expansion in terms of YZ-theory vertices:
+\be
+ \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
+\ee
+where we have defined a new oriented vertex in terms of our scalar-vector building block of \ref{YMSvert},
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} = \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} +\cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed}\,.
+\ee
+\be
+\vec{V}^{c}_{ab} =V^{b}_{ac}+V^{a}_{bc}
+\ee
+All the $(\varepsilon\varepsilon)^1$ diagram permutations are isolated to the cubic sector and together manifest color-kinematics duality.
+However, the exception of the last diagram which introduces a $(\varepsilon\varepsilon)^2$ factor, must conspire with the Yang-Mills contact to preserve the duality off-shell
+
+\be
+\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed} = (s_{13}-s_{12}) \varepsilon_{(12)} \varepsilon_{(34)}
+\ee
+One was to resolve this is to introduce higher spin modes in order to accomodate the internal index contractions needed to recover the s-channal contract:
+\be
+\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{Bfield}{nhpRed}{}{nhpRed} = s_{12 }(\varepsilon_{(13)} \varepsilon_{(24)} - \varepsilon_{(14)} \varepsilon_{(23)})
+\ee
 

### 2023-09-18 notes/2loopNLSM.tex
edits

@@
 \begin{enumerate}
-\item \textbf{Locality}: Diagram numerators are polynomials in momenta and
+\item \textbf{Off-shell Locality}: Diagram numerators are polynomials in momenta and
   polarizations, \eg the diagrams only have poles given by the
@@
 Furthermore, the diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
-\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory.
+\item  \textbf{On-shell Unitarity }: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory when internal momenta are taken on-shell.
 \end{enumerate}
@@
 
-\paragraph{Locality}
+\paragraph{Off-shell Locality}
 
@@
 
-\paragraph{Unitarity}
+\paragraph{On-shell Unitarity}
 
@@
 \be
-\ee
-Note from James:  I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.
-\be
-\nGonScalar \equiv \frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}} = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
+\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
 \ee
@@
 \be
-\left[\nGonScalar\right]_{\epsilon \rightarrow k} =  f_\pi^{-n} [12][23]\cdots [n1]
+ \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
 \ee
@@
 \subsection{Two-loop obstruction}
-At two-loop, introducing terms that conspire with four-point contacts is unavoidable. Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
+At two-loop, introducing terms that conspire with four-point contacts is unavoidable (add diagram). Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
 \section{Two-loop bootstrap}
@@
 \section{Conclusions and Outlook}
-\subsection{All-loop No-Go Theorem}
-This could be a section about our expectations for all-loop construction requiring non-local color-dual integrands. Lay out counterfactual proof, i,e. define the following statement:
-\be
- Q_L=\textit{``the $L$-loop numerator is polynomial and color-dual"}. 
-\ee
-Then it is clear that if the kinematic numerator is polynomial and color-dual, evaluating it in kinematic regions where the internal legs are on-shell won't disrupt the kinematic algrebraic relations, and it must still be polynomial.
-Thus we find:
-\be
-Q_L \Rightarrow Q_{L-1}
-\ee
-Or equivalently,
-\be
-\text{not }Q_{L-1}\Rightarrow \text{not }Q_L
-\ee
-We have found that the two-loop integrand for Yang-Mills cannot be constructed from a color-dual polynomial kinematic numerator.
-Thus, if a color-dual representation exists at all-loop order for Yang-Mills it must be a rational function of kinematics.
-
+In summary, we have found that the two-loop integrand for Yang-Mills cannot be constructed from a color-dual numerator that is a polynomial in the kinematic variables.
+Thus, if a color-dual representation exists at all-loop order for Yang-Mills, it must be a rational function of kinematics.
+
+This seems to be a rather unnatural constraint on color-dual theories from the perspective of point-like quantum field theories.
+After all, introducing operators that produce rational functions of kinematics must be non-local.
+Thus, in order to identify valid color-dual representation of Yang-Mills beyond tree-level, we must relax the constraint of \textit{off-shell locality}, and realize locality only in the limit of \textit{on-shell} kinematics.
+Below we provide an overview of what one might expect for such a construction, and provide some simple examples at tree-level that manifest this structure.
+\subsection{Non-local construction of scattering amplitudes}
+ For example, consider the simple four-point example of a color-dual representation of Yang-Mills theory. 
+\be
+\mathcal{N}_{(12|34)}^{\text{YM}} = \frac{t_8F^4}{3} \frac{s_{13}-s_{12}}{s_{23}{s_{13}}}
+\ee
+By construction, this functionally symmetric numerator is anti-symmetric and obeys the Jacobi identity:
+\be
+\mathcal{N}_{(12|34)}^{\text{YM}} + \mathcal{N}_{(13|42)}^{\text{YM}} +\mathcal{N}_{(14|23)}^{\text{YM}} = 0
+\ee
+However, it must also factorize to kinematics that are consistent with the local Feynman rules of \ref{}. Evaluating the residues on $s=s_{12}$, $t=s_{23}$ and $u=s_{13}$ poles, we find:
+\begin{align}
+\text{Res}\left[\frac{ \mathcal{N}_{s}^{\text{YM}} }{s}\right]^{s=0}&= \frac{2}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\\
+\text{Res}\left[\frac{\mathcal{N}_{t}^{\text{YM}} }{t}\right]^{s=0}&= -\frac{1}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\\
+\text{Res}\left[\frac{\mathcal{N}_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\end{align}
+Plugging these into a cubic graph representation of Yang-Mills \ref{}, we find:
+\be
+\text{Res}\left[\mathcal{A}_4^{\text{YM}}\right]^{s=0} = \frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} (2c_s-c_t-c_u) =  \mathcal{A}_{(12|l)}^{\text{YM}}\mathcal{A}_{(-l|34)}^{\text{YM}} 
+\ee
+where we have applied the color structure Jacobi identity, $c_s+c_t+c_u=0$.
+While we can absolutely apply a generalized gauge trasformation \cite{BCJ} to restore field theoretic locality to the cubic numerators, we can see clearly that this is an aesthetic choice.
+Moreover, by abandoning traditional notions of off-shell locality, we can massage the color-dual numerators into a form that is manifestly gauge invariant.
+As an organizational principle, pulling out an overall gauge-invariant factors comes with the added advantage of simplifying a loop-level construction of color-dual numerators for Yang-Mills.
+\subsection{Non-local construction of color-dual integrands}
 Much of the complexity for $D$-dimensional vector theories at loop-level arises due to the mixing between external polarization and internal loop momenta.
-One advantage of expanding ansatz construction towards functions of rational kinematics is the prospect of stripping out overall factors of gauge invariant tensors.
-For example, consider the simple four-point example of a color-dual representation of Yang-Mills theory.
-\be
-\mathcal{N}_{(12|34)}^{\text{YM}} = \frac{1}{3}\left[\frac{t_8F^4}{s_{23}} -  \frac{t_8F^4}{s_{13}}\right]
-\ee
-\be
-\mathcal{N}_{(12|34)}^{\text{YM}} + \mathcal{N}_{(13|42)}^{\text{YM}} +\mathcal{N}_{(14|23)}^{\text{YM}} = 0
-\ee
-\be
-\text{Res}\left[\frac{c_s \mathcal{N}_{s}^{\text{YM}} }{s}\right]^{s=0}= \frac{2}{3} \frac{t_8F^4}{t} \qquad 
-\text{Res}\left[\frac{\mathcal{N}_{t}^{\text{YM}} }{t}\right]^{s=0}= \frac{1}{3} \frac{t_8F^4}{t}
-\ee
-\be
-A^{\text{YM}}_{(1234)} = \frac{t_8F^4}{s_{12}s_{23}}
-\ee
+As noted, one advantage of expanding ansatz construction towards functions of rational kinematics is the prospect of stripping out overall factors of gauge invariant tensors.
+Rather than building an ansatz from the irreducible scalar products of \ref{},
+\be
+\mathcal{N}^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
+\ee
+where $\mathcal{O}_i$ are the basis tensors of \cite{}, and $ \mathcal{R}_i$ is a rational function of momenta of the form;
+\be
+\mathcal{R}_{m,L} = \frac{P_{b+a}(kk,kl,ll)}{Q_a(kk,kl,ll)}, \qquad b=m+2(l-1)
+\ee
+where $P_{a}$ and $Q_a$ are degree-$a$ polynomials exclusively of $D$-dimensional scalar kinematics. 
 \subsection{Future Directions}\label{sec:Discussion}

### 2023-09-18 notes/2loopNLSM.tex
Added a few references

@@
 The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.
-However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu} ref[Ingrid+JJ, Aslan+JJ] \jm{I cited DF$^2$ and fundamental fermions.
+However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2023vjg, Carrasco:2020ywq} \jm{I cited DF$^2$, fundamental fermions, Aslan+JJ, Ingrid+JJ.
 Is there anything else anyone wants to mention?}.}
@@
 Graph symmetries are an avatar of Bose symmetry.
-For a pure ansatz construction it is very reasonable to impose graph symmetries, but color-kinematics duality at tree-level is often achieved at the expense of manifest Bose symmetry \cite{Cheung:2016prv, Cheung:2021zvb, Brandhuber:2021bsf} \citepls{Alex numerators from CHY}.
+For a pure ansatz construction it is very reasonable to impose graph symmetries, but color-kinematics duality at tree-level is often achieved at the expense of manifest Bose symmetry \cite{Cheung:2016prv, Cheung:2021zvb, Brandhuber:2021bsf, Edison:2020ehu}.
 In an ansatz construction graph symmetries are imposed for \emph{every} graph, not just the basis graphs.
@@
 As one can see above, the Jacobi identity of \ref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$.
-Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
+Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
 \be
@@
 Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$.
-By taking a derivative, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
+By taking a derivative\footnote{Another way to understand this derivative is that it selects the large $D$ behavior of the integrand.}, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
 \be
@@
 \cref{eq:other-path}. After discarding these types of cuts, we are
-left with 8 \ace{(maybe a few more to account for dangling trees)}
+left with 8 \ace{(maybe a few more to account for dangling trees)} \jm{How about we just say that there are 8 N$^1$ cuts ignoring dangling trees?}
 unique cut topologies, shown in \cref{fig:ym-nmc}, to check.  Seven of

### 2023-09-18 notes/2loopNLSM.tex
Starting to think about abstract.
A few actual sentences in abstract.

@@
 \abstract{
-\ace{I will start working here over the weekendish}
+
+  We catalog and analyze ?4? theories which all manifest the duality
+  between color and kinematics both at tree and one-loop level.  We
+  identify a unifying theory, \emph{semi-abelian} Yang--Mills, from
+  which all four of the theories can be extracted.  Joint
+  consideration of these theories sheds light on the long-standing
+  problem.
+
+  \begin{itemize}
+  \item Catalog themes among ``manifestly'' color dual theories
+  \item Identify obstructions going $1 \to 2$ loop
+  \item Highlight obstructions and overcome via NLSM bootstrap
+  \item Brief revisit of 2L YM
+  \end{itemize}
 

### 2023-09-19 notes/2loopNLSM.tex
4pt pion numerators

@@
 In theories where the kinematic algebra is known, it is often the algebra of volume preserving diffeomorphisms \cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz, Cheung:2021zvb, Cheung:2022mix}.
+As a simple example, color-dual numerators for 4pt pion scattering at tree level are
+\begin{align}
+&n_s = s(t-u)\\
+&n_t = t(u-s)\\
+&n_u = u(s-t)
+\end{align}
+where the coupling has been normalized away.
+These numerators sum to zero by explicit calculation.
 
@@
 The double copy can be proven at tree level using the KLT relations but there is significant evidence that the double copy persists to all loop orders \cite{KLT, KiermaierTalk} \citepls{Any loop papers we want?}.
+In addition to pointing at deep structure hidden in the Lagrangian for gravity, the double copy is immensely useful at a utilitarian level since it is much more efficient at producing $\mathcal{M}_m^L$ than traditional methods like Feynman rules.
 
@@
 At 1-loop, every diagram can be related to one topology as well, in this case the $n$-gon, but the pattern does not persist to 2-loops.
-
-\jm{Should we do some example like 4pt NLSM or 4pt YM and say that it's simpler than GR?  I don't think it would add much.}
 

### 2023-09-19 notes/2loopNLSM.tex
Fund BCJ + misc

@@
 The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.
-However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2023vjg, Carrasco:2020ywq} \jm{I cited DF$^2$, fundamental fermions, Aslan+JJ, Ingrid+JJ.
-Is there anything else anyone wants to mention?}.}
+However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2023vjg, Carrasco:2020ywq}.}
 the denominator $d_\Gamma$ is the product of propagators associated with the graph $\Gamma$, and the numerator $n_\Gamma$ is all of the remaining kinematic factors including dot products of momenta and polarization vectors.
@@
 These numerators sum to zero by explicit calculation.
+Note that the $s$-channel numerator contains an explicit factor of $s$ that cancels with the propagator and the same goes for the $t$- and $u$-channels so that the net result is a local function, just as one would expect for the pion tree amplitude.
 
@@
 
-Many of the 1-loop results presented in \sect{} are informed by the tree-level double-copy so we will review the tree case here.
+Many of the 1-loop results presented in \cref{sec:cubic} are informed by the tree-level double-copy so we will review the tree case here.
 The color structure of tree-level amplitudes is particularly simple.
@@
 \ee
-with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$ terms, indicating that there are additional relations (the Kleiss-Kuijf relations) amongst the partial amplitudes \cite{Kleiss:1988ne}.\footnote{The fundamental BCJ relations further reduce the basis of partial amplitudes down to $(n-3)!$ \cite{BCJ}.}
-Since the Jacobi identity can be used to express any tree-level color factor in terms of the half ladders, it is enough to specify the numerators of the half ladder diagrams in order to satisfy color-kinematics duality at tree level.
+with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$ terms, indicating that there are additional relations -- the Kleiss-Kuijf (KK) relations -- amongst the partial amplitudes \cite{Kleiss:1988ne}.
+The KK relations are generic to any theory with purely adjoint particles.
+Color-kinematics duality implies that the KK basis is overcomplete and can be reduced to a basis of $(n-3)!$ amplitudes via the fundamental BCJ identities \cite{BCJ}
+\be
+\sum \limits_{i=2}^{n-1} k_1 \cdot (k_2+...+k_i) A_n[2,...,i,1,i+1,...,n] =0.
+\ee
+In terms of constructing explicit color-dual solutions at tree level, it is enough to specify the numerator of the half ladder because any diagram can be reduced to a half ladder through successive applications of the Jacobi identity.
 At 1-loop, every diagram can be related to one topology as well, in this case the $n$-gon, but the pattern does not persist to 2-loops.
@@
 See refs \cite{} for some recent examples.
-Indeed, as we'll show in \ref{cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point.
+Indeed, as we'll show in \cref{sec:cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point.
 Absent information about the kinematic algebra, one can make progress in the construction of loop-level color-dual amplitudes by employing a color-dual bootstrap.
@@
 As mentioned earlier, this is possible to do even for a theory with quartic (or higher multiplicity) vertices by multiplying and dividing by propagators.
-In the case of the 4pt 2-loop example promised above, there are 14 cubic graph topologies (shown in Fig \sect{}) ignoring tadpoles and bubble on external leg (BEL) graphs.
+In the case of the 4pt 2-loop example promised above, there are 14 cubic graph topologies (shown in \cref{fig:MaxCuts}) ignoring tadpoles and bubble on external leg (BEL) graphs.
 
@@
 
-\section{One-loop cubic construction} \label{cubic}
+\section{One-loop cubic construction}
+\label{sec:cubic}
 Here we'll describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
@@
 }
-  \caption{The 14 non-pathological maximal-cut diagrams}
+  \caption{The 14 non-pathological maximal-cut diagrams} \label{fig:MaxCuts}
   \end{figure}

### 2023-09-19 notes/2loopNLSM.tex
Conclusion + misc

@@
 \be
+\label{eq:semiYM}
 \mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
@@
 \be
-F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
+F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c .
 \ee
@@
 Indeed, as we describe in the Appendix \ref{}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{}, J-theory \cite{}, and self-dual Yang-Mills \cite{}.
+Specifically, semi-Abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
 We can use the Ward identity of \ref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant with the abelian polarizations are taken on-shell, $\bar{\varepsilon} \rightarrow k$.
@@
 However, these methods cannot be reapplied to generate higher-loop numerators, which begs the question ``is it possible to find globally color-dual numerators beyond 1-loop''.
-We will tackle this question for N$^2$LO 2-to-2 scattering in NLSM before moving on to the same process in YM.
-
-Ignoring tadpoles and BEL graphs, there are 14 cubic 4pt 2-loop graphs (see later picture) which are related to each other via 21 Jacobi relations.
-As mentioned in (review section), color-kinematics duality ensures that the numerator of every graph can be expressed in terms of a basis of the double box and penta-triangle,
+We will tackle this question for 4pt 2-loop scattering in NLSM before moving on to the same process in YM.
+
+Ignoring tadpoles and BEL graphs, there are 14 cubic 4pt 2-loop graphs (see \cref{fig:MaxCuts}) which are related to each other via 21 Jacobi relations.
+As mentioned in \cref{sec:bootstrap}, color-kinematics duality ensures that the numerator of every graph can be expressed in terms of a basis of the double box and penta-triangle,
 \begin{equation}
@@
 One hope would be to factor out some piece of the 1-loop numerator since this at least manifests antisymmetry for the vertices involving external legs.
-However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov theory \cite{Zakharov:1973pp, Cheung:2022mix}.
+However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}.
 
 Why don't you just set all of the generalized gauge freedom parameters to zero?
-You can learn useful things by not doing this (see N=4), this allows us to introduce more physics into the problem, and, unsurprisingly, setting them to zero produces more a more complex answer with more unwieldy rational numbers than using physics.
+You can learn useful things by not doing this (see N=4), this allows us to introduce more physics into the problem, and, unsurprisingly, setting them to zero produces a more complex answer with more unwieldy rational numbers than using physics.
 
@@
 \label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) .
-\ee
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c),
+\ee
+where more details can be found in \cref{sec:CKLagrangians}.
 The color-stripped Feynman rule for the vertex is simply $V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where off-shell color-kinematics duality to all orders in perturbation theory simply follows from the Schouten identity.
@@
 pathological diagrams including the newly-appearing type discussed in
-\cref{eq:other-path}. After discarding these types of cuts, we are
-left with 8 \ace{(maybe a few more to account for dangling trees)} \jm{How about we just say that there are 8 N$^1$ cuts ignoring dangling trees?}
-unique cut topologies, shown in \cref{fig:ym-nmc}, to check.  Seven of
-these next-to-maximal cuts are consistent with the kinematic Jacobi
-relations and symmetries.  Interestingly, the ``kissing triangles''
+\cref{eq:other-path}.
+After discarding these types of cuts, there are 8 cut topologies (see \cref{fig:ym-nmc}) ignoring cuts with dangling trees.
+Seven of these next-to-maximal cuts are consistent with the kinematic Jacobi
+relations and symmetries.  Interestingly, the ``kissing triangles'' or ``bowtie''
 cut,
@@
 cannot be satisfied by either the unrestricted or the BDN-restricted
-ansatz with Jacobi relations and symmetries applied.
+ansatz with Jacobi relations and symmetries applied. \jm{I would just focus on what we do since we do something more general than BDN.}
 \begin{figure}
@@
 \section{Conclusions and Outlook}
-In summary, we have found that the two-loop integrand for Yang-Mills cannot be constructed from a color-dual numerator that is a polynomial in the kinematic variables.
-Thus, if a color-dual representation exists at all-loop order for Yang-Mills, it must be a rational function of kinematics.
-
-This seems to be a rather unnatural constraint on color-dual theories from the perspective of point-like quantum field theories.
+There is overwhelming evidence that YM and NLSM obey color-kinematics duality at loop level even though naive Lagrangians for these theories do not manifest the duality.
+At tree level, the duality can be manifested by breaking manifest Bose symmetry at the Lagrangian level, either by explicitly picking different gluon states (as in SDYM) or by picking states that only restore Bose symmetry in the final amplitude (as in NLSM).
+All of these theories can be encapsulated in the semi-Abelian YM theory presented in \cref{eq:semiYM} which obscures the Bose symmetry of the external states due to the presence of the two gauge fields $A_\mu$ and $\bar{A}_\mu$.
+The kinetic mixing between the two gauge fields permits globally color-dual 1-loop integrands, but special care must be taken so that the integrands produced from semi-Abelian YM correspond to SDYM or NLSM.
+Due to the kinetic mixing that stems from the broken Bose symmetry, it is impossible to construct a 2-loop integrand for semi-Abelian YM theory, that is, the theory is 1-loop exact.
+Obtaining a globally color-dual integrand beyond 1-loop then requires sacrificing more than just Bose symmetry and in this paper it is argued that off-shell locality must be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in order to obtain color-dual 2-loop integrands.}
+
+\jm{I am intentionally shying away from really firm statements like 'you must abandon locality' because there are always loopholes and we made a lot of other assumptions in fixing our \ansatze{}.}
+
+Kinematic ``numerators'' that are rational functions of the kinematics appear unnatural from the perspective of point-like quantum field theories.
 After all, introducing operators that produce rational functions of kinematics must be non-local.
@@
 \label{sec:CKLagrangians}
+
+Below we review the four manifestly color-dual theories that appear in this paper, in particular SDYM, two formulations of NLSM, and ZM.
+All of these theories are closely tied together by the semi-Abelian YM theory in \cref{eq:semiYM} or in other words the cubic sector of YM.
+The manifestly color-dual equations of motion for SDYM and NLSM are derived by picking a gauge and then placing a constraint not on the YM equation of motion or Bianchi identity but rather directly on the field strength itself.
+Other theories can be obtained from SDYM and NLSM by judicious modification of the propagator.
+In all of these theories, the kinematic algebra is that of (volume preserving) diffeomorphisms or some close variant thereof.
+In almost all of these theories, Bose symmetry is broken or obscured at the Lagrangian level.
+Because of the broken Bose symmetry (and the inherited kinetic mixing of semi-Abelian YM), these theories cannot produce color-dual numerators at 2-loop or higher.
+
+\jm{I've deleted the boxes around equations.
+I actually really like them normally but if we're boxing something in the appendix then it feels like that's a major enough result that it should be in the main body of the paper.}
+
 \paragraph{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
@@
 Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
-\begin{eBox}
 \be
@@
 \ee
-\end{eBox}
 The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
@@
 For this reason, the color-dual nature depends critically on the loop order of the amplitude and does not hold generically beyond one-loop.
-
-Next we will briefly describe a 2D scalar theory, Zakharov-Mikhailov (ZM) theory, whose equations of motion bear a striking resemblance to the SDYM equatioi of motion given above in \cref{SDEOM}.
 
@@
 Plugging this redefinition of the gauge fields in, upto cubic order, we thus obtain the following Lagrangian:
-\begin{eBox}
 \be
@@
 \ee
-\end{eBox}
 The Feynman rules for this Lagrangian are simply:
@@
 \ee
-Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian
-\begin{eBox}
-\be
-\mathcal{L}^{\text{J}} =\bar{J}^\mu \Box J_\mu +g f^{abc} \bar{J}^\mu J^\nu \partial_\nu J^\mu .
-\ee
-\end{eBox}
+Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-Abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
+In other words, \emph{J-theory and semi-Abelian YM are identical}.
 By calculating an off-shell 4pt correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
-Kinematic algebra is diff algebra (as usual).
-How to extract physical states... (longitudinal J, weird J bar, restores broken Bose).
+As might be expected, the kinematic algebra is the diffeomorphism algebra.
+For details about external states and how to extract NLSM (a scalar theory) from semi-YM (a vector theory) we refer the reader to \cite{Cheung:2021zvb}.
+Note that the different external particles break manifest Bose symmetry.
 
@@
 After plugging $\varphi$ into \cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
-\begin{eBox}
 \be
@@
 \ee
-\end{eBox}
 This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
@@
 This suggests that the two lightcone coordinates $u$ and $w$ should be identified as the coordinates of the 2D space.
-The 4D d'Alembertian in lightcone coordinates, $\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$, cannot be interpreted as the 2D equivalent, so the kinetic term of SDYM must be scrapped and replaced with the correct 2D version.
+The 4D d'Alembertian in lightcone coordinates, $\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$, cannot be interpreted as the 2D equivalent, so the kinetic term of SDYM must be replaced with the correct 2D version.
 This argument should be understood purely as an alternative route to ZM theory.
@@
 Similar to the difficulties of renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
-As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
-
-\paragraph{Wess-Zumino-Witten theory -- James}
-I want to write this down or I'm going to completely forget it
-
-Should probably also mention that BAS has CK at Lagrangian level (duh).
-
-\paragraph{Cubic 2-form theory -- James}
-
-Cubic 2-form theory also has trivial CK.
-If you change the propagator (this trick is a theme) then you get YM at least classically.
-This is the nonsense ``covariant'' DC.
-
-\paragraph{Chern-Simons theory -- James}
-We won't use this but it's useful to treat all of the CK theories in one place
-Cite Henrik Maor
-Again you place some constraint on the field strength and use Lorenz gauge
-
-\paragraph{Generalities of known color-dual theories -- James}
-Should this section maybe go first?
-
-\begin{itemize}
-\item This paper kills all ``simple'' color-dual, loop-level Lagrangians for YM but it remains possible that one exists for NLSM.
-\item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
-\item All of the theories described above have diff as kinematic algebra, SU(N) for BAS, or rigid/spin Lorenz for cubic 2-form theory
-\item All of the theories choose a simple gauge like Lorenz or lightcone
-\item All of the theories place some constraint on the field strength directly and get their equations of motion directly from that constraint, not the YM EOM.
-\item (Almost all of the theories (aside from NLSM) have trivial amplitudes at least at tree level)
-\item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
-\item For off-shell CK, the kinetic term is relatively unimportant so long as the poles are correctly/consistently identified (what do you mean by s,t,u channel poles).
-This might screw up locality in the squared theory.
-\end{itemize}
+As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dimensional regularization.
+
 \section{Spinor-helicity and conventions}
+\jm{I would be happy to say that we use a mostly minus metric and the spinor helicity conventions of \cite{jjmcTASI2014} in the introduction and omit this appendix.}
+
 Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. For massless momenta, $k_a$ and $k_b$, we have 
@@
 If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
-\item Reiterate that the (tree) amplitudes of CS and SDYM are zero.
+\item Reiterate that the tree amplitudes of SDYM are zero and 1-loop is the first interesting case.
 \item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.

### 2023-09-19 notes/2loopNLSM.tex
Small edits

@@
 
-Aside from a few special theories that permit an off-shell Lagrangian description \citepls{}, color-dual integrands are constructed from an ansatz.
+Aside from a few special theories that permit an off-shell Lagrangian description \cite{Monteiro2011pc, Cheung:2016prv, Cheung:2021zvb, Cheung:2020djz, Ben-Shahar:2022ixa, Ben-Shahar:2021zww, Ben-Shahar:2021doh}, color-dual integrands are constructed from an ansatz.
 The four conditions we impose on an ansatz are summarized here and elaborated on below.\footnote{The four ansatz conditions are similar to those of Ref.~\cite{Bern:2015ooa} except that the authors demand that the numerators have the same loop power counting as Feynman gauge Feynman rules.
@@
 
+\jm{Rather than quoting the number of parameters in the BDN ansatz, I would prefer to just focus on what we did since it's more general.
+I don't want it to sound like we just patched a minor hole in their argument when I think you've done something much cooler by pinpointing the failure to the bowtie graph.}
+
 Two-loop color-dual integrands for non-supersymmetric YM have been investigated before but only for a limited ansatz that manifests locality \cite{Bern:2015ooa}.
@@
 cannot be satisfied by either the unrestricted or the BDN-restricted
-ansatz with Jacobi relations and symmetries applied. \jm{I would just focus on what we do since we do something more general than BDN.}
+ansatz with Jacobi relations and symmetries applied. 
 \begin{figure}
@@
 
-\jm{I am intentionally shying away from really firm statements like 'you must abandon locality' because there are always loopholes and we made a lot of other assumptions in fixing our \ansatze{}.}
+\jm{I am intentionally shying away from really firm statements like `you must abandon locality' because there are always loopholes and we made a lot of other assumptions in fixing our \ansatze{}.}
 

### 2023-09-19 notes/2loopNLSM.tex
small edits

--- 2023-09-19 notes/2loopNLSM.tex
@@
 \section{Background}
-To set the stage, in this section we will provide an overview of color-kinematics duality -- both the on-shell and off-shell construction.
+To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions.
 We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM.
@@
 The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.
-However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2023vjg, Carrasco:2020ywq}.}
+However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2023vjg, Carrasco:2020ywq} \jm{I cited DF$^2$, fundamental fermions, Aslan+JJ, Ingrid+JJ.
+Is there anything else anyone wants to mention?}.}
 the denominator $d_\Gamma$ is the product of propagators associated with the graph $\Gamma$, and the numerator $n_\Gamma$ is all of the remaining kinematic factors including dot products of momenta and polarization vectors.
@@
 These numerators sum to zero by explicit calculation.
-Note that the $s$-channel numerator contains an explicit factor of $s$ that cancels with the propagator and the same goes for the $t$- and $u$-channels so that the net result is a local function, just as one would expect for the pion tree amplitude.
 
@@
 
-Many of the 1-loop results presented in \cref{sec:cubic} are informed by the tree-level double-copy so we will review the tree case here.
+Many of the 1-loop results presented in \sect{} are informed by the tree-level double-copy so we will review the tree case here.
 The color structure of tree-level amplitudes is particularly simple.
@@
 \ee
-with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$ terms, indicating that there are additional relations -- the Kleiss-Kuijf (KK) relations -- amongst the partial amplitudes \cite{Kleiss:1988ne}.
-The KK relations are generic to any theory with purely adjoint particles.
-Color-kinematics duality implies that the KK basis is overcomplete and can be reduced to a basis of $(n-3)!$ amplitudes via the fundamental BCJ identities \cite{BCJ}
-\be
-\sum \limits_{i=2}^{n-1} k_1 \cdot (k_2+...+k_i) A_n[2,...,i,1,i+1,...,n] =0.
-\ee
-In terms of constructing explicit color-dual solutions at tree level, it is enough to specify the numerator of the half ladder because any diagram can be reduced to a half ladder through successive applications of the Jacobi identity.
+with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$ terms, indicating that there are additional relations (the Kleiss-Kuijf relations) amongst the partial amplitudes \cite{Kleiss:1988ne}.\footnote{The fundamental BCJ relations further reduce the basis of partial amplitudes down to $(n-3)!$ \cite{BCJ}.}
+Since the Jacobi identity can be used to express any tree-level color factor in terms of the half ladders, it is enough to specify the numerators of the half ladder diagrams in order to satisfy color-kinematics duality at tree level.
 At 1-loop, every diagram can be related to one topology as well, in this case the $n$-gon, but the pattern does not persist to 2-loops.
@@
 See refs \cite{} for some recent examples.
-Indeed, as we'll show in \cref{sec:cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point.
+Indeed, as we'll show in \ref{cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point.
 Absent information about the kinematic algebra, one can make progress in the construction of loop-level color-dual amplitudes by employing a color-dual bootstrap.
@@
 As mentioned earlier, this is possible to do even for a theory with quartic (or higher multiplicity) vertices by multiplying and dividing by propagators.
-In the case of the 4pt 2-loop example promised above, there are 14 cubic graph topologies (shown in \cref{fig:MaxCuts}) ignoring tadpoles and bubble on external leg (BEL) graphs.
+In the case of the 4pt 2-loop example promised above, there are 14 cubic graph topologies (shown in Fig \sect{}) ignoring tadpoles and bubble on external leg (BEL) graphs.
 
@@
 
-\section{One-loop cubic construction}
-\label{sec:cubic}
+\section{One-loop cubic construction} \label{cubic}
 Here we'll describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
@@
 }
-  \caption{The 14 non-pathological maximal-cut diagrams} \label{fig:MaxCuts}
+  \caption{The 14 non-pathological maximal-cut diagrams}
   \end{figure}
@@
 \be
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =\mathcal{X}(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
 \ee
@@
 As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dim reg.
-
-\paragraph{Wess-Zumino-Witten theory -- James}
-I want to write this down or I'm going to completely forget it
-
-Should probably also mention that BAS has CK at Lagrangian level (duh).
-
-\paragraph{Cubic 2-form theory -- James}
-
-Cubic 2-form theory also has trivial CK.
-If you change the propagator (this trick is a theme) then you get YM at least classically.
-This is the nonsense ``covariant'' DC.
-
-\paragraph{Chern-Simons theory -- James}
-We won't use this but it's useful to treat all of the CK theories in one place
-Cite Henrik Maor
-Again you place some constraint on the field strength and use Lorenz gauge
-
-\paragraph{Generalities of known color-dual theories -- James}
-Should this section maybe go first?
-
-\begin{itemize}
-\item This paper kills all ``simple'' color-dual, loop-level Lagrangians for YM but it remains possible that one exists for NLSM.
-\item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
-\item All of the theories described above have diff as kinematic algebra, SU(N) for BAS, or rigid/spin Lorenz for cubic 2-form theory
-\item All of the theories choose a simple gauge like Lorenz or lightcone
-\item All of the theories place some constraint on the field strength directly and get their equations of motion directly from that constraint, not the YM EOM.
-\item (Almost all of the theories (aside from NLSM) have trivial amplitudes at least at tree level)
-\item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
-\item For off-shell CK, the kinetic term is relatively unimportant so long as the poles are correctly/consistently identified (what do you mean by s,t,u channel poles).
-This might screw up locality in the squared theory.
-\end{itemize}
 \section{Spinor-helicity and conventions}

### 2023-09-19 notes/2loopNLSM.tex
A very rough first abstract.

@@
   which all four of the theories can be extracted.  Joint
-  consideration of these theories sheds light on the long-standing
-  problem.
-
-  \begin{itemize}
-  \item Catalog themes among ``manifestly'' color dual theories
-  \item Identify obstructions going $1 \to 2$ loop
-  \item Highlight obstructions and overcome via NLSM bootstrap
-  \item Brief revisit of 2L YM
-  \end{itemize}
+  consideration of these theories highlights that the lifting of
+  one-loop color-kinematics dual numerators to two loops may be just
+  as challenging as the step from tree level to one loop.  As a first
+  step in understanding the two-loop challenge, we construct
+  color-dual two-loop four-point non-linear sigma model (NLSM)
+  numerators using generalized unitarity methods.  The double-copy of
+  the constructed NLSM numerators with themselves, $\mathcal{N}=0$
+  Yang--Mills, and $\mathcal{N}=4$ Yang--Mills correctly reproduce the
+  known physical unitarity cuts of special Gallileons, Born-Infeld
+  theory, and Dirac-Born-Infeld-Volkov-Akulov theory, respectively.
+  These NLSM numerators are in explicit tension with generalizations
+  of the one-loop NLSM numerators. \ace{I realize that we all know
+    this, but does/will a statement to this effect actually make it
+    into the draft?}  Additionally, we revisit the two-loop four-point
+  Yang--Mills problem in order to identify the exact point of
+  inconsistency in a local color-dual construction.
 

### 2023-09-19 notes/2loopNLSM.tex
added intro

--- 2023-09-19 notes/2loopNLSM.tex
@@
 \setstackgap{L}{7pt}
-
-\section{Introduction}
-\section{Background}
+\newpage
+\section{Introduction}\label{intro}
+Since the turn of the century, our understanding of the $S$-matrix and its hidden structure has expanded dramatically.
+At the heart of this progress is the mantra that physical observables are simpler when studied on-shell.
+However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell structure at the heart of many quantum field theories.
+A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors.
+When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{}.
+
+However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, the duality between color and kinematics remains a conjecture at loop level.
+Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{}.
+In this work, we use the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven to permit color-dual representations at tree-level \cite{}, as case studies for advancing our understanding of the kinematic algebra to the multi-loop level.
+
+We begin by providing background on the duality between color
+
+In contrast to presently available on two-loop construction of color-dual integrands \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional.
+This makes our methods and results particularly well suited or tackling  We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public.
+ \section{Background}\label{background}
 To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions.
 We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM.
-\subsection{Color-dual Amplitudes}
+\subsection{Color-dual Amplitudes}\label{onShellCK}
 
@@
 
-\subsection{Color-dual Lagrangians}
+\subsection{Color-dual Lagrangians}\label{offShellCK}
 While BCJ relations is an on-shell statement about the color-dual nature of scattering amplitudes, one might aspire to hard code color-kinematics duality by realizing an off-shell Lagrangian description of the theory.
@@
 This is a sufficient condition of the amplitudes to obey BCJ relations.
-Off-shell desciription of color-dual theories are rare, and only a few examples are available in the literature.
+Off-shell description of color-dual theories are rare, and only a few examples are available in the literature.
 Typically when one goes about construction color-dual theories directly from a set of cubic interactions, higher point Jacobi and antisymmetry constraints require introducing additional operators.
@@
 With this in hand, we can construct a Lagrangian description of the of the cubic sector for Yang-Mills, and will demonstrate that the resulting amplitudes with manifestly color-dual Feynman rules are equivalent to both SDYM and NLSM through one-loop.
-\subsection{Semi-abelian Yang-Mills theory}
+\subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
 As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell.
@@
 
-\subsection{One-loop color-dual integrands}
+\subsection{One-loop color-dual integrands}\label{oneLoopCK}
 Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM).
@@
 Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
-\subsection{Two-loop obstruction}
+\subsection{Two-loop obstruction}\label{2LoopObstruction}
 At two-loop, introducing terms that conspire with four-point contacts is unavoidable (add diagram). Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
-\section{Two-loop bootstrap}
-
-\subsection{Two-loop NLSM}
+\section{Two-loop bootstrap}\label{2loopBoot}
+
+\subsection{Two-loop NLSM}\label{2loopNLSM}
 \label{sec:pions}
@@
 
-\subsection{Double-copy verification}
+\subsection{Double-copy verification}\label{doubleCopyVerify}
 \ace{I'm punting a lot of discussion to Ref \cite{Carrasco:2023qgz}.
@@
 
-\subsection{Two-loop Yang-Mills revisited}
+\subsection{Two-loop Yang-Mills revisited}\label{2loopYM}
 
@@
 
-\section{Conclusions and Outlook}
+\section{Conclusions and Outlook}\label{conclusions}
 There is overwhelming evidence that YM and NLSM obey color-kinematics duality at loop level even though naive Lagrangians for these theories do not manifest the duality.
@@
 Below we provide an overview of what one might expect for such a construction, and provide some simple examples at tree-level that manifest this structure.
-\subsection{Non-local construction of scattering amplitudes}
+\subsection{Non-local construction of scattering amplitudes}\label{nonLocalScattering}
  For example, consider the simple four-point example of a color-dual representation of Yang-Mills theory. 
@@
 As an organizational principle, pulling out an overall gauge-invariant factors comes with the added advantage of simplifying a loop-level construction of color-dual numerators for Yang-Mills.
-\subsection{Non-local construction of color-dual integrands}
+\subsection{Non-local construction of color-dual integrands}\label{nonLocalLoops}
 Much of the complexity for $D$-dimensional vector theories at loop-level arises due to the mixing between external polarization and internal loop momenta.
@@
 
-\section{Spinor-helicity and conventions}
+\section{Spinor-helicity and conventions}\label{Conventions}
 \jm{I would be happy to say that we use a mostly minus metric and the spinor helicity conventions of \cite{jjmcTASI2014} in the introduction and omit this appendix.}
@@
 \ee
-\section{Regulating BEL integrals}
+\section{Regulating BEL integrals}\label{BELreg}
 At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles.

### 2023-09-19 notes/2loopNLSM.tex
more edits to intro
intro done. now going to add citations

@@
 \section{Introduction}\label{intro}
-Since the turn of the century, our understanding of the $S$-matrix and its hidden structure has expanded dramatically.
+Since the turn of the century, our understanding of the $S$-matrix and its hidden structures has expanded dramatically.
 At the heart of this progress is the mantra that physical observables are simpler when studied on-shell.
 However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell structure at the heart of many quantum field theories.
-A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors.
+A shining example of this hidden simplicity is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors.
 When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{}.
 
-However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, the duality between color and kinematics remains a conjecture at loop level.
+However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, the color-kinematics remains a conjecture at loop level.
 Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{}.
@@
 
-We begin by providing background on the duality between color
-
+We begin with an overview of color-kinematics duality in \cref{background}.
+We then construct a manifestly color-dual theory in \cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point numerators for both NLSM and the self-dual sector of Yang-Mills through one-loop.
+The construction of this theory, which we dub semi-abelian Yang-Mills, relies on isolating the cubic sector of pure Yang-Mills amplitudes from the four-point contacts that are needed to fully realize non-abelian gauge symmetry.
+Promoting this construction beyond one-loop runs into an obstruction that we describe in \cref{2loopObstruction}.
+
+Faced with this obstruction, we study the multi-loop sector of both NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz based color-dual bootstrap.
 In contrast to presently available on two-loop construction of color-dual integrands \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional.
-This makes our methods and results particularly well suited or tackling  We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public.
+This makes our methods and results particularly well suited for algorithmically extracting rational terms from the $D$-dependence of dimensionally regulated loop momenta.
+We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public.
+
+With this solver, we are able to compute a two-loop integrand for NLSM that globally manifests the duality off-shell.
+This represents a new bench mark for color-dual representations in non-supersymmetric gauge theories.
+However in contrast, we find surprisingly that Yang-Mills does not permit a globally color-dual representation when considering the most general polynomial ansatz of irreducible scalar products.
+Concretely, we find a sharp failure point between the ``kissing triangles'' cut, and the following jacobi triple:
+\begin{equation}
+   \NMCutC
+  \Rightarrow
+  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
+\end{equation}
+We comment on the implications of this finding in \cref{conclusions}, and discuss alternative approaches where one relaxes field theoretic locality in order to accommodate the construction of globally color-dual numerators to all-loop order.
+
 \section{Background}\label{background}

### 2023-09-19 notes/2loopNLSM.tex
added citations. Going to read though and cull

--- 2023-09-19 notes/2loopNLSM.tex
@@
 \section{Introduction}\label{intro}
-Since the turn of the century, our understanding of the $S$-matrix and its hidden structure has expanded dramatically.
+Since the turn of the century, our understanding of the $S$-matrix and its hidden structures has expanded dramatically.
 At the heart of this progress is the mantra that physical observables are simpler when studied on-shell.
-However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell structure at the heart of many quantum field theories.
+However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell simplicity at the heart of many quantum field theories.
 A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors.
@@
 
-However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, the duality between color and kinematics remains a conjecture at loop level.
+However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, color-kinematics remains a conjecture at loop level.
 Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{}.
@@
 
-We begin by providing background on the duality between color
-
-In contrast to presently available on two-loop construction of color-dual integrands \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional.
-This makes our methods and results particularly well suited or tackling  We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public.
+We begin with an overview of color-kinematics duality in \cref{background}.
+We then construct a manifestly color-dual theory in \cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point numerators for both NLSM and the self-dual sector of Yang-Mills through one-loop.
+The construction of this theory, which we dub \textit{semi-abelian Yang-Mills}, relies on isolating the cubic sector of pure Yang-Mills amplitudes from the four-point contacts that are needed to fully realize non-abelian gauge symmetry.
+Despite the potency of this theory at one-loop, the construction runs into an obstruction at two-loop, which we describe in \cref{2LoopObstruction}.
+
+Faced with this obstruction, we study the multi-loop sector of both NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz based color-dual bootstrap.
+In contrast to much of the available literature on construction of color-dual integrands at two-loop \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional.
+This makes our methods and results particularly well suited for algorithmically extracting rational terms from the $D$-dependence of dimensionally regulated loop momenta.
+We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public.
+
+With this solver, we are able to compute a two-loop integrand for NLSM that globally manifests the duality off-shell.
+This represents a new benchmark for color-dual representations in non-supersymmetric gauge theories.
+However in contrast, we find surprisingly that Yang-Mills does not permit a globally color-dual representation, even when considering the most general polynomial ansatz of Lorentz covariant kinematics.
+Concretely, we find a sharp failure point between the ``bowtie'' cut, and the following jacobi triple:
+\begin{equation}
+   \NMCutC
+  \Rightarrow
+  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
+\end{equation}
+We comment on the implications of this finding in \cref{conclusions}, and discuss alternative approaches where one must relax field theoretic locality in order to accommodate the construction of globally color-dual multi-loop integrands.
+
 \section{Background}\label{background}
 To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions.
-We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM.
+We then detail a color-dual boostrap approach for constructing integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM.
 \subsection{Color-dual Amplitudes}\label{onShellCK}
@@
 are the multiplicities of the blobs.}
-As an example, consider the ``kissing triangle'' cut topology -- one of
+As an example, consider the ``bowtie'' cut topology -- one of
 the factorization channels of the iterated unitarity cut -- which has
@@
 \section{Two-loop bootstrap}\label{2loopBoot}
-
+We now employ the color-dual bootstrap method described in \cref{bootstrap}.
+We will employ an ansatz constructed from  $D$-dimensionally Lorentz covariant kinematics.
+To fix remaining freedom in the NLSM bootstrap, we will match down to ZM theory in $D=2$.
+This is merely an aesthetic choice, so the final results of both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
 \subsection{Two-loop NLSM}\label{2loopNLSM}
@@
 }
-  \caption{The 14 non-pathological maximal-cut diagrams} \label{fig:MaxCuts}
+  \caption{The 14 non-pathological maximal-cut diagrams, including all dangling tree diagrams.} \label{fig:MaxCuts}
   \end{figure}
@@
 Seven of these next-to-maximal cuts are consistent with the kinematic Jacobi
-relations and symmetries.  Interestingly, the ``kissing triangles'' or ``bowtie''
+relations and symmetries.  Interestingly, the ``bowtie'' or ``kissing-triangles''
 cut,
@@
  \NMCutE, \NMCutF, \NMCutA, \NMCutC,  }
-  \caption{The 8 non-pathological next-to-maximal-cut diagrams.}
+  \caption{The 8 non-pathological 1-particle-irreducible next-to-maximal-cut diagrams used in our cut constraints on the Yang-Mills integrand.}
   \label{fig:ym-nmc}
@@
 crossed-box, and 5040 free paramters on the penta-triangle.  Then
-impose the ``kissing triangle'' next-to-maximal cut, which in the
+impose the ``bowtie'' next-to-maximal cut, which in the
 \emph{non-planar} $t$-$u$ color channel only recieves contributions
@@
 symmetry, and the kinematic Jacobi relations for just three diagrams
-are incompatible with the ``kissing triangle'' cut.
+are incompatible with the ``bowtie'' cut.
 
@@
 \be
-\mathcal{R}_{m,L} = \frac{P_{b+a}(kk,kl,ll)}{Q_a(kk,kl,ll)}, \qquad b=m+2(l-1)
+\mathcal{R}_{m,L} = \frac{P_{b+a}(k^2,kl,l^2)}{Q_a(k^2,kl,l^2)}, \qquad b=m+2(l-1)
 \ee

### 2023-09-19 notes/2loopNLSM.tex
some more edits
Added some graphs for two-loop construction. Absorbed helicity decomposition games into the beginning of section 3. Restructed some games wiith semi-YM. Eyes are bleeding now though, so going to add more more citatiios ad thenn hand off

@@
 Concretely, we find a sharp failure point between the ``bowtie'' cut, and the following jacobi triple:
+\begin{eBox}
 \begin{equation}
@@
 \end{equation}
+\end{eBox}
 We comment on the implications of this finding in \cref{conclusions}, and discuss alternative approaches where one must relax field theoretic locality in order to accommodate the construction of globally color-dual multi-loop integrands.
@@
 Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form.
-The organizational principle underlying this construction can be easily understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog}, which we summarize briefly below.
-\subsection{Block Decomposition of Yang-Mills}
-The $D$-dimensional Lagrangians of \ref{} can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order.
-Start with reducible amplitude block decomp from Ref.
-\cite{Pavao:2022kog}:
+The organizational principle underlying this construction can be easily understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog},
 \begin{equation}\label{eq:pureVecRABD}
@@
 \end{equation}
-By a simple mass-dimensioin argument, we know the tree-level cubic sector must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
+By a simple mass-dimensioin argument, we know the tree-level cubic sector of Yang-Mills must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
 \be
@@
 \ee
-When decomposed in this way, in order for the full amplitude to be gauge invariant, the polarization stripped building blocks, must obey a set of Ward-Identities between different helicity sectors:
+When decomposed in this way, the polarization stripped building blocks must obey a set of Ward-Identities between different helicity sectors in order for the full amplitude to be gauge invariant,:
  \begin{equation}\label{eq:GIrelA}
@@
 Indeed, as we describe in the Appendix \ref{}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{}, J-theory \cite{}, and self-dual Yang-Mills \cite{}.
+The Feynman rules fo this theory are simply:
+\be
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
+\ee
 Specifically, semi-Abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
@@
 \subsection{Two-loop obstruction}\label{2LoopObstruction}
-At two-loop, introducing terms that conspire with four-point contacts is unavoidable (add diagram). Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
+At two-loop, introducing terms that conspire with four-point contacts is unavoidable.
+At one-loop, we were able to avoid internal contractions of $\bar{A}_\mu A^\mu$ by selecting external states of appropriate weight.
+However, at two-loop when choosing all external $A_\mu$ states, the amplitude vanishes in semi-YM theory:
+\be
+\mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(+,+,+,+)=0
+\ee
+In order to produce non-vanishing interactions, we would need to reintroduce $D$-dimensional vertices from the diagonal group of $G_L\times G_R$.
+Doing so will necessarily introduce internal contractions of $\bar{A}_\mu A^\mu$,
+\be
+\mathcal{A}^{\text{YM}}_{\text{2-loop}}(+,+,+,+)=\doubleBoxObstructionA +\doubleBoxObstructionB+\cdots 
+\ee
+However, this immediately runs into the difficulty of introducing the four-point contact needed for color-kinematics to be satisfied on all internal edges.
+To do this prescriptively would require knowledge of the full kinematic algebra for Yang-Mills off-shell.
+Since this is presently unavailable, to approach the problem of two-loop construction, we instead employ an ansatz based approach.
 \section{Two-loop bootstrap}\label{2loopBoot}
@@
 \ee
-Using this definition on the final \jm{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
+Using this definition on the first self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
 \be\label{SDEOM}
@@
 In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
-In this form, we can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
+We can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
 Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.
@@
 \be
-\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i \varepsilon_3 (p_1-p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
+\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i (\varepsilon_3 p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
 \ee
@@
 
-This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z-\bar{Z}$ on-shell states. As such, the single vertex in this theory is the same as for YZ theory: 
+This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z$-$\bar{Z}$ on-shell states.
+As such, the single vertex in this theory is the same as the pure vector vertex of YZ theory in Lorenz gauge, where $\partial_\mu J^\mu = 0$:
 \be

### 2023-09-19 notes/2loopNLSM.tex
added citations - my hands are off

@@
 
-  We catalog and analyze ?4? theories which all manifest the duality
-  between color and kinematics both at tree and one-loop level.  We
-  identify a unifying theory, \emph{semi-abelian} Yang--Mills, from
-  which all four of the theories can be extracted.  Joint
+  We make progress towards understanding how color-dual representations must be constructed at the multi-loop level. First
+  identify a cubic theory, \emph{semi-abelian} Yang--Mills, that unifies many of the color-dual theories constructed in the literature, and provides a construction of color-dual numerators at one-loop directly from Feynman rules.
+Joint
   consideration of these theories highlights that the lifting of
@@
 \setstackgap{L}{7pt}
-\newpage
+
 \section{Introduction}\label{intro}
 Since the turn of the century, our understanding of the $S$-matrix and its hidden structures has expanded dramatically.
-At the heart of this progress is the mantra that physical observables are simpler when studied on-shell.
+At the heart of this progress is the mantra that physical observables are simpler when studied on-shell \cite{Parke:1986gb,TasiLance,Cheung:2017pzi}.
 However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell simplicity at the heart of many quantum field theories.
-A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors.
-When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{}.
-
-However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, color-kinematics remains a conjecture at loop level.
-Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{}.
-In this work, we use the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven to permit color-dual representations at tree-level \cite{}, as case studies for advancing our understanding of the kinematic algebra to the multi-loop level.
+A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ,Bern:2010ue,BCJreview}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors.
+When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{BCJ,Bern:2010ue}.
+
+However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{FiveLoopN4,GeneralizedDoubleCopyFiveLoops,Bern:2018jmv,Carrasco:2021otn}, color-kinematics remains a conjecture at loop level.
+Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{Mogull:2015adi,Johansson:2017bfl,KalinN2TwoLoop}.
+In this work, we use the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven to permit color-dual representations at tree-level \cite{Feng:2010my,Cachazo:2014xea}, as case studies for advancing our understanding of the kinematic algebra to the multi-loop level.
 
@@
 Faced with this obstruction, we study the multi-loop sector of both NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz based color-dual bootstrap.
-In contrast to much of the available literature on construction of color-dual integrands at two-loop \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional.
+In contrast to much of the available literature on construction of color-dual integrands at two-loop \cite{Bern:2013yya,Mogull:2015adi,Johansson:2017bfl}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional.
 This makes our methods and results particularly well suited for algorithmically extracting rational terms from the $D$-dependence of dimensionally regulated loop momenta.
@@
 Concretely, we find a sharp failure point between the ``bowtie'' cut, and the following jacobi triple:
-\begin{eBox}
 \begin{equation}
@@
 \end{equation}
-\end{eBox}
 We comment on the implications of this finding in \cref{conclusions}, and discuss alternative approaches where one must relax field theoretic locality in order to accommodate the construction of globally color-dual multi-loop integrands.
@@
 The KK relations are generic to any theory with purely adjoint particles.
-Color-kinematics duality implies that the KK basis is overcomplete and can be reduced to a basis of $(n-3)!$ amplitudes via the fundamental BCJ identities \cite{BCJ}
+Color-kinematics duality implies that the KK basis is overcomplete and can be reduced to a basis of $(n-3)!$ amplitudes via the fundamental BCJ identities \cite{BCJ,Feng:2010my}
 \be
@@
 Typically when one goes about construction color-dual theories directly from a set of cubic interactions, higher point Jacobi and antisymmetry constraints require introducing additional operators.
-See refs \cite{} for some recent examples.
+See refs \cite{Ben-Shahar:2022ixa} for some recent examples.
 Indeed, as we'll show in \cref{sec:cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point.
@@
 Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents.
-Indeed, as we describe in the Appendix \ref{}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{}, J-theory \cite{}, and self-dual Yang-Mills \cite{}.
+Indeed, as we describe in the Appendix \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{Cheung:2016prv}, J-theory \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills \cite{Monteiro2011pc}.
 The Feynman rules fo this theory are simply:
@@
 Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM).
-At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{}:
+At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{Monteiro2011pc}:
 \be
@@
 \ee
-where $\mathcal{O}_i$ are the basis tensors of \cite{}, and $ \mathcal{R}_i$ is a rational function of momenta of the form;
+where $\mathcal{O}_i$ are the basis tensors of \cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}_i$ is a rational function of momenta of the form;
 \be

### 2023-09-19 notes/2loopNLSM.tex
Alex partial readthrough.

@@
 
-  We make progress towards understanding how color-dual representations must be constructed at the multi-loop level. First
-  identify a cubic theory, \emph{semi-abelian} Yang--Mills, that unifies many of the color-dual theories constructed in the literature, and provides a construction of color-dual numerators at one-loop directly from Feynman rules.
-Joint
-  consideration of these theories highlights that the lifting of
-  one-loop color-kinematics dual numerators to two loops may be just
-  as challenging as the step from tree level to one loop.  As a first
-  step in understanding the two-loop challenge, we construct
-  color-dual two-loop four-point non-linear sigma model (NLSM)
-  numerators using generalized unitarity methods.  The double-copy of
-  the constructed NLSM numerators with themselves, $\mathcal{N}=0$
-  Yang--Mills, and $\mathcal{N}=4$ Yang--Mills correctly reproduce the
-  known physical unitarity cuts of special Gallileons, Born-Infeld
-  theory, and Dirac-Born-Infeld-Volkov-Akulov theory, respectively.
-  These NLSM numerators are in explicit tension with generalizations
-  of the one-loop NLSM numerators. \ace{I realize that we all know
-    this, but does/will a statement to this effect actually make it
-    into the draft?}  Additionally, we revisit the two-loop four-point
+  We make progress towards understanding how color-dual
+  representations must be constructed at the multi-loop level. First
+  we identify a cubic theory, \emph{semi-abelian} Yang--Mills, that
+  unifies many of the color-dual theories constructed in the
+  literature, and provides a construction of color-dual numerators at
+  one-loop directly from Feynman rules. Joint consideration of these
+  theories highlights that the lifting of one-loop color-kinematics
+  dual numerators to two loops may be just as challenging as the step
+  from tree level to one loop.  As a first step in understanding the
+  two-loop challenge, we construct color-dual two-loop four-point
+  non-linear sigma model (NLSM) numerators using generalized unitarity
+  methods.  The double-copy of the constructed NLSM numerators with
+  themselves, $\mathcal{N}=0$ Yang--Mills, and $\mathcal{N}=4$
+  Yang--Mills correctly reproduce the known physical unitarity cuts of
+  special Gallileons, Born-Infeld theory, and
+  Dirac-Born-Infeld-Volkov-Akulov theory, respectively.  These NLSM
+  numerators are in explicit tension with generalizations of the
+  one-loop NLSM numerators. \ace{I realize that we all know this, but
+    does/will a statement to this effect actually make it into the
+    draft?}  Additionally, we revisit the two-loop four-point
   Yang--Mills problem in order to identify the exact point of
@@
 \section{Introduction}\label{intro}
-Since the turn of the century, our understanding of the $S$-matrix and its hidden structures has expanded dramatically.
-At the heart of this progress is the mantra that physical observables are simpler when studied on-shell \cite{Parke:1986gb,TasiLance,Cheung:2017pzi}.
-However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell simplicity at the heart of many quantum field theories.
-A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ,Bern:2010ue,BCJreview}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors.
-When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{BCJ,Bern:2010ue}.
-
-However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{FiveLoopN4,GeneralizedDoubleCopyFiveLoops,Bern:2018jmv,Carrasco:2021otn}, color-kinematics remains a conjecture at loop level.
-Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{Mogull:2015adi,Johansson:2017bfl,KalinN2TwoLoop}.
-In this work, we use the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven to permit color-dual representations at tree-level \cite{Feng:2010my,Cachazo:2014xea}, as case studies for advancing our understanding of the kinematic algebra to the multi-loop level.
-
-We begin with an overview of color-kinematics duality in \cref{background}.
-We then construct a manifestly color-dual theory in \cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point numerators for both NLSM and the self-dual sector of Yang-Mills through one-loop.
-The construction of this theory, which we dub \textit{semi-abelian Yang-Mills}, relies on isolating the cubic sector of pure Yang-Mills amplitudes from the four-point contacts that are needed to fully realize non-abelian gauge symmetry.
-Despite the potency of this theory at one-loop, the construction runs into an obstruction at two-loop, which we describe in \cref{2LoopObstruction}.
-
-Faced with this obstruction, we study the multi-loop sector of both NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz based color-dual bootstrap.
-In contrast to much of the available literature on construction of color-dual integrands at two-loop \cite{Bern:2013yya,Mogull:2015adi,Johansson:2017bfl}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional.
-This makes our methods and results particularly well suited for algorithmically extracting rational terms from the $D$-dependence of dimensionally regulated loop momenta.
-We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public.
-
-With this solver, we are able to compute a two-loop integrand for NLSM that globally manifests the duality off-shell.
-This represents a new benchmark for color-dual representations in non-supersymmetric gauge theories.
-However in contrast, we find surprisingly that Yang-Mills does not permit a globally color-dual representation, even when considering the most general polynomial ansatz of Lorentz covariant kinematics.
-Concretely, we find a sharp failure point between the ``bowtie'' cut, and the following jacobi triple:
+Since the turn of the century, our understanding of the $S$-matrix and
+its hidden structures has expanded dramatically. At the heart of this
+progress is the mantra that physical observables are simpler when
+studied on-shell
+\cite{Parke:1986gb,TasiLance,Cheung:2017pzi}. However, while plugging
+in on-shell states certainly offers a path towards taming the
+factorial growth of Feynman diagrams, it also obscures the off-shell
+simplicity at the heart of many quantum field theories. A shining
+example of this hidden structure is the duality between color and
+kinematics \cite{BCJ,Bern:2010ue,BCJreview}, which states that the
+kinematic numerators of gauge theory amplitudes can be rearranged to
+obey the same algebraic identities as the constituent color
+factors. When this duality is realized globally off-shell, it
+dramatically decreases the combinatorial complexity posed by integrand
+construction, and offers a path towards efficient assembly of quantum
+gravity integrands directly from simpler gauge theory building blocks
+via the double copy \cite{BCJ,Bern:2010ue}.
+
+However, despite the tremendous success in leveraging this duality to
+compute gauge and gravity observables to high orders in perturbation
+theory \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv,
+  Carrasco:2021otn}, color-kinematics remains a conjecture at loop
+level. Indeed, there are many examples in the literature where
+identifying color-dual representations beyond one-loop has posed a
+formidable challenge
+\cite{Mogull:2015adi,Johansson:2017bfl,KalinN2TwoLoop} \ace{BDN might
+  fit better here rather than the 2loop SQCD}. In this work, we use
+the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven
+to permit color-dual representations at tree-level
+\cite{Feng:2010my,Cachazo:2014xea}, as case studies for advancing our
+understanding of the kinematic algebra to the multi-loop level.
+
+We begin with an overview of color-kinematics duality in
+\cref{background}. We then construct a manifestly color-dual theory in
+\cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point
+numerators for both NLSM and the self-dual sector of Yang-Mills
+through one-loop. The construction of this theory, which we dub
+\textit{semi-abelian Yang-Mills}, relies on isolating the cubic sector
+of pure Yang-Mills amplitudes from the four-point contacts that are
+needed to fully realize non-abelian gauge symmetry. Despite the
+potency of this theory at one-loop, the construction runs into an
+obstruction at two-loop, which we describe in \cref{2LoopObstruction}.
+
+Faced with this obstruction, we study the multi-loop sector of both
+NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz based
+color-dual bootstrap. In contrast to much of the available literature
+on construction of color-dual integrands at two-loop
+\cite{Bern:2013yya,Mogull:2015adi,Johansson:2017bfl}, our results are
+completely agnostic to the spacetime dimension; all the polarizations
+and momenta appearing in our construction will remain formally
+$D$-dimensional. This makes our methods and results particularly well
+suited for algorithmically extracting rational terms from the
+$D$-dependence of dimensionally regulated loop momenta. We are able to
+achieve this by employing a custom solver, \texttt{FiniteFieldSolve},
+which will soon be made public. \ace{This either needs an extra
+  context sentence, or moved out of the intro.}
+
+With this solver, we are able to compute a two-loop integrand for NLSM
+that globally manifests the duality off-shell. This represents a new
+benchmark for color-dual representations in non-supersymmetric gauge
+theories. However in contrast, we find surprisingly that Yang-Mills
+does not permit a globally color-dual representation, \ace{Maybe tone
+  down surprise and ref BDN} even when considering the most general
+polynomial ansatz of Lorentz covariant kinematics. Concretely, we find
+a sharp failure point between the ``bowtie'' cut, and the following
+jacobi triple:
 \begin{equation}
@@
 \end{equation}
-We comment on the implications of this finding in \cref{conclusions}, and discuss alternative approaches where one must relax field theoretic locality in order to accommodate the construction of globally color-dual multi-loop integrands.
+We comment on the implications of this finding in \cref{conclusions},
+and discuss alternative approaches where one must relax field
+theoretic locality in order to accommodate the construction of
+globally color-dual multi-loop integrands.
 
 \section{Background}\label{background}
-To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions.
-We then detail a color-dual boostrap approach for constructing integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM.
+To set the stage, in this section we provide an overview of
+color-kinematics duality -- both the on-shell and off-shell
+constructions. We then detail a color-dual boostrap approach for
+constructing integrands in theories for which the off-shell kinematic
+algebra has not yet been identified, like Yang-Mills and NLSM.
 \subsection{Color-dual Amplitudes}\label{onShellCK}
 
-I think this belongs in another section...
-Why DC is cool:
-1) Reduction in computational complexity.
-Off-shell high spin is terrible.
-Gravity has infinitely many very complex Feynman rules as a result of gauge redundancy but YM only has two relatively simple Feynman rules.
-2) DC points to deep structure hidden in Lagrangian formulation.
-
-Color-kinematics duality is a statement about the off-shell graphical simplicity that manifest redundancy in the on-shell observables of gauge and gravity theories.
-Ignoring factors of $i$ and the coupling constant, a generic $m$-point $L$-loop amplitude in a color-dual theory -- such as NLSM, YM, or bi-adjoint scalar theory -- can be written as
-\be
+%I think this belongs in another section...
+%Why DC is cool:
+%1) Reduction in computational complexity.
+%Off-shell high spin is terrible.
+%Gravity has infinitely many very complex Feynman rules as a result of gauge redundancy but YM only has two relatively simple Feynman rules.
+%2) DC points to deep structure hidden in Lagrangian formulation.
+
+Color-kinematics duality is a statement about the off-shell graphical
+simplicity that manifest redundancy in the on-shell observables of
+gauge and gravity theories. Ignoring factors of $i$ and the coupling
+constant, a generic $m$-point $L$-loop amplitude in a color-dual
+theory -- such as NLSM, YM, or bi-adjoint scalar
+theory\ace{technically this is true as written for any theory.  In
+  fact we slip that type of disclaimer in quite a lot throughout the
+  rest of the section} -- can be written as
+\begin{equation}
 \mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma n_\Gamma}{d_\Gamma} .
-\ee
-Here the spacetime dimension is $D$.
-Even though the underlying theory may have quartic (or higher multiplicity) vertices, it is possible to multiply and divide by propagators so that the sum runs over only purely cubic graphs $\Gamma$.
-Overcounting is removed by the internal symmetry factor $S_\Gamma$, which tracks the number of graph symmetries with external legs held fixed.
-The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.
-However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2023vjg, Carrasco:2020ywq}.}
-the denominator $d_\Gamma$ is the product of propagators associated with the graph $\Gamma$, and the numerator $n_\Gamma$ is all of the remaining kinematic factors including dot products of momenta and polarization vectors.
-
-The color factors $c_\Gamma$ are not independent and are related to one another via a set of Jacobi identities that look schematically like
-\be
+\end{equation}
+Here the spacetime dimension is $D$.  Even though the underlying
+theory may have quartic (or higher multiplicity) vertices, it is
+possible to multiply and divide by propagators so that the sum runs
+over only purely cubic graphs $\Gamma$.  Overcounting is removed by
+the internal symmetry factor $S_\Gamma$, which tracks the number of
+graph symmetries with external legs held fixed.  The color factor
+$c_\Gamma$ is the string of structure constants $f^{abc}$ associated
+with the graph $\Gamma$,\footnote{This paper is focused on theories
+  with particles that transform in the adjoint.  However, the double
+  copy can be applied to a far more diverse set of theories with
+  particles that transform in the fundamental or more diverse
+  representations, see for example \cite{Johansson:2017srf,
+    Johansson2014zca, Johansson:2015oia, Johansson:2019dnu,
+    Carrasco:2023vjg, Carrasco:2020ywq}.}  the denominator $d_\Gamma$
+is the product of propagators associated with the graph $\Gamma$, and
+the numerator $n_\Gamma$ is all of the remaining kinematic factors
+including dot products of momenta and polarization vectors.
+
+The color factors $c_\Gamma$ are not independent and are related to
+one another via a set of Jacobi identities that look schematically
+like
+\begin{equation}
 c_i+c_j+c_k=0,
-\ee
-where $i$, $j$, and $k$ are three graphs.
-Example Jacobi relations are presented in detail in \cref{sec:bootstrap}.
-Color-kinematics duality states that there exists a way to rearrange factors between the various kinematic numerators $n_\Gamma$ such that the numerators obey all of the same Jacobi identities as the color factors
-\be
+\end{equation}
+where $i$, $j$, and $k$ are three graphs.  Example Jacobi relations
+are presented in detail in \cref{sec:bootstrap}.  Color-kinematics
+duality states that there exists a way to rearrange factors between
+the various kinematic numerators $n_\Gamma$ such that the numerators
+obey all of the same Jacobi identities as the color factors
+\begin{equation}
 n_i +n_j +n_k=0.
-\ee
-If color-kinematics duality can be achieved at the off-shell level, then the kinematic numerators should satisfy an algebra just like the color factors.
-In theories where the kinematic algebra is known, it is often the algebra of volume preserving diffeomorphisms \cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz, Cheung:2021zvb, Cheung:2022mix}.
-As a simple example, color-dual numerators for 4pt pion scattering at tree level are
+\end{equation}
+If color-kinematics duality can be achieved at the off-shell level,
+then the kinematic numerators should satisfy an algebra just like the
+color factors.  In theories where the kinematic algebra is known, it
+is often the algebra of volume preserving diffeomorphisms
+\cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz,
+  Cheung:2021zvb, Cheung:2022mix}.  As a simple example, color-dual
+numerators for 4pt pion scattering at tree level are
 \begin{align}
@@
 \end{align}
-where the coupling has been normalized away.
-These numerators sum to zero by explicit calculation.
-Note that the $s$-channel numerator contains an explicit factor of $s$ that cancels with the propagator and the same goes for the $t$- and $u$-channels so that the net result is a local function, just as one would expect for the pion tree amplitude.
-
-Once color-dual numerators $n_\Gamma$ have been found, they can be used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a \emph{different} amplitude to produce the corresponding amplitude in the double-copy theory
-\be\label{DCconstruction}
-\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)} ~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma \tilde{n}_\Gamma}{d_\Gamma}.
-\ee
-Importantly, the $\tilde{n}_\Gamma$ do not need to respect color-kinematics duality.
-The prototypical example of the double-copy is that YM double copied with YM results in gravity where the gauge invariance of each separate gluon produces the diffeomorphism invariance of the graviton.
-The double copy can be proven at tree level using the KLT relations but there is significant evidence that the double copy persists to all loop orders \cite{KLT, KiermaierTalk} \citepls{Any loop papers we want?}.
-In addition to pointing at deep structure hidden in the Lagrangian for gravity, the double copy is immensely useful at a utilitarian level since it is much more efficient at producing $\mathcal{M}_m^L$ than traditional methods like Feynman rules.
-
-Many of the 1-loop results presented in \cref{sec:cubic} are informed by the tree-level double-copy so we will review the tree case here.
+where the coupling has been normalized away.  These numerators sum to
+zero by explicit calculation.  Note that the $s$-channel numerator
+contains an explicit factor of $s$ that cancels with the propagator
+and the same goes for the $t$- and $u$-channels so that the net result
+is a local function, just as one would expect for the pion tree
+amplitude.
+
+Once color-dual numerators $n_\Gamma$ have been found, they can be
+used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a
+\emph{different} amplitude to produce the corresponding amplitude in
+the double-copy theory \be\label{DCconstruction}
+\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
+\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma
+  \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)}
+~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
+\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma
+  \tilde{n}_\Gamma}{d_\Gamma}.
+\end{equation}
+Importantly, the $\tilde{n}_\Gamma$ do not need to respect
+color-kinematics duality.  The prototypical example of the double-copy
+is that YM double copied with YM results in gravity where the gauge
+invariance of each separate gluon produces the diffeomorphism
+invariance of the graviton.  The double copy can be proven at tree
+level using the KLT relations but there is significant evidence that
+the double copy persists to all loop orders \cite{KLT, KiermaierTalk}
+\citepls{Any loop papers we want?}.  In addition to pointing at deep
+structure hidden in the Lagrangian for gravity, the double copy is
+immensely useful at a utilitarian level since it is much more
+efficient at producing $\mathcal{M}_m^L$ than traditional methods like
+Feynman rules.
+
+Many of the 1-loop results presented in \cref{sec:cubic} are informed
+by the tree-level double-copy so we will review the tree case here.
 The color structure of tree-level amplitudes is particularly simple.
-A fully color dressed tree amplitude $\mathcal{A}_n$ in YM, NLSM, or bi-adjoint scalar theory can be decomposed in terms of the trace basis
-\be
+A fully color dressed tree amplitude $\mathcal{A}_n$ in YM, NLSM, or
+bi-adjoint scalar theory can be decomposed in terms of the trace basis
+\begin{equation}
   \mathcal{A}_n = \sum \limits_{\sigma\in S_{n-1}} \text{Tr}(T^{a_{\sigma_1}} T^{a_{\sigma_2}}...T^{a_{\sigma_{n-1}}} T^{a_n}) A_n[\sigma_1, \sigma_2,...\sigma_{n-1}, n],
-\ee
-where $T^a$ are generators of the gauge group and, because of the cyclicity of the trace, one of the legs is held fixed so that the sum runs over the $(n-1)!$ permutations of the remaining external legs.
-The coefficients of the color factors are the color-ordered partial amplitudes $A_n[...]$.
-Any tree-level color factor can be converted into a linear combination of Del Duca-Dixon-Maltoni (DDM) half-ladder color factors
-\be
+  \label{eq:trace-basis}
+\end{equation}
+where $T^a$ are generators of the gauge group and, because of the
+cyclicity of the trace, one of the legs is held fixed so that the sum
+runs over the $(n-1)!$ permutations of the remaining external legs.
+The coefficients of the color factors are the color-ordered partial
+amplitudes $A_n[...]$.  Any tree-level color factor can be converted
+into a linear combination of Del Duca-Dixon-Maltoni (DDM) half-ladder
+color factors
+\begin{equation}
 \text{DDM}[a_1, a_2,... a_n] \equiv f^{a_1 a_2 b_1} f^{b_1 a_3 b_2} f^{b_2 a_4 b_3}...f^{b_{n-3} a_{n-1} a_n}
-\ee
+\end{equation}
 associated with the graph
-\be
+\begin{equation}
 \halfLadder
-\ee
+\end{equation}
 by repeated application of the Jacobi identity \cite{DixonMaltoni}.
 The fully color-dressed tree amplitude can then be re-expressed as
-\be
+\begin{equation}
   \mathcal{A}_n = \sum \limits_{\sigma\in S_{n-2}} \text{DDM}[a_1, a_{\sigma_2}, a_{\sigma_3}, a_{\sigma_{n-1}}, a_n]  A_n[1, \sigma_2,...\sigma_{n-1}, n]
-\ee
-with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$ terms, indicating that there are additional relations -- the Kleiss-Kuijf (KK) relations -- amongst the partial amplitudes \cite{Kleiss:1988ne}.
-The KK relations are generic to any theory with purely adjoint particles.
-Color-kinematics duality implies that the KK basis is overcomplete and can be reduced to a basis of $(n-3)!$ amplitudes via the fundamental BCJ identities \cite{BCJ,Feng:2010my}
-\be
+  \label{eq:ddm-basis}
+\end{equation}
+with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$
+terms, indicating that there are additional relations -- the
+Kleiss-Kuijf (KK) relations \cite{Kleiss:1988ne} -- amongst the
+partial amplitudes appearing in the right-hand side of
+\cref{eq:trace-basis}.  The KK relations are generic to any theory
+with purely adjoint particles.  Color-kinematics duality further
+implies that the KK basis is overcomplete and can be reduced to a
+basis of $(n-3)!$ amplitudes via the fundamental BCJ identities
+\cite{BCJ,Feng:2010my}
+\begin{equation}
 \sum \limits_{i=2}^{n-1} k_1 \cdot (k_2+...+k_i) A_n[2,...,i,1,i+1,...,n] =0.
-\ee
-In terms of constructing explicit color-dual solutions at tree level, it is enough to specify the numerator of the half ladder because any diagram can be reduced to a half ladder through successive applications of the Jacobi identity.
-At 1-loop, every diagram can be related to one topology as well, in this case the $n$-gon, but the pattern does not persist to 2-loops.
+\end{equation}
+In terms of constructing explicit color-dual solutions at tree level,
+it is enough to specify the numerator of the half ladder because any
+diagram can be reduced to a half ladder through successive
+applications of the Jacobi identity.  At 1-loop, every diagram can be
+related to one topology as well, in this case the $n$-gon, but the
+pattern does not persist to 2-loops.
 
 \subsection{Color-dual Lagrangians}\label{offShellCK}
-While BCJ relations is an on-shell statement about the color-dual nature of scattering amplitudes, one might aspire to hard code color-kinematics duality by realizing an off-shell Lagrangian description of the theory.
-The double-copy construction of \ref{DCconstruction} would suggest a manifestly cubic Lagrangian of the form:
-\be
+While the BCJ relations are an on-shell statement about the color-dual
+nature of scattering amplitudes, one might aspire to hard code
+color-kinematics duality by realizing an off-shell Lagrangian
+description of the theory. The double-copy construction of
+\cref{DCconstruction} would suggest a manifestly cubic Lagrangian of
+the form:
+\begin{equation}
 \mathcal{L} = P_V^{ab}P_W^{ij}\mathcal{O}^a_i \Box \mathcal{O}^b_j +  V^{abc} W^{ijk}\mathcal{O}^a_i \mathcal{O}^b_j \mathcal{O}^c_k
-\ee
-where $V^{abc}$ and $W^{ijk}$ are cubic Feynman rules mixing field operators $\mathcal{O}^{a}_i$ indexed by quantum numbers $a$ and $i$.
-We have introduced $P_V^{ab}$ and $P_W^{ij}$ projection operators to encode non-local kinetic structure that could in principle participate in the construction.
-Should the off-shell Feynman rules of this cubic theory be antisymmetric and satisfy Jacobi identities on all internal edges,
+\end{equation}
+where $V^{abc}$ and $W^{ijk}$ are cubic Feynman rules mixing field
+operators $\mathcal{O}^{a}_i$ indexed by quantum numbers $a$ and
+$i$. We have introduced $P_V^{ab}$ and $P_W^{ij}$ projection operators
+to encode non-local kinetic structure that could in principle
+participate in the construction. Should the off-shell Feynman rules of
+this cubic theory be antisymmetric and satisfy Jacobi identities on
+all internal edges,
 \begin{align}
@@
 where 
-\be
+\begin{equation}
 {}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}V^{b_1a_3b_2}\cdots V^{b_{n-3} a_{n-2}a_n}\,.
-\ee
-This is a sufficient condition of the amplitudes to obey BCJ relations.
-Off-shell description of color-dual theories are rare, and only a few examples are available in the literature.
-Typically when one goes about construction color-dual theories directly from a set of cubic interactions, higher point Jacobi and antisymmetry constraints require introducing additional operators.
-See refs \cite{Ben-Shahar:2022ixa} for some recent examples.
-Indeed, as we'll show in \cref{sec:cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point.
-Absent information about the kinematic algebra, one can make progress in the construction of loop-level color-dual amplitudes by employing a color-dual bootstrap.
+\end{equation}
+This is a sufficient condition of the amplitudes to obey BCJ
+relations. \ace{Reword previous 2 sentences} Off-shell descriptions of
+color-dual theories are rare, and only a few examples are available in
+the literature \cite{Monteiro2011pc, Cheung:2016prv, Cheung:2021zvb,
+  Cheung:2020djz, Ben-Shahar:2022ixa, Ben-Shahar:2021zww,
+  Ben-Shahar:2021doh}\ace{Are these a reasonable
+  collection?  Just grabbed the ones below}. Typically when one goes about constructing color-dual
+theories directly from a set of cubic interactions, higher point
+Jacobi and antisymmetry constraints require introducing additional
+operators. See refs \cite{Ben-Shahar:2022ixa} for some recent
+examples. Indeed, as we'll show in \cref{sec:cubic}, Yang-Mills
+requires introducing a cubic 2-form interaction in order to manifest
+the kinematic algebra just at four-point. Absent information about the
+kinematic algebra, one can make progress in the construction of
+loop-level color-dual amplitudes by employing a color-dual bootstrap.
+
 \subsection{Color-dual Bootstrap}
@@
 
-Aside from a few special theories that permit an off-shell Lagrangian description \cite{Monteiro2011pc, Cheung:2016prv, Cheung:2021zvb, Cheung:2020djz, Ben-Shahar:2022ixa, Ben-Shahar:2021zww, Ben-Shahar:2021doh}, color-dual integrands are constructed from an ansatz.
-The four conditions we impose on an ansatz are summarized here and elaborated on below.\footnote{The four ansatz conditions are similar to those of Ref.~\cite{Bern:2015ooa} except that the authors demand that the numerators have the same loop power counting as Feynman gauge Feynman rules.
-This is an additional assumption that is most emphatically not made here.}
+Aside from a few special theories that permit an off-shell Lagrangian
+description \cite{Monteiro2011pc, Cheung:2016prv, Cheung:2021zvb,
+  Cheung:2020djz, Ben-Shahar:2022ixa, Ben-Shahar:2021zww,
+  Ben-Shahar:2021doh}, color-dual integrands are constructed from an
+ansatz.  The four conditions we impose on an ansatz are summarized
+here and elaborated on below.\footnote{The four ansatz conditions are
+  similar to those of Ref.~\cite{Bern:2015ooa} except that there
+  authors demand that the numerators have the same loop power counting
+  as Feynman gauge Feynman rules.  This is an additional assumption
+  that is most emphatically not made here.}
 \begin{enumerate}
-\item \textbf{Off-shell Locality}: Diagram numerators are polynomials in momenta and
-  polarizations, \eg the diagrams only have poles given by the
-  propagators of the diagrams.
-  \item  \textbf{Color-kinematics duality}: The numerators obey the same Jacobi identities as the color factors.
-This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
-\item  \textbf{Graph symmetries}: The diagram numerators are only a function of the diagram's topology and labeling.
-Furthermore, the diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
-\item  \textbf{On-shell Unitarity }: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory when internal momenta are taken on-shell.
+\item \textbf{Off-shell Locality}: Diagram numerators are polynomials
+  in momenta and polarizations, \eg the diagrams only have poles given
+  by the propagators of the diagrams.
+\item \textbf{Color-kinematics duality}: The numerators obey the same
+  Jacobi identities as the color factors.  This implicitly requires
+  that the integrand is expressed in terms of purely cubic diagrams.
+\item \textbf{Graph symmetries}: The diagram numerators are only a
+  function of the diagram's topology and labeling.  Furthermore, the
+  diagram numerators are invariant under the automorphisms of the
+  diagrams \emph{including signs that compensate for color-factor sign
+    changes}.
+\item \textbf{On-shell Unitarity }: The cuts of the ansatz must
+  reproduce the physical unitarity cuts of the theory when internal
+  momenta are taken on-shell.
 \end{enumerate}
 
-In order to clarify general statements, the following subsections include examples from a 4pt 2-loop integrand for some color-dual theory like YM or NLSM.
-This is the simplest integrand that demonstrates the full machinery of the color-dual bootstrap.
-All tree and 1-loop processes are generated by single basis diagrams (the half ladder and $n$-gon respectively) so they lack examples of the ``boundary'' Jacobi relations to be described shortly.
-Choosing the 4pt 2-loop integrand also has the advantage that this process appears prominently in this paper.
+In order to clarify general statements, the following subsections
+include examples from a 4-point 2-loop integrand for some generic
+color-dual theory like YM or NLSM.  This is the simplest case that
+demonstrates the full machinery of the color-dual bootstrap.  All tree
+and 1-loop processes are generated by single basis diagrams (the half
+ladder and $n$-gon respectively) so they lack examples of the
+``boundary'' Jacobi relations to be described shortly \ace{This is not
+  strictly true.  Boundary Jacobi occur in 1L when demanding that BEL
+  and/or tadpole are 0.  However, I appreciate that logic that 2L is
+  the first time where an A+A+A=0 Jacobi occurs, rather than A+A=0.}.
+Choosing the 4-point 2-loop integrand also has the advantage that this
+process appears prominently in this paper.
 
@@
 
-The kinematic numerators must be $D$-dimensional, Lorentz invariant, local (polynomial) functions of the graph kinematics with the correct power counting and external states.
-Insisting on a local numerator is partly a matter of convenience as the ansatz for a rational function would quickly grow out of control without a guiding principle for what terms to include.
-Locality is also physically motivated since Feynman rules typically produce polynomial numerators.
-While these assumptions are well motivated from a physical and complexity standpoint, the literature has featured numerators that violate locality, modify naive power counting through the inclusion of higher spin modes, and break manifest Lorentz invariance \cite{Square, WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv, Cheung:2021zvb}.
-These developments suggest that relaxing locality is a viable alternative when the condition proves too stringent for an ansatz.
-We will comment more on locality in \sect{}.
-
-\jm{The next section feels a little redundant and silly sometimes because the integrand, color factors, kinematic numerators, etc.
-were defined a while ago.
-I'm not sure how to merge the two sections though.}
+The kinematic numerators must be $D$-dimensional, Lorentz invariant,
+local (polynomial) functions of the graph kinematics with the correct
+power counting and external states.  Insisting on a local numerator is
+partly a matter of convenience as the ansatz for a rational function
+would quickly grow out of control without a guiding principle for what
+terms to include.  Locality is also physically motivated since Feynman
+rules typically produce polynomial numerators.  While these
+assumptions are well motivated from a physical and complexity
+standpoint, the literature has featured numerators that violate
+locality, modify naive power counting through the inclusion of higher
+spin modes, and break manifest Lorentz invariance \cite{Square,
+  WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ,
+  Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv,
+  Cheung:2021zvb}.  These developments suggest that relaxing locality
+is a viable alternative when the condition proves too stringent for an
+ansatz.  We will comment more on locality in \cref{conclusions}.
+
+\jm{The next section feels a little redundant and silly sometimes
+  because the integrand, color factors, kinematic numerators,
+  etc. were defined a while ago.  I'm not sure how to merge the two
+  sections though.}
 
 \paragraph{Color-kinematics duality}
-
-Color-kinematics duality is a statement about color factors, kinematic numerators, and the accompanying Jacobi relations.
-Adjoint-type color factors are associated with cubic graphs, so satisfying color-kinematics duality implicitly requires expressing the integrand in terms of such graphs.
-As mentioned earlier, this is possible to do even for a theory with quartic (or higher multiplicity) vertices by multiplying and dividing by propagators.
-In the case of the 4pt 2-loop example promised above, there are 14 cubic graph topologies (shown in \cref{fig:MaxCuts}) ignoring tadpoles and bubble on external leg (BEL) graphs.
-
-With the integrand expressed in terms of cubic graphs, it is possible to discuss the main ingredient in color-kinematics duality -- the Jacobi relations.
-The color factors in an integrand obey a set of Jacobi identities.
-Color-kinematics duality states that there \emph{exists} a way of writing the kinematic numerators of the integrand so that they obey the same set of Jacobi identities.
-The Jacobi identities can be divided into two categories:  \emph{defining} relations and \emph{boundary} relations.
-Defining Jacobi relations can be used to express any graph in terms of a basis.
-For example, the double box, crossed box, and penta-triangle are related to each other as follows
-\be % [[11]]
+\begin{figure}
+\centering
+{\MCutC, \MCutD, \sumoCut, \MCutJ,  
+ \\
+  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
+\\
+\MCutI,  \MCutE, \MCutK, 
+\\
+ \MCutL, \MCutG,  \MCutH,
+}
+\caption{The 14 non-pathological 4-point 2-loop cubic diagrams,
+  including all dangling tree diagrams.} \label{fig:MaxCuts}
+  \end{figure}
+
+Color-kinematics duality is a statement about color factors, kinematic
+numerators, and the accompanying Jacobi relations.  Adjoint-type color
+factors are associated with cubic graphs, so satisfying
+color-kinematics duality implicitly requires expressing the integrand
+in terms of such graphs. As mentioned earlier, this is possible to do
+even for a theory with quartic (or higher multiplicity) vertices by
+multiplying and dividing by propagators.  In the case of the 4-point
+2-loop example promised above, there are 14 cubic graph topologies
+(shown in \cref{fig:MaxCuts}) ignoring tadpoles and bubble on external
+leg (BEL) graphs.
+
+With the integrand expressed in terms of cubic graphs, it is possible
+to discuss the main ingredient in color-kinematics duality -- the
+Jacobi relations.  The color factors in an integrand obey a set of
+Jacobi identities.  Color-kinematics duality states that there
+\emph{exists} a way of writing the kinematic numerators of the
+integrand so that they obey the same set of Jacobi identities.  The
+Jacobi identities can be divided into two categories: \emph{defining}
+relations and \emph{boundary} relations.  Defining Jacobi relations
+can be used to express any graph in terms of a basis.  For example,
+the double box, crossed box, and penta-triangle are related to each
+other as follows \be % [[11]]
 \label{eq:TwoLoopJacobiOne}
-\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0,
-\ee
-where the shared propagator is shown in red.
-Using this relation the crossed box can be written (or \emph{defined}) in terms of the other two.
-In this way, all of the 14 cubic 4pt 2-loop topologies can be written in terms of a basis of the double box and penta-triangle.
-(Any two of the double box, crossed box, and penta-triangle would suffice for a basis but the planar basis is chosen for simplicity in this work.)
-The numerator of each of the two basis graphs receives its own ansatz and the numerator of any other graph can be expressed in terms of these two.
+\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0\,,
+\end{equation}
+where the shared propagator is shown in red.  Using this relation the
+crossed box can be written (or \emph{defined}) in terms of the other
+two.  In this way, all of the 14 cubic 4-point 2-loop topologies can be
+written in terms of a basis of the double box and penta-triangle.
+(Any two of the double box, crossed box, and penta-triangle would
+suffice for a basis but the planar basis is chosen for simplicity in
+this work.)  The numerator of each of the two basis graphs receives
+its own ansatz and the numerator of any other graph can be expressed
+in terms of these two.
 
@@
 \JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
-\ee
-where the shared propagator is shown in red as before.
-Each of the crossed box numerators can be written in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator \ansatze{}.
-While defining Jacobi relations simplify how many numerators require \ansatze{}, boundary relations place restrictions on those \ansatze{}.
-In principle there could be Jacobi relations involving tadpoles and BEL graphs, which would be subtle to handle.
-One option is to force the numerators of these graphs to zero.
-However, since these graphs will not contribute to physical unitarity cuts, we take a different approach.
-These graphs are allowed to have non-zero numerators but any Jacobi relations involving them are simply not imposed or solved.
-See Ref.~\cite{Bern:2012uf} for a discussion of BELs in the context of color-kinematics duality.
-
-What has just been described is sometimes referred to as ``global'' color-kinematics duality because the Jacobi identities are solved by a single (global) integrand with off-shell internal lines.
-In order to perform the double copy it is enough to simply satisfy the Jacobi identities on the generalized unitarity cuts, meaning that each graph can be assigned its own ansatz \cite{Bern:2015ooa}.
-If a global solution cannot be found, this is one way to enlarge the ansatz where the other option described above was to incorporate non-local terms in the ``numerators''.
-A globally color-dual integrand is desirable because of its simplicity and because a color-dual Lagrangian would naively produce precisely this object.
+\end{equation}
+where the shared propagator is shown in red as before.  Each of the
+crossed box numerators can be written in terms of the double box and
+penta-triangle so this Jacobi relation places constraints on the basis
+numerator \ansatze{}.  While defining Jacobi relations simplify how
+many numerators require \ansatze{}, boundary relations place
+restrictions on those \ansatze{}.  In principle there could be Jacobi
+relations involving tadpoles and BEL graphs, which would be subtle to
+handle.  One option is to force the numerators of these graphs to
+zero.  However, since these graphs will not contribute to physical
+unitarity cuts, we take a different approach.  These graphs are
+allowed to have non-zero numerators but any Jacobi relations involving
+them are simply not imposed or solved.  See Refs.~\cite{Bern:2012uf,
+  Edison:2022jln} for discussions of BELs in the context of
+color-kinematics duality.
+
+\ace{Awkward phrasing/transition.}  What has just been described is
+sometimes referred to as ``global'' color-kinematics duality because
+the Jacobi identities are solved by a single (global) integrand with
+off-shell internal lines.  In order to perform the double copy it is
+enough to simply satisfy the Jacobi identities on the generalized
+unitarity cuts, meaning that each graph can be assigned its own ansatz
+\cite{Bern:2015ooa}.  If a global solution cannot be found, this is
+one way to enlarge the ansatz where the other option described above
+was to incorporate non-local terms in the ``numerators''.  A globally
+color-dual integrand is desirable because of its simplicity and
+because a color-dual Lagrangian would naively produce precisely this
+object.
 
@@
 
-Every numerator is required to respect all of the symmetries (or automorphisms) of its associated graph.
-Graph symmetries are an avatar of Bose symmetry.
-For a pure ansatz construction it is very reasonable to impose graph symmetries, but color-kinematics duality at tree-level is often achieved at the expense of manifest Bose symmetry \cite{Cheung:2016prv, Cheung:2021zvb, Brandhuber:2021bsf, Edison:2020ehu}.
-In an ansatz construction graph symmetries are imposed for \emph{every} graph, not just the basis graphs.
+Every numerator is required to respect all of the symmetries (or
+automorphisms) of its associated graph.  Graph symmetries are an
+avatar of Bose symmetry.  For a pure ansatz construction it is very
+reasonable to impose graph symmetries, but color-kinematics duality at
+tree-level is often achieved at the expense of manifest Bose symmetry
+\cite{Cheung:2016prv, Cheung:2021zvb, Brandhuber:2021bsf,
+  Edison:2020ehu}.  In an ansatz construction graph symmetries are
+imposed for \emph{every} graph, not just the basis graphs.
 %For example, the symmetries of the crossed box are spanned by
-%\be
+%\begin{equation}
 %\CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{3}{4} \text{ and } \CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{4}{3}
-%\ee
-For example, the symmetries of the crossed box
-\be
+% \end{equation}
+\ace{is there a reason we commented out this diagram?}  For example,
+the symmetries of the crossed box
+\begin{equation}
 \CrossedBoxGraphSym{1}{2}{3}{4}
-\ee
+\end{equation}
 are spanned by $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
@@
 Furthermore, care must be taken with the signs in a symmetry relation.
-To compensate for the antisymmetric color factors, $f^{abc}$, graph vertices are all totally antisymmetric and hence have signs built into their orientations.
-Once the signs are included in the symmetry relations, the crossed box can be expressed in terms of the double box and penta-triangle, thus imposing non-trivial constraints on the ansatz.
+To compensate for the antisymmetric color factors, $f^{abc}$, graph
+vertices are all totally antisymmetric and hence have signs built into
+their orientations.  Once the signs are included in the symmetry
+relations, the crossed box can be expressed in terms of the double box
+and penta-triangle, thus imposing non-trivial constraints on the
+ansatz. \ace{I'm not quite sure why the signs are mentioned in the
+  previous sentence?}
 
@@
 
-The final constraints comes from ensuring that the ansatz correctly reproduces the generalized unitarity cuts of the desired theory, thus guaranteeing that the numerators encode the correct physical, theory-dependent information.
-Generalized unitarity methods has been reviewed in many places so we will be light on details here \cite{BCFUnitarity, BernHuangReview, Bern:2015ooa, Bourjaily:2017wjl, JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview, Edison:2022jln}.
-\ace{Here is a semi-random collection of unitarity-related citations.  Probably want to bulk it up a bit more.}
-Recently, generalized unitarity was optimized for even-multiplicity theories like NLSM \cite{Carrasco:2023qgz}.
-
-Generalized unitarity equates products of on-shell tree amplitudes, encoded via
-a graph $\gamma$, to sums over compatible\footnote{A diagram $g$ is compatible with the
-  cut diagram $\gamma$ if $g$ is isomorphic to $\gamma$ or to any of
-  the additional factorization channels of $\gamma$. } diagram
-numerators evaluated on the support of the on-shell conditions and
-weighted by their uncut propagators
+The final constraints comes from ensuring that the ansatz correctly
+reproduces the generalized unitarity cuts of the desired theory, thus
+guaranteeing that the numerators encode the correct physical,
+theory-dependent information.  Generalized unitarity methods has been
+reviewed in many places so we will be light on details here
+\cite{BCFUnitarity, BernHuangReview, Bern:2015ooa, Bourjaily:2017wjl,
+  JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview,
+  Edison:2022jln, Edison:2022jln}.  \ace{Here is a semi-random
+  collection of unitarity-related citations.  Probably want to bulk it
+  up a bit more.}  Recently, generalized unitarity was optimized for
+even-multiplicity theories like NLSM \cite{Carrasco:2023qgz}.
+
+Generalized unitarity equates products of on-shell tree amplitudes,
+encoded via a graph $\gamma$, to sums over compatible\footnote{A
+  diagram $g$ is compatible with the cut diagram $\gamma$ if $g$ is
+  isomorphic to $\gamma$ or to any of the additional factorization
+  channels of $\gamma$. } diagram numerators evaluated on the support
+of the on-shell conditions and weighted by their uncut propagators
 \begin{equation}
@@
 \textcolor{ucp-color}{uncut propagators}.  From now on we will leave
-the cut $\delta(\ell^2)$s implicit.
-\jm{Again, I love the colors!  Would it be possible to add $\ell$ labels to the RHS of \cref{eq:example-cut-sum} to show what $\ell_5$, $\ell_6$... are?}
+the cut $\delta(\ell^2)$s implicit.  \jm{Again, I love the colors!
+  Would it be possible to add $\ell$ labels to the RHS of
+  \cref{eq:example-cut-sum} to show what $\ell_5$, $\ell_6$... are?}
+\ace{It is doable, will work on it once our text is a bit more happy}
 
@@
 Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
-inserting color-ordered amplitudes in the product of trees, and
-restricting the set of compatible diagrams to those whose color
-factors reduce to the appropriate DDM element when summing over
-\emph{only the uncut color contractions}.  In this situation, the
-color becomes an overall factor on the entire equality and thus can be
-ignored.  Cuts that are organized in this manner are known as
-``color-ordered'' cuts, in the same sense as color-ordered tree
-amplitudes.  Since the DDM basis (and dual Kleiss-Kuijf amplitude
-basis \cite{Kleiss:1988ne}) have $(n-2)!$ elements, one generally
-needs to evaluate that many separate color-orderings of the same cut.
-\jm{Don't you need $(n-2)!$ for each blob in the cut?
-So you need to evaluate $(n_1-2)!
-(n_2-2)!...$ cuts where $n_1$, $n_2$...
-are the multiplicities of the blobs.}
-As an example, consider the ``bowtie'' cut topology -- one of
-the factorization channels of the iterated unitarity cut -- which has
-two topologically distinct color-ordered expansions
+inserting color-ordered amplitudes, a la the right hand side of
+\cref{eq:ddm-basis} in the product of trees, and restricting the set
+of compatible diagrams to those whose color factors reduce to the
+appropriate DDM element when summing over \emph{only the uncut color
+  contractions}.  In this situation, the color becomes an overall
+factor on the entire cut equality and thus can be ignored.  Cuts that
+are organized in this manner are known as ``color-ordered'' cuts, in
+the same sense as color-ordered tree amplitudes.  Since the DDM basis
+(and dual Kleiss-Kuijf amplitude basis \cite{Kleiss:1988ne}) have
+$(n-2)!$ elements, one generally needs to evaluate that many separate
+color-orderings of the same cut. \jm{Don't you need $(n-2)!$ for each
+  blob in the cut?  So you need to evaluate $(n_1-2)! (n_2-2)!...$
+  cuts where $n_1$, $n_2$... are the multiplicities of the
+  blobs.}\ace{Yes.  Lets figure out a way to word it.} As an example,
+consider the ``bowtie'' cut topology -- one of the factorization
+channels of the iterated unitarity cut -- which has two topologically
+distinct color-ordered expansions
 \begin{equation}
@@
 \end{equation}
-which serve as a complete basis for the full cut.
-
-Even though unitarity methods aim to generate loop-level data from well-defined on-shell information, the procedure can encounter subtleties.
-Beginning at one loop, there are classes of cuts that are
+which serve as a complete basis for the full cut.  \ace{One of the
+  diagrams here got shifted around somehow.  Probably need to rebuild
+  the whole fig manifest}
+
+Even though unitarity methods aim to generate loop-level data from
+well-defined on-shell information, the procedure can encounter
+subtleties.  Beginning at one loop, there are classes of cuts that are
 difficult to properly define due to hidden non-physical singularities.
@@
 \begin{equation}
-\frac{\delta(\textcolor{cut-color}{k_4^2})}{\textcolor{ucp-color}{s\, k_4^2}}
+\frac{\delta(\textcolor{cut-color}{k_4^2})}{s\,\textcolor{ucp-color}{ k_4^2}}
 n \left[
@@
     \draw[ultra thick] (e1)--(i1)--(i2)--(i3) to [out=80,in=100,min distance=0.4cm](i4)--(e4);
-    \draw[ultra thick,ucp-color](i1)--(i2)--(i3);
+    \draw[ultra thick](i1)--(i2);
+    \draw[ultra thick,ucp-color](i2)--(i3);
     \draw[ultra thick,cut-color](i4)--(e4);
@@
 in which one of the \textcolor{ucp-color}{uncut propagators} is set
-equal to an \textcolor{cut-color}{external on-shell propagator}. \jm{I think the blue line might extend too far to the left in the picture.}
+equal to an \textcolor{cut-color}{external on-shell propagator}.
 Discussions about how to resolve these types of singularities can be
 found in Refs.~\cite{Edison:2022jln, Edison:2022smn, Edison:2020uzf,
-  Geyer:2015bja, Bern:2012uf} \citepls{Minahan}.  In addition to the
+  Geyer:2015bja, Bern:2012uf, Minahan:1987ha} \ace{Should really make
+  sure that is the right Geyer paper}.  In addition to the
 bubble-on-external-leg cuts, there is a related class of cuts in which
@@
 on-shell tree amplitudes.  The cut to be performed can, itself, be
-encoded in a graph.  For example, potential 4pt 2-loop cuts include
+encoded in a graph.  For example, potential 4-point 2-loop cuts include
 \begin{equation}
@@
 physical cuts where (d) is known as a maximal cut since the maximal
-number of propagators have been put on shell.
-\fi
+number of propagators have been put on shell.  \fi
 
@@
 freedom does not affect the physical integrand or its double copy.
+
+\ace{End of Alex first readthrough}
 
@@
 Starting with the Yang-Mills Lagrangian,
-\be
+\begin{equation}
 \mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2 + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
-\ee
+\end{equation}
 We can express the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
-\be
+\begin{equation}
 T^k_{ij} = (\varepsilon_i\varepsilon_j)(\varepsilon_k p_i)
-\ee
+\end{equation}
 This kinematic generator is anti-symmetric in $1\leftrightarrow 2$ exchange, and from it we can construct the full Lorenz gauge Yang-Mills vertex by summing over cyclic permutations:
-\be
+\begin{equation}
 V^{(123)}_{\text{YM}} = T^3_{12} +\text{cyc}(123)
-\ee
+\end{equation}
 Contracting this with the vector state sum, we can see that the cubic Yang-Mills vertex does not alone satisfy the four-point Jacobi identity:
@@
 {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4+\text{cyc}(234) = \varepsilon_{(12)}  \varepsilon_{(34)} (s_{13}-s_{23}) +\text{cyc}(234) \neq 0
-\ee
+\end{equation}
 where $ \varepsilon_{(ij)} =  \varepsilon_{i}\cdot  \varepsilon_{j}$.
 Of course, it is not hard to see that one can simply absorb the remaining terms into the definition of the four-point kinematic numerators:
-\be
+\begin{equation}
 {}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4 = {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4 + s_{12} (\varepsilon_{(13)}\varepsilon_{(24)}-\varepsilon_{(14)}\varepsilon_{(23)})
-\ee
+\end{equation}
 where $V_{\text{YM}+B}$ indicates the introduction of an additional two-form studied in \cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian. 
-\be
+\begin{equation}
 {}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
-\ee
+\end{equation}
 where the new cubic Lagrangian is of the form:
-\be
+\begin{equation}
 \mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 - B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu A^c_\nu
@@
 Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
-\be
+\begin{equation}
 {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0
-\ee
+\end{equation}
 Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form.
@@
 By a simple mass-dimensioin argument, we know the tree-level cubic sector of Yang-Mills must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
-\be
+\begin{equation}
 A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
-\ee
+\end{equation}
 while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products:
-\be
+\begin{equation}
 A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
-\ee
+\end{equation}
 When decomposed in this way, the polarization stripped building blocks must obey a set of Ward-Identities between different helicity sectors in order for the full amplitude to be gauge invariant,:
@@
 \begin{eBox}
-\be
+\begin{equation}
 \label{eq:semiYM}
 \mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
-\ee
+\end{equation}
 \end{eBox}
 where,
-\be
+\begin{equation}
 \bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
-\ee
-\be
+\end{equation}
+\begin{equation}
 F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c .
-\ee
+\end{equation}
 Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents.
@@
 The Feynman rules fo this theory are simply:
-\be
+\begin{equation}
 \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
-\ee
+\end{equation}
 Specifically, semi-Abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
@@
 Indeed, the $D$-dimensional description of $J$ theory is just the following blocks in the RABD expansion of Yang-Mills:
-\be
+\begin{equation}
 A(...,\bar{A}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
-\ee
+\end{equation}
 and similarly so at one-loop:
-\be
+\begin{equation}
 A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}
-\ee
+\end{equation}
 To recover NLSM at one-loop, we need to extract out the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars:
 \begin{eBox}
-\be
+\begin{equation}
 A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}
-\ee
+\end{equation}
 \end{eBox}
@@
 At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{Monteiro2011pc}:
-\be
+\begin{equation}
 X(p,k) = p_u k_w-p_w k_u
-\ee
+\end{equation}
 At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop.
 This can be done using the cubic semi-YM vertices of the previous section:
-\be
+\begin{equation}
 \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
-\ee
+\end{equation}
 Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase.
@@
 Below we provide a four-point example:
-\be
+\begin{equation}
 \simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
-\ee
+\end{equation}
 where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
-\be
+\begin{equation}
 \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
-\ee
+\end{equation}
 Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$.
 By taking a derivative\footnote{Another way to understand this derivative is that it selects the large $D$ behavior of the integrand.}, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
-\be
+\begin{equation}
 \frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
-\ee
+\end{equation}
 This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop.
 For more background, we refer the reader to appendix \ref{}.
-\be
+\begin{equation}
  \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
-\ee
+\end{equation}
 Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
@@
 However, at two-loop when choosing all external $A_\mu$ states, the amplitude vanishes in semi-YM theory:
-\be
+\begin{equation}
 \mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(+,+,+,+)=0
-\ee
+\end{equation}
 In order to produce non-vanishing interactions, we would need to reintroduce $D$-dimensional vertices from the diagonal group of $G_L\times G_R$.
 Doing so will necessarily introduce internal contractions of $\bar{A}_\mu A^\mu$,
-\be
+\begin{equation}
 \mathcal{A}^{\text{YM}}_{\text{2-loop}}(+,+,+,+)=\doubleBoxObstructionA +\doubleBoxObstructionB+\cdots 
-\ee
+\end{equation}
 However, this immediately runs into the difficulty of introducing the four-point contact needed for color-kinematics to be satisfied on all internal edges.
@@
 However, these methods cannot be reapplied to generate higher-loop numerators, which begs the question ``is it possible to find globally color-dual numerators beyond 1-loop''.
-We will tackle this question for 4pt 2-loop scattering in NLSM before moving on to the same process in YM.
-
-Ignoring tadpoles and BEL graphs, there are 14 cubic 4pt 2-loop graphs (see \cref{fig:MaxCuts}) which are related to each other via 21 Jacobi relations.
+We will tackle this question for 4-point 2-loop scattering in NLSM before moving on to the same process in YM.
+
+Ignoring tadpoles and BEL graphs, there are 14 cubic 4-point 2-loop graphs (see \cref{fig:MaxCuts}) which are related to each other via 21 Jacobi relations.
 As mentioned in \cref{sec:bootstrap}, color-kinematics duality ensures that the numerator of every graph can be expressed in terms of a basis of the double box and penta-triangle,
@@
 Cuts (b) and (c) of \cref{eq:PotentialCuts} are the only physical cuts that need to be enforced.  \jm{Move some of the cut pictures here?}
-This means that even at two loops, unitarity is still only probing the on-shell 4pt NLSM amplitude.
+This means that even at two loops, unitarity is still only probing the on-shell 4-point NLSM amplitude.
 The other cuts besides (b) and (c) are either pathological or vanish because they involve a 3pt point on-shell amplitude (which vanishes on general grounds for scalar theories).
@@
 $\mathcal{N}=4$ SYM provides several hints for further conditions to impose on the ansatz.
-For example, for maximally supersymmetric gauge theory it is possible to enforce the no triangle hypothesis, manifest loop power counting, and, at least for 4pt and up to four loops, strip off a factor of $st A_\text{tree}$ from the integrand (I'm not sure I know all of the papers to cite here).
+For example, for maximally supersymmetric gauge theory it is possible to enforce the no triangle hypothesis, manifest loop power counting, and, at least for 4-point and up to four loops, strip off a factor of $st A_\text{tree}$ from the integrand (I'm not sure I know all of the papers to cite here).
 For the NLSM integrand it is desirable to make color-kinematics duality as manifest as possible.
@@
 ZM theory is governed by the Lagrangian
-\be
+\begin{equation}
 \label{eq:ZMLagrangian}
 \mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c),
-\ee
+\end{equation}
 where more details can be found in \cref{sec:CKLagrangians}.
@@
 Only \emph{ordered} amplitudes can be defined unambiguously from the Feynman rules.
-At 4pt, only the alternating sector is free of subtleties and the amplitude for this process vanishes.
+At 4-point, only the alternating sector is free of subtleties and the amplitude for this process vanishes.
 In equations, $A[LRLR]=0$ where $R$ corresponds to a right mover and $L$ corresponds to a left mover.
@@
 
-It is tempting to try to match the pion 4pt 2-loop integrand to ZM on the cuts, but given that the cuts only probe the on-shell 4pt amplitude, which is either subtle or vanishes for ZM, it is better to compare the off-shell numerators directly.
+It is tempting to try to match the pion 4-point 2-loop integrand to ZM on the cuts, but given that the cuts only probe the on-shell 4-point amplitude, which is either subtle or vanishes for ZM, it is better to compare the off-shell numerators directly.
 As local functions, the numerators never suffer from any of the subtleties of on-shell 2D kinematics.
@@
 A generic term in the ZM numerator (of either basis graph) looks schematically like
-\be
+\begin{equation}
 \label{eq:ZMLoopPowCount}
 \ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
-\ee
+\end{equation}
 whereas a generic set of local, cubic Feynman rules could have produced terms with up to $m+n=12$ powers of loop momenta.
 When the pion numerator is forced to have the loop power counting structure in \cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge freedom parameters reduces to 58.
-The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4pt pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}
+The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4-point pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}
 
@@
 from terms of the form:
-\be
+\begin{equation}
 \mathcal{N}_{\text{2box}},\mathcal{N}_{\text{pt}}\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
-\ee
+\end{equation}
 in addition to the purely momentum-dependent terms show in
@@
 that directly involve such pathological diagrams.  That leaves us with
-14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc}, on
+14 non-pathological cubic diagrams, shown above in \cref{fig:MaxCuts}, on
 which to impose maximal cuts and symmetries.  Doing so, we are left
@@
 the BDN-restricted ansatz.
-\begin{figure}
-\centering
-{\MCutC, \MCutD, \sumoCut, \MCutJ,  
- \\
-  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
-\\
-\MCutI,  \MCutE, \MCutK, 
-\\
- \MCutL, \MCutG,  \MCutH,
-}
-  \caption{The 14 non-pathological maximal-cut diagrams, including all dangling tree diagrams.} \label{fig:MaxCuts}
-  \end{figure}
 
@@
  For example, consider the simple four-point example of a color-dual representation of Yang-Mills theory. 
-\be
+\begin{equation}
 \mathcal{N}_{(12|34)}^{\text{YM}} = \frac{t_8F^4}{3} \frac{s_{13}-s_{12}}{s_{23}{s_{13}}}
-\ee
+\end{equation}
 By construction, this functionally symmetric numerator is anti-symmetric and obeys the Jacobi identity:
-\be
+\begin{equation}
 \mathcal{N}_{(12|34)}^{\text{YM}} + \mathcal{N}_{(13|42)}^{\text{YM}} +\mathcal{N}_{(14|23)}^{\text{YM}} = 0
-\ee
+\end{equation}
 However, it must also factorize to kinematics that are consistent with the local Feynman rules of \ref{}. Evaluating the residues on $s=s_{12}$, $t=s_{23}$ and $u=s_{13}$ poles, we find:
@@
 Plugging these into a cubic graph representation of Yang-Mills \ref{}, we find:
-\be
+\begin{equation}
 \text{Res}\left[\mathcal{A}_4^{\text{YM}}\right]^{s=0} = \frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} (2c_s-c_t-c_u) =  \mathcal{A}_{(12|l)}^{\text{YM}}\mathcal{A}_{(-l|34)}^{\text{YM}} 
-\ee
+\end{equation}
 where we have applied the color structure Jacobi identity, $c_s+c_t+c_u=0$.
@@
 Rather than building an ansatz from the irreducible scalar products of \ref{},
-\be
+\begin{equation}
 \mathcal{N}^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
-\ee
+\end{equation}
 where $\mathcal{O}_i$ are the basis tensors of \cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}_i$ is a rational function of momenta of the form;
-\be
+\begin{equation}
 \mathcal{R}_{m,L} = \frac{P_{b+a}(k^2,kl,l^2)}{Q_a(k^2,kl,l^2)}, \qquad b=m+2(l-1)
-\ee
+\end{equation}
 where $P_{a}$ and $Q_a$ are degree-$a$ polynomials exclusively of $D$-dimensional scalar kinematics. 
@@
 \paragraph{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
-\be
+\begin{equation}
 \mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
-\ee
+\end{equation}
 To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
@@
 F_{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
-\ee
+\end{equation}
 where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength.
 Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
-\be
+\begin{equation}
 D^\mu F^{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
-\ee
+\end{equation}
 Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills.
@@
 Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
-\be
+\begin{equation}
 u = t+x,\quad v=t-x, \quad w = y+iz
-\ee
+\end{equation}
 which gives the following expression for the invariant line element:
-\be
+\begin{equation}
 ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
-\ee
+\end{equation}
 Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
@@
 Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
-\be
+\begin{equation}
 A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
-\ee
+\end{equation}
 The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
-\be
+\begin{equation}
 A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
-\ee
+\end{equation}
 This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
@@
 A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
-\ee
+\end{equation}
 Using this definition on the first self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
@@
 (\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
-\ee
+\end{equation}
 Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
-\be
+\begin{equation}
 \mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
-\ee
+\end{equation}
 The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
-\be
+\begin{equation}
 \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
-\ee
+\end{equation}
 In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
@@
 Plugging this redefinition of the gauge fields in, upto cubic order, we thus obtain the following Lagrangian:
-\be
+\begin{equation}
 \mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)
-\ee
+\end{equation}
 The Feynman rules for this Lagrangian are simply:
-\be
+\begin{equation}
 \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i (\varepsilon_3 p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
-\ee
+\end{equation}
 Now we review of the construction of NLSM numerators at tree-level. In this construction, we can define generators of the kinematic algebra can be expressed as follows
@@
 T^a_{ij}= i \varepsilon_a(p_i-p_j)
-\ee
+\end{equation}
 where momentum conservation requires
-\be
+\begin{equation}
 p_a + p_i + p_j =0
-\ee
+\end{equation}
 The kinematic half-ladder diagrams then takes on the following concise definition:
-\be
+\begin{equation}
 n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
-\ee
+\end{equation}
 Since there are on pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the chiral current algebra is manifestly cubic.
@@
 They can be defined implicitly below:
-\be
+\begin{equation}
 [T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}
-\ee
+\end{equation}
 Given this definition, the Feynman rule associated with kinematic structure constant is simply:
@@
 i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c) 
-\ee
+\end{equation}
 where $p_{ab}=p_a+p_b$ and $\varepsilon$ and $\bar{\varepsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
 The on-shell state sum for the polarization vectors is simply:
-\be
+\begin{equation}
 \sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}
-\ee
+\end{equation}
 Notice that the vector state sum is gauge fixed since the $Y\,Z$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$.
@@
 \varepsilon^\mu_{(p)} = p^\mu \qquad \bar{\varepsilon}^\mu_{(p)} = \frac{q^\mu}{pq}
-\ee
+\end{equation}
 where $q^2=0$ is some null reference momentum. With this, we can define tree-level pion scattering in two equivalent ways:
-\be
+\begin{equation}
 A^{\text{NLSM}} = A(...,Y,...,Y,...) = A(...,\bar{Z},...) 
-\ee
+\end{equation}
 where the ellipses denote additional on-shell $Z$-particles.
@@
 A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
-\ee
+\end{equation}
 Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration.
@@
 where we have defined the short hand notation:
-\be
+\begin{equation}
 {}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
-\ee
+\end{equation}
 Similarly, we find the following ordered amplitude when plugging in these numerators:
-\be
+\begin{equation}
 A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
-\ee
+\end{equation}
 Plugging in the on-shell polarizatoin of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
@@
 Two constraints, the field strength should vanish
-\be
+\begin{equation}
 \label{eq:FieldStrengthJ}
 F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
-\ee
+\end{equation}
 which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
 The second condition is that the chiral current should be in Lorenz gauge
-\be
+\begin{equation}
 \label{eq:LorenzGaugeJ}
 \partial_\mu J^\mu=0
-\ee
+\end{equation}
 which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
 Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
-\be
+\begin{equation}
 \label{eq:JTheoryEOM}
 \Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
-\ee
+\end{equation}
 Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-Abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
 In other words, \emph{J-theory and semi-Abelian YM are identical}.
-By calculating an off-shell 4pt correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
+By calculating an off-shell 4-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
 As might be expected, the kinematic algebra is the diffeomorphism algebra.
@@
 As such, the single vertex in this theory is the same as the pure vector vertex of YZ theory in Lorenz gauge, where $\partial_\mu J^\mu = 0$:
-\be
+\begin{equation}
 \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
-\ee
+\end{equation}
 
@@
 After plugging $\varphi$ into \cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
-\be
+\begin{equation}
 \label{eq:ZMLagrangian}
 \mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
-\ee
+\end{equation}
 This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
@@
 The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \cref{eq:ZMLagrangian}, giving
-\be
+\begin{equation}
 \langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
-\ee
+\end{equation}
 The vertex is (1) functionally symmetric and (2) the kinematic portion of the vertex is completely anti-symmetric: 
-\be
+\begin{equation}
 \cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
-\ee
+\end{equation}
 This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
 To prove off-shell color kinematics duality for any multiplicity and loop order it is enough to observe that the sum of the off-shell $s$-, $t$-, and $u$-channel numerators sum to zero
-\be
+\begin{equation}
 \label{eq:ZMJacobi}
 \langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
-\ee
+\end{equation}
 by virtue of the 2D Levi-Civita identity $\varepsilon_{\mu\nu}\varepsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
@@
 With this, we still obtain the same completeness relation for the SDYM spinors:
-\be
+\begin{equation}
 X(a,b)Q(b,a) = \frac{1}{2}s_{ab}
-\ee
+\end{equation}
 \section{Regulating BEL integrals}\label{BELreg}
@@
 Thus, $Y\!Z$ theory gives us the following one-loop $n$-gon numerator:
-\be
+\begin{equation}
 N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+2\, (F^1F^2\cdots F^n)
-\ee
+\end{equation}
 where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops.
 Plugging in the Feynman rule of \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
-\be
+\begin{equation}
 N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
-\ee
+\end{equation}
 and similarly so for the internal vector contribution:
-\be
+\begin{equation}
  (F^1F^2\cdots F^n) = (D-4)(l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
-\ee
+\end{equation}
 The dimension dependent factor essentially counts that number of internal vector states.
@@
 The $n$-gon numerator above has scalar insertions of the following kinematic vertex:
-\be
+\begin{equation}
 T^{a}_{LR} = k_a(l_L-l_{R}) = (l_L+l_{R}) (l_L-l_{R})  = l_L^2-l_{R}^2 
-\ee
+\end{equation}
 Given this structure, in the next section we will attempt to construct two-loop basis diagrams from these cubic vertex assignments and try to reverse engineer the particle content that produces these master numerators.
@@
 The BEL diagram can be reconstructed from the $n$-gon as follows:
-\be
+\begin{equation}
 N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
-\ee
+\end{equation}
 where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
-\be
+\begin{equation}
 N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
-\ee
+\end{equation}
 Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
-\be
+\begin{equation}
 \mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
-\ee
+\end{equation}
 where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$.
@@
 \item Forcing pions to match ZM in 2D does funny things.
-The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
+The pion coupling constant is dropped but is implicitly set by the ordered 4-point amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
 I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
 Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
-For 4pt tree, $z=2/3$ (I matched the half ladder).
-For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
-For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
+For 4-point tree, $z=2/3$ (I matched the half ladder).
+For 4-point 1-loop, $z$ is free/pure generalized gauge (I matched the box).
+For 4-point 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
 For 6pt tree, $z$ is 12/35 (I matched the half ladder).
@@
 Only well defined object is numerator.
-\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
+\item At 4-point 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
 At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
@@
 This doesn't work.
-\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
+\item To clean up the NLSM 4-point 2-loop answer I forced the answer to match ZM in 2D.
 The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
@@
 \item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
-\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4pt, 6pt, and 8pt.
-\item Should probably give the 4pt pion amplitude somewhere to show my conventions.
+\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4-point, 6pt, and 8pt.
+\item Should probably give the 4-point pion amplitude somewhere to show my conventions.
 \end{itemize}
@@
 \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} =T^3_{12}
-\ee
-\be
+\end{equation}
+\begin{equation}
 V^{c}_{ab} = (\varepsilon_a\varepsilon_b)(\varepsilon_c k_a)
-\ee
+\end{equation}
 With this, the full vector interaction can be expressed as a sum over cyclic permutations:
-\be
+\begin{equation}
 \cubic{hgrey0}{gluon}{}{gluon}{}{gluon}{}  =  \cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed} + \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} + \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} +\text{h.c.}
-\ee
+\end{equation}
 The state-sum between two three-point gluon vertex yields the following expansion in terms of YZ-theory vertices:
-\be
+\begin{equation}
  \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
-\ee
+\end{equation}
 where we have defined a new oriented vertex in terms of our scalar-vector building block of \ref{YMSvert},
-\be
+\begin{equation}
 \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} = \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} +\cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed}\,.
-\ee
-\be
+\end{equation}
+\begin{equation}
 \vec{V}^{c}_{ab} =V^{b}_{ac}+V^{a}_{bc}
-\ee
+\end{equation}
 All the $(\varepsilon\varepsilon)^1$ diagram permutations are isolated to the cubic sector and together manifest color-kinematics duality.
@@
 
-\be
+\begin{equation}
 \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed} = (s_{13}-s_{12}) \varepsilon_{(12)} \varepsilon_{(34)}
-\ee
+\end{equation}
 One was to resolve this is to introduce higher spin modes in order to accomodate the internal index contractions needed to recover the s-channal contract:
-\be
+\begin{equation}
 \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{Bfield}{nhpRed}{}{nhpRed} = s_{12 }(\varepsilon_{(13)} \varepsilon_{(24)} - \varepsilon_{(14)} \varepsilon_{(23)})
-\ee
+\end{equation}
 

### 2023-09-19 notes/2loopNLSM.tex
added comment about TikZ preamble
Minor edits

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
@@
 ]
+%Uncomment this  ^^^^^^^^ to compile in new images in real time. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
     does/will a statement to this effect actually make it into the
-    draft?}  Additionally, we revisit the two-loop four-point
-  Yang--Mills problem in order to identify the exact point of
-  inconsistency in a local color-dual construction.
+    draft?}
+We find that the most general \emph{local} numerator for two-loop four-point numerator for $\mathcal{N}=0$ YM fails global color-kinematics duality and we pinpoint the failure to the kissing-triangles cut.
 
@@
 formidable challenge
-\cite{Mogull:2015adi,Johansson:2017bfl,KalinN2TwoLoop} \ace{BDN might
-  fit better here rather than the 2loop SQCD}. In this work, we use
+\cite{Mogull:2015adi, Johansson:2017bfl, KalinN2TwoLoop, Bern:2015ooa}. In this work, we use
 the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven
@@
 benchmark for color-dual representations in non-supersymmetric gauge
-theories. However in contrast, we find surprisingly that Yang-Mills
-does not permit a globally color-dual representation, \ace{Maybe tone
-  down surprise and ref BDN} even when considering the most general
-polynomial ansatz of Lorentz covariant kinematics. Concretely, we find
-a sharp failure point between the ``bowtie'' cut, and the following
-jacobi triple:
+theories.
+However in sharp contrast, we find that Yang-Mills
+does not permit a globally color-dual representation, even when considering the most general
+polynomial ansatz of Lorentz covariant kinematics.\footnote{Globally color-dual local numerators for two-loop pure YM have been studied before but only in the context of a limited ansatz subject to certain loop power counting constraints \cite{Bern:2015ooa}.}
+Concretely, the failure point can be pinpointed to a conflict between between the ``bowtie'' cut and the following Jacobi triple
 \begin{equation}
@@
 constructions. We then detail a color-dual boostrap approach for
-constructing integrands in theories for which the off-shell kinematic
+constructing integrands in theories for which the fully off-shell kinematic
 algebra has not yet been identified, like Yang-Mills and NLSM.
@@
 \cref{DCconstruction} would suggest a manifestly cubic Lagrangian of
-the form:
+the form
 \begin{equation}
@@
 to encode non-local kinetic structure that could in principle
-participate in the construction. Should the off-shell Feynman rules of
-this cubic theory be antisymmetric and satisfy Jacobi identities on
-all internal edges,
+participate in the construction.
+The theory will be color dual if the cubic vertex is antisymmetric and satisfies the Jacobi identity, specifically,
 \begin{align}
-\textit{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0\,,
+\textit{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0
 \\
-\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\,,
+\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0
 \end{align}
@@
 \end{equation}
-This is a sufficient condition of the amplitudes to obey BCJ
-relations. \ace{Reword previous 2 sentences} Off-shell descriptions of
+Off-shell descriptions of
 color-dual theories are rare, and only a few examples are available in
@@
   Cheung:2020djz, Ben-Shahar:2022ixa, Ben-Shahar:2021zww,
-  Ben-Shahar:2021doh}\ace{Are these a reasonable
-  collection?  Just grabbed the ones below}. Typically when one goes about constructing color-dual
+  Ben-Shahar:2021doh}.
+\ace{Are these a reasonable collection?  Just grabbed the ones below}
+\jm{These references get repeated in a second.  I'll fix this.}
+Typically when one goes about constructing color-dual
 theories directly from a set of cubic interactions, higher point

### 2023-09-20 notes/2loopNLSM.tex
First read through

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-\usetikzlibrary{external}  
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-\tikzexternalize[                     %% Activate externalization
- prefix=images/,                    %% Avoid cluttering the directory
- system call={                       %% Use lualatex in system call
-    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
- },
-]
-%Uncomment this  ^^^^^^^^ to compile in new images in real time. 
+% Comment the following out to compile new images
+%
+%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+%\usetikzlibrary{external}  
+%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+%\tikzexternalize[                     %% Activate externalization
+% prefix=images/,                    %% Avoid cluttering the directory
+% system call={                       %% Use lualatex in system call
+%    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
+% },
+%]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%Why DC is cool:
+%1) Reduction in computational complexity.
+%Off-shell high spin is terrible.
+%Gravity has infinitely many very complex Feynman rules as a result of gauge redundancy but YM only has two relatively simple Feynman rules.
+%2) DC points to deep structure hidden in Lagrangian formulation.
+
 \section{Background}\label{background}
@@
 
-%I think this belongs in another section...
-%Why DC is cool:
-%1) Reduction in computational complexity.
-%Off-shell high spin is terrible.
-%Gravity has infinitely many very complex Feynman rules as a result of gauge redundancy but YM only has two relatively simple Feynman rules.
-%2) DC points to deep structure hidden in Lagrangian formulation.
-
 Color-kinematics duality is a statement about the off-shell graphical
@@
   fact we slip that type of disclaimer in quite a lot throughout the
-  rest of the section} -- can be written as
+  rest of the section} \jm{I removed the second time we say `YM, NLSM, $\phi^3$' which was redundant.
+I don't mind if we say it here because I want people to tell people that these are the kinds of theories we're thinking about.
+We could omit it but then we'd have to say that the theory has at least one color factor and is probably an adjoint type theory and at that point I'd rather just give an example.} -- can be written as
 \begin{equation}
@@
 the various kinematic numerators $n_\Gamma$ such that the numerators
-obey all of the same Jacobi identities as the color factors
+obey the same Jacobi identities as the color factors
 \begin{equation}
@@
 \cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz,
-  Cheung:2021zvb, Cheung:2022mix}.  As a simple example, color-dual
-numerators for 4pt pion scattering at tree level are
+  Cheung:2021zvb, Cheung:2022mix}.
+When the kinematic algebra is not known explicitly, the kinematic numerators are typically constructed from an ansatz.
+As an example, the result of such a calculation for 4pt pion scattering at tree level produces the numerators
 \begin{align}
@@
 level using the KLT relations but there is significant evidence that
-the double copy persists to all loop orders \cite{KLT, KiermaierTalk}
-\citepls{Any loop papers we want?}.  In addition to pointing at deep
+the double copy persists to all loop orders \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv, Carrasco:2021otn, KLT, KiermaierTalk}.
+In addition to pointing at deep
 structure hidden in the Lagrangian for gravity, the double copy is
@@
 The color structure of tree-level amplitudes is particularly simple.
-A fully color dressed tree amplitude $\mathcal{A}_n$ in YM, NLSM, or
-bi-adjoint scalar theory can be decomposed in terms of the trace basis
+A fully color dressed tree amplitude $\mathcal{A}_n$ can be decomposed in terms of the trace basis
 \begin{equation}
@@
 applications of the Jacobi identity.  At 1-loop, every diagram can be
-related to one topology as well, in this case the $n$-gon, but the
-pattern does not persist to 2-loops.
+related to one topology as well, in this case the $n$-gon.
+Two-loop calculations play an important role in our understanding of color-kinematics duality because this is the first order where multiple basis graphs are required, at least for a generic theory.
 
@@
   Ben-Shahar:2021doh}.
-\ace{Are these a reasonable collection?  Just grabbed the ones below}
-\jm{These references get repeated in a second.  I'll fix this.}
 Typically when one goes about constructing color-dual
@@
 Jacobi and antisymmetry constraints require introducing additional
-operators. See refs \cite{Ben-Shahar:2022ixa} for some recent
-examples. Indeed, as we'll show in \cref{sec:cubic}, Yang-Mills
+operators. See ref \cite{Ben-Shahar:2022ixa} for a recent
+example. Indeed, as we will show in \cref{sec:cubic}, Yang-Mills
 requires introducing a cubic 2-form interaction in order to manifest
@@
 
-Aside from a few special theories that permit an off-shell Lagrangian
-description \cite{Monteiro2011pc, Cheung:2016prv, Cheung:2021zvb,
-  Cheung:2020djz, Ben-Shahar:2022ixa, Ben-Shahar:2021zww,
-  Ben-Shahar:2021doh}, color-dual integrands are constructed from an
-ansatz.  The four conditions we impose on an ansatz are summarized
+When an off-shell color-dual Lagrangian is not known, the amplitude integrand must be constructed from an ansatz.  The four conditions we impose on an integrand ansatz are summarized
 here and elaborated on below.\footnote{The four ansatz conditions are
-  similar to those of Ref.~\cite{Bern:2015ooa} except that there
+  similar to those of Ref.~\cite{Bern:2015ooa} except that there the
   authors demand that the numerators have the same loop power counting
@@
 \item \textbf{Off-shell Locality}: Diagram numerators are polynomials
-  in momenta and polarizations, \eg the diagrams only have poles given
+  in momenta and polarizations, e.g., the diagrams only have poles given
   by the propagators of the diagrams.
@@
   diagram numerators are invariant under the automorphisms of the
-  diagrams \emph{including signs that compensate for color-factor sign
-    changes}.
+  diagrams including signs that compensate for color-factor sign
+    changes.
 \item \textbf{On-shell Unitarity }: The cuts of the ansatz must
@@
 include examples from a 4-point 2-loop integrand for some generic
-color-dual theory like YM or NLSM.  This is the simplest case that
+color-dual theory like YM.  This is the simplest case that
 demonstrates the full machinery of the color-dual bootstrap.  All tree
 and 1-loop processes are generated by single basis diagrams (the half
-ladder and $n$-gon respectively) so they lack examples of the
-``boundary'' Jacobi relations to be described shortly \ace{This is not
-  strictly true.  Boundary Jacobi occur in 1L when demanding that BEL
-  and/or tadpole are 0.  However, I appreciate that logic that 2L is
-  the first time where an A+A+A=0 Jacobi occurs, rather than A+A=0.}.
+ladder and $n$-gon respectively) so they lack examples of three-term
+``boundary'' Jacobi relations to be described shortly.
 Choosing the 4-point 2-loop integrand also has the advantage that this
@@
 local (polynomial) functions of the graph kinematics with the correct
-power counting and external states.  Insisting on a local numerator is
+power counting and external states.
+Insisting on a local numerator is
 partly a matter of convenience as the ansatz for a rational function
@@
 is a viable alternative when the condition proves too stringent for an
-ansatz.  We will comment more on locality in \cref{conclusions}.
+ansatz.
+In particular, the most natural way to guarantee locality is to require the off-shell numerators to be polynomial functions of kinematics.
+However, simply requiring on-shell locality may suffice.
+This alternative will be discussed in \cref{nonLocalScattering}.
 
@@
 \\
- \MCutL, \MCutG,  \MCutH,
+ \MCutL, \MCutG,  \MCutH
 }
@@
 % \end{equation}
-\ace{is there a reason we commented out this diagram?}  For example,
+\ace{is there a reason we commented out this diagram?} \jm{You can try either one.  I liked the one I left in better.}
+For example,
 the symmetries of the crossed box
@@
 \label{sec:cubic}
-Here we'll describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
+Here we will describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
 It has to do with how the vector state sum mixes with the four-point contact.
@@
 \end{equation}
-We can express the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
-\begin{equation}
-T^k_{ij} = (\varepsilon_i\varepsilon_j)(\varepsilon_k p_i)
-\end{equation}
-This kinematic generator is anti-symmetric in $1\leftrightarrow 2$ exchange, and from it we can construct the full Lorenz gauge Yang-Mills vertex by summing over cyclic permutations:
-\begin{equation}
-V^{(123)}_{\text{YM}} = T^3_{12} +\text{cyc}(123)
-\end{equation}
-Contracting this with the vector state sum, we can see that the cubic Yang-Mills vertex does not alone satisfy the four-point Jacobi identity:
+we can express the YM three-point interaction in terms of the following vertex in Lorenz gauge
+\begin{equation}
+T^k_{ij} = (\varepsilon_i\varepsilon_j)(\varepsilon_k p_i).
+\end{equation}
+This kinematic generator is anti-symmetric in $1\leftrightarrow 2$ exchange, and from it we can construct the full Lorenz gauge Yang-Mills vertex by summing over cyclic permutations
+\begin{equation}
+V^{(123)}_{\text{YM}} = T^3_{12} +\text{cyc}(123).
+\end{equation}
+Contracting this with the vector state sum, we can see that the cubic Yang-Mills vertex does not satisfy the four-point Jacobi identity
 \be\label{cubicJac}
@@
 where $ \varepsilon_{(ij)} =  \varepsilon_{i}\cdot  \varepsilon_{j}$.
-Of course, it is not hard to see that one can simply absorb the remaining terms into the definition of the four-point kinematic numerators:
+The remaining terms can be absorbed into the definition of the four-point kinematic numerator
 \begin{equation}
@@
 where $V_{\text{YM}+B}$ indicates the introduction of an additional two-form studied in \cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian.
-\begin{equation}
+After the introduction of the 2-form, the numerators now satisfy the Jacobi identity
+\be
 {}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
-\end{equation}
-where the new cubic Lagrangian is of the form:
-\begin{equation}
-\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 - B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu A^c_\nu
+\ee
+where the new cubic Lagrangian takes the form
+\be
+\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 - B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu A^c_\nu\, .
 \ee 
@@
 
-As one can see above, the Jacobi identity of \ref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$.
-Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
-\begin{equation}
-{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0
+As can be seen above, the Jacobi identity of \cref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$.
+Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions
+\begin{equation}
+{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0\,.
 \end{equation}
 Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form.
-The organizational principle underlying this construction can be easily understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog},
+The organizational principle underlying this construction can be understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog},
 \begin{equation}\label{eq:pureVecRABD}
@@
 \end{equation}
-By a simple mass-dimensioin argument, we know the tree-level cubic sector of Yang-Mills must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
-\begin{equation}
-A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
-\end{equation}
-while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products:
+\jm{Nic, could you give a quick recap of what all of the symbols mean in the equation above?}
+By a simple mass-dimensioin argument, we know the tree-level cubic sector of Yang-Mills must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$,
+\begin{equation}
+A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\, ,
+\end{equation}
+while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products,
 \begin{equation}
@@
 \end{equation}
-When decomposed in this way, the polarization stripped building blocks must obey a set of Ward-Identities between different helicity sectors in order for the full amplitude to be gauge invariant,:
+When decomposed in this way, the polarization stripped building blocks must obey a set of Ward-identities between different ``helicity'' (or $(\varepsilon \varepsilon)$) sectors in order for the full amplitude to be gauge invariant,
  \begin{equation}\label{eq:GIrelA}
@@
 As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell.
-However, the contrapositive is also true -- if we get rid of the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.
-
-We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G \rightarrow G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$.
-However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$, and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preffered $U(1)$-directions.
+However, the contrapositive is also true -- if we omit the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.
+
+We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G$ to $G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$.
+However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preferred $U(1)$-directions.
 We call this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
@@
 \end{eBox}
-where,
+where
 \begin{equation}
@@
 Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents.
-Indeed, as we describe in the Appendix \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{Cheung:2016prv}, J-theory \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills \cite{Monteiro2011pc}.
-The Feynman rules fo this theory are simply:
-\begin{equation}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
-\end{equation}
+Indeed, as we describe in Appendix \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{Cheung:2016prv}, J-theory \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills \cite{Monteiro2011pc}.
 Specifically, semi-Abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
-We can use the Ward identity of \ref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant with the abelian polarizations are taken on-shell, $\bar{\varepsilon} \rightarrow k$.
+The Feynman rule for the cubic vertex is
+\begin{equation}
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
+\end{equation}
+The propagator kinetic mixes between the two gauge fields and has the standard Feynman rule of $i/k^2$.
+We can use the Ward identity of \cref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant when the abelian polarizations are taken to be longitudinal, $\bar{\varepsilon} \rightarrow k$.
 
@@
 SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states.
-Indeed, the $D$-dimensional description of $J$ theory is just the following blocks in the RABD expansion of Yang-Mills:
+Indeed, the $D$-dimensional description of $J$-theory is just the following blocks in the expansion of Yang-Mills given in \ref{Pavao:2022kog}
 \begin{equation}
@@
 \end{equation}
-and similarly so at one-loop:
-\begin{equation}
-A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}
-\end{equation}
-To recover NLSM at one-loop, we need to extract out the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars:
+and similarly so at one-loop
+\begin{equation}
+A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}\, .
+\end{equation}
+To recover NLSM at one-loop, we need to extract the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars
 \begin{eBox}
 \begin{equation}
-A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}
+A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}\, .
 \end{equation}
@@
 \section{Two-loop bootstrap}\label{2loopBoot}
-We now employ the color-dual bootstrap method described in \cref{bootstrap}.
+We now employ the color-dual bootstrap method described in \cref{sec:bootstrap}.
 We will employ an ansatz constructed from  $D$-dimensionally Lorentz covariant kinematics.
@@
 This is merely an aesthetic choice, so the final results of both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
-\subsection{Two-loop NLSM}\label{2loopNLSM}
+\subsection{Two-loop NLSM}
 \label{sec:pions}
@@
 
+\begin{figure}
+  \begin{center}
+	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
+  \end{center}
+  \caption{The two physical cut topologies shared by NLSM, sGal, BI, and DBIVA}
+  \label{fig:emu}
+\end{figure}
+
 The final essential constraint is unitarity.
-Cuts (b) and (c) of \cref{eq:PotentialCuts} are the only physical cuts that need to be enforced.  \jm{Move some of the cut pictures here?}
-This means that even at two loops, unitarity is still only probing the on-shell 4-point NLSM amplitude.
-The other cuts besides (b) and (c) are either pathological or vanish because they involve a 3pt point on-shell amplitude (which vanishes on general grounds for scalar theories).
-In order to manifest the $\mathbb{Z}_2$ symmetry of NLSM at the integrand level, we enforce that all non-pathological cuts containing a 3pt vertex (such as the maximal cut) vanish.
+The only two physical cuts that need to be enforced, shown in \cref{fig:emu}, only involve 4pt vertices meaning that even at two loops, unitarity is still only probing the on-shell 4-point NLSM amplitude.
+Unitarity cuts besides those shown in \cref{fig:emu} are either pathological or vanish because they involve a 3pt point on-shell amplitude (which vanishes on general grounds for scalar theories).
+In order to manifest the $\mathbb{Z}_2$ symmetry of NLSM at the integrand level, we require that all non-pathological cuts containing a 3pt vertex (such as the maximal cut) vanish.
 Imposing all relevant cuts leaves 765 free parameters representing the generalized gauge freedom in the answer.
@@
 However, the plethora of generalized gauge freedom parameters leaves the option for enforcing additional aesthetic constraints.
+All remaining generalized gauge parameters could be set to zero but a simpler and more insightful result can be obtained through physical arguments.
 $\mathcal{N}=4$ SYM provides several hints for further conditions to impose on the ansatz.
-For example, for maximally supersymmetric gauge theory it is possible to enforce the no triangle hypothesis, manifest loop power counting, and, at least for 4-point and up to four loops, strip off a factor of $st A_\text{tree}$ from the integrand (I'm not sure I know all of the papers to cite here).
+For example, for maximally supersymmetric gauge theory it is possible to enforce the no triangle hypothesis, manifest loop power counting, and, at least for 4-point and up to four loops, strip off a factor of $st A_\text{tree}$ from the integrand \citepls{Alex, I'm not sure I know what papers to cite here.}.
 For the NLSM integrand it is desirable to make color-kinematics duality as manifest as possible.
@@
 
-Why don't you just set all of the generalized gauge freedom parameters to zero?
-You can learn useful things by not doing this (see N=4), this allows us to introduce more physics into the problem, and, unsurprisingly, setting them to zero produces a more complex answer with more unwieldy rational numbers than using physics.
-
 ZM theory is governed by the Lagrangian
@@
 where more details can be found in \cref{sec:CKLagrangians}.
-The color-stripped Feynman rule for the vertex is simply $V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where off-shell color-kinematics duality to all orders in perturbation theory simply follows from the Schouten identity.
+The color-stripped Feynman rule for the vertex is $V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where off-shell color-kinematics duality to all orders in perturbation theory simply follows from the Schouten identity.
 Since the theory only has a cubic vertex and the theory has manifest off-shell color-kinematics duality, it is trivial to read off the color-dual numerator for any graph.
@@
 On-shell ZM amplitudes naturally divide into sectors corresponding to the configuration of left and right movers, where the scattering in many sectors is rather subtle.
-Only \emph{ordered} amplitudes can be defined unambiguously from the Feynman rules.
+Only color-ordered amplitudes can be defined unambiguously from the Feynman rules.
 At 4-point, only the alternating sector is free of subtleties and the amplitude for this process vanishes.
 In equations, $A[LRLR]=0$ where $R$ corresponds to a right mover and $L$ corresponds to a left mover.
-In every other configuration of right and left movers, such as $A[RRRR]$, one of the internal propagators is incidentally on-shell since $k_R^2=k_L^2=0$.
+In every other configuration of right and left movers, such as $A[RRRR]$, one of the internal propagators is accidentally on-shell since $k_R^2=k_L^2=0$.
 
@@
 Since ZM theory is only being used for the kinematical structure of its numerators, it is natural to introduce a proportionality constant $z$ between the NLSM and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.
-The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically \cite{Nappi:1979ig}.}
+The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically in two dimensions \cite{Nappi:1979ig}.}
 This introduces an extra degree of freedom into the problem.
@@
 \ace{I'm punting a lot of discussion to Ref \cite{Carrasco:2023qgz}.
-  Do we think that is a problem?}
-
-\begin{figure}
-  \begin{center}
-	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
-  \end{center}
-  \caption{The two physical cut topologies shared by sGal, BI, and DBIVA}
-  \label{fig:emu}
-\end{figure}
-
-With a cubic color-dual pion representation in hand, we can perfrom
+  Do we think that is a problem?} \jm{I think that's fine.}
+
+With a cubic color-dual pion representation in hand, we can perform
 double copies with many theories to extract ``gravitational''
@@
 the single copy conspire to produce the double-copy theory's version
-of ``diff. invariance'' \citepls{}.  With pions as one of our single
+of ``diffeomorphism invariance'' \citepls{}.  With pions as one of our single
 copies, we will look at producing numerators for special Gallileons,
@@
 construction \cite{Carrasco:2023qgz}.  One of the shared features of
-these 3 theories is that they all have the same physical cut
+these three theories is that they all have the same physical cut
 topologies in 4D: the two diagrams shown in \cref{fig:emu}, which are
-only composed of even-point amplitudes.
+only composed of four-point amplitudes.
 
@@
 and the cubic $\mathcal{N}=4$ sYM representation from the well-known
-$n_{\text{DB}} = n_{\text{CB}} = s^2t\, \atree)$ \citepls{}.
+$n_{\text{DB}} = n_{\text{CB}} = s^2t\, \atree$ \citepls{}.
 On the other hand, we use the methods of Ref.~\cite{Carrasco:2023qgz}
-to directly compute the needed basis cuts in all 3 theories without
+to directly compute the needed basis cuts in all three theories without
 relying on a color-dual pion representation.  We find exact agreement
@@
 \jm{Rather than quoting the number of parameters in the BDN ansatz, I would prefer to just focus on what we did since it's more general.
-I don't want it to sound like we just patched a minor hole in their argument when I think you've done something much cooler by pinpointing the failure to the bowtie graph.}
-
-Two-loop color-dual integrands for non-supersymmetric YM have been investigated before but only for a limited ansatz that manifests locality \cite{Bern:2015ooa}.
-
-Given the close ties between pion and gluon scattering for trees and
-at one loop, the success of a globally color-dual solution for pions
-at two loops warrants a reexamination of the two-loop pure Yang--Mills
-problem.  As discussed above in \cref{sec:bootstrap}, BDN failed at
-finding an off-shell color-dual representation satisfying 7
-assumptions, and were forced to develop an on-shell notion of
-color-kinematics duality \cite{Bern:2015ooa}.  Thus we must decide
-which assumption(s) to break.  From both a motivation and
-implementation standpoint, the simplest assumption to break is the
-``power-counting'' statement, which we now analyze.
-
-We follow the same general procedure as outlined above, again
+I don't want it to sound like we just patched a minor hole in their argument when I think you've done something much cooler by pinpointing the failure to the bowtie graph.
+I know you put time and effort into analyzing the BDN ansatz but I'm worried that the more we talk about it, the more it will overshadow the real success here.}
+
+Given the close ties between pion and gluon scattering for trees and at one loop, the existence of the two-loop pion numerator prompts us to investigate the most general local numerator for YM, without any of the loop power counting assumptions of  \cite{Bern:2015ooa}.
+We follow the same general procedure as in \cref{sec:pions}, again
 identifying the double-box and penta-triangle as the Jacobi basis
-graphs and building a generic ansatz for each of their numerators.
+graphs and building a the most general ansatz for each of their numerators compatible with the assumptions in \cref{sec:bootstrap}.
 Because we are now considering pure Yang--Mills, each monomial in the
@@
 in addition to the purely momentum-dependent terms show in
-\cref{eq:scalar-basis}.  In our labeling of the two loop Jacobi-basis
+\cref{eq:scalar-basis} where $\mathcal{N}_{\text{2box}}$ and $\mathcal{N}_{\text{pt}}$ represent the numerators of the double-box and penta-triangle respectively.
+In our labeling of the two loop Jacobi-basis
 diagrams, shown in \cref{eq:jacobi-basis}, we find that the power
@@
 Seven of these next-to-maximal cuts are consistent with the kinematic Jacobi
-relations and symmetries.  Interestingly, the ``bowtie'' or ``kissing-triangles''
+relations and symmetries.  Critically, the ``bowtie'' or ``kissing-triangles''
 cut,
@@
 involving four polarizations and six momenta (any combination of
-external or loop).  Each ansatz will be 10,010 terms initially.  Next
+external or loop).  Each ansatz will have 10,010 terms initially.  Next
 impose the symmetry constraints on each of the three diagrams, leaving
@@
 symmetry, and the kinematic Jacobi relations for just three diagrams
-are incompatible with the ``bowtie'' cut.
+are incompatible with the ``bowtie'' cut. \jm{Insert clip of Gordon Ramsay saying ``delicious'' here.}
 
@@
 \section{Spinor-helicity and conventions}\label{Conventions}
-\jm{I would be happy to say that we use a mostly minus metric and the spinor helicity conventions of \cite{jjmcTASI2014} in the introduction and omit this appendix.}
 
@@
 
-\section{Notes to self -- James}
-\jm{Notes to self -- James}
-\begin{itemize}
-\item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
-\item Cite papers arguing about whether NLSM in 2D is non-trivial or not.
-\item Explain why you need to take a certain portion of the YZ numerator to get the right answer.
-Basically you can't have a vector particle circle the loop -- NLSM is a scalar theory so only scalar DOF should actually live in cuts.
-If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
-\item Reiterate that the tree amplitudes of SDYM are zero and 1-loop is the first interesting case.
-\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
-This observation is due to other people but an easy way to see it.
-ZM and 2D NLSM have the same EOM after a field redefinition.
-This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
-\item Forcing pions to match ZM in 2D does funny things.
-The pion coupling constant is dropped but is implicitly set by the ordered 4-point amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
-I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
-Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
-For 4-point tree, $z=2/3$ (I matched the half ladder).
-For 4-point 1-loop, $z$ is free/pure generalized gauge (I matched the box).
-For 4-point 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
-For 6pt tree, $z$ is 12/35 (I matched the half ladder).
-So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
-Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
-\item Explain how matching to ZM is a little silly.
-Check that NLSM and ZM numerator agree on cuts.
-Can't do that or else it becomes subtle.
-Only well defined object is numerator.
-\item At 4-point 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
-At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
-\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.
-So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\varepsilon$ identities.
-Make an ansatz where you do every pairing of $\varepsilon$'s.
-This doesn't work.
-\item To clean up the NLSM 4-point 2-loop answer I forced the answer to match ZM in 2D.
-The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
-I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
-\item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
-\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4-point, 6pt, and 8pt.
-\item Should probably give the 4-point pion amplitude somewhere to show my conventions.
-\end{itemize}
+\section{Notes to self}
+\jm{Nic, this used to be where my notes to myself were but I deleted them.  It looks like you wrote yourself some notes here.  Do you still want them?}
+
 \be \label{YMSvert}

### 2023-09-20 notes/2loopNLSM.tex
some edits in intro & abstract

@@
   representations must be constructed at the multi-loop level. First
-  we identify a cubic theory, \emph{semi-abelian} Yang--Mills, that
-  unifies many of the color-dual theories constructed in the
-  literature, and provides a construction of color-dual numerators at
-  one-loop directly from Feynman rules. Joint consideration of these
-  theories highlights that the lifting of one-loop color-kinematics
-  dual numerators to two loops may be just as challenging as the step
-  from tree level to one loop.  As a first step in understanding the
+  we identify a cubic theory, semi-abelian Yang--Mills, that
+  unifies many of the color-dual theories studied in the
+  literature, and provides a prescriptive approach for constructing color-dual numerators at
+  one-loop directly from Feynman rules. Consideration of this
+  theory highlights that the lifting from one-loop color-kinematics
+  dual numerators to two loops is just as challenging as the progression
+  from tree-level to one-loop.  As a first step in understanding the
   two-loop challenge, we construct color-dual two-loop four-point
-  non-linear sigma model (NLSM) numerators using generalized unitarity
-  methods.  The double-copy of the constructed NLSM numerators with
-  themselves, $\mathcal{N}=0$ Yang--Mills, and $\mathcal{N}=4$
-  Yang--Mills correctly reproduce the known physical unitarity cuts of
+  nonlinear sigma model (NLSM) numerators using a $D$-dimensional color-dual bootstrap.  The double-copy of the constructed NLSM numerators with
+  themselves, pure Yang--Mills, and $\mathcal{N}=4$
+  super-Yang-Mills correctly reproduce the known physical unitarity cuts of
   special Gallileons, Born-Infeld theory, and
@@
   numerators are in explicit tension with generalizations of the
-  one-loop NLSM numerators. \ace{I realize that we all know this, but
-    does/will a statement to this effect actually make it into the
-    draft?}
-We find that the most general \emph{local} numerator for two-loop four-point numerator for $\mathcal{N}=0$ YM fails global color-kinematics duality and we pinpoint the failure to the kissing-triangles cut.
+  one-loop NLSM numerators.
+Using our constructive bootstrap, we also find that the most general \emph{local} two-loop four-point numerator for pure Yang-Mills fails to satisfy global color-kinematics duality.
+We pinpoint the failure to the bow-tie unitarity cut, and discuss a path towards \emph{non-local} construction of color-dual integrands at generic loop order.
 
@@
 Since the turn of the century, our understanding of the $S$-matrix and
-its hidden structures has expanded dramatically. At the heart of this
+its concealed structures has expanded dramatically. At the heart of this
 progress is the mantra that physical observables are simpler when
@@
 color-dual bootstrap. In contrast to much of the available literature
-on construction of color-dual integrands at two-loop
+on color-dual integrand construction at two-loop
 \cite{Bern:2013yya,Mogull:2015adi,Johansson:2017bfl}, our results are
@@
 suited for algorithmically extracting rational terms from the
-$D$-dependence of dimensionally regulated loop momenta. We are able to
-achieve this by employing a custom solver, \texttt{FiniteFieldSolve},
+$D$-dependence of dimensionally regulated loop momenta.
+Prior to this work, one of the primary barriers in studying multi-loop color-dual integrands $D$-dimensionally is the explosion of terms that one encounters in generic ansatz-based constructions at high-loop order.
+We were able overcome this barrier by employing a custom solver, \texttt{FiniteFieldSolve},
 which will soon be made public. \ace{This either needs an extra
@@
 However in sharp contrast, we find that Yang-Mills
-does not permit a globally color-dual representation, even when considering the most general
+does \emph{not} permit a globally color-dual representation, even when considering the most general
 polynomial ansatz of Lorentz covariant kinematics.\footnote{Globally color-dual local numerators for two-loop pure YM have been studied before but only in the context of a limited ansatz subject to certain loop power counting constraints \cite{Bern:2015ooa}.}
-Concretely, the failure point can be pinpointed to a conflict between between the ``bowtie'' cut and the following Jacobi triple
+Concretely, the failure point can be pinpointed to a conflict between between the ``bowtie'' cut and the following Jacobi triple:
 \begin{equation}
@@
 theoretic locality in order to accommodate the construction of
-globally color-dual multi-loop integrands.
+globally color-dual integrands at generic loop order.
 
@@
 \begin{equation}
-{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}V^{b_1a_3b_2}\cdots V^{b_{n-3} a_{n-2}a_n}\,.
+{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}P_{b_1 c_1}V^{c_1 a_3b_2}\cdots P_{b_{n-3}c_{n-3}}V^{c_{n-3} a_{n-1}a_n}\,.
 \end{equation}
@@
 
-When an off-shell color-dual Lagrangian is not known, the amplitude integrand must be constructed from an ansatz.  The four conditions we impose on an integrand ansatz are summarized
+When an off-shell color-dual Lagrangian is not known, the loop-level amplitude integrand must be constructed from an ansatz.  The four conditions we impose on an integrand ansatz are summarized
 here and elaborated on below.\footnote{The four ansatz conditions are

### 2023-09-20 notes/2loopNLSM.tex
Small edits.

--- 2023-09-20 notes/2loopNLSM.tex
@@
 % Comment the following out to compile new images
-%
-%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-%\usetikzlibrary{external}  
-%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-%\tikzexternalize[                     %% Activate externalization
-% prefix=images/,                    %% Avoid cluttering the directory
-% system call={                       %% Use lualatex in system call
-%    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
-% },
-%]
+
+\usetikzlibrary{external}  
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\tikzexternalize[                     %% Activate externalization
+prefix=images/,                    %% Avoid cluttering the directory
+system call={                       %% Use lualatex in system call
+   pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
+},
+]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:cubic}
-Here we will describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
-It has to do with how the vector state sum mixes with the four-point contact.
-Starting with the Yang-Mills Lagrangian,
-\begin{equation}
-\mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2 + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
-\end{equation}
-we can express the YM three-point interaction in terms of the following vertex in Lorenz gauge
+Here we will describe why constructing the full Yang-Mills kinematic
+algebra (outside the self-dual sector) is generically hard, and why
+the same reason makes NLSM beyond one-loop hard as well. The major
+obstacle stems from the vector state sum mixing with higher-point
+contacts. Starting with the Yang-Mills Lagrangian,
+\begin{equation}
+  \mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2
+  + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu
+  + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
+\end{equation}
+we can express the YM three-point interaction in terms of the
+following vertex in Lorenz gauge
 \begin{equation}
@@
 \end{equation}
-This kinematic generator is anti-symmetric in $1\leftrightarrow 2$ exchange, and from it we can construct the full Lorenz gauge Yang-Mills vertex by summing over cyclic permutations
+This kinematic generator is anti-symmetric in $1\leftrightarrow 2$
+exchange, and from it we can construct the full Lorenz gauge
+Yang-Mills vertex by summing over cyclic permutations
 \begin{equation}
@@
 \end{equation}
-Contracting this with the vector state sum, we can see that the cubic Yang-Mills vertex does not satisfy the four-point Jacobi identity
-\be\label{cubicJac}
+Contracting this with the vector state sum, we can see that the cubic
+Yang-Mills vertex does not satisfy the four-point Jacobi identity
+\begin{equation}
+  \label{cubicJac}
   {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4+\text{cyc}(234) = \varepsilon_{(12)}  \varepsilon_{(34)} (s_{13}-s_{23}) +\text{cyc}(234) \neq 0
@@
 where $ \varepsilon_{(ij)} = \varepsilon_{i}\cdot \varepsilon_{j}$.
-The remaining terms can be absorbed into the definition of the four-point kinematic numerator
+The remaining terms can be absorbed into the definition of the
+four-point kinematic numerator
 \begin{equation}
@@
 \end{equation}
-where $V_{\text{YM}+B}$ indicates the introduction of an additional two-form studied in \cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian.
-After the introduction of the 2-form, the numerators now satisfy the Jacobi identity
-\be
-{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
-\ee
-where the new cubic Lagrangian takes the form
-\be
-\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 - B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu A^c_\nu\, .
-\ee 
-Of course, higher multiplicity would require further redefinition of the three-point vertex to satisfy Jacobi identites on all internal edges.
-While introducing successively higher spin states could in principle work at tree level, we will see that it is not consistent with what we find at general loop order.
-We will comment on this in \sect{}.
-For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.
-
-As can be seen above, the Jacobi identity of \cref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$.
-Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions
+where $V_{\text{YM}+B}$ indicates the introduction of an additional
+two-form studied in Ref.~\cite{Ben-Shahar:2022ixa} for constructing the
+NMHV Yang-Mills Lagrangian.  After the introduction of the 2-form, the
+numerators now satisfy the Jacobi identity \be {}_1\langle
+V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0 \ee
+where the new cubic Lagrangian takes the form \be
+\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 -
+B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu
+A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu
+A^c_\nu\, .  \ee Of course, higher multiplicity would require further
+redefinition of the three-point vertex to satisfy Jacobi identites on
+all internal edges. While introducing successively higher spin states
+could in principle work at tree level, we will see that it is not
+consistent with what we find at general loop order. We will comment on
+this in \sect{}. For now, we will study how to construct one-loop
+integrands consistent with the color-kinematics by isolating the cubic
+sector of the state sum above.
+
+As can be seen above, the Jacobi identity of \cref{cubicJac} fails
+only in terms with two factors of polarization dot products,
+$(\varepsilon\varepsilon)^2$. Whereas, if we restricted ourselves to
+just considering factors with a single polarization dot product, the
+Jacobi identity of Yang-Mills would be satisfied \textit{off-shell}
+and in arbitrary spacetime dimensions
 \begin{equation}
@@
 \end{equation}
-Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form.
-The organizational principle underlying this construction can be understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog},
+Thus for our approach at one-loop, we aim to build color-dual
+integrands directly from kinematic factors of this form. The
+organizational principle underlying this construction can be
+understood in terms of a polarization decomposition of vector
+amplitudes introduced by one of the authors \cite{Pavao:2022kog},
 \begin{equation}\label{eq:pureVecRABD}
@@
 \end{equation}
-\jm{Nic, could you give a quick recap of what all of the symbols mean in the equation above?}
-By a simple mass-dimensioin argument, we know the tree-level cubic sector of Yang-Mills must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$,
+\jm{Nic, could you give a quick recap of what all of the symbols mean
+  in the equation above?}  By a simple mass-dimensioin argument, we
+know the tree-level cubic sector of Yang-Mills must be at
+$\mathcal{O}((\varepsilon\varepsilon)^1)$,
 \begin{equation}
@@
 \end{equation}
-while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products,
+while at one-loop, the cubic sector corresponds to
+$\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot
+products,
 \begin{equation}
@@
 \end{equation}
-When decomposed in this way, the polarization stripped building blocks must obey a set of Ward-identities between different ``helicity'' (or $(\varepsilon \varepsilon)$) sectors in order for the full amplitude to be gauge invariant,
+When decomposed in this way, the polarization stripped building blocks
+must obey a set of Ward-identities between different ``helicity'' (or
+$(\varepsilon \varepsilon)$) sectors in order for the full amplitude
+to be gauge invariant,
  \begin{equation}\label{eq:GIrelA}
@@
 \end{equation}
-With this in hand, we can construct a Lagrangian description of the of the cubic sector for Yang-Mills, and will demonstrate that the resulting amplitudes with manifestly color-dual Feynman rules are equivalent to both SDYM and NLSM through one-loop.
+With this in hand, we can construct a Lagrangian description of the of
+the cubic sector for Yang-Mills, and will demonstrate that the
+resulting amplitudes with manifestly color-dual Feynman rules are
+equivalent to both SDYM and NLSM through one-loop.
+
 \subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
-As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell.
-However, the contrapositive is also true -- if we omit the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.
-
-We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G$ to $G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$.
-However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preferred $U(1)$-directions.
-We call this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
+As we demonstrate above, if we include factors of
+$(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to
+keep the Yang-Mills four-point contact for color-kinematics duality to
+be restored on-shell. However, the contrapositive is also true -- if
+we omit the four-point Yang-Mills vertex, then we only need terms that
+contribute to the manifestly color-dual cubic sector of the theory.
+
+We can achieve this construction by splitting the gauge group of the
+full Yang-Mills action from $G$ to $G_L \times G_R$, where the full
+non-abelian gauge symmetry is restored only when we identify
+$G_L = G_R$. However, if we break the left gauge group down to
+$G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to
+$G_R \rightarrow U(N)$, then we are left with a semi-abelian theory
+that is gauge invariant in the preferred $U(1)$-directions. We call
+this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
 \begin{eBox}
@@
 \end{equation}
-Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents.
-Indeed, as we describe in Appendix \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{Cheung:2016prv}, J-theory \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills \cite{Monteiro2011pc}.
-Specifically, semi-Abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
-The Feynman rule for the cubic vertex is
+Here we can think of the abelian vector as a background field that
+sources on-shell $A_\mu$ currents. Indeed, as we describe in Appendix
+\cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
+heart of YZ-theory \cite{Cheung:2016prv}, J-theory
+\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
+\cite{Monteiro2011pc}.  Specifically, semi-Abelian YM is simply a
+clever reinterpretation of the Lagrangian obtained by integrating an
+auxiliary field into the J-theory equations of motion.  The Feynman
+rule for the cubic vertex is
 \begin{equation}
@@
 \end{equation}
-The propagator kinetic mixes between the two gauge fields and has the standard Feynman rule of $i/k^2$.
-We can use the Ward identity of \cref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant when the abelian polarizations are taken to be longitudinal, $\bar{\varepsilon} \rightarrow k$.
-
-We can select out both of these manifestly cubic sectors by selecting only $\varepsilon^+\varepsilon^+$ in light-cone gauge (i.e.
-SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states.
-Indeed, the $D$-dimensional description of $J$-theory is just the following blocks in the expansion of Yang-Mills given in \ref{Pavao:2022kog}
+The propagator kinetic mixes between the two gauge fields and has the
+standard Feynman rule of $i/k^2$.  We can use the Ward identity of
+\cref{eq:GIrelA} to check that the amplitudes are indeed gauge
+invariant when the abelian polarizations are taken to be longitudinal,
+$\bar{\varepsilon} \rightarrow k$.
+
+We can select out both of these manifestly cubic sectors by selecting
+only $\varepsilon^+\varepsilon^+$ in light-cone gauge (i.e. SDYM) and
+one-minus at tree-level OR what $J$-theory and $YZ$-theory select with
+their on-shell states. Indeed, the $D$-dimensional description of
+$J$-theory is just the following blocks in the expansion of Yang-Mills
+given in \ref{Pavao:2022kog}
 \begin{equation}
@@
 \end{equation}
-To recover NLSM at one-loop, we need to extract the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars
+To recover NLSM at one-loop, we need to extract the $D$-dependent part
+that corresponds to an internal $YY$-loop from extra-dimensional
+scalars
 \begin{eBox}
@@
 \end{eBox}
-Why must we take the derivative with respect to $D$?
-After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators.
-However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes.
-Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes.
-However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit.
-We will construct these one-loop integrands below in the next section.
+Why must we take the derivative with respect to $D$? After all,
+$J$-theory and $YZ$-theory both have well defined propagators for
+internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we noted
+in the previous section, all the $J$ and $Z$ states must be on-shell
+in order to produce NLSM amplitudes. Thus, the unitarity cuts of $J$
+theory at one-loop will not produce NLSM amplitudes. However, the
+internal $YY$-loop is a valid forward limit, since as constructed YZ
+theory is valid for off-shell Y-particles, and thus they serve as a
+valid forward limit. We will construct these one-loop integrands below
+in the next section.
 

### 2023-09-20 notes/2loopNLSM.tex
Updated image cache

--- 2023-09-20 notes/2loopNLSM.tex
@@
 % Comment the following out to compile new images
-%
-%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-%\usetikzlibrary{external}  
-%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-%\tikzexternalize[                     %% Activate externalization
-% prefix=images/,                    %% Avoid cluttering the directory
-% system call={                       %% Use lualatex in system call
-%    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
-% },
-%]
+
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\usetikzlibrary{external}  
+\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+\tikzexternalize[                     %% Activate externalization
+ prefix=images/,                    %% Avoid cluttering the directory
+ system call={                       %% Use lualatex in system call
+    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
+ },
+]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-09-20 notes/2loopNLSM.tex
Fixed broken refs

@@
 SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states.
-Indeed, the $D$-dimensional description of $J$-theory is just the following blocks in the expansion of Yang-Mills given in \ref{Pavao:2022kog}
+Indeed, the $D$-dimensional description of $J$-theory is just the following blocks in the expansion of Yang-Mills given in \cite{Pavao:2022kog}
 \begin{equation}
@@
 This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop.
-For more background, we refer the reader to appendix \ref{}.
+For more background, we refer the reader to \cref{sec:CKLagrangians}.
 \begin{equation}

### 2023-09-20 notes/2loopNLSM.tex
Standardized 'semi-abelian'

@@
 Indeed, as we describe in Appendix \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{Cheung:2016prv}, J-theory \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills \cite{Monteiro2011pc}.
-Specifically, semi-Abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
+Specifically, semi-abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
 The Feynman rule for the cubic vertex is
@@
 At tree level, the duality can be manifested by breaking manifest Bose symmetry at the Lagrangian level, either by explicitly picking different gluon states (as in SDYM) or by picking states that only restore Bose symmetry in the final amplitude (as in NLSM).
-All of these theories can be encapsulated in the semi-Abelian YM theory presented in \cref{eq:semiYM} which obscures the Bose symmetry of the external states due to the presence of the two gauge fields $A_\mu$ and $\bar{A}_\mu$.
-The kinetic mixing between the two gauge fields permits globally color-dual 1-loop integrands, but special care must be taken so that the integrands produced from semi-Abelian YM correspond to SDYM or NLSM.
-Due to the kinetic mixing that stems from the broken Bose symmetry, it is impossible to construct a 2-loop integrand for semi-Abelian YM theory, that is, the theory is 1-loop exact.
+All of these theories can be encapsulated in the semi-abelian YM theory presented in \cref{eq:semiYM} which obscures the Bose symmetry of the external states due to the presence of the two gauge fields $A_\mu$ and $\bar{A}_\mu$.
+The kinetic mixing between the two gauge fields permits globally color-dual 1-loop integrands, but special care must be taken so that the integrands produced from semi-abelian YM correspond to SDYM or NLSM.
+Due to the kinetic mixing that stems from the broken Bose symmetry, it is impossible to construct a 2-loop integrand for semi-abelian YM theory, that is, the theory is 1-loop exact.
 Obtaining a globally color-dual integrand beyond 1-loop then requires sacrificing more than just Bose symmetry and in this paper it is argued that off-shell locality must be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in order to obtain color-dual 2-loop integrands.}
@@
 Below we review the four manifestly color-dual theories that appear in this paper, in particular SDYM, two formulations of NLSM, and ZM.
-All of these theories are closely tied together by the semi-Abelian YM theory in \cref{eq:semiYM} or in other words the cubic sector of YM.
+All of these theories are closely tied together by the semi-abelian YM theory in \cref{eq:semiYM} or in other words the cubic sector of YM.
 The manifestly color-dual equations of motion for SDYM and NLSM are derived by picking a gauge and then placing a constraint not on the YM equation of motion or Bianchi identity but rather directly on the field strength itself.
@@
 In almost all of these theories, Bose symmetry is broken or obscured at the Lagrangian level.
-Because of the broken Bose symmetry (and the inherited kinetic mixing of semi-Abelian YM), these theories cannot produce color-dual numerators at 2-loop or higher.
+Because of the broken Bose symmetry (and the inherited kinetic mixing of semi-abelian YM), these theories cannot produce color-dual numerators at 2-loop or higher.
 
@@
 \end{equation}
-Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-Abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
-In other words, \emph{J-theory and semi-Abelian YM are identical}.
+Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
+In other words, \emph{J-theory and semi-abelian YM are identical}.
 By calculating an off-shell 4-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.

### 2023-09-20 notes/2loopNLSM.tex
Lorenz gauge concern

@@
 \begin{equation}
-F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c .
-\end{equation}
+F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
+\end{equation}
+where $A_\mu$ is in Lorenz gauge.
+\jm{I'm pretty sure A has to be in Lorenz gauge.}
 Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents.
@@
 
+\jm{Do you need to put semi-Abelian YM in axial/lightcone gauge in order to recover SDYM?}
 We can select out both of these manifestly cubic sectors by selecting only $\varepsilon^+\varepsilon^+$ in light-cone gauge (i.e.

### 2023-09-20 notes/2loopNLSM.tex
Lorenz gauge comment

--- 2023-09-20 notes/2loopNLSM.tex
@@
 \begin{equation}
-F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c .
-\end{equation}
+F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
+\end{equation}
+and $A_\mu$ is in Lorenz gauge.
 Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents.
@@
 Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
-In other words, \emph{J-theory and semi-abelian YM are identical}.
+Since both theories are in Lorenz gauge this means that \emph{J-theory and semi-abelian YM are identical}.
 By calculating an off-shell 4-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.

### 2023-09-20 notes/2loopNLSM.tex
More comments from readthrough.

--- 2023-09-20 notes/2loopNLSM.tex
@@
 
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
 \usetikzlibrary{external}  
@@
 \begin{enumerate}
+\item Settle on $n$ vs $N$ vs $\mathcal{N}$ as the symbol for
+  numerator
 \item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
@@
 suited for algorithmically extracting rational terms from the
-$D$-dependence of dimensionally regulated loop momenta.
-Prior to this work, one of the primary barriers in studying multi-loop color-dual integrands $D$-dimensionally is the explosion of terms that one encounters in generic ansatz-based constructions at high-loop order.
-We were able overcome this barrier by employing a custom solver, \texttt{FiniteFieldSolve},
-which will soon be made public. \ace{This either needs an extra
-  context sentence, or moved out of the intro.}
+$D$-dependence of dimensionally regulated loop momenta. Prior to this
+work, one of the primary barriers in studying multi-loop color-dual
+integrands $D$-dimensionally is the explosion of terms that one
+encounters in generic ansatz-based constructions at high-loop
+order. We were able overcome this barrier by employing a custom
+solver, \texttt{FiniteFieldSolve}, which will soon be made
+public.
 
@@
 
-\ace{End of Alex first readthrough}
-
 \section{One-loop cubic construction}
 \label{sec:cubic}
-Here we will describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well.
-It has to do with how the vector state sum mixes with the four-point contact.
-Starting with the Yang-Mills Lagrangian,
-\begin{equation}
-\mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2 + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
-\end{equation}
-we can express the YM three-point interaction in terms of the following vertex in Lorenz gauge
+Here we will describe why constructing the full Yang-Mills kinematic
+algebra (outside the self-dual sector) is generically hard, and why
+the same reason makes NLSM beyond one-loop hard as well. The major
+obstacle stems from the vector state sum mixing with higher-point
+contacts. Starting with the Yang-Mills Lagrangian,
+\begin{equation}
+  \mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2
+  + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu
+  + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
+\end{equation}
+we can express the YM three-point interaction in terms of the
+following vertex in Lorenz gauge
 \begin{equation}
@@
 \end{equation}
-where $V_{\text{YM}+B}$ indicates the introduction of an additional two-form studied in \cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian.
-After the introduction of the 2-form, the numerators now satisfy the Jacobi identity
-\be
-{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
-\ee
+where $V_{\text{YM}+B}$ indicates the introduction of an additional
+two-form studied in Ref.~\cite{Ben-Shahar:2022ixa} for constructing the
+NMHV Yang-Mills Lagrangian.  After the introduction of the 2-form, the
+numerators now satisfy the Jacobi identity
+\begin{equation}
+  {}_1\langle
+  V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
+\end{equation}
 where the new cubic Lagrangian takes the form
-\be
-\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 - B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu A^c_\nu\, .
-\ee 
-Of course, higher multiplicity would require further redefinition of the three-point vertex to satisfy Jacobi identites on all internal edges.
-While introducing successively higher spin states could in principle work at tree level, we will see that it is not consistent with what we find at general loop order.
-We will comment on this in \sect{}.
-For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.
-
-As can be seen above, the Jacobi identity of \cref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$.
-Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions
+\begin{equation}
+\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 -
+B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu
+A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu
+A^c_\nu\, .
+\end{equation}
+Of course, higher multiplicity would require further redefinition of
+the three-point vertex to satisfy Jacobi identites on all internal
+edges. While introducing successively higher spin states could in
+principle work at tree level, we will see that it is not consistent
+with what we find at general loop order. We will comment on this in
+\cref{sec:Discussion} \ace{Is this the sec you are thinking of?}. For
+now, we will study how to construct one-loop integrands consistent
+with the color-kinematics by isolating the cubic sector of the state
+sum above.
+
+As can be seen above, the Jacobi identity of \cref{cubicJac} fails
+only in terms with two factors of polarization dot products,
+$(\varepsilon\varepsilon)^2$. Whereas if we restricted ourselves to
+just considering factors with a single polarization dot product, the
+Jacobi identity of Yang-Mills would be satisfied \textit{off-shell}
+and in arbitrary spacetime dimensions
 \begin{equation}
@@
 \end{equation}
-Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form.
-The organizational principle underlying this construction can be understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog},
+\ace{Should we mention that this is closely related to MHV vs NMHV?}
+Thus for our approach at one-loop, we aim to build color-dual
+integrands directly from kinematic factors of this form. The
+organizational principle underlying this construction can be
+understood in terms of a polarization decomposition of vector
+amplitudes introduced by one of the authors \cite{Pavao:2022kog},
 \begin{equation}\label{eq:pureVecRABD}
@@
 \end{equation}
-With this in hand, we can construct a Lagrangian description of the of the cubic sector for Yang-Mills, and will demonstrate that the resulting amplitudes with manifestly color-dual Feynman rules are equivalent to both SDYM and NLSM through one-loop.
+With this in hand, we can construct a Lagrangian description of the of
+the cubic sector for Yang-Mills, and will demonstrate that the
+resulting amplitudes with manifestly color-dual Feynman rules are
+equivalent to both SDYM and NLSM through one-loop.
+
 \subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
-As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell.
-However, the contrapositive is also true -- if we omit the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.
-
-We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G$ to $G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$.
-However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preferred $U(1)$-directions.
-We call this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
+As we demonstrate above, if we include factors of
+$(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to
+keep the Yang-Mills four-point contact for color-kinematics duality to
+be restored on-shell. However, the contrapositive is also true -- if
+we omit the four-point Yang-Mills vertex, then we only need terms that
+contribute to the manifestly color-dual cubic sector of the theory.
+
+We can achieve this construction by splitting the gauge group of the
+full Yang-Mills action from $G$ to $G_L \times G_R$, where the full
+non-abelian gauge symmetry is restored only when we identify
+$G_L = G_R$. However, if we break the left gauge group down to
+$G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to
+$G_R \rightarrow U(N)$, then we are left with a semi-abelian theory
+that is gauge invariant in the preferred $U(1)$-directions. We call
+this manifestly color-dual theory \textit{semi-abelian Yang-Mills},
 \begin{eBox}
@@
 \end{equation}
-Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents.
-Indeed, as we describe in Appendix \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{Cheung:2016prv}, J-theory \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills \cite{Monteiro2011pc}.
-Specifically, semi-abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
-The Feynman rule for the cubic vertex is
-\begin{equation}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
-\end{equation}
-The propagator kinetic mixes between the two gauge fields and has the standard Feynman rule of $i/k^2$.
-We can use the Ward identity of \cref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant when the abelian polarizations are taken to be longitudinal, $\bar{\varepsilon} \rightarrow k$.
-
-We can select out both of these manifestly cubic sectors by selecting only $\varepsilon^+\varepsilon^+$ in light-cone gauge (i.e.
-SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states.
-Indeed, the $D$-dimensional description of $J$-theory is just the following blocks in the expansion of Yang-Mills given in \cite{Pavao:2022kog}
+Here we can think of the abelian vector as a background field that
+sources on-shell $A_\mu$ currents. Indeed, as we describe in Appendix
+\cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
+heart of YZ-theory \cite{Cheung:2016prv}, J-theory
+\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
+\cite{Monteiro2011pc}.  Specifically, semi-Abelian YM is simply a
+clever reinterpretation of the Lagrangian obtained by integrating an
+auxiliary field into the J-theory equations of motion.  The Feynman
+rule for the cubic vertex is
+\begin{equation}
+  \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
+  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
+\end{equation}
+The kinetic term mixes the two gauge fields and has the standard
+Feynman rule of $i/k^2$.  We can use the Ward identity of
+\cref{eq:GIrelA} to check that the amplitudes are indeed gauge
+invariant when the abelian polarizations are taken to be longitudinal,
+$\bar{\varepsilon} \rightarrow k$.
+
+We can select out both \ace{which both?} of these manifestly cubic
+sectors by selecting only $\varepsilon^+\varepsilon^+$ in light-cone
+gauge (i.e. SDYM) and one-minus at tree-level OR what $J$-theory and
+$YZ$-theory select with their on-shell states. Indeed, the
+$D$-dimensional description of $J$-theory is just the following blocks
+in the expansion of Yang-Mills given in Ref.~\cite{Pavao:2022kog}
 \begin{equation}
@@
 \end{eBox}
-Why must we take the derivative with respect to $D$?
-After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators.
-However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes.
-Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes.
-However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit.
-We will construct these one-loop integrands below in the next section.
+Why must we take the derivative with respect to $D$? After all,
+$J$-theory and $YZ$-theory both have well defined propagators for
+internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we discuss
+in \cref{sec:CKLagrangians} \ace{I think this is where we do this
+  now}, all the $J$ and $Z$ states must be on-shell in order to
+produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at
+one-loop will not produce NLSM amplitudes. However, the internal
+$YY$-loop is a valid forward limit for producing NLSM amplitudes,
+since as constructed YZ theory mathces to NLSM for off-shell
+Y-particles. We will construct these one-loop integrands in the
+next section.
 
 \subsection{One-loop color-dual integrands}\label{oneLoopCK}
-Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM).
-At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{Monteiro2011pc}:
+Our first application of this theory for color-dual construction at
+loop level is for self-dual Yang-Mills (SDYM). At tree-level, the
+off-shell cubic vertices can be written in terms of light cone
+coordinates \cite{Monteiro2011pc}:
 \begin{equation}
@@
 \end{equation}
-At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop.
-This can be done using the cubic semi-YM vertices of the previous section:
+At loop-level, this construction needs to be analytically continued to
+general dimension in order to apply dimensional regularization at
+one-loop. This can be done using the cubic semi-YM vertices of the
+previous section:
 \begin{equation}
@@
 \end{equation}
-Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase.
-Of course, this has the advantage of permitting a $D$-dimensional construction of the one-loop integrand.
-Below we provide a four-point example:
+Plugging in on-shell all-plus helicity states in light-cone gauge will
+yield precisely the 4D SDYM vertex, up to an unphysical phase \ace{Can
+  we provide an example?}. Of course, this has the advantage of
+permitting a $D$-dimensional construction of the one-loop
+integrand. Below we provide a four-point example:
 \begin{equation}
@@
 \end{equation}
-Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$.
-By taking a derivative\footnote{Another way to understand this derivative is that it selects the large $D$ behavior of the integrand.}, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
+Due to the state-sum of internal loop factors,
+$\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above
+depends explicitly on the spacetime dimension, $D$. By taking a
+derivative\footnote{Another way to understand this derivative is that
+  it selects the large $D$ behavior of the integrand.}, we can recover
+the integrand needed for all-plus one-loop amplitudes with an internal
+scalar:
 \begin{equation}
@@
 \end{equation}
-This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop.
-For more background, we refer the reader to \cref{sec:CKLagrangians}.
+This integrand numerator with internal scalar loop is precisely what
+one would obtain from the Feynman rules of YZ-theory, absent the $XZ$
+internal vector loop. For more background, we refer the reader to
+\cref{sec:CKLagrangians}.
 \begin{equation}
@@
 Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
+
 \subsection{Two-loop obstruction}\label{2LoopObstruction}
-At two-loop, introducing terms that conspire with four-point contacts is unavoidable.
-At one-loop, we were able to avoid internal contractions of $\bar{A}_\mu A^\mu$ by selecting external states of appropriate weight.
-However, at two-loop when choosing all external $A_\mu$ states, the amplitude vanishes in semi-YM theory:
+At two-loop, introducing terms that conspire with four-point contacts
+is unavoidable. At one-loop, we were able to avoid internal
+contractions of $\bar{A}_\mu A^\mu$ by selecting appropriate external
+states. However, at two-loop when choosing all external $A_\mu$
+states, the amplitude vanishes in semi-YM theory:
 \begin{equation}
@@
 \end{equation}
-In order to produce non-vanishing interactions, we would need to reintroduce $D$-dimensional vertices from the diagonal group of $G_L\times G_R$.
-Doing so will necessarily introduce internal contractions of $\bar{A}_\mu A^\mu$,
+In order to produce non-vanishing interactions, we would need to
+reintroduce $D$-dimensional vertices from the diagonal group of
+$G_L\times G_R$. Doing so will necessarily introduce internal
+contractions of $\bar{A}_\mu A^\mu$,
 \begin{equation}
@@
 \end{equation}
-However, this immediately runs into the difficulty of introducing the four-point contact needed for color-kinematics to be satisfied on all internal edges.
-To do this prescriptively would require knowledge of the full kinematic algebra for Yang-Mills off-shell.
-Since this is presently unavailable, to approach the problem of two-loop construction, we instead employ an ansatz based approach.
-\section{Two-loop bootstrap}\label{2loopBoot}
-We now employ the color-dual bootstrap method described in \cref{sec:bootstrap}.
-We will employ an ansatz constructed from  $D$-dimensionally Lorentz covariant kinematics.
-To fix remaining freedom in the NLSM bootstrap, we will match down to ZM theory in $D=2$.
-This is merely an aesthetic choice, so the final results of both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
+However, this immediately runs into the difficulty of introducing the
+four-point contact needed for color-kinematics to be satisfied on all
+internal edges. To do this prescriptively would require knowledge of
+the full kinematic algebra for Yang-Mills off-shell. Since this is
+presently unavailable, to approach the problem of two-loop
+construction, we instead employ an ansatz based approach.
+
+\section{Two-loop bootstrap}
+\label{2loopBoot}
+\ace{Lets bulk this section intro up a bit}
+
+We now employ the color-dual bootstrap method described in
+\cref{sec:bootstrap}. We will employ an ansatz constructed from
+$D$-dimensionally Lorentz covariant kinematics. To fix remaining
+freedom in the NLSM bootstrap, we will match down to ZM theory in
+$D=2$. This is merely an aesthetic choice, so the final results of
+both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
+
 \subsection{Two-loop NLSM}
@@
 
-As we have seen, it is possible to coerce tree numerators into 1-loop numerators at any multiplicity for pions.
-However, these methods cannot be reapplied to generate higher-loop numerators, which begs the question ``is it possible to find globally color-dual numerators beyond 1-loop''.
-We will tackle this question for 4-point 2-loop scattering in NLSM before moving on to the same process in YM.
-
-Ignoring tadpoles and BEL graphs, there are 14 cubic 4-point 2-loop graphs (see \cref{fig:MaxCuts}) which are related to each other via 21 Jacobi relations.
-As mentioned in \cref{sec:bootstrap}, color-kinematics duality ensures that the numerator of every graph can be expressed in terms of a basis of the double box and penta-triangle,
+As we have seen, it is possible to coerce tree numerators into 1-loop
+numerators at any multiplicity for pions.  However, these methods
+cannot be reapplied to generate higher-loop numerators, which begs the
+question ``is it possible to find globally color-dual numerators
+beyond 1-loop?''  We will tackle this question for 4-point 2-loop
+scattering in NLSM before moving on to the same process in YM.
+
+Ignoring tadpoles and BEL graphs, there are 14 cubic 4-point 2-loop
+graphs (see \cref{fig:MaxCuts}) which are related to each other via 21
+Jacobi relations.  As mentioned in \cref{sec:bootstrap},
+color-kinematics duality ensures that the numerator of every graph can
+be expressed in terms of a basis of the double box and penta-triangle,
 \begin{equation}
@@
 \end{equation}
-For a scalar theory like NLSM the numerator only depends on dot products of momenta.
-The basis of Mandelstam invariants for both of these graphs can be taken to be
+For a scalar theory like NLSM the numerator only depends on dot
+products of momenta.  The basis of momentum invariants for both of
+these graphs can be taken to be
 \begin{equation}
@@
 %%%%
-% Basis for both diagrams
-% {d[p[1], p[3]], d[p[1], p[6]], d[p[1], p[7]], d[p[2], p[3]],  d[p[2], p[6]], d[p[2], p[7]], d[p[3], p[6]], d[p[3], p[7]],  d[p[6], p[6]], d[p[6], p[7]], d[p[7], p[7]]}
+% Basis for both diagrams {d[p[1], p[3]], d[p[1], p[6]], d[p[1],
+% p[7]], d[p[2], p[3]], d[p[2], p[6]], d[p[2], p[7]], d[p[3], p[6]],
+% d[p[3], p[7]], d[p[6], p[6]], d[p[6], p[7]], d[p[7], p[7]]}
 %%%%
-Every vertex in NLSM scales as $k^2$ so the numerator of each diagram scales as $k^{12}$.
-At this mass dimension there are 8,008 independent dot products of momenta.
-With two basis graphs there is a total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is not suited to equations with sixteen thousand parameters so a different method is desirable.
-One possibility is to use a solver designed for integral reduction.
-However, these solvers typically assume that the matrix has a very low density which is not the case for equations coming from NLSM which typically have a density of a few percent.
-While the equations in YM naturally separate into different ``helicity'' sectors (or $e_i \cdot e_j$ and $e_i \cdot k_j$ sectors in $D$ dimensions), there is no such separation of sectors in a scalar theory where any product of momenta can interfere with any other.
-The NLSM constraint equations were solved using a custom solver, \texttt{FiniteFieldSolve}, designed to solve large linear systems of arbitrary density.
-\texttt{FiniteFieldSolve} will be released publicly shortly.}
-Imposing all of the Jacobi relations eliminates all but 4,473 of the original free parameters.
-Further imposing graph symmetries reduces the number of free parameters to 1,243.
+Every vertex in NLSM scales as $k^2$ so the numerator of each diagram
+scales as $k^{12}$.  At this mass dimension there are 8,008
+independent dot products of momenta.  With two basis graphs there is a
+total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is
+  not suited to equations with sixteen thousand parameters so a
+  different method is desirable.  One possibility is to use a solver
+  designed for integral reduction.  However, these solvers typically
+  assume that the matrix has a very low density which is not the case
+  for equations coming from NLSM which typically have a density of a
+  few percent.  While the equations in YM naturally separate into
+  different ``helicity'' sectors (or $e_i \cdot e_j$ and
+  $e_i \cdot k_j$ sectors in $D$ dimensions), there is no such
+  separation of sectors in a scalar theory where any product of
+  momenta can interfere with any other.  The NLSM constraint equations
+  were solved using a custom solver, \texttt{FiniteFieldSolve},
+  designed to solve large linear systems of arbitrary density.
+  \texttt{FiniteFieldSolve} will be released publicly shortly.\ace{I
+    want to rephrase this slightly, but need to think about it a bit
+    more}} Imposing the boundary Jacobi relations eliminates all but
+4,473 of the original free parameters.  Further imposing graph
+symmetries reduces the number of free parameters to 1,243.
 
@@
 
-The final essential constraint is unitarity.
-The only two physical cuts that need to be enforced, shown in \cref{fig:emu}, only involve 4pt vertices meaning that even at two loops, unitarity is still only probing the on-shell 4-point NLSM amplitude.
-Unitarity cuts besides those shown in \cref{fig:emu} are either pathological or vanish because they involve a 3pt point on-shell amplitude (which vanishes on general grounds for scalar theories).
-In order to manifest the $\mathbb{Z}_2$ symmetry of NLSM at the integrand level, we require that all non-pathological cuts containing a 3pt vertex (such as the maximal cut) vanish.
-Imposing all relevant cuts leaves 765 free parameters representing the generalized gauge freedom in the answer.
-
-%It is possible to automatically enforce (or ``bake in'') the double box and penta-triangle max cuts on the ansatz by writing the ansatz in terms of inverse propagators (and remaining irreducible scalar products) and then only keeping terms that involve at least one inverse propagator since those terms will vanish on those max cuts, just as the product of 3pt scalar amplitudes will.
-%However, for the sake of simplicity we do not take this route.
-
-At this point color-kinematics duality has been satisfied, so the double copy will proceed without issue.
-However, the plethora of generalized gauge freedom parameters leaves the option for enforcing additional aesthetic constraints.
-All remaining generalized gauge parameters could be set to zero but a simpler and more insightful result can be obtained through physical arguments.
-$\mathcal{N}=4$ SYM provides several hints for further conditions to impose on the ansatz.
-For example, for maximally supersymmetric gauge theory it is possible to enforce the no triangle hypothesis, manifest loop power counting, and, at least for 4-point and up to four loops, strip off a factor of $st A_\text{tree}$ from the integrand \citepls{Alex, I'm not sure I know what papers to cite here.}.
-For the NLSM integrand it is desirable to make color-kinematics duality as manifest as possible.
-One hope would be to factor out some piece of the 1-loop numerator since this at least manifests antisymmetry for the vertices involving external legs.
-However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}.
+The final essential constraint is unitarity.  The two physical cuts
+that need to be enforced, shown in \cref{fig:emu}, only involve
+4-point vertices.  Notably this means that even at two loops,
+unitarity is still only probing the on-shell 4-point NLSM amplitude.
+Unitarity cuts besides those shown in \cref{fig:emu} are either
+pathological or vanish because they involve a 3pt point on-shell
+amplitude (which vanishes on general grounds for scalar theories
+\ace{This feels like overstating things.  For instance, what about
+  $\phi^3$ or BAS?}).  In order to manifest the $\mathbb{Z}_2$
+symmetry of NLSM at the integrand level, we require that all
+non-pathological cuts containing a 3pt vertex (such as the maximal
+cut) vanishs.  Imposing all relevant cuts leaves 765 free parameters
+representing the generalized gauge freedom in the answer.
+
+% It is possible to automatically enforce (or ``bake in'') the double
+% box and penta-triangle max cuts on the ansatz by writing the ansatz
+% in terms of inverse propagators (and remaining irreducible scalar
+% products) and then only keeping terms that involve at least one
+% inverse propagator since those terms will vanish on those max cuts,
+% just as the product of 3pt scalar amplitudes will.  However, for the
+% sake of simplicity we do not take this route.
+
+At this point color-kinematics duality has been satisfied, so the
+double copy will proceed without issue.  However, the plethora of
+generalized gauge freedom parameters leaves the option for enforcing
+additional aesthetic constraints.  All remaining generalized gauge
+parameters could be set to zero, but a simpler and more insightful
+result can be obtained through physical arguments.  $\mathcal{N}=4$
+SYM provides several hints for further conditions to impose on the
+ansatz.  For example, for maximally supersymmetric gauge theory it is
+possible to enforce the no triangle hypothesis, manifest loop power
+counting, and, for 4-point and up to at least six loops, strip off a
+factor of $st \atree$ from the integrand \cite{FiveLoopN4,
+  Bern:2012uf, Bern:2010fy, SuperSum, Carrasco:2021otn,
+  JJHenrikReview, BRY, BDDPR, Neq44np}.  For the NLSM integrand it is
+desirable to make color-kinematics duality as manifest as possible.
+One hope would be to factor out some piece of the 1-loop numerator
+since this at least manifests antisymmetry for the vertices involving
+external legs.  However, a more fruitful direction is to match onto
+the one known theory with pion power counting that manifests
+color-kinematics duality to all loop orders, namely,
+Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}.
 
@@
 \label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c),
-\end{equation}
-where more details can be found in \cref{sec:CKLagrangians}.
-The color-stripped Feynman rule for the vertex is $V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where off-shell color-kinematics duality to all orders in perturbation theory simply follows from the Schouten identity.
-Since the theory only has a cubic vertex and the theory has manifest off-shell color-kinematics duality, it is trivial to read off the color-dual numerator for any graph.
-From the presence of the Levi-Civita tensor $\varepsilon^{\mu\nu}$, the theory clearly resides in two spacetime dimensions where scattering is notoriously plagued by infrared regulation issues.
-Every on-shell particle is either a right mover, with momentum proportional to $k_R^\mu \equiv (1,1)$, or a left mover, with momentum proportional to $k_L^\mu \equiv (1,-1)$.
-On-shell ZM amplitudes naturally divide into sectors corresponding to the configuration of left and right movers, where the scattering in many sectors is rather subtle.
-Only color-ordered amplitudes can be defined unambiguously from the Feynman rules.
-At 4-point, only the alternating sector is free of subtleties and the amplitude for this process vanishes.
-In equations, $A[LRLR]=0$ where $R$ corresponds to a right mover and $L$ corresponds to a left mover.
-In every other configuration of right and left movers, such as $A[RRRR]$, one of the internal propagators is accidentally on-shell since $k_R^2=k_L^2=0$.
-
-It is tempting to try to match the pion 4-point 2-loop integrand to ZM on the cuts, but given that the cuts only probe the on-shell 4-point amplitude, which is either subtle or vanishes for ZM, it is better to compare the off-shell numerators directly.
-As local functions, the numerators never suffer from any of the subtleties of on-shell 2D kinematics.
-Since the physical cuts are difficult to compare, ZM theory is being used here simply as a tool to eliminate generalized gauge freedom; ZM theory has the right power counting and kinematic structure in 2D to compare against.
-Since ZM theory is only being used for the kinematical structure of its numerators, it is natural to introduce a proportionality constant $z$ between the NLSM and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.
-The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically in two dimensions \cite{Nappi:1979ig}.}
-This introduces an extra degree of freedom into the problem.
-Mechanically, the pion numerator is matched to ZM by first taking every possible assignment of right and left movers for the external particles and then restricting the pion numerator to 2D.
-The loop momenta are restricted to 2D but left off-shell.
-After performing the 2D matching, there are only 365 parameters of generalized gauge freedom.
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2
++ g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c),
+\end{equation}
+where more details can be found in \cref{sec:CKLagrangians}.  The
+color-stripped Feynman rule for the vertex is
+$V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where
+off-shell color-kinematics duality to all orders in perturbation
+theory simply follows from the Schouten identity in 2D.  Since the theory
+only has a cubic vertex and manifest off-shell color-kinematics
+duality, it is trivial to read off the color-dual numerator for any
+graph.  From the presence of the Levi-Civita tensor
+$\varepsilon^{\mu\nu}$, the theory clearly resides in two spacetime
+dimensions where scattering is notoriously plagued by infrared
+regulation issues.  Every on-shell particle is either a right mover,
+with momentum proportional to $k_R^\mu \equiv (1,1)$, or a left mover,
+with momentum proportional to $k_L^\mu \equiv (1,-1)$.  On-shell ZM
+amplitudes naturally divide into sectors corresponding to the
+configuration of left and right movers, where the scattering in many
+sectors is rather subtle.  Only color-ordered amplitudes can be
+defined unambiguously from the Feynman rules.  At 4-point, only the
+alternating sector is free of subtleties and the amplitude for this
+process vanishes.  In equations, $A[LRLR]=0$ where $R$ corresponds to
+a right mover and $L$ corresponds to a left mover.  In every other
+configuration of right and left movers, such as $A[RRRR]$, one of the
+internal propagators is accidentally on-shell since $k_R^2=k_L^2=0$.
+
+\ace{Lets tighten up this paragraph a bit, especially the second half}
+It is tempting to try to match the pion 4-point 2-loop integrand to ZM
+on the cuts, but given that the cuts only probe the on-shell 4-point
+amplitude, which is either subtle or vanishes for ZM, it is better to
+compare the off-shell numerators directly.  As local functions, the
+numerators never suffer from any of the subtleties of on-shell 2D
+kinematics.  Since the physical cuts are difficult to compare, ZM
+theory is being used here simply as a tool to eliminate generalized
+gauge freedom; ZM theory has the right power counting and kinematic
+structure in 2D to compare against.  Since ZM theory is only being
+used for the kinematical structure of its numerators, it is natural to
+introduce a proportionality constant $z$ between the NLSM and ZM
+numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
+parameter $z$, which would normally be fixed on cuts, effectively
+encodes the discrepancy between the coupling constants of the two
+theories.\footnote{Floating the proportionality parameter $z$ is also
+  motivated because ZM is believed to be quantum mechanically
+  different from NLSM even though they are dual classically in two
+  dimensions \cite{Nappi:1979ig}.}  This introduces an extra degree of
+freedom into the problem.  Mechanically, the pion numerator is matched
+to ZM by first taking every possible assignment of right and left
+movers for the external particles and then restricting the pion
+numerator to 2D.  The loop momenta are restricted to 2D but left
+off-shell.  After performing the 2D matching, there are only 365
+parameters of generalized gauge freedom.
 
@@
 \end{equation}
-whereas a generic set of local, cubic Feynman rules could have produced terms with up to $m+n=12$ powers of loop momenta.
-When the pion numerator is forced to have the loop power counting structure in \cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge freedom parameters reduces to 58.
-The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4-point pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}
-
-\subsection{Double-copy verification}\label{doubleCopyVerify}
-\ace{I'm punting a lot of discussion to Ref \cite{Carrasco:2023qgz}.
-  Do we think that is a problem?} \jm{I think that's fine.}
+whereas a generic set of local, cubic Feynman rules could have
+produced terms with up to $m+n=12$ powers of loop momenta.  When the
+pion numerator is forced to have the loop power counting structure in
+\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
+freedom parameters reduces to 58.  The pion numerator appearing in the
+ancillary files makes exactly this choice.\footnote{When the 4-point
+  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
+  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
+  $z$ is fixed to $216/565$, which is clearly unrelated to the
+  difference in coupling constants.} \ace{Is this actually where we
+  want this particular footnote to appear?}
+
+\subsection{Double-copy verification}
+\label{doubleCopyVerify}
 
@@
 double copies with many theories to extract ``gravitational''
-amplitudes.  Such double-copy constructions are important nontrivial
-checks on the underlying single-copy theories: the Jacobi relations in
-the single copy conspire to produce the double-copy theory's version
-of ``diffeomorphism invariance'' \citepls{}.  With pions as one of our single
-copies, we will look at producing numerators for special Gallileons,
-Born-Infeld theory, and DBIVA by double-copying against pions,
-$\mathcal{N}=0$ YM, and $\mathcal{N}=4$ sYM respectively \citepls{}.
-These output theories were recently studied extensively by one of the
-authors and Carrasco from the perspective of direct unitarity cut
-construction \cite{Carrasco:2023qgz}.  One of the shared features of
-these three theories is that they all have the same physical cut
-topologies in 4D: the two diagrams shown in \cref{fig:emu}, which are
-only composed of four-point amplitudes.
+amplitudes.  In particular, we produce numerators for special
+Gallileons, Born-Infeld theory, and DBIVA by double-copying against
+pions, $\mathcal{N}=0$ YM, and $\mathcal{N}=4$ sYM respectively
+\citepls{}.  Such double-copy constructions are important nontrivial
+checks on the underlying single-copy theories as the Jacobi relations
+in the single copy conspire to produce the double-copy theory's
+version of ``diffeomorphism invariance'': XX for sGal, and gauge
+invariance of the BI photon and DBIVA supermultiplet \citepls{}.  All
+three of these double-copy theories were recently studied extensively
+by one of the authors and Carrasco from the perspective of direct
+unitarity cut construction \cite{Carrasco:2023qgz}.  One of the shared
+features of these three theories is that they all have the same
+physical cut topologies in 4D: the two diagrams shown in
+\cref{fig:emu}, which are only composed of four-point amplitudes.
 
@@
 and the cubic $\mathcal{N}=4$ sYM representation from the well-known
-$n_{\text{DB}} = n_{\text{CB}} = s^2t\, \atree$ \citepls{}.
+$n_{2\text{box}} = n_{\text{cross-box}} = s^2t\, \atree$ \citepls{}.
 On the other hand, we use the methods of Ref.~\cite{Carrasco:2023qgz}
@@
 
-\jm{Rather than quoting the number of parameters in the BDN ansatz, I would prefer to just focus on what we did since it's more general.
-I don't want it to sound like we just patched a minor hole in their argument when I think you've done something much cooler by pinpointing the failure to the bowtie graph.
-I know you put time and effort into analyzing the BDN ansatz but I'm worried that the more we talk about it, the more it will overshadow the real success here.}
-
-Given the close ties between pion and gluon scattering for trees and at one loop, the existence of the two-loop pion numerator prompts us to investigate the most general local numerator for YM, without any of the loop power counting assumptions of  \cite{Bern:2015ooa}.
-We follow the same general procedure as in \cref{sec:pions}, again
-identifying the double-box and penta-triangle as the Jacobi basis
-graphs and building a the most general ansatz for each of their numerators compatible with the assumptions in \cref{sec:bootstrap}.
-Because we are now considering pure Yang--Mills, each monomial in the
-local ansatz must consist of five Lorentz scalar dot products instead
-of the six for NLSM, and each monomial must be linear in each of the
-four external gluon polarizations.  Thus, the ansatz will be built
-from terms of the form:
+\jm{Rather than quoting the number of parameters in the BDN ansatz, I
+  would prefer to just focus on what we did since it's more general.
+  I don't want it to sound like we just patched a minor hole in their
+  argument when I think you've done something much cooler by
+  pinpointing the failure to the bowtie graph. I know you put time and
+  effort into analyzing the BDN ansatz but I'm worried that the more
+  we talk about it, the more it will overshadow the real success
+  here.}
+
+Given the close ties between pion and gluon scattering for trees and
+at one loop, the existence of the two-loop pion numerator prompts us
+to investigate the most general local numerator for YM, without any of
+the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.  We
+follow the same general procedure as in \cref{sec:pions}, again
+identifying the double-box (2box) and penta-triangle (pt) as the
+Jacobi basis graphs and building a the most general ansatz for each of
+their numerators compatible with the assumptions in
+\cref{sec:bootstrap}.  Because we are now considering pure
+Yang--Mills, each monomial in the local ansatz must consist of five
+Lorentz scalar dot products instead of the six for NLSM, and each
+monomial must be linear in each of the four external gluon
+polarizations.  Thus, the numerator ansatz for both diagrams will be
+built from terms of the form:
 \begin{equation}
@@
 \end{equation}
-in addition to the purely momentum-dependent terms show in
-\cref{eq:scalar-basis} where $\mathcal{N}_{\text{2box}}$ and $\mathcal{N}_{\text{pt}}$ represent the numerators of the double-box and penta-triangle respectively.
-In our labeling of the two loop Jacobi-basis
+where the $k_i$ take the same definition as described near
+\cref{eq:scalar-basis}.  In our labeling of the two loop Jacobi-basis
 diagrams, shown in \cref{eq:jacobi-basis}, we find that the power
@@
 invariance on the two basis diagrams, we reduce the number of terms to
-XX for the double-box, and YY for the penta-triangle.  The
-power-counting restriction of BDN would further reduce these counts to
-2232 and 4072.  In Ref.~\cite{Bern:2015ooa}, the unitarity matching
-constraints were imposed using a spanning set of minimal physical
-cuts, shown in \cref{fig:ym-spanning}.  Instead of also directly going
-to the spanning cuts, we work within the framework of the Method of
-Maximal Cuts \citepls{} in order to identify the simplest cut that is
-in tension with the kinematic Jacobi relations.
+XX for the double-box, and YY for the penta-triangle.  In
+Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
+imposed using a spanning set of minimal physical cuts, shown in
+\cref{fig:ym-spanning}.  Instead of also directly going to the
+spanning cuts, we work within the framework of the Method of Maximal
+Cuts \citepls{} in order to identify the simplest cut that is in
+tension with the kinematic Jacobi relations.
 
@@
 numerators on BEL diagrams.  We will simply avoid imposing constraints
-that directly involve such pathological diagrams.  That leaves us with
-14 non-pathological cubic diagrams, shown above in \cref{fig:MaxCuts}, on
-which to impose maximal cuts and symmetries.  Doing so, we are left
-with AA total parameters in the unrestricted ansatz and BB total in
-the BDN-restricted ansatz.
+that directly involve such pathological diagrams.  That again leaves
+us with the 14 non-pathological cubic diagrams shown above in
+\cref{fig:MaxCuts}, on which to impose maximal cuts and symmetries.
+Doing so, we are left with AA total parameters in the unrestricted
+ansatz.
 
@@
 pathological diagrams including the newly-appearing type discussed in
-\cref{eq:other-path}.
-After discarding these types of cuts, there are 8 cut topologies (see \cref{fig:ym-nmc}) ignoring cuts with dangling trees.
-Seven of these next-to-maximal cuts are consistent with the kinematic Jacobi
-relations and symmetries.  Critically, the ``bowtie'' or ``kissing-triangles''
-cut,
+\cref{eq:other-path}.  After discarding these types of cuts as well as
+those involving cuts of external Mandelstams, there are 8 cut
+topologies (see \cref{fig:ym-nmc}).  Seven of these next-to-maximal
+cuts are consistent with the kinematic Jacobi relations and
+symmetries.  Critically, the ``bowtie'' cut,
 \begin{equation*}
@@
 \end{equation*}
-cannot be satisfied by either the unrestricted or the BDN-restricted
-ansatz with Jacobi relations and symmetries applied. 
+cannot be satisfied by either the ansatz with Jacobi relations and
+symmetries applied.
+
 \begin{figure}
@@
 
-\iffalse
-We now turn to exploring the use of non-local numerators to skirt the
-incompatibility.  We expect that promoting the numerators to
-sufficiently complicated rational functions of the momenta will
-eventually produce a color-dual representation.  At worst one could
-imagine diagram ``numerator'' functions where all possible propagators
-of all diagrams appear in each diagram ``numerator's'' denominator, at
-which point required contributions could be arbitrarily rearranged
-between diagrams.  However, given the success of non-local loop
-numerators in other contexts \cite{Square, WeinzierlBCJLagrangian,
-  Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl}, we hope that
-only relatively tame additional denominators are required.
-
-As a first attempt at such a non-local representation, we consider
-allowing one factor each of $s$,$t$, or $u$ in the denominator of each
-of the double-box and penta-triangle numerators, in addition to the
-standard local \ansatze{}.  In order to not over-count the local terms,
-we restrict the non-local \ansatze{} to only truly rational terms, \eg
-for the term $n_{\text{nl}}\sim \frac{x}{s}$ we drop all terms with
-$x \propto s$.  Thus each basis diagram ansatz contains 114,422 terms
-to start, 10,010 from the local terms and 34,804 from each of the
-three non-local pieces.
-\fi
-
 \section{Conclusions and Outlook}\label{conclusions}
-There is overwhelming evidence that YM and NLSM obey color-kinematics duality at loop level even though naive Lagrangians for these theories do not manifest the duality.
-At tree level, the duality can be manifested by breaking manifest Bose symmetry at the Lagrangian level, either by explicitly picking different gluon states (as in SDYM) or by picking states that only restore Bose symmetry in the final amplitude (as in NLSM).
-All of these theories can be encapsulated in the semi-abelian YM theory presented in \cref{eq:semiYM} which obscures the Bose symmetry of the external states due to the presence of the two gauge fields $A_\mu$ and $\bar{A}_\mu$.
-The kinetic mixing between the two gauge fields permits globally color-dual 1-loop integrands, but special care must be taken so that the integrands produced from semi-abelian YM correspond to SDYM or NLSM.
-Due to the kinetic mixing that stems from the broken Bose symmetry, it is impossible to construct a 2-loop integrand for semi-abelian YM theory, that is, the theory is 1-loop exact.
-Obtaining a globally color-dual integrand beyond 1-loop then requires sacrificing more than just Bose symmetry and in this paper it is argued that off-shell locality must be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in order to obtain color-dual 2-loop integrands.}
+There is overwhelming evidence that YM and NLSM obey color-kinematics
+duality at loop level even though naive Lagrangians for these theories
+do not manifest the duality.  At tree level, the duality can be
+manifested by breaking manifest Bose symmetry at the Lagrangian level,
+either by explicitly picking different gluon states (as in SDYM) or by
+picking states that only restore Bose symmetry in the final amplitude
+(as in NLSM).  All of these theories can be encapsulated in the
+semi-Abelian YM theory presented in \cref{eq:semiYM} which obscures
+the Bose symmetry of the external states due to the presence of the
+two gauge fields $A_\mu$ and $\bar{A}_\mu$.  The kinetic mixing
+between the two gauge fields permits globally color-dual 1-loop
+integrands, but special care must be taken so that the integrands
+produced from semi-Abelian YM correspond to SDYM or NLSM.  Due to the
+kinetic mixing that stems from the broken Bose symmetry, it is
+impossible to construct a 2-loop integrand for semi-Abelian YM theory,
+that is, the theory is 1-loop exact.  Obtaining a globally color-dual
+integrand beyond 1-loop then requires sacrificing more than just Bose
+symmetry and in this paper it is argued that off-shell locality must
+be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in
+  order to obtain color-dual 2-loop integrands.}
 
@@
 Below we review the four manifestly color-dual theories that appear in this paper, in particular SDYM, two formulations of NLSM, and ZM.
-All of these theories are closely tied together by the semi-abelian YM theory in \cref{eq:semiYM} or in other words the cubic sector of YM.
+All of these theories are closely tied together by the semi-Abelian YM theory in \cref{eq:semiYM} or in other words the cubic sector of YM.
 The manifestly color-dual equations of motion for SDYM and NLSM are derived by picking a gauge and then placing a constraint not on the YM equation of motion or Bianchi identity but rather directly on the field strength itself.
@@
 In almost all of these theories, Bose symmetry is broken or obscured at the Lagrangian level.
-Because of the broken Bose symmetry (and the inherited kinetic mixing of semi-abelian YM), these theories cannot produce color-dual numerators at 2-loop or higher.
+Because of the broken Bose symmetry (and the inherited kinetic mixing of semi-Abelian YM), these theories cannot produce color-dual numerators at 2-loop or higher.
 
@@
 \end{equation}
-Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
-In other words, \emph{J-theory and semi-abelian YM are identical}.
+Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-Abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
+In other words, \emph{J-theory and semi-Abelian YM are identical}.
 By calculating an off-shell 4-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.

### 2023-09-20 notes/2loopNLSM.tex

@@
 \begin{equation}
-F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c .
-\end{equation}
+F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
+\end{equation}
+and $A_\mu$ is in Lorenz gauge.
 Here we can think of the abelian vector as a background field that
@@
 %%%%
-% Basis for both diagrams {d[p[1], p[3]], d[p[1], p[6]], d[p[1],
-% p[7]], d[p[2], p[3]], d[p[2], p[6]], d[p[2], p[7]], d[p[3], p[6]],
-% d[p[3], p[7]], d[p[6], p[6]], d[p[6], p[7]], d[p[7], p[7]]}
+% Basis for both diagrams
+% {d[p[1], p[3]], d[p[1], p[6]], d[p[1], p[7]], d[p[2], p[3]],  d[p[2], p[6]], d[p[2], p[7]], d[p[3], p[6]], d[p[3], p[7]],  d[p[6], p[6]], d[p[6], p[7]], d[p[7], p[7]]}
 %%%%
@@
 \section{Conclusions and Outlook}\label{conclusions}
-There is overwhelming evidence that YM and NLSM obey color-kinematics
-duality at loop level even though naive Lagrangians for these theories
-do not manifest the duality.  At tree level, the duality can be
-manifested by breaking manifest Bose symmetry at the Lagrangian level,
-either by explicitly picking different gluon states (as in SDYM) or by
-picking states that only restore Bose symmetry in the final amplitude
-(as in NLSM).  All of these theories can be encapsulated in the
-semi-Abelian YM theory presented in \cref{eq:semiYM} which obscures
-the Bose symmetry of the external states due to the presence of the
-two gauge fields $A_\mu$ and $\bar{A}_\mu$.  The kinetic mixing
-between the two gauge fields permits globally color-dual 1-loop
-integrands, but special care must be taken so that the integrands
-produced from semi-Abelian YM correspond to SDYM or NLSM.  Due to the
-kinetic mixing that stems from the broken Bose symmetry, it is
-impossible to construct a 2-loop integrand for semi-Abelian YM theory,
-that is, the theory is 1-loop exact.  Obtaining a globally color-dual
-integrand beyond 1-loop then requires sacrificing more than just Bose
-symmetry and in this paper it is argued that off-shell locality must
-be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in
-  order to obtain color-dual 2-loop integrands.}
+There is overwhelming evidence that YM and NLSM obey color-kinematics duality at loop level even though naive Lagrangians for these theories do not manifest the duality.
+At tree level, the duality can be manifested by breaking manifest Bose symmetry at the Lagrangian level, either by explicitly picking different gluon states (as in SDYM) or by picking states that only restore Bose symmetry in the final amplitude (as in NLSM).
+All of these theories can be encapsulated in the semi-abelian YM theory presented in \cref{eq:semiYM} which obscures the Bose symmetry of the external states due to the presence of the two gauge fields $A_\mu$ and $\bar{A}_\mu$.
+The kinetic mixing between the two gauge fields permits globally color-dual 1-loop integrands, but special care must be taken so that the integrands produced from semi-abelian YM correspond to SDYM or NLSM.
+Due to the kinetic mixing that stems from the broken Bose symmetry, it is impossible to construct a 2-loop integrand for semi-abelian YM theory, that is, the theory is 1-loop exact.
+Obtaining a globally color-dual integrand beyond 1-loop then requires sacrificing more than just Bose symmetry and in this paper it is argued that off-shell locality must be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in order to obtain color-dual 2-loop integrands.}
 
@@
 \end{equation}
-Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-Abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
-In other words, \emph{J-theory and semi-Abelian YM are identical}.
+Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
+Since both theories are in Lorenz gauge this means that \emph{J-theory and semi-abelian YM are identical}.
 By calculating an off-shell 4-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.

### 2023-09-20 notes/2loopNLSM.tex
Wrap up of my first pass.  A few diag rebuilds.

@@
   representations must be constructed at the multi-loop level. First
-  we identify a cubic theory, semi-abelian Yang--Mills, that
-  unifies many of the color-dual theories studied in the
-  literature, and provides a prescriptive approach for constructing color-dual numerators at
-  one-loop directly from Feynman rules. Consideration of this
-  theory highlights that the lifting from one-loop color-kinematics
-  dual numerators to two loops is just as challenging as the progression
-  from tree-level to one-loop.  As a first step in understanding the
-  two-loop challenge, we construct color-dual two-loop four-point
-  nonlinear sigma model (NLSM) numerators using a $D$-dimensional color-dual bootstrap.  The double-copy of the constructed NLSM numerators with
-  themselves, pure Yang--Mills, and $\mathcal{N}=4$
-  super-Yang-Mills correctly reproduce the known physical unitarity cuts of
-  special Gallileons, Born-Infeld theory, and
-  Dirac-Born-Infeld-Volkov-Akulov theory, respectively.  These NLSM
-  numerators are in explicit tension with generalizations of the
-  one-loop NLSM numerators.
-Using our constructive bootstrap, we also find that the most general \emph{local} two-loop four-point numerator for pure Yang-Mills fails to satisfy global color-kinematics duality.
-We pinpoint the failure to the bow-tie unitarity cut, and discuss a path towards \emph{non-local} construction of color-dual integrands at generic loop order.
+  we identify a cubic theory, semi-abelian Yang-Mills, that unifies
+  many of the color-dual theories studied in the literature, and
+  provides a prescriptive approach for constructing color-dual
+  numerators at one-loop directly from Feynman rules. Consideration of
+  this theory highlights that the lifting from one-loop
+  color-kinematics dual numerators to two loops is just as challenging
+  as the progression from tree-level to one-loop.  As a first step in
+  understanding the two-loop challenge, we construct color-dual
+  two-loop four-point nonlinear sigma model (NLSM) numerators using a
+  $D$-dimensional color-dual bootstrap.  The double-copy of the
+  constructed NLSM numerators with themselves, pure Yang-Mills, and
+  $\mathcal{N}=4$ super-Yang-Mills correctly reproduce the known
+  physical unitarity cuts of special Gallileons, Born-Infeld theory,
+  and Dirac-Born-Infeld-Volkov-Akulov theory, respectively.  These
+  NLSM numerators are in explicit tension with generalizations of the
+  one-loop NLSM numerators. Using our constructive bootstrap \ace{I am
+    really hesitant to call the bootstrap constructive.  While it
+    technically constructs, ``constructive'' has some additional
+    connotations}, we also find that the most general \emph{local}
+  two-loop four-point numerator for pure Yang-Mills fails to satisfy
+  global color-kinematics duality. We pinpoint the failure to the
+  bow-tie unitarity cut, and discuss a path towards \emph{non-local}
+  construction of color-dual integrands at generic loop order.
 
@@
   numerator
+\item \ace{I am starting to get a bit concerned about the overuse of the
+  phrase ``color-dual''}
 \item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
@@
 benchmark for color-dual representations in non-supersymmetric gauge
-theories.
-However in sharp contrast, we find that Yang-Mills
-does \emph{not} permit a globally color-dual representation, even when considering the most general
-polynomial ansatz of Lorentz covariant kinematics.\footnote{Globally color-dual local numerators for two-loop pure YM have been studied before but only in the context of a limited ansatz subject to certain loop power counting constraints \cite{Bern:2015ooa}.}
-Concretely, the failure point can be pinpointed to a conflict between between the ``bowtie'' cut and the following Jacobi triple:
+theories.  However in sharp contrast, we find that Yang-Mills does
+\emph{not} permit a globally color-dual representation, even when
+considering the most general polynomial ansatz of Lorentz covariant
+kinematics.\footnote{Globally color-dual local numerators for two-loop
+  pure YM have been studied before but only in the context of a
+  limited ansatz subject to certain loop power counting constraints
+  \cite{Bern:2015ooa}.}  Concretely, the failure point can be
+pinpointed to a conflict between between the ``bowtie'' cut and the
+following Jacobi triple:
 \begin{equation}
@@
   fact we slip that type of disclaimer in quite a lot throughout the
-  rest of the section} \jm{I removed the second time we say `YM, NLSM, $\phi^3$' which was redundant.
-I don't mind if we say it here because I want people to tell people that these are the kinds of theories we're thinking about.
-We could omit it but then we'd have to say that the theory has at least one color factor and is probably an adjoint type theory and at that point I'd rather just give an example.} -- can be written as
+  rest of the section} \jm{I removed the second time we say `YM, NLSM,
+  $\phi^3$' which was redundant.  I don't mind if we say it here
+  because I want people to tell people that these are the kinds of
+  theories we're thinking about.  We could omit it but then we'd have
+  to say that the theory has at least one color factor and is probably
+  an adjoint type theory and at that point I'd rather just give an
+  example.} -- can be written as
 \begin{equation}
   \mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma n_\Gamma}{d_\Gamma} .
+  \label{eq:gen-amp}
 \end{equation}
@@
 level using the KLT relations but there is significant evidence that
-the double copy persists to all loop orders \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv, Carrasco:2021otn, KLT, KiermaierTalk}.
-In addition to pointing at deep
+the double copy persists to all loop orders \cite{FiveLoopN4,
+  GeneralizedDoubleCopyFiveLoops, Bern:2018jmv, Carrasco:2021otn, KLT,
+  KiermaierTalk}.  In addition to pointing at potential undiscovered
 structure hidden in the Lagrangian for gravity, the double copy is
@@
 The color structure of tree-level amplitudes is particularly simple.
-A fully color dressed tree amplitude $\mathcal{A}_n$ can be decomposed in terms of the trace basis
+A fully color dressed tree amplitude $\mathcal{A}_n$ can be decomposed
+in terms of the trace basis
 \begin{equation}
@@
 applications of the Jacobi identity.  At 1-loop, every diagram can be
-related to one topology as well, in this case the $n$-gon.
-Two-loop calculations play an important role in our understanding of color-kinematics duality because this is the first order where multiple basis graphs are required, at least for a generic theory.
+related to one topology as well, in this case the $n$-gon.  Two-loop
+calculations play an important role in our understanding of
+color-kinematics duality because this is the first order where
+multiple basis graphs are required, at least for a generic theory.
 
@@
 to encode non-local kinetic structure that could in principle
-participate in the construction.
-The theory will be color dual if the cubic vertex is antisymmetric and satisfies the Jacobi identity, specifically,
+participate in the construction.  The theory will be color dual if the
+cubic vertex is antisymmetric and satisfies the Jacobi identity,
+specifically,
 \begin{align}
@@
 
-When an off-shell color-dual Lagrangian is not known, the loop-level amplitude integrand must be constructed from an ansatz.  The four conditions we impose on an integrand ansatz are summarized
-here and elaborated on below.\footnote{The four ansatz conditions are
-  similar to those of Ref.~\cite{Bern:2015ooa} except that there the
-  authors demand that the numerators have the same loop power counting
-  as Feynman gauge Feynman rules.  This is an additional assumption
-  that is most emphatically not made here.}
+When an off-shell color-dual Lagrangian is not known, the loop-level
+amplitude integrand must be constructed from an ansatz.  The four
+conditions we impose on an integrand ansatz are summarized here and
+elaborated on below.\footnote{The four ansatz conditions are similar
+  to those of Ref.~\cite{Bern:2015ooa} except that there the authors
+  demand that the numerators have the same loop power counting as
+  Feynman gauge Feynman rules.  This is an additional assumption that
+  is most emphatically not made here.}
 \begin{enumerate}
@@
 local (polynomial) functions of the graph kinematics with the correct
-power counting and external states.
-Insisting on a local numerator is
+power counting and external states.  Insisting on a local numerator is
 partly a matter of convenience as the ansatz for a rational function
@@
 is a viable alternative when the condition proves too stringent for an
-ansatz.
-In particular, the most natural way to guarantee locality is to require the off-shell numerators to be polynomial functions of kinematics.
-However, simply requiring on-shell locality may suffice.
+ansatz.  In particular, the most natural way to guarantee locality is
+to require the off-shell numerators to be polynomial functions of
+kinematics.  However, simply requiring on-shell locality may suffice.
 This alternative will be discussed in \cref{nonLocalScattering}.
@@
 \label{eq:TwoLoopJacobiOne}
-\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0\,,
+\JacobiOneDoubleBox + \JacobiOneCrossedBox + \JacobiOnePentaTriangle
+=0\,,
 \end{equation}
@@
 
-After using the defining Jacobi relations to relate every graph to the basis, any remaining Jacobi relations will be referred to as boundary relations.
-In other words, boundary relations (indirectly) relate basis elements to themselves.
-For example, the crossed box numerator is related to itself via the following Jacobi relation
-\be % [[19]]
+After using the defining Jacobi relations to relate every graph to the
+basis, any remaining Jacobi relations will be referred to as boundary
+relations.  In other words, boundary relations (indirectly) relate
+basis elements to themselves.  For example, the crossed box numerator
+is related to itself via the following Jacobi relation \be % [[19]]
 \label{eq:TwoLoopJacobiTwo}
@@
 % \end{equation}
-\ace{is there a reason we commented out this diagram?} \jm{You can try either one.  I liked the one I left in better.}
-For example,
-the symmetries of the crossed box
+\ace{is there a reason we commented out this diagram?} \jm{You can try
+  either one.  I liked the one I left in better.}  For example, the
+symmetries of the crossed box
 \begin{equation}
@@
   JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview,
-  Edison:2022jln, Edison:2022jln}.  \ace{Here is a semi-random
+  Edison:2022jln, Edison:2022smn}.  \ace{Here is a semi-random
   collection of unitarity-related citations.  Probably want to bulk it
@@
 Refs.~\cite{Kosmopoulos:2020pcd,Edison:2022jln} for recent discussion
-and detailed examples of evaluating state sums).
-As an example of the two types of expressions appearing in \cref{eq:SchematicCutEquation}, consider the so-called iterated two-particle cut which can be represented as a product of trees via
+and detailed examples of evaluating state sums).  As an example of the
+two types of expressions appearing in \cref{eq:SchematicCutEquation},
+consider the so-called iterated two-particle cut which can be
+represented as a product of trees via
 \begin{equation}
@@
 (and dual Kleiss-Kuijf amplitude basis \cite{Kleiss:1988ne}) have
-$(n-2)!$ elements, one generally needs to evaluate that many separate
-color-orderings of the same cut. \jm{Don't you need $(n-2)!$ for each
-  blob in the cut?  So you need to evaluate $(n_1-2)! (n_2-2)!...$
-  cuts where $n_1$, $n_2$... are the multiplicities of the
-  blobs.}\ace{Yes.  Lets figure out a way to word it.} As an example,
-consider the ``bowtie'' cut topology -- one of the factorization
-channels of the iterated unitarity cut -- which has two topologically
-distinct color-ordered expansions
+$(n-2)!$ elements, one generally needs to evaluate
+$(n_1-2)! (n_2-2)!...$ separate color-orderings of the same cut, where
+$n_1$, $n_2$... are the multiplicities of the amplitudes making up the
+cut. As an example, consider the ``bowtie'' cut topology -- one of the
+factorization channels of the iterated unitarity cut -- which has two
+topologically distinct color-ordered expansions
 \begin{equation}
@@
 \end{equation}
-which serve as a complete basis for the full cut.  \ace{One of the
-  diagrams here got shifted around somehow.  Probably need to rebuild
-  the whole fig manifest}
+which serve as a complete basis for the full cut.
 
@@
 \begin{equation}
+  \label{eq:ym-lag}
   \mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2
@@
 
-The loop momentum structure of ZM theory provides one final hint for simplifying the pion numerators.
-A generic term in the ZM numerator (of either basis graph) looks schematically like
+The loop momentum structure of ZM theory provides one final hint for
+simplifying the pion numerators.  A generic term in the ZM numerator
+(of either basis graph) looks schematically like
 \begin{equation}
@@
 \cref{sec:bootstrap}.  Because we are now considering pure
-Yang--Mills, each monomial in the local ansatz must consist of five
+Yang-Mills, each monomial in the local ansatz must consist of five
 Lorentz scalar dot products instead of the six for NLSM, and each
@@
   \mathcal{N}_{\text{2box}},\mathcal{N}_{\text{pt}}\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
+  \label{eq:ym-basis}
 \end{equation}
@@
   \caption{The three spanning physical unitarity cuts of pure
-    Yang--Mills at 2 loops}
+    Yang-Mills at 2 loops}
   \label{fig:ym-spanning}
@@
 Thus we have identified the minimal failure state for a
-globally-color-dual two-loop Yang--Mills representation: locality,
+globally-color-dual two-loop Yang-Mills representation: locality,
 symmetry, and the kinematic Jacobi relations for just three diagrams
@@
 \section{Conclusions and Outlook}\label{conclusions}
-There is overwhelming evidence that YM and NLSM obey color-kinematics duality at loop level even though naive Lagrangians for these theories do not manifest the duality.
-At tree level, the duality can be manifested by breaking manifest Bose symmetry at the Lagrangian level, either by explicitly picking different gluon states (as in SDYM) or by picking states that only restore Bose symmetry in the final amplitude (as in NLSM).
-All of these theories can be encapsulated in the semi-abelian YM theory presented in \cref{eq:semiYM} which obscures the Bose symmetry of the external states due to the presence of the two gauge fields $A_\mu$ and $\bar{A}_\mu$.
-The kinetic mixing between the two gauge fields permits globally color-dual 1-loop integrands, but special care must be taken so that the integrands produced from semi-abelian YM correspond to SDYM or NLSM.
-Due to the kinetic mixing that stems from the broken Bose symmetry, it is impossible to construct a 2-loop integrand for semi-abelian YM theory, that is, the theory is 1-loop exact.
-Obtaining a globally color-dual integrand beyond 1-loop then requires sacrificing more than just Bose symmetry and in this paper it is argued that off-shell locality must be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in order to obtain color-dual 2-loop integrands.}
-
-\jm{I am intentionally shying away from really firm statements like `you must abandon locality' because there are always loopholes and we made a lot of other assumptions in fixing our \ansatze{}.}
-
-Kinematic ``numerators'' that are rational functions of the kinematics appear unnatural from the perspective of point-like quantum field theories.
-After all, introducing operators that produce rational functions of kinematics must be non-local.
-Thus, in order to identify valid color-dual representation of Yang-Mills beyond tree-level, we must relax the constraint of \textit{off-shell locality}, and realize locality only in the limit of \textit{on-shell} kinematics.
-Below we provide an overview of what one might expect for such a construction, and provide some simple examples at tree-level that manifest this structure.
-\subsection{Non-local construction of scattering amplitudes}\label{nonLocalScattering}
- For example, consider the simple four-point example of a color-dual representation of Yang-Mills theory. 
+There is overwhelming evidence that YM and NLSM obey color-kinematics
+duality at loop level even though naive Lagrangians for these theories
+do not manifest the duality.  At tree level, the duality can be
+manifested by breaking manifest Bose symmetry at the Lagrangian level,
+either by explicitly picking different gluon states (as in SDYM) or by
+picking states that only restore Bose symmetry in the final amplitude
+(as in NLSM).  All of these theories can be encapsulated in the
+semi-abelian YM theory presented in \cref{eq:semiYM} which obscures
+the Bose symmetry of the external states due to the presence of the
+two gauge fields $A_\mu$ and $\bar{A}_\mu$.  The kinetic mixing
+between the two gauge fields permits globally color-dual 1-loop
+integrands, but special care must be taken so that the integrands
+produced from semi-abelian YM correspond to SDYM or NLSM.  Due to the
+kinetic mixing that stems from the broken Bose symmetry, it is
+impossible to construct a 2-loop integrand for semi-abelian YM theory,
+that is, the theory is 1-loop exact.  Obtaining a globally color-dual
+integrand beyond 1-loop then requires sacrificing more than just Bose
+symmetry and in this paper it is argued that off-shell locality must
+be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in
+  order to obtain color-dual 2-loop integrands.}  \ace{I want to
+  rephrase especially the last sentence.}
+
+\jm{I am intentionally shying away from really firm statements like
+  `you must abandon locality' because there are always loopholes and
+  we made a lot of other assumptions in fixing our \ansatze{}.}
+
+Kinematic ``numerators'' that are rational functions of the kinematics
+appear unnatural from the perspective of point-like quantum field
+theories. After all, operators that produce rational functions of
+kinematics must be non-local.\ace{A few more connecting sentences
+  here.  This is a bit of a big jump without some amount of summary}
+Thus, in order to identify valid color-dual representation of
+Yang-Mills beyond tree-level, we must relax the constraint of
+\textit{off-shell locality}, and realize locality only in the limit of
+\textit{on-shell} kinematics. Below we provide an overview of what one
+might expect for such a construction, and provide some simple examples
+at tree-level that manifest this structure.
+
+\subsection{Non-local construction of scattering amplitudes}
+\label{nonLocalScattering}
+For example, consider the simple four-point example of a color-dual
+representation of Yang-Mills theory.
 \begin{equation}
@@
 \end{equation}
-By construction, this functionally symmetric numerator is anti-symmetric and obeys the Jacobi identity:
+By construction, this functionally symmetric numerator is
+anti-symmetric and obeys the Jacobi identity:
 \begin{equation}
@@
 \end{equation}
-However, it must also factorize to kinematics that are consistent with the local Feynman rules of \ref{}. Evaluating the residues on $s=s_{12}$, $t=s_{23}$ and $u=s_{13}$ poles, we find:
+However, it must also factorize to kinematics that are consistent with
+the local Feynman rules of \cref{eq:ym-lag}. Evaluating the residue on
+the $s=s_{12} \to 0$ pole we find:
 \begin{align}
@@
 \end{align}
-Plugging these into a cubic graph representation of Yang-Mills \ref{}, we find:
-\begin{equation}
-\text{Res}\left[\mathcal{A}_4^{\text{YM}}\right]^{s=0} = \frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} (2c_s-c_t-c_u) =  \mathcal{A}_{(12|l)}^{\text{YM}}\mathcal{A}_{(-l|34)}^{\text{YM}} 
-\end{equation}
-where we have applied the color structure Jacobi identity, $c_s+c_t+c_u=0$.
-While we can absolutely apply a generalized gauge trasformation \cite{BCJ} to restore field theoretic locality to the cubic numerators, we can see clearly that this is an aesthetic choice.
-Moreover, by abandoning traditional notions of off-shell locality, we can massage the color-dual numerators into a form that is manifestly gauge invariant.
-As an organizational principle, pulling out an overall gauge-invariant factors comes with the added advantage of simplifying a loop-level construction of color-dual numerators for Yang-Mills.
-\subsection{Non-local construction of color-dual integrands}\label{nonLocalLoops}
-Much of the complexity for $D$-dimensional vector theories at loop-level arises due to the mixing between external polarization and internal loop momenta.
-As noted, one advantage of expanding ansatz construction towards functions of rational kinematics is the prospect of stripping out overall factors of gauge invariant tensors.
-Rather than building an ansatz from the irreducible scalar products of \ref{},
+with $t=s_{23}$ and $u=s_{13}$.
+Plugging these into a cubic graph representation of Yang-Mills, the
+tree level version of \cref{eq:gen-amp}, we find:
+\begin{equation}
+  \text{Res}\left[\mathcal{A}_4^{\text{YM}}\right]^{s=0}
+  = \frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} (2c_s-c_t-c_u)
+  =  \mathcal{A}_{(12|l)}^{\text{YM}}\mathcal{A}_{(-l|34)}^{\text{YM}} 
+\end{equation}
+where we have applied the color structure Jacobi identity,
+$c_s+c_t+c_u=0$. While we can absolutely apply a generalized gauge
+trasformation \cite{BCJ} to restore field theoretic locality to the
+cubic numerators, we can see clearly that this is an aesthetic
+choice. Moreover, by abandoning traditional notions of off-shell
+locality, we incidentally gained enough freedom to massage the
+color-dual numerators into a form that is manifestly gauge invariant
+for all particles. As an organizational principle, pulling out overall
+gauge-invariant factors comes with the added advantage of simplifying
+a loop-level construction of color-dual numerators for Yang-Mills.
+
+\subsection{Non-local construction of color-dual integrands}
+\label{nonLocalLoops}
+\ace{This subsection needs either more substance, or just get cut}
+
+Much of the complexity for $D$-dimensional vector theories at
+loop-level arises due to the mixing between external polarization and
+internal loop momenta. As noted, one advantage of expanding ansatz
+construction towards functions of rational kinematics is the prospect
+of stripping out overall factors of gauge invariant tensors. Rather
+than building an ansatz from the irreducible scalar products of
+\cref{eq:ym-basis},
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{O}_i$ are the basis tensors of \cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}_i$ is a rational function of momenta of the form;
+where $\mathcal{O}_i$ are the basis tensors of
+\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}_i$ is a
+rational function of momenta of the form;
 \begin{equation}
@@
 \subsection{Future Directions}\label{sec:Discussion}
-\paragraph{Acknowledgments} The authors would like to thank ...
-for insightful conversations, related collaboration, and encouragement throughout the completion of this work.
-This work was supported by the DOE under contract DE-SC0015910 and by the Alfred P.
-Sloan Foundation.
-N.H.P.
-additionally acknowledges the Northwestern University Amplitudes and Insight group, the Department of Physics and Astronomy, and Weinberg College for their generous support.
-Feynman diagrams were typeset using TikZ-Feynman \cite{Ellis:2016jkw}.
+
+%\paragraph{Acknowledgments}
+\subsection*{Acknowledgments}
+The authors would like to thank ... for insightful conversations,
+related collaboration, and encouragement throughout the completion of
+this work. This work was supported by the DOE under contract
+DE-SC0015910 and by the Alfred P. Sloan
+Foundation. N.H.P. additionally acknowledges the Northwestern
+University Amplitudes and Insight group, the Department of Physics and
+Astronomy, and Weinberg College for their generous support.  Feynman
+diagrams were typeset using TikZ-Feynman \cite{Ellis:2016jkw}.
 
 \appendix
+% Wizardry to disable subappendix showing up in TOC
+\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}% This turns off subsections
 \section{Catalog of color-dual theories}
@@
 
-Below we review the four manifestly color-dual theories that appear in this paper, in particular SDYM, two formulations of NLSM, and ZM.
-All of these theories are closely tied together by the semi-abelian YM theory in \cref{eq:semiYM} or in other words the cubic sector of YM.
-The manifestly color-dual equations of motion for SDYM and NLSM are derived by picking a gauge and then placing a constraint not on the YM equation of motion or Bianchi identity but rather directly on the field strength itself.
-Other theories can be obtained from SDYM and NLSM by judicious modification of the propagator.
-In all of these theories, the kinematic algebra is that of (volume preserving) diffeomorphisms or some close variant thereof.
-In almost all of these theories, Bose symmetry is broken or obscured at the Lagrangian level.
-Because of the broken Bose symmetry (and the inherited kinetic mixing of semi-abelian YM), these theories cannot produce color-dual numerators at 2-loop or higher.
-
-\jm{I've deleted the boxes around equations.
-I actually really like them normally but if we're boxing something in the appendix then it feels like that's a major enough result that it should be in the main body of the paper.}
-
-\paragraph{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
-\begin{equation}
-\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
-\end{equation}
-To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
-\be\label{SDcon}
-F_{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
-\end{equation}
-where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength.
-Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
-\begin{equation}
-D^\mu F^{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
-\end{equation}
-Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills.
-In this paper, we will focus on the perturbative aspects of this constraint.
-Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
+Below we review the four manifestly color-dual theories that appear in
+this paper, in particular SDYM, two formulations of NLSM, and ZM.  All
+of these theories are closely tied together by the semi-abelian YM
+theory in \cref{eq:semiYM} or in other words the cubic sector of YM.
+The manifestly color-dual equations of motion for SDYM and NLSM are
+derived by picking a gauge and then placing a constraint not on the YM
+equation of motion or Bianchi identity but rather directly on the
+field strength itself.  Other theories can be obtained from SDYM and
+NLSM by judicious modification of the propagator.  In all of these
+theories, the kinematic algebra is that of (volume preserving)
+diffeomorphisms or some close variant thereof.  In almost all of these
+theories, Bose symmetry is broken or obscured at the Lagrangian level.
+Because of the broken Bose symmetry (and the inherited kinetic mixing
+of semi-abelian YM), these theories cannot produce color-dual
+numerators at 2-loop or higher.
+
+\jm{I've deleted the boxes around equations.  I actually really like
+  them normally but if we're boxing something in the appendix then it
+  feels like that's a major enough result that it should be in the
+  main body of the paper.}
+
+\ace{There are some cyclic references in the catalog that are gonna be
+  a bit annoying to clean up: ZM refers to J, YZ refers to ZM and
+  SDYM, J refers to YZ.  I have currently switched the order to: SDYM,
+  ZM, YZ, J, but we should probably discuss.}
+
+\subsection{Self-Dual Yang-Mills} The first example in the literature
+of color-dual Feynman rules is that of Yang-Mills theory in the
+self-dual sector (SDYM).  We summarize the appoach of
+Ref.~\cite{Monteiro2011pc} for extracting the kinematic algebra.
+% \begin{equation}
+% \mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
+% \end{equation}
+To obtain the Lagrangian for self-dual Yang-Mills from standard Yang-Mills, we apply the
+self-dual condition that equates the non-abelian $SU(N)$ field
+strength,
+$F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu
+,A_\nu]$, to its dual 2-form:
+\begin{equation}
+  \label{SDcon} F_{\mu\nu} = \frac{1}{2}
+  \varepsilon_{\mu\nu\rho\sigma}F^{\rho\sigma} \,.
+\end{equation}
+Solutions to the self-dual condition automatically satisfy the
+Yang-Mills equation of motion due to the Bianchi identity:
+\begin{equation}
+D^\mu F^{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0 \,.
+\end{equation}
+Solutions to \cref{SDcon} correspond to instanton configurations that
+are probed by the gauge field path integral in the full
+non-perturbative description of Yang-Mills. In this paper, we will
+focus on the perturbative aspects of this constraint. We begin by
+transforming from Cartesian coordinates to light cone coordinates,
+$(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, via:
 \begin{equation}
@@
 \end{equation}
-which gives the following expression for the invariant line element:
-\begin{equation}
-ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
-\end{equation}
-Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
+which yields the invariant line element:
+\begin{equation}
+ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x} \,.
+\end{equation}
+Applying this coordinate transformation to the self-dual condition of
+\cref{SDcon}, produces three simple constraint equations:
 \begin{align} \label{SDLightCone1}
@@
  \label{SDLightCone3}
- F_{v\bar{w}} &= 0\,,
+ F_{v\bar{w}} &= 0\,.
 \end{align}
-Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
-\begin{equation}
-A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
-\end{equation}
-The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
-\begin{equation}
-A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
-\end{equation}
-This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
-\be\label{SDDef}
-A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
-\end{equation}
-Using this definition on the first self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
-\be\label{SDEOM}
-(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
-\end{equation}
-Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
-\begin{equation}
-\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
-\end{equation}
-The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
-\begin{equation}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
-\end{equation}
-In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}.
-We can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
-Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.
-
-As we will show in \sect{}, the color-dual nature of SDYM can be understood as a direct consequence of isolating the \textit{cubic-sector} of the full Yang-Mills amplitudes by projecting along particular on-shell states.
-For this reason, the color-dual nature depends critically on the loop order of the amplitude and does not hold generically beyond one-loop.
-
-\paragraph{YZ-Theory}
-SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \cref{sec:ZMTheory}, does as well.
-This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
-On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung:2016prv}.
+Thus, in light-cone gauge, $A_u=0$, we realize the self-dual
+conditions in terms of the gauge field as
+\begin{align}
+  A_u=0 \text{ and } (\ref{SDLightCone1}) \quad&\Rightarrow \quad A_w=0\\
+  A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad&\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}} \label{eq:sd-divs}\,.
+\end{align}
+This last constraint can be manifested by writing the gauge field in
+terms of a single degree of freedom which we call $\Psi$:
+\begin{equation}
+  \label{SDDef}
+A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi \,.
+\end{equation}
+Using this definition on the first self-dual constraint equation
+yields the following equation of motion for the dynamical scalar
+field:
+\begin{equation}
+  \label{SDEOM}
+(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0 \,.
+\end{equation}
+Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange
+multiplier, we obtain the following interaction Lagrangian for
+self-dual Yang-Mills theory:
+\begin{equation}
+  \mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ] \,.
+\end{equation}
+The color-ordered ordered cubic Feynman rule for this theory can be
+immediately read off as:
+\begin{equation}
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2} \,.
+\end{equation}
+In this form, the Lagrangian and Feynman rules are manifestly
+color-dual \textit{off-shell}. We can see the effect \cref{SDcon} had
+on the Feynman rules of the full Yang-Mills Lagrangian: it simply
+decoupled the anti-MHV three-point vertex from the theory, leaving
+only the MHV three-point vertex. Before proceeding, it is important to
+note that the mass-dimension of the theory appears to differ from that
+of Yang-Mills -- we comment on this in detail in \cref{Conventions}.
+
+\ace{I think the below is fully covered in Sections 2 and 3 now.  Can
+  we cut it?}  As we will show in \sect{}, the color-dual nature of
+SDYM can be understood as a direct consequence of isolating the
+\textit{cubic-sector} of the full Yang-Mills amplitudes by projecting
+along particular on-shell states. For this reason, the color-dual
+nature depends critically on the loop order of the amplitude and does
+not hold generically beyond one-loop.
+
+\subsection{Zakharov-Mikhailov theory}
+\label{sec:ZMTheory}
+While J-theory manifests color-kinematics duality, it only does so at
+tree level because J-theory breaks manifest Bose symmetry.  Manifest
+color-kinematics duality can be achieved at all loop orders by
+restricting J-theory to two spacetime dimensions where the chiral
+current can be dualized to a scalar
+$J^\mu = \varepsilon^{\mu\nu} \partial_\nu \varphi$, which trivially
+enforces Lorenz gauge.  After plugging $\varphi$ into
+\cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$
+(rather than some new field) can be integrated in to obtain the
+Zakharov-Mikhailov (ZM) Lagrangian
+\begin{equation}
+\label{eq:ZMLagrangian}
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
+\end{equation}
+This procedure makes it clear that ZM and NLSM encode the same
+classical physics, that is, their equations of motion are dual to each
+other.  ZM theory can also be tenuously motivated from SDYM theory.
+The power counting of the interaction term in the SDYM equation of
+motion \cref{SDEOM} makes it clear that the theory is critical in 2D.
+This suggests that the two lightcone coordinates $u$ and $w$ should be
+identified as the coordinates of the 2D space.  The 4D d'Alembertian
+in lightcone coordinates,
+$\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$,
+cannot be interpreted as the 2D equivalent, so the kinetic term of
+SDYM must be replaced with the correct 2D version.  This argument
+should be understood purely as an alternative route to ZM theory.
+While NLSM and ZM are the same theory classically when restricted to
+2D, SDYM and ZM are not because, for example, the tree amplitudes of
+SDYM vanish but those of ZM do not (cite argumentative papers).
+
+The color-stripped Feynman rule for the three-point vertex can be read
+off from the Lagrangian \cref{eq:ZMLagrangian}, giving
+\begin{equation}
+\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
+\end{equation}
+The vertex is (1) functionally symmetric and (2) the kinematic portion
+of the vertex is completely anti-symmetric:
+\begin{equation}
+\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
+\end{equation}
+This important property is due to momentum conservation alone and does
+not need any additional kinematic constraints to satisfy the duality.
+To prove off-shell color kinematics duality for any multiplicity and
+loop order it is enough to observe that the sum of the off-shell $s$-,
+$t$-, and $u$-channel numerators sum to zero
+\begin{equation}
+\label{eq:ZMJacobi}
+\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
+\end{equation}
+by virtue of the 2D Levi-Civita identity
+$\varepsilon_{\mu\nu}\varepsilon_{\rho\sigma} =
+\eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
+Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the
+Schouten identity.
+
+Since ZM theory manifested color-kinematics duality without any
+reference to the on-shell condition, a mass term can be added to ZM
+theory without spoiling color-kinematics duality.  In fact, the
+kinetic term could be dramatically altered.  In general, if the
+on-shell conditions are not used, color-kinematics duality is
+unaffected by the details of the propagator structure.  Of course,
+dramatically altering the pole structure could spoil locality in the
+double-coppied theory.  As already mentioned, the only difference
+classically between ZM and SDYM is the propagator structure.  While
+both theories are color dual for the same reason, altering the
+propagators has profound consequences since SDYM tree amplitudes
+vanish and manifest color-kinematics does not persist to all loop
+orders.  Color dual theories with the same interactions but different
+kinetic terms have appeared in the literature before.  For example,
+J-theory and the theory of non-Abelian fluids presented in
+\cite{Cheung:2020djz} differ only in their propagators. Specifically,
+taking the static limit of the fluid's $(D+1)$-dimensional kinetic
+term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates
+yields the relativistic d'Alembertian of $D$-dimensional J-theory.
+
+While the color-dual nature of ZM theory is rather elegant, the
+loop-level construction introduces complications when applying
+dimensional regularization. Similar to the difficulties of
+renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity
+in promoting the integrands to formal $D$-dimensional expressions. As
+such, in our two-loop bootstrap of NLSM we will only use the ZM
+integrands as a mechanism for reducing the residual gauge freedom in
+our final solution -- rather than a full $D$-dimensional integrand to
+which we match off-shell in dimensional regularization.
+
+\subsection{YZ-Theory}
+Both SDYM and ZM theory involve explicit reliance to the spacetime
+dimension, which makes the theories poorly suited for constructing
+dimensionally-regulated loop-level amplitudes.  On the other hand,
+YZ-theory is an honest $D$-dimensional theory that captures the
+classical physics of the nonlinear sigma model (NLSM) while
+manifesting the duality between color and kinematics
+\cite{Cheung:2016prv}.
 
@@
 
-\paragraph{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
-For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
-The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
-First order formulation of NLSM in terms of chiral current $J^\mu$.
-Two equations.
-Two constraints, the field strength should vanish
+\subsection{J-theory}
+There is an alternative color-dual formulation of NLSM that the theory
+manifestly corresponds to NLSM at least at tree level
+\cite{Cheung:2021zvb}.  For related formulations of NLSM that do not
+treat color-kinematics duality see \cite{Freedman:1980us,
+  Slavnov:1971mz}.  The construction begins with a first order
+formulation of NLSM in terms of chiral currents $J^\mu$.  First order
+formulation of NLSM in terms of chiral current $J^\mu$.  Two
+equations.  Two constraints, the field strength should vanish
 \begin{equation}
@@
 \end{equation}
-
-\paragraph{Zakharov-Mikhailov theory}
-\label{sec:ZMTheory}
-While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
-Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \varepsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
-After plugging $\varphi$ into \cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
-\begin{equation}
-\label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
-\end{equation}
-This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
-ZM theory can also be tenuously motivated from SDYM theory.
-The power counting of the interaction term in the SDYM equation of motion \cref{SDEOM} makes it clear that the theory is critical in 2D.
-This suggests that the two lightcone coordinates $u$ and $w$ should be identified as the coordinates of the 2D space.
-The 4D d'Alembertian in lightcone coordinates, $\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$, cannot be interpreted as the 2D equivalent, so the kinetic term of SDYM must be replaced with the correct 2D version.
-This argument should be understood purely as an alternative route to ZM theory.
-While NLSM and ZM are the same theory classically when restricted to 2D, SDYM and ZM are not because, for example, the tree amplitudes of SDYM vanish but those of ZM do not (cite argumentative papers).
-
-The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \cref{eq:ZMLagrangian}, giving
-\begin{equation}
-\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
-\end{equation}
-The vertex is (1) functionally symmetric and (2) the kinematic portion of the vertex is completely anti-symmetric: 
-\begin{equation}
-\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
-\end{equation}
-This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
-To prove off-shell color kinematics duality for any multiplicity and loop order it is enough to observe that the sum of the off-shell $s$-, $t$-, and $u$-channel numerators sum to zero
-\begin{equation}
-\label{eq:ZMJacobi}
-\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
-\end{equation}
-by virtue of the 2D Levi-Civita identity $\varepsilon_{\mu\nu}\varepsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
-Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.
-
-Since ZM theory manifested color-kinematics duality without any reference to the on-shell condition, a mass term can be added to ZM theory without spoiling color-kinematics duality.
-In fact, the kinetic term could be dramatically altered.
-In general, if the on-shell conditions are not used, color-kinematics duality is unaffected by the details of the propagator structure.
-Of course, dramatically altering the pole structure could spoil locality in the double-coppied theory.
-As already mentioned, the only difference classically between ZM and SDYM is the propagator structure.
-While both theories are color dual for the same reason, altering the propagators has profound consequences since SDYM tree amplitudes vanish and manifest color-kinematics does not persist to all loop orders.
-Color dual theories with the same interactions but different kinetic terms have appeared in the literature before.
-For example, J-theory and the theory of non-Abelian fluids presented in \cite{Cheung:2020djz} differ only in their propagators.
-Specifically, taking the static limit of the fluid's $(D+1)$-dimensional kinetic term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates yields the relativistic d'Alembertian of $D$-dimensional J-theory.
-
-While the color-dual nature of ZM theory is rather elegant, the loop-level construction introduces complications when applying dimensional regularization.
-Similar to the difficulties of renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity in promoting the integrands to formal $D$-dimensional expressions.
-As such, in our two-loop bootstrap of NLSM we will only use the ZM integrands as a mechanism for reducing the residual gauge freedom in our final solution -- rather than a full $D$-dimensional integrand to which we match off-shell in dimensional regularization.
 

### 2023-09-21 notes/2loopNLSM.tex
big push

@@
 
-\abstract{
-
-  We make progress towards understanding how color-dual
+\abstract{ We make progress in understanding how color-dual
   representations must be constructed at the multi-loop level. First
@@
   many of the color-dual theories studied in the literature, and
-  provides a prescriptive approach for constructing color-dual
+  provides a prescriptive approach for constructing $D$-dimensional color-dual
   numerators at one-loop directly from Feynman rules. Consideration of
@@
   NLSM numerators are in explicit tension with generalizations of the
-  one-loop NLSM numerators. Using our constructive bootstrap \ace{I am
-    really hesitant to call the bootstrap constructive.  While it
-    technically constructs, ``constructive'' has some additional
-    connotations}, we also find that the most general \emph{local}
-  two-loop four-point numerator for pure Yang-Mills fails to satisfy
+  one-loop NLSM numerators. Using our loop-level bootstrap, we also find that the most general \emph{local} ansatz
+  for two-loop four-point pure Yang-Mills fails to satisfy
   global color-kinematics duality. We pinpoint the failure to the
-  bow-tie unitarity cut, and discuss a path towards \emph{non-local}
+  bowtie unitarity cut, and discuss a path forward towards \emph{non-local}
   construction of color-dual integrands at generic loop order.
@@
 \cite{Feng:2010my,Cachazo:2014xea}, as case studies for advancing our
-understanding of the kinematic algebra to the multi-loop level.
+understanding of the kinematic algebra toward the multi-loop level.
 
@@
 possible to multiply and divide by propagators so that the sum runs
-over only purely cubic graphs $\Gamma$.  Overcounting is removed by
+over the set of purely cubic graphs, $\Gamma$.  Overcounting is removed by
 the internal symmetry factor $S_\Gamma$, which tracks the number of
@@
   representations, see for example \cite{Johansson:2017srf,
-    Johansson2014zca, Johansson:2015oia, Johansson:2019dnu,
-    Carrasco:2023vjg, Carrasco:2020ywq}.}  the denominator $d_\Gamma$
+    Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2020ywq,
+    Carrasco:2023vjg}.}  the denominator $d_\Gamma$
 is the product of propagators associated with the graph $\Gamma$, and
@@
 
-Many of the 1-loop results presented in \cref{sec:cubic} are informed
+Many of the one-loop results presented in \cref{sec:cubic} are informed
 by the tree-level double-copy so we will review the tree case here.
@@
 color-kinematics duality because this is the first order where
-multiple basis graphs are required, at least for a generic theory.
+multiple basis graphs are required, at least for a generic theory. We refer the reader to \cite{BCJreview} for more background on the topic.
 
@@
 the form
-\begin{equation}
-\mathcal{L} = P_V^{ab}P_W^{ij}\mathcal{O}^a_i \Box \mathcal{O}^b_j +  V^{abc} W^{ijk}\mathcal{O}^a_i \mathcal{O}^b_j \mathcal{O}^c_k
-\end{equation}
-where $V^{abc}$ and $W^{ijk}$ are cubic Feynman rules mixing field
-operators $\mathcal{O}^{a}_i$ indexed by quantum numbers $a$ and
-$i$. We have introduced $P_V^{ab}$ and $P_W^{ij}$ projection operators
+\begin{equation}\label{cubicCKLag}
+\mathcal{L} = P_V^{ab}P_W^{\mu\nu}\mathcal{O}^a_\mu \Box \mathcal{O}^b_\nu +  V^{abc} W^{\mu \nu \rho}\mathcal{O}^a_\mu \mathcal{O}^b_\nu \mathcal{O}^c_\rho
+\end{equation}
+where $V^{abc}$ and $W^{\mu \nu \rho}$ are cubic Feynman rules mixing field
+operators $\mathcal{O}^{a}_\mu$ indexed by quantum numbers $a$ and
+$\mu$. The Feynman rules for this theory are simply:
+\be\label{CKFrules}
+\begin{split}
+\propFrule{$a,\mu$}{$b,\nu$}{$k \rightarrow $}{} &= \frac{i}{k^2} P_V^{ab}P_W^{\mu\nu}
+\\
+\cubicFrule{$a,\mu$}{$b,\nu$}{$c,\rho$}{}{}{} &= i V^{abc}W^{\mu \nu \rho}
+\end{split}
+\ee
+We have introduced $P_V^{ab}$ and $P_W^{\mu\nu}$ projection operators
 to encode non-local kinetic structure that could in principle
-participate in the construction.  The theory will be color dual if the
-cubic vertex is antisymmetric and satisfies the Jacobi identity,
+participate in the construction, as is the case for $DF^2$ theory \cite{Johansson:2017srf}.
+Though generally these quadratic dressings are simply delta functions, $P_V^{ab} = \delta^{ab}$, or flat space metrics, $P_W^{\mu\nu}=\eta^{\mu\nu}$.
+As written, the theory will be color dual if the off-shell cubic vertex is antisymmetric and satisfies the Jacobi identity,
 specifically,
@@
 \end{align}
-where 
-\begin{equation}
-{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}P_{b_1 c_1}V^{c_1 a_3b_2}\cdots P_{b_{n-3}c_{n-3}}V^{c_{n-3} a_{n-1}a_n}\,.
-\end{equation}
-Off-shell descriptions of
+where using the Feynman rules of \cref{CKFrules}, the bracketed expression is the half-ladder numerator of the following diagram,
+\begin{equation}
+{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv N\left[\halfLadder\right]\,,
+\end{equation}
+and likewise for the $W^{\mu \nu \rho}$ dressing. Off-shell descriptions of
 color-dual theories are rare, and only a few examples are available in
@@
 theories directly from a set of cubic interactions, higher point
-Jacobi and antisymmetry constraints require introducing additional
-operators. See ref \cite{Ben-Shahar:2022ixa} for a recent
+Jacobi and antisymmetry constraints require introducing additional operators \cite{Carrasco:2022lbm,Carrasco:2022sck}, sometimes including additional propagating fields not originally considered in the spectrum.
+See ref.~\cite{Ben-Shahar:2022ixa} for a recent
 example. Indeed, as we will show in \cref{sec:cubic}, Yang-Mills
-requires introducing a cubic 2-form interaction in order to manifest
+requires introducing a cubic two-form interaction in order to manifest
 the kinematic algebra just at four-point. Absent information about the
@@
     changes.
-\item \textbf{On-shell Unitarity }: The cuts of the ansatz must
+\item \textbf{On-shell Unitarity}: The cuts of the ansatz must
   reproduce the physical unitarity cuts of the theory when internal
@@
 In order to clarify general statements, the following subsections
-include examples from a 4-point 2-loop integrand for some generic
+include examples from a four-point two-loop integrand for some generic
 color-dual theory like YM.  This is the simplest case that
 demonstrates the full machinery of the color-dual bootstrap.  All tree
-and 1-loop processes are generated by single basis diagrams (the half
+and one-loop processes are generated by single basis diagrams (the half
 ladder and $n$-gon respectively) so they lack examples of three-term
 ``boundary'' Jacobi relations to be described shortly.
-Choosing the 4-point 2-loop integrand also has the advantage that this
+Choosing the four-point two-loop integrand also has the advantage that this
 process appears prominently in this paper.
@@
 }
-\caption{The 14 non-pathological 4-point 2-loop cubic diagrams,
+\caption{The 14 non-pathological four-point two-loop cubic diagrams,
   including all dangling tree diagrams.} \label{fig:MaxCuts}
@@
 even for a theory with quartic (or higher multiplicity) vertices by
-multiplying and dividing by propagators.  In the case of the 4-point
-2-loop example promised above, there are 14 cubic graph topologies
+multiplying and dividing by propagators.  In the case of the four-point
+two-loop example promised above, there are 14 cubic graph topologies
 (shown in \cref{fig:MaxCuts}) ignoring tadpoles and bubble on external
@@
 crossed box can be written (or \emph{defined}) in terms of the other
-two.  In this way, all of the 14 cubic 4-point 2-loop topologies can be
+two.  In this way, all of the 14 cubic four-point two-loop topologies can be
 written in terms of a basis of the double box and penta-triangle.
@@
 Discussions about how to resolve these types of singularities can be
-found in Refs.~\cite{Edison:2022jln, Edison:2022smn, Edison:2020uzf,
-  Geyer:2015bja, Bern:2012uf, Minahan:1987ha} \ace{Should really make
-  sure that is the right Geyer paper}.  In addition to the
+found in Refs.~\cite{Minahan:1987ha, Bern:2012uf, 
+  Geyer:2015bja,Geyer:2015jch,Edison:2020uzf, Edison:2022jln, Edison:2022smn}. In addition to the
 bubble-on-external-leg cuts, there is a related class of cuts in which
@@
 on-shell tree amplitudes.  The cut to be performed can, itself, be
-encoded in a graph.  For example, potential 4-point 2-loop cuts include
+encoded in a graph.  For example, potential four-point two-loop cuts include
 \begin{equation}
@@
 we can express the YM three-point interaction in terms of the
-following vertex in Lorenz gauge
-\begin{equation}
-T^k_{ij} = (\varepsilon_i\varepsilon_j)(\varepsilon_k p_i).
-\end{equation}
-This kinematic generator is anti-symmetric in $1\leftrightarrow 2$
+following vertex in Lorenz gauge:
+\begin{equation}
+\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} =(\varepsilon_i\varepsilon_j)(\varepsilon_k p_i).
+\end{equation}
+This kinematic vertex is anti-symmetric in $1\leftrightarrow 2$
 exchange, and from it we can construct the full Lorenz gauge
-Yang-Mills vertex by summing over cyclic permutations
-\begin{equation}
-V^{(123)}_{\text{YM}} = T^3_{12} +\text{cyc}(123).
+Yang-Mills vertex by summing over cyclic permutations,
+\begin{equation}
+V^{(123)}_{\text{YM}} = \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}  +\text{cyc}(123)\,.
 \end{equation}
 Contracting this with the vector state sum, we can see that the cubic
-Yang-Mills vertex does not satisfy the four-point Jacobi identity
+Yang-Mills vertex does not satisfy the four-point Jacobi identity:
 \begin{equation}
@@
 where $ \varepsilon_{(ij)} = \varepsilon_{i}\cdot \varepsilon_{j}$.
-The remaining terms can be absorbed into the definition of the
-four-point kinematic numerator
+However, the remaining terms can be absorbed into the definition of the
+four-point kinematic numerator, as follows
 \begin{equation}
@@
 \end{equation}
-where $V_{\text{YM}+B}$ indicates the introduction of an additional
-two-form studied in Ref.~\cite{Ben-Shahar:2022ixa} for constructing the
-NMHV Yang-Mills Lagrangian.  After the introduction of the 2-form, the
-numerators now satisfy the Jacobi identity
+Note that this new definition of the $s$-channel numerator contains two factors of $\varepsilon_{(ij)} $ that contract spacetime indices \textit{across} the factorization, suggesting the inclusion of a spin-2 mode.
+As such, we use $V_{\text{YM}+B}$ to denote the inclusion of an additional two-form, as was studied in Ref.~\cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian.
+After the introduction of the two-form, the
+numerators now satisfy the Jacobi identity:
 \begin{equation}
   {}_1\langle
-  V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
-\end{equation}
-where the new cubic Lagrangian takes the form
+  V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0\,,
+\end{equation}
+where the new cubic Lagrangian takes the form\,,
 \begin{equation}
@@
 \end{equation}
-Of course, higher multiplicity would require further redefinition of
-the three-point vertex to satisfy Jacobi identites on all internal
+Of course, higher multiplicity would likely require further redefinition of
+the three-point vertex to satisfy Jacobi identities on all internal
 edges. While introducing successively higher spin states could in
@@
 with what we find at general loop order. We will comment on this in
-\cref{sec:Discussion} \ace{Is this the sec you are thinking of?}. For
+\cref{sec:Discussion} \ace{Is this the sec you are thinking of?} \nhp{ Yes. thanks :-)}. For
 now, we will study how to construct one-loop integrands consistent
@@
 \end{equation}
-\ace{Should we mention that this is closely related to MHV vs NMHV?}
-Thus for our approach at one-loop, we aim to build color-dual
-integrands directly from kinematic factors of this form. The
-organizational principle underlying this construction can be
-understood in terms of a polarization decomposition of vector
-amplitudes introduced by one of the authors \cite{Pavao:2022kog},
+\ace{Should we mention that this is closely related to MHV vs NMHV?} \nhp{Yes, I added a couple sentences and reference below -- let me know what you think}.
+
+This restriction to the $(\varepsilon\varepsilon)^1$ cubic sector of Yang-Mills is closely related to the MHV decomposition of color-dual numerators \cite{ElvangHuangReview,Chen:2019ywi,Chen:2021chy}, where choosing appropriate reference vectors sends all $(\varepsilon\varepsilon) \rightarrow 0$, with the exception of one of the positive helicity polarizations, $\varepsilon^+_1$, dotted into all the $n-2$ negative helicity modes in the full MHV amplitude, $\varepsilon^+_1 \varepsilon^-_i \neq 0$.
+We describe this in detail in \cref{Conventions}.
+With the interest in constructing dimension agnostic color-dual integrands at one-loop, we want to avoid making specific reference to 4D helicity states.
+
+Thus for our approach at one-loop, we aim to build color-dual integrands directly from $D$-dimensional kinematic factors that are $\mathcal{O}((\varepsilon\varepsilon)^1)$ at tree-level, and $\mathcal{O}((\varepsilon\varepsilon)^0)$ at one-loop.
+The $D$-dimensional organizational principle underlying this construction can be understood in terms of a vector amplitude decomposition introduced by one of the authors \cite{Pavao:2022kog},
 \begin{equation}\label{eq:pureVecRABD}
@@
 \end{equation}
-\jm{Nic, could you give a quick recap of what all of the symbols mean
-  in the equation above?}  By a simple mass-dimensioin argument, we
-know the tree-level cubic sector of Yang-Mills must be at
+where we have introduced the shorthand notation, $\varepsilon_{(ij)\cdots (kl)} \equiv (\varepsilon_i \varepsilon_j)\cdots (\varepsilon_k \varepsilon_l)$, and  $S^{2|k}_{\sigma}$ is the set of $k$ pairs of external legs appearing in the color-ordered label list, $\sigma$.
+For example, at four-point, $S^{2|1}_{\sigma} =  \{(12),(13),(14),(23),(24),(34)\}$, and $S^{2|2}_{\sigma} =  \{(12)(34),(13)(24),(14)(23)\}$.
+The sum thus selects out kinematic building blocks, $\Delta_{(\sigma)}^{(\rho)}$,that are each weighted by different polarization dot products.
+Some simple four-point examples include,
+\be
+\Delta^{(13)}_{(1234)} =\frac{(k_1 \varepsilon_2)(k_{3} \varepsilon_4)}{s_{12}}+\frac{(k_1 \varepsilon_4)(k_{3} \varepsilon_2)}{s_{14}}, \qquad \Delta^{(13)(24)}_{(1234)} =1, \qquad \Delta^{(12)(34)}_{(1234)} =\frac{s_{13}}{s_{12}}\,.
+\ee
+We direct the reader to ref.~\cite{Pavao:2022kog} for further details. By a simple mass-dimension argument \cite{ElvangHuangReview}, we know the tree-level cubic sector of Yang-Mills must be at
 $\mathcal{O}((\varepsilon\varepsilon)^1)$,
 \begin{equation}
-A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\, ,
+A_{(\text{tree})}^{\text{cubic-YM}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\, ,
 \end{equation}
@@
 \begin{equation}
-A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
+A_{(\text{1-loop})}^{\text{cubic-YM}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
 \end{equation}
 When decomposed in this way, the polarization stripped building blocks
-must obey a set of Ward-identities between different ``helicity'' (or
-$(\varepsilon \varepsilon)$) sectors in order for the full amplitude
+must obey a set of Ward-identities between different ``helicity'', or
+$(\varepsilon \varepsilon)^n$, sectors in order for the full amplitude
 to be gauge invariant,
@@
 \subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
-As we demonstrate above, if we include factors of
+As we argued above, if we include factors of
 $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to
@@
 \end{equation}
-The kinetic term mixes the two gauge fields and has the standard
+where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply:
+\be
+\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}
+\ee
+As one can see, the kinetic term mixes the two gauge fields and has the standard
 Feynman rule of $i/k^2$.  We can use the Ward identity of
@@
 
-We can select out both \ace{which both?} of these manifestly cubic
-sectors by selecting only $\varepsilon^+\varepsilon^+$ in light-cone
-gauge (i.e. SDYM) and one-minus at tree-level OR what $J$-theory and
-$YZ$-theory select with their on-shell states. Indeed, the
+As noted above, we can select out can manifestly cubic
+sector of semi-abelian Yang-Mills from the full theory of \cref{eq:ym-lag} by selecting only $(\varepsilon^+\varepsilon^+)$ in light-cone gauge (i.e.
+SDYM) and one-minus at tree-level or by plugging in the on-shell states of $J$-theory \cite{Cheung:2020djz,Cheung:2021zvb} and
+$YZ$-theory \cite{Cheung:2016prv}. Indeed, the
 $D$-dimensional description of $J$-theory is just the following blocks
@@
 To recover NLSM at one-loop, we need to extract the $D$-dependent part
-that corresponds to an internal $YY$-loop from extra-dimensional
+that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional
 scalars
@@
 internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we discuss
-in \cref{sec:CKLagrangians} \ace{I think this is where we do this
-  now}, all the $J$ and $Z$ states must be on-shell in order to
+in \cref{sec:CKLagrangians}, all the $J$ and $Z$ states must be on-shell in order to
 produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at
@@
 $YY$-loop is a valid forward limit for producing NLSM amplitudes,
-since as constructed YZ theory mathces to NLSM for off-shell
-Y-particles. We will construct these one-loop integrands in the
-next section.
+since as constructed YZ theory matches to NLSM for off-shell
+Y-particles. We provide explicit expressions for these one-loop amplitudes in the next section.
 
@@
 previous section:
-\begin{equation}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
+\begin{equation} \label{DdimSDYM}
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
 \end{equation}
@@
 yield precisely the 4D SDYM vertex, up to an unphysical phase \ace{Can
-  we provide an example?}. Of course, this has the advantage of
+  we provide an example?} \nhp{yes, provided}:
+  \be
+  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
+ \ee
+where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}.
+Of course, the form of \cref{DdimSDYM} has the advantage of
 permitting a $D$-dimensional construction of the one-loop
@@
 \end{equation}
-where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
+where $l_i = l+k_1+k_2+\cdots+ k_i$ and the bracket $\langle \cdots\rangle$ indicates that we have applied the off-shell state projector, $\sum {\varepsilon^\mu_{(+l_i)}\varepsilon^\nu_{(-l_i)}}=P_{(l_i)}^{\mu\nu}$ on all internal polarizations.
+In general, the $n$-gon vertex would be
 \begin{equation}
@@
 Due to the state-sum of internal loop factors,
-$\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above
+$\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}\sim D$, the integrand above
 depends explicitly on the spacetime dimension, $D$. By taking a
@@
 \begin{equation}
-\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
+\partial_D \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 \varepsilon_1)(l_2 \varepsilon_2)\cdots (l_n \varepsilon_n)
 \end{equation}
 This integrand numerator with internal scalar loop is precisely what
-one would obtain from the Feynman rules of YZ-theory, absent the $XZ$
+one would obtain from the Feynman rules of YZ-theory, absent the $\bar{Z}Z$
 internal vector loop. For more background, we refer the reader to
-\cref{sec:CKLagrangians}.
-\begin{equation}
- \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
-\end{equation}
-Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
-
+\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator:
+\begin{equation}
+ \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
+\end{equation}
+Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$, since when plugging on longitudinal modes, the $n$-gon can be re-expressed completely in terms of inverse propagators, $2(k_i \cdot l_i) = l_{i}^2-l^2_{i-1}$.
+We have verified through 10-point one-loop that this $n$-gon expression is a valid color-dual representation for NLSM.
+
+Before proceeding, we note that the above definition does give rise to ``pathological" bubble-on-external-leg (BEL) diagrams discussed previously in \cref{sec:bootstrap}.
+However, one can show that these diagrams integrate to zero for spacetime dimension, $D>2$, and thus can be disregarded as unphysical.
+For the interested reader, in \cref{BELreg} we provide a detailed overview of this dimensional regularization of the BEL diagram.
 \subsection{Two-loop obstruction}\label{2LoopObstruction}
@@
 \begin{equation}
-\mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(+,+,+,+)=0
+\mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=0
 \end{equation}
@@
 reintroduce $D$-dimensional vertices from the diagonal group of
-$G_L\times G_R$. Doing so will necessarily introduce internal
+$G_L\times G_R$ that have the wrong weight. Doing so will necessarily permit internal
 contractions of $\bar{A}_\mu A^\mu$,
 \begin{equation}
-\mathcal{A}^{\text{YM}}_{\text{2-loop}}(+,+,+,+)=\doubleBoxObstructionA +\doubleBoxObstructionB+\cdots 
-\end{equation}
-However, this immediately runs into the difficulty of introducing the
+\mathcal{A}^{\text{YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=\doubleBoxObstructionA +\doubleBoxObstructionB+\cdots 
+\end{equation}
+where we used white dots to indicate interaction vertices of weight\footnote{We choose the convention that the abelianized gauge fields carry weight $\mathcal{W}[\bar{A}] = -1$, and non-abelian vectors are $\mathcal{W}[\bar{A}] = +1$.} $\mathcal{W}[\bar{A}\bar{A} A] = -1$, rather than the isolated semi-YM vertex which always carries weight $\mathcal{W}[\bar{A}A A] = +1$.
+This immediately runs into the difficulty of introducing the
 four-point contact needed for color-kinematics to be satisfied on all
-internal edges. To do this prescriptively would require knowledge of
+internal edges. By a simple weight counting argument, one can see that including this wrong sign interactions is unavoidable at two-loop and higher.
+
+Thus, to construct two-loop numerators prescriptively, as we have done at one-loop, would require knowledge of
 the full kinematic algebra for Yang-Mills off-shell. Since this is
@@
 \label{2loopBoot}
-\ace{Lets bulk this section intro up a bit}
+\ace{Lets bulk this section intro up a bit} \nhp{Is this sufficient?}
 
 We now employ the color-dual bootstrap method described in
-\cref{sec:bootstrap}. We will employ an ansatz constructed from
+\cref{sec:bootstrap}. We will start with an ansatz constructed from
 $D$-dimensionally Lorentz covariant kinematics. To fix remaining
@@
 question ``is it possible to find globally color-dual numerators
-beyond 1-loop?''  We will tackle this question for 4-point 2-loop
+beyond 1-loop?''  We will tackle this question for four-point two-loop
 scattering in NLSM before moving on to the same process in YM.
 
-Ignoring tadpoles and BEL graphs, there are 14 cubic 4-point 2-loop
+Ignoring tadpoles and BEL graphs, there are 14 cubic four-point two-loop
 graphs (see \cref{fig:MaxCuts}) which are related to each other via 21
@@
 that need to be enforced, shown in \cref{fig:emu}, only involve
-4-point vertices.  Notably this means that even at two loops,
-unitarity is still only probing the on-shell 4-point NLSM amplitude.
+four-point vertices.  Notably this means that even at two loops,
+unitarity is still only probing the on-shell four-point NLSM amplitude.
 Unitarity cuts besides those shown in \cref{fig:emu} are either
@@
 possible to enforce the no triangle hypothesis, manifest loop power
-counting, and, for 4-point and up to at least six loops, strip off a
+counting, and, for four-point and up to at least six loops, strip off a
 factor of $st \atree$ from the integrand \cite{FiveLoopN4,
@@
 desirable to make color-kinematics duality as manifest as possible.
-One hope would be to factor out some piece of the 1-loop numerator
+One hope would be to factor out some piece of the one-loop numerator
 since this at least manifests antisymmetry for the vertices involving
@@
 color-kinematics duality to all loop orders, namely,
-Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}.
-
-ZM theory is governed by the Lagrangian
+Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}. ZM theory is governed by the Lagrangian
 \begin{equation}
@@
 sectors is rather subtle.  Only color-ordered amplitudes can be
-defined unambiguously from the Feynman rules.  At 4-point, only the
+defined unambiguously from the Feynman rules.  At four-point, only the
 alternating sector is free of subtleties and the amplitude for this
@@
 \ace{Lets tighten up this paragraph a bit, especially the second half}
-It is tempting to try to match the pion 4-point 2-loop integrand to ZM
-on the cuts, but given that the cuts only probe the on-shell 4-point
+It is tempting to try to match the pion four-point two-loop integrand to ZM
+on the cuts, but given that the cuts only probe the on-shell four-point
 amplitude, which is either subtle or vanishes for ZM, it is better to
@@
 freedom parameters reduces to 58.  The pion numerator appearing in the
-ancillary files makes exactly this choice.\footnote{When the 4-point
+ancillary files makes exactly this choice.\footnote{When the four-point
   pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
@@
 With a cubic color-dual pion representation in hand, we can perform
-double copies with many theories to extract ``gravitational''
+double copies with many theories to extract colorless gravity-like
 amplitudes.  In particular, we produce numerators for special
@@
 pions, $\mathcal{N}=0$ YM, and $\mathcal{N}=4$ sYM respectively
-\citepls{}.  Such double-copy constructions are important nontrivial
+\cite{Cachazo:2014xea,Cheung:2015ota,Cheung:2016drk}.  Such double-copy constructions are important nontrivial
 checks on the underlying single-copy theories as the Jacobi relations
 in the single copy conspire to produce the double-copy theory's
-version of ``diffeomorphism invariance'': XX for sGal, and gauge
-invariance of the BI photon and DBIVA supermultiplet \citepls{}.  All
+version of linear diffeomorphism invariance: enhanced shift symmetry for special Galilleons, and gauge
+invariance of the BI photon and DBIVA supermultiplet \cite{Hinterbichler:2015pqa}.  All
 three of these double-copy theories were recently studied extensively
@@
 and the cubic $\mathcal{N}=4$ sYM representation from the well-known
-$n_{2\text{box}} = n_{\text{cross-box}} = s^2t\, \atree$ \citepls{}.
+$n_{2\text{box}} = n_{\text{cross-box}} = s^2t\, \atree$ \cite{Bern:1997nh}.
 On the other hand, we use the methods of Ref.~\cite{Carrasco:2023qgz}
@@
 Yang-Mills, each monomial in the local ansatz must consist of five
-Lorentz scalar dot products instead of the six for NLSM, and each
+Lorentz scalar dot product s instead of the six for NLSM, and each
 monomial must be linear in each of the four external gluon
@@
 \begin{equation}
-  \mathcal{N}_{\text{2box}},\mathcal{N}_{\text{pt}}\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
+  \mathcal{N}^{\text{YM}}\left[\NLSMBasisDoubleBox \right]\text{ and }\mathcal{N}^{\text{YM}}\left[\NLSMBasisPentaTriangle \right]\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
   \label{eq:ym-basis}
@@
 spanning cuts, we work within the framework of the Method of Maximal
-Cuts \citepls{} in order to identify the simplest cut that is in
+Cuts \cite{Bern:2007ct} in order to identify the simplest cut that is in
 tension with the kinematic Jacobi relations.
@@
 kinetic mixing that stems from the broken Bose symmetry, it is
-impossible to construct a 2-loop integrand for semi-abelian YM theory,
-that is, the theory is 1-loop exact.  Obtaining a globally color-dual
-integrand beyond 1-loop then requires sacrificing more than just Bose
+impossible to construct a two-loop integrand for semi-abelian YM theory,
+that is, the theory is one-loop exact.  Obtaining a globally color-dual
+integrand beyond one-loop then requires sacrificing more than just Bose
 symmetry and in this paper it is argued that off-shell locality must
 be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in
-  order to obtain color-dual 2-loop integrands.}  \ace{I want to
+  order to obtain color-dual two-loop integrands.}  \ace{I want to
   rephrase especially the last sentence.}
@@
 of semi-abelian YM), these theories cannot produce color-dual
-numerators at 2-loop or higher.
+numerators at two-loop or higher.
 
@@
 $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu
-,A_\nu]$, to its dual 2-form:
+,A_\nu]$, to its dual two-form:
 \begin{equation}
@@
 
-\ace{I think the below is fully covered in Sections 2 and 3 now.  Can
-  we cut it?}  As we will show in \sect{}, the color-dual nature of
-SDYM can be understood as a direct consequence of isolating the
-\textit{cubic-sector} of the full Yang-Mills amplitudes by projecting
-along particular on-shell states. For this reason, the color-dual
-nature depends critically on the loop order of the amplitude and does
-not hold generically beyond one-loop.
-
 \subsection{Zakharov-Mikhailov theory}
@@
 Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the
-Schouten identity.
-
-Since ZM theory manifested color-kinematics duality without any
+Schouten identity. Below we provide the double-box and penta-triangle expressions to which we matched our NLSM integrands to in the text:
+\be
+\ZMBasisDoubleBox =\left[\begin{split}
+  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
+\\
+\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
+\end{split}\right]
+\ee
+\be
+\ZMBasisPentaTriangle =\left[\begin{split}
+  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
+\\
+\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
+\end{split}\right]
+\ee
+
+Amusingly, since ZM theory manifested color-kinematics duality without any
 reference to the on-shell condition, a mass term can be added to ZM
@@
 dimensional regularization. Similar to the difficulties of
-renormalizing chiral fermions \citepls{ 'tHooft}, there is ambiguity
+renormalizing chiral fermions \cite{tHooft:1972tcz}, there is ambiguity
 in promoting the integrands to formal $D$-dimensional expressions. As
@@
 where $X$ and $Z$ are $d$-vectors and $Y$ is a scalar field.
-Considering the conjugate nature of the X-Z propagator, in this work we will make the replacement $X\rightarrow \bar{Z}$.
+Considering the conjugate nature of the $XZ$ propagator, in this work we will make the replacement $X\rightarrow \bar{Z}$.
 Plugging this redefinition of the gauge fields in, upto cubic order, we thus obtain the following Lagrangian:
@@
 Since both theories are in Lorenz gauge this means that \emph{J-theory and semi-abelian YM are identical}.
-By calculating an off-shell 4-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
+By calculating an off-shell four-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
 As might be expected, the kinematic algebra is the diffeomorphism algebra.
@@
 
-This theory is one-to-one with the observables amplitudes of YZ-theory when only considering $Z$-$\bar{Z}$ on-shell states.
-As such, the single vertex in this theory is the same as the pure vector vertex of YZ theory in Lorenz gauge, where $\partial_\mu J^\mu = 0$:
+This theory is one-to-one with the observables amplitudes of $YZ$-theory when only considering $Z$$\bar{Z}$ on-shell states.
+As such, the single vertex in this theory is the same as the pure vector vertex of $YZ$ theory in Lorenz gauge, where $\partial_\mu J^\mu = 0$:
 \begin{equation}
@@
 
-Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. For massless momenta, $k_a$ and $k_b$, we have 
-\begin{equation}
-s_{ab} = (k_a+k_b)^2= \langle ab \rangle[ba]\,,
-\end{equation}
-the component definition of our spinor bracket that are consistent with the conventions above,
+Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. The component definition of our spinor bracket that are consistent with the conventions above,
 \begin{align}
@@
 \end{align}
-where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
+where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$, one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:
+\begin{equation}
+s_{ab} = (k_a+k_b)^2= \langle ab \rangle[ba]\,.
+\end{equation}
+Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
 \begin{equation}\label{eq:4DPols}
@@
 \end{align}
-The conventions we use in the text where the holomorphic spinor cares extra mass dimension essentially amounts to shifting the bracket by the following:
+The conventions we use in the text where the holomorphic spinor, $X(p,k)$, carries extra mass dimension essentially amounts to shifting the bracket by the following overall factor:
 \begin{align}
@@
 \begin{equation}
- (F^1F^2\cdots F^n) = (D-4)(l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
+ (F^1F^2\cdots F^n) = D (l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
 \end{equation}
@@
 While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM.
-However, the scalar contribution, that comes dressed with an overall factor $(D-4)$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts.
+However, the scalar contribution, that comes dressed with an overall factor $D$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts.
 In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality.
@@
 
-\section{Notes to self}
-\jm{Nic, this used to be where my notes to myself were but I deleted them.  It looks like you wrote yourself some notes here.  Do you still want them?}
-
-\be \label{YMSvert}
-\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} =T^3_{12}
-\end{equation}
-\begin{equation}
-V^{c}_{ab} = (\varepsilon_a\varepsilon_b)(\varepsilon_c k_a)
-\end{equation}
-With this, the full vector interaction can be expressed as a sum over cyclic permutations:
-\begin{equation}
-\cubic{hgrey0}{gluon}{}{gluon}{}{gluon}{}  =  \cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed} + \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} + \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} +\text{h.c.}
-\end{equation}
-The state-sum between two three-point gluon vertex yields the following expansion in terms of YZ-theory vertices:
-\begin{equation}
- \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
-\end{equation}
-where we have defined a new oriented vertex in terms of our scalar-vector building block of \ref{YMSvert},
-\begin{equation}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} = \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} +\cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed}\,.
-\end{equation}
-\begin{equation}
-\vec{V}^{c}_{ab} =V^{b}_{ac}+V^{a}_{bc}
-\end{equation}
-All the $(\varepsilon\varepsilon)^1$ diagram permutations are isolated to the cubic sector and together manifest color-kinematics duality.
-However, the exception of the last diagram which introduces a $(\varepsilon\varepsilon)^2$ factor, must conspire with the Yang-Mills contact to preserve the duality off-shell
-
-\begin{equation}
-\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed} = (s_{13}-s_{12}) \varepsilon_{(12)} \varepsilon_{(34)}
-\end{equation}
-One was to resolve this is to introduce higher spin modes in order to accomodate the internal index contractions needed to recover the s-channal contract:
-\begin{equation}
-\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{Bfield}{nhpRed}{}{nhpRed} = s_{12 }(\varepsilon_{(13)} \varepsilon_{(24)} - \varepsilon_{(14)} \varepsilon_{(23)})
-\end{equation}
-
 \bibliographystyle{JHEP}

### 2023-09-21 notes/2loopNLSM.tex
Small edits

@@
 where $l_i = l+k_1+k_2+\cdots+ k_i$ and the bracket $\langle \cdots\rangle$ indicates that we have applied the off-shell state projector, $\sum {\varepsilon^\mu_{(+l_i)}\varepsilon^\nu_{(-l_i)}}=P_{(l_i)}^{\mu\nu}$ on all internal polarizations.
+\jm{So $l$ runs between legs $n$ and $1$, right?
+Can we show that on all of the diagrams here?
+Is the projector the normal one $P \sim \eta + \{k,q\}/k.q$?
+Can we say that?
+I would normally call that the on-shell state projector not the off-shell one but I could easily be missing something.}
 In general, the $n$-gon vertex would be
@@
 We have verified through 10-point one-loop that this $n$-gon expression is a valid color-dual representation for NLSM.
+\jm{I only checked 4, 6, 8 so unless someone checked 10pt I would say `through 8pt'.}
 

### 2023-09-21 notes/2loopNLSM.tex
changes over zoom

--- 2023-09-21 notes/2loopNLSM.tex
@@
 
-\usetikzlibrary{external}  
-\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-\tikzexternalize[                     %% Activate externalization
-prefix=images/,                    %% Avoid cluttering the directory
-system call={                       %% Use lualatex in system call
-   pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
-},
-]
+%\usetikzlibrary{external}  
+%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
+%\tikzexternalize[                     %% Activate externalization
+%prefix=images/,                    %% Avoid cluttering the directory
+%system call={                       %% Use lualatex in system call
+  % pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" %"\texsource" || rm "\image.pdf"
+%},
+%]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\emailAdd{alexander.edison@northwestern.edu, james.mangan@northwestern.edu, pavao@u.northwestern.edu}
+\emailAdd{alexander.edison@northwestern.edu, 
+\\
+james.mangan@northwestern.edu, 
+\\
+pavao@u.northwestern.edu}
 
@@
 \begin{enumerate}
-\item Settle on $n$ vs $N$ vs $\mathcal{N}$ as the symbol for
-  numerator
+%\item Settle on $n$ vs $N$ vs $\mathcal{N}$ as the symbol for
+ % numerator
+
 \item \ace{I am starting to get a bit concerned about the overuse of the
-  phrase ``color-dual''}
+  phrase ``color-dual''} \nhp{We all choose capital $N$}
 \item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
@@
   an adjoint type theory and at that point I'd rather just give an
-  example.} -- can be written as
+  example.} \nhp{Nic will clarify between cubic vs color-dual here}-- can be written as
 \begin{equation}
@@
 
-\jm{The next section feels a little redundant and silly sometimes
-  because the integrand, color factors, kinematic numerators,
-  etc. were defined a while ago.  I'm not sure how to merge the two
-  sections though.}
-
 \paragraph{Color-kinematics duality}
@@
 
-\ace{Awkward phrasing/transition.}  What has just been described is
+\ace{Awkward phrasing/transition.} \nhp{will message language} What has just been described is
 sometimes referred to as ``global'' color-kinematics duality because
@@
 imposed for \emph{every} graph, not just the basis graphs.
-%For example, the symmetries of the crossed box are spanned by
+For example, the symmetries of the crossed box are spanned by,
+\nhp{Alex, fix the scaling to get the boxes to fit}
+\be
+\CrossedBoxGraphSym{1}{2}{3}{4}\!\! \sim\!\! \CrossedBoxGraphSym{2}{1}{3}{4} 
+\text{ and }
+\CrossedBoxGraphSym{1}{2}{3}{4} \!\!\sim\!\! \CrossedBoxGraphSym{2}{1}{4}{3}
+\ee
+%\ace{is there a reason we commented out this diagram?} \jm{You can try
+ % either one.  I liked the one I left in better.}  For example, the
+%symmetries of the crossed box
 %\begin{equation}
-%\CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{3}{4} \text{ and } \CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{4}{3}
-% \end{equation}
-\ace{is there a reason we commented out this diagram?} \jm{You can try
-  either one.  I liked the one I left in better.}  For example, the
-symmetries of the crossed box
-\begin{equation}
-\CrossedBoxGraphSym{1}{2}{3}{4}
-\end{equation}
-are spanned by $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
+%\CrossedBoxGraphSym{1}{2}{3}{4}
+%\end{equation}
+which are just functional relabelings of external legs, $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
 In general, internal edge labels must be tracked as well.
@@
 vertices are all totally antisymmetric and hence have signs built into
-their orientations.  Once the signs are included in the symmetry
-relations, the crossed box can be expressed in terms of the double box
+their orientations.  Once imposing symmetry relations, the crossed box can be expressed in terms of the double box
 and penta-triangle, thus imposing non-trivial constraints on the
-ansatz. \ace{I'm not quite sure why the signs are mentioned in the
-  previous sentence?}
+ansatz. 
+\nhp{Someone add in comment here about how symmetry relations imposes constraints of jacobi from equation above}.
+%\ace{I'm not quite sure why the signs are mentioned in the
+%  previous sentence?}
 
@@
 reviewed in many places so we will be light on details here
-\cite{BCFUnitarity, BernHuangReview, Bern:2015ooa, Bourjaily:2017wjl,
+\cite{BCFUnitarity, Bern:2015ooa, Bourjaily:2017wjl,
   JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview,
-  Edison:2022jln, Edison:2022smn}.  \ace{Here is a semi-random
-  collection of unitarity-related citations.  Probably want to bulk it
-  up a bit more.}  Recently, generalized unitarity was optimized for
+  Edison:2022jln, Edison:2022smn}. Recently, generalized unitarity was optimized for
 even-multiplicity theories like NLSM \cite{Carrasco:2023qgz}.
@@
 with what we find at general loop order. We will comment on this in
-\cref{sec:Discussion} \ace{Is this the sec you are thinking of?} \nhp{ Yes. thanks :-)}. For
+\cref{sec:Discussion}. For
 now, we will study how to construct one-loop integrands consistent
@@
 \end{equation}
-\ace{Should we mention that this is closely related to MHV vs NMHV?} \nhp{Yes, I added a couple sentences and reference below -- let me know what you think}.
-
-This restriction to the $(\varepsilon\varepsilon)^1$ cubic sector of Yang-Mills is closely related to the MHV decomposition of color-dual numerators \cite{ElvangHuangReview,Chen:2019ywi,Chen:2021chy}, where choosing appropriate reference vectors sends all $(\varepsilon\varepsilon) \rightarrow 0$, with the exception of one of the positive helicity polarizations, $\varepsilon^+_1$, dotted into all the $n-2$ negative helicity modes in the full MHV amplitude, $\varepsilon^+_1 \varepsilon^-_i \neq 0$.
+This restriction to the $(\varepsilon\varepsilon)^1$ cubic sector of Yang-Mills is closely related to the MHV decomposition of color-dual numerators \cite{TasiLance,ElvangHuangReview,Chen:2019ywi,Chen:2021chy}, where choosing appropriate reference vectors sends all $(\varepsilon\varepsilon) \rightarrow 0$, with the exception of one of the positive helicity polarizations, $\varepsilon^+_1$, dotted into all the $n-2$ negative helicity modes in the full MHV amplitude, $\varepsilon^+_1 \varepsilon^-_i \neq 0$.
 We describe this in detail in \cref{Conventions}.
@@
 permitting a $D$-dimensional construction of the one-loop
-integrand. Below we provide a four-point example:
+integrand. Below we provide a four-point example: \nhp{change ordering on legs}
 \begin{equation}
@@
 \end{equation}
-where $l_i = l+k_1+k_2+\cdots+ k_i$ and the bracket $\langle \cdots\rangle$ indicates that we have applied the off-shell state projector, $\sum {\varepsilon^\mu_{(+l_i)}\varepsilon^\nu_{(-l_i)}}=P_{(l_i)}^{\mu\nu}$ on all internal polarizations.
-In general, the $n$-gon vertex would be
+where $l_i = l+k_1+k_2+\cdots+ k_i$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+l_i)}\varepsilon^\nu_{(-l_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
+In general, the $n$-gon diagram would be,
 \begin{equation}
@@
 \end{equation}
-Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$, since when plugging on longitudinal modes, the $n$-gon can be re-expressed completely in terms of inverse propagators, $2(k_i \cdot l_i) = l_{i}^2-l^2_{i-1}$.
+Where we have define the antisymmetric kinematic variable, $[ij] = l_i^2 - l_j^2$, since when plugging on longitudinal modes, the $n$-gon can be re-expressed completely in terms of inverse propagators, $2(k_i \cdot l_i) = l_{i}^2-l^2_{i-1}$.
 We have verified through 10-point one-loop that this $n$-gon expression is a valid color-dual representation for NLSM.
 
-Before proceeding, we note that the above definition does give rise to ``pathological" bubble-on-external-leg (BEL) diagrams discussed previously in \cref{sec:bootstrap}.
+Before proceeding, we note that the above definition does give rise to ``pathological" bubble-on-external-leg (BEL) diagrams, discussed previously in \cref{sec:bootstrap}.
 However, one can show that these diagrams integrate to zero for spacetime dimension, $D>2$, and thus can be disregarded as unphysical.
@@
 \label{2loopBoot}
-\ace{Lets bulk this section intro up a bit} \nhp{Is this sufficient?}
+\ace{Lets bulk this section intro up a bit} \nhp{@Alex will bulk this up}
 
@@
 Gallileons, Born-Infeld theory, and DBIVA by double-copying against
-pions, $\mathcal{N}=0$ YM, and $\mathcal{N}=4$ sYM respectively
+pions, pure YM, and $\mathcal{N}=4$ sYM respectively
 \cite{Cachazo:2014xea,Cheung:2015ota,Cheung:2016drk}.  Such double-copy constructions are important nontrivial
@@
 To construct the double-copy theories, we source the cubic
-$\mathcal{N}=0$ YM numerators from Ref.~\cite{Bern:2015ooa} (which
+pure YM numerators from Ref.~\cite{Bern:2015ooa} (which
 additionally satisfies a relaxed form of color-kinematics duality),
@@
 symmetry, and the kinematic Jacobi relations for just three diagrams
-are incompatible with the ``bowtie'' cut. \jm{Insert clip of Gordon Ramsay saying ``delicious'' here.}
+are incompatible with the ``bowtie'' cut.
 
@@
 There is overwhelming evidence that YM and NLSM obey color-kinematics
-duality at loop level even though naive Lagrangians for these theories
+duality at loop level, even though naive Lagrangians for these theories
 do not manifest the duality.  At tree level, the duality can be
@@
 
-\subsection{Non-local construction of color-dual integrands}
-\label{nonLocalLoops}
-\ace{This subsection needs either more substance, or just get cut}
+\subsection{Future Directions}\label{sec:Discussion}
 
@@
 \cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}_i$ is a
-rational function of momenta of the form;
-\begin{equation}
-\mathcal{R}_{m,L} = \frac{P_{b+a}(k^2,kl,l^2)}{Q_a(k^2,kl,l^2)}, \qquad b=m+2(l-1)
-\end{equation}
-where $P_{a}$ and $Q_a$ are degree-$a$ polynomials exclusively of $D$-dimensional scalar kinematics. 
-\subsection{Future Directions}\label{sec:Discussion}
+rational function of scalar products.
 
@@
 numerators at two-loop or higher.
-
-\jm{I've deleted the boxes around equations.  I actually really like
-  them normally but if we're boxing something in the appendix then it
-  feels like that's a major enough result that it should be in the
-  main body of the paper.}
 
@@
 Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets.
-In terms of light-cone coordinates that we employed in the text, the angles and squares can be rewritten as follows:
+In terms of light-cone coordinates that we employed above in \cref{sec:CKLagrangians}, the angles and squares can be rewritten as follows:
 \begin{align}

### 2023-09-21 notes/2loopNLSM.tex
clean sheet

@@
   and Dirac-Born-Infeld-Volkov-Akulov theory, respectively.  These
-  NLSM numerators are in explicit tension with generalizations of the
-  one-loop NLSM numerators. Using our loop-level bootstrap, we also find that the most general \emph{local} ansatz
+  NLSM numerators are in tension with generalizations our one-loop construction. Using our loop-level bootstrap, we also find that the most general \emph{local} ansatz
   for two-loop four-point pure Yang-Mills fails to satisfy
@@
 
-TODO:\\
-For now, let's put the things we need to check/compute here in the abstract. 
-\begin{enumerate}
+%TODO:\\
+%For now, let's put the things we need to check/compute here in the abstract. 
+%\begin{enumerate}
 %\item Settle on $n$ vs $N$ vs $\mathcal{N}$ as the symbol for
@@
 
-\item \ace{I am starting to get a bit concerned about the overuse of the
-  phrase ``color-dual''} \nhp{We all choose capital $N$}
-\item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
-    , \textcolor{cut-color}{\texttt{cut-color}},
-    \textcolor{refl-color}{\texttt{refl-color}}, and
-    \textcolor{jacobi-color}{\texttt{jacobi-color}} as aliases for
-    other colors so that we don't have to keep changing colors in
-    multiple locations when we want to change diagram color schemes.
-    I think I have updated all of the diagrams to use the
-    correctly-named color, but haven't changed any of the backing
-    colors for the names.}
-\end{enumerate}
+%\item \ace{I am starting to get a bit concerned about the overuse of the
+  %phrase ``color-dual''} \nhp{We all choose capital $N$}
+%\item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
+   % , \textcolor{cut-color}{\texttt{cut-color}},
+  %  \textcolor{refl-color}{\texttt{refl-color}}, and
+  %  \textcolor{jacobi-color}{\texttt{jacobi-color}} as aliases for
+  %  other colors so that we don't have to keep changing colors in
+   % multiple locations when we want to change diagram color schemes.
+    %I think I have updated all of the diagrams to use the
+  %  correctly-named color, but haven't changed any of the backing
+   % colors for the names.}
+%\end{enumerate}
 }
@@
 
+Color-kinematics duality is a statement about color factors, kinematic
+numerators, and the accompanying Jacobi relations.  Adjoint-type color
+factors are associated with cubic graphs, so satisfying
+color-kinematics duality implicitly requires expressing the integrand
+in terms of such graphs. As mentioned earlier, this is possible to do
+even for a theory with quartic (or higher multiplicity) vertices by
+multiplying and dividing by propagators.  In the case of the four-point
+two-loop example promised above, there are 14 cubic graph topologies
+(shown in \cref{fig:MaxCuts}) ignoring tadpoles and bubble on external
+leg (BEL) graphs.
+
+With the integrand expressed in terms of cubic graphs, it is possible
+to discuss the main ingredient in color-kinematics duality -- the
+Jacobi relations.  The color factors in an integrand obey a set of
+Jacobi identities.  Color-kinematics duality states that there
+\emph{exists} a way of writing the kinematic numerators of the
+integrand so that they obey the same set of Jacobi identities.  The
+Jacobi identities can be divided into two categories: \emph{defining}
+relations and \emph{boundary} relations.  Defining Jacobi relations
+can be used to express any graph in terms of a basis.  For example,
+the double box, crossed box, and penta-triangle are related to each
+other as follows \be % [[11]]
+\label{eq:TwoLoopJacobiOne}
+\JacobiOneDoubleBox + \JacobiOneCrossedBox + \JacobiOnePentaTriangle
+=0\,,
+\end{equation}
+where the shared propagator is shown in red.  Using this relation the
+crossed box can be written (or \emph{defined}) in terms of the other
+two.  In this way, all of the 14 cubic four-point two-loop topologies can be
+written in terms of a basis of the double box and penta-triangle.
+(Any two of the double box, crossed box, and penta-triangle would
+suffice for a basis but the planar basis is chosen for simplicity in
+this work.)  The numerator of each of the two basis graphs receives
+its own ansatz and the numerator of any other graph can be expressed
+in terms of these two.
+
+After using the defining Jacobi relations to relate every graph to the
+basis, any remaining Jacobi relations will be referred to as boundary
+relations.  In other words, boundary relations (indirectly) relate
+basis elements to themselves.  For example, the crossed box numerator
+is related to itself via the following Jacobi relation \be % [[19]]
+\label{eq:TwoLoopJacobiTwo}
+\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
+\end{equation}
+where the shared propagator is shown in red as before.  Each of the
+crossed box numerators can be written in terms of the double box and
+penta-triangle so this Jacobi relation places constraints on the basis
+numerator \ansatze{}.  While defining Jacobi relations simplify how
+many numerators require \ansatze{}, boundary relations place
+restrictions on those \ansatze{}.  In principle there could be Jacobi
+relations involving tadpoles and BEL graphs, which would be subtle to
+handle.  One option is to force the numerators of these graphs to
+zero.  However, since these graphs will not contribute to physical
+unitarity cuts, we take a different approach.  These graphs are
+allowed to have non-zero numerators but any Jacobi relations involving
+them are simply not imposed or solved.  See Refs.~\cite{Bern:2012uf,
+  Edison:2022jln} for discussions of BELs in the context of
+color-kinematics duality.
 \paragraph{Color-kinematics duality}
@@
   \end{figure}
-
-Color-kinematics duality is a statement about color factors, kinematic
-numerators, and the accompanying Jacobi relations.  Adjoint-type color
-factors are associated with cubic graphs, so satisfying
-color-kinematics duality implicitly requires expressing the integrand
-in terms of such graphs. As mentioned earlier, this is possible to do
-even for a theory with quartic (or higher multiplicity) vertices by
-multiplying and dividing by propagators.  In the case of the four-point
-two-loop example promised above, there are 14 cubic graph topologies
-(shown in \cref{fig:MaxCuts}) ignoring tadpoles and bubble on external
-leg (BEL) graphs.
-
-With the integrand expressed in terms of cubic graphs, it is possible
-to discuss the main ingredient in color-kinematics duality -- the
-Jacobi relations.  The color factors in an integrand obey a set of
-Jacobi identities.  Color-kinematics duality states that there
-\emph{exists} a way of writing the kinematic numerators of the
-integrand so that they obey the same set of Jacobi identities.  The
-Jacobi identities can be divided into two categories: \emph{defining}
-relations and \emph{boundary} relations.  Defining Jacobi relations
-can be used to express any graph in terms of a basis.  For example,
-the double box, crossed box, and penta-triangle are related to each
-other as follows \be % [[11]]
-\label{eq:TwoLoopJacobiOne}
-\JacobiOneDoubleBox + \JacobiOneCrossedBox + \JacobiOnePentaTriangle
-=0\,,
-\end{equation}
-where the shared propagator is shown in red.  Using this relation the
-crossed box can be written (or \emph{defined}) in terms of the other
-two.  In this way, all of the 14 cubic four-point two-loop topologies can be
-written in terms of a basis of the double box and penta-triangle.
-(Any two of the double box, crossed box, and penta-triangle would
-suffice for a basis but the planar basis is chosen for simplicity in
-this work.)  The numerator of each of the two basis graphs receives
-its own ansatz and the numerator of any other graph can be expressed
-in terms of these two.
-
-After using the defining Jacobi relations to relate every graph to the
-basis, any remaining Jacobi relations will be referred to as boundary
-relations.  In other words, boundary relations (indirectly) relate
-basis elements to themselves.  For example, the crossed box numerator
-is related to itself via the following Jacobi relation \be % [[19]]
-\label{eq:TwoLoopJacobiTwo}
-\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
-\end{equation}
-where the shared propagator is shown in red as before.  Each of the
-crossed box numerators can be written in terms of the double box and
-penta-triangle so this Jacobi relation places constraints on the basis
-numerator \ansatze{}.  While defining Jacobi relations simplify how
-many numerators require \ansatze{}, boundary relations place
-restrictions on those \ansatze{}.  In principle there could be Jacobi
-relations involving tadpoles and BEL graphs, which would be subtle to
-handle.  One option is to force the numerators of these graphs to
-zero.  However, since these graphs will not contribute to physical
-unitarity cuts, we take a different approach.  These graphs are
-allowed to have non-zero numerators but any Jacobi relations involving
-them are simply not imposed or solved.  See Refs.~\cite{Bern:2012uf,
-  Edison:2022jln} for discussions of BELs in the context of
-color-kinematics duality.
-
 \ace{Awkward phrasing/transition.} \nhp{will message language} What has just been described is
@@
   JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview,
-  Edison:2022jln, Edison:2022smn}. Recently, generalized unitarity was optimized for
-even-multiplicity theories like NLSM \cite{Carrasco:2023qgz}.
-
-Generalized unitarity equates products of on-shell tree amplitudes,
+  Edison:2022jln, Edison:2022smn}, which was recently optimized for effective field theories like NLSM \cite{Carrasco:2023qgz}. Generalized unitarity equates products of on-shell tree amplitudes,
 encoded via a graph $\gamma$, to sums over compatible\footnote{A
@@
 \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
-heart of YZ-theory \cite{Cheung:2016prv}, J-theory
+heart of $YZ$-theory \cite{Cheung:2016prv}, J-theory
 \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
@@
 $YY$-loop is a valid forward limit for producing NLSM amplitudes,
-since as constructed YZ theory matches to NLSM for off-shell
+since as constructed $YZ$-theory matches to NLSM for off-shell
 Y-particles. We provide explicit expressions for these one-loop amplitudes in the next section.
@@
 This integrand numerator with internal scalar loop is precisely what
-one would obtain from the Feynman rules of YZ-theory, absent the $\bar{Z}Z$
+one would obtain from the Feynman rules of $YZ$-theory, absent the $\bar{Z}Z$
 internal vector loop. For more background, we refer the reader to
@@
 
-\subsection{YZ-Theory}
+\subsection{$YZ$-theory}
 Both SDYM and ZM theory involve explicit reliance to the spacetime
@@
 dimensionally-regulated loop-level amplitudes.  On the other hand,
-YZ-theory is an honest $D$-dimensional theory that captures the
+$YZ$-theory is an honest $D$-dimensional theory that captures the
 classical physics of the nonlinear sigma model (NLSM) while
@@
 
-One can understand YZ-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions. 
+One can understand $YZ$-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions. 
 Starting with the Yang-Mills Lagrangian, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
@@
 As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
-Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
+Given this special property of $YZ$-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
 This is essentially what $J$-thepory does, as we will show below.

### 2023-09-21 notes/2loopNLSM.tex
Fixed scaling on automorphism diagram equations.
Cleaned up end-of-graph-symmetries comment.

@@
 For example, the symmetries of the crossed box are spanned by,
-\nhp{Alex, fix the scaling to get the boxes to fit}
-\be
-\CrossedBoxGraphSym{1}{2}{3}{4}\!\! \sim\!\! \CrossedBoxGraphSym{2}{1}{3}{4} 
+\begin{equation}
+\scalebox{0.8}{\CrossedBoxGraphSym{1}{2}{3}{4}}\!\! \sim\!\! \scalebox{0.8}{\CrossedBoxGraphSym{2}{1}{3}{4}}
 \text{ and }
-\CrossedBoxGraphSym{1}{2}{3}{4} \!\!\sim\!\! \CrossedBoxGraphSym{2}{1}{4}{3}
-\ee
-%\ace{is there a reason we commented out this diagram?} \jm{You can try
+\scalebox{0.8}{\CrossedBoxGraphSym{1}{2}{3}{4}} \!\!\sim\!\! \scalebox{0.8}{\CrossedBoxGraphSym{2}{1}{4}{3}}
+\end{equation}
+% \ace{is there a reason we commented out this diagram?} \jm{You can try
  % either one.  I liked the one I left in better.}  For example, the
@@
 %\end{equation}
-which are just functional relabelings of external legs, $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
-In general, internal edge labels must be tracked as well.
-Furthermore, care must be taken with the signs in a symmetry relation.
-To compensate for the antisymmetric color factors, $f^{abc}$, graph
-vertices are all totally antisymmetric and hence have signs built into
-their orientations.  Once imposing symmetry relations, the crossed box can be expressed in terms of the double box
-and penta-triangle, thus imposing non-trivial constraints on the
-ansatz. 
-\nhp{Someone add in comment here about how symmetry relations imposes constraints of jacobi from equation above}.
-%\ace{I'm not quite sure why the signs are mentioned in the
-%  previous sentence?}
+which are just functional relabelings of external legs,
+$\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.  In general,
+internal edge labels must be tracked as well.  Furthermore, care must
+be taken with the signs in a symmetry relation.  To compensate for the
+antisymmetric color factors, $f^{abc}$, graph vertices are all totally
+antisymmetric and hence have signs built into their orientations.
+When used in conjuction with the Jacobi relations, \eg
+\cref{eq:TwoLoopJacobiOne}, the symmetry constraints of non-basis
+graphs still impose conditions on the basis ansatz.  In fact, since
+the symmetry properites of a graph are directly linked with
+transformations of its color dressing, the resulting constraints can
+be thought of as a subclass of the \emph{boundary} Jacobi relations.
 

### 2023-09-21 notes/2loopNLSM.tex
Reworked intro to section 4, incorporating some of the statements at the beginning of 4.1

@@
 cut. As an example, consider the ``bowtie'' cut topology -- one of the
-factorization channels of the iterated unitarity cut -- which has two
+factorization channels of the iterated unitarity cut -- that has two
 topologically distinct color-ordered expansions
@@
 Plugging in on-shell all-plus helicity states in light-cone gauge will
-yield precisely the 4D SDYM vertex, up to an unphysical phase \ace{Can
-  we provide an example?} \nhp{yes, provided}:
+yield precisely the 4D SDYM vertex, up to an unphysical phase:
   \be
@@
 
-Thus, to construct two-loop numerators prescriptively, as we have done at one-loop, would require knowledge of
-the full kinematic algebra for Yang-Mills off-shell. Since this is
-presently unavailable, to approach the problem of two-loop
-construction, we instead employ an ansatz based approach.
-
-\section{Two-loop bootstrap}
+Thus, to construct two-loop numerators prescriptively, as we have done
+at one-loop, would require knowledge of the full kinematic algebra for
+Yang-Mills off-shell. Since this is presently unavailable, to approach
+the problem of two-loop construction, we instead employ an ansatz
+based approach.
+
+\section{Two-loop four-point bootstrap}
 \label{2loopBoot}
-\ace{Lets bulk this section intro up a bit} \nhp{@Alex will bulk this up}
-
-We now employ the color-dual bootstrap method described in
-\cref{sec:bootstrap}. We will start with an ansatz constructed from
-$D$-dimensionally Lorentz covariant kinematics. To fix remaining
-freedom in the NLSM bootstrap, we will match down to ZM theory in
-$D=2$. This is merely an aesthetic choice, so the final results of
-both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
-
-\subsection{Two-loop NLSM}
-\label{sec:pions}
-
-As we have seen, it is possible to coerce tree numerators into 1-loop
-numerators at any multiplicity for pions.  However, these methods
-cannot be reapplied to generate higher-loop numerators, which begs the
-question ``is it possible to find globally color-dual numerators
-beyond 1-loop?''  We will tackle this question for four-point two-loop
-scattering in NLSM before moving on to the same process in YM.
-
+
+As we have just seen, it is possible to coerce tree numerators into
+1-loop numerators at any multiplicity for pions (and related
+theories), but that these methods cannot be reapplied to generate
+higher-loop numerators.  For pions in particular, the no-go statement
+is only for \emph{one particular representation of the theory} so does
+not completely preclude the existence of a two-loop color-dual
+representation.  We thus turn to the color-dual bootstrap method
+described in \cref{sec:bootstrap} to construct a color-dual
+representation of two-loop four-point NLSM.  Because of the similarity
+of the problem setup, we will also use the opportunity to revisit the
+construction of a color-dual representation of pure YM, extending the
+search space beyond what was covered in Ref.~\cite{Bern:2015ooa}.
+
+Both representations share the same cubic graph basis, and thus their
+defining Jacobi relations lead to the same numerator basis.
 Ignoring tadpoles and BEL graphs, there are 14 cubic four-point two-loop
@@
 \end{equation}
+However, the actual numerator dressings and physical properties
+differ, so we discuss them separately below.
+
+\subsection{Two-loop NLSM}
+\label{sec:pions}
+
 For a scalar theory like NLSM the numerator only depends on dot
-products of momenta.  The basis of momentum invariants for both of
-these graphs can be taken to be
+products of momenta.  The basis of momentum invariants for both of the
+graphs can be taken to be
 \begin{equation}
 \label{eq:scalar-basis}
-\{ k_{13}, k_{23}, k_{15}, k_{16}, k_{25}, k_{26}, k_{35}, k_{36}, k_{55}, k_{56}, k_{66} \},
+N^{\text{NLSM}}\left[
+  \scalebox{0.75}{\NLSMBasisDoubleBox} \right]
+\text{ and }
+N^{\text{NLSM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]\in
+\left\{\begin{array}{cccc}
+    k_{13},& k_{23},& k_{15},& k_{16}, \\
+    k_{25},& k_{26},& k_{35},& k_{36}, \\
+    k_{55},& k_{56},& k_{66}
+  \end{array}
+  \right\},
 \end{equation}
@@
 
-\begin{figure}
-  \begin{center}
-	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
-  \end{center}
-  \caption{The two physical cut topologies shared by NLSM, sGal, BI, and DBIVA}
-  \label{fig:emu}
-\end{figure}
-
 The final essential constraint is unitarity.  The two physical cuts
@@
 representing the generalized gauge freedom in the answer.
+
+\begin{figure}[h]
+  \begin{center}
+	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
+  \end{center}
+  \caption{The two physical cut topologies shared by NLSM, sGal, BI, and DBIVA}
+  \label{fig:emu}
+\end{figure}
 

### 2023-09-21 notes/2loopNLSM.tex
Merged the two ZM footnotes in the pion section.

@@
 possible to enforce the no triangle hypothesis, manifest loop power
-counting, and, for four-point and up to at least six loops, strip off a
-factor of $st \atree$ from the integrand \cite{FiveLoopN4,
+counting, and, for four-point and up to at least six loops, strip off
+a factor of $st \atree$ from the integrand \cite{FiveLoopN4,
   Bern:2012uf, Bern:2010fy, SuperSum, Carrasco:2021otn,
@@
 color-kinematics duality to all loop orders, namely,
-Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}. ZM theory is governed by the Lagrangian
+Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp,
+  Cheung:2022mix}. ZM theory is governed by the Lagrangian
 \begin{equation}
@@
 \ace{Lets tighten up this paragraph a bit, especially the second half}
-It is tempting to try to match the pion four-point two-loop integrand to ZM
-on the cuts, but given that the cuts only probe the on-shell four-point
-amplitude, which is either subtle or vanishes for ZM, it is better to
-compare the off-shell numerators directly.  As local functions, the
-numerators never suffer from any of the subtleties of on-shell 2D
-kinematics.  Since the physical cuts are difficult to compare, ZM
-theory is being used here simply as a tool to eliminate generalized
-gauge freedom; ZM theory has the right power counting and kinematic
-structure in 2D to compare against.  Since ZM theory is only being
-used for the kinematical structure of its numerators, it is natural to
-introduce a proportionality constant $z$ between the NLSM and ZM
-numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
+It is tempting to try to match the pion four-point two-loop integrand
+to ZM on the cuts, but given that the cuts only probe the on-shell
+four-point amplitude, which is either subtle or vanishes for ZM, it is
+better to compare the off-shell numerators directly.  As local
+functions, the numerators never suffer from any of the subtleties of
+on-shell 2D kinematics.  Since the physical cuts are difficult to
+compare, ZM theory is being used here simply as a tool to eliminate
+generalized gauge freedom; ZM theory has the right power counting and
+kinematic structure in 2D to compare against.  Since ZM theory is only
+being used for the kinematical structure of its numerators, it is
+natural to introduce a proportionality constant $z$ between the NLSM
+and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
 parameter $z$, which would normally be fixed on cuts, effectively
@@
   different from NLSM even though they are dual classically in two
-  dimensions \cite{Nappi:1979ig}.}  This introduces an extra degree of
+  dimensions \cite{Nappi:1979ig}.  When the four-point
+  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
+  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
+  $z$ is fixed to $216/565$, which is clearly unrelated to the
+  difference in coupling constants.}  This introduces an extra degree of
 freedom into the problem.  Mechanically, the pion numerator is matched
@@
 freedom parameters reduces to 58.  The pion numerator appearing in the
-ancillary files makes exactly this choice.\footnote{When the four-point
-  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
-  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
-  $z$ is fixed to $216/565$, which is clearly unrelated to the
-  difference in coupling constants.} \ace{Is this actually where we
+ancillary files makes exactly this choice. \ace{Is this actually where we
   want this particular footnote to appear?}

### 2023-09-21 notes/2loopNLSM.tex
Resized YM numerator span diagrams.
fixed forward refs in catalog app

--- 2023-09-21 notes/2loopNLSM.tex
@@
 Though generally these quadratic dressings are simply delta functions, $P_V^{ab} = \delta^{ab}$, or flat space metrics, $P_W^{\mu\nu}=\eta^{\mu\nu}$.
-As written, the theory will be color dual if the off-shell cubic vertex is antisymmetric and satisfies the Jacobi identity,
-specifically,
+As written, the theory will be color dual if the off-shell cubic vertex is antisymmetric and satisfies the Jacobi identity.
+Specifically,
 \begin{align}
@@
 \\
-\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0
+\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\label{jacID}
 \end{align}
@@
 For example, the symmetries of the crossed box are spanned by,
-\begin{equation}
-\scalebox{0.8}{\CrossedBoxGraphSym{1}{2}{3}{4}}\!\! \sim\!\! \scalebox{0.8}{\CrossedBoxGraphSym{2}{1}{3}{4}}
+\nhp{Alex, fix the scaling to get the boxes to fit}
+\be
+\CrossedBoxGraphSym{1}{2}{3}{4}\!\! \sim\!\! \CrossedBoxGraphSym{2}{1}{3}{4} 
 \text{ and }
-\scalebox{0.8}{\CrossedBoxGraphSym{1}{2}{3}{4}} \!\!\sim\!\! \scalebox{0.8}{\CrossedBoxGraphSym{2}{1}{4}{3}}
-\end{equation}
-% \ace{is there a reason we commented out this diagram?} \jm{You can try
+\CrossedBoxGraphSym{1}{2}{3}{4} \!\!\sim\!\! \CrossedBoxGraphSym{2}{1}{4}{3}
+\ee
+%\ace{is there a reason we commented out this diagram?} \jm{You can try
  % either one.  I liked the one I left in better.}  For example, the
@@
 %\end{equation}
-which are just functional relabelings of external legs,
-$\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.  In general,
-internal edge labels must be tracked as well.  Furthermore, care must
-be taken with the signs in a symmetry relation.  To compensate for the
-antisymmetric color factors, $f^{abc}$, graph vertices are all totally
-antisymmetric and hence have signs built into their orientations.
-When used in conjuction with the Jacobi relations, \eg
-\cref{eq:TwoLoopJacobiOne}, the symmetry constraints of non-basis
-graphs still impose conditions on the basis ansatz.  In fact, since
-the symmetry properites of a graph are directly linked with
-transformations of its color dressing, the resulting constraints can
-be thought of as a subclass of the \emph{boundary} Jacobi relations.
+which are just functional relabelings of external legs, $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
+In general, internal edge labels must be tracked as well.
+Furthermore, care must be taken with the signs in a symmetry relation.
+To compensate for the antisymmetric color factors, $f^{abc}$, graph
+vertices are all totally antisymmetric and hence have signs built into
+their orientations.  Once imposing symmetry relations, the crossed box can be expressed in terms of the double box
+and penta-triangle, thus imposing non-trivial constraints on the
+ansatz. 
+\nhp{Someone add in comment here about how symmetry relations imposes constraints of jacobi from equation above}.
+%\ace{I'm not quite sure why the signs are mentioned in the
+%  previous sentence?}
 
@@
 clever reinterpretation of the Lagrangian obtained by integrating an
-auxiliary field into the J-theory equations of motion.  The Feynman
+auxiliary field into the $J$-theory equations of motion.  The Feynman
 rule for the cubic vertex is
@@
 
-Below we review the four manifestly color-dual theories that appear in
-this paper, in particular SDYM, two formulations of NLSM, and ZM.  All
+Below we review the four manifestly color-dual theories that we mention in
+the text, in particular self-dual Yang-Mills (SDYM) \cite{Monteiro2011pc}, two formulations of NLSM \cite{Cheung:2016prv,Cheung:2020djz,Cheung:2021zvb}, and ZM \cite{Zakharov:1973pp, Cheung:2022mix}.
+All
 of these theories are closely tied together by the semi-abelian YM
-theory in \cref{eq:semiYM} or in other words the cubic sector of YM.
+theory in \cref{eq:semiYM}, which gives the cubic sector of pure YM.
 The manifestly color-dual equations of motion for SDYM and NLSM are
-derived by picking a gauge and then placing a constraint not on the YM
-equation of motion or Bianchi identity but rather directly on the
-field strength itself.  Other theories can be obtained from SDYM and
-NLSM by judicious modification of the propagator.  In all of these
-theories, the kinematic algebra is that of (volume preserving)
-diffeomorphisms or some close variant thereof.  In almost all of these
+derived by picking a gauge and then placing a constraint directly on the
+field strength. In almost all of these
 theories, Bose symmetry is broken or obscured at the Lagrangian level.
 Because of the broken Bose symmetry (and the inherited kinetic mixing
-of semi-abelian YM), these theories cannot produce color-dual
-numerators at two-loop or higher.
-
-\ace{There are some cyclic references in the catalog that are gonna be
-  a bit annoying to clean up: ZM refers to J, YZ refers to ZM and
-  SDYM, J refers to YZ.  I have currently switched the order to: SDYM,
-  ZM, YZ, J, but we should probably discuss.}
+of semi-abelian YM), these theories require additional interactions to produce color-dual representations beyond one-loop.
 
@@
 \end{equation}
-Solutions to \cref{SDcon} correspond to instanton configurations that
-are probed by the gauge field path integral in the full
-non-perturbative description of Yang-Mills. In this paper, we will
-focus on the perturbative aspects of this constraint. We begin by
+Furthermore, field configurations that satisfy \cref{SDcon} correspond to instantons which are probed by the path integral in the full non-perturbative description of Yang-Mills.
+To construct a perturbative action, begin by
 transforming from Cartesian coordinates to light cone coordinates,
@@
 \begin{equation}
-u = t+x,\quad v=t-x, \quad w = y+iz
+u = t+x,\quad v=t-x, \quad w = y+iz, \quad \bar{w} = y-iz
 \end{equation}
@@
 \end{align}
-This last constraint can be manifested by writing the gauge field in
+This last constraint is satisfied by writing the gauge field in
 terms of a single degree of freedom which we call $\Psi$:
@@
 
+\subsection{YZ-theory}
+Self-dual Yang-Mills involves explicit reliance on the spacetime
+dimension, which makes the theory poorly suited for constructing
+dimensionally-regulated loop-level amplitudes.  On the other hand,
+$YZ$-theory of \cite{Cheung:2016prv} is an honest $D$-dimensional theory that captures the
+classical physics of the nonlinear sigma model (NLSM) while
+manifesting the duality between color and kinematics.
+
+One can understand $YZ$-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions \cite{Cheung:2017yef}, down to $d$-dimensions. 
+Starting with the Yang-Mills Lagrangian of \cref{eq:ym-lag}, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
+\begin{align}
+X_M &= (X_\mu,0,-iX_\mu) 
+\\
+Y_M &= (0,Y,0) 
+\\
+Z_M &= (Z_\mu,0,iZ_\mu) 
+\end{align}
+where $X$ and $Z$ are $d$-vectors and $Y$ is a scalar field.
+Considering the conjugate nature of the $XZ$ propagator, in this work we make the replacement $X\rightarrow \bar{Z}$.
+Plugging this redefinition of the gauge fields in,, we thus obtain the following Lagrangian up to cubic order in the interactions:
+\begin{equation}
+\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)
+\end{equation}
+The Feynman rules for this Lagrangian are simply:
+\begin{equation}
+\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i (\varepsilon_3 p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{3})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{3})(\varepsilon_1\bar{\varepsilon}_3)
+\end{equation}
+Note that the pure vector vertex on the left is \textit{exactly} what was obtain from semi-abelian YM in \cref{eq:semiYM}.
+Using this, we review of the construction of NLSM numerators at tree-level.
+In this construction, we can define generators of the kinematic algebra as follows
+\be\label{eq:FeynmanRuleYYZ}
+T^a_{ij}= i \varepsilon_a(p_i-p_j)
+\end{equation}
+where momentum conservation requires
+\begin{equation}
+p_a + p_i + p_j =0
+\end{equation}
+The kinematic half-ladder diagrams then takes on the following concise definition:
+\begin{equation}
+n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
+\end{equation}
+Since there are no pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the chiral current algebra is manifestly cubic.
+Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom.
+They can be defined implicitly below:
+\begin{equation}
+[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}
+\end{equation}
+Given this definition, the Feynman rule associated with kinematic structure constant is simply:
+\be\label{eq:FeynmanRuleXZZ}
+i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c) 
+\end{equation}
+where $p_{ab}=p_a+p_b$ and $\varepsilon$ and $\bar{\varepsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
+The gauge-fixed state sum for this theory is simply:
+\begin{equation}
+\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}
+\end{equation}
+Notice that the vector state sum is gauge fixed since the $YZ$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$.
+To recover NLSM amplitudes from this these kinematic structure constants at tree-level, we simply plug in the following on-shell polarizations for the $Z$ and $\bar{Z}$ particles:
+\be\label{eq:onShellZStates}
+\varepsilon^\mu_{(p)} = p^\mu \qquad \bar{\varepsilon}^\mu_{(p)} = \frac{q^\mu}{pq}
+\end{equation}
+where $q^2=0$ is some null reference momentum. With this, we can define tree-level pion scattering in two equivalent ways:
+\begin{equation}
+A^{\text{NLSM}} = A(...,Y,...,Y,...) = A(...,\bar{Z},...) 
+\end{equation}
+where the ellipses denote additional on-shell $Z$-particles.
+Subject to a particular gauge choice, the kinematic numerators in latter definition for pion scattering is equivalent to those $J$-theory, first written down by Cheung and one of the authors \cite{Cheung:2021zvb}.
+In this paradigm, the on-shell $\bar{Z}$ state is equivalent to the root leg appearing in the color-dual $J$-theory numerators.
+
+It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion.
+First we'll start with two $Y$ particles on legs 1 and 4.
+Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
+\begin{align}
+n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
+\\
+ n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
+\end{align}
+Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
+\be\label{eq:NLSMYZ4point}
+A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
+\end{equation}
+Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration.
+Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free.
+This produces the following numerators:
+\begin{align}
+n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
+\\
+ n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
+\end{align}
+where we have defined the short hand notation:
+\begin{equation}
+{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
+\end{equation}
+Similarly, we find the following ordered amplitude when plugging in these numerators:
+\begin{equation}
+A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
+\end{equation}
+Plugging in the on-shell polarizatoin of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
+Indeed, this construction is valid to all orders at tree-level.
+One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
+\begin{align}
+A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
+\\
+&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
+\end{align}
+Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
+As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
+Given this special property of $YZ$-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
+This is essentially what $J$-theory does, as we will show below.
+
+\subsection{J-theory}
+The construction begins with a first order
+formulation of NLSM in terms of chiral currents, $J^\mu$ \cite{Cheung:2021zvb}, subject to particular constraints. For related formulations of NLSM that do not
+treat color-kinematics duality see \cite{Freedman:1980us,
+  Slavnov:1971mz}. The first constraint is that the field strength associated with $J_\mu$ should vanish:
+\begin{equation}
+\label{eq:FieldStrengthJ}
+F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
+\end{equation}
+which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
+The second condition is that the chiral current should be in Lorenz gauge
+\begin{equation}
+\label{eq:LorenzGaugeJ}
+\partial_\mu J^\mu=0
+\end{equation}
+which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
+Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
+\begin{equation}
+\label{eq:JTheoryEOM}
+\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
+\end{equation}
+Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
+Since both theories are in Lorenz gauge this means that \emph{J-theory and semi-abelian YM are identical}.
+Furthermore, this theory is one-to-one with the observables amplitudes of $YZ$-theory when only considering $Z$$\bar{Z}$ on-shell states.
+As such, the single vertex in this theory is the same as the pure vector vertex of $YZ$ theory in Lorenz gauge, where $\partial_\mu J^\mu = 0$:
+\begin{equation}
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
+\end{equation}
+By calculating an off-shell four-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality, as described in \cref{offShellCK}.
+As might be expected, the kinematic algebra is the diffeomorphism algebra \cite{Cheung:2021zvb}. Note that the different external particles break manifest Bose symmetry.
+
 \subsection{Zakharov-Mikhailov theory}
 \label{sec:ZMTheory}
-While J-theory manifests color-kinematics duality, it only does so at
-tree level because J-theory breaks manifest Bose symmetry.  Manifest
+While $J$-theory manifests color-kinematics duality, it only does so at
+tree level because $J$-theory breaks manifest Bose symmetry.  Manifest
 color-kinematics duality can be achieved at all loop orders by
-restricting J-theory to two spacetime dimensions where the chiral
+restricting $J$-theory to two spacetime dimensions where the chiral
 current can be dualized to a scalar
@@
 This procedure makes it clear that ZM and NLSM encode the same
-classical physics, that is, their equations of motion are dual to each
-other.  ZM theory can also be tenuously motivated from SDYM theory.
+classical physics, since their equations of motion are dual to each
+other.  Furthermore, ZM theory can also be motivated from SDYM theory.
 The power counting of the interaction term in the SDYM equation of
@@
 cannot be interpreted as the 2D equivalent, so the kinetic term of
-SDYM must be replaced with the correct 2D version.  This argument
-should be understood purely as an alternative route to ZM theory.
-While NLSM and ZM are the same theory classically when restricted to
-2D, SDYM and ZM are not because, for example, the tree amplitudes of
-SDYM vanish but those of ZM do not (cite argumentative papers).
+SDYM must be replaced with the correct 2D version.
+However, changing the kinetic term in \cref{cubicCKLag} will have no effect on the Jacobi identity of \cref{jacID}, and thus does not interfere color-kinematics duality.
 
@@
 \end{equation}
-The vertex is (1) functionally symmetric and (2) the kinematic portion
+Unlike $J$-theory and $YZ$-theory, the vertex is (1) functionally symmetric and (2) the kinematic portion
 of the vertex is completely anti-symmetric:
@@
 \ee
-
-Amusingly, since ZM theory manifested color-kinematics duality without any
+Furthermore, since ZM theory manifests color-kinematics duality without any
 reference to the on-shell condition, a mass term can be added to ZM
-theory without spoiling color-kinematics duality.  In fact, the
-kinetic term could be dramatically altered.  In general, if the
+theory without spoiling color-kinematics duality \cite{Cheung:2022mix}. In general, if the
 on-shell conditions are not used, color-kinematics duality is
-unaffected by the details of the propagator structure.  Of course,
-dramatically altering the pole structure could spoil locality in the
-double-coppied theory.  As already mentioned, the only difference
+unaffected by the details of the propagator structure.
+
+Of course, dramatically altering the pole structure could spoil locality in the
+double-copied theory.  As already mentioned, the only difference
 classically between ZM and SDYM is the propagator structure.  While
@@
 vanish and manifest color-kinematics does not persist to all loop
-orders.  Color dual theories with the same interactions but different
+orders.
+
+Color dual theories with the same interactions but different
 kinetic terms have appeared in the literature before.  For example,
-J-theory and the theory of non-Abelian fluids presented in
+$J$-theory and the theory of non-Abelian fluids presented in
 \cite{Cheung:2020djz} differ only in their propagators. Specifically,
@@
 term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates
-yields the relativistic d'Alembertian of $D$-dimensional J-theory.
+yields the relativistic d'Alembertian of $D$-dimensional $J$-theory.
 
@@
 in promoting the integrands to formal $D$-dimensional expressions. As
-such, in our two-loop bootstrap of NLSM we will only use the ZM
+such, in our two-loop bootstrap of NLSM we only used the ZM
 integrands as a mechanism for reducing the residual gauge freedom in
-our final solution -- rather than a full $D$-dimensional integrand to
-which we match off-shell in dimensional regularization.
-
-\subsection{$YZ$-theory}
-Both SDYM and ZM theory involve explicit reliance to the spacetime
-dimension, which makes the theories poorly suited for constructing
-dimensionally-regulated loop-level amplitudes.  On the other hand,
-$YZ$-theory is an honest $D$-dimensional theory that captures the
-classical physics of the nonlinear sigma model (NLSM) while
-manifesting the duality between color and kinematics
-\cite{Cheung:2016prv}.
-
-One can understand $YZ$-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions, down to $d$ dimensions. 
-Starting with the Yang-Mills Lagrangian, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
-\begin{align}
-X_M &= (X_\mu,0,-iX_\mu) 
-\\
-Y_M &= (0,Y,0) 
-\\
-Z_M &= (Z_\mu,0,iZ_\mu) 
-\end{align}
-where $X$ and $Z$ are $d$-vectors and $Y$ is a scalar field.
-Considering the conjugate nature of the $XZ$ propagator, in this work we will make the replacement $X\rightarrow \bar{Z}$.
-Plugging this redefinition of the gauge fields in, upto cubic order, we thus obtain the following Lagrangian:
-\begin{equation}
-\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)
-\end{equation}
-The Feynman rules for this Lagrangian are simply:
-\begin{equation}
-\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i (\varepsilon_3 p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
-\end{equation}
-Now we review of the construction of NLSM numerators at tree-level. In this construction, we can define generators of the kinematic algebra can be expressed as follows
-\be\label{eq:FeynmanRuleYYZ}
-T^a_{ij}= i \varepsilon_a(p_i-p_j)
-\end{equation}
-where momentum conservation requires
-\begin{equation}
-p_a + p_i + p_j =0
-\end{equation}
-The kinematic half-ladder diagrams then takes on the following concise definition:
-\begin{equation}
-n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
-\end{equation}
-Since there are on pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the chiral current algebra is manifestly cubic.
-Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom.
-They can be defined implicitly below:
-\begin{equation}
-[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}
-\end{equation}
-Given this definition, the Feynman rule associated with kinematic structure constant is simply:
-\be\label{eq:FeynmanRuleXZZ}
-i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c) 
-\end{equation}
-where $p_{ab}=p_a+p_b$ and $\varepsilon$ and $\bar{\varepsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
-The on-shell state sum for the polarization vectors is simply:
-\begin{equation}
-\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}
-\end{equation}
-Notice that the vector state sum is gauge fixed since the $Y\,Z$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$.
-To recover NLSM amplitudes from this these kinematic structure constants at tree-level, we simply plug in the following on-shell polarizations for the $Z$ and $\bar{Z}$ particles:
-\be\label{eq:onShellZStates}
-\varepsilon^\mu_{(p)} = p^\mu \qquad \bar{\varepsilon}^\mu_{(p)} = \frac{q^\mu}{pq}
-\end{equation}
-where $q^2=0$ is some null reference momentum. With this, we can define tree-level pion scattering in two equivalent ways:
-\begin{equation}
-A^{\text{NLSM}} = A(...,Y,...,Y,...) = A(...,\bar{Z},...) 
-\end{equation}
-where the ellipses denote additional on-shell $Z$-particles.
-Subject to a particular gauge choice, the kinematic numerators in latter definition for pion scattering is equivalent to those $J$-theory, first written down by Cheung and one of the authors \cite{Cheung:2021zvb}.
-In this paradigm, the on-shell $\bar{Z}$ state is equivalent to the root leg appearing in the color-dual $J$-theory numerators.
-
-It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion.
-First we'll start with two $Y$ particles on legs 1 and 4.
-Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
-\begin{align}
-n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
-\\
- n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
-\end{align}
-Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
-\be\label{eq:NLSMYZ4point}
-A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
-\end{equation}
-Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration.
-Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free.
-This produces the following numerators:
-\begin{align}
-n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
-\\
- n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
-\end{align}
-where we have defined the short hand notation:
-\begin{equation}
-{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
-\end{equation}
-Similarly, we find the following ordered amplitude when plugging in these numerators:
-\begin{equation}
-A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
-\end{equation}
-Plugging in the on-shell polarizatoin of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
-Indeed, this construction is valid to all orders at tree-level.
-One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
-\begin{align}
-A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
-\\
-&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
-\end{align}
-Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
-As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
-Given this special property of $YZ$-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
-This is essentially what $J$-thepory does, as we will show below.
-
-\subsection{J-theory}
-There is an alternative color-dual formulation of NLSM that the theory
-manifestly corresponds to NLSM at least at tree level
-\cite{Cheung:2021zvb}.  For related formulations of NLSM that do not
-treat color-kinematics duality see \cite{Freedman:1980us,
-  Slavnov:1971mz}.  The construction begins with a first order
-formulation of NLSM in terms of chiral currents $J^\mu$.  First order
-formulation of NLSM in terms of chiral current $J^\mu$.  Two
-equations.  Two constraints, the field strength should vanish
-\begin{equation}
-\label{eq:FieldStrengthJ}
-F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
-\end{equation}
-which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
-The second condition is that the chiral current should be in Lorenz gauge
-\begin{equation}
-\label{eq:LorenzGaugeJ}
-\partial_\mu J^\mu=0
-\end{equation}
-which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
-Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
-\begin{equation}
-\label{eq:JTheoryEOM}
-\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
-\end{equation}
-Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
-Since both theories are in Lorenz gauge this means that \emph{J-theory and semi-abelian YM are identical}.
-By calculating an off-shell four-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
-As might be expected, the kinematic algebra is the diffeomorphism algebra.
-For details about external states and how to extract NLSM (a scalar theory) from semi-YM (a vector theory) we refer the reader to \cite{Cheung:2021zvb}.
-Note that the different external particles break manifest Bose symmetry.
-
-This theory is one-to-one with the observables amplitudes of $YZ$-theory when only considering $Z$$\bar{Z}$ on-shell states.
-As such, the single vertex in this theory is the same as the pure vector vertex of $YZ$ theory in Lorenz gauge, where $\partial_\mu J^\mu = 0$:
-\begin{equation}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
-\end{equation}
+our final solution.
 

### 2023-09-21 notes/2loopNLSM.tex
Small tweaks in YM.

--- 2023-09-21 notes/2loopNLSM.tex
@@
 freedom parameters reduces to 58.  The pion numerator appearing in the
-ancillary files makes exactly this choice. \ace{Is this actually where we
-  want this particular footnote to appear?}
+ancillary files makes exactly this choice.
 
@@
 
-\jm{Rather than quoting the number of parameters in the BDN ansatz, I
-  would prefer to just focus on what we did since it's more general.
-  I don't want it to sound like we just patched a minor hole in their
-  argument when I think you've done something much cooler by
-  pinpointing the failure to the bowtie graph. I know you put time and
-  effort into analyzing the BDN ansatz but I'm worried that the more
-  we talk about it, the more it will overshadow the real success
-  here.}
-
 Given the close ties between pion and gluon scattering for trees and
@@
 follow the same general procedure as in \cref{sec:pions}, again
-identifying the double-box (2box) and penta-triangle (pt) as the
+identifying the double-box and penta-triangle as the
 Jacobi basis graphs and building a the most general ansatz for each of
@@
 \begin{equation}
-  \mathcal{N}^{\text{YM}}\left[\NLSMBasisDoubleBox \right]\text{ and }\mathcal{N}^{\text{YM}}\left[\NLSMBasisPentaTriangle \right]\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
+  \mathcal{N}^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
+  \text{ and }
+  \mathcal{N}^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
+  \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
   \label{eq:ym-basis}

### 2023-09-21 notes/2loopNLSM.tex
Started working on solver footnote.

@@
 total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is
-  not suited to equations with sixteen thousand parameters so a
-  different method is desirable.  One possibility is to use a solver
-  designed for integral reduction.  However, these solvers typically
-  assume that the matrix has a very low density which is not the case
-  for equations coming from NLSM which typically have a density of a
-  few percent.  While the equations in YM naturally separate into
-  different ``helicity'' sectors (or $e_i \cdot e_j$ and
-  $e_i \cdot k_j$ sectors in $D$ dimensions), there is no such
-  separation of sectors in a scalar theory where any product of
-  momenta can interfere with any other.  The NLSM constraint equations
-  were solved using a custom solver, \texttt{FiniteFieldSolve},
-  designed to solve large linear systems of arbitrary density.
-  \texttt{FiniteFieldSolve} will be released publicly shortly.\ace{I
-    want to rephrase this slightly, but need to think about it a bit
-    more}} Imposing the boundary Jacobi relations eliminates all but
-4,473 of the original free parameters.  Further imposing graph
-symmetries reduces the number of free parameters to 1,243.
+  not suited to solving large sets of equations with sixteen thousand
+  parameters, so a different method is desirable.  One possibility is
+  to use a sprase solver, as often employed for integral reduction.
+  However, these solvers typically assume that the matrix has a very
+  low density which is not the case for equations coming from NLSM
+  which typically have a density of a few percent.  While the
+  equations in YM naturally separate into different ``helicity''
+  sectors (or $e_i \cdot e_j$ and $e_i \cdot k_j$ sectors in $D$
+  dimensions), there is no such separation of sectors in a scalar
+  theory where any product of momenta can interfere with any other.
+  The NLSM constraint equations were solved using a custom solver,
+  \texttt{FiniteFieldSolve}, designed to solve large linear systems of
+  arbitrary density.  \texttt{FiniteFieldSolve} will be released
+  publicly shortly.\ace{I want to rephrase this slightly, but need to
+    think about it a bit more}} Imposing the boundary Jacobi relations
+eliminates all but 4,473 of the original free parameters.  Further
+imposing graph symmetries reduces the number of free parameters to
+1,243.
 

### 2023-09-21 notes/2loopNLSM.tex

--- 2023-09-21 notes/2loopNLSM.tex
@@
 Color-kinematics duality is a statement about the off-shell graphical
-simplicity that manifest redundancy in the on-shell observables of
+simplicity that manifests redundancy in the on-shell observables of
 gauge and gravity theories. Ignoring factors of $i$ and the coupling
-constant, a generic $m$-point $L$-loop amplitude in a color-dual
-theory -- such as NLSM, YM, or bi-adjoint scalar
-theory\ace{technically this is true as written for any theory.  In
-  fact we slip that type of disclaimer in quite a lot throughout the
-  rest of the section} \jm{I removed the second time we say `YM, NLSM,
-  $\phi^3$' which was redundant.  I don't mind if we say it here
-  because I want people to tell people that these are the kinds of
-  theories we're thinking about.  We could omit it but then we'd have
-  to say that the theory has at least one color factor and is probably
-  an adjoint type theory and at that point I'd rather just give an
-  example.} \nhp{Nic will clarify between cubic vs color-dual here}-- can be written as
+constant, the starting point to realize the duality is to express generic $m$-point $L$-loop amplitudes in a cubic graph representation:
 \begin{equation}
@@
 Here the spacetime dimension is $D$.  Even though the underlying
-theory may have quartic (or higher multiplicity) vertices, it is
+theory may have quartic (or higher multiplicity) vertices, like NLSM and gravity, it is
 possible to multiply and divide by propagators so that the sum runs
@@
 the internal symmetry factor $S_\Gamma$, which tracks the number of
-graph symmetries with external legs held fixed.  The color factor
+graph symmetries with external legs held fixed.
+
+The color factor
 $c_\Gamma$ is the string of structure constants $f^{abc}$ associated
@@
 
-The color factors $c_\Gamma$ are not independent and are related to
+In this form the color factors $c_\Gamma$ are not independent and are related to
 one another via a set of Jacobi identities that look schematically
@@
 where $i$, $j$, and $k$ are three graphs.  Example Jacobi relations
-are presented in detail in \cref{sec:bootstrap}.  Color-kinematics
-duality states that there exists a way to rearrange factors between
+are presented in detail in \cref{sec:bootstrap}. The duality between color and kinematics is the statement that that there exists a way to rearrange factors between
 the various kinematic numerators $n_\Gamma$ such that the numerators
@@
 When the kinematic algebra is not known explicitly, the kinematic numerators are typically constructed from an ansatz.
-As an example, the result of such a calculation for 4pt pion scattering at tree level produces the numerators
+As an example, the result of such a calculation for four-point NLSM pion scattering at tree level produces the numerators
 \begin{align}
@@
 \emph{different} amplitude to produce the corresponding amplitude in
-the double-copy theory \be\label{DCconstruction}
+a new colorless theory: \be\label{DCconstruction}
 \tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
@@
 \end{equation}
+This is known as the double-copy construction \cite{BCJ,Bern:2010ue,BCJreview}.
 Importantly, the $\tilde{n}_\Gamma$ do not need to respect
@@
 total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is
-  not suited to equations with sixteen thousand parameters so a
-  different method is desirable.  One possibility is to use a solver
-  designed for integral reduction.  However, these solvers typically
-  assume that the matrix has a very low density which is not the case
-  for equations coming from NLSM which typically have a density of a
-  few percent.  While the equations in YM naturally separate into
-  different ``helicity'' sectors (or $e_i \cdot e_j$ and
-  $e_i \cdot k_j$ sectors in $D$ dimensions), there is no such
-  separation of sectors in a scalar theory where any product of
-  momenta can interfere with any other.  The NLSM constraint equations
-  were solved using a custom solver, \texttt{FiniteFieldSolve},
-  designed to solve large linear systems of arbitrary density.
-  \texttt{FiniteFieldSolve} will be released publicly shortly.\ace{I
-    want to rephrase this slightly, but need to think about it a bit
-    more}} Imposing the boundary Jacobi relations eliminates all but
-4,473 of the original free parameters.  Further imposing graph
-symmetries reduces the number of free parameters to 1,243.
-
-\begin{figure}
-  \begin{center}
-	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
-  \end{center}
-  \caption{The two physical cut topologies shared by NLSM, sGal, BI, and DBIVA}
-  \label{fig:emu}
-\end{figure}
+  not suited to solving large sets of equations with sixteen thousand
+  parameters, so a different method is desirable.  One possibility is
+  to use a sprase solver, as often employed for integral reduction.
+  However, these solvers typically assume that the matrix has a very
+  low density which is not the case for equations coming from NLSM
+  which typically have a density of a few percent.  While the
+  equations in YM naturally separate into different ``helicity''
+  sectors (or $e_i \cdot e_j$ and $e_i \cdot k_j$ sectors in $D$
+  dimensions), there is no such separation of sectors in a scalar
+  theory where any product of momenta can interfere with any other.
+  The NLSM constraint equations were solved using a custom solver,
+  \texttt{FiniteFieldSolve}, designed to solve large linear systems of
+  arbitrary density.  \texttt{FiniteFieldSolve} will be released
+  publicly shortly.\ace{I want to rephrase this slightly, but need to
+    think about it a bit more}} Imposing the boundary Jacobi relations
+eliminates all but 4,473 of the original free parameters.  Further
+imposing graph symmetries reduces the number of free parameters to
+1,243.
 
@@
 
+\begin{figure}[h]
+  \begin{center}
+	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
+  \end{center}
+  \caption{The two physical cut topologies shared by NLSM, sGal, BI, and DBIVA}
+  \label{fig:emu}
+\end{figure}
+
 % It is possible to automatically enforce (or ``bake in'') the double
@@
 freedom parameters reduces to 58.  The pion numerator appearing in the
-ancillary files makes exactly this choice.\footnote{When the four-point
-  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
-  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
-  $z$ is fixed to $216/565$, which is clearly unrelated to the
-  difference in coupling constants.} \ace{Is this actually where we
-  want this particular footnote to appear?}
+ancillary files makes exactly this choice.
 

### 2023-09-21 notes/2loopNLSM.tex
clarified cubic vs color-dual

@@
 cut. As an example, consider the ``bowtie'' cut topology -- one of the
-factorization channels of the iterated unitarity cut -- that has two
+factorization channels of the iterated unitarity cut -- which has two
 topologically distinct color-ordered expansions
@@
 Plugging in on-shell all-plus helicity states in light-cone gauge will
-yield precisely the 4D SDYM vertex, up to an unphysical phase:
+yield precisely the 4D SDYM vertex, up to an unphysical phase \ace{Can
+  we provide an example?} \nhp{yes, provided}:
   \be
@@
 
-Thus, to construct two-loop numerators prescriptively, as we have done
-at one-loop, would require knowledge of the full kinematic algebra for
-Yang-Mills off-shell. Since this is presently unavailable, to approach
-the problem of two-loop construction, we instead employ an ansatz
-based approach.
-
-\section{Two-loop four-point bootstrap}
+Thus, to construct two-loop numerators prescriptively, as we have done at one-loop, would require knowledge of
+the full kinematic algebra for Yang-Mills off-shell. Since this is
+presently unavailable, to approach the problem of two-loop
+construction, we instead employ an ansatz based approach.
+
+\section{Two-loop bootstrap}
 \label{2loopBoot}
-
-As we have just seen, it is possible to coerce tree numerators into
-1-loop numerators at any multiplicity for pions (and related
-theories), but that these methods cannot be reapplied to generate
-higher-loop numerators.  For pions in particular, the no-go statement
-is only for \emph{one particular representation of the theory} so does
-not completely preclude the existence of a two-loop color-dual
-representation.  We thus turn to the color-dual bootstrap method
-described in \cref{sec:bootstrap} to construct a color-dual
-representation of two-loop four-point NLSM.  Because of the similarity
-of the problem setup, we will also use the opportunity to revisit the
-construction of a color-dual representation of pure YM, extending the
-search space beyond what was covered in Ref.~\cite{Bern:2015ooa}.
-
-Both representations share the same cubic graph basis, and thus their
-defining Jacobi relations lead to the same numerator basis.
+\ace{Lets bulk this section intro up a bit} \nhp{@Alex will bulk this up}
+
+We now employ the color-dual bootstrap method described in
+\cref{sec:bootstrap}. We will start with an ansatz constructed from
+$D$-dimensionally Lorentz covariant kinematics. To fix remaining
+freedom in the NLSM bootstrap, we will match down to ZM theory in
+$D=2$. This is merely an aesthetic choice, so the final results of
+both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
+
+\subsection{Two-loop NLSM}
+\label{sec:pions}
+
+As we have seen, it is possible to coerce tree numerators into 1-loop
+numerators at any multiplicity for pions.  However, these methods
+cannot be reapplied to generate higher-loop numerators, which begs the
+question ``is it possible to find globally color-dual numerators
+beyond 1-loop?''  We will tackle this question for four-point two-loop
+scattering in NLSM before moving on to the same process in YM.
+
 Ignoring tadpoles and BEL graphs, there are 14 cubic four-point two-loop
@@
 \end{equation}
-However, the actual numerator dressings and physical properties
-differ, so we discuss them separately below.
-
-\subsection{Two-loop NLSM}
-\label{sec:pions}
-
 For a scalar theory like NLSM the numerator only depends on dot
-products of momenta.  The basis of momentum invariants for both of the
-graphs can be taken to be
+products of momenta.  The basis of momentum invariants for both of
+these graphs can be taken to be
 \begin{equation}
 \label{eq:scalar-basis}
-N^{\text{NLSM}}\left[
-  \scalebox{0.75}{\NLSMBasisDoubleBox} \right]
-\text{ and }
-N^{\text{NLSM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]\in
-\left\{\begin{array}{cccc}
-    k_{13},& k_{23},& k_{15},& k_{16}, \\
-    k_{25},& k_{26},& k_{35},& k_{36}, \\
-    k_{55},& k_{56},& k_{66}
-  \end{array}
-  \right\},
+\{ k_{13}, k_{23}, k_{15}, k_{16}, k_{25}, k_{26}, k_{35}, k_{36}, k_{55}, k_{56}, k_{66} \},
 \end{equation}
@@
 total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is
-  not suited to solving large sets of equations with sixteen thousand
-  parameters, so a different method is desirable.  One possibility is
-  to use a sprase solver, as often employed for integral reduction.
-  However, these solvers typically assume that the matrix has a very
-  low density which is not the case for equations coming from NLSM
-  which typically have a density of a few percent.  While the
-  equations in YM naturally separate into different ``helicity''
-  sectors (or $e_i \cdot e_j$ and $e_i \cdot k_j$ sectors in $D$
-  dimensions), there is no such separation of sectors in a scalar
-  theory where any product of momenta can interfere with any other.
-  The NLSM constraint equations were solved using a custom solver,
-  \texttt{FiniteFieldSolve}, designed to solve large linear systems of
-  arbitrary density.  \texttt{FiniteFieldSolve} will be released
-  publicly shortly.\ace{I want to rephrase this slightly, but need to
-    think about it a bit more}} Imposing the boundary Jacobi relations
-eliminates all but 4,473 of the original free parameters.  Further
-imposing graph symmetries reduces the number of free parameters to
-1,243.
+  not suited to equations with sixteen thousand parameters so a
+  different method is desirable.  One possibility is to use a solver
+  designed for integral reduction.  However, these solvers typically
+  assume that the matrix has a very low density which is not the case
+  for equations coming from NLSM which typically have a density of a
+  few percent.  While the equations in YM naturally separate into
+  different ``helicity'' sectors (or $e_i \cdot e_j$ and
+  $e_i \cdot k_j$ sectors in $D$ dimensions), there is no such
+  separation of sectors in a scalar theory where any product of
+  momenta can interfere with any other.  The NLSM constraint equations
+  were solved using a custom solver, \texttt{FiniteFieldSolve},
+  designed to solve large linear systems of arbitrary density.
+  \texttt{FiniteFieldSolve} will be released publicly shortly.\ace{I
+    want to rephrase this slightly, but need to think about it a bit
+    more}} Imposing the boundary Jacobi relations eliminates all but
+4,473 of the original free parameters.  Further imposing graph
+symmetries reduces the number of free parameters to 1,243.
+
+\begin{figure}
+  \begin{center}
+	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
+  \end{center}
+  \caption{The two physical cut topologies shared by NLSM, sGal, BI, and DBIVA}
+  \label{fig:emu}
+\end{figure}
 
@@
 
-\begin{figure}[h]
-  \begin{center}
-	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
-  \end{center}
-  \caption{The two physical cut topologies shared by NLSM, sGal, BI, and DBIVA}
-  \label{fig:emu}
-\end{figure}
-
 % It is possible to automatically enforce (or ``bake in'') the double
@@
 possible to enforce the no triangle hypothesis, manifest loop power
-counting, and, for four-point and up to at least six loops, strip off
-a factor of $st \atree$ from the integrand \cite{FiveLoopN4,
+counting, and, for four-point and up to at least six loops, strip off a
+factor of $st \atree$ from the integrand \cite{FiveLoopN4,
   Bern:2012uf, Bern:2010fy, SuperSum, Carrasco:2021otn,
@@
 color-kinematics duality to all loop orders, namely,
-Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp,
-  Cheung:2022mix}. ZM theory is governed by the Lagrangian
+Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}. ZM theory is governed by the Lagrangian
 \begin{equation}
@@
 \ace{Lets tighten up this paragraph a bit, especially the second half}
-It is tempting to try to match the pion four-point two-loop integrand
-to ZM on the cuts, but given that the cuts only probe the on-shell
-four-point amplitude, which is either subtle or vanishes for ZM, it is
-better to compare the off-shell numerators directly.  As local
-functions, the numerators never suffer from any of the subtleties of
-on-shell 2D kinematics.  Since the physical cuts are difficult to
-compare, ZM theory is being used here simply as a tool to eliminate
-generalized gauge freedom; ZM theory has the right power counting and
-kinematic structure in 2D to compare against.  Since ZM theory is only
-being used for the kinematical structure of its numerators, it is
-natural to introduce a proportionality constant $z$ between the NLSM
-and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
+It is tempting to try to match the pion four-point two-loop integrand to ZM
+on the cuts, but given that the cuts only probe the on-shell four-point
+amplitude, which is either subtle or vanishes for ZM, it is better to
+compare the off-shell numerators directly.  As local functions, the
+numerators never suffer from any of the subtleties of on-shell 2D
+kinematics.  Since the physical cuts are difficult to compare, ZM
+theory is being used here simply as a tool to eliminate generalized
+gauge freedom; ZM theory has the right power counting and kinematic
+structure in 2D to compare against.  Since ZM theory is only being
+used for the kinematical structure of its numerators, it is natural to
+introduce a proportionality constant $z$ between the NLSM and ZM
+numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
 parameter $z$, which would normally be fixed on cuts, effectively
@@
   different from NLSM even though they are dual classically in two
-  dimensions \cite{Nappi:1979ig}.  When the four-point
-  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
-  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
-  $z$ is fixed to $216/565$, which is clearly unrelated to the
-  difference in coupling constants.}  This introduces an extra degree of
+  dimensions \cite{Nappi:1979ig}.}  This introduces an extra degree of
 freedom into the problem.  Mechanically, the pion numerator is matched
@@
 freedom parameters reduces to 58.  The pion numerator appearing in the
-ancillary files makes exactly this choice.
+ancillary files makes exactly this choice.\footnote{When the four-point
+  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
+  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
+  $z$ is fixed to $216/565$, which is clearly unrelated to the
+  difference in coupling constants.} \ace{Is this actually where we
+  want this particular footnote to appear?}
 
@@
 
+\jm{Rather than quoting the number of parameters in the BDN ansatz, I
+  would prefer to just focus on what we did since it's more general.
+  I don't want it to sound like we just patched a minor hole in their
+  argument when I think you've done something much cooler by
+  pinpointing the failure to the bowtie graph. I know you put time and
+  effort into analyzing the BDN ansatz but I'm worried that the more
+  we talk about it, the more it will overshadow the real success
+  here.}
+
 Given the close ties between pion and gluon scattering for trees and
@@
 follow the same general procedure as in \cref{sec:pions}, again
-identifying the double-box and penta-triangle as the
+identifying the double-box (2box) and penta-triangle (pt) as the
 Jacobi basis graphs and building a the most general ansatz for each of
@@
 \begin{equation}
-  \mathcal{N}^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
-  \text{ and }
-  \mathcal{N}^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
-  \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
+  \mathcal{N}^{\text{YM}}\left[\NLSMBasisDoubleBox \right]\text{ and }\mathcal{N}^{\text{YM}}\left[\NLSMBasisPentaTriangle \right]\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
   \label{eq:ym-basis}

### 2023-09-21 notes/2loopNLSM.tex
fixed n vs N vs calN

@@
 \begin{equation}
-  \mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma n_\Gamma}{d_\Gamma} .
+  \mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{C_\Gamma N_\Gamma}{d_\Gamma} .
   \label{eq:gen-amp}
@@
 The color factor
-$c_\Gamma$ is the string of structure constants $f^{abc}$ associated
+$C_\Gamma$ is the string of structure constants $f^{abc}$ associated
 with the graph $\Gamma$,\footnote{This paper is focused on theories
@@
 is the product of propagators associated with the graph $\Gamma$, and
-the numerator $n_\Gamma$ is all of the remaining kinematic factors
+the numerator $N_\Gamma$ is all of the remaining kinematic factors
 including dot products of momenta and polarization vectors.
 
-In this form the color factors $c_\Gamma$ are not independent and are related to
+In this form the color factors $C_\Gamma$ are not independent and are related to
 one another via a set of Jacobi identities that look schematically
@@
 \begin{equation}
-c_i+c_j+c_k=0,
+C_i+C_j+C_k=0,
 \end{equation}
@@
 are presented in detail in \cref{sec:bootstrap}. The duality between color and kinematics is the statement that that there exists a way to rearrange factors between
-the various kinematic numerators $n_\Gamma$ such that the numerators
+the various kinematic numerators $N_\Gamma$ such that the numerators
 obey the same Jacobi identities as the color factors
 \begin{equation}
-n_i +n_j +n_k=0.
+N_i +N_j +N_k=0.
 \end{equation}
@@
 \begin{align}
-&n_s = s(t-u)\\
-&n_t = t(u-s)\\
-&n_u = u(s-t)
+&N_s = s(t-u)\\
+&N_t = t(u-s)\\
+&N_u = u(s-t)
 \end{align}
@@
 
-Once color-dual numerators $n_\Gamma$ have been found, they can be
-used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a
+Once color-dual numerators $N_\Gamma$ have been found, they can be
+used to replace the color factors ($C_\Gamma \to N_\Gamma$) in a
 \emph{different} amplitude to produce the corresponding amplitude in
@@
 \tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
-\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma
-  \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)}
+\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{C_\Gamma
+  \tilde{N}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(C_\Gamma \to N_\Gamma)}
 ~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
-\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma
-  \tilde{n}_\Gamma}{d_\Gamma}.
+\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{N_\Gamma
+  \tilde{N}_\Gamma}{d_\Gamma}.
 \end{equation}

### 2023-09-21 notes/2loopNLSM.tex
Solver footnote reworked.

--- 2023-09-21 notes/2loopNLSM.tex
@@
   However, these solvers typically assume that the matrix has a very
-  low density which is not the case for equations coming from NLSM
-  which typically have a density of a few percent.  While the
-  equations in YM naturally separate into different ``helicity''
-  sectors (or $e_i \cdot e_j$ and $e_i \cdot k_j$ sectors in $D$
-  dimensions), there is no such separation of sectors in a scalar
-  theory where any product of momenta can interfere with any other.
-  The NLSM constraint equations were solved using a custom solver,
-  \texttt{FiniteFieldSolve}, designed to solve large linear systems of
-  arbitrary density.  \texttt{FiniteFieldSolve} will be released
-  publicly shortly.\ace{I want to rephrase this slightly, but need to
-    think about it a bit more}} Imposing the boundary Jacobi relations
+  low density.  While the equations in YM naturally separate into
+  different ``helicity'' sectors (or $e_i \cdot e_j$ and
+  $e_i \cdot k_j$ sectors in $D$ dimensions) which limits the
+  cross-talk between equations and thus the effective density, there
+  is no such separation of sectors in a scalar theory.  Thus the NLSM
+  constraint equations were solved using a custom solver, working name
+  \texttt{FiniteFieldSolve}, designed to exactly solve large linear
+  systems of arbitrary density.  \texttt{FiniteFieldSolve} will be
+  released publicly shortly.} Imposing the boundary Jacobi relations
 eliminates all but 4,473 of the original free parameters.  Further

### 2023-09-21 notes/2loopNLSM.tex
fixed all n vs N vs mathcalN and YZ + J

--- 2023-09-21 notes/2loopNLSM.tex
@@
 = \sum_{g \text{ compat } \gamma}
-\frac{n[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
+\frac{N[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
  \, ,
@@
     (\textcolor{ucp-color}{\ell_7})^2}
-  \ n\left[
+  \ N\left[
     \IUCContrib{1}{4}{3}{2}
@@
     (\textcolor{ucp-color}{\ell_7'})^2}
-  \ n\left[
+  \ N\left[
     \IUCContrib{1}{3}{4}{2}
@@
 \textcolor{ucp-color}{uncut propagators}.  From now on we will leave
-the cut $\delta(\ell^2)$s implicit.  \jm{Again, I love the colors!
-  Would it be possible to add $\ell$ labels to the RHS of
-  \cref{eq:example-cut-sum} to show what $\ell_5$, $\ell_6$... are?}
-\ace{It is doable, will work on it once our text is a bit more happy}
+the cut $\delta(\ell^2)$s implicit.
+
+%% \jm{Again, I love the colors!
+%%  Would it be possible to add $\ell$ labels to the RHS of
+%5  \cref{eq:example-cut-sum} to show what $\ell_5$, $\ell_6$... are?}
+%%\ace{It is doable, will work on it once our text is a bit more happy}
 
@@
       \frac{1}{\textcolor{ucp-color}{s_{12}}}
-      n \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
+      N \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
       \right]
@@
       \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
-      n \left[
+      N \left[
       \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
@@
       \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
-      n\left[
+      N\left[
       \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
@@
 \begin{equation}
-\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
+N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
 \end{equation}
@@
 \begin{equation}
-\partial_D \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 \varepsilon_1)(l_2 \varepsilon_2)\cdots (l_n \varepsilon_n)
+\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 \varepsilon_1)(l_2 \varepsilon_2)\cdots (l_n \varepsilon_n)
 \end{equation}
@@
 \begin{equation}
- \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
+N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
 \end{equation}
@@
 For a scalar theory like NLSM the numerator only depends on dot
-products of momenta.  The basis of momentum invariants for both of
+products of momenta.  The basis of momentum invariants for the numerators assigned to both of
 these graphs can be taken to be
@@
 Unitarity cuts besides those shown in \cref{fig:emu} are either
-pathological or vanish because they involve a 3pt point on-shell
-amplitude (which vanishes on general grounds for scalar theories
-\ace{This feels like overstating things.  For instance, what about
-  $\phi^3$ or BAS?}).  In order to manifest the $\mathbb{Z}_2$
+pathological or vanish because they involve a three-point point on-shell
+amplitude. In order to manifest the $\mathbb{Z}_2$
 symmetry of NLSM at the integrand level, we require that all
-non-pathological cuts containing a 3pt vertex (such as the maximal
-cut) vanishs.  Imposing all relevant cuts leaves 765 free parameters
+non-pathological cuts containing a three-point vertex (such as the maximal
+cut) vanishes.  Imposing all relevant cuts leaves 765 free parameters
 representing the generalized gauge freedom in the answer.
@@
 % inverse propagator since those terms will vanish on those max cuts,
-% just as the product of 3pt scalar amplitudes will.  However, for the
+% just as the product of three-point scalar amplitudes will.  However, for the
 % sake of simplicity we do not take this route.
@@
 numerator to 2D.  The loop momenta are restricted to 2D but left
-off-shell.  After performing the 2D matching, there are only 365
-parameters of generalized gauge freedom.
+off-shell.  After performing the 2D matching to the following ZM basis numerators:
+\be
+\ZMBasisDoubleBox =\left[\begin{split}
+  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
+\\
+\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
+\end{split}\right]
+\ee
+\be
+\ZMBasisPentaTriangle =\left[\begin{split}
+  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
+\\
+\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
+\end{split}\right]
+\ee
+there are only 365 parameters of generalized gauge freedom. An overview of ZM theory and its color-dual construction can be found at the end of \cref{sec:CKLagrangians}.
 
@@
 \begin{equation}
-  \mathcal{N}^{\text{YM}}\left[\NLSMBasisDoubleBox \right]\text{ and }\mathcal{N}^{\text{YM}}\left[\NLSMBasisPentaTriangle \right]\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
+N^{\text{YM}}\left[\NLSMBasisDoubleBox \right]\text{ and }N^{\text{YM}}\left[\NLSMBasisPentaTriangle \right]\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
   \label{eq:ym-basis}
@@
   \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
-  n \left[
+  N \left[
     \KTDBContrib{1}{2}{3}{4}
@@
   \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
-  n\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
+  N\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
 \end{equation}
@@
 \begin{equation}
-\mathcal{N}_{(12|34)}^{\text{YM}} = \frac{t_8F^4}{3} \frac{s_{13}-s_{12}}{s_{23}{s_{13}}}
+N_{(12|34)}^{\text{YM}} = \frac{t_8F^4}{3} \frac{s_{13}-s_{12}}{s_{23}{s_{13}}}
 \end{equation}
@@
 \begin{equation}
-\mathcal{N}_{(12|34)}^{\text{YM}} + \mathcal{N}_{(13|42)}^{\text{YM}} +\mathcal{N}_{(14|23)}^{\text{YM}} = 0
+N_{(12|34)}^{\text{YM}} + N_{(13|42)}^{\text{YM}} +N_{(14|23)}^{\text{YM}} = 0
 \end{equation}
@@
 \begin{align}
-\text{Res}\left[\frac{ \mathcal{N}_{s}^{\text{YM}} }{s}\right]^{s=0}&= \frac{2}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
-\\
-\text{Res}\left[\frac{\mathcal{N}_{t}^{\text{YM}} }{t}\right]^{s=0}&= -\frac{1}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
-\\
-\text{Res}\left[\frac{\mathcal{N}_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\text{Res}\left[\frac{ N_{s}^{\text{YM}} }{s}\right]^{s=0}&= \frac{2}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\\
+\text{Res}\left[\frac{N_{t}^{\text{YM}} }{t}\right]^{s=0}&= -\frac{1}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\\
+\text{Res}\left[\frac{N_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
 \end{align}
@@
 \begin{equation}
-\mathcal{N}^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
+N^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
 \end{equation}
 where $\mathcal{O}_i$ are the basis tensors of
-\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}_i$ is a
+\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ is a
 rational function of scalar products.

### 2023-09-21 notes/2loopNLSM.tex

--- 2023-09-21 notes/2loopNLSM.tex
@@
 \label{2loopBoot}
+\ace{Lets bulk this section intro up a bit} \nhp{@Alex will bulk this up}
 
@@
 \begin{equation}
-  \mathcal{N}^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
+  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
   \text{ and }
-  \mathcal{N}^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
+  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
   \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}

### 2023-09-21 notes/2loopNLSM.tex
small edit
massaging CK intro

@@
 
-\title{\center  \fontsize{18.8}{20} \selectfont  Towards Globally Color-Dual All-Loop Integrands}
+\title{\center  \fontsize{18.8}{20} \selectfont  Towards Globally Color-Dual Multi-Loop Integrands}
 
@@
 local (polynomial) functions of the graph kinematics with the correct
-power counting and external states.  Insisting on a local numerator is
+power counting and external states. Locality is also physically motivated since Feynman
+rules by construction produce polynomial numerators. Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of
+kinematics. However, insisting on a local numerator is
 partly a matter of convenience as the ansatz for a rational function
 would quickly grow out of control without a guiding principle for what
-terms to include.  Locality is also physically motivated since Feynman
-rules typically produce polynomial numerators.  While these
+terms to include.  While these
 assumptions are well motivated from a physical and complexity
@@
 is a viable alternative when the condition proves too stringent for an
-ansatz.  In particular, the most natural way to guarantee locality is
-to require the off-shell numerators to be polynomial functions of
-kinematics.  However, simply requiring on-shell locality may suffice.
+ansatz. As such, requiring instead that locality is only realized \textit{on-shell} may suffice.
 This alternative will be discussed in \cref{nonLocalScattering}.
+
+\paragraph{Color-kinematics duality}
 
@@
 them are simply not imposed or solved.  See Refs.~\cite{Bern:2012uf,
-  Edison:2022jln} for discussions of BELs in the context of
+  Edison:2022jln} and \cref{BELref} for discussions of BELs in the context of
 color-kinematics duality.
-\paragraph{Color-kinematics duality}
+
 \begin{figure}
@@
 }
-\caption{The 14 non-pathological four-point two-loop cubic diagrams,
-  including all dangling tree diagrams.} \label{fig:MaxCuts}
+\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
   \end{figure}
-\ace{Awkward phrasing/transition.} \nhp{will message language} What has just been described is
+What we have just been described is
 sometimes referred to as ``global'' color-kinematics duality because
@@
 \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
-heart of $YZ$-theory \cite{Cheung:2016prv}, J-theory
+heart of $YZ$-theory \cite{Cheung:2016prv}, $J$-theory
 \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
@@
 \ee
-there are only 365 parameters of generalized gauge freedom. An overview of ZM theory and its color-dual construction can be found at the end of \cref{sec:CKLagrangians}.
-
+there are only 365 parameters of generalized gauge freedom.
+An overview of ZM theory and its color-dual construction can be found at the end of \cref{sec:CKLagrangians}.
 The loop momentum structure of ZM theory provides one final hint for
@@
 Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.
-Thus, $Y\!Z$ theory gives us the following one-loop $n$-gon numerator:
-\begin{equation}
-N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+2\, (F^1F^2\cdots F^n)
+Thus, $YZ$ theory gives us the following one-loop $n$-gon numerator:
+\begin{equation}
+N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+ (F^1F^2\cdots F^n)
 \end{equation}

### 2023-09-21 notes/2loopNLSM.tex
Added labels to cut example.

@@
   \ N\left[
-    \IUCContrib{1}{4}{3}{2}
+    \IUCContrib{1}{4}{3}{2}{\ell_5}{\ell_6}{\ell_7}
                               \right] \notag \\
@@
   \ N\left[
-    \IUCContrib{1}{3}{4}{2}
+    \IUCContrib{1}{3}{4}{2}{\ell_5}{\ell_6}{\ell_7'}
     \right] + 25\text{ others.}
@@
 permitting a $D$-dimensional construction of the one-loop
-integrand. Below we provide a four-point example: \nhp{change ordering on legs}
+integrand. Below we provide a four-point example:
 \begin{equation}
@@
 \label{2loopBoot}
-\ace{Lets bulk this section intro up a bit} \nhp{@Alex will bulk this up}
-
 As we have just seen, it is possible to coerce tree numerators into

### 2023-09-21 notes/2loopNLSM.tex
CK fix and box ordering
small edit

@@
   \end{figure}
-What we have just been described is
+What we have just described is
 sometimes referred to as ``global'' color-kinematics duality because
@@
   \ N\left[
-    \IUCContrib{1}{4}{3}{2}{\ell_5}{\ell_6}{\ell_7}
+    \IUCContrib{1}{4}{3}{2}
                               \right] \notag \\
@@
   \ N\left[
-    \IUCContrib{1}{3}{4}{2}{\ell_5}{\ell_6}{\ell_7'}
+    \IUCContrib{1}{3}{4}{2}
     \right] + 25\text{ others.}

### 2023-09-21 notes/2loopNLSM.tex
eBoxed the Gordan Ramsey chef kiss

@@
 them are simply not imposed or solved.  See Refs.~\cite{Bern:2012uf,
-  Edison:2022jln} and \cref{BELref} for discussions of BELs in the context of
+  Edison:2022jln} and \cref{BELreg} for discussions of BELs in the context of
 color-kinematics duality.
@@
 \cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
+\begin{eBox}
 \begin{equation}
@@
 \end{equation}
+\end{eBox}
 Thus we have identified the minimal failure state for a
@@
 \begin{equation}
-N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+ (F^1F^2\cdots F^n)
+N^{n\text{-gon},YZ}_{(12...n)} = \langle T^{1}T^{2}\cdots T^{n}\rangle+ \rangle F^1F^2\cdots F^n\rangle
 \end{equation}

### 2023-09-21 notes/2loopNLSM.tex
Tried to fix all l -> \ell in main text.

--- 2023-09-21 notes/2loopNLSM.tex
@@
 yield precisely the 4D SDYM vertex, up to an unphysical phase:
-  \be
+  \begin{equation}
   \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
- \ee
+ \end{equation}
 where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}.
@@
 \begin{equation}
-\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
-\end{equation}
-where $l_i = l+k_1+k_2+\cdots+ k_i$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+l_i)}\varepsilon^\nu_{(-l_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
+\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
+\end{equation}
+where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
 In general, the $n$-gon diagram would be,
 \begin{equation}
-N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
+N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
 \end{equation}
 Due to the state-sum of internal loop factors,
-$\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}\sim D$, the integrand above
+$\sum {\varepsilon_{(+\ell)}\varepsilon_{(-\ell)}}\sim D$, the integrand above
 depends explicitly on the spacetime dimension, $D$. By taking a
@@
 \begin{equation}
-\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 \varepsilon_1)(l_2 \varepsilon_2)\cdots (l_n \varepsilon_n)
+\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
 \end{equation}
@@
 \end{equation}
-Where we have define the antisymmetric kinematic variable, $[ij] = l_i^2 - l_j^2$, since when plugging on longitudinal modes, the $n$-gon can be re-expressed completely in terms of inverse propagators, $2(k_i \cdot l_i) = l_{i}^2-l^2_{i-1}$.
-We have verified through 10-point one-loop that this $n$-gon expression is a valid color-dual representation for NLSM.
+Where we have define the antisymmetric kinematic variable,
+$[ij] = \ell_i^2 - \ell_j^2$, since when plugging on longitudinal
+modes, the $n$-gon can be re-expressed completely in terms of inverse
+propagators, $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$. We have
+verified through 10-point one-loop that this $n$-gon expression is a
+valid color-dual representation for NLSM.
 

### 2023-09-21 notes/2loopNLSM.tex
push small change

--- 2023-09-21 notes/2loopNLSM.tex
@@
 \textcolor{ucp-color}{uncut propagators}.  From now on we will leave
-the cut $\delta(\ell^2)$s implicit.
+the cut $\delta(\ell^2)$ factors implicit.
 
@@
 
-\ace{Lets tighten up this paragraph a bit, especially the second half}
+%\ace{Lets tighten up this paragraph a bit, especially the second half}
+
 It is tempting to try to match the pion four-point two-loop integrand
@@
 be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in
-  order to obtain color-dual two-loop integrands.}  \ace{I want to
-  rephrase especially the last sentence.}
-
-\jm{I am intentionally shying away from really firm statements like
-  `you must abandon locality' because there are always loopholes and
-  we made a lot of other assumptions in fixing our \ansatze{}.}
+  order to obtain color-dual two-loop integrands.}
 
@@
 theories. After all, operators that produce rational functions of
-kinematics must be non-local.\ace{A few more connecting sentences
-  here.  This is a bit of a big jump without some amount of summary}
-Thus, in order to identify valid color-dual representation of
+kinematics must be non-local. Thus, in order to identify valid color-dual representation of
 Yang-Mills beyond tree-level, we must relax the constraint of

### 2023-09-21 notes/2loopNLSM.tex
l -> \ell in appendix C

--- 2023-09-21 notes/2loopNLSM.tex
@@
 \end{equation}
-where we used white dots to indicate interaction vertices of weight\footnote{We choose the convention that the abelianized gauge fields carry weight $\mathcal{W}[\bar{A}] = -1$, and non-abelian vectors are $\mathcal{W}[\bar{A}] = +1$.} $\mathcal{W}[\bar{A}\bar{A} A] = -1$, rather than the isolated semi-YM vertex which always carries weight $\mathcal{W}[\bar{A}A A] = +1$.
-This immediately runs into the difficulty of introducing the
+where we used white dots to indicate interaction vertices of
+weight\footnote{We choose the convention that the abelianized gauge
+  fields carry weight $\mathcal{W}[\bar{A}] = -1$, and non-abelian
+  vectors are $\mathcal{W}[\bar{A}] = +1$.}
+$\mathcal{W}[\bar{A}\bar{A} A] = -1$, rather than the isolated semi-YM
+vertex which always carries weight $\mathcal{W}[\bar{A}A A] =
++1$. This immediately runs into the difficulty of introducing the
 four-point contact needed for color-kinematics to be satisfied on all
-internal edges. By a simple weight counting argument, one can see that including this wrong sign interactions is unavoidable at two-loop and higher.
+internal edges. By a simple weight counting argument, one can see that
+including this wrong sign interactions is unavoidable at two-loop and
+higher.
 
@@
 
-Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. The component definition of our spinor bracket that are consistent with the conventions above,
+Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which
+we quote now. The component definition of our spinor bracket that are
+consistent with the conventions above,
 \begin{align}
@@
 \end{align}
-where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$, one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:
+where the $a_i$ are component values of the four-vector,
+$k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$,
+one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:
 \begin{equation}
@@
 \end{equation}
-Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
+Four-dimensional polarization dot products with fixed helicity states
+can be mapped as follows:
 \begin{equation}\label{eq:4DPols}
@@
 \end{equation}
-Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets.
-In terms of light-cone coordinates that we employed above in \cref{sec:CKLagrangians}, the angles and squares can be rewritten as follows:
+Note that given the above definition, the spinor helicity variables
+carry the same mass dimension for both the angle and square
+brackets. In terms of light-cone coordinates that we employed above in
+\cref{sec:CKLagrangians}, the angles and squares can be rewritten as
+follows:
 \begin{align}
@@
 \end{align}
-The conventions we use in the text where the holomorphic spinor, $X(p,k)$, carries extra mass dimension essentially amounts to shifting the bracket by the following overall factor:
+The conventions we use in the text where the holomorphic spinor,
+$X(p,k)$, carries extra mass dimension essentially amounts to shifting
+the bracket by the following overall factor:
 \begin{align}
@@
 \section{Regulating BEL integrals}\label{BELreg}
-At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles.
-Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.
-Thus, $YZ$ theory gives us the following one-loop $n$-gon numerator:
+At one-loop, weight counting tells us that the $n$-gon master
+numerator must have $n$ on-shell $Z$-particles. Unitarity requires
+that there are three distinct contributions from $Y\!Z$ theory -- the
+first from an off-shell $Y$-loop particle and then two more from
+different orientations of a $\bar{Z}Z$-loop.  Thus, $YZ$ theory gives
+us the following one-loop $n$-gon numerator:
 \begin{equation}
@@
 \end{equation}
-where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops.
-Plugging in the Feynman rule of \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
-\begin{equation}
-N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
+where $(\,\cdots)$ indicates an internal contraction over the $YY$ and
+$\bar{Z}Z$ loops. Plugging in the Feynman rule of
+\cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily
+obtain expressions in terms of the internal loop factors $\ell_i$ and the
+external momenta $k_i$ (we define the $\ell_i$ loop momentum as that
+flowing into $k_i$ and out of $k_{i-1}$):
+\begin{equation}
+N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n)
 \end{equation}
@@
 \begin{equation}
- (F^1F^2\cdots F^n) = D (l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
-\end{equation}
-The dimension dependent factor essentially counts that number of internal vector states.
-While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM.
-However, the scalar contribution, that comes dressed with an overall factor $D$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts.
-In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality.
-We leave this as a direction of future work.
+ (F^1F^2\cdots F^n) = D (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n) + \mathcal{O}(D^0)
+\end{equation}
+The dimension dependent factor essentially counts that number of
+internal vector states. While this $n$-gon is manifestly color-dual,
+it does not produce the right cuts for NLSM. However, the scalar
+contribution, that comes dressed with an overall factor $D$
+\textit{does} manifest the duality globally, and satisfies all the
+desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory
+compute one-loop color-dual numerators consistent with NLSM cuts, we
+must add some additional states to cancel off he spurious poles, while
+preserving color-kinematics duality. We leave this as a direction of
+future work.
 
@@
 \begin{equation}
-T^{a}_{LR} = k_a(l_L-l_{R}) = (l_L+l_{R}) (l_L-l_{R})  = l_L^2-l_{R}^2 
+T^{a}_{LR} = k_a(\ell_L-\ell_{R}) = (\ell_L+\ell_{R}) (\ell_L-\ell_{R})  = \ell_L^2-\ell_{R}^2 
 \end{equation}
@@
 \begin{equation}
-N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
-\end{equation}
-where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
-\begin{equation}
-N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
+N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,\ell)}-N^{\text{NLSM}}_{(1243,\ell)}-N^{\text{NLSM}}_{(1342,\ell)}+N^{\text{NLSM}}_{(1432,\ell)}
+\end{equation}
+where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $\ell_i$, we obtain the following expression for the BEL
+\begin{equation}
+N^{\text{BEL}}_{1|2,34} = s_{12} (\ell+k_1)^2 \ell^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
 \end{equation}
@@
 \begin{equation}
-\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
+\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D \ell}{i\pi^{D/2}} \frac{\ell^\mu }{\ell^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
 \end{equation}

### 2023-09-21 notes/2loopNLSM.tex
small edit again -- I'll actually work on conclusion now

--- 2023-09-21 notes/2loopNLSM.tex
@@
 leg (BEL) graphs.
-
+\begin{figure}
+\centering
+{\MCutC, \MCutD, \sumoCut, \MCutJ,  
+ \\
+  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
+\\
+\MCutI,  \MCutE, \MCutK, 
+\\
+ \MCutL, \MCutG,  \MCutH
+}
+\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
+  \end{figure}
 With the integrand expressed in terms of cubic graphs, it is possible
@@
 
-\begin{figure}
-\centering
-{\MCutC, \MCutD, \sumoCut, \MCutJ,  
- \\
-  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
-\\
-\MCutI,  \MCutE, \MCutK, 
-\\
- \MCutL, \MCutG,  \MCutH
-}
-\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
-  \end{figure}
 What we have just described is
@@
   \label{eq:kt-color-ord}
-   \NMCutC =
+\!\!\! \!\!\! \!  \NMCutC =
   \begin{cases}
@@
 \end{equation}
-which serve as a complete basis for the full cut.
-
-Even though unitarity methods aim to generate loop-level data from
+which serve as a complete basis for the full cut. Even though unitarity methods aim to generate loop-level data from
 well-defined on-shell information, the procedure can encounter

### 2023-09-21 notes/2loopNLSM.tex
l -> \ell in appendix A

--- 2023-09-21 notes/2loopNLSM.tex
@@
 Schouten identity. Below we provide the double-box and penta-triangle expressions to which we matched our NLSM integrands to in the text:
-\be
+\begin{equation}
 \ZMBasisDoubleBox =\left[\begin{split}
-  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
-\\
-\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
+  \langle (\ell_1+k_4) \ell_1 \rangle\langle \ell_1\ell_2 \rangle\langle \ell_2 (\ell_2+k_1) \rangle  \langle (\ell_2+k_1)(\ell_2+k_1+k_2) \rangle 
+\\
+\langle (\ell_1+k_3+k_4)(\ell_2+k_1+k_2) \rangle\langle (\ell_1+k_3+k_4)(\ell_1+k_4) \rangle
 \end{split}\right]
-\ee
-\be
-\ZMBasisPentaTriangle =\left[\begin{split}
-  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
-\\
-\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
-\end{split}\right]
-\ee
-Furthermore, since ZM theory manifests color-kinematics duality without any
-reference to the on-shell condition, a mass term can be added to ZM
-theory without spoiling color-kinematics duality \cite{Cheung:2022mix}. In general, if the
-on-shell conditions are not used, color-kinematics duality is
-unaffected by the details of the propagator structure.
+\end{equation}
+\begin{equation}
+  \ZMBasisPentaTriangle =\left[
+    \begin{split}
+      \langle (\ell_1+k_4) \ell_1 \rangle\langle \ell_1\ell_2 \rangle\langle \ell_2 (\ell_2+k_1) \rangle  \langle (\ell_2+k_1)(\ell_1-k_1) \rangle 
+      \\
+      \langle (\ell_1+k_3+k_4)(\ell_1-k_1) \rangle\langle (\ell_1+k_3+k_4)(\ell_1+k_4) \rangle
+    \end{split}
+  \right]
+\end{equation}
+Furthermore, since ZM theory manifests color-kinematics duality
+without any reference to the on-shell condition, a mass term can be
+added to ZM theory without spoiling color-kinematics duality
+\cite{Cheung:2022mix}. In general, if the on-shell conditions are not
+used, color-kinematics duality is unaffected by the details of the
+propagator structure.
 

### 2023-09-21 notes/2loopNLSM.tex
small push
James edits.

--- 2023-09-21 notes/2loopNLSM.tex
@@
 
-\title{\center  \fontsize{18.8}{20} \selectfont  Towards Globally Color-Dual Multi-Loop Integrands}
+\title{\center  \fontsize{18.8}{20} \selectfont  Towards Globally Color-Dual All-Loop Integrands}
 
@@
 local (polynomial) functions of the graph kinematics with the correct
-power counting and external states. Locality is also physically motivated since Feynman
-rules by construction produce polynomial numerators. Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of
-kinematics. However, insisting on a local numerator is
+power counting and external states.  Insisting on a local numerator is
 partly a matter of convenience as the ansatz for a rational function
 would quickly grow out of control without a guiding principle for what
-terms to include.  While these
+terms to include.  Locality is also physically motivated since Feynman
+rules typically produce polynomial numerators.  While these
 assumptions are well motivated from a physical and complexity
@@
 is a viable alternative when the condition proves too stringent for an
-ansatz. As such, requiring instead that locality is only realized \textit{on-shell} may suffice.
+ansatz.  In particular, the most natural way to guarantee locality is
+to require the off-shell numerators to be polynomial functions of
+kinematics.  However, simply requiring on-shell locality may suffice.
 This alternative will be discussed in \cref{nonLocalScattering}.
-
-\paragraph{Color-kinematics duality}
 
@@
 them are simply not imposed or solved.  See Refs.~\cite{Bern:2012uf,
-  Edison:2022jln} and \cref{BELreg} for discussions of BELs in the context of
+  Edison:2022jln} for discussions of BELs in the context of
 color-kinematics duality.
-
+\paragraph{Color-kinematics duality}
 \begin{figure}
@@
 }
-\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
+\caption{The 14 non-pathological four-point two-loop cubic diagrams,
+  including all dangling tree diagrams.} \label{fig:MaxCuts}
   \end{figure}
-What we have just described is
+\ace{Awkward phrasing/transition.} \nhp{will message language} What has just been described is
 sometimes referred to as ``global'' color-kinematics duality because
@@
 = \sum_{g \text{ compat } \gamma}
-\frac{N[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
+\frac{n[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
  \, ,
@@
     (\textcolor{ucp-color}{\ell_7})^2}
-  \ N\left[
-    \IUCContrib{1}{4}{3}{2}{\ell_5}{\ell_6}{\ell_7}
+  \ n\left[
+    \IUCContrib{1}{4}{3}{2}
                               \right] \notag \\
@@
     (\textcolor{ucp-color}{\ell_7'})^2}
-  \ N\left[
-    \IUCContrib{1}{3}{4}{2}{\ell_5}{\ell_6}{\ell_7'}
+  \ n\left[
+    \IUCContrib{1}{3}{4}{2}
     \right] + 25\text{ others.}
@@
 \textcolor{ucp-color}{uncut propagators}.  From now on we will leave
-the cut $\delta(\ell^2)$s implicit.
-
-%% \jm{Again, I love the colors!
-%%  Would it be possible to add $\ell$ labels to the RHS of
-%5  \cref{eq:example-cut-sum} to show what $\ell_5$, $\ell_6$... are?}
-%%\ace{It is doable, will work on it once our text is a bit more happy}
+the cut $\delta(\ell^2)$s implicit.  \jm{Again, I love the colors!
+  Would it be possible to add $\ell$ labels to the RHS of
+  \cref{eq:example-cut-sum} to show what $\ell_5$, $\ell_6$... are?}
+\ace{It is doable, will work on it once our text is a bit more happy}
 
@@
       \frac{1}{\textcolor{ucp-color}{s_{12}}}
-      N \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
+      n \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
       \right]
@@
       \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
-      N \left[
+      n \left[
       \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
@@
       \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
-      N\left[
+      n\left[
       \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
@@
 \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
-heart of $YZ$-theory \cite{Cheung:2016prv}, $J$-theory
+heart of $YZ$-theory \cite{Cheung:2016prv}, J-theory
 \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
@@
 Plugging in on-shell all-plus helicity states in light-cone gauge will
-yield precisely the 4D SDYM vertex, up to an unphysical phase:
-  \begin{equation}
+yield precisely the 4D SDYM vertex, up to an unphysical phase \ace{Can
+  we provide an example?} \nhp{yes, provided}:
+  \be
   \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
- \end{equation}
+ \ee
 where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}.
@@
 permitting a $D$-dimensional construction of the one-loop
-integrand. Below we provide a four-point example:
-\begin{equation}
-\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
-\end{equation}
-where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
+integrand. Below we provide a four-point example: \nhp{change ordering on legs}
+\begin{equation}
+\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
+\end{equation}
+where $l_i = l+k_1+k_2+\cdots+ k_i$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+l_i)}\varepsilon^\nu_{(-l_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
 In general, the $n$-gon diagram would be,
 \begin{equation}
-N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
+\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
 \end{equation}
 Due to the state-sum of internal loop factors,
-$\sum {\varepsilon_{(+\ell)}\varepsilon_{(-\ell)}}\sim D$, the integrand above
+$\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}\sim D$, the integrand above
 depends explicitly on the spacetime dimension, $D$. By taking a
@@
 \begin{equation}
-\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
+\partial_D \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 \varepsilon_1)(l_2 \varepsilon_2)\cdots (l_n \varepsilon_n)
 \end{equation}
@@
 \begin{equation}
-N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
-\end{equation}
-Where we have define the antisymmetric kinematic variable,
-$[ij] = \ell_i^2 - \ell_j^2$, since when plugging on longitudinal
-modes, the $n$-gon can be re-expressed completely in terms of inverse
-propagators, $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$. We have
-verified through 10-point one-loop that this $n$-gon expression is a
-valid color-dual representation for NLSM.
+ \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
+\end{equation}
+Where we have define the antisymmetric kinematic variable, $[ij] = l_i^2 - l_j^2$, since when plugging on longitudinal modes, the $n$-gon can be re-expressed completely in terms of inverse propagators, $2(k_i \cdot l_i) = l_{i}^2-l^2_{i-1}$.
+We have verified through 10-point one-loop that this $n$-gon expression is a valid color-dual representation for NLSM.
 
@@
 \end{equation}
-where we used white dots to indicate interaction vertices of
-weight\footnote{We choose the convention that the abelianized gauge
-  fields carry weight $\mathcal{W}[\bar{A}] = -1$, and non-abelian
-  vectors are $\mathcal{W}[\bar{A}] = +1$.}
-$\mathcal{W}[\bar{A}\bar{A} A] = -1$, rather than the isolated semi-YM
-vertex which always carries weight $\mathcal{W}[\bar{A}A A] =
-+1$. This immediately runs into the difficulty of introducing the
+where we used white dots to indicate interaction vertices of weight\footnote{We choose the convention that the abelianized gauge fields carry weight $\mathcal{W}[\bar{A}] = -1$, and non-abelian vectors are $\mathcal{W}[\bar{A}] = +1$.} $\mathcal{W}[\bar{A}\bar{A} A] = -1$, rather than the isolated semi-YM vertex which always carries weight $\mathcal{W}[\bar{A}A A] = +1$.
+This immediately runs into the difficulty of introducing the
 four-point contact needed for color-kinematics to be satisfied on all
-internal edges. By a simple weight counting argument, one can see that
-including this wrong sign interactions is unavoidable at two-loop and
-higher.
-
-Thus, to construct two-loop numerators prescriptively, as we have done
-at one-loop, would require knowledge of the full kinematic algebra for
-Yang-Mills off-shell. Since this is presently unavailable, to approach
-the problem of two-loop construction, we instead employ an ansatz
-based approach.
-
-\section{Two-loop four-point bootstrap}
+internal edges. By a simple weight counting argument, one can see that including this wrong sign interactions is unavoidable at two-loop and higher.
+
+Thus, to construct two-loop numerators prescriptively, as we have done at one-loop, would require knowledge of
+the full kinematic algebra for Yang-Mills off-shell. Since this is
+presently unavailable, to approach the problem of two-loop
+construction, we instead employ an ansatz based approach.
+
+\section{Two-loop bootstrap}
 \label{2loopBoot}
-As we have just seen, it is possible to coerce tree numerators into
-1-loop numerators at any multiplicity for pions (and related
-theories), but that these methods cannot be reapplied to generate
-higher-loop numerators.  For pions in particular, the no-go statement
-is only for \emph{one particular representation of the theory} so does
-not completely preclude the existence of a two-loop color-dual
-representation.  We thus turn to the color-dual bootstrap method
-described in \cref{sec:bootstrap} to construct a color-dual
-representation of two-loop four-point NLSM.  Because of the similarity
-of the problem setup, we will also use the opportunity to revisit the
-construction of a color-dual representation of pure YM, extending the
-search space beyond what was covered in Ref.~\cite{Bern:2015ooa}.
-
-Both representations share the same cubic graph basis, and thus their
-defining Jacobi relations lead to the same numerator basis.
+\ace{Lets bulk this section intro up a bit} \nhp{@Alex will bulk this up}
+
+We now employ the color-dual bootstrap method described in
+\cref{sec:bootstrap}. We will start with an ansatz constructed from
+$D$-dimensionally Lorentz covariant kinematics. To fix remaining
+freedom in the NLSM bootstrap, we will match down to ZM theory in
+$D=2$. This is merely an aesthetic choice, so the final results of
+both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
+
+\subsection{Two-loop NLSM}
+\label{sec:pions}
+
+As we have seen, it is possible to coerce tree numerators into 1-loop
+numerators at any multiplicity for pions.  However, these methods
+cannot be reapplied to generate higher-loop numerators, which begs the
+question ``is it possible to find globally color-dual numerators
+beyond 1-loop?''  We will tackle this question for four-point two-loop
+scattering in NLSM before moving on to the same process in YM.
+
 Ignoring tadpoles and BEL graphs, there are 14 cubic four-point two-loop
@@
 total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is
-  not suited to solving large sets of equations with sixteen thousand
-  parameters, so a different method is desirable.  One possibility is
-  to use a sprase solver, as often employed for integral reduction.
-  However, these solvers typically assume that the matrix has a very
-  low density.  While the equations in YM naturally separate into
+  not suited to equations with sixteen thousand parameters so a
+  different method is desirable.  One possibility is to use a solver
+  designed for integral reduction.  However, these solvers typically
+  assume that the matrix has a very low density which is not the case
+  for equations coming from NLSM which typically have a density of a
+  few percent.  While the equations in YM naturally separate into
   different ``helicity'' sectors (or $e_i \cdot e_j$ and
-  $e_i \cdot k_j$ sectors in $D$ dimensions) which limits the
-  cross-talk between equations and thus the effective density, there
-  is no such separation of sectors in a scalar theory.  Thus the NLSM
-  constraint equations were solved using a custom solver, working name
-  \texttt{FiniteFieldSolve}, designed to exactly solve large linear
-  systems of arbitrary density.  \texttt{FiniteFieldSolve} will be
-  released publicly shortly.} Imposing the boundary Jacobi relations
-eliminates all but 4,473 of the original free parameters.  Further
-imposing graph symmetries reduces the number of free parameters to
-1,243.
-
-The final essential constraint is unitarity.  The two physical cuts
-that need to be enforced, shown in \cref{fig:emu}, only involve
-four-point vertices.  Notably this means that even at two loops,
-unitarity is still only probing the on-shell four-point NLSM amplitude.
-Unitarity cuts besides those shown in \cref{fig:emu} are either
-pathological or vanish because they involve a three-point point on-shell
-amplitude. In order to manifest the $\mathbb{Z}_2$
-symmetry of NLSM at the integrand level, we require that all
-non-pathological cuts containing a three-point vertex (such as the maximal
-cut) vanishes.  Imposing all relevant cuts leaves 765 free parameters
-representing the generalized gauge freedom in the answer.
-
-\begin{figure}[h]
+  $e_i \cdot k_j$ sectors in $D$ dimensions), there is no such
+  separation of sectors in a scalar theory where any product of
+  momenta can interfere with any other.  The NLSM constraint equations
+  were solved using a custom solver, \texttt{FiniteFieldSolve},
+  designed to solve large linear systems of arbitrary density.
+  \texttt{FiniteFieldSolve} will be released publicly shortly.\ace{I
+    want to rephrase this slightly, but need to think about it a bit
+    more}} Imposing the boundary Jacobi relations eliminates all but
+4,473 of the original free parameters.  Further imposing graph
+symmetries reduces the number of free parameters to 1,243.
+
+\begin{figure}
   \begin{center}
@@
 \end{figure}
+
+The final essential constraint is unitarity.  The two physical cuts
+that need to be enforced, shown in \cref{fig:emu}, only involve
+four-point vertices.  Notably this means that even at two loops,
+unitarity is still only probing the on-shell four-point NLSM amplitude.
+Unitarity cuts besides those shown in \cref{fig:emu} are either
+pathological or vanish because they involve a 3pt point on-shell
+amplitude (which vanishes on general grounds for scalar theories
+\ace{This feels like overstating things.  For instance, what about
+  $\phi^3$ or BAS?}).  In order to manifest the $\mathbb{Z}_2$
+symmetry of NLSM at the integrand level, we require that all
+non-pathological cuts containing a 3pt vertex (such as the maximal
+cut) vanishs.  Imposing all relevant cuts leaves 765 free parameters
+representing the generalized gauge freedom in the answer.
 
@@
 At this point color-kinematics duality has been satisfied, so the
-double copy will proceed without issue.  However, the plethora of
+double copy should proceed without issue.  However, the plethora of
 generalized gauge freedom parameters leaves the option for enforcing
@@
 color-kinematics duality to all loop orders, namely,
-Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp,
-  Cheung:2022mix}. ZM theory is governed by the Lagrangian
+Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}.
+ZM theory is governed by the Lagrangian
 \begin{equation}
@@
 \end{equation}
-where more details can be found in \cref{sec:CKLagrangians}.  The
+where more details can be found in \cref{sec:ZMTheory}.  The
 color-stripped Feynman rule for the vertex is
@@
 theory simply follows from the Schouten identity in 2D.  Since the theory
-only has a cubic vertex and manifest off-shell color-kinematics
+is purely cubic and manifests off-shell color-kinematics
 duality, it is trivial to read off the color-dual numerator for any
@@
 
-\ace{Lets tighten up this paragraph a bit, especially the second half}
-It is tempting to try to match the pion four-point two-loop integrand
-to ZM on the cuts, but given that the cuts only probe the on-shell
-four-point amplitude, which is either subtle or vanishes for ZM, it is
-better to compare the off-shell numerators directly.  As local
-functions, the numerators never suffer from any of the subtleties of
-on-shell 2D kinematics.  Since the physical cuts are difficult to
-compare, ZM theory is being used here simply as a tool to eliminate
-generalized gauge freedom; ZM theory has the right power counting and
-kinematic structure in 2D to compare against.  Since ZM theory is only
-being used for the kinematical structure of its numerators, it is
-natural to introduce a proportionality constant $z$ between the NLSM
-and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.  The
-parameter $z$, which would normally be fixed on cuts, effectively
-encodes the discrepancy between the coupling constants of the two
-theories.\footnote{Floating the proportionality parameter $z$ is also
-  motivated because ZM is believed to be quantum mechanically
-  different from NLSM even though they are dual classically in two
-  dimensions \cite{Nappi:1979ig}.  When the four-point
-  pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is
-  normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$, the parameter
-  $z$ is fixed to $216/565$, which is clearly unrelated to the
-  difference in coupling constants.}  This introduces an extra degree of
-freedom into the problem.  Mechanically, the pion numerator is matched
-to ZM by first taking every possible assignment of right and left
-movers for the external particles and then restricting the pion
-numerator to 2D.  The loop momenta are restricted to 2D but left
-off-shell.  After performing the 2D matching to the following ZM basis numerators:
+It is tempting to try to match the pion four-point two-loop integrand to ZM
+on the cuts, but given that the cuts only probe the on-shell four-point
+amplitude, which is either subtle or vanishes for ZM, it is better to
+compare the off-shell numerators directly.
+The numerators of the two basis graphs are
 \be
@@
 \ee
-there are only 365 parameters of generalized gauge freedom.
-An overview of ZM theory and its color-dual construction can be found at the end of \cref{sec:CKLagrangians}.
+where $\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu$ is the color-stripped ZM vertex.
+As local functions, the
+numerators never suffer from any of the subtleties of on-shell 2D
+kinematics.
+We introduce a proportionality constant $z$ between the numerators of the two theories, $N_\text{NLSM} \vert_{2D} = z ~ N_\text{ZM}$, because we are only interested in how the kinematical structure of $N_\text{ZM}$ can be used to eliminate gauge freedom in $N_\text{NSLM}$.\footnote{Another reason for introducing the parameter $z$ is because the theories are believed to differ at loop level even though they are dual classically in 2D \cite{Nappi:1979ig}.
+Once all of the constraints from this section are imposed, $z$ is fixed to $216/565$ where the four-point pion tree amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$.}
+Mechanically, the pion numerator is matched
+to ZM by first taking every possible assignment of right and left
+movers for the external particles and then restricting the pion
+numerator to 2D.  The loop momenta are restricted to 2D but left
+off-shell.  After performing the 2D matching, there are only 365
+parameters of generalized gauge freedom.
+
 The loop momentum structure of ZM theory provides one final hint for
@@
 produced terms with up to $m+n=12$ powers of loop momenta.  When the
-pion numerator is forced to have the loop power counting structure in
+pion numerators are forced to have the loop power counting structure in
 \cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
-freedom parameters reduces to 58.  The pion numerator appearing in the
-ancillary files makes exactly this choice.
+freedom parameters reduces to 58.  The pion numerators appearing in the
+ancillary files make exactly this choice.
 
@@
 \begin{equation}
-  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
-  \text{ and }
-  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
-  \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
+  \mathcal{N}^{\text{YM}}\left[\NLSMBasisDoubleBox \right]\text{ and }\mathcal{N}^{\text{YM}}\left[\NLSMBasisPentaTriangle \right]\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
   \label{eq:ym-basis}
@@
   \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
-  N \left[
+  n \left[
     \KTDBContrib{1}{2}{3}{4}
@@
   \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
-  N\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
+  n\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
 \end{equation}
@@
 \cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
-\begin{eBox}
 \begin{equation}
@@
 \end{equation}
-\end{eBox}
 Thus we have identified the minimal failure state for a
@@
 \begin{equation}
-N_{(12|34)}^{\text{YM}} = \frac{t_8F^4}{3} \frac{s_{13}-s_{12}}{s_{23}{s_{13}}}
+\mathcal{N}_{(12|34)}^{\text{YM}} = \frac{t_8F^4}{3} \frac{s_{13}-s_{12}}{s_{23}{s_{13}}}
 \end{equation}
@@
 \begin{equation}
-N_{(12|34)}^{\text{YM}} + N_{(13|42)}^{\text{YM}} +N_{(14|23)}^{\text{YM}} = 0
+\mathcal{N}_{(12|34)}^{\text{YM}} + \mathcal{N}_{(13|42)}^{\text{YM}} +\mathcal{N}_{(14|23)}^{\text{YM}} = 0
 \end{equation}
@@
 \begin{align}
-\text{Res}\left[\frac{ N_{s}^{\text{YM}} }{s}\right]^{s=0}&= \frac{2}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
-\\
-\text{Res}\left[\frac{N_{t}^{\text{YM}} }{t}\right]^{s=0}&= -\frac{1}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
-\\
-\text{Res}\left[\frac{N_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\text{Res}\left[\frac{ \mathcal{N}_{s}^{\text{YM}} }{s}\right]^{s=0}&= \frac{2}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\\
+\text{Res}\left[\frac{\mathcal{N}_{t}^{\text{YM}} }{t}\right]^{s=0}&= -\frac{1}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\\
+\text{Res}\left[\frac{\mathcal{N}_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
 \end{align}
@@
 \begin{equation}
-N^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
+\mathcal{N}^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
 \end{equation}
 where $\mathcal{O}_i$ are the basis tensors of
-\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ is a
+\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}_i$ is a
 rational function of scalar products.
@@
 Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the
-Schouten identity. Below we provide the double-box and penta-triangle expressions to which we matched our NLSM integrands to in the text:
-\begin{equation}
-\ZMBasisDoubleBox =\left[\begin{split}
-  \langle (\ell_1+k_4) \ell_1 \rangle\langle \ell_1\ell_2 \rangle\langle \ell_2 (\ell_2+k_1) \rangle  \langle (\ell_2+k_1)(\ell_2+k_1+k_2) \rangle 
-\\
-\langle (\ell_1+k_3+k_4)(\ell_2+k_1+k_2) \rangle\langle (\ell_1+k_3+k_4)(\ell_1+k_4) \rangle
-\end{split}\right]
-\end{equation}
-\begin{equation}
-  \ZMBasisPentaTriangle =\left[
-    \begin{split}
-      \langle (\ell_1+k_4) \ell_1 \rangle\langle \ell_1\ell_2 \rangle\langle \ell_2 (\ell_2+k_1) \rangle  \langle (\ell_2+k_1)(\ell_1-k_1) \rangle 
-      \\
-      \langle (\ell_1+k_3+k_4)(\ell_1-k_1) \rangle\langle (\ell_1+k_3+k_4)(\ell_1+k_4) \rangle
-    \end{split}
-  \right]
-\end{equation}
-Furthermore, since ZM theory manifests color-kinematics duality
-without any reference to the on-shell condition, a mass term can be
-added to ZM theory without spoiling color-kinematics duality
-\cite{Cheung:2022mix}. In general, if the on-shell conditions are not
-used, color-kinematics duality is unaffected by the details of the
-propagator structure.
+Schouten identity.
+Since ZM theory manifests color-kinematics duality without any
+reference to the on-shell condition, a mass term can be added to ZM
+theory without spoiling color-kinematics duality \cite{Cheung:2022mix}. In general, if the
+on-shell conditions are not used, color-kinematics duality is
+unaffected by the details of the propagator structure.
 
@@
 
-Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which
-we quote now. The component definition of our spinor bracket that are
-consistent with the conventions above,
+Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. The component definition of our spinor bracket that are consistent with the conventions above,
 \begin{align}
@@
 \end{align}
-where the $a_i$ are component values of the four-vector,
-$k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$,
-one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:
+where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$, one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:
 \begin{equation}
@@
 \end{equation}
-Four-dimensional polarization dot products with fixed helicity states
-can be mapped as follows:
+Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
 \begin{equation}\label{eq:4DPols}
@@
 \end{equation}
-Note that given the above definition, the spinor helicity variables
-carry the same mass dimension for both the angle and square
-brackets. In terms of light-cone coordinates that we employed above in
-\cref{sec:CKLagrangians}, the angles and squares can be rewritten as
-follows:
+Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets.
+In terms of light-cone coordinates that we employed above in \cref{sec:CKLagrangians}, the angles and squares can be rewritten as follows:
 \begin{align}
@@
 \end{align}
-The conventions we use in the text where the holomorphic spinor,
-$X(p,k)$, carries extra mass dimension essentially amounts to shifting
-the bracket by the following overall factor:
+The conventions we use in the text where the holomorphic spinor, $X(p,k)$, carries extra mass dimension essentially amounts to shifting the bracket by the following overall factor:
 \begin{align}
@@
 \section{Regulating BEL integrals}\label{BELreg}
-At one-loop, weight counting tells us that the $n$-gon master
-numerator must have $n$ on-shell $Z$-particles. Unitarity requires
-that there are three distinct contributions from $Y\!Z$ theory -- the
-first from an off-shell $Y$-loop particle and then two more from
-different orientations of a $\bar{Z}Z$-loop.  Thus, $YZ$ theory gives
-us the following one-loop $n$-gon numerator:
-\begin{equation}
-N^{n\text{-gon},YZ}_{(12...n)} = \langle T^{1}T^{2}\cdots T^{n}\rangle+ \rangle F^1F^2\cdots F^n\rangle
-\end{equation}
-where $(\,\cdots)$ indicates an internal contraction over the $YY$ and
-$\bar{Z}Z$ loops. Plugging in the Feynman rule of
-\cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily
-obtain expressions in terms of the internal loop factors $\ell_i$ and the
-external momenta $k_i$ (we define the $\ell_i$ loop momentum as that
-flowing into $k_i$ and out of $k_{i-1}$):
-\begin{equation}
-N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n)
+At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles.
+Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.
+Thus, $Y\!Z$ theory gives us the following one-loop $n$-gon numerator:
+\begin{equation}
+N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+2\, (F^1F^2\cdots F^n)
+\end{equation}
+where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops.
+Plugging in the Feynman rule of \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
+\begin{equation}
+N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
 \end{equation}
@@
 \begin{equation}
- (F^1F^2\cdots F^n) = D (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n) + \mathcal{O}(D^0)
-\end{equation}
-The dimension dependent factor essentially counts that number of
-internal vector states. While this $n$-gon is manifestly color-dual,
-it does not produce the right cuts for NLSM. However, the scalar
-contribution, that comes dressed with an overall factor $D$
-\textit{does} manifest the duality globally, and satisfies all the
-desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory
-compute one-loop color-dual numerators consistent with NLSM cuts, we
-must add some additional states to cancel off he spurious poles, while
-preserving color-kinematics duality. We leave this as a direction of
-future work.
+ (F^1F^2\cdots F^n) = D (l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
+\end{equation}
+The dimension dependent factor essentially counts that number of internal vector states.
+While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM.
+However, the scalar contribution, that comes dressed with an overall factor $D$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts.
+In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality.
+We leave this as a direction of future work.
 
@@
 \begin{equation}
-T^{a}_{LR} = k_a(\ell_L-\ell_{R}) = (\ell_L+\ell_{R}) (\ell_L-\ell_{R})  = \ell_L^2-\ell_{R}^2 
+T^{a}_{LR} = k_a(l_L-l_{R}) = (l_L+l_{R}) (l_L-l_{R})  = l_L^2-l_{R}^2 
 \end{equation}
@@
 \begin{equation}
-N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,\ell)}-N^{\text{NLSM}}_{(1243,\ell)}-N^{\text{NLSM}}_{(1342,\ell)}+N^{\text{NLSM}}_{(1432,\ell)}
-\end{equation}
-where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $\ell_i$, we obtain the following expression for the BEL
-\begin{equation}
-N^{\text{BEL}}_{1|2,34} = s_{12} (\ell+k_1)^2 \ell^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
+N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
+\end{equation}
+where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
+\begin{equation}
+N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
 \end{equation}
@@
 \begin{equation}
-\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D \ell}{i\pi^{D/2}} \frac{\ell^\mu }{\ell^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
+\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
 \end{equation}

### 2023-09-21 notes/2loopNLSM.tex

--- 2023-09-21 notes/2loopNLSM.tex
@@
 is a viable alternative when the condition proves too stringent for an
-ansatz. As such, requiring instead that locality is only realized \textit{on-shell} may suffice.
+ansatz.  In particular, the most natural way to guarantee locality is
+to require the off-shell numerators to be polynomial functions of
+kinematics.  However, simply requiring on-shell locality may suffice.
 This alternative will be discussed in \cref{nonLocalScattering}.
@@
 leg (BEL) graphs.
+
+\begin{figure}
+\centering
+{\MCutC, \MCutD, \sumoCut, \MCutJ,  
+ \\
+  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
+\\
+\MCutI,  \MCutE, \MCutK, 
+\\
+ \MCutL, \MCutG,  \MCutH
+}
+\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
+  \end{figure}
 
@@
 
-Thus, to construct two-loop numerators prescriptively, as we have done
-at one-loop, would require knowledge of the full kinematic algebra for
-Yang-Mills off-shell. Since this is presently unavailable, to approach
-the problem of two-loop construction, we instead employ an ansatz
-based approach.
+Thus, to construct two-loop numerators prescriptively, as we have done at one-loop, would require knowledge of
+the full kinematic algebra for Yang-Mills off-shell. Since this is
+presently unavailable, to approach the problem of two-loop
+construction, we instead employ an ansatz based approach.
 

### 2023-09-21 notes/2loopNLSM.tex
some edits on loops

--- 2023-09-21 notes/2loopNLSM.tex
@@
   representations, see for example \cite{Johansson:2017srf,
-    Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2020ywq,
+    Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2020ywq,Carrasco:2022jxn,
     Carrasco:2023vjg}.}  the denominator $d_\Gamma$
@@
 the numerator $N_\Gamma$ is all of the remaining kinematic factors
-including dot products of momenta and polarization vectors.
-
-In this form the color factors $C_\Gamma$ are not independent and are related to
+including dot products of momenta and polarization vectors. In this 
+form the color factors $C_\Gamma$ are not independent and are related to
 one another via a set of Jacobi identities that look schematically
@@
 \begin{eBox}
-\begin{equation}
+\begin{equation}\label{chefsKiss}
    \NMCutC
@@
 \section{Conclusions and Outlook}\label{conclusions}
+
 There is overwhelming evidence that YM and NLSM obey color-kinematics
@@
 \label{nonLocalScattering}
-For example, consider the simple four-point example of a color-dual
-representation of Yang-Mills theory.
+As an exemplar of an off-shell non-local construction, consider the simple four-point example of a color-dual
+representation of Yang-Mills theory. We can define a functional numerator, $N_{(12|34)}^{\text{YM}}$, as follows, 
 \begin{equation}
@@
 \end{equation}
-By construction, this functionally symmetric numerator is
+where $N_s = N_{(12|34)}$, $N_t = N_{(14|23)}$ and $N_u = N_{(13|42)}$. By construction, this functionally symmetric numerator is
 anti-symmetric and obeys the Jacobi identity:
@@
 where we have applied the color structure Jacobi identity,
-$c_s+c_t+c_u=0$. While we can absolutely apply a generalized gauge
-trasformation \cite{BCJ} to restore field theoretic locality to the
-cubic numerators, we can see clearly that this is an aesthetic
-choice. Moreover, by abandoning traditional notions of off-shell
+$c_s+c_t+c_u=0$. In light of our findings in \cref{chefsKiss},  While we can absolutely apply a generalized gauge
+transformation \cite{BCJ} to restore field theoretic locality to the
+cubic numerators, it is maybe aesthetic
+choice.
+
+Moreover, by abandoning traditional notions of off-shell
 locality, we incidentally gained enough freedom to massage the
@@
 a loop-level construction of color-dual numerators for Yang-Mills.
-
-\subsection{Future Directions}\label{sec:Discussion}
 
@@
 rational function of scalar products.
+\subsection{Future Directions}\label{sec:Discussion}
 
@@
 where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$.
-Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
+Thus, in sufficiently large dimension, $D>2$, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
 

### 2023-09-21 notes/2loopNLSM.tex
Starting to drop YM numbers in where needed.

@@
 where the $k_i$ take the same definition as described near
-\cref{eq:scalar-basis}.  In our labeling of the two loop Jacobi-basis
-diagrams, shown in \cref{eq:jacobi-basis}, we find that the power
-counting bound proposed by Bern, Davies, and Nohle leads to an initial
-ansatz with 10,000 terms in the double-box, and 9849 terms for the
-penta-triangle.  Without power counting restrictions, both the
-double-box and the penta-triangle ansatz have an ansatz with 10,010
-terms each.  Imposing diagram automorphisms and maximal-cut gauge
-invariance on the two basis diagrams, we reduce the number of terms to
-XX for the double-box, and YY for the penta-triangle.  In
-Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
-imposed using a spanning set of minimal physical cuts, shown in
-\cref{fig:ym-spanning}.  Instead of also directly going to the
-spanning cuts, we work within the framework of the Method of Maximal
-Cuts \cite{Bern:2007ct} in order to identify the simplest cut that is in
-tension with the kinematic Jacobi relations.
+\cref{eq:scalar-basis}.  Without any power counting restrictions
+imposed, both the double-box and the penta-triangle have an ansatz
+with 10,010 terms each.  Imposing diagram automorphisms and
+maximal-cut gauge invariance on the two basis diagrams, we reduce the
+number of terms to 2235 for the double-box, and 4133 for the
+penta-triangle.  In Ref.~\cite{Bern:2015ooa}, the unitarity matching
+constraints were imposed using a spanning set of minimal physical
+cuts, shown in \cref{fig:ym-spanning}.  Instead of also directly going
+to the spanning cuts, we work within the framework of the Method of
+Maximal Cuts \cite{Bern:2007ct} in order to identify the simplest cut
+that is in tension with the kinematic Jacobi relations.
 

### 2023-09-21 notes/2loopNLSM.tex
Update 2loopNLSM.tex

--- 2023-09-21 notes/2loopNLSM.tex
@@
 
+\begin{figure}[t]
+  \begin{center}
+	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
+  \end{center}
+  \caption{The two physical cut topologies shared by NLSM, sGal, BI, and DBIVA}
+  \label{fig:emu}
+\end{figure}
 It is tempting to try to match the pion four-point two-loop integrand to ZM
@@
 \section{Conclusions and Outlook}\label{conclusions}
-
-There is overwhelming evidence that YM and NLSM obey color-kinematics
-duality at loop level, even though naive Lagrangians for these theories
-do not manifest the duality.  At tree level, the duality can be
+In summary, we have found that there is a tension between color-kinematics duality and an off-shell local construction of the two-loop four-point of the pure Yang-Mills integrand in $D$-dimensions.
+At tree level, we demonstrated that the duality can be
 manifested by breaking manifest Bose symmetry at the Lagrangian level,
@@
 the Bose symmetry of the external states due to the presence of the
-two gauge fields $A_\mu$ and $\bar{A}_\mu$.  The kinetic mixing
-between the two gauge fields permits globally color-dual 1-loop
+two gauge fields $A_\mu$ and $\bar{A}_\mu$.
+
+In addition to the natural tree-level construction, we found that kinetic mixing
+between the two gauge fields permits globally color-dual one-loop
 integrands, but special care must be taken so that the integrands
@@
 integrand beyond one-loop then requires sacrificing more than just Bose
-symmetry and in this paper it is argued that off-shell locality must
-be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in
-  order to obtain color-dual two-loop integrands.}
-
-Kinematic ``numerators'' that are rational functions of the kinematics
-appear unnatural from the perspective of point-like quantum field
-theories. After all, operators that produce rational functions of
-kinematics must be non-local. Thus, in order to identify valid color-dual representation of
-Yang-Mills beyond tree-level, we must relax the constraint of
+symmetry and in this paper we have argued that off-shell locality must
+be abandoned. \footnote{An example of this can already be found in the literature, where Locality is relaxed in \cite{Mogull:2015adi} in
+  order to obtain color-dual two-loop integrands with on-shell 4D states.}
+
+We concede building loop-level numerators from rational functions of the kinematics
+is rather unnatural from the perspective of point-like quantum field
+theories.
+After all, operators that produce rational functions are typically non-local in their construction.
+The archetypal example of non-local quantum operators are string vertex operators with $\alpha'$ corrections.
+These operators promote local tree-level amplitudes to stringy extended objects by integrating over the open string world-sheet:
+\be
+\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}t_8 F^4 \int_0^1 dx \,(1-x)^{\alpha' s_{12}-1} x^{\alpha' s_{12}-1}
+\ee
+The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure at in the color-ordering of the Park-Taylor factor in the denominator.
+While introducing a string world sheet is a jump from what we have found in this work, our funding certainly suggest that we must do \textit{something} to relax the constraint of
 \textit{off-shell locality}, and realize locality only in the limit of
-\textit{on-shell} kinematics. Below we provide an overview of what one
+\textit{on-shell} kinematics. This could be acheived by either modifying the kinetic term or potentially something more exotic. Below we provide an overview of what one
 might expect for such a construction, and provide some simple examples
@@
 anti-symmetric and obeys the Jacobi identity:
-\begin{equation}
+\begin{equation}\label{nonLocalNum}
 N_{(12|34)}^{\text{YM}} + N_{(13|42)}^{\text{YM}} +N_{(14|23)}^{\text{YM}} = 0
@@
 where we have applied the color structure Jacobi identity,
-$c_s+c_t+c_u=0$. In light of our findings in \cref{chefsKiss},  While we can absolutely apply a generalized gauge
+$c_s+c_t+c_u=0$.
+In light of our findings in \cref{chefsKiss}, building color-dual numerators in this way where locality is only realized on-shell might be a more natural approach.
+While we can absolutely apply a generalized gauge
 transformation \cite{BCJ} to restore field theoretic locality to the
-cubic numerators, it is maybe aesthetic
-choice.
+cubic numerators, this could merely be an aesthetic choice that is only permissible at tree-level.
 
 Moreover, by abandoning traditional notions of off-shell
-locality, we incidentally gained enough freedom to massage the
+locality, we incidentally have gained enough functional freedom to massage the
 color-dual numerators into a form that is manifestly gauge invariant
@@
 
-Much of the complexity for $D$-dimensional vector theories at
-loop-level arises due to the mixing between external polarization and
-internal loop momenta. As noted, one advantage of expanding ansatz
-construction towards functions of rational kinematics is the prospect
-of stripping out overall factors of gauge invariant tensors. Rather
+\subsection{Future Directions}\label{sec:Discussion}
+With an eye towards generalizing this construction for future multi-loop studies, we note that the four-point half-ladder secretly makes use of the color-dual structure of NLSM.
+At four-point, we can construct permutation invariants from the single BCJ basis amplitude of both NLSM and pure YM theory as follows:
+\be
+s t A^{\text{YM}}_{(s,t)} = t_8F^4 \qquad s t A^{\text{NLSM}}_{(s,t)} = s_{12}s_{23}s_{13}
+\ee
+Using this, we can redefine our non-local numerator of \cref{nonLocalNum} in a form that recasts color-dual structure to NLSM, and removes all the vector structure of Yang-Mills as an overall $t_8F^4$ factor:
+\be
+N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s_{12}s_{23}s_{13}} 
+\ee
+One advantage of this construction is that reduces some of the $D$-dimensional complexity vector theories that arises due to the mixing between external polarization and
+internal loop momenta. But maybe more importantly, it puts all the heavy lifting of functional jacobi relations on the scalar kinematic numerator, $N_{(12|34)}^{\text{NLSM}}$. Thus, rather
 than building an ansatz from the irreducible scalar products of
-\cref{eq:ym-basis},
+\cref{eq:ym-basis}, one might instead consider the following construction
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{O}_i$ are the basis tensors of
-\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ is a
-rational function of scalar products.
-\subsection{Future Directions}\label{sec:Discussion}
+where $\mathcal{O}_i$ are the gauge invariant tensor basis elements of
+\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ are
+rational functions of irreducible scalar products of \cref{eq:scalar-basis}.
+It would be interesting if a similar construction as our toy tree-level example could be uplifted to two-loop using the globally color-dual NLSM integrand that we have computed in this work.
+We see this as a natural future direction worth investigating that is made possible given the results of this work.
 

### 2023-09-22 notes/2loopNLSM.tex
Partial read through

@@
 % Comment the following out to compile new images
-
+%
 %\usetikzlibrary{external}  
@@
 %system call={                       %% Use lualatex in system call
-  % pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" %"\texsource" || rm "\image.pdf"
+%  % pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" %"\texsource" || rm "\image.pdf"
 %},
@@
 
-\newcommand{\ie}{i.e.~}
-\newcommand{\eg}{e.g.~}
+\newcommand{\ie}{i.e.,}
+\newcommand{\eg}{e.g.,}
 \usepackage{xspace}
@@
 
-\abstract{ We make progress in understanding how color-dual
-  representations must be constructed at the multi-loop level. First
-  we identify a cubic theory, semi-abelian Yang-Mills, that unifies
+\abstract{We report on progress in understanding how to construct color-dual multi-loop amplitudes.
+First we identify a cubic theory, semi-abelian Yang-Mills, that unifies
   many of the color-dual theories studied in the literature, and
   provides a prescriptive approach for constructing $D$-dimensional color-dual
-  numerators at one-loop directly from Feynman rules. Consideration of
+  numerators through one-loop directly from Feynman rules. Consideration of
   this theory highlights that the lifting from one-loop
@@
   and Dirac-Born-Infeld-Volkov-Akulov theory, respectively.  These
-  NLSM numerators are in tension with generalizations our one-loop construction. Using our loop-level bootstrap, we also find that the most general \emph{local} ansatz
+  NLSM numerators are in tension with generalizations of our one-loop construction. Using our loop-level bootstrap, we also find that the most general \emph{local} ansatz
   for two-loop four-point pure Yang-Mills fails to satisfy
@@
 studied on-shell
-\cite{Parke:1986gb,TasiLance,Cheung:2017pzi}. However, while plugging
-in on-shell states certainly offers a path towards taming the
+\cite{Parke:1986gb,TasiLance,Cheung:2017pzi}. However, while inserting on-shell states certainly offers a path towards taming the
 factorial growth of Feynman diagrams, it also obscures the off-shell
@@
 
-However, despite the tremendous success in leveraging this duality to
+Despite the tremendous success in leveraging this duality to
 compute gauge and gravity observables to high orders in perturbation
@@
 suited for algorithmically extracting rational terms from the
-$D$-dependence of dimensionally regulated loop momenta. Prior to this
-work, one of the primary barriers in studying multi-loop color-dual
-integrands $D$-dimensionally is the explosion of terms that one
-encounters in generic ansatz-based constructions at high-loop
-order. We were able overcome this barrier by employing a custom
-solver, \texttt{FiniteFieldSolve}, which will soon be made
-public.
+$D$-dependence of dimensionally regulated loop momenta.
+The ansatz approach to constructing numerators generally results in an explosion of terms, but in the case of scalar theories there is an added difficulty because the linear equations become dense.
+We were able overcome this barrier by employing a custom
+solver, \texttt{FiniteFieldSolve}, which will be made
+public soon.
 
@@
 simplicity that manifests redundancy in the on-shell observables of
-gauge and gravity theories. Ignoring factors of $i$ and the coupling
-constant, the starting point to realize the duality is to express generic $m$-point $L$-loop amplitudes in a cubic graph representation:
-\begin{equation}
-  \mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{C_\Gamma N_\Gamma}{d_\Gamma} .
+certain field theories. Ignoring factors of $i$ and the coupling
+constant, the starting point to realize the duality is to express generic $n$-point $L$-loop amplitudes in a cubic graph representation:
+\begin{equation}
+  \mathcal{A}_n^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{C_\Gamma N_\Gamma}{d_\Gamma} .
   \label{eq:gen-amp}
@@
 Here the spacetime dimension is $D$.  Even though the underlying
-theory may have quartic (or higher multiplicity) vertices, like NLSM and gravity, it is
+theory may have quartic (or higher multiplicity) vertices, like YM and NLSM, it is
 possible to multiply and divide by propagators so that the sum runs
@@
 When the kinematic algebra is not known explicitly, the kinematic numerators are typically constructed from an ansatz.
-As an example, the result of such a calculation for four-point NLSM pion scattering at tree level produces the numerators
+As an example, the result of such a calculation for four-point NLSM scattering at tree level produces the numerators
 \begin{align}
@@
 contains an explicit factor of $s$ that cancels with the propagator
-and the same goes for the $t$- and $u$-channels so that the net result
-is a local function, just as one would expect for the pion tree
+and the same goes for the $t$- and $u$-channels.
+The net result is that the amplitude is a local function, just as one would expect for the pion tree
 amplitude.
@@
 \emph{different} amplitude to produce the corresponding amplitude in
-a new colorless theory: \be\label{DCconstruction}
-\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
+a new theory,
+\be\label{DCconstruction}
+\tilde{\mathcal{A}}_n^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
 \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{C_\Gamma
   \tilde{N}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(C_\Gamma \to N_\Gamma)}
-~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
+~~ \mathcal{M}_n^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
 \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{N_\Gamma
@@
 This is known as the double-copy construction \cite{BCJ,Bern:2010ue,BCJreview}.
-Importantly, the $\tilde{n}_\Gamma$ do not need to respect
+Importantly, the $\tilde{N}_\Gamma$ do not need to respect
 color-kinematics duality.  The prototypical example of the double-copy
@@
 invariance of the graviton.  The double copy can be proven at tree
-level using the KLT relations but there is significant evidence that
+level using the Kawai-Lewellen-Tye (KLT) relations but there is significant evidence that
 the double copy persists to all loop orders \cite{FiveLoopN4,
   GeneralizedDoubleCopyFiveLoops, Bern:2018jmv, Carrasco:2021otn, KLT,
-  KiermaierTalk}.  In addition to pointing at potential undiscovered
+  KiermaierTalk}.  In addition to pointing at undiscovered
 structure hidden in the Lagrangian for gravity, the double copy is
 immensely useful at a utilitarian level since it is much more
-efficient at producing $\mathcal{M}_m^L$ than traditional methods like
+efficient at producing $\mathcal{M}_n^L$ than traditional methods like
 Feynman rules.
@@
 \end{equation}
-with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$
-terms, indicating that there are additional relations -- the
+with legs $1$ and $n$ fixed.  Since the the sum only contains $(n-2)!$
+terms, there must be additional relations -- the
 Kleiss-Kuijf (KK) relations \cite{Kleiss:1988ne} -- amongst the
@@
 implies that the KK basis is overcomplete and can be reduced to a
-basis of $(n-3)!$ amplitudes via the fundamental BCJ identities
+basis of $(n-3)!$ amplitudes via the fundamental Bern-Carrasco-Johansson (BCJ) identities
 \cite{BCJ,Feng:2010my}
@@
 In terms of constructing explicit color-dual solutions at tree level,
-it is enough to specify the numerator of the half ladder because any
-diagram can be reduced to a half ladder through successive
-applications of the Jacobi identity.  At 1-loop, every diagram can be
-related to one topology as well, in this case the $n$-gon.  Two-loop
+it is enough to specify the numerator of the half-ladder because any
+diagram can be reduced to a half-ladder through successive
+applications of the Jacobi identity.  At one-loop, every diagram can be
+related to one topology as well, in this case the $n$-gon, which can be understood as a forward limit of the half-ladder.  Two-loop
 calculations play an important role in our understanding of
@@
 While the BCJ relations are an on-shell statement about the color-dual
-nature of scattering amplitudes, one might aspire to hard code
-color-kinematics duality by realizing an off-shell Lagrangian
-description of the theory. The double-copy construction of
+nature of scattering amplitudes, one might aspire to trivialize
+the duality by encoding it in an off-shell Lagrangian
+of the theory. The double-copy construction of
 \cref{DCconstruction} would suggest a manifestly cubic Lagrangian of
@@
 participate in the construction, as is the case for $DF^2$ theory \cite{Johansson:2017srf}.
-Though generally these quadratic dressings are simply delta functions, $P_V^{ab} = \delta^{ab}$, or flat space metrics, $P_W^{\mu\nu}=\eta^{\mu\nu}$.
+Generally, these quadratic dressings are simply delta functions, $P_V^{ab} = \delta^{ab}$, or flat space metrics, $P_W^{\mu\nu}=\eta^{\mu\nu}$.
 As written, the theory will be color dual if the off-shell cubic vertex is antisymmetric and satisfies the Jacobi identity.
+\jm{We're talking about kinematic numerators but using $V$s.
+Should $V$ be swapped with $W$?
+If we do swap them then we need to swap $a$ with $\mu$ too.}
 Specifically,
 \begin{align}
-\textit{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0
-\\
-\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\label{jacID}
+\text{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0
+\\
+\text{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\label{jacID}
 \end{align}
-where using the Feynman rules of \cref{CKFrules}, the bracketed expression is the half-ladder numerator of the following diagram,
-\begin{equation}
-{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv N\left[\halfLadder\right]\,,
-\end{equation}
-and likewise for the $W^{\mu \nu \rho}$ dressing. Off-shell descriptions of
+where, using the Feynman rules of \cref{CKFrules}, the bracketed expression is the half-ladder numerator \jm{Color factor?} of the following diagram,
+\begin{align}
+{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} &\equiv V^{a_1 a_2 b_1} V^{b_1 a_3 b_2} ...V^{b_{n-3} a_{n-1} a_n}\\
+&= C\left[\halfLadder\right]\,,
+\end{align}
+and likewise for the $W^{\mu \nu \rho}$ dressing.
+Off-shell descriptions of
 color-dual theories are rare, and only a few examples are available in
@@
 theories directly from a set of cubic interactions, higher point
-Jacobi and antisymmetry constraints require introducing additional operators \cite{Carrasco:2022lbm,Carrasco:2022sck}, sometimes including additional propagating fields not originally considered in the spectrum.
-See ref.~\cite{Ben-Shahar:2022ixa} for a recent
-example. Indeed, as we will show in \cref{sec:cubic}, Yang-Mills
+Jacobi and antisymmetry constraints require introducing additional operators \cite{Carrasco:2022lbm,Carrasco:2022sck} or propagating fields \cite{Ben-Shahar:2022ixa}.
+Indeed, as we will show in \cref{sec:cubic}, Yang-Mills
 requires introducing a cubic two-form interaction in order to manifest
@@
   is most emphatically not made here.}
+After imposing the four constraints below, any remaining coefficients in the ansatz encode ``generalized gauge freedom'', meaning that the
+choice of coefficients does not affect the physical integrand or its double copy.
 \begin{enumerate}
@@
   that the integrand is expressed in terms of purely cubic diagrams.
-\item \textbf{Graph symmetries}: The diagram numerators are only a
+\item \textbf{Graph symmetries}: A diagram's numerators is only a
   function of the diagram's topology and labeling.  Furthermore, the
@@
 local (polynomial) functions of the graph kinematics with the correct
-power counting and external states. Locality is also physically motivated since Feynman
-rules by construction produce polynomial numerators. Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of
+power counting and external states. Locality is physically motivated since Feynman
+rules produce polynomial numerators. Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of
 kinematics. However, insisting on a local numerator is
@@
 is a viable alternative when the condition proves too stringent for an
-ansatz.  In particular, the most natural way to guarantee locality is
-to require the off-shell numerators to be polynomial functions of
-kinematics.  However, simply requiring on-shell locality may suffice.
+ansatz.  However, simply requiring on-shell locality may suffice.
 This alternative will be discussed in \cref{nonLocalScattering}.
@@
 \cite{Bern:2015ooa}.  If a global solution cannot be found, this is
-one way to enlarge the ansatz where the other option described above
-was to incorporate non-local terms in the ``numerators''.  A globally
+one way to enlarge the ansatz, where another option is to incorporate non-local terms in the ``numerators''.  A globally
 color-dual integrand is desirable because of its simplicity and
@@
 antisymmetric and hence have signs built into their orientations.
-When used in conjuction with the Jacobi relations, \eg
+When used in conjuction with the Jacobi relations, \eg{}
 \cref{eq:TwoLoopJacobiOne}, the symmetry constraints of non-basis
@@
 
-The final constraints comes from ensuring that the ansatz correctly
+The final constraints come from ensuring that the ansatz correctly
 reproduces the generalized unitarity cuts of the desired theory, thus
 guaranteeing that the numerators encode the correct physical,
-theory-dependent information.  Generalized unitarity methods has been
-reviewed in many places so we will be light on details here
+theory-dependent information.  Generalized unitarity has been
+reviewed in many places
 \cite{BCFUnitarity, Bern:2015ooa, Bourjaily:2017wjl,
   JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview,
-  Edison:2022jln, Edison:2022smn}, which was recently optimized for effective field theories like NLSM \cite{Carrasco:2023qgz}. Generalized unitarity equates products of on-shell tree amplitudes,
+  Edison:2022jln, Edison:2022smn} and was recently optimized for effective field theories like NLSM \cite{Carrasco:2023qgz}. Generalized unitarity equates products of on-shell tree amplitudes,
 encoded via a graph $\gamma$, to sums over compatible\footnote{A
@@
 two types of expressions appearing in \cref{eq:SchematicCutEquation},
-consider the so-called iterated two-particle cut which can be
+the iterated two-particle cut can be
 represented as a product of trees via
@@
 convenient to project onto a specific element of the Del
-Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
-inserting color-ordered amplitudes, a la the right hand side of
+Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni}.  This is done by only
+inserting color-ordered amplitudes, \emph{a la} the right hand side of
 \cref{eq:ddm-basis} in the product of trees, and restricting the set
@@
 The quintessential example of such a ``pathological'' cut is the 3-1
-two-particle cut at one loop which hides a bubble-on-external-leg
+two-particle cut at one loop which hides a bubble-on-external-leg (BEL)
 singularity
@@
   Geyer:2015bja,Geyer:2015jch,Edison:2020uzf, Edison:2022jln, Edison:2022smn}. In addition to the
-bubble-on-external-leg cuts, there is a related class of cuts in which
+BEL cuts, there is a related class of cuts in which
 an uncut propagator is set to zero by an \emph{internal cut
@@
 
-\iffalse
-The essence of generalized unitarity is that when internal lines are
-placed on-shell, the integrand should factorize into a product of
-on-shell tree amplitudes.  The cut to be performed can, itself, be
-encoded in a graph.  For example, potential four-point two-loop cuts include
-\begin{equation}
-\label{eq:PotentialCuts}
-\text{(a)} \SubtleCut ~~~~ \text{(b)} \PhysicalCutOne{}{}{}{} ~~~~ \text{(c)} \PhysicalCutTwo{}{}{}{} ~~~~ \text{(d)}  \MaxCut
-\end{equation}
-as well as many more.
-In these graphs, all exposed propagators are understood to be cut/on-shell.
-As an equation, a unitarity cut looks schematically like
-\begin{equation}
-\label{eq:SchematicCutEquation}
-\sum \limits_\text{topologies} \frac{n \vert_\text{cut}}{\prod \limits_\text{uncut} k^2} = \sum \limits_\text{states} \prod \limits_\text{blobs} A_\text{tree} \, .
-\end{equation}
-The right hand side of the equation is a product of on-shell tree
-amplitudes, represented graphically in \cref{eq:PotentialCuts} by grey
-blobs.  States crossing (or propagating across) the cut must be summed
-over.  For scalars this sum is trivial but for spinning particles this
-is no longer the case and the physical state projector must be
-inserted (see Dimitrius paper for simplifying this operation).  The
-graph topologies appearing in the left hand side of
-\cref{eq:SchematicCutEquation} come from blowing up the grey blobs
-into cubic tree graphs in every conceivable way.  The numerator of
-each graph is related back to the basis numerators via Jacobi
-relations.  For each of these topologies, the numerator of the
-associated graph is subjected to the cut constraints and is then
-divided by the uncut propagators.  The right hand side is assumed to
-be known, which places a constraint on the numerator ansatz in the
-left hand side.
-
-It is possible to work with either color-dressed cuts or color-ordered
-cuts.  For color-dressed cuts the grey blobs are blown up into all
-possible channels and all color factors $f^{abc}$ are explicitly
-retained on both sides of the unitarity equation
-\cref{eq:SchematicCutEquation}.  For color-ordered cuts the grey blobs
-are only blown up in color-ordered channels, all color factors in
-\cref{eq:SchematicCutEquation} are suppressed, and the product of
-on-shell amplitudes only extends over color-ordered trees.  Since
-color-ordered cuts do not contain the full color information of the
-theory, it is necessary to do multiple color-ordered cuts -- over
-different orderings of the blob labels -- in order to fully capture
-all of the cut information.  For a color dual theory such as NLSM or
-YM it is enough to do $(n-2)!$ labelings of each blob due to the
-Kleiss-Kuijf and $U(1)$ decoupling identities (cite KK).  In this
-sense color-dressed cuts contain extraneous information that is
-bypassed when using color-ordered cuts.
-
-In our construction, only well-defined cuts are imposed so, for
-example, cut (a) of \cref{eq:PotentialCuts} is not enforced since it
-is possible to blow up the left blob into a tree amplitude with an
-on-shell internal propagator.  Cuts (b), (c), and (d) represent
-physical cuts where (d) is known as a maximal cut since the maximal
-number of propagators have been put on shell.  \fi
-
-After imposing all four of the conditions above, any remaining free
-parameters represent ``generalized gauge freedom'' meaning that the
-freedom does not affect the physical integrand or its double copy.
-
 \section{One-loop cubic construction}
@@
 Contracting this with the vector state sum, we can see that the cubic
-Yang-Mills vertex does not satisfy the four-point Jacobi identity:
+Yang-Mills vertex does not satisfy the four-point Jacobi identity,
 \begin{equation}
@@
 However, the remaining terms can be absorbed into the definition of the
-four-point kinematic numerator, as follows
-\begin{equation}
-{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4 = {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4 + s_{12} (\varepsilon_{(13)}\varepsilon_{(24)}-\varepsilon_{(14)}\varepsilon_{(23)})
-\end{equation}
-Note that this new definition of the $s$-channel numerator contains two factors of $\varepsilon_{(ij)} $ that contract spacetime indices \textit{across} the factorization, suggesting the inclusion of a spin-2 mode.
+four-point kinematic numerator as follows
+\begin{equation}
+{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4 = {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4 + s_{12} (\varepsilon_{(13)}\varepsilon_{(24)}-\varepsilon_{(14)}\varepsilon_{(23)}).
+\end{equation}
+Note that this new definition of the $s$-channel numerator contains two factors of $\varepsilon_{(ij)} $ that contract spacetime indices \textit{across} the factorization channel, suggesting the inclusion of a spin-2 mode.
 As such, we use $V_{\text{YM}+B}$ to denote the inclusion of an additional two-form, as was studied in Ref.~\cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian.
 After the introduction of the two-form, the
-numerators now satisfy the Jacobi identity:
+numerators now satisfy the Jacobi identity
 \begin{equation}
@@
 \end{equation}
-where the new cubic Lagrangian takes the form\,,
+where the new cubic Lagrangian takes the form,
 \begin{equation}
@@
 now, we will study how to construct one-loop integrands consistent
-with the color-kinematics by isolating the cubic sector of the state
+with color-kinematics by isolating the cubic sector of the state
 sum above.
@@
 only in terms with two factors of polarization dot products,
-$(\varepsilon\varepsilon)^2$. Whereas if we restricted ourselves to
+$(\varepsilon\varepsilon)^2$. If we restricted ourselves to
 just considering factors with a single polarization dot product, the
@@
 \end{equation}
-This restriction to the $(\varepsilon\varepsilon)^1$ cubic sector of Yang-Mills is closely related to the MHV decomposition of color-dual numerators \cite{TasiLance,ElvangHuangReview,Chen:2019ywi,Chen:2021chy}, where choosing appropriate reference vectors sends all $(\varepsilon\varepsilon) \rightarrow 0$, with the exception of one of the positive helicity polarizations, $\varepsilon^+_1$, dotted into all the $n-2$ negative helicity modes in the full MHV amplitude, $\varepsilon^+_1 \varepsilon^-_i \neq 0$.
+This restriction to the $(\varepsilon\varepsilon)^1$ cubic sector of Yang-Mills is closely related to the MHV decomposition of color-dual numerators \cite{TasiLance,ElvangHuangReview,Chen:2019ywi,Chen:2021chy}.
+In the MHV sector it is possible to choose the reference vectors so that all dot products of polarization vectors vanish, $(\varepsilon\varepsilon) \rightarrow 0$, except those involving one of the positive helicity polarizations, $\varepsilon^+_1 \varepsilon^-_i \neq 0$.
 We describe this in detail in \cref{Conventions}.
-With the interest in constructing dimension agnostic color-dual integrands at one-loop, we want to avoid making specific reference to 4D helicity states.
+By focusing on $(\varepsilon\varepsilon)$ structure rather than specific 4D helicity states, we will be able to construct dimension agnostic color dual integrands at one-loop.
 
@@
 Here we can think of the abelian vector as a background field that
-sources on-shell $A_\mu$ currents. Indeed, as we describe in Appendix
+sources on-shell $A_\mu$ currents. Indeed, as we describe in
 \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
@@
   \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
-  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
-\end{equation}
-where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply:
+  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
+\end{equation}
+where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply
 \be
-\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}
+\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}.
 \ee
-As one can see, the kinetic term mixes the two gauge fields and has the standard
-Feynman rule of $i/k^2$.  We can use the Ward identity of
+We can use the Ward identity of
 \cref{eq:GIrelA} to check that the amplitudes are indeed gauge
@@
 SDYM) and one-minus at tree-level or by plugging in the on-shell states of $J$-theory \cite{Cheung:2020djz,Cheung:2021zvb} and
-$YZ$-theory \cite{Cheung:2016prv}. Indeed, the
-$D$-dimensional description of $J$-theory is just the following blocks
+$YZ$-theory \cite{Cheung:2016prv}. Indeed, semi-YM is just the following blocks
 in the expansion of Yang-Mills given in Ref.~\cite{Pavao:2022kog}
@@
 \begin{equation}
-A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}\, .
-\end{equation}
+A(...)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}}\, .
+\end{equation}
+\jm{For the tree amplitude how about we use something like}
+\begin{equation}
+A(1,2...,i,...n)_{\text{tree}} = \sum_{i\neq j}\Delta^{(ij)}_{\text{tree}} \sim \sum (\varepsilon_i \varepsilon) (\varepsilon k)^{n-2} (kk)^{3-n}
+\end{equation}
+where $i$ is the $\bar{A}_\mu$ particle.
+\jm{And something similar for 1-loop?
+This is one of the more important results of the paper so I'd like to add some schematic version of the $\Delta$s to make this paragraph as self-contained and clear as possible even if it introduces some redundancy.}
 To recover NLSM at one-loop, we need to extract the $D$-dependent part
@@
 \subsection{One-loop color-dual integrands}\label{oneLoopCK}
+\jm{Would it be alright to omit the coupling constants in this section?  I think we've done so elsewhere.}
 Our first application of this theory for color-dual construction at
@@
 graphs can be taken to be
+\jm{This looks beautiful!  Thank you to whoever formatted this.}
 \begin{equation}
@@
 The numerators of the two basis graphs are
+\jm{I think I can simplify these numerators a little.  I'll work on it.  I like having them here to break up the text block a little.}
 \be

### 2023-09-22 notes/2loopNLSM.tex
cleaned up conclusions

@@
 In general, the $n$-gon diagram would be,
-\begin{equation}
+\begin{equation}\label{SDYMnGon}
 N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
@@
 \cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator:
-\begin{equation}
+\begin{equation}\label{NLSMnGon}
 N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
@@
 contractions of $\bar{A}_\mu A^\mu$,
-\begin{equation}
+\begin{equation}\label{2loopTension}
 \mathcal{A}^{\text{YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=\doubleBoxObstructionA +\doubleBoxObstructionB+\cdots 
@@
 \section{Conclusions and Outlook}\label{conclusions}
-In summary, we have found that there is a tension between color-kinematics duality and an off-shell local construction of the two-loop four-point of the pure Yang-Mills integrand in $D$-dimensions.
-At tree level, we demonstrated that the duality can be
+
+In summary, we have found that there is a tension between color-kinematics duality and an off-shell local construction of the two-loop four-point pure Yang-Mills integrand in $D$-dimensions.
+At tree level, we found that the duality can be
 manifested by breaking manifest Bose symmetry at the Lagrangian level,
@@
 between the two gauge fields permits globally color-dual one-loop
-integrands, but special care must be taken so that the integrands
-produced from semi-abelian YM correspond to SDYM or NLSM.  Due to the
-kinetic mixing that stems from the broken Bose symmetry, it is
-impossible to construct a two-loop integrand for semi-abelian YM theory,
-that is, the theory is one-loop exact.  Obtaining a globally color-dual
+integrands, and after plugging in suitable on-shell states, the integrands
+produced by semi-abelian YM correspond are those of SDYM in \cref{SDYMnGon} 
+and NLSM in \cref{NLSMnGon}.  Due to the
+kinetic mixing that stems from the broken Bose symmetry, \cref{2loopTension} shows why it is
+impossible to construct a two-loop integrand for semi-abelian YM theory.
+In \cref{2loopBoot}, we overcame this obstruction by successfully constructing two-loop NLSM numerators with an ansatz based bootstrap.
+However, we found that the same approach fails for two-loop pure Yang-Mills, and pin-pointed the failure point to a particular unitarity cut captured by \cref{chefsKiss}.
+Thus, obtaining a globally color-dual
 integrand beyond one-loop then requires sacrificing more than just Bose
-symmetry and in this paper we have argued that off-shell locality must
-be abandoned. \footnote{An example of this can already be found in the literature, where Locality is relaxed in \cite{Mogull:2015adi} in
-  order to obtain color-dual two-loop integrands with on-shell 4D states.}
+symmetry, and in this paper we have argued that off-shell locality must
+be abandoned for color-dual constructions of multi-loop Yang-Mills. \footnote{An example of this can already be found in the literature, where Locality is relaxed in \cite{Mogull:2015adi} in
+  order to obtain color-dual two-loop integrands with on-shell 4D states.} To expand the available function space, we propose that one should consider including rational functions of kinematics, rather than just polynomials.
 
@@
 The archetypal example of non-local quantum operators are string vertex operators with $\alpha'$ corrections.
-These operators promote local tree-level amplitudes to stringy extended objects by integrating over the open string world-sheet:
+These operators promote local tree-level amplitudes to stringy extended objects by integrating over disc integrals of the open string worldsheet:
 \be
-\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}t_8 F^4 \int_0^1 dx \,(1-x)^{\alpha' s_{12}-1} x^{\alpha' s_{12}-1}
+\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}\supset t_8 F^4 \int_0^1 dx \,\frac{ x^{\alpha' s_{12}}(1-x)^{\alpha' s_{23}}}{x(1-x)(s_{12}+s_{23})}
 \ee
-The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure at in the color-ordering of the Park-Taylor factor in the denominator.
-While introducing a string world sheet is a jump from what we have found in this work, our funding certainly suggest that we must do \textit{something} to relax the constraint of
-\textit{off-shell locality}, and realize locality only in the limit of
-\textit{on-shell} kinematics. This could be acheived by either modifying the kinetic term or potentially something more exotic. Below we provide an overview of what one
-might expect for such a construction, and provide some simple examples
-at tree-level that manifest this structure.
+The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure color and kinematic factors \cite{Carrasco:2019yyn}.
+While introducing some type of worldsheet formulation of color-dual numerators might seem unjustified given the results of this work, our findings certainly suggest that we must do \textit{something} to relax the constraint of off-shell locality, and realize locality only in the limit of
+\textit{on-shell} kinematics. This could be acheived by either modifying the kinetic term or potentially something new and more exotic. Below we provide some simple examples
+at tree-level of what one might consider for implementing such a construction.
 
@@
 \label{nonLocalScattering}
-As an exemplar of an off-shell non-local construction, consider the simple four-point example of a color-dual
+As an exemplar of an off-shell non-local structure, consider the simple four-point example of a color-dual
 representation of Yang-Mills theory. We can define a functional numerator, $N_{(12|34)}^{\text{YM}}$, as follows, 
@@
 \ee
-One advantage of this construction is that reduces some of the $D$-dimensional complexity vector theories that arises due to the mixing between external polarization and
-internal loop momenta. But maybe more importantly, it puts all the heavy lifting of functional jacobi relations on the scalar kinematic numerator, $N_{(12|34)}^{\text{NLSM}}$. Thus, rather
+One advantage of this construction is that it reduces some of the $D$-dimensional complexity of vector theories that arises due to the mixing between external polarization and
+internal loop momenta. But maybe more importantly, it puts all the heavy lifting of functional Jacobi relations on the scalar kinematic numerator, $N_{(12|34)}^{\text{NLSM}}$. Thus, rather
 than building an ansatz from the irreducible scalar products of
@@
 \end{equation}
-where $\mathcal{O}_i$ are the gauge invariant tensor basis elements of
+where $\mathcal{O}_i$ are the on-shell gauge invariant tensor basis elements of
 \cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ are
 rational functions of irreducible scalar products of \cref{eq:scalar-basis}.
-It would be interesting if a similar construction as our toy tree-level example could be uplifted to two-loop using the globally color-dual NLSM integrand that we have computed in this work.
-We see this as a natural future direction worth investigating that is made possible given the results of this work.
+It would be interesting if a similar construction as our tree-level example could be uplifted to two-loop using the globally color-dual NLSM integrand that we have computed in this work.
+We see this as a natural future direction worth investigating that is made possible given our findings.
 

### 2023-09-22 notes/2loopNLSM.tex
conclusion

@@
 \ee
-The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure color and kinematic factors \cite{Carrasco:2019yyn}.
+The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure color and kinematic factors \cite{MafraBCJAmplString,Broedel:2013tta,Mafra:2016mcc,Carrasco:2019yyn}.
 While introducing some type of worldsheet formulation of color-dual numerators might seem unjustified given the results of this work, our findings certainly suggest that we must do \textit{something} to relax the constraint of off-shell locality, and realize locality only in the limit of

### 2023-09-22 notes/2loopNLSM.tex
added in appropriate ek and kk scaling for polarization blocks

@@
 This restriction to the $(\varepsilon\varepsilon)^1$ cubic sector of Yang-Mills is closely related to the MHV decomposition of color-dual numerators \cite{TasiLance,ElvangHuangReview,Chen:2019ywi,Chen:2021chy}.
-In the MHV sector it is possible to choose the reference vectors so that all dot products of polarization vectors vanish, $(\varepsilon\varepsilon) \rightarrow 0$, except those involving one of the positive helicity polarizations, $\varepsilon^+_1 \varepsilon^-_i \neq 0$.
+In the MHV sector it is possible to choose the reference vectors so that all dot products of polarization vectors vanish, $(\varepsilon\varepsilon) \rightarrow 0$, except those involving one of the positive helicity polarizations, $(\varepsilon^+_1 \varepsilon^-_i )\neq 0$.
 We describe this in detail in \cref{Conventions}.
@@
 
-\subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
+\subsection{semi-abelian Yang-Mills theory}\label{semiYM}
 As we argued above, if we include factors of
@@
 \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
-\cite{Monteiro2011pc}.  Specifically, semi-Abelian YM is simply a
+\cite{Monteiro2011pc}.  Specifically, semi-abelian YM is simply a
 clever reinterpretation of the Lagrangian obtained by integrating an
@@
 \begin{equation}
-A(...,\bar{A}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
+A(A_1,...,\bar{A}_i,...,A_n)_{\text{tree}} = \sum_{i\neq j} (\varepsilon_i \varepsilon_j) \Delta^{(ij)}_{\text{tree}} \sim \sum_{i\neq j} (\varepsilon_i \varepsilon_j)  \sum_a \,[(\varepsilon k)^{n-2} (kk)^{3-n}]_a\,,
 \end{equation}
@@
 \begin{equation}
-A(...)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}}\, .
-\end{equation}
-\jm{For the tree amplitude how about we use something like}
-\begin{equation}
-A(1,2...,i,...n)_{\text{tree}} = \sum_{i\neq j}\Delta^{(ij)}_{\text{tree}} \sim \sum (\varepsilon_i \varepsilon) (\varepsilon k)^{n-2} (kk)^{3-n}
-\end{equation}
-where $i$ is the $\bar{A}_\mu$ particle.
-\jm{And something similar for 1-loop?
-This is one of the more important results of the paper so I'd like to add some schematic version of the $\Delta$s to make this paragraph as self-contained and clear as possible even if it introduces some redundancy.}
-To recover NLSM at one-loop, we need to extract the $D$-dependent part
+A(A_1,...,A_n)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}} \sim \sum_a\,[ (\varepsilon k)^{n} (kk)^{-n}]_a\, .
+\end{equation}
+where $[\,\cdots]_a$ are terms with appropriate powers of $(\varepsilon k)$ and $(kk)$.
+As we describe in detail in \cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to extract the $D$-dependent part
 that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional
@@
 since as constructed $YZ$-theory matches to NLSM for off-shell
-Y-particles. We provide explicit expressions for these one-loop amplitudes in the next section.
+Y-particles. We now provide explicit expressions for these one-loop amplitudes in the next section.
 
 \subsection{One-loop color-dual integrands}\label{oneLoopCK}
-\jm{Would it be alright to omit the coupling constants in this section?  I think we've done so elsewhere.}
 Our first application of this theory for color-dual construction at
-loop level is for self-dual Yang-Mills (SDYM). At tree-level, the
+loop level is for self-dual Yang-Mills (SDYM). As we have done throughout the text, we will set all coupling constants to unity. At tree-level, the
 off-shell cubic vertices can be written in terms of light cone
@@
 \begin{equation}
-\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
+\simplebox = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
 \end{equation}
@@
 \begin{equation}\label{SDYMnGon}
-N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
+N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
 \end{equation}
@@
 \begin{equation}
-\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
+\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = 2^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
 \end{equation}
@@
 \begin{equation}\label{NLSMnGon}
-N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
+N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =   [12][23]\cdots [n1]
 \end{equation}
@@
 integrand beyond one-loop then requires sacrificing more than just Bose
-symmetry, and in this paper we have argued that off-shell locality must
-be abandoned for color-dual constructions of multi-loop Yang-Mills. \footnote{An example of this can already be found in the literature, where Locality is relaxed in \cite{Mogull:2015adi} in
-  order to obtain color-dual two-loop integrands with on-shell 4D states.} To expand the available function space, we propose that one should consider including rational functions of kinematics, rather than just polynomials.
+symmetry, and in this paper we have argued that off-shell locality\footnote{An example of this can already be found in the literature, where locality is relaxed in \cite{Mogull:2015adi} in
+  order to obtain color-dual two-loop integrands with on-shell 4D states.} must
+be abandoned for color-dual constructions of multi-loop Yang-Mills.
+To expand the available function space, we propose that one should consider including rational functions of kinematics, rather than just polynomials.
 

### 2023-09-22 notes/2loopNLSM.tex
small edits

@@
 Below we review the four manifestly color-dual theories that we mention in
-the text, in particular self-dual Yang-Mills (SDYM) \cite{Monteiro2011pc}, two formulations of NLSM \cite{Cheung:2016prv,Cheung:2020djz,Cheung:2021zvb}, and ZM \cite{Zakharov:1973pp, Cheung:2022mix}.
-All
+the text, self-dual Yang-Mills (SDYM) \cite{Monteiro2011pc}, two formulations of NLSM \cite{Cheung:2016prv,Cheung:2020djz,Cheung:2021zvb}, and ZM \cite{Zakharov:1973pp, Cheung:2022mix}.  All
 of these theories are closely tied together by the semi-abelian YM
@@
 theories, Bose symmetry is broken or obscured at the Lagrangian level.
-Because of the broken Bose symmetry (and the inherited kinetic mixing
+Since Bose symmetry is broken (and inherit the kinetic mixing
 of semi-abelian YM), these theories require additional interactions to produce color-dual representations beyond one-loop.
@@
 Furthermore, field configurations that satisfy \cref{SDcon} correspond to instantons which are probed by the path integral in the full non-perturbative description of Yang-Mills.
-To construct a perturbative action, begin by
+To construct a manifestly perturbative action, one begins by
 transforming from Cartesian coordinates to light cone coordinates,

### 2023-09-22 notes/2loopNLSM.tex
fixed BEL appendix

@@
 One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
-\begin{align}
+\begin{align} \label{YZCut1}
 A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
 \\
-&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
+&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...) \label{YZCut2}
 \end{align}
@@
 \begin{equation}
-N^{n\text{-gon},YZ}_{(12...n)} = \langle T^{1}T^{2}\cdots T^{n}\rangle+ \rangle F^1F^2\cdots F^n\rangle
-\end{equation}
-where $(\,\cdots)$ indicates an internal contraction over the $YY$ and
+N^{n\text{-gon},YZ}_{(12...n)} = \langle T^{1}T^{2}\cdots T^{n}\rangle+ \langle F^1F^2\cdots F^n\rangle
+\end{equation}
+where $\langle\,\cdots\rangle$ indicates an internal contraction over the $YY$ and
 $\bar{Z}Z$ loops. Plugging in the Feynman rule of
@@
 \begin{equation}
-N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n)
-\end{equation}
-and similarly so for the internal vector contribution:
-\begin{equation}
- (F^1F^2\cdots F^n) = D (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n) + \mathcal{O}(D^0)
+N_{(12...n)}^{\text{NLSM}}=\langle T^{1}T^{2}\cdots T^{n}\rangle =2^n (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n)
+\end{equation}
+which is what we found in the text.
+Similarly, there is a pure vector contribution that is identical to the semi-abelian YM $n$-gon numerator that we constructed in \cref{SDYMnGon} after projecting external states along longitudinal modes $\varepsilon \rightarrow k$:
+\begin{equation}
+ \langle F^1F^2\cdots F^n \rangle= D (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n) + \mathcal{O}(D^0)
 \end{equation}
@@
 \textit{does} manifest the duality globally, and satisfies all the
-desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory
-compute one-loop color-dual numerators consistent with NLSM cuts, we
-must add some additional states to cancel off he spurious poles, while
+desired pion cuts due to the factorization of \cref{YZCut1} and \cref{YZCut2}. In order for the Feynman rules for $Y\!Z$ theory
+compute one-loop color-dual numerators consistent with NLSM cuts, one would have to add some additional states to cancel off he spurious poles, while
 preserving color-kinematics duality. We leave this as a direction of
@@
 
-While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $Y\!Z$ loop alone gives us a desired expression for the $n$-gon.
-The important takeaway is that we now have a guess for the form of the off-shell three-point vertex that has a chance of manifesting the duality off-shell.
-The $n$-gon numerator above has scalar insertions of the following kinematic vertex:
-\begin{equation}
-T^{a}_{LR} = k_a(\ell_L-\ell_{R}) = (\ell_L+\ell_{R}) (\ell_L-\ell_{R})  = \ell_L^2-\ell_{R}^2 
-\end{equation}
-Given this structure, in the next section we will attempt to construct two-loop basis diagrams from these cubic vertex assignments and try to reverse engineer the particle content that produces these master numerators.
-
-Before proceeding, we note a strange property of the $n$-gon numerator for the pions.
-In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs).
-However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble.
+While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $\bar{Y}Y$ loop alone gives us a desired expression for the $n$-gon.
+However, as we noted in the text, the $n$-gon numerator have the strange property that they produce \textit{non-vanishing} values for bubbles on external legs (BELs).
+However through direct integration of the BEL integrand, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble.
 The BEL diagram can be reconstructed from the $n$-gon as follows:
 \begin{equation}
-N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,\ell)}-N^{\text{NLSM}}_{(1243,\ell)}-N^{\text{NLSM}}_{(1342,\ell)}+N^{\text{NLSM}}_{(1432,\ell)}
-\end{equation}
-where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $\ell_i$, we obtain the following expression for the BEL
-\begin{equation}
-N^{\text{BEL}}_{1|2,34} = s_{12} (\ell+k_1)^2 \ell^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
+N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234|\ell)}-N^{\text{NLSM}}_{(1243|\ell)}-N^{\text{NLSM}}_{(1342|\ell)}+N^{\text{NLSM}}_{(1432|\ell)}
+\end{equation}
+where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $\ell_i$, we obtain the following expression for the BEL:
+\begin{equation}
+N^{\text{BEL}}_{1|2,34} = s_{12} (\ell+k_1)^2 \ell^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \,.
 \end{equation}

### 2023-09-22 notes/2loopNLSM.tex
Done w readthrough

@@
 
-\usepackage[notcite]{showkeys}
+%\usepackage[notcite]{showkeys}
 \usepackage{tikz-feynman} 
@@
 \begin{equation}
-A(A_1,...,A_n)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}} \sim \sum_a\,[ (\varepsilon k)^{n} (kk)^{-n}]_a\, .
+A(A_1,...,A_n)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}} \sim \sum_a\,[ (\varepsilon k)^{n} (kk)^{-n}]_a
 \end{equation}
 where $[\,\cdots]_a$ are terms with appropriate powers of $(\varepsilon k)$ and $(kk)$.
-As we describe in detail in \cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to extract the $D$-dependent part
+\jm{Should we mention transmutation around here?} As we describe in detail in \cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to extract the $D$-dependent part
 that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional
@@
 off-shell cubic vertices can be written in terms of light cone
-coordinates \cite{Monteiro2011pc}:
-\begin{equation}
-X(p,k) = p_u k_w-p_w k_u
+coordinates \cite{Monteiro2011pc}
+\begin{equation}
+X(p,k) = p_u k_w-p_w k_u.
 \end{equation}
@@
 one-loop. This can be done using the cubic semi-YM vertices of the
-previous section:
+previous section
 \begin{equation} \label{DdimSDYM}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
 \end{equation}
 Plugging in on-shell all-plus helicity states in light-cone gauge will
-yield precisely the 4D SDYM vertex, up to an unphysical phase:
-  \begin{equation}
-  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
- \end{equation}
-where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}.
+yield precisely the 4D SDYM vertex, up to an unphysical phase
+  \begin{equation}
+  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}\, ,
+ \end{equation}
+where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge.
+In the second equality, momentum conservation has been applied to redefine the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$, given in \cref{Conventions}.
+\jm{Did I say this alright?}
 Of course, the form of \cref{DdimSDYM} has the advantage of
 permitting a $D$-dimensional construction of the one-loop
-integrand. Below we provide a four-point example:
-\begin{equation}
-\simplebox = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
-\end{equation}
-where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
-In general, the $n$-gon diagram would be,
+integrand. As an example, the four-point numerator is
+\begin{equation}
+\simplebox = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle \, ,
+\end{equation}
+where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$, on all internal polarizations.
+In general, the $n$-gon diagram is
 \begin{equation}\label{SDYMnGon}
-N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
-\end{equation}
+N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle\, .
+\end{equation}
+Recall that all other numerators can be obtained from the $n$-gon through Jacobi.
 Due to the state-sum of internal loop factors,
@@
   it selects the large $D$ behavior of the integrand.}, we can recover
-the integrand needed for all-plus one-loop amplitudes with an internal
-scalar:
-\begin{equation}
-\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = 2^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
+the integrand needed for the all-plus one-loop amplitudes with an internal
+scalar
+\begin{equation}
+\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = 2^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)\, .
 \end{equation}
@@
 internal vector loop. For more background, we refer the reader to
-\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator:
+\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator
 \begin{equation}\label{NLSMnGon}
-N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =   [12][23]\cdots [n1]
-\end{equation}
-Where we have define the antisymmetric kinematic variable,
-$[ij] = \ell_i^2 - \ell_j^2$, since when plugging on longitudinal
-modes, the $n$-gon can be re-expressed completely in terms of inverse
-propagators, $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$. We have
+N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =   [12][23]\cdots [n1]\, ,
+\end{equation}
+where we have define the antisymmetric kinematic variable,
+$[ij] = \ell_i^2 - \ell_j^2 = 2(k_i \cdot \ell_i)$.
+We have
 verified through 10-point one-loop that this $n$-gon expression is a
@@
 However, one can show that these diagrams integrate to zero for spacetime dimension, $D>2$, and thus can be disregarded as unphysical.
-For the interested reader, in \cref{BELreg} we provide a detailed overview of this dimensional regularization of the BEL diagram.
+For the interested reader, in \cref{BELreg} we provide a detailed overview of this dimensional regularization of the relevant BEL diagram.
 \subsection{Two-loop obstruction}\label{2LoopObstruction}
@@
 states. However, at two-loop when choosing all external $A_\mu$
-states, the amplitude vanishes in semi-YM theory:
-\begin{equation}
-\mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=0
-\end{equation}
+states, the amplitude vanishes in semi-YM theory
+\begin{equation}
+\mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=0,
+\end{equation}
+that is, the theory is one-loop exact.
 In order to produce non-vanishing interactions, we would need to
@@
 Thus, to construct two-loop numerators prescriptively, as we have done at one-loop, would require knowledge of
-the full kinematic algebra for Yang-Mills off-shell. Since this is
-presently unavailable, to approach the problem of two-loop
-construction, we instead employ an ansatz based approach.
+the full kinematic algebra for Yang-Mills off-shell.  Since this is presently unavailable, we will tackle the two-loop integrand using an ansatz approach.
 
@@
 As we have just seen, it is possible to coerce tree numerators into
-1-loop numerators at any multiplicity for pions (and related
-theories), but that these methods cannot be reapplied to generate
-higher-loop numerators.  For pions in particular, the no-go statement
-is only for \emph{one particular representation of the theory} so does
+one-loop numerators at any multiplicity for pions and related
+theories, but that these methods cannot be reapplied to generate
+higher-loop numerators.  For pions in particular, the two-loop no-go statement
+is only for \emph{one particular representation of the theory} so it does
 not completely preclude the existence of a two-loop color-dual
-representation.  We thus turn to the color-dual bootstrap method
+integrand.  We thus turn to the color-dual bootstrap method
 described in \cref{sec:bootstrap} to construct a color-dual
@@
 construction of a color-dual representation of pure YM, extending the
-search space beyond what was covered in Ref.~\cite{Bern:2015ooa}.
-
-Both representations share the same cubic graph basis, and thus their
-defining Jacobi relations lead to the same numerator basis.
-Ignoring tadpoles and BEL graphs, there are 14 cubic four-point two-loop
+search space beyond what was covered in Ref.~\cite{Bern:2015ooa} to include the most general local ansatz.
+
+Both NLSM and YM share the same cubic graph basis, and thus their
+defining Jacobi relations lead to the same graph basis.
+Ignoring tadpole and BEL graphs, there are 14 cubic four-point two-loop
 graphs (see \cref{fig:MaxCuts}) which are related to each other via 21
@@
 \end{equation}
-However, the actual numerator dressings and physical properties
-differ, so we discuss them separately below.
+Obviously, the actual numerator dressings and physical properties
+of the two theories differ, so we discuss them separately below.
 
@@
 graphs can be taken to be
-\jm{This looks beautiful!  Thank you to whoever formatted this.}
 \begin{equation}
@@
 amplitude. In order to manifest the $\mathbb{Z}_2$
-symmetry of NLSM at the integrand level, we require that all
+symmetry of NLSM at the integrand level, we also require that all
 non-pathological cuts containing a three-point vertex (such as the maximal
-cut) vanishes.  Imposing all relevant cuts leaves 765 free parameters
+cut) vanishe.  Imposing all relevant cuts leaves 765 free parameters
 representing the generalized gauge freedom in the answer.
@@
 color-stripped Feynman rule for the vertex is
-$V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where
+$V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu \equiv \langle k_1 k_2 \rangle$ where
 off-shell color-kinematics duality to all orders in perturbation
@@
 sectors is rather subtle.  Only color-ordered amplitudes can be
-defined unambiguously from the Feynman rules.  At four-point, only the
+defined unambiguously from the naive Feynman rules.  At four-point, only the
 alternating sector is free of subtleties and the amplitude for this
@@
 \ee
-where $\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu$ is the color-stripped ZM vertex.
+where, again, $\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu$ is the color-stripped ZM vertex.
 As local functions, the
@@
 kinematics.
-We introduce a proportionality constant $z$ between the numerators of the two theories, $N_\text{NLSM} \vert_{2D} = z ~ N_\text{ZM}$, because we are only interested in how the kinematical structure of $N_\text{ZM}$ can be used to eliminate gauge freedom in $N_\text{NSLM}$.\footnote{Another reason for introducing the parameter $z$ is because the theories are believed to differ at loop level even though they are dual classically in 2D \cite{Nappi:1979ig}.
+We introduce a proportionality constant $z$ between the numerators of the two theories, $N_\text{NLSM} \vert_{2D} = z ~ N_\text{ZM}$, because we are only interested in how the kinematical structure of $N_\text{ZM}$ can be used to eliminate gauge freedom in $N_\text{NSLM}$.\footnote{Another reason for introducing the parameter $z$ is because the ZM and NLSM are believed to differ at loop level even though they are dual classically in 2D \cite{Nappi:1979ig}.
 Once all of the constraints from this section are imposed, $z$ is fixed to $216/565$ where the four-point pion tree amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$.}
@@
 in the single copy conspire to produce the double-copy theory's
-version of linear diffeomorphism invariance: enhanced shift symmetry for special Galilleons, and gauge
+version of linear diffeomorphism invariance: enhanced shift symmetry for special Galilleons and gauge
 invariance of the BI photon and DBIVA supermultiplet \cite{Hinterbichler:2015pqa}.  All
@@
 identifying the double-box and penta-triangle as the
-Jacobi basis graphs and building a the most general ansatz for each of
+Jacobi basis graphs and building the most general ansatz for each of
 their numerators compatible with the assumptions in
@@
 Yang-Mills, each monomial in the local ansatz must consist of five
-Lorentz scalar dot product s instead of the six for NLSM, and each
+Lorentz scalar dot products instead of the six for NLSM, and each
 monomial must be linear in each of the four external gluon
 polarizations.  Thus, the numerator ansatz for both diagrams will be
-built from terms of the form:
+built from terms of the form
 \begin{equation}
@@
 maximal-cut gauge invariance on the two basis diagrams, we reduce the
-number of terms to 2235 for the double-box, and 4133 for the
-penta-triangle.  In Ref.~\cite{Bern:2015ooa}, the unitarity matching
-constraints were imposed using a spanning set of minimal physical
-cuts, shown in \cref{fig:ym-spanning}.  Instead of also directly going
-to the spanning cuts, we work within the framework of the Method of
-Maximal Cuts \cite{Bern:2007ct} in order to identify the simplest cut
-that is in tension with the kinematic Jacobi relations.
+number of terms to 2,235 for the double-box, and 4,133 for the
+penta-triangle.  The minimal set of spanning physical cuts is shown
+in \cref{fig:ym-spanning}, but we choose to work within the framework
+of the method of maximal cuts \cite{Bern:2007ct} in
+order to identify the simplest cut that is in tension with the kinematic
+Jacobi relations.
+Maximal cuts and symmetries must be imposed on the 14 non-pathological
+cubic diagrams shown above in \cref{fig:MaxCuts}.
+Doing so, we are left with AA \jm{We need this number from Alex} total parameters in the unrestricted
+ansatz.
 
@@
   \caption{The three spanning physical unitarity cuts of pure
-    Yang-Mills at 2 loops}
+    Yang-Mills at two loops}
   \label{fig:ym-spanning}
 \end{figure}
-
-Similar to the pion construction in \cref{sec:pions}, we use the
-kinematic Jacobi relations to define the numerators for all cubic
-graphs in terms of the two basis graphs, including allowing nontrivial
-numerators on BEL diagrams.  We will simply avoid imposing constraints
-that directly involve such pathological diagrams.  That again leaves
-us with the 14 non-pathological cubic diagrams shown above in
-\cref{fig:MaxCuts}, on which to impose maximal cuts and symmetries.
-Doing so, we are left with AA total parameters in the unrestricted
-ansatz.
 
@@
 those involving cuts of external Mandelstams, there are 8 cut
-topologies (see \cref{fig:ym-nmc}).  Seven of these next-to-maximal
+topologies (see \cref{fig:ym-nmc}). \jm{Why did we delete the disclaimer about dangling trees?}  Seven of these next-to-maximal
 cuts are consistent with the kinematic Jacobi relations and
@@
 \end{equation*}
-cannot be satisfied by either the ansatz with Jacobi relations and
-symmetries applied.
+cannot be satisfied by the ansatz once Jacobi relations and
+symmetries are applied.
 
@@
 impose the symmetry constraints on each of the three diagrams, leaving
-2761 free parameters on the double-box, 2576 free parameters on the
-crossed-box, and 5040 free paramters on the penta-triangle.  Then
+2,761 free parameters on the double-box, 2,576 free parameters on the
+crossed-box, and 5,040 free paramters on the penta-triangle.  Then
 impose the ``bowtie'' next-to-maximal cut, which in the
@@
 picking states that only restore Bose symmetry in the final amplitude
-(as in NLSM).  All of these theories can be encapsulated in the
+(as in NLSM).  Both of these theories can be encapsulated in the
 semi-abelian YM theory presented in \cref{eq:semiYM} which obscures
@@
 
-In addition to the natural tree-level construction, we found that kinetic mixing
+In addition to the tree-level construction, we found that kinetic mixing
 between the two gauge fields permits globally color-dual one-loop
-integrands, and after plugging in suitable on-shell states, the integrands
-produced by semi-abelian YM correspond are those of SDYM in \cref{SDYMnGon} 
+integrands. After plugging in suitable on-shell states, the integrands
+produced by semi-abelian YM correspond to those of SDYM in \cref{SDYMnGon} 
 and NLSM in \cref{NLSMnGon}.  Due to the
@@
 In \cref{2loopBoot}, we overcame this obstruction by successfully constructing two-loop NLSM numerators with an ansatz based bootstrap.
-However, we found that the same approach fails for two-loop pure Yang-Mills, and pin-pointed the failure point to a particular unitarity cut captured by \cref{chefsKiss}.
+However, we found that the same approach fails for two-loop pure Yang-Mills, and pin-pointed the failure to a particular unitarity cut captured by \cref{chefsKiss}.
 Thus, obtaining a globally color-dual
 integrand beyond one-loop then requires sacrificing more than just Bose
-symmetry, and in this paper we have argued that off-shell locality\footnote{An example of this can already be found in the literature, where locality is relaxed in \cite{Mogull:2015adi} in
+symmetry, and in this paper we have argued that off-shell locality\footnote{An example of this can already be found in the literature, where locality is relaxed in Ref.~\cite{Mogull:2015adi} in
   order to obtain color-dual two-loop integrands with on-shell 4D states.} must
@@
 The archetypal example of non-local quantum operators are string vertex operators with $\alpha'$ corrections.
-These operators promote local tree-level amplitudes to stringy extended objects by integrating over disc integrals of the open string worldsheet:
+These operators promote local tree-level amplitudes to stringy extended objects by integrating over disc integrals of the open string worldsheet
 \be
-\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}\supset t_8 F^4 \int_0^1 dx \,\frac{ x^{\alpha' s_{12}}(1-x)^{\alpha' s_{23}}}{x(1-x)(s_{12}+s_{23})}
+\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}\supset t_8 F^4 \int_0^1 dx \,\frac{ x^{\alpha' s_{12}}(1-x)^{\alpha' s_{23}}}{x(1-x)(s_{12}+s_{23})}\, .
 \ee
-The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure color and kinematic factors \cite{MafraBCJAmplString,Broedel:2013tta,Mafra:2016mcc,Carrasco:2019yyn}.
+The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving color-kinematics duality \cite{MafraBCJAmplString,Broedel:2013tta,Mafra:2016mcc,Carrasco:2019yyn}.
 While introducing some type of worldsheet formulation of color-dual numerators might seem unjustified given the results of this work, our findings certainly suggest that we must do \textit{something} to relax the constraint of off-shell locality, and realize locality only in the limit of
@@
 where $N_s = N_{(12|34)}$, $N_t = N_{(14|23)}$ and $N_u = N_{(13|42)}$. By construction, this functionally symmetric numerator is
-anti-symmetric and obeys the Jacobi identity:
+anti-symmetric and obeys the Jacobi identity
 \begin{equation}\label{nonLocalNum}
-N_{(12|34)}^{\text{YM}} + N_{(13|42)}^{\text{YM}} +N_{(14|23)}^{\text{YM}} = 0
+N_{(12|34)}^{\text{YM}} + N_{(13|42)}^{\text{YM}} +N_{(14|23)}^{\text{YM}} = 0.
 \end{equation}
@@
 the local Feynman rules of \cref{eq:ym-lag}. Evaluating the residue on
-the $s=s_{12} \to 0$ pole we find:
+the $s=s_{12} \to 0$ pole we find
 \begin{align}
@@
 \\
-\text{Res}\left[\frac{N_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
+\text{Res}\left[\frac{N_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} \, ,
 \end{align}
@@
 Plugging these into a cubic graph representation of Yang-Mills, the
-tree level version of \cref{eq:gen-amp}, we find:
+tree level version of \cref{eq:gen-amp}, we find
 \begin{equation}
@@
   = \frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} (2c_s-c_t-c_u)
-  =  \mathcal{A}_{(12|l)}^{\text{YM}}\mathcal{A}_{(-l|34)}^{\text{YM}} 
+  =  \mathcal{A}_{(12|l)}^{\text{YM}}\mathcal{A}_{(-l|34)}^{\text{YM}} \, ,
 \end{equation}
@@
 for all particles. As an organizational principle, pulling out overall
-gauge-invariant factors comes with the added advantage of simplifying
+gauge-invariant factors comes with the added advantage \jm{possibility of?} of simplifying
 a loop-level construction of color-dual numerators for Yang-Mills.
@@
 \subsection{Future Directions}\label{sec:Discussion}
-With an eye towards generalizing this construction for future multi-loop studies, we note that the four-point half-ladder secretly makes use of the color-dual structure of NLSM.
-At four-point, we can construct permutation invariants from the single BCJ basis amplitude of both NLSM and pure YM theory as follows:
+With an eye towards generalizing the non-local construction above to future multi-loop studies, we note that the four-point half-ladder \jm{Of YM?} secretly makes use of the color-dual structure of NLSM.
+At four-point, we can construct permutation invariants from the single BCJ basis amplitude of both NLSM and pure YM theory as follows
 \be
-s t A^{\text{YM}}_{(s,t)} = t_8F^4 \qquad s t A^{\text{NLSM}}_{(s,t)} = s_{12}s_{23}s_{13}
+s t A^{\text{YM}}_{(s,t)} = t_8F^4 \qquad s t A^{\text{NLSM}}_{(s,t)} = s t u\, .
 \ee
-Using this, we can redefine our non-local numerator of \cref{nonLocalNum} in a form that recasts color-dual structure to NLSM, and removes all the vector structure of Yang-Mills as an overall $t_8F^4$ factor:
+\jm{$s$ vs $s_{12}$ in this section?  We need $N^{\text{NLSM}}$ not $A^{\text{NLSM}}$?}
+
+Using this, we can redefine the non-local numerators of \cref{nonLocalNum} so that the vector structure of YM is captured in a permutation invariant prefactor and the kinematic Jacobi identity is entirely due to the NLSM numerators
 \be
-N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s_{12}s_{23}s_{13}} 
+N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s_{12}s_{23}s_{13}} \, .
 \ee
@@
 DE-SC0015910 and by the Alfred P. Sloan
-Foundation. N.H.P. additionally acknowledges the Northwestern
+Foundation. N.H.P. \jm{Do we all need to do this?} additionally acknowledges the Northwestern
 University Amplitudes and Insight group, the Department of Physics and
@@
 theories, Bose symmetry is broken or obscured at the Lagrangian level.
-Since Bose symmetry is broken (and inherit the kinetic mixing
-of semi-abelian YM), these theories require additional interactions to produce color-dual representations beyond one-loop.
+Since Bose symmetry is broken, the ensuing kinetic mixing prevents color-dual representations beyond one-loop without the introduction of additional interactions.
 
@@
 To obtain the Lagrangian for self-dual Yang-Mills from standard Yang-Mills, we apply the
-self-dual condition that equates the non-abelian $SU(N)$ field
+self-duality condition that equates the non-abelian $SU(N)$ field
 strength,
 $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu
-,A_\nu]$, to its dual two-form:
+,A_\nu]$, to its dual two-form,
 \begin{equation}
@@
 Solutions to the self-dual condition automatically satisfy the
-Yang-Mills equation of motion due to the Bianchi identity:
+Yang-Mills equation of motion due to the Bianchi identity,
 \begin{equation}
@@
 transforming from Cartesian coordinates to light cone coordinates,
-$(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, via:
-\begin{equation}
-u = t+x,\quad v=t-x, \quad w = y+iz, \quad \bar{w} = y-iz
-\end{equation}
-which yields the invariant line element:
+$(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, via
+\begin{equation}
+u = t+x,\quad v=t-x, \quad w = y+iz, \quad \bar{w} = y-iz\, ,
+\end{equation}
+which yields the invariant line element,
 \begin{equation}
@@
 Applying this coordinate transformation to the self-dual condition of
-\cref{SDcon}, produces three simple constraint equations:
+\cref{SDcon}, produces three constraint equations on the field strength,
 \begin{align} \label{SDLightCone1}
-F_{uw} &=0\,,
+F_{uw} &=0
 \\
  \label{SDLightCone2}
- F_{uv} &= F_{w\bar{w}}\,,
+ F_{uv} &= F_{w\bar{w}}
 \\
@@
 \end{align}
-Thus, in light-cone gauge, $A_u=0$, we realize the self-dual
-conditions in terms of the gauge field as
+In light-cone gauge, $A_u=0$, we the self-duality condition restricts the gauge field as follows:
 \begin{align}
@@
 \end{align}
-This last constraint is satisfied by writing the gauge field in
-terms of a single degree of freedom which we call $\Psi$:
+The last constraint is satisfied by writing the gauge field in
+terms of a single scalar field $\Psi$ via
 \begin{equation}
   \label{SDDef}
-A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi \,.
+A_v = \frac{1}{2} \partial_w \Psi ~~~ \text{ and } ~~~ A_{\bar{w}} = \frac{1}{2} \partial_u \Psi \,.
 \end{equation}
@@
 Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange
-multiplier, we obtain the following interaction Lagrangian for
+multiplier, we obtain the following Lagrangian for
 self-dual Yang-Mills theory:
@@
 \end{equation}
-The color-ordered ordered cubic Feynman rule for this theory can be
-immediately read off as:
+The color-ordered cubic Feynman rule for this theory can be
+immediately read off as
 \begin{equation}
@@
 In this form, the Lagrangian and Feynman rules are manifestly
-color-dual \textit{off-shell}. We can see the effect \cref{SDcon} had
-on the Feynman rules of the full Yang-Mills Lagrangian: it simply
-decoupled the anti-MHV three-point vertex from the theory, leaving
-only the MHV three-point vertex. Before proceeding, it is important to
+color-dual \textit{off-shell}.
+The effect of \cref{SDcon} on the full YM Lagrangian is to decouple the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
+Before proceeding, it is important to
 note that the mass-dimension of the theory appears to differ from that
@@
 $YZ$-theory of \cite{Cheung:2016prv} is an honest $D$-dimensional theory that captures the
-classical physics of the nonlinear sigma model (NLSM) while
+classical physics of NLSM while
 manifesting the duality between color and kinematics.
@@
 Considering the conjugate nature of the $XZ$ propagator, in this work we make the replacement $X\rightarrow \bar{Z}$.
-Plugging this redefinition of the gauge fields in,, we thus obtain the following Lagrangian up to cubic order in the interactions:
-\begin{equation}
-\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)
-\end{equation}
-The Feynman rules for this Lagrangian are simply:
-\begin{equation}
-\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i (\varepsilon_3 p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{3})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{3})(\varepsilon_1\bar{\varepsilon}_3)
+Plugging in this redefinition of the gauge fields produces the following Lagrangian up to cubic order in the interactions
+\begin{equation}
+\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)\, .
+\end{equation}
+The Feynman rules for this Lagrangian are simply
+\begin{equation}
+\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i (\varepsilon_3 p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{3})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{3})(\varepsilon_1\bar{\varepsilon}_3) \, .
 \end{equation}
@@
 \begin{equation}
-p_a + p_i + p_j =0
-\end{equation}
-The kinematic half-ladder diagrams then takes on the following concise definition:
-\begin{equation}
-n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}
-\end{equation}
-Since there are no pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the chiral current algebra is manifestly cubic.
+p_a + p_i + p_j =0\, .
+\end{equation}
+The kinematic half-ladder diagrams then take on the following concise form
+\begin{equation}
+n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}\, .
+\end{equation}
+Since there are no pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the \jm{kinematic?} chiral current algebra is manifestly cubic.
 Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom.
-They can be defined implicitly below:
-\begin{equation}
-[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}
-\end{equation}
-Given this definition, the Feynman rule associated with kinematic structure constant is simply:
+\jm{I'm a little confused.
+Why are we mentioning this?} They can be defined implicitly through
+\begin{equation}
+[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}\, .
+\end{equation}
+Given this definition, the Feynman rule associated with kinematic structure constant is
 \be\label{eq:FeynmanRuleXZZ}
-i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c) 
+i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c)\, ,
 \end{equation}
 where $p_{ab}=p_a+p_b$ and $\varepsilon$ and $\bar{\varepsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
-The gauge-fixed state sum for this theory is simply:
-\begin{equation}
-\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}
+The gauge-fixed state sum for this theory is simply
+\begin{equation}
+\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}\, .
 \end{equation}
 Notice that the vector state sum is gauge fixed since the $YZ$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$.
-To recover NLSM amplitudes from this these kinematic structure constants at tree-level, we simply plug in the following on-shell polarizations for the $Z$ and $\bar{Z}$ particles:
+Tree-level NLSM amplitudes are recovered from the kinematic structure constants by plugging in
 \be\label{eq:onShellZStates}
@@
 \end{equation}
-where $q^2=0$ is some null reference momentum. With this, we can define tree-level pion scattering in two equivalent ways:
-\begin{equation}
-A^{\text{NLSM}} = A(...,Y,...,Y,...) = A(...,\bar{Z},...) 
+ for the on-shell polarizations for $Z$ and $\bar{Z}$, respectively, where $q^2=0$ is some null reference momentum.
+ The tree-level pion amplitude can then be defined in two equivalent ways,
+\begin{equation}
+\label{eq:TwoNLSMMethods}
+A^{\text{NLSM}} = A(...,Y,...,Y,...) ~~~ \text{ and } ~~~ A^{\text{NLSM}}= A(...,\bar{Z},...) \, ,
 \end{equation}
 where the ellipses denote additional on-shell $Z$-particles.
-Subject to a particular gauge choice, the kinematic numerators in latter definition for pion scattering is equivalent to those $J$-theory, first written down by Cheung and one of the authors \cite{Cheung:2021zvb}.
-In this paradigm, the on-shell $\bar{Z}$ state is equivalent to the root leg appearing in the color-dual $J$-theory numerators.
-
-It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion.
-First we'll start with two $Y$ particles on legs 1 and 4.
+In a suitable gauge, the kinematic numerators in the latter definition for pion scattering are equivalent to those of $J$-theory, where $\bar{Z}$ corresponds to the root leg of $J$-theory \cite{Cheung:2021zvb}.
+
+It is instructive to see how both of the constructions in \cref{eq:TwoNLSMMethods} produce valid tree-level amplitudes for the pion.
+First we will start with $Y$ particles on legs 1 and 4.
 Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
@@
 \\
- n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
+ n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})\, .
 \end{align}
-Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
+Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result,
 \be\label{eq:NLSMYZ4point}
-A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
-\end{equation}
-Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration.
-Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free.
-This produces the following numerators:
+A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}\, .
+\end{equation}
+For the $Z$ and $\bar{Z}$ configuration, the numerators are 
 \begin{align}
@@
 \\
- n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
+ n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}\, ,
 \end{align}
-where we have defined the short hand notation:
-\begin{equation}
-{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
-\end{equation}
-Similarly, we find the following ordered amplitude when plugging in these numerators:
-\begin{equation}
-A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
-\end{equation}
-Plugging in the on-shell polarizatoin of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
-Indeed, this construction is valid to all orders at tree-level.
-One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
+where we have used the shorthand
+\begin{equation}
+{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}\, .
+\end{equation}
+The polarization vector of the $\bar{Z}$ particle has not been contracted into the numerators above, resulting in the free $\mu_1$ index.
+These numerators produce the partial amplitude
+\begin{equation}
+A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}\, .
+\end{equation}
+Plugging in the on-shell polarization of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
+Indeed, this construction is valid to all multiplicity at tree-level.
+One can see this by considering the only two possible factorization channels that contribute to each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut,
 \begin{align} \label{YZCut1}
@@
 \\
-&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...) \label{YZCut2}
+&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...) \, . \label{YZCut2}
 \end{align}
 Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
-As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
+As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell \jm{I'm confused again.}, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
 Given this special property of $YZ$-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
@@
 \subsection{J-theory}
-The construction begins with a first order
-formulation of NLSM in terms of chiral currents, $J^\mu$ \cite{Cheung:2021zvb}, subject to particular constraints. For related formulations of NLSM that do not
+$J$-theory is obtained through a first order reformulation of NLSM in terms of the chiral current \cite{Cheung:2021zvb}.\footnote{For related formulations of NLSM that do not
 treat color-kinematics duality see \cite{Freedman:1980us,
-  Slavnov:1971mz}. The first constraint is that the field strength associated with $J_\mu$ should vanish:
+  Slavnov:1971mz}.} Two constraints are placed on the chiral current.  First, the field strength associated with $J_\mu$ should vanish,
 \begin{equation}
 \label{eq:FieldStrengthJ}
-F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
+F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0\, ,
 \end{equation}
 which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
-The second condition is that the chiral current should be in Lorenz gauge
+The second condition is that the chiral current should be in Lorenz gauge,
 \begin{equation}
 \label{eq:LorenzGaugeJ}
-\partial_\mu J^\mu=0
+\partial_\mu J^\mu=0\, ,
 \end{equation}
@@
 Since both theories are in Lorenz gauge this means that \emph{J-theory and semi-abelian YM are identical}.
-Furthermore, this theory is one-to-one with the observables amplitudes of $YZ$-theory when only considering $Z$$\bar{Z}$ on-shell states.
-As such, the single vertex in this theory is the same as the pure vector vertex of $YZ$ theory in Lorenz gauge, where $\partial_\mu J^\mu = 0$:
-\begin{equation}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)
-\end{equation}
-By calculating an off-shell four-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality, as described in \cref{offShellCK}.
+Furthermore, this theory is one-to-one with the observables amplitudes of $YZ$-theory when only considering on-shell $Z$$\bar{Z}$ states.
+As such, the single vertex in this theory is the same as the pure vector vertex of $YZ$ theory in Lorenz gauge,
+\begin{equation}
+\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)\, .
+\end{equation}
+By calculating an off-shell four-point correlation function it is possible to check that the $J$-theory, or semi-YM theory, Lagrangian automatically satisfies color-kinematics duality, as described in \cref{offShellCK}.
 As might be expected, the kinematic algebra is the diffeomorphism algebra \cite{Cheung:2021zvb}. Note that the different external particles break manifest Bose symmetry.
@@
 (rather than some new field) can be integrated in to obtain the
-Zakharov-Mikhailov (ZM) Lagrangian
+Zakharov-Mikhailov (ZM) Lagrangian,
 \begin{equation}
 \label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
+\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) .
 \end{equation}
@@
 SDYM must be replaced with the correct 2D version.
-However, changing the kinetic term in \cref{cubicCKLag} will have no effect on the Jacobi identity of \cref{jacID}, and thus does not interfere color-kinematics duality.
+However, changing the kinetic term in \cref{cubicCKLag} will have no effect on the Jacobi identity of \cref{jacID}, and thus does not interfere with color-kinematics duality.
 
@@
 \begin{equation}
-\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
-\end{equation}
-Unlike $J$-theory and $YZ$-theory, the vertex is (1) functionally symmetric and (2) the kinematic portion
-of the vertex is completely anti-symmetric:
-\begin{equation}
-\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
-\end{equation}
-This important property is due to momentum conservation alone and does
-not need any additional kinematic constraints to satisfy the duality.
+\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu\, .
+\end{equation}
+Unlike $J$-theory and $YZ$-theory, the color-stripped vertex is functionally antisymmetric on all legs
+\begin{equation}
+\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle \, .
+\end{equation}
+This key property is due to momentum conservation alone.
 To prove off-shell color kinematics duality for any multiplicity and
@@
 
-Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which
-we quote now. The component definition of our spinor bracket that are
-consistent with the conventions above,
+We use the same conventions as Ref.~\cite{jjmcTASI2014}, which
+we quote now. The component-wise definitions of the spinor brackets are
 \begin{align}
@@
 \end{align}
-where the $a_i$ are component values of the four-vector,
+where the $a_i$ are components of the four-vector,
 $k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$,
-one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:
+one can apply the on-shell condition, $k_a^2=k_b^2=0$, to show that
 \begin{equation}
@@
 Four-dimensional polarization dot products with fixed helicity states
-can be mapped as follows:
+are mapped to
 \begin{equation}\label{eq:4DPols}
@@
 carry the same mass dimension for both the angle and square
-brackets. In terms of light-cone coordinates that we employed above in
+brackets. In terms of the light-cone coordinates that we employed in
 \cref{sec:CKLagrangians}, the angles and squares can be rewritten as
-follows:
 \begin{align}
@@
 \\
-[ab] &= \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{\sqrt{a_ub_u}}\,,
+[ab] &= \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{\sqrt{a_ub_u}}\,.
 \end{align}
 The conventions we use in the text where the holomorphic spinor,
-$X(p,k)$, carries extra mass dimension essentially amounts to shifting
-the bracket by the following overall factor:
+$X(p,k)$, carries extra mass dimension amounts to shifting
+the bracket by an overall factor,
 \begin{align}
@@
 \\
-[ab] &\rightarrow \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{a_ub_u}\equiv Q(a,b)\,,
+[ab] &\rightarrow \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{a_ub_u}\equiv Q(a,b)\, .
 \end{align}
-With this, we still obtain the same completeness relation for the SDYM spinors:
-\begin{equation}
-X(a,b)Q(b,a) = \frac{1}{2}s_{ab}
-\end{equation}
+With this choice we still obtain the same completeness relation for the SDYM spinors,
+\begin{equation}
+X(a,b)Q(b,a) = \frac{1}{2}s_{ab}\, .
+\end{equation}
+
 \section{Regulating BEL integrals}\label{BELreg}
-At one-loop, weight counting tells us that the $n$-gon master
+This appendix covers the bubble-on-external-leg (BEL) integrals that result from the $n$-gon numerator of $Y\!Z$ theory.
+Before covering the BEL integrals themselves, we will need the appropriate numerator.
+Weight counting tells us that the $n$-gon master
 numerator must have $n$ on-shell $Z$-particles. Unitarity requires
-that there are three distinct contributions from $Y\!Z$ theory -- the
-first from an off-shell $Y$-loop particle and then two more from
+that there are three distinct contributions to the $n$-gon: one from an off-shell $Y$-loop particle and then two more from
 different orientations of a $\bar{Z}Z$-loop.  Thus, $YZ$ theory gives
@@
 where $\langle\,\cdots\rangle$ indicates an internal contraction over the $YY$ and
-$\bar{Z}Z$ loops. Plugging in the Feynman rule of
-\cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily
-obtain expressions in terms of the internal loop factors $\ell_i$ and the
-external momenta $k_i$ (we define the $\ell_i$ loop momentum as that
-flowing into $k_i$ and out of $k_{i-1}$):
+$\bar{Z}Z$ loops and $T$ and $F$ were given in \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, respectively.
+In terms of the external momenta $k_i$ and the loop momenta $\ell_i$, where $\ell_i$ flows into $k_i$ and out of $k_{i-1}$, the NLSM numerator is
 \begin{equation}
@@
 \end{equation}
-which is what we found in the text.
-Similarly, there is a pure vector contribution that is identical to the semi-abelian YM $n$-gon numerator that we constructed in \cref{SDYMnGon} after projecting external states along longitudinal modes $\varepsilon \rightarrow k$:
-\begin{equation}
- \langle F^1F^2\cdots F^n \rangle= D (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n) + \mathcal{O}(D^0)
-\end{equation}
-The dimension dependent factor essentially counts that number of
+which is the same as \cref{NLSMnGon} after using $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$.
+Similarly, there is a pure vector contribution that is identical to the semi-abelian YM $n$-gon numerator that we constructed in \cref{SDYMnGon} after projecting external states along longitudinal modes $\varepsilon \rightarrow k$,
+\begin{equation}
+ \langle F^1F^2\cdots F^n \rangle= D (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n) + \mathcal{O}(D^0)\, .
+\end{equation}
+The dimension-dependent factor essentially counts that number of
 internal vector states. While this $n$-gon is manifestly color-dual,
@@
 desired pion cuts due to the factorization of \cref{YZCut1} and \cref{YZCut2}. In order for the Feynman rules for $Y\!Z$ theory
-compute one-loop color-dual numerators consistent with NLSM cuts, one would have to add some additional states to cancel off he spurious poles, while
+compute one-loop color-dual numerators consistent with NLSM cuts, one would have to add additional states to cancel off the spurious poles, while
 preserving color-kinematics duality. We leave this as a direction of
@@
 
-While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $\bar{Y}Y$ loop alone gives us a desired expression for the $n$-gon.
-However, as we noted in the text, the $n$-gon numerator have the strange property that they produce \textit{non-vanishing} values for bubbles on external legs (BELs).
-However through direct integration of the BEL integrand, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble.
-The BEL diagram can be reconstructed from the $n$-gon as follows:
-\begin{equation}
-N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234|\ell)}-N^{\text{NLSM}}_{(1243|\ell)}-N^{\text{NLSM}}_{(1342|\ell)}+N^{\text{NLSM}}_{(1432|\ell)}
-\end{equation}
-where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $\ell_i$, we obtain the following expression for the BEL:
+While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $\bar{Y}Y$ loop alone gives us the desired expression for the $n$-gon.
+However, as we noted in the text, the $n$-gon numerator has the strange property that it produces \textit{non-vanishing} bubble-on-external-leg (BEL) graphs.
+However, the BEL diagram integrates to zero after integral reduction.
+As an example, the four-point BEL diagram can be reconstructed from the $n$-gon,
+\begin{equation}
+N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234|\ell)}-N^{\text{NLSM}}_{(1243|\ell)}-N^{\text{NLSM}}_{(1342|\ell)}+N^{\text{NLSM}}_{(1432|\ell)}\, ,
+\end{equation}
+where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $\ell_i$, the BEL reduces to
 \begin{equation}
@@
 \end{equation}
-Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
-\begin{equation}
-\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D \ell}{i\pi^{D/2}} \frac{\ell^\mu }{\ell^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
-\end{equation}
-where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$.
+Notice there is an overall factor that cancels one of the propagators. Plugging this numerator into the amplitude produces an integral of the form
+\begin{equation}
+\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D \ell}{i\pi^{D/2}} \frac{\ell^\mu }{\ell^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}\, ,
+\end{equation}
+where we have introduced a mass regulator that will be proportional to the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$.
 Thus, in sufficiently large dimension, $D>2$, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.

### 2023-09-22 notes/2loopNLSM.tex
small change

--- 2023-09-22 notes/2loopNLSM.tex
@@
 Thus we have identified the minimal failure state for a
-globally-color-dual two-loop Yang-Mills representation: locality,
+globally-color-dual two-loop Yang-Mills representation: off-shell locality,
 symmetry, and the kinematic Jacobi relations for just three diagrams
@@
 It would be interesting if a similar construction as our tree-level example could be uplifted to two-loop using the globally color-dual NLSM integrand that we have computed in this work.
-We see this as a natural future direction worth investigating that is made possible given our findings.
+We see this as a natural future direction worth investigating that is now made possible by our findings.
 

### 2023-09-22 notes/2loopNLSM.tex
fixed numerators in text

@@
 As written, the theory will be color dual if the off-shell cubic vertex is antisymmetric and satisfies the Jacobi identity.
-\jm{We're talking about kinematic numerators but using $V$s.
-Should $V$ be swapped with $W$?
-If we do swap them then we need to swap $a$ with $\mu$ too.}
 Specifically,
 \begin{align}
-\text{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0
-\\
-\text{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\label{jacID}
+\text{anti-symmetry}:& \quad{}_{\mu_1}\langle W^{\mu_2} \rangle_{\mu_3}+\text{cyc}(23)=0
+\\
+\text{Jacobi identity}:& \quad {}_{\mu_1}\langle W^{\mu_2} W^{\mu_3}\rangle_{\mu_4}+\text{cyc}(234)=0\label{jacID}
 \end{align}
-where, using the Feynman rules of \cref{CKFrules}, the bracketed expression is the half-ladder numerator \jm{Color factor?} of the following diagram,
-\begin{align}
-{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} &\equiv V^{a_1 a_2 b_1} V^{b_1 a_3 b_2} ...V^{b_{n-3} a_{n-1} a_n}\\
-&= C\left[\halfLadder\right]\,,
-\end{align}
-and likewise for the $W^{\mu \nu \rho}$ dressing.
+where, using the Feynman rules of \cref{CKFrules}, the bracketed expression is the half-ladder numerator of the following diagram,
+\be
+{}_{\mu_1}\langle W^{\mu_2}W^{\mu_3}\cdots W^{\mu_{n-1}} \rangle_{\mu_n} = N\left[\halfLadder\right]\,,
+\ee
+and likewise for the $V^{abc}$ dressing.
 Off-shell descriptions of

### 2023-09-22 notes/2loopNLSM.tex
edits

@@
 \be
-{}_{\mu_1}\langle W^{\mu_2}W^{\mu_3}\cdots W^{\mu_{n-1}} \rangle_{\mu_n} = N\left[\halfLadder\right]\,,
+{}_{\mu_1}\langle W^{\mu_2}W^{\mu_3}\cdots W^{\mu_{n-1}} \rangle_{\mu_n} = N\left[\halfLadderKinetic\right]\,,
 \ee
@@
 \ee
-We direct the reader to ref.~\cite{Pavao:2022kog} for further details. By a simple mass-dimension argument \cite{ElvangHuangReview}, we know the tree-level cubic sector of Yang-Mills must be at
+We direct the reader to ref.~\cite{Pavao:2022kog} for further details.
+The expansion of \cref{eq:pureVecRABD} comes with the added advantage of making the unifying relations of \cite{Cheung:2017ems} absolutely manifest.
+By a simple mass-dimension argument \cite{ElvangHuangReview}, we know the tree-level cubic sector of Yang-Mills must be at
 $\mathcal{O}((\varepsilon\varepsilon)^1)$,
@@
 SDYM) and one-minus at tree-level or by plugging in the on-shell states of $J$-theory \cite{Cheung:2020djz,Cheung:2021zvb} and
-$YZ$-theory \cite{Cheung:2016prv}. Indeed, semi-YM is just the following blocks
+$YZ$-theory \cite{Cheung:2016prv}. Indeed, semi-YM is just the following building blocks
 in the expansion of Yang-Mills given in Ref.~\cite{Pavao:2022kog}

### 2023-09-22 notes/2loopNLSM.tex
edits with James

@@
 As an example, the result of such a calculation for four-point NLSM scattering at tree level produces the numerators
-\begin{align}
-&N_s = s(t-u)\\
-&N_t = t(u-s)\\
-&N_u = u(s-t)
+\begin{align}\label{pionNums}
+&N^{\text{NLSM}}_s = s(t-u)\\
+&N^{\text{NLSM}}_t = t(u-s)\\
+&N^{\text{NLSM}}_u = u(s-t)
 \end{align}
@@
 We direct the reader to ref.~\cite{Pavao:2022kog} for further details.
-The expansion of \cref{eq:pureVecRABD} comes with the added advantage of making the unifying relations of \cite{Cheung:2017ems} absolutely manifest.
+The expansion of \cref{eq:pureVecRABD} comes with the added advantage of making the transmutation relations of \cite{Cheung:2017ems} absolutely manifest.
 By a simple mass-dimension argument \cite{ElvangHuangReview}, we know the tree-level cubic sector of Yang-Mills must be at
@@
 where $[\,\cdots]_a$ are terms with appropriate powers of $(\varepsilon k)$ and $(kk)$.
-\jm{Should we mention transmutation around here?} As we describe in detail in \cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to extract the $D$-dependent part
+As we describe in detail in \cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to extract the $D$-dependent part
 that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional
@@
 where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge.
-In the second equality, momentum conservation has been applied to redefine the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$, given in \cref{Conventions}.
-\jm{Did I say this alright?}
+In the second equality, momentum conservation has been applied to the redefined the spinor bracket, $\langle 12\rangle \rightarrow X(k_1,k_2)$, whose definition is given in \cref{Conventions}.
 Of course, the form of \cref{DdimSDYM} has the advantage of
@@
 The numerators of the two basis graphs are
-\jm{I think I can simplify these numerators a little.  I'll work on it.  I like having them here to break up the text block a little.}
 \be
@@
 Jacobi relations.
-Maximal cuts and symmetries must be imposed on the 14 non-pathological
+Maximal cuts and symmetries are then imposed on the 14 non-pathological
 cubic diagrams shown above in \cref{fig:MaxCuts}.
-Doing so, we are left with AA \jm{We need this number from Alex} total parameters in the unrestricted
-ansatz.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%Doing so, we are left with AA \jm{We need this number from Alex} total parameters in the unrestricted
+%%%ansatz.
+
+%Return to this is give exactly numbers in place of AA!!!
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \cref{eq:other-path}.  After discarding these types of cuts as well as
-those involving cuts of external Mandelstams, there are 8 cut
-topologies (see \cref{fig:ym-nmc}). \jm{Why did we delete the disclaimer about dangling trees?}  Seven of these next-to-maximal
+those involving cuts of external Mandelstams, there are 8 one-particle-irreducible cut
+topologies (see \cref{fig:ym-nmc}). Seven of these next-to-maximal
 cuts are consistent with the kinematic Jacobi relations and
@@
 for all particles. As an organizational principle, pulling out overall
-gauge-invariant factors comes with the added advantage \jm{possibility of?} of simplifying
+gauge-invariant factors comes with the added advantage of possibly simplifying
 a loop-level construction of color-dual numerators for Yang-Mills.
@@
 \subsection{Future Directions}\label{sec:Discussion}
-With an eye towards generalizing the non-local construction above to future multi-loop studies, we note that the four-point half-ladder \jm{Of YM?} secretly makes use of the color-dual structure of NLSM.
+With an eye towards generalizing the non-local construction above to future multi-loop studies, we note that the four-point half-ladder of Yang-Mills secretly makes use of the color-dual structure of NLSM.
 At four-point, we can construct permutation invariants from the single BCJ basis amplitude of both NLSM and pure YM theory as follows
@@
 \ee
-\jm{$s$ vs $s_{12}$ in this section?  We need $N^{\text{NLSM}}$ not $A^{\text{NLSM}}$?}
-
 Using this, we can redefine the non-local numerators of \cref{nonLocalNum} so that the vector structure of YM is captured in a permutation invariant prefactor and the kinematic Jacobi identity is entirely due to the NLSM numerators
 \be
-N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s_{12}s_{23}s_{13}} \, .
+N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s t u } \, .
 \ee
+where four-point pion numerator, $N_s^{\text{NLSM}}$, is given in \cref{pionNums}.
 One advantage of this construction is that it reduces some of the $D$-dimensional complexity of vector theories that arises due to the mixing between external polarization and
@@
 DE-SC0015910 and by the Alfred P. Sloan
-Foundation. N.H.P. \jm{Do we all need to do this?} additionally acknowledges the Northwestern
+Foundation. N.H.P. additionally acknowledges the Northwestern
 University Amplitudes and Insight group, the Department of Physics and
@@
 \end{equation}
-Note that the pure vector vertex on the left is \textit{exactly} what was obtain from semi-abelian YM in \cref{eq:semiYM}.
-Using this, we review of the construction of NLSM numerators at tree-level.
-In this construction, we can define generators of the kinematic algebra as follows
+Note that the pure vector vertex on the right is \textit{exactly} what was obtain from semi-abelian YM in \cref{eq:semiYM}.
+We now review of the construction of NLSM numerators at tree-level from $YZ$-theory.
+In this construction, we can define $D$-dimensional generators of the kinematic algebra as follows,
 \be\label{eq:FeynmanRuleYYZ}
-T^a_{ij}= i \varepsilon_a(p_i-p_j)
-\end{equation}
-where momentum conservation requires
+T^a_{ij}= i \varepsilon_a(p_i-p_j)\,,
+\end{equation}
+where momentum conservation requires\,,
 \begin{equation}
@@
 \begin{equation}
-n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = (T^{a_1}T^{a_2}\cdots T^{a_n})_{ij}\, .
-\end{equation}
-Since there are no pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the \jm{kinematic?} chiral current algebra is manifestly cubic.
-Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom.
-\jm{I'm a little confused.
-Why are we mentioning this?} They can be defined implicitly through
+n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = {}_i\langle T^{a_1}T^{a_2}\cdots T^{a_n}\rangle_j\, .
+\end{equation}
+Since there are no pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the kinematic algebra is manifestly cubic.
+Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom because there are no quartic vertices.
+They can be defined implicitly through
 \begin{equation}

### 2023-09-22 notes/2loopNLSM.tex
some final edits

@@
 \begin{align}
-n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
-\\
- n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}\, ,
+n^{\bar{Z}Z}_s &= {}_4\langle F^{3}F^{2}\rangle_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
+\\
+ n^{\bar{Z}Z}_t &=   {}_2\langle F^{3}F^{4}\rangle_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}\, ,
 \end{align}
@@
 \begin{equation}
-{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}\, .
+{}_x \langle F^{a_1}F^{a_2}\cdots F^{a_n}\rangle _{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}\, .
 \end{equation}
@@
 Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
-As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell \jm{I'm confused again.}, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes.
-Given this special property of $YZ$-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
+As long as we plug in valid on-shell states for $Z$ and $\bar{Z}$ from \cref{eq:onShellZStates}, these numerators will produce NLSM ordered amplitudes.
+Given this special property of $YZ$-theory (namely that the $Z\bar{Z}$ and $YY$ constructions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
 This is essentially what $J$-theory does, as we will show below.

### 2023-09-22 notes/2loopNLSM.tex
final edits for ck at one-loop semiYM

@@
 
-\subsection{semi-abelian Yang-Mills theory}\label{semiYM}
+\subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
 As we argued above, if we include factors of
@@
 $\bar{\varepsilon} \rightarrow k$.
-
-As noted above, we can select out can manifestly cubic
+Furthermore, a simple calculation shows that the off-shell four-point correlation function computed from this vertex satisfies the Jacobi identity of \cref{jacID}.
+This ensures that color-kinematics duality holds to all multiplicity at tree-level.
+Moreover, since the number of propagating degrees of freedom in $D$, rather than $D-2$ for gauge-invariant non-abelian vectors, taking a forward limit on the cubic graphs will yield valid color-dual representations at one-loop as well.
+
+As noted above, we can select out the manifestly cubic
 sector of semi-abelian Yang-Mills from the full theory of \cref{eq:ym-lag} by selecting only $(\varepsilon^+\varepsilon^+)$ in light-cone gauge (i.e.
@@
 since as constructed $YZ$-theory matches to NLSM for off-shell
-Y-particles. We now provide explicit expressions for these one-loop amplitudes in the next section.
+$Y$-particles. We now provide explicit expressions for these one-loop amplitudes in the next section.
 
@@
 \end{equation}
-By calculating an off-shell four-point correlation function it is possible to check that the $J$-theory, or semi-YM theory, Lagrangian automatically satisfies color-kinematics duality, as described in \cref{offShellCK}.
+By calculating an off-shell four-point correlation function it is possible to check that the Lagrangians of $J$-theory and semi-YM theory automatically satisfies color-kinematics duality, as described in \cref{offShellCK}.
 As might be expected, the kinematic algebra is the diffeomorphism algebra \cite{Cheung:2021zvb}. Note that the different external particles break manifest Bose symmetry.

### 2023-09-22 notes/2loopNLSM.tex
final push

@@
 SDYM) and one-minus at tree-level or by plugging in the on-shell states of $J$-theory \cite{Cheung:2020djz,Cheung:2021zvb} and
-$YZ$-theory \cite{Cheung:2016prv}. Indeed, semi-YM is just the following building blocks
-in the expansion of Yang-Mills given in Ref.~\cite{Pavao:2022kog}
+$YZ$-theory \cite{Cheung:2016prv}. Indeed, semi-YM is just the following sum over building blocks
+in the expansion of Yang-Mills given in Ref.~\cite{Pavao:2022kog},
 \begin{equation}
@@
 \end{equation}
-and similarly so at one-loop
-\begin{equation}
-A(A_1,...,A_n)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}} \sim \sum_a\,[ (\varepsilon k)^{n} (kk)^{-n}]_a
+and similarly so at one-loop,
+\begin{equation}
+A(A_1,...,A_n)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}} \sim \sum_a\,[ (\varepsilon k)^{n} (kk)^{-n}]_a\,,
 \end{equation}

### 2023-09-25 notes/2loopNLSM.tex
Updated ZM nums

@@
 \cref{eq:GIrelA} to check that the amplitudes are indeed gauge
-invariant when the abelian polarizations are taken to be longitudinal,
+invariant when the \emph{abelian} polarizations are taken to be longitudinal,
 $\bar{\varepsilon} \rightarrow k$.
-Furthermore, a simple calculation shows that the off-shell four-point correlation function computed from this vertex satisfies the Jacobi identity of \cref{jacID}.
-This ensures that color-kinematics duality holds to all multiplicity at tree-level.
-Moreover, since the number of propagating degrees of freedom in $D$, rather than $D-2$ for gauge-invariant non-abelian vectors, taking a forward limit on the cubic graphs will yield valid color-dual representations at one-loop as well.
+Furthermore, a simple calculation shows that the four-point correlation function of this theory satisfies the Jacobi identity of \cref{jacID} \emph{off-shell}.
+This ensures that color-kinematics duality holds to all multiplicity and loop order.
+We also note that semi-YM does not have any ghosts from non-abelian gauge symmetry that could spoil color-kinematics at loop level.
+Due to the Feynman rules of this theory, the amplitudes are non-vanishing only at tree-level and one-loop.
+We demonstrate the implications of this property in \cref{2LoopObstruction}.
 
@@
 The numerators of the two basis graphs are
-\be
-\ZMBasisDoubleBox =\left[\begin{split}
-  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
-\\
-\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
-\end{split}\right]
-\ee
-\be
-\ZMBasisPentaTriangle =\left[\begin{split}
-  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
-\\
-\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
-\end{split}\right]
-\ee
-where, again, $\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu$ is the color-stripped ZM vertex.
+%\left[\begin{split}
+%  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
+%\\
+%\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
+%\end{split}\right]
+%
+%\left[\begin{split}
+%  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
+%\\
+%\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
+%\end{split}\right]
+%
+\begin{align}
+N^{\text{ZM}}\left[ \scalebox{0.75}{\ZMBasisDoubleBox} \right] &=
+\begin{aligned}
+&\langle \ell_1 \ell_2 \rangle \langle k_4 \ell_1 \rangle \langle \ell_2 k_1 \rangle \langle k_3 (\ell_1+k_4)\rangle \\
+& \langle (k_1+\ell_2) k_2 \rangle \langle (\ell_2+k_{12})(\ell_1-k_{12})\rangle
+\end{aligned} \\
+N^{\text{ZM}}\left[ \scalebox{0.75}{\ZMBasisPentaTriangle} \right] &=
+\begin{aligned}
+&\langle \ell_1 \ell_2 \rangle \langle k_4 \ell_1 \rangle \langle \ell_2 k_1 \rangle \langle k_3 (\ell_1+k_4) \rangle \\
+& \langle (k_1-\ell_1) k_2 \rangle \langle (\ell_2+k_1) (\ell_1-k_1)\rangle
+\end{aligned}
+\end{align}
+where $k_{12} = k_1+k_2$ and, again, $\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu$ is the color-stripped ZM vertex.
 As local functions, the

### 2023-09-27 notes/2loopNLSM.tex
Fixed typo Kezhu found

@@
 color-kinematics duality -- both the on-shell and off-shell
-constructions. We then detail a color-dual boostrap approach for
+constructions. We then detail a color-dual bootstrap approach for
 constructing integrands in theories for which the fully off-shell kinematic

### 2023-09-27 notes/2loopNLSM.tex
safety commit

@@
 
-\title{\center  \fontsize{18.8}{20} \selectfont  Towards Globally Color-Dual Multi-Loop Integrands}
+\title{\center  \fontsize{18.8}{20} \selectfont  Globally Color-Dual Multi-Loop Integrands}
 
@@
   provides a prescriptive approach for constructing $D$-dimensional color-dual
-  numerators through one-loop directly from Feynman rules. Consideration of
-  this theory highlights that the lifting from one-loop
-  color-kinematics dual numerators to two loops is just as challenging
-  as the progression from tree-level to one-loop.  As a first step in
-  understanding the two-loop challenge, we construct color-dual
-  two-loop four-point nonlinear sigma model (NLSM) numerators using a
-  $D$-dimensional color-dual bootstrap.  The double-copy of the
-  constructed NLSM numerators with themselves, pure Yang-Mills, and
-  $\mathcal{N}=4$ super-Yang-Mills correctly reproduce the known
-  physical unitarity cuts of special Gallileons, Born-Infeld theory,
-  and Dirac-Born-Infeld-Volkov-Akulov theory, respectively.  These
-  NLSM numerators are in tension with generalizations of our one-loop construction. Using our loop-level bootstrap, we also find that the most general \emph{local} ansatz
-  for two-loop four-point pure Yang-Mills fails to satisfy
-  global color-kinematics duality. We pinpoint the failure to the
+  numerators through one-loop directly from Feynman rules. By a simple weight counting argument, this approach does not further generalize to two-loops.  As a first step in
+  understanding the two-loop challenge, we use a $D$-dimensional color-dual bootstrap to 
+  successfully construct globally color-dual
+  \emph{local} two-loop four-point nonlinear sigma model (NLSM) numerators.  The double-copy of the
+these NLSM numerators with themselves, pure Yang-Mills, and
+  $\mathcal{N}=4$ super-Yang-Mills correctly reproduce the known unitarity constructed integrands 
+  of special Gallileons, Born-Infeld theory,
+  and Dirac-Born-Infeld-Volkov-Akulov theory, respectively. 
+  Applying our loop-level bootstrap, we exhaustively search the space of integrands consistent with point-like interactions and find that two-loop four-point pure Yang-Mills fails to satisfy global color-kinematics duality, completing a search previously initiated in the literature.
+  We pinpoint the failure to the
   bowtie unitarity cut, and discuss a path forward towards \emph{non-local}
@@
 We begin with an overview of color-kinematics duality in
-\cref{background}. We then construct a manifestly color-dual theory in
+\cref{background}, and define the notion of ``globally'' color-dual integrands in \cref{sec:bootstrap}. 
+We then construct a manifestly color-dual theory in
 \cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point
@@
 We were able overcome this barrier by employing a custom
-solver, \texttt{FiniteFieldSolve}, which will be made
-public soon.
+solver, \texttt{FiniteFieldSolve}, which will soon be made
+public.
 
@@
 \begin{split}
-\propFrule{$a,\mu$}{$b,\nu$}{$k \rightarrow $}{} &= \frac{i}{k^2} P_V^{ab}P_W^{\mu\nu}
+\propFrule{$a,\mu$}{$b,\nu$}{$k \rightarrow $}{} &= \frac{i}{k^2} (P_V^{-1})^{ab}(P_W^{-1})^{\mu\nu}
 \\
@@
   that the integrand is expressed in terms of purely cubic diagrams.
-\item \textbf{Graph symmetries}: A diagram's numerators is only a
+\item \textbf{Graph symmetries}: A diagram's numerator is only a
   function of the diagram's topology and labeling.  Furthermore, the
@@
 found in Refs.~\cite{Minahan:1987ha, Bern:2012uf, 
-  Geyer:2015bja,Geyer:2015jch,Edison:2020uzf, Edison:2022jln, Edison:2022smn}. In addition to the
+  Geyer:2015bja,Geyer:2015jch,Edison:2020uzf, Edison:2022jln, Edison:2022smn} and \cref{BELreg}. In addition to the
 BEL cuts, there is a related class of cuts in which
@@
 \begin{equation}\label{NLSMnGon}
-N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =   [12][23]\cdots [n1]\, ,
-\end{equation}
-where we have define the antisymmetric kinematic variable,
-$[ij] = \ell_i^2 - \ell_j^2 = 2(k_i \cdot \ell_i)$.
+N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =   [\![ 12]\!][\![23]\!]\cdots [\![n1]\!]\, ,
+\end{equation}
+where we have defined the antisymmetric kinematic variable,
+$[\![ij]\!] = \ell_i^2 - \ell_j^2 = 2(k_i \cdot \ell_i)$.
 We have
@@
 valid color-dual representation for NLSM.
+Thus, composing the $n$-gon numerators of \cref{SDYMnGon} and \cref{NLSMnGon} would yield $D$-dimensional integrands that project down to the 4D all-plus Born-Infeld one-loop amplitudes studied in Ref.~\cite{Elvang:2020kuj}.
 
@@
 &\langle \ell_1 \ell_2 \rangle \langle k_4 \ell_1 \rangle \langle \ell_2 k_1 \rangle \langle k_3 (\ell_1+k_4)\rangle \\
-& \langle (k_1+\ell_2) k_2 \rangle \langle (\ell_2+k_{12})(\ell_1-k_{12})\rangle
+& \times \langle (k_1+\ell_2) k_2 \rangle \langle (\ell_2+k_{12})(\ell_1-k_{12})\rangle
 \end{aligned} \\
@@
 &\langle \ell_1 \ell_2 \rangle \langle k_4 \ell_1 \rangle \langle \ell_2 k_1 \rangle \langle k_3 (\ell_1+k_4) \rangle \\
-& \langle (k_1-\ell_1) k_2 \rangle \langle (\ell_2+k_1) (\ell_1-k_1)\rangle
+& \times  \langle (k_1-\ell_1) k_2 \rangle \langle (\ell_2+k_1) (\ell_1-k_1)\rangle
 \end{aligned}
@@
 
-%%Doing so, we are left with AA \jm{We need this number from Alex} total parameters in the unrestricted
+%%Doing so, we are left with AA total parameters in the unrestricted
 %%%ansatz.
@@
 
-In fact, we can make the failure extremely precise.  Start with the
-diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
-the double-box, crossed-box, and penta-triangle.  For each of the
-three diagrams, write down the most generic parity-even local ansatz
+In fact, we can make the failure extremely precise. First, start with the
+diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}, which includes
+the double-box, crossed-box, and penta-triangle. Then \emph{without} defining the crossed-box in terms of the other two diagrams, write down the most generic parity-even local ansatz
 involving four polarizations and six momenta (any combination of
-external or loop).  Each ansatz will have 10,010 terms initially.  Next
+external or loop) for each of the three diagrams.  Each ansatz will have 10,010 terms initially.  Next
 impose the symmetry constraints on each of the three diagrams, leaving
 2,761 free parameters on the double-box, 2,576 free parameters on the
-crossed-box, and 5,040 free paramters on the penta-triangle.  Then
+crossed-box, and 5,040 free parameters on the penta-triangle.  Finally
 impose the ``bowtie'' next-to-maximal cut, which in the
-\emph{non-planar} $t$-$u$ color channel only recieves contributions
+\emph{non-planar} $t$-$u$ color channel only receives contributions
 from the double-box
@@
 After imposing this cut, we find that the original Jacobi relation,
-\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
+\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied.
+In other words, the constraints imposed by the single Jacobi relation and the three sets of diagram symmetries conspire in a way that is inconsistent with the ``bowtie'' cut.
+The contrapositive to this surprising result can be summarized in the following diagrammatic statement, which prioritizes the physical unitarity cut:
 \begin{eBox}
@@
 \subsection*{Acknowledgments}
-The authors would like to thank ... for insightful conversations,
-related collaboration, and encouragement throughout the completion of
+The authors would like to thank John Joseph Carrasco, Sasank Chava, Clifford Cheung, Kezhu Guo, Nia Robles, Aslan Seifi, Fei Teng, and Suna Zekio\u{g}lu for insightful conversations,
+feedback on earlier drafts, and encouragement throughout the completion of
 this work. This work was supported by the DOE under contract
 DE-SC0015910 and by the Alfred P. Sloan
-Foundation. N.H.P. additionally acknowledges the Northwestern
+Foundation. Additionally we would like to acknowledge the Northwestern
 University Amplitudes and Insight group, the Department of Physics and

### 2023-09-27 notes/2loopNLSM.tex
rest of edits

@@
 
-\title{\center  \fontsize{18.8}{20} \selectfont  Globally Color-Dual Multi-Loop Integrands}
+\title{\center  \fontsize{18}{20} \selectfont  Revealing the Landscape of Globally Color-Dual Multi-loop Integrands}
 
@@
   and Dirac-Born-Infeld-Volkov-Akulov theory, respectively. 
-  Applying our loop-level bootstrap, we exhaustively search the space of integrands consistent with point-like interactions and find that two-loop four-point pure Yang-Mills fails to satisfy global color-kinematics duality, completing a search previously initiated in the literature.
+  Applying our bootstrap to two-loop four-point pure Yang-Mills, we exhaustively search the space of local numerators and find that it fails to satisfy global color-kinematics duality, completing a search previously initiated in the literature.
   We pinpoint the failure to the
@@
 we omit the four-point Yang-Mills vertex, then we only need terms that
-contribute to the manifestly color-dual cubic sector of the theory.
-
-We can achieve this construction by splitting the gauge group of the
-full Yang-Mills action from $G$ to $G_L \times G_R$, where the full
-non-abelian gauge symmetry is restored only when we identify
-$G_L = G_R$. However, if we break the left gauge group down to
-$G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to
-$G_R \rightarrow U(N)$, then we are left with a semi-abelian theory
-that is gauge invariant in the preferred $U(1)$-directions. We call
+contribute to the manifestly color-dual cubic sector of the theory. We call
 this manifestly color-dual theory \textit{semi-abelian Yang-Mills},
@@
 \end{equation}
-and $A_\mu$ is in Lorenz gauge.
+and $A_\mu$ is in Lorenz gauge. We can construct this Lagrangian from \cref{eq:ym-lag} by keeping the right field strength covariant under
+$U(N)$, and making the left field strength gauge covariant under
+$U(1)^{N^2}$.
+Note that since $U(1)$ covariance is identical to $U(1)$ invariance, the amplitudes of this semi-abelian theory vanish under $\bar{\varepsilon}(k) \rightarrow k$, where $\bar{\varepsilon}$ is the polarization of an external $\bar{A}_\mu$ vector.
+
 Here we can think of the abelian vector as a background field that

### 2023-09-27 notes/2loopNLSM.tex
Orcid insertions and 4.9 rescaling.
Added YM note.

@@
 \usepackage{cleveref}
+\usepackage{orcidlink}
 \usepackage[normalem]{ulem}
@@
 
-\author{\large Alex Edison,}
-\author{\large James Mangan,}
-\author{\large and Nicolas H. Pavao}
+\author{\large Alex Edison \orcidlink{0000-0002-5430-9500},}
+\author{\large James Mangan  \orcidlink{0000-0002-9713-7446},}
+\author{\large and Nicolas H. Pavao \orcidlink{0000-0002-9817-8266}}
 
@@
 \\
-pavao@u.northwestern.edu}
+pavao@u.northwestern.edu }
 
@@
 number of terms to 2,235 for the double-box, and 4,133 for the
-penta-triangle.  The minimal set of spanning physical cuts is shown
-in \cref{fig:ym-spanning}, but we choose to work within the framework
-of the method of maximal cuts \cite{Bern:2007ct} in
-order to identify the simplest cut that is in tension with the kinematic
-Jacobi relations.
-Maximal cuts and symmetries are then imposed on the 14 non-pathological
-cubic diagrams shown above in \cref{fig:MaxCuts}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%Doing so, we are left with AA total parameters in the unrestricted
-%%%ansatz.
-
-%Return to this is give exactly numbers in place of AA!!!
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+penta-triangle.  The minimal set of spanning physical cuts is shown in
+\cref{fig:ym-spanning}, but we choose to work within the framework of
+the method of maximal cuts \cite{Bern:2007ct} in order to identify the
+simplest cut that is in tension with the kinematic Jacobi relations.
+Maximal cuts and symmetries are then imposed on the 14
+non-pathological cubic diagrams shown above in \cref{fig:MaxCuts}.
+Doing so, we are left with 596 total parameters in the ansatz.
 
@@
 \begin{equation}\label{chefsKiss}
-   \NMCutC
-  \Rightarrow
-  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
+   \scalebox{0.9}{\NMCutC} \!\!
+  \Rightarrow \!\!
+  \scalebox{0.85}{\JacobiOneDoubleBox}
+  +  \scalebox{0.85}{\JacobiOneCrossedBox}
+  + \scalebox{0.85}{\JacobiOnePentaTriangle} \neq 0 \,.
 \end{equation}

### 2023-09-27 notes/2loopNLSM.tex
All non-functional comments removed.
Two main comment blocks remain: the tikz-externalize block, and the emacs/auctex options block.

@@
 \usepackage[dvipsnames]{xcolor}
-%\usepackage{hyperref}
 \usepackage{xspace}
@@
 
-%\usepackage[notcite]{showkeys}
 \usepackage{tikz-feynman} 
@@
 \colorlet{refl-color}{nhp4}
-
-%Comment commands
-\newcommand{\ace}[1]{\textcolor{darkgreen}{\textbf{AE:}{ #1}}}
-\newcommand{\nhp}[1]{\textcolor{nhpRed}{\textbf{NHP:}{#1}}}
-\newcommand{\jm}[1]{\textcolor{blue}{\textbf{JM: }{#1}}}
 
@@
 \newcommand{\forr}{\ , \quad \text{for}  \quad}
-\newcommand{\ansatze}{ans\"atze} %Because words are hard
-
-%TODO-type commands
-\newcommand{\citepls}[1]{{\bf\color{red}[[Cite Needed: #1]]}}
-\newcommand{\sect}{\textbf{\textcolor{red}{RefSec}}}
+\newcommand{\ansatze}{ans\"atze}
 
@@
 
-%TODO:\\
-%For now, let's put the things we need to check/compute here in the abstract. 
-%\begin{enumerate}
-%\item Settle on $n$ vs $N$ vs $\mathcal{N}$ as the symbol for
- % numerator
-
-%\item \ace{I am starting to get a bit concerned about the overuse of the
-  %phrase ``color-dual''} \nhp{We all choose capital $N$}
-%\item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
-   % , \textcolor{cut-color}{\texttt{cut-color}},
-  %  \textcolor{refl-color}{\texttt{refl-color}}, and
-  %  \textcolor{jacobi-color}{\texttt{jacobi-color}} as aliases for
-  %  other colors so that we don't have to keep changing colors in
-   % multiple locations when we want to change diagram color schemes.
-    %I think I have updated all of the diagrams to use the
-  %  correctly-named color, but haven't changed any of the backing
-   % colors for the names.}
-%\end{enumerate}
 }
@@
 globally color-dual integrands at generic loop order.
-
-%Why DC is cool:
-%1) Reduction in computational complexity.
-%Off-shell high spin is terrible.
-%Gravity has infinitely many very complex Feynman rules as a result of gauge redundancy but YM only has two relatively simple Feynman rules.
-%2) DC points to deep structure hidden in Lagrangian formulation.
 
@@
 the double box, crossed box, and penta-triangle are related to each
-other as follows \be % [[11]]
+other as follows
+\begin{equation}
 \label{eq:TwoLoopJacobiOne}
@@
 basis elements to themselves.  For example, the crossed box numerator
-is related to itself via the following Jacobi relation \be % [[19]]
+is related to itself via the following Jacobi relation
+\begin{equation}
 \label{eq:TwoLoopJacobiTwo}
@@
 \end{equation}
-% \ace{is there a reason we commented out this diagram?} \jm{You can try
- % either one.  I liked the one I left in better.}  For example, the
-%symmetries of the crossed box
-%\begin{equation}
-%\CrossedBoxGraphSym{1}{2}{3}{4}
-%\end{equation}
 which are just functional relabelings of external legs,
@@
 the cut $\delta(\ell^2)$ factors implicit.
-
-%% \jm{Again, I love the colors!
-%%  Would it be possible to add $\ell$ labels to the RHS of
-%5  \cref{eq:example-cut-sum} to show what $\ell_5$, $\ell_6$... are?}
-%%\ace{It is doable, will work on it once our text is a bit more happy}
 
@@
 (mid1) --[ultra thick,](a3),
-%(mid1) --[ultra thick,](mid3),
 (mid1) --[ultra thick,out=60,in=120,min distance=0.4cm](mid3),
@@
 where $k_{ij}$ means $k_i \cdot k_j$, $k_5=\ell_1$, and $k_6 = \ell_2$.
-%%%%
-% Basis for both diagrams
-% {d[p[1], p[3]], d[p[1], p[6]], d[p[1], p[7]], d[p[2], p[3]],  d[p[2], p[6]], d[p[2], p[7]], d[p[3], p[6]], d[p[3], p[7]],  d[p[6], p[6]], d[p[6], p[7]], d[p[7], p[7]]}
-%%%%
 Every vertex in NLSM scales as $k^2$ so the numerator of each diagram
@@
 representing the generalized gauge freedom in the answer.
-
-% It is possible to automatically enforce (or ``bake in'') the double
-% box and penta-triangle max cuts on the ansatz by writing the ansatz
-% in terms of inverse propagators (and remaining irreducible scalar
-% products) and then only keeping terms that involve at least one
-% inverse propagator since those terms will vanish on those max cuts,
-% just as the product of 3pt scalar amplitudes will.  However, for the
-% sake of simplicity we do not take this route.
 
@@
 The numerators of the two basis graphs are
-%\left[\begin{split}
-%  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_2+k_1+k_2) \rangle 
-%\\
-%\langle (l_1+k_3+k_4)(l_2+k_1+k_2) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
-%\end{split}\right]
-%
-%\left[\begin{split}
-%  \langle (l_1+k_4) l_1 \rangle\langle l_1l_2 \rangle\langle l_2 (l_2+k_1) \rangle  \langle (l_2+k_1)(l_1-k_1) \rangle 
-%\\
-%\langle (l_1+k_3+k_4)(l_1-k_1) \rangle\langle (l_1+k_3+k_4)(l_1+k_4) \rangle
-%\end{split}\right]
-%
 \begin{align}
@@
 
-%\paragraph{Acknowledgments}
 \subsection*{Acknowledgments}
@@
 \appendix
-% Wizardry to disable subappendix showing up in TOC
-\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}% This turns off subsections
+\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
 \section{Catalog of color-dual theories}
@@
 Ref.~\cite{Monteiro2011pc} for extracting the kinematic algebra.
-% \begin{equation}
-% \mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
-% \end{equation}
 To obtain the Lagrangian for self-dual Yang-Mills from standard Yang-Mills, we apply the
@@
 \label{eq:ZMJacobi}
-\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
+\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 
 \end{equation}

### 2023-09-27 notes/CSTheory.tex
CS theory edits

--- 2023-09-27 notes/2loopNLSM.tex
@@
 \usepackage{cleveref}
-\usepackage{orcidlink}
 \usepackage[normalem]{ulem}
@@
 
-\author{\large Alex Edison \orcidlink{0000-0002-5430-9500},}
-\author{\large James Mangan  \orcidlink{0000-0002-9713-7446},}
-\author{\large and Nicolas H. Pavao \orcidlink{0000-0002-9817-8266}}
+\author{\large Alex Edison,}
+\author{\large James Mangan,}
+\author{\large and Nicolas H. Pavao}
 
@@
 
-\section{Introduction}\label{intro}
-Since the turn of the century, our understanding of the $S$-matrix and
-its concealed structures has expanded dramatically. At the heart of this
-progress is the mantra that physical observables are simpler when
-studied on-shell
-\cite{Parke:1986gb,TasiLance,Cheung:2017pzi}. However, while inserting on-shell states certainly offers a path towards taming the
-factorial growth of Feynman diagrams, it also obscures the off-shell
-simplicity at the heart of many quantum field theories. A shining
-example of this hidden structure is the duality between color and
-kinematics \cite{BCJ,Bern:2010ue,BCJreview}, which states that the
-kinematic numerators of gauge theory amplitudes can be rearranged to
-obey the same algebraic identities as the constituent color
-factors. When this duality is realized globally off-shell, it
-dramatically decreases the combinatorial complexity posed by integrand
-construction, and offers a path towards efficient assembly of quantum
-gravity integrands directly from simpler gauge theory building blocks
-via the double copy \cite{BCJ,Bern:2010ue}.
-
-Despite the tremendous success in leveraging this duality to
-compute gauge and gravity observables to high orders in perturbation
-theory \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv,
-  Carrasco:2021otn}, color-kinematics remains a conjecture at loop
-level. Indeed, there are many examples in the literature where
-identifying color-dual representations beyond one-loop has posed a
-formidable challenge
-\cite{Mogull:2015adi, Johansson:2017bfl, KalinN2TwoLoop, Bern:2015ooa}. In this work, we use
-the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven
-to permit color-dual representations at tree-level
-\cite{Feng:2010my,Cachazo:2014xea}, as case studies for advancing our
-understanding of the kinematic algebra toward the multi-loop level.
-
-We begin with an overview of color-kinematics duality in
-\cref{background}, and define the notion of ``globally'' color-dual integrands in \cref{sec:bootstrap}. 
-We then construct a manifestly color-dual theory in
-\cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point
-numerators for both NLSM and the self-dual sector of Yang-Mills
-through one-loop. The construction of this theory, which we dub
-\textit{semi-abelian Yang-Mills}, relies on isolating the cubic sector
-of pure Yang-Mills amplitudes from the four-point contacts that are
-needed to fully realize non-abelian gauge symmetry. Despite the
-potency of this theory at one-loop, the construction runs into an
-obstruction at two-loop, which we describe in \cref{2LoopObstruction}.
-
-Faced with this obstruction, we study the multi-loop sector of both
-NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz based
-color-dual bootstrap. In contrast to much of the available literature
-on color-dual integrand construction at two-loop
-\cite{Bern:2013yya,Mogull:2015adi,Johansson:2017bfl}, our results are
-completely agnostic to the spacetime dimension; all the polarizations
-and momenta appearing in our construction will remain formally
-$D$-dimensional. This makes our methods and results particularly well
-suited for algorithmically extracting rational terms from the
-$D$-dependence of dimensionally regulated loop momenta.
-The ansatz approach to constructing numerators generally results in an explosion of terms, but in the case of scalar theories there is an added difficulty because the linear equations become dense.
-We were able overcome this barrier by employing a custom
-solver, \texttt{FiniteFieldSolve}, which will soon be made
-public.
-
-With this solver, we are able to compute a two-loop integrand for NLSM
-that globally manifests the duality off-shell. This represents a new
-benchmark for color-dual representations in non-supersymmetric gauge
-theories.  However in sharp contrast, we find that Yang-Mills does
-\emph{not} permit a globally color-dual representation, even when
-considering the most general polynomial ansatz of Lorentz covariant
-kinematics.\footnote{Globally color-dual local numerators for two-loop
-  pure YM have been studied before but only in the context of a
-  limited ansatz subject to certain loop power counting constraints
-  \cite{Bern:2015ooa}.}  Concretely, the failure point can be
-pinpointed to a conflict between between the ``bowtie'' cut and the
-following Jacobi triple:
-\begin{equation}
-   \NMCutC
-  \Rightarrow
-  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
-\end{equation}
-We comment on the implications of this finding in \cref{conclusions},
-and discuss alternative approaches where one must relax field
-theoretic locality in order to accommodate the construction of
-globally color-dual integrands at generic loop order.
-
-\section{Background}\label{background}
-To set the stage, in this section we provide an overview of
-color-kinematics duality -- both the on-shell and off-shell
-constructions. We then detail a color-dual bootstrap approach for
-constructing integrands in theories for which the fully off-shell kinematic
-algebra has not yet been identified, like Yang-Mills and NLSM.
-\subsection{Color-dual Amplitudes}\label{onShellCK}
-
-Color-kinematics duality is a statement about the off-shell graphical
-simplicity that manifests redundancy in the on-shell observables of
-certain field theories. Ignoring factors of $i$ and the coupling
-constant, the starting point to realize the duality is to express generic $n$-point $L$-loop amplitudes in a cubic graph representation:
-\begin{equation}
-  \mathcal{A}_n^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{C_\Gamma N_\Gamma}{d_\Gamma} .
-  \label{eq:gen-amp}
-\end{equation}
-Here the spacetime dimension is $D$.  Even though the underlying
-theory may have quartic (or higher multiplicity) vertices, like YM and NLSM, it is
-possible to multiply and divide by propagators so that the sum runs
-over the set of purely cubic graphs, $\Gamma$.  Overcounting is removed by
-the internal symmetry factor $S_\Gamma$, which tracks the number of
-graph symmetries with external legs held fixed.
-
-The color factor
-$C_\Gamma$ is the string of structure constants $f^{abc}$ associated
-with the graph $\Gamma$,\footnote{This paper is focused on theories
-  with particles that transform in the adjoint.  However, the double
-  copy can be applied to a far more diverse set of theories with
-  particles that transform in the fundamental or more diverse
-  representations, see for example \cite{Johansson:2017srf,
-    Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2020ywq,Carrasco:2022jxn,
-    Carrasco:2023vjg}.}  the denominator $d_\Gamma$
-is the product of propagators associated with the graph $\Gamma$, and
-the numerator $N_\Gamma$ is all of the remaining kinematic factors
-including dot products of momenta and polarization vectors. In this 
-form the color factors $C_\Gamma$ are not independent and are related to
-one another via a set of Jacobi identities that look schematically
-like
-\begin{equation}
-C_i+C_j+C_k=0,
-\end{equation}
-where $i$, $j$, and $k$ are three graphs.  Example Jacobi relations
-are presented in detail in \cref{sec:bootstrap}. The duality between color and kinematics is the statement that that there exists a way to rearrange factors between
-the various kinematic numerators $N_\Gamma$ such that the numerators
-obey the same Jacobi identities as the color factors
-\begin{equation}
-N_i +N_j +N_k=0.
-\end{equation}
-If color-kinematics duality can be achieved at the off-shell level,
-then the kinematic numerators should satisfy an algebra just like the
-color factors.  In theories where the kinematic algebra is known, it
-is often the algebra of volume preserving diffeomorphisms
-\cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz,
-  Cheung:2021zvb, Cheung:2022mix}.
-When the kinematic algebra is not known explicitly, the kinematic numerators are typically constructed from an ansatz.
-As an example, the result of such a calculation for four-point NLSM scattering at tree level produces the numerators
-\begin{align}\label{pionNums}
-&N^{\text{NLSM}}_s = s(t-u)\\
-&N^{\text{NLSM}}_t = t(u-s)\\
-&N^{\text{NLSM}}_u = u(s-t)
+\section{Chern-Simons Theory}\label{intro}
+The final theory that is unified by semi-abelian Yang-Mills is that Chern-Simons theory.
+As we will show below, plugging in appropriate on-shell states to the semintegrands constructed in the text will produce precisely the kinematic numerators for this theory.
+\begin{align}
+\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} = \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2\varepsilon^{\rho}_3 \qquad  &\Rightarrow  \qquad   \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
+  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
+\\
+\propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho \qquad  &\Rightarrow  \qquad \propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2}= \frac{i}{k^2} \eta^{\mu\nu}
 \end{align}
-where the coupling has been normalized away.  These numerators sum to
-zero by explicit calculation.  Note that the $s$-channel numerator
-contains an explicit factor of $s$ that cancels with the propagator
-and the same goes for the $t$- and $u$-channels.
-The net result is that the amplitude is a local function, just as one would expect for the pion tree
-amplitude.
-
-Once color-dual numerators $N_\Gamma$ have been found, they can be
-used to replace the color factors ($C_\Gamma \to N_\Gamma$) in a
-\emph{different} amplitude to produce the corresponding amplitude in
-a new theory,
-\be\label{DCconstruction}
-\tilde{\mathcal{A}}_n^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
-\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{C_\Gamma
-  \tilde{N}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(C_\Gamma \to N_\Gamma)}
-~~ \mathcal{M}_n^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
-\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{N_\Gamma
-  \tilde{N}_\Gamma}{d_\Gamma}.
-\end{equation}
-This is known as the double-copy construction \cite{BCJ,Bern:2010ue,BCJreview}.
-Importantly, the $\tilde{N}_\Gamma$ do not need to respect
-color-kinematics duality.  The prototypical example of the double-copy
-is that YM double copied with YM results in gravity where the gauge
-invariance of each separate gluon produces the diffeomorphism
-invariance of the graviton.  The double copy can be proven at tree
-level using the Kawai-Lewellen-Tye (KLT) relations but there is significant evidence that
-the double copy persists to all loop orders \cite{FiveLoopN4,
-  GeneralizedDoubleCopyFiveLoops, Bern:2018jmv, Carrasco:2021otn, KLT,
-  KiermaierTalk}.  In addition to pointing at undiscovered
-structure hidden in the Lagrangian for gravity, the double copy is
-immensely useful at a utilitarian level since it is much more
-efficient at producing $\mathcal{M}_n^L$ than traditional methods like
-Feynman rules.
-
-Many of the one-loop results presented in \cref{sec:cubic} are informed
-by the tree-level double-copy so we will review the tree case here.
-The color structure of tree-level amplitudes is particularly simple.
-A fully color dressed tree amplitude $\mathcal{A}_n$ can be decomposed
-in terms of the trace basis
-\begin{equation}
-  \mathcal{A}_n = \sum \limits_{\sigma\in S_{n-1}} \text{Tr}(T^{a_{\sigma_1}} T^{a_{\sigma_2}}...T^{a_{\sigma_{n-1}}} T^{a_n}) A_n[\sigma_1, \sigma_2,...\sigma_{n-1}, n],
-  \label{eq:trace-basis}
-\end{equation}
-where $T^a$ are generators of the gauge group and, because of the
-cyclicity of the trace, one of the legs is held fixed so that the sum
-runs over the $(n-1)!$ permutations of the remaining external legs.
-The coefficients of the color factors are the color-ordered partial
-amplitudes $A_n[...]$.  Any tree-level color factor can be converted
-into a linear combination of Del Duca-Dixon-Maltoni (DDM) half-ladder
-color factors
-\begin{equation}
-\text{DDM}[a_1, a_2,... a_n] \equiv f^{a_1 a_2 b_1} f^{b_1 a_3 b_2} f^{b_2 a_4 b_3}...f^{b_{n-3} a_{n-1} a_n}
-\end{equation}
-associated with the graph
-\begin{equation}
-\halfLadder
-\end{equation}
-by repeated application of the Jacobi identity \cite{DixonMaltoni}.
-The fully color-dressed tree amplitude can then be re-expressed as
-\begin{equation}
-  \mathcal{A}_n = \sum \limits_{\sigma\in S_{n-2}} \text{DDM}[a_1, a_{\sigma_2}, a_{\sigma_3}, a_{\sigma_{n-1}}, a_n]  A_n[1, \sigma_2,...\sigma_{n-1}, n]
-  \label{eq:ddm-basis}
-\end{equation}
-with legs $1$ and $n$ fixed.  Since the the sum only contains $(n-2)!$
-terms, there must be additional relations -- the
-Kleiss-Kuijf (KK) relations \cite{Kleiss:1988ne} -- amongst the
-partial amplitudes appearing in the right-hand side of
-\cref{eq:trace-basis}.  The KK relations are generic to any theory
-with purely adjoint particles.  Color-kinematics duality further
-implies that the KK basis is overcomplete and can be reduced to a
-basis of $(n-3)!$ amplitudes via the fundamental Bern-Carrasco-Johansson (BCJ) identities
-\cite{BCJ,Feng:2010my}
-\begin{equation}
-\sum \limits_{i=2}^{n-1} k_1 \cdot (k_2+...+k_i) A_n[2,...,i,1,i+1,...,n] =0.
-\end{equation}
-In terms of constructing explicit color-dual solutions at tree level,
-it is enough to specify the numerator of the half-ladder because any
-diagram can be reduced to a half-ladder through successive
-applications of the Jacobi identity.  At one-loop, every diagram can be
-related to one topology as well, in this case the $n$-gon, which can be understood as a forward limit of the half-ladder.  Two-loop
-calculations play an important role in our understanding of
-color-kinematics duality because this is the first order where
-multiple basis graphs are required, at least for a generic theory. We refer the reader to \cite{BCJreview} for more background on the topic.
-
-\subsection{Color-dual Lagrangians}\label{offShellCK}
-While the BCJ relations are an on-shell statement about the color-dual
-nature of scattering amplitudes, one might aspire to trivialize
-the duality by encoding it in an off-shell Lagrangian
-of the theory. The double-copy construction of
-\cref{DCconstruction} would suggest a manifestly cubic Lagrangian of
-the form
-\begin{equation}\label{cubicCKLag}
-\mathcal{L} = P_V^{ab}P_W^{\mu\nu}\mathcal{O}^a_\mu \Box \mathcal{O}^b_\nu +  V^{abc} W^{\mu \nu \rho}\mathcal{O}^a_\mu \mathcal{O}^b_\nu \mathcal{O}^c_\rho
-\end{equation}
-where $V^{abc}$ and $W^{\mu \nu \rho}$ are cubic Feynman rules mixing field
-operators $\mathcal{O}^{a}_\mu$ indexed by quantum numbers $a$ and
-$\mu$. The Feynman rules for this theory are simply:
-\be\label{CKFrules}
-\begin{split}
-\propFrule{$a,\mu$}{$b,\nu$}{$k \rightarrow $}{} &= \frac{i}{k^2} (P_V^{-1})^{ab}(P_W^{-1})^{\mu\nu}
-\\
-\cubicFrule{$a,\mu$}{$b,\nu$}{$c,\rho$}{}{}{} &= i V^{abc}W^{\mu \nu \rho}
-\end{split}
-\ee
-We have introduced $P_V^{ab}$ and $P_W^{\mu\nu}$ projection operators
-to encode non-local kinetic structure that could in principle
-participate in the construction, as is the case for $DF^2$ theory \cite{Johansson:2017srf}.
-Generally, these quadratic dressings are simply delta functions, $P_V^{ab} = \delta^{ab}$, or flat space metrics, $P_W^{\mu\nu}=\eta^{\mu\nu}$.
-As written, the theory will be color dual if the off-shell cubic vertex is antisymmetric and satisfies the Jacobi identity.
-Specifically,
-\begin{align}
-\text{anti-symmetry}:& \quad{}_{\mu_1}\langle W^{\mu_2} \rangle_{\mu_3}+\text{cyc}(23)=0
-\\
-\text{Jacobi identity}:& \quad {}_{\mu_1}\langle W^{\mu_2} W^{\mu_3}\rangle_{\mu_4}+\text{cyc}(234)=0\label{jacID}
-\end{align}
-where, using the Feynman rules of \cref{CKFrules}, the bracketed expression is the half-ladder numerator of the following diagram,
-\be
-{}_{\mu_1}\langle W^{\mu_2}W^{\mu_3}\cdots W^{\mu_{n-1}} \rangle_{\mu_n} = N\left[\halfLadderKinetic\right]\,,
-\ee
-and likewise for the $V^{abc}$ dressing.
-Off-shell descriptions of
-color-dual theories are rare, and only a few examples are available in
-the literature \cite{Monteiro2011pc, Cheung:2016prv, Cheung:2021zvb,
-  Cheung:2020djz, Ben-Shahar:2022ixa, Ben-Shahar:2021zww,
-  Ben-Shahar:2021doh}.
-Typically when one goes about constructing color-dual
-theories directly from a set of cubic interactions, higher point
-Jacobi and antisymmetry constraints require introducing additional operators \cite{Carrasco:2022lbm,Carrasco:2022sck} or propagating fields \cite{Ben-Shahar:2022ixa}.
-Indeed, as we will show in \cref{sec:cubic}, Yang-Mills
-requires introducing a cubic two-form interaction in order to manifest
-the kinematic algebra just at four-point. Absent information about the
-kinematic algebra, one can make progress in the construction of
-loop-level color-dual amplitudes by employing a color-dual bootstrap.
-
-\subsection{Color-dual Bootstrap}
-\label{sec:bootstrap}
-
-When an off-shell color-dual Lagrangian is not known, the loop-level
-amplitude integrand must be constructed from an ansatz.  The four
-conditions we impose on an integrand ansatz are summarized here and
-elaborated on below.\footnote{The four ansatz conditions are similar
-  to those of Ref.~\cite{Bern:2015ooa} except that there the authors
-  demand that the numerators have the same loop power counting as
-  Feynman gauge Feynman rules.  This is an additional assumption that
-  is most emphatically not made here.}
-After imposing the four constraints below, any remaining coefficients in the ansatz encode ``generalized gauge freedom'', meaning that the
-choice of coefficients does not affect the physical integrand or its double copy.
-\begin{enumerate}
-\item \textbf{Off-shell Locality}: Diagram numerators are polynomials
-  in momenta and polarizations, e.g., the diagrams only have poles given
-  by the propagators of the diagrams.
-\item \textbf{Color-kinematics duality}: The numerators obey the same
-  Jacobi identities as the color factors.  This implicitly requires
-  that the integrand is expressed in terms of purely cubic diagrams.
-\item \textbf{Graph symmetries}: A diagram's numerator is only a
-  function of the diagram's topology and labeling.  Furthermore, the
-  diagram numerators are invariant under the automorphisms of the
-  diagrams including signs that compensate for color-factor sign
-    changes.
-\item \textbf{On-shell Unitarity}: The cuts of the ansatz must
-  reproduce the physical unitarity cuts of the theory when internal
-  momenta are taken on-shell.
-\end{enumerate}
-
-In order to clarify general statements, the following subsections
-include examples from a four-point two-loop integrand for some generic
-color-dual theory like YM.  This is the simplest case that
-demonstrates the full machinery of the color-dual bootstrap.  All tree
-and one-loop processes are generated by single basis diagrams (the half
-ladder and $n$-gon respectively) so they lack examples of three-term
-``boundary'' Jacobi relations to be described shortly.
-Choosing the four-point two-loop integrand also has the advantage that this
-process appears prominently in this paper.
-
-\paragraph{Off-shell Locality}
-
-The kinematic numerators must be $D$-dimensional, Lorentz invariant,
-local (polynomial) functions of the graph kinematics with the correct
-power counting and external states. Locality is physically motivated since Feynman
-rules produce polynomial numerators. Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of
-kinematics. However, insisting on a local numerator is
-partly a matter of convenience as the ansatz for a rational function
-would quickly grow out of control without a guiding principle for what
-terms to include.  While these
-assumptions are well motivated from a physical and complexity
-standpoint, the literature has featured numerators that violate
-locality, modify naive power counting through the inclusion of higher
-spin modes, and break manifest Lorentz invariance \cite{Square,
-  WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ,
-  Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv,
-  Cheung:2021zvb}.  These developments suggest that relaxing locality
-is a viable alternative when the condition proves too stringent for an
-ansatz.  However, simply requiring on-shell locality may suffice.
-This alternative will be discussed in \cref{nonLocalScattering}.
-
-\paragraph{Color-kinematics duality}
-
-Color-kinematics duality is a statement about color factors, kinematic
-numerators, and the accompanying Jacobi relations.  Adjoint-type color
-factors are associated with cubic graphs, so satisfying
-color-kinematics duality implicitly requires expressing the integrand
-in terms of such graphs. As mentioned earlier, this is possible to do
-even for a theory with quartic (or higher multiplicity) vertices by
-multiplying and dividing by propagators.  In the case of the four-point
-two-loop example promised above, there are 14 cubic graph topologies
-(shown in \cref{fig:MaxCuts}) ignoring tadpoles and bubble on external
-leg (BEL) graphs.
-
-\begin{figure}
-\centering
-{\MCutC, \MCutD, \sumoCut, \MCutJ,  
- \\
-  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
-\\
-\MCutI,  \MCutE, \MCutK, 
-\\
- \MCutL, \MCutG,  \MCutH
-}
-\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
-  \end{figure}
-
-With the integrand expressed in terms of cubic graphs, it is possible
-to discuss the main ingredient in color-kinematics duality -- the
-Jacobi relations.  The color factors in an integrand obey a set of
-Jacobi identities.  Color-kinematics duality states that there
-\emph{exists} a way of writing the kinematic numerators of the
-integrand so that they obey the same set of Jacobi identities.  The
-Jacobi identities can be divided into two categories: \emph{defining}
-relations and \emph{boundary} relations.  Defining Jacobi relations
-can be used to express any graph in terms of a basis.  For example,
-the double box, crossed box, and penta-triangle are related to each
-other as follows
-\begin{equation}
-\label{eq:TwoLoopJacobiOne}
-\JacobiOneDoubleBox + \JacobiOneCrossedBox + \JacobiOnePentaTriangle
-=0\,,
-\end{equation}
-where the shared propagator is shown in red.  Using this relation the
-crossed box can be written (or \emph{defined}) in terms of the other
-two.  In this way, all of the 14 cubic four-point two-loop topologies can be
-written in terms of a basis of the double box and penta-triangle.
-(Any two of the double box, crossed box, and penta-triangle would
-suffice for a basis but the planar basis is chosen for simplicity in
-this work.)  The numerator of each of the two basis graphs receives
-its own ansatz and the numerator of any other graph can be expressed
-in terms of these two.
-
-After using the defining Jacobi relations to relate every graph to the
-basis, any remaining Jacobi relations will be referred to as boundary
-relations.  In other words, boundary relations (indirectly) relate
-basis elements to themselves.  For example, the crossed box numerator
-is related to itself via the following Jacobi relation
-\begin{equation}
-\label{eq:TwoLoopJacobiTwo}
-\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
-\end{equation}
-where the shared propagator is shown in red as before.  Each of the
-crossed box numerators can be written in terms of the double box and
-penta-triangle so this Jacobi relation places constraints on the basis
-numerator \ansatze{}.  While defining Jacobi relations simplify how
-many numerators require \ansatze{}, boundary relations place
-restrictions on those \ansatze{}.  In principle there could be Jacobi
-relations involving tadpoles and BEL graphs, which would be subtle to
-handle.  One option is to force the numerators of these graphs to
-zero.  However, since these graphs will not contribute to physical
-unitarity cuts, we take a different approach.  These graphs are
-allowed to have non-zero numerators but any Jacobi relations involving
-them are simply not imposed or solved.  See Refs.~\cite{Bern:2012uf,
-  Edison:2022jln} and \cref{BELreg} for discussions of BELs in the context of
-color-kinematics duality.
-
-What we have just described is
-sometimes referred to as ``global'' color-kinematics duality because
-the Jacobi identities are solved by a single (global) integrand with
-off-shell internal lines.  In order to perform the double copy it is
-enough to simply satisfy the Jacobi identities on the generalized
-unitarity cuts, meaning that each graph can be assigned its own ansatz
-\cite{Bern:2015ooa}.  If a global solution cannot be found, this is
-one way to enlarge the ansatz, where another option is to incorporate non-local terms in the ``numerators''.  A globally
-color-dual integrand is desirable because of its simplicity and
-because a color-dual Lagrangian would naively produce precisely this
-object.
-
-\paragraph{Graph symmetries}
-
-Every numerator is required to respect all of the symmetries (or
-automorphisms) of its associated graph.  Graph symmetries are an
-avatar of Bose symmetry.  For a pure ansatz construction it is very
-reasonable to impose graph symmetries, but color-kinematics duality at
-tree-level is often achieved at the expense of manifest Bose symmetry
-\cite{Cheung:2016prv, Cheung:2021zvb, Brandhuber:2021bsf,
-  Edison:2020ehu}.  In an ansatz construction graph symmetries are
-imposed for \emph{every} graph, not just the basis graphs.
-For example, the symmetries of the crossed box are spanned by,
-\begin{equation}
-\scalebox{0.8}{\CrossedBoxGraphSym{1}{2}{3}{4}}\!\! \sim\!\! \scalebox{0.8}{\CrossedBoxGraphSym{2}{1}{3}{4}}
-\text{ and }
-\scalebox{0.8}{\CrossedBoxGraphSym{1}{2}{3}{4}} \!\!\sim\!\! \scalebox{0.8}{\CrossedBoxGraphSym{2}{1}{4}{3}}
-\end{equation}
-which are just functional relabelings of external legs,
-$\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.  In general,
-internal edge labels must be tracked as well.  Furthermore, care must
-be taken with the signs in a symmetry relation.  To compensate for the
-antisymmetric color factors, $f^{abc}$, graph vertices are all totally
-antisymmetric and hence have signs built into their orientations.
-When used in conjuction with the Jacobi relations, \eg{}
-\cref{eq:TwoLoopJacobiOne}, the symmetry constraints of non-basis
-graphs still impose conditions on the basis ansatz.  In fact, since
-the symmetry properites of a graph are directly linked with
-transformations of its color dressing, the resulting constraints can
-be thought of as a subclass of the \emph{boundary} Jacobi relations.
-
-\paragraph{On-shell Unitarity}
-
-The final constraints come from ensuring that the ansatz correctly
-reproduces the generalized unitarity cuts of the desired theory, thus
-guaranteeing that the numerators encode the correct physical,
-theory-dependent information.  Generalized unitarity has been
-reviewed in many places
-\cite{BCFUnitarity, Bern:2015ooa, Bourjaily:2017wjl,
-  JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview,
-  Edison:2022jln, Edison:2022smn} and was recently optimized for effective field theories like NLSM \cite{Carrasco:2023qgz}. Generalized unitarity equates products of on-shell tree amplitudes,
-encoded via a graph $\gamma$, to sums over compatible\footnote{A
-  diagram $g$ is compatible with the cut diagram $\gamma$ if $g$ is
-  isomorphic to $\gamma$ or to any of the additional factorization
-  channels of $\gamma$. } diagram numerators evaluated on the support
-of the on-shell conditions and weighted by their uncut propagators
-\begin{equation}
-\label{eq:SchematicCutEquation}
-\text{Cut}[\gamma]= \sum_{\substack{\text{states}\\\text{crossing } E(\gamma)}} \prod_{v \in V(\gamma)} \atree(v)
-= \sum_{g \text{ compat } \gamma}
-\frac{N[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
- \, ,
-\end{equation}
-where $V(\gamma)$ are the vertices of $\gamma$ and $E(\gamma)$ its
-edges.  The sum over states hides much of the complexity of cut
-construction: for scalars the process is trivial while spinning states
-greatly complicate matters (see
-Refs.~\cite{Kosmopoulos:2020pcd,Edison:2022jln} for recent discussion
-and detailed examples of evaluating state sums).  As an example of the
-two types of expressions appearing in \cref{eq:SchematicCutEquation},
-the iterated two-particle cut can be
-represented as a product of trees via
-\begin{equation}
-  \label{eq:example-cut-prod}
-  \ExCutLabeled{1}{2}{3}{4} = \!\!\!\!\! \sum_{\substack{\text{states of }\\ \{\ell_1, \ell_2, \ell_3, \ell_4\}}} \!\!\!\!\!\!\!
-  \atree(1,2,\ell_1,\ell_2) \atree(-\ell_1,-\ell_2,\ell_3,\ell_4) \atree(-\ell_3,-\ell_4,3,4)
-\end{equation}
-or as a collection of diagram numerators via
-\begin{align}
-  \label{eq:example-cut-sum}
-  \ExCutLabeled{1}{2}{3}{4} &=
-  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
-    \delta(\textcolor{cut-color}{\ell_2^2})
-    \delta(\textcolor{cut-color}{\ell_3^2})
-    \delta(\textcolor{cut-color}{\ell_4^2})}{(\textcolor{ucp-color}{\ell_5})^2
-    (\textcolor{ucp-color}{\ell_6})^2
-    (\textcolor{ucp-color}{\ell_7})^2}
-  \ N\left[
-    \IUCContrib{1}{4}{3}{2}{\ell_5}{\ell_6}{\ell_7}
-                              \right] \notag \\
-  &\quad + 
-  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
-    \delta(\textcolor{cut-color}{\ell_2^2})
-    \delta(\textcolor{cut-color}{\ell_3^2})
-    \delta(\textcolor{cut-color}{\ell_4^2})}
-    {(\textcolor{ucp-color}{\ell_5})^2
-    (\textcolor{ucp-color}{\ell_6})^2
-    (\textcolor{ucp-color}{\ell_7'})^2}
-  \ N\left[
-    \IUCContrib{1}{3}{4}{2}{\ell_5}{\ell_6}{\ell_7'}
-    \right] + 25\text{ others.}
-\end{align}
-When drawing cut diagrams, we will use gray blobs as in the left-hand
-sides of \cref{eq:example-cut-prod,eq:example-cut-sum} and all drawn
-legs are assumed to be on-shell.  When drawing numerator contributions
-to cuts, we will not use blobs on vertices, and will use
-\textcolor{cut-color}{dashed lines} bisecting edges to denote cut
-lines and use colored edges to highlight the
-\textcolor{ucp-color}{uncut propagators}.  From now on we will leave
-the cut $\delta(\ell^2)$ factors implicit.
-
-In color-charged theories, both sides of the cut can be further
-decomposed according to the color algebra.  For theories charged under
-the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes, it is
-convenient to project onto a specific element of the Del
-Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni}.  This is done by only
-inserting color-ordered amplitudes, \emph{a la} the right hand side of
-\cref{eq:ddm-basis} in the product of trees, and restricting the set
-of compatible diagrams to those whose color factors reduce to the
-appropriate DDM element when summing over \emph{only the uncut color
-  contractions}.  In this situation, the color becomes an overall
-factor on the entire cut equality and thus can be ignored.  Cuts that
-are organized in this manner are known as ``color-ordered'' cuts, in
-the same sense as color-ordered tree amplitudes.  Since the DDM basis
-(and dual Kleiss-Kuijf amplitude basis \cite{Kleiss:1988ne}) have
-$(n-2)!$ elements, one generally needs to evaluate
-$(n_1-2)! (n_2-2)!...$ separate color-orderings of the same cut, where
-$n_1$, $n_2$... are the multiplicities of the amplitudes making up the
-cut. As an example, consider the ``bowtie'' cut topology -- one of the
-factorization channels of the iterated unitarity cut -- that has two
-topologically distinct color-ordered expansions
-\begin{equation}
-  \label{eq:kt-color-ord}
-\!\!\! \!\!\! \!  \NMCutC =
-  \begin{cases}
-     s\text{-}t \text{ channel}
-    &
-      \frac{1}{\textcolor{ucp-color}{s_{12}}}
-      N \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
-      \right]
-      +
-      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
-      N \left[
-      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
-      \right]\\
-    t\text{-}u \text{ channel}
-    & 
-      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
-      N \left[
-      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
-      \right]
-      +
-      \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
-      N\left[
-      \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
-      \right]
-  \end{cases}
-\end{equation}
-which serve as a complete basis for the full cut.
-
-Even though unitarity methods aim to generate loop-level data from
-well-defined on-shell information, the procedure can encounter
-subtleties.  Beginning at one loop, there are classes of cuts that are
-difficult to properly define due to hidden non-physical singularities.
-The quintessential example of such a ``pathological'' cut is the 3-1
-two-particle cut at one loop which hides a bubble-on-external-leg (BEL)
-singularity
-\begin{equation}
-\frac{\delta(\textcolor{cut-color}{k_4^2})}{s\,\textcolor{ucp-color}{ k_4^2}}
-n \left[
-  \begin{tikzpicture}
-    \ver{e1}{-1,0};
-    \ver{e2}{-0.6,0.4};
-    \ver{e3}{-0.3,0.4};
-    \ver{i1}{-0.6,0};
-    \ver{i2}{-0.3,0};
-    \ver{i3}{0,0};
-    \ver{i4}{0.8,0};
-    \ver{co}{$(i3)!0.5!(i4)$};
-    \ver{e4}{1.2,0};
-    \draw[ultra thick] (e1)--(i1)--(i2)--(i3) to [out=80,in=100,min distance=0.4cm](i4)--(e4);
-    \draw[ultra thick](i1)--(i2);
-    \draw[ultra thick,ucp-color](i2)--(i3);
-    \draw[ultra thick,cut-color](i4)--(e4);
-    \draw[ultra thick] (i3) to [out=-80,in=-100,min distance=0.4cm](i4);
-    \draw[ultra thick] (e2) -- (i1);
-    \draw[ultra thick] (e3)--(i2);
-    \draw[ultra thick,dashed,cut-color] (co)--++(90:0.5);
-    \draw[ultra thick,dashed,cut-color] (co)--++(-90:0.5);
-  \end{tikzpicture}
-  \right]
-  \in   \begin{tikzpicture}
-\begin{feynman}
-\vertex (a1) at (-.8, -0.6) {1};
-\vertex (a2) at (-.8, 0.6) {3};
-\vertex (a3) at (-1, 0) {2};
-\vertex [dot, scale=2](mid1) at (0,0){};
-\vertex [dot, scale=1.5,hgrey0](mid2) at (0,0){};
-\vertex [dot, scale=2](mid3) at (1,0){};
-\vertex [dot, scale=1.5,hgrey0](mid4) at (1,0){};
-\vertex (a4) at (1.8, 0) {4};
-\diagram{
-(mid1) --[ultra thick,](a1),
-(mid1) --[ultra thick,](a2),
-(mid1) --[ultra thick,](a3),
-(mid1) --[ultra thick,out=60,in=120,min distance=0.4cm](mid3),
-(mid1) --[ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
-(mid3) --[ultra thick](a4),
-};
-\end{feynman}
-\end{tikzpicture}
-\end{equation}
-in which one of the \textcolor{ucp-color}{uncut propagators} is set
-equal to an \textcolor{cut-color}{external on-shell propagator}.
-Discussions about how to resolve these types of singularities can be
-found in Refs.~\cite{Minahan:1987ha, Bern:2012uf, 
-  Geyer:2015bja,Geyer:2015jch,Edison:2020uzf, Edison:2022jln, Edison:2022smn} and \cref{BELreg}. In addition to the
-BEL cuts, there is a related class of cuts in which
-an uncut propagator is set to zero by an \emph{internal cut
-  condition}, for instance,
-\begin{equation}
-  \label{eq:other-path}
-  \begin{tikzpicture}
-    \pgfmathsetmacro{\ri}{1};
-    \pgfmathsetmacro{\re}{0.6};
-    \pgfmathsetmacro{\ang}{35};
-    \begin{feynman}
-      \blob{i1}{\ang:\ri};
-      \blob{i2}{180-\ang:\ri};
-      \blob{i3}{180+\ang:\ri};
-      \blob{i4}{-\ang:\ri};
-      \blob{i5}{ $(i1)!0.5!(i2)$ };
-      \ver{e1}{45:\ri+\re};
-      \ver{e2}{135:\ri+\re};
-      \ver{e3}{225:\ri+\re};
-      \ver{e4}{-45:\ri+\re};
-
-      \diagram{
-        {[edges={ultra thick}] (e1)--(i1),
-          (e2)--(i2),
-          (e3)--(i3),
-          (e4)--(i4),
-          (i5)--(i1)--(i4)--(i3)--(i2),
-          (i2) --[out=60,in=180-60] (i5),
-          (i2) --[out=-60,in=180+60] (i5)
-        };
-      };
-    \end{feynman}
-  \end{tikzpicture}
-  \text{ contains a contribution from }
-  \begin{tikzpicture}
-    \pgfmathsetmacro{\ri}{1};
-    \pgfmathsetmacro{\re}{0.6};
-    \pgfmathsetmacro{\ang}{35};
-    \pgfmathsetmacro{\cang}{90};
-    \pgfmathsetmacro{\cl}{1.1};
-      \ver{i1}{\ang:\ri};
-      \ver{i2}{180-\ang:\ri};
-      \ver{i3}{180+\ang:\ri};
-      \ver{i4}{-\ang:\ri};
-      \ver{i5}{ $(i1)!0.25!(i2)$ };
-      \ver{i6}{ $(i1)!0.75!(i2)$ };
-
-      \ver{e1}{45:\ri+\re};
-      \ver{e2}{135:\ri+\re};
-      \ver{e3}{225:\ri+\re};
-      \ver{e4}{-45:\ri+\re};
-
-      \ver{c1}{0:\cl};
-      \ver{c2}{\cang:\cl};
-      \ver{c3}{2*\cang:\cl};
-      \ver{c4}{3*\cang:\cl};
-      \ver{ci}{$(i5)!0.5!(i1)$};
-      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
-      \draw[ultra thick] (e1)--(i1);
-      \draw[ultra thick] (e2)--(i2);
-      \draw[ultra thick] (e3)--(i3);
-      \draw[ultra thick] (e4)--(i4);
-      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
-      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
-      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c1);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c2);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c3);
-      \draw[dashed,ultra thick,cut-color] (0,0) -- (c4);
-      \draw[dashed,ultra thick,cut-color] (c5) -- ++(90:0.7*\cl);
-      \node[fill=white,circle] (c) at (0,0) {};
-  \end{tikzpicture}.
-\end{equation}
-Fully resolving both of these problems is beyond the scope of the
-current work, so we will simply not impose any constraints that
-require handling these types of cuts.
-
-\section{One-loop cubic construction}
-\label{sec:cubic}
-Here we will describe why constructing the full Yang-Mills kinematic
-algebra (outside the self-dual sector) is generically hard, and why
-the same reason makes NLSM beyond one-loop hard as well. The major
-obstacle stems from the vector state sum mixing with higher-point
-contacts. Starting with the Yang-Mills Lagrangian,
-\begin{equation}
-  \label{eq:ym-lag}
-  \mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2
-  + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu
-  + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
-\end{equation}
-we can express the YM three-point interaction in terms of the
-following vertex in Lorenz gauge:
-\begin{equation}
-\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} =(\varepsilon_i\varepsilon_j)(\varepsilon_k p_i).
-\end{equation}
-This kinematic vertex is anti-symmetric in $1\leftrightarrow 2$
-exchange, and from it we can construct the full Lorenz gauge
-Yang-Mills vertex by summing over cyclic permutations,
-\begin{equation}
-V^{(123)}_{\text{YM}} = \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}  +\text{cyc}(123)\,.
-\end{equation}
-Contracting this with the vector state sum, we can see that the cubic
-Yang-Mills vertex does not satisfy the four-point Jacobi identity,
-\begin{equation}
-  \label{cubicJac}
-  {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4+\text{cyc}(234) = \varepsilon_{(12)}  \varepsilon_{(34)} (s_{13}-s_{23}) +\text{cyc}(234) \neq 0
-\end{equation}
-where $ \varepsilon_{(ij)} = \varepsilon_{i}\cdot \varepsilon_{j}$.
-However, the remaining terms can be absorbed into the definition of the
-four-point kinematic numerator as follows
-\begin{equation}
-{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4 = {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4 + s_{12} (\varepsilon_{(13)}\varepsilon_{(24)}-\varepsilon_{(14)}\varepsilon_{(23)}).
-\end{equation}
-Note that this new definition of the $s$-channel numerator contains two factors of $\varepsilon_{(ij)} $ that contract spacetime indices \textit{across} the factorization channel, suggesting the inclusion of a spin-2 mode.
-As such, we use $V_{\text{YM}+B}$ to denote the inclusion of an additional two-form, as was studied in Ref.~\cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian.
-After the introduction of the two-form, the
-numerators now satisfy the Jacobi identity
-\begin{equation}
-  {}_1\langle
-  V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0\,,
-\end{equation}
-where the new cubic Lagrangian takes the form,
-\begin{equation}
-\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 -
-B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu
-A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu
-A^c_\nu\, .
-\end{equation}
-Of course, higher multiplicity would likely require further redefinition of
-the three-point vertex to satisfy Jacobi identities on all internal
-edges. While introducing successively higher spin states could in
-principle work at tree level, we will see that it is not consistent
-with what we find at general loop order. We will comment on this in
-\cref{sec:Discussion}. For
-now, we will study how to construct one-loop integrands consistent
-with color-kinematics by isolating the cubic sector of the state
-sum above.
-
-As can be seen above, the Jacobi identity of \cref{cubicJac} fails
-only in terms with two factors of polarization dot products,
-$(\varepsilon\varepsilon)^2$. If we restricted ourselves to
-just considering factors with a single polarization dot product, the
-Jacobi identity of Yang-Mills would be satisfied \textit{off-shell}
-and in arbitrary spacetime dimensions
-\begin{equation}
-{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0\,.
-\end{equation}
-This restriction to the $(\varepsilon\varepsilon)^1$ cubic sector of Yang-Mills is closely related to the MHV decomposition of color-dual numerators \cite{TasiLance,ElvangHuangReview,Chen:2019ywi,Chen:2021chy}.
-In the MHV sector it is possible to choose the reference vectors so that all dot products of polarization vectors vanish, $(\varepsilon\varepsilon) \rightarrow 0$, except those involving one of the positive helicity polarizations, $(\varepsilon^+_1 \varepsilon^-_i )\neq 0$.
-We describe this in detail in \cref{Conventions}.
-By focusing on $(\varepsilon\varepsilon)$ structure rather than specific 4D helicity states, we will be able to construct dimension agnostic color dual integrands at one-loop.
-
-Thus for our approach at one-loop, we aim to build color-dual integrands directly from $D$-dimensional kinematic factors that are $\mathcal{O}((\varepsilon\varepsilon)^1)$ at tree-level, and $\mathcal{O}((\varepsilon\varepsilon)^0)$ at one-loop.
-The $D$-dimensional organizational principle underlying this construction can be understood in terms of a vector amplitude decomposition introduced by one of the authors \cite{Pavao:2022kog},
-\begin{equation}\label{eq:pureVecRABD}
-A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
-\end{equation}
-where we have introduced the shorthand notation, $\varepsilon_{(ij)\cdots (kl)} \equiv (\varepsilon_i \varepsilon_j)\cdots (\varepsilon_k \varepsilon_l)$, and  $S^{2|k}_{\sigma}$ is the set of $k$ pairs of external legs appearing in the color-ordered label list, $\sigma$.
-For example, at four-point, $S^{2|1}_{\sigma} =  \{(12),(13),(14),(23),(24),(34)\}$, and $S^{2|2}_{\sigma} =  \{(12)(34),(13)(24),(14)(23)\}$.
-The sum thus selects out kinematic building blocks, $\Delta_{(\sigma)}^{(\rho)}$,that are each weighted by different polarization dot products.
-Some simple four-point examples include,
-\be
-\Delta^{(13)}_{(1234)} =\frac{(k_1 \varepsilon_2)(k_{3} \varepsilon_4)}{s_{12}}+\frac{(k_1 \varepsilon_4)(k_{3} \varepsilon_2)}{s_{14}}, \qquad \Delta^{(13)(24)}_{(1234)} =1, \qquad \Delta^{(12)(34)}_{(1234)} =\frac{s_{13}}{s_{12}}\,.
-\ee
-We direct the reader to ref.~\cite{Pavao:2022kog} for further details.
-The expansion of \cref{eq:pureVecRABD} comes with the added advantage of making the transmutation relations of \cite{Cheung:2017ems} absolutely manifest.
-By a simple mass-dimension argument \cite{ElvangHuangReview}, we know the tree-level cubic sector of Yang-Mills must be at
-$\mathcal{O}((\varepsilon\varepsilon)^1)$,
-\begin{equation}
-A_{(\text{tree})}^{\text{cubic-YM}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\, ,
-\end{equation}
-while at one-loop, the cubic sector corresponds to
-$\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot
-products,
-\begin{equation}
-A_{(\text{1-loop})}^{\text{cubic-YM}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
-\end{equation}
-When decomposed in this way, the polarization stripped building blocks
-must obey a set of Ward-identities between different ``helicity'', or
-$(\varepsilon \varepsilon)^n$, sectors in order for the full amplitude
-to be gauge invariant,
- \begin{equation}\label{eq:GIrelA}
-\Delta_{(\sigma)}^{(\rho)}\Big|_{\epsilon_i\rightarrow k_i} =-
-\sum_{j \in \rho^c} (k_i \varepsilon_j)\Delta_{(\sigma )}^{(\rho\cup (ij))} \,.
-\end{equation}
-With this in hand, we can construct a Lagrangian description of the of
-the cubic sector for Yang-Mills, and will demonstrate that the
-resulting amplitudes with manifestly color-dual Feynman rules are
-equivalent to both SDYM and NLSM through one-loop.
-
-\subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
-As we argued above, if we include factors of
-$(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to
-keep the Yang-Mills four-point contact for color-kinematics duality to
-be restored on-shell. However, the contrapositive is also true -- if
-we omit the four-point Yang-Mills vertex, then we only need terms that
-contribute to the manifestly color-dual cubic sector of the theory. We call
-this manifestly color-dual theory \textit{semi-abelian Yang-Mills},
-\begin{eBox}
-\begin{equation}
-\label{eq:semiYM}
-\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
-\end{equation}
-\end{eBox}
-where
-\begin{equation}
-\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
-\end{equation}
-\begin{equation}
-F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
-\end{equation}
-and $A_\mu$ is in Lorenz gauge. We can construct this Lagrangian from \cref{eq:ym-lag} by keeping the right field strength covariant under
-$U(N)$, and making the left field strength gauge covariant under
-$U(1)^{N^2}$.
-Note that since $U(1)$ covariance is identical to $U(1)$ invariance, the amplitudes of this semi-abelian theory vanish under $\bar{\varepsilon}(k) \rightarrow k$, where $\bar{\varepsilon}$ is the polarization of an external $\bar{A}_\mu$ vector.
-
-Here we can think of the abelian vector as a background field that
-sources on-shell $A_\mu$ currents. Indeed, as we describe in
-\cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
-heart of $YZ$-theory \cite{Cheung:2016prv}, $J$-theory
-\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
-\cite{Monteiro2011pc}.  Specifically, semi-abelian YM is simply a
-clever reinterpretation of the Lagrangian obtained by integrating an
-auxiliary field into the $J$-theory equations of motion.  The Feynman
-rule for the cubic vertex is
-\begin{equation}
-  \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
-  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
-\end{equation}
-where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply
-\be
-\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}.
-\ee
-We can use the Ward identity of
-\cref{eq:GIrelA} to check that the amplitudes are indeed gauge
-invariant when the \emph{abelian} polarizations are taken to be longitudinal,
-$\bar{\varepsilon} \rightarrow k$.
-Furthermore, a simple calculation shows that the four-point correlation function of this theory satisfies the Jacobi identity of \cref{jacID} \emph{off-shell}.
-This ensures that color-kinematics duality holds to all multiplicity and loop order.
-We also note that semi-YM does not have any ghosts from non-abelian gauge symmetry that could spoil color-kinematics at loop level.
-Due to the Feynman rules of this theory, the amplitudes are non-vanishing only at tree-level and one-loop.
-We demonstrate the implications of this property in \cref{2LoopObstruction}.
-
-As noted above, we can select out the manifestly cubic
-sector of semi-abelian Yang-Mills from the full theory of \cref{eq:ym-lag} by selecting only $(\varepsilon^+\varepsilon^+)$ in light-cone gauge (i.e.
-SDYM) and one-minus at tree-level or by plugging in the on-shell states of $J$-theory \cite{Cheung:2020djz,Cheung:2021zvb} and
-$YZ$-theory \cite{Cheung:2016prv}. Indeed, semi-YM is just the following sum over building blocks
-in the expansion of Yang-Mills given in Ref.~\cite{Pavao:2022kog},
-\begin{equation}
-A(A_1,...,\bar{A}_i,...,A_n)_{\text{tree}} = \sum_{i\neq j} (\varepsilon_i \varepsilon_j) \Delta^{(ij)}_{\text{tree}} \sim \sum_{i\neq j} (\varepsilon_i \varepsilon_j)  \sum_a \,[(\varepsilon k)^{n-2} (kk)^{3-n}]_a\,,
-\end{equation}
-and similarly so at one-loop,
-\begin{equation}
-A(A_1,...,A_n)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}} \sim \sum_a\,[ (\varepsilon k)^{n} (kk)^{-n}]_a\,,
-\end{equation}
-where $[\,\cdots]_a$ are terms with appropriate powers of $(\varepsilon k)$ and $(kk)$.
-As we describe in detail in \cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to extract the $D$-dependent part
-that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional
-scalars
-\begin{eBox}
-\begin{equation}
-A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}\, .
-\end{equation}
-\end{eBox}
-Why must we take the derivative with respect to $D$? After all,
-$J$-theory and $YZ$-theory both have well defined propagators for
-internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we discuss
-in \cref{sec:CKLagrangians}, all the $J$ and $Z$ states must be on-shell in order to
-produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at
-one-loop will not produce NLSM amplitudes. However, the internal
-$YY$-loop is a valid forward limit for producing NLSM amplitudes,
-since as constructed $YZ$-theory matches to NLSM for off-shell
-$Y$-particles. We now provide explicit expressions for these one-loop amplitudes in the next section.
-
-\subsection{One-loop color-dual integrands}\label{oneLoopCK}
-Our first application of this theory for color-dual construction at
-loop level is for self-dual Yang-Mills (SDYM). As we have done throughout the text, we will set all coupling constants to unity. At tree-level, the
-off-shell cubic vertices can be written in terms of light cone
-coordinates \cite{Monteiro2011pc}
-\begin{equation}
-X(p,k) = p_u k_w-p_w k_u.
-\end{equation}
-At loop-level, this construction needs to be analytically continued to
-general dimension in order to apply dimensional regularization at
-one-loop. This can be done using the cubic semi-YM vertices of the
-previous section
-\begin{equation} \label{DdimSDYM}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
-\end{equation}
-Plugging in on-shell all-plus helicity states in light-cone gauge will
-yield precisely the 4D SDYM vertex, up to an unphysical phase
-  \begin{equation}
-  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}\, ,
- \end{equation}
-where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge.
-In the second equality, momentum conservation has been applied to the redefined the spinor bracket, $\langle 12\rangle \rightarrow X(k_1,k_2)$, whose definition is given in \cref{Conventions}.
-Of course, the form of \cref{DdimSDYM} has the advantage of
-permitting a $D$-dimensional construction of the one-loop
-integrand. As an example, the four-point numerator is
-\begin{equation}
-\simplebox = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle \, ,
-\end{equation}
-where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$, on all internal polarizations.
-In general, the $n$-gon diagram is
-\begin{equation}\label{SDYMnGon}
-N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle\, .
-\end{equation}
-Recall that all other numerators can be obtained from the $n$-gon through Jacobi.
-Due to the state-sum of internal loop factors,
-$\sum {\varepsilon_{(+\ell)}\varepsilon_{(-\ell)}}\sim D$, the integrand above
-depends explicitly on the spacetime dimension, $D$. By taking a
-derivative\footnote{Another way to understand this derivative is that
-  it selects the large $D$ behavior of the integrand.}, we can recover
-the integrand needed for the all-plus one-loop amplitudes with an internal
-scalar
-\begin{equation}
-\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = 2^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)\, .
-\end{equation}
-This integrand numerator with internal scalar loop is precisely what
-one would obtain from the Feynman rules of $YZ$-theory, absent the $\bar{Z}Z$
-internal vector loop. For more background, we refer the reader to
-\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator
-\begin{equation}\label{NLSMnGon}
-N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =   [\![ 12]\!][\![23]\!]\cdots [\![n1]\!]\, ,
-\end{equation}
-where we have defined the antisymmetric kinematic variable,
-$[\![ij]\!] = \ell_i^2 - \ell_j^2 = 2(k_i \cdot \ell_i)$.
-We have
-verified through 10-point one-loop that this $n$-gon expression is a
-valid color-dual representation for NLSM.
-Thus, composing the $n$-gon numerators of \cref{SDYMnGon} and \cref{NLSMnGon} would yield $D$-dimensional integrands that project down to the 4D all-plus Born-Infeld one-loop amplitudes studied in Ref.~\cite{Elvang:2020kuj}.
-
-Before proceeding, we note that the above definition does give rise to ``pathological" bubble-on-external-leg (BEL) diagrams, discussed previously in \cref{sec:bootstrap}.
-However, one can show that these diagrams integrate to zero for spacetime dimension, $D>2$, and thus can be disregarded as unphysical.
-For the interested reader, in \cref{BELreg} we provide a detailed overview of this dimensional regularization of the relevant BEL diagram.
-\subsection{Two-loop obstruction}\label{2LoopObstruction}
-At two-loop, introducing terms that conspire with four-point contacts
-is unavoidable. At one-loop, we were able to avoid internal
-contractions of $\bar{A}_\mu A^\mu$ by selecting appropriate external
-states. However, at two-loop when choosing all external $A_\mu$
-states, the amplitude vanishes in semi-YM theory
-\begin{equation}
-\mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=0,
-\end{equation}
-that is, the theory is one-loop exact.
-In order to produce non-vanishing interactions, we would need to
-reintroduce $D$-dimensional vertices from the diagonal group of
-$G_L\times G_R$ that have the wrong weight. Doing so will necessarily permit internal
-contractions of $\bar{A}_\mu A^\mu$,
-\begin{equation}\label{2loopTension}
-\mathcal{A}^{\text{YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=\doubleBoxObstructionA +\doubleBoxObstructionB+\cdots 
-\end{equation}
-where we used white dots to indicate interaction vertices of
-weight\footnote{We choose the convention that the abelianized gauge
-  fields carry weight $\mathcal{W}[\bar{A}] = -1$, and non-abelian
-  vectors are $\mathcal{W}[\bar{A}] = +1$.}
-$\mathcal{W}[\bar{A}\bar{A} A] = -1$, rather than the isolated semi-YM
-vertex which always carries weight $\mathcal{W}[\bar{A}A A] =
-+1$. This immediately runs into the difficulty of introducing the
-four-point contact needed for color-kinematics to be satisfied on all
-internal edges. By a simple weight counting argument, one can see that
-including this wrong sign interactions is unavoidable at two-loop and
-higher.
-
-Thus, to construct two-loop numerators prescriptively, as we have done at one-loop, would require knowledge of
-the full kinematic algebra for Yang-Mills off-shell.  Since this is presently unavailable, we will tackle the two-loop integrand using an ansatz approach.
-
-\section{Two-loop four-point bootstrap}
-\label{2loopBoot}
-As we have just seen, it is possible to coerce tree numerators into
-one-loop numerators at any multiplicity for pions and related
-theories, but that these methods cannot be reapplied to generate
-higher-loop numerators.  For pions in particular, the two-loop no-go statement
-is only for \emph{one particular representation of the theory} so it does
-not completely preclude the existence of a two-loop color-dual
-integrand.  We thus turn to the color-dual bootstrap method
-described in \cref{sec:bootstrap} to construct a color-dual
-representation of two-loop four-point NLSM.  Because of the similarity
-of the problem setup, we will also use the opportunity to revisit the
-construction of a color-dual representation of pure YM, extending the
-search space beyond what was covered in Ref.~\cite{Bern:2015ooa} to include the most general local ansatz.
-
-Both NLSM and YM share the same cubic graph basis, and thus their
-defining Jacobi relations lead to the same graph basis.
-Ignoring tadpole and BEL graphs, there are 14 cubic four-point two-loop
-graphs (see \cref{fig:MaxCuts}) which are related to each other via 21
-Jacobi relations.  As mentioned in \cref{sec:bootstrap},
-color-kinematics duality ensures that the numerator of every graph can
-be expressed in terms of a basis of the double box and penta-triangle,
-\begin{equation}
-\label{eq:jacobi-basis}
-\NLSMBasisDoubleBox \text{ and } \NLSMBasisPentaTriangle .
-\end{equation}
-Obviously, the actual numerator dressings and physical properties
-of the two theories differ, so we discuss them separately below.
-
-\subsection{Two-loop NLSM}
-\label{sec:pions}
-
-For a scalar theory like NLSM the numerator only depends on dot
-products of momenta.  The basis of momentum invariants for both of the
-graphs can be taken to be
-\begin{equation}
-\label{eq:scalar-basis}
-N^{\text{NLSM}}\left[
-  \scalebox{0.75}{\NLSMBasisDoubleBox} \right]
-\text{ and }
-N^{\text{NLSM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]\in
-\left\{\begin{array}{cccc}
-    k_{13},& k_{23},& k_{15},& k_{16}, \\
-    k_{25},& k_{26},& k_{35},& k_{36}, \\
-    k_{55},& k_{56},& k_{66}
-  \end{array}
-  \right\},
-\end{equation}
-where $k_{ij}$ means $k_i \cdot k_j$, $k_5=\ell_1$, and $k_6 = \ell_2$.
-Every vertex in NLSM scales as $k^2$ so the numerator of each diagram
-scales as $k^{12}$.  At this mass dimension there are 8,008
-independent dot products of momenta.  With two basis graphs there is a
-total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is
-  not suited to solving large sets of equations with sixteen thousand
-  parameters, so a different method is desirable.  One possibility is
-  to use a sprase solver, as often employed for integral reduction.
-  However, these solvers typically assume that the matrix has a very
-  low density.  While the equations in YM naturally separate into
-  different ``helicity'' sectors (or $e_i \cdot e_j$ and
-  $e_i \cdot k_j$ sectors in $D$ dimensions) which limits the
-  cross-talk between equations and thus the effective density, there
-  is no such separation of sectors in a scalar theory.  Thus the NLSM
-  constraint equations were solved using a custom solver, working name
-  \texttt{FiniteFieldSolve}, designed to exactly solve large linear
-  systems of arbitrary density.  \texttt{FiniteFieldSolve} will be
-  released publicly shortly.} Imposing the boundary Jacobi relations
-eliminates all but 4,473 of the original free parameters.  Further
-imposing graph symmetries reduces the number of free parameters to
-1,243.
-
-The final essential constraint is unitarity.  The two physical cuts
-that need to be enforced, shown in \cref{fig:emu}, only involve
-four-point vertices.  Notably this means that even at two loops,
-unitarity is still only probing the on-shell four-point NLSM amplitude.
-Unitarity cuts besides those shown in \cref{fig:emu} are either
-pathological or vanish because they involve a three-point point on-shell
-amplitude. In order to manifest the $\mathbb{Z}_2$
-symmetry of NLSM at the integrand level, we also require that all
-non-pathological cuts containing a three-point vertex (such as the maximal
-cut) vanishe.  Imposing all relevant cuts leaves 765 free parameters
-representing the generalized gauge freedom in the answer.
-
-At this point color-kinematics duality has been satisfied, so the
-double copy will proceed without issue.  However, the plethora of
-generalized gauge freedom parameters leaves the option for enforcing
-additional aesthetic constraints.  All remaining generalized gauge
-parameters could be set to zero, but a simpler and more insightful
-result can be obtained through physical arguments.  $\mathcal{N}=4$
-SYM provides several hints for further conditions to impose on the
-ansatz.  For example, for maximally supersymmetric gauge theory it is
-possible to enforce the no triangle hypothesis, manifest loop power
-counting, and, for four-point and up to at least six loops, strip off
-a factor of $st \atree$ from the integrand \cite{FiveLoopN4,
-  Bern:2012uf, Bern:2010fy, SuperSum, Carrasco:2021otn,
-  JJHenrikReview, BRY, BDDPR, Neq44np}.  For the NLSM integrand it is
-desirable to make color-kinematics duality as manifest as possible.
-One hope would be to factor out some piece of the one-loop numerator
-since this at least manifests antisymmetry for the vertices involving
-external legs.  However, a more fruitful direction is to match onto
-the one known theory with pion power counting that manifests
-color-kinematics duality to all loop orders, namely,
-Zakharov-Mikhailov (ZM) theory \cite{Zakharov:1973pp, Cheung:2022mix}.
-ZM theory is governed by the Lagrangian
-\begin{equation}
-\label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2
-+ g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c),
-\end{equation}
-where more details can be found in \cref{sec:CKLagrangians}.  The
-color-stripped Feynman rule for the vertex is
-$V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu \equiv \langle k_1 k_2 \rangle$ where
-off-shell color-kinematics duality to all orders in perturbation
-theory simply follows from the Schouten identity in 2D.  Since the theory
-is purely cubic and manifests off-shell color-kinematics
-duality, it is trivial to read off the color-dual numerator for any
-graph.  From the presence of the Levi-Civita tensor
-$\varepsilon^{\mu\nu}$, the theory clearly resides in two spacetime
-dimensions where scattering is notoriously plagued by infrared
-regulation issues.  Every on-shell particle is either a right mover,
-with momentum proportional to $k_R^\mu \equiv (1,1)$, or a left mover,
-with momentum proportional to $k_L^\mu \equiv (1,-1)$.  On-shell ZM
-amplitudes naturally divide into sectors corresponding to the
-configuration of left and right movers, where the scattering in many
-sectors is rather subtle.  Only color-ordered amplitudes can be
-defined unambiguously from the naive Feynman rules.  At four-point, only the
-alternating sector is free of subtleties and the amplitude for this
-process vanishes.  In equations, $A[LRLR]=0$ where $R$ corresponds to
-a right mover and $L$ corresponds to a left mover.  In every other
-configuration of right and left movers, such as $A[RRRR]$, one of the
-internal propagators is accidentally on-shell since $k_R^2=k_L^2=0$.
-
-\begin{figure}[t]
-  \begin{center}
-	\PhysicalCutOne{}{}{}{} \PhysicalCutTwo{}{}{}{}
-  \end{center}
-  \caption{The two physical cut topologies shared by NLSM, sGal, BI, and DBIVA}
-  \label{fig:emu}
-\end{figure}
-It is tempting to try to match the pion four-point two-loop integrand to ZM
-on the cuts, but given that the cuts only probe the on-shell four-point
-amplitude, which is either subtle or vanishes for ZM, it is better to
-compare the off-shell numerators directly.
-The numerators of the two basis graphs are
-\begin{align}
-N^{\text{ZM}}\left[ \scalebox{0.75}{\ZMBasisDoubleBox} \right] &=
-\begin{aligned}
-&\langle \ell_1 \ell_2 \rangle \langle k_4 \ell_1 \rangle \langle \ell_2 k_1 \rangle \langle k_3 (\ell_1+k_4)\rangle \\
-& \times \langle (k_1+\ell_2) k_2 \rangle \langle (\ell_2+k_{12})(\ell_1-k_{12})\rangle
-\end{aligned} \\
-N^{\text{ZM}}\left[ \scalebox{0.75}{\ZMBasisPentaTriangle} \right] &=
-\begin{aligned}
-&\langle \ell_1 \ell_2 \rangle \langle k_4 \ell_1 \rangle \langle \ell_2 k_1 \rangle \langle k_3 (\ell_1+k_4) \rangle \\
-& \times  \langle (k_1-\ell_1) k_2 \rangle \langle (\ell_2+k_1) (\ell_1-k_1)\rangle
-\end{aligned}
-\end{align}
-where $k_{12} = k_1+k_2$ and, again, $\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu$ is the color-stripped ZM vertex.
-As local functions, the
-numerators never suffer from any of the subtleties of on-shell 2D
-kinematics.
-We introduce a proportionality constant $z$ between the numerators of the two theories, $N_\text{NLSM} \vert_{2D} = z ~ N_\text{ZM}$, because we are only interested in how the kinematical structure of $N_\text{ZM}$ can be used to eliminate gauge freedom in $N_\text{NSLM}$.\footnote{Another reason for introducing the parameter $z$ is because the ZM and NLSM are believed to differ at loop level even though they are dual classically in 2D \cite{Nappi:1979ig}.
-Once all of the constraints from this section are imposed, $z$ is fixed to $216/565$ where the four-point pion tree amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \varepsilon_{\mu\nu}k_2^\nu$.}
-Mechanically, the pion numerator is matched
-to ZM by first taking every possible assignment of right and left
-movers for the external particles and then restricting the pion
-numerator to 2D.  The loop momenta are restricted to 2D but left
-off-shell.  After performing the 2D matching, there are only 365
-parameters of generalized gauge freedom.
-
-The loop momentum structure of ZM theory provides one final hint for
-simplifying the pion numerators.  A generic term in the ZM numerator
-(of either basis graph) looks schematically like
-\begin{equation}
-\label{eq:ZMLoopPowCount}
-\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
-\end{equation}
-whereas a generic set of local, cubic Feynman rules could have
-produced terms with up to $m+n=12$ powers of loop momenta.  When the
-pion numerators are forced to have the loop power counting structure in
-\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
-freedom parameters reduces to 58.  The pion numerators appearing in the
-ancillary files make exactly this choice.
-
-\subsection{Double-copy verification}
-\label{doubleCopyVerify}
-
-With a cubic color-dual pion representation in hand, we can perform
-double copies with many theories to extract colorless gravity-like
-amplitudes.  In particular, we produce numerators for special
-Gallileons, Born-Infeld theory, and DBIVA by double-copying against
-pions, pure YM, and $\mathcal{N}=4$ sYM respectively
-\cite{Cachazo:2014xea,Cheung:2015ota,Cheung:2016drk}.  Such double-copy constructions are important nontrivial
-checks on the underlying single-copy theories as the Jacobi relations
-in the single copy conspire to produce the double-copy theory's
-version of linear diffeomorphism invariance: enhanced shift symmetry for special Galilleons and gauge
-invariance of the BI photon and DBIVA supermultiplet \cite{Hinterbichler:2015pqa}.  All
-three of these double-copy theories were recently studied extensively
-by one of the authors and Carrasco from the perspective of direct
-unitarity cut construction \cite{Carrasco:2023qgz}.  One of the shared
-features of these three theories is that they all have the same
-physical cut topologies in 4D: the two diagrams shown in
-\cref{fig:emu}, which are only composed of four-point amplitudes.
-
-To construct the double-copy theories, we source the cubic
-pure YM numerators from Ref.~\cite{Bern:2015ooa} (which
-additionally satisfies a relaxed form of color-kinematics duality),
-and the cubic $\mathcal{N}=4$ sYM representation from the well-known
-$n_{2\text{box}} = n_{\text{cross-box}} = s^2t\, \atree$ \cite{Bern:1997nh}.
-On the other hand, we use the methods of Ref.~\cite{Carrasco:2023qgz}
-to directly compute the needed basis cuts in all three theories without
-relying on a color-dual pion representation.  We find exact agreement
-in each of the three theories for both physical cuts.  Since
-Ref.~\cite{Carrasco:2023qgz} has already exhaustively explored the
-properties of four-point loop amplitudes in these theories, we direct
-interested readers there for more information.
-
-\subsection{Two-loop Yang-Mills revisited}\label{2loopYM}
-
-Given the close ties between pion and gluon scattering for trees and
-at one loop, the existence of the two-loop pion numerator prompts us
-to investigate the most general local numerator for YM, without any of
-the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.  We
-follow the same general procedure as in \cref{sec:pions}, again
-identifying the double-box and penta-triangle as the
-Jacobi basis graphs and building the most general ansatz for each of
-their numerators compatible with the assumptions in
-\cref{sec:bootstrap}.  Because we are now considering pure
-Yang-Mills, each monomial in the local ansatz must consist of five
-Lorentz scalar dot products instead of the six for NLSM, and each
-monomial must be linear in each of the four external gluon
-polarizations.  Thus, the numerator ansatz for both diagrams will be
-built from terms of the form
-\begin{equation}
-  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
-  \text{ and }
-  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
-  \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
-  \label{eq:ym-basis}
-\end{equation}
-where the $k_i$ take the same definition as described near
-\cref{eq:scalar-basis}.  Without any power counting restrictions
-imposed, both the double-box and the penta-triangle have an ansatz
-with 10,010 terms each.  Imposing diagram automorphisms and
-maximal-cut gauge invariance on the two basis diagrams, we reduce the
-number of terms to 2,235 for the double-box, and 4,133 for the
-penta-triangle.  The minimal set of spanning physical cuts is shown in
-\cref{fig:ym-spanning}, but we choose to work within the framework of
-the method of maximal cuts \cite{Bern:2007ct} in order to identify the
-simplest cut that is in tension with the kinematic Jacobi relations.
-Maximal cuts and symmetries are then imposed on the 14
-non-pathological cubic diagrams shown above in \cref{fig:MaxCuts}.
-Doing so, we are left with 596 total parameters in the ansatz.
-
-\begin{figure}
-  \begin{center}
-    \begin{subfigure}{0.3\textwidth}
-      \begin{center}
-        \LMCut
-      \end{center}
-    \end{subfigure}
-    \begin{subfigure}{0.3\textwidth}
-      \begin{center}
-        \PhysicalCutOne{}{}{}{}
-      \end{center}
-    \end{subfigure}
-    \begin{subfigure}{0.3\textwidth}
-      \begin{center}
-        \PhysicalCutTwo{}{}{}{}
-      \end{center}
-    \end{subfigure}
-  \end{center}
-  \caption{The three spanning physical unitarity cuts of pure
-    Yang-Mills at two loops}
-  \label{fig:ym-spanning}
-\end{figure}
-
-Proceeding to the next-to-maximal cuts, we continue to avoid
-pathological diagrams including the newly-appearing type discussed in
-\cref{eq:other-path}.  After discarding these types of cuts as well as
-those involving cuts of external Mandelstams, there are 8 one-particle-irreducible cut
-topologies (see \cref{fig:ym-nmc}). Seven of these next-to-maximal
-cuts are consistent with the kinematic Jacobi relations and
-symmetries.  Critically, the ``bowtie'' cut,
-\begin{equation*}
-   \NMCutC \,,
-\end{equation*}
-cannot be satisfied by the ansatz once Jacobi relations and
-symmetries are applied.
-
-\begin{figure}
-\centering
- { \NMCutH, \NMCutG,  \NMCutD,\NMCutB, 
- \\
- \NMCutE, \NMCutF, \NMCutA, \NMCutC,  }
-  \caption{The 8 non-pathological 1-particle-irreducible next-to-maximal-cut diagrams used in our cut constraints on the Yang-Mills integrand.}
-  \label{fig:ym-nmc}
-\end{figure}
-
-In fact, we can make the failure extremely precise. First, start with the
-diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}, which includes
-the double-box, crossed-box, and penta-triangle. Then \emph{without} defining the crossed-box in terms of the other two diagrams, write down the most generic parity-even local ansatz
-involving four polarizations and six momenta (any combination of
-external or loop) for each of the three diagrams.  Each ansatz will have 10,010 terms initially.  Next
-impose the symmetry constraints on each of the three diagrams, leaving
-2,761 free parameters on the double-box, 2,576 free parameters on the
-crossed-box, and 5,040 free parameters on the penta-triangle.  Finally
-impose the ``bowtie'' next-to-maximal cut, which in the
-\emph{non-planar} $t$-$u$ color channel only receives contributions
-from the double-box
-\begin{equation}
-   \NMCutC
-  =
-  \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
-  N \left[
-    \KTDBContrib{1}{2}{3}{4}
-  \right]
-  +
-  \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
-  N\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
-\end{equation}
-After imposing this cut, we find that the original Jacobi relation,
-\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied.
-In other words, the constraints imposed by the single Jacobi relation and the three sets of diagram symmetries conspire in a way that is inconsistent with the ``bowtie'' cut.
-The contrapositive to this surprising result can be summarized in the following diagrammatic statement, which prioritizes the physical unitarity cut:
-\begin{eBox}
-\begin{equation}\label{chefsKiss}
-   \scalebox{0.9}{\NMCutC} \!\!
-  \Rightarrow \!\!
-  \scalebox{0.85}{\JacobiOneDoubleBox}
-  +  \scalebox{0.85}{\JacobiOneCrossedBox}
-  + \scalebox{0.85}{\JacobiOnePentaTriangle} \neq 0 \,.
-\end{equation}
-\end{eBox}
-Thus we have identified the minimal failure state for a
-globally-color-dual two-loop Yang-Mills representation: off-shell locality,
-symmetry, and the kinematic Jacobi relations for just three diagrams
-are incompatible with the ``bowtie'' cut.
-
-\section{Conclusions and Outlook}\label{conclusions}
-
-In summary, we have found that there is a tension between color-kinematics duality and an off-shell local construction of the two-loop four-point pure Yang-Mills integrand in $D$-dimensions.
-At tree level, we found that the duality can be
-manifested by breaking manifest Bose symmetry at the Lagrangian level,
-either by explicitly picking different gluon states (as in SDYM) or by
-picking states that only restore Bose symmetry in the final amplitude
-(as in NLSM).  Both of these theories can be encapsulated in the
-semi-abelian YM theory presented in \cref{eq:semiYM} which obscures
-the Bose symmetry of the external states due to the presence of the
-two gauge fields $A_\mu$ and $\bar{A}_\mu$.
-
-In addition to the tree-level construction, we found that kinetic mixing
-between the two gauge fields permits globally color-dual one-loop
-integrands. After plugging in suitable on-shell states, the integrands
-produced by semi-abelian YM correspond to those of SDYM in \cref{SDYMnGon} 
-and NLSM in \cref{NLSMnGon}.  Due to the
-kinetic mixing that stems from the broken Bose symmetry, \cref{2loopTension} shows why it is
-impossible to construct a two-loop integrand for semi-abelian YM theory.
-In \cref{2loopBoot}, we overcame this obstruction by successfully constructing two-loop NLSM numerators with an ansatz based bootstrap.
-However, we found that the same approach fails for two-loop pure Yang-Mills, and pin-pointed the failure to a particular unitarity cut captured by \cref{chefsKiss}.
-Thus, obtaining a globally color-dual
-integrand beyond one-loop then requires sacrificing more than just Bose
-symmetry, and in this paper we have argued that off-shell locality\footnote{An example of this can already be found in the literature, where locality is relaxed in Ref.~\cite{Mogull:2015adi} in
-  order to obtain color-dual two-loop integrands with on-shell 4D states.} must
-be abandoned for color-dual constructions of multi-loop Yang-Mills.
-To expand the available function space, we propose that one should consider including rational functions of kinematics, rather than just polynomials.
-
-We concede building loop-level numerators from rational functions of the kinematics
-is rather unnatural from the perspective of point-like quantum field
-theories.
-After all, operators that produce rational functions are typically non-local in their construction.
-The archetypal example of non-local quantum operators are string vertex operators with $\alpha'$ corrections.
-These operators promote local tree-level amplitudes to stringy extended objects by integrating over disc integrals of the open string worldsheet
-\be
-\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}\supset t_8 F^4 \int_0^1 dx \,\frac{ x^{\alpha' s_{12}}(1-x)^{\alpha' s_{23}}}{x(1-x)(s_{12}+s_{23})}\, .
-\ee
-The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving color-kinematics duality \cite{MafraBCJAmplString,Broedel:2013tta,Mafra:2016mcc,Carrasco:2019yyn}.
-While introducing some type of worldsheet formulation of color-dual numerators might seem unjustified given the results of this work, our findings certainly suggest that we must do \textit{something} to relax the constraint of off-shell locality, and realize locality only in the limit of
-\textit{on-shell} kinematics. This could be acheived by either modifying the kinetic term or potentially something new and more exotic. Below we provide some simple examples
-at tree-level of what one might consider for implementing such a construction.
-
-\subsection{Non-local construction of scattering amplitudes}
-\label{nonLocalScattering}
-As an exemplar of an off-shell non-local structure, consider the simple four-point example of a color-dual
-representation of Yang-Mills theory. We can define a functional numerator, $N_{(12|34)}^{\text{YM}}$, as follows, 
-\begin{equation}
-N_{(12|34)}^{\text{YM}} = \frac{t_8F^4}{3} \frac{s_{13}-s_{12}}{s_{23}{s_{13}}}
-\end{equation}
-where $N_s = N_{(12|34)}$, $N_t = N_{(14|23)}$ and $N_u = N_{(13|42)}$. By construction, this functionally symmetric numerator is
-anti-symmetric and obeys the Jacobi identity
-\begin{equation}\label{nonLocalNum}
-N_{(12|34)}^{\text{YM}} + N_{(13|42)}^{\text{YM}} +N_{(14|23)}^{\text{YM}} = 0.
-\end{equation}
-However, it must also factorize to kinematics that are consistent with
-the local Feynman rules of \cref{eq:ym-lag}. Evaluating the residue on
-the $s=s_{12} \to 0$ pole we find
-\begin{align}
-\text{Res}\left[\frac{ N_{s}^{\text{YM}} }{s}\right]^{s=0}&= \frac{2}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
-\\
-\text{Res}\left[\frac{N_{t}^{\text{YM}} }{t}\right]^{s=0}&= -\frac{1}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
-\\
-\text{Res}\left[\frac{N_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} \, ,
-\end{align}
-with $t=s_{23}$ and $u=s_{13}$.
-Plugging these into a cubic graph representation of Yang-Mills, the
-tree level version of \cref{eq:gen-amp}, we find
-\begin{equation}
-  \text{Res}\left[\mathcal{A}_4^{\text{YM}}\right]^{s=0}
-  = \frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} (2c_s-c_t-c_u)
-  =  \mathcal{A}_{(12|l)}^{\text{YM}}\mathcal{A}_{(-l|34)}^{\text{YM}} \, ,
-\end{equation}
-where we have applied the color structure Jacobi identity,
-$c_s+c_t+c_u=0$.
-In light of our findings in \cref{chefsKiss}, building color-dual numerators in this way where locality is only realized on-shell might be a more natural approach.
-While we can absolutely apply a generalized gauge
-transformation \cite{BCJ} to restore field theoretic locality to the
-cubic numerators, this could merely be an aesthetic choice that is only permissible at tree-level.
-
-Moreover, by abandoning traditional notions of off-shell
-locality, we incidentally have gained enough functional freedom to massage the
-color-dual numerators into a form that is manifestly gauge invariant
-for all particles. As an organizational principle, pulling out overall
-gauge-invariant factors comes with the added advantage of possibly simplifying
-a loop-level construction of color-dual numerators for Yang-Mills.
-
-\subsection{Future Directions}\label{sec:Discussion}
-With an eye towards generalizing the non-local construction above to future multi-loop studies, we note that the four-point half-ladder of Yang-Mills secretly makes use of the color-dual structure of NLSM.
-At four-point, we can construct permutation invariants from the single BCJ basis amplitude of both NLSM and pure YM theory as follows
-\be
-s t A^{\text{YM}}_{(s,t)} = t_8F^4 \qquad s t A^{\text{NLSM}}_{(s,t)} = s t u\, .
-\ee
-Using this, we can redefine the non-local numerators of \cref{nonLocalNum} so that the vector structure of YM is captured in a permutation invariant prefactor and the kinematic Jacobi identity is entirely due to the NLSM numerators
-\be
-N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s t u } \, .
-\ee
-where four-point pion numerator, $N_s^{\text{NLSM}}$, is given in \cref{pionNums}.
-One advantage of this construction is that it reduces some of the $D$-dimensional complexity of vector theories that arises due to the mixing between external polarization and
-internal loop momenta. But maybe more importantly, it puts all the heavy lifting of functional Jacobi relations on the scalar kinematic numerator, $N_{(12|34)}^{\text{NLSM}}$. Thus, rather
-than building an ansatz from the irreducible scalar products of
-\cref{eq:ym-basis}, one might instead consider the following construction
-\begin{equation}
-N^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
-\end{equation}
-where $\mathcal{O}_i$ are the on-shell gauge invariant tensor basis elements of
-\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ are
-rational functions of irreducible scalar products of \cref{eq:scalar-basis}.
-It would be interesting if a similar construction as our tree-level example could be uplifted to two-loop using the globally color-dual NLSM integrand that we have computed in this work.
-We see this as a natural future direction worth investigating that is now made possible by our findings.
-
-\subsection*{Acknowledgments}
-The authors would like to thank John Joseph Carrasco, Sasank Chava, Clifford Cheung, Kezhu Guo, Nia Robles, Aslan Seifi, Fei Teng, and Suna Zekio\u{g}lu for insightful conversations,
-feedback on earlier drafts, and encouragement throughout the completion of
-this work. This work was supported by the DOE under contract
-DE-SC0015910 and by the Alfred P. Sloan
-Foundation. Additionally we would like to acknowledge the Northwestern
-University Amplitudes and Insight group, the Department of Physics and
-Astronomy, and Weinberg College for their generous support.  Feynman
-diagrams were typeset using TikZ-Feynman \cite{Ellis:2016jkw}.
-
-\appendix
-\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
-\section{Catalog of color-dual theories}
-\label{sec:CKLagrangians}
-
-Below we review the four manifestly color-dual theories that we mention in
-the text, self-dual Yang-Mills (SDYM) \cite{Monteiro2011pc}, two formulations of NLSM \cite{Cheung:2016prv,Cheung:2020djz,Cheung:2021zvb}, and ZM \cite{Zakharov:1973pp, Cheung:2022mix}.  All
-of these theories are closely tied together by the semi-abelian YM
-theory in \cref{eq:semiYM}, which gives the cubic sector of pure YM.
-The manifestly color-dual equations of motion for SDYM and NLSM are
-derived by picking a gauge and then placing a constraint directly on the
-field strength. In almost all of these
-theories, Bose symmetry is broken or obscured at the Lagrangian level.
-Since Bose symmetry is broken, the ensuing kinetic mixing prevents color-dual representations beyond one-loop without the introduction of additional interactions.
-
-\subsection{Self-Dual Yang-Mills} The first example in the literature
-of color-dual Feynman rules is that of Yang-Mills theory in the
-self-dual sector (SDYM).  We summarize the appoach of
-Ref.~\cite{Monteiro2011pc} for extracting the kinematic algebra.
-To obtain the Lagrangian for self-dual Yang-Mills from standard Yang-Mills, we apply the
-self-duality condition that equates the non-abelian $SU(N)$ field
-strength,
-$F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu
-,A_\nu]$, to its dual two-form,
-\begin{equation}
-  \label{SDcon} F_{\mu\nu} = \frac{1}{2}
-  \varepsilon_{\mu\nu\rho\sigma}F^{\rho\sigma} \,.
-\end{equation}
-Solutions to the self-dual condition automatically satisfy the
-Yang-Mills equation of motion due to the Bianchi identity,
-\begin{equation}
-D^\mu F^{\mu\nu} = \frac{1}{2} \varepsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0 \,.
-\end{equation}
-Furthermore, field configurations that satisfy \cref{SDcon} correspond to instantons which are probed by the path integral in the full non-perturbative description of Yang-Mills.
-To construct a manifestly perturbative action, one begins by
-transforming from Cartesian coordinates to light cone coordinates,
-$(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, via
-\begin{equation}
-u = t+x,\quad v=t-x, \quad w = y+iz, \quad \bar{w} = y-iz\, ,
-\end{equation}
-which yields the invariant line element,
-\begin{equation}
-ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x} \,.
-\end{equation}
-Applying this coordinate transformation to the self-dual condition of
-\cref{SDcon}, produces three constraint equations on the field strength,
-\begin{align} \label{SDLightCone1}
-F_{uw} &=0
-\\
- \label{SDLightCone2}
- F_{uv} &= F_{w\bar{w}}
-\\
- \label{SDLightCone3}
- F_{v\bar{w}} &= 0\,.
-\end{align}
-In light-cone gauge, $A_u=0$, we the self-duality condition restricts the gauge field as follows:
-\begin{align}
-  A_u=0 \text{ and } (\ref{SDLightCone1}) \quad&\Rightarrow \quad A_w=0\\
-  A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad&\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}} \label{eq:sd-divs}\,.
-\end{align}
-The last constraint is satisfied by writing the gauge field in
-terms of a single scalar field $\Psi$ via
-\begin{equation}
-  \label{SDDef}
-A_v = \frac{1}{2} \partial_w \Psi ~~~ \text{ and } ~~~ A_{\bar{w}} = \frac{1}{2} \partial_u \Psi \,.
-\end{equation}
-Using this definition on the first self-dual constraint equation
-yields the following equation of motion for the dynamical scalar
-field:
-\begin{equation}
-  \label{SDEOM}
-(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0 \,.
-\end{equation}
-Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange
-multiplier, we obtain the following Lagrangian for
-self-dual Yang-Mills theory:
-\begin{equation}
-  \mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ] \,.
-\end{equation}
-The color-ordered cubic Feynman rule for this theory can be
-immediately read off as
-\begin{equation}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2} \,.
-\end{equation}
-In this form, the Lagrangian and Feynman rules are manifestly
-color-dual \textit{off-shell}.
-The effect of \cref{SDcon} on the full YM Lagrangian is to decouple the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex.
-Before proceeding, it is important to
-note that the mass-dimension of the theory appears to differ from that
-of Yang-Mills -- we comment on this in detail in \cref{Conventions}.
-
-\subsection{YZ-theory}
-Self-dual Yang-Mills involves explicit reliance on the spacetime
-dimension, which makes the theory poorly suited for constructing
-dimensionally-regulated loop-level amplitudes.  On the other hand,
-$YZ$-theory of \cite{Cheung:2016prv} is an honest $D$-dimensional theory that captures the
-classical physics of NLSM while
-manifesting the duality between color and kinematics.
-
-One can understand $YZ$-theory as a particular dimensional reduction of Yang-Mills in $D=2d+1$ dimensions \cite{Cheung:2017yef}, down to $d$-dimensions. 
-Starting with the Yang-Mills Lagrangian of \cref{eq:ym-lag}, one can redefine the gauge fields, $A_M$, in terms of $X$, $Y$ and $Z$ fields:
-\begin{align}
-X_M &= (X_\mu,0,-iX_\mu) 
-\\
-Y_M &= (0,Y,0) 
-\\
-Z_M &= (Z_\mu,0,iZ_\mu) 
-\end{align}
-where $X$ and $Z$ are $d$-vectors and $Y$ is a scalar field.
-Considering the conjugate nature of the $XZ$ propagator, in this work we make the replacement $X\rightarrow \bar{Z}$.
-Plugging in this redefinition of the gauge fields produces the following Lagrangian up to cubic order in the interactions
-\begin{equation}
-\mathcal{L}^{\text{YZ}} =\frac{1}{2} (\partial Y)^2 + (\partial Z)(\partial \bar{Z}) - g f^{abc} \left( \bar{Z}_{\mu\nu}Z^{\mu} Z^\nu + [Y,\partial_\mu Y] Z^\mu \right)\, .
-\end{equation}
-The Feynman rules for this Lagrangian are simply
-\begin{equation}
-\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = i (\varepsilon_3 p_2)\qquad \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{3})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{3})(\varepsilon_1\bar{\varepsilon}_3) \, .
-\end{equation}
-Note that the pure vector vertex on the right is \textit{exactly} what was obtain from semi-abelian YM in \cref{eq:semiYM}.
-We now review of the construction of NLSM numerators at tree-level from $YZ$-theory.
-In this construction, we can define $D$-dimensional generators of the kinematic algebra as follows,
-\be\label{eq:FeynmanRuleYYZ}
-T^a_{ij}= i \varepsilon_a(p_i-p_j)\,,
-\end{equation}
-where momentum conservation requires\,,
-\begin{equation}
-p_a + p_i + p_j =0\, .
-\end{equation}
-The kinematic half-ladder diagrams then take on the following concise form
-\begin{equation}
-n^{\text{NLSM}}_{(i|a_1a_2...a_n|j)} = {}_i\langle T^{a_1}T^{a_2}\cdots T^{a_n}\rangle_j\, .
-\end{equation}
-Since there are no pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the kinematic algebra is manifestly cubic.
-Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom because there are no quartic vertices.
-They can be defined implicitly through
-\begin{equation}
-[T^a,T^b]_{ij}= F^{a}_{\,b|c}T^c_{ij}\, .
-\end{equation}
-Given this definition, the Feynman rule associated with kinematic structure constant is
-\be\label{eq:FeynmanRuleXZZ}
-i F^{a}_{\,b|c} = (\varepsilon_b p_{ab})(\varepsilon_a\bar{\varepsilon}_c) - (\varepsilon_a p_{ab})(\varepsilon_b\bar{\varepsilon}_c)\, ,
-\end{equation}
-where $p_{ab}=p_a+p_b$ and $\varepsilon$ and $\bar{\varepsilon}$ are the polarizations of the $Z$-vectors particle and its conjugate field, respectively.
-The gauge-fixed state sum for this theory is simply
-\begin{equation}
-\sum_{\text{states}} \varepsilon^{\,\mu}_{(p)}\bar{\varepsilon}^{\,\nu}_{(-p)} = \eta^{\mu\nu}\, .
-\end{equation}
-Notice that the vector state sum is gauge fixed since the $YZ$ model explicitly chooses Lorenz gauge for the $Z$ particles, $\partial_\mu Z^\mu=0$.
-Tree-level NLSM amplitudes are recovered from the kinematic structure constants by plugging in
-\be\label{eq:onShellZStates}
-\varepsilon^\mu_{(p)} = p^\mu \qquad \bar{\varepsilon}^\mu_{(p)} = \frac{q^\mu}{pq}
-\end{equation}
- for the on-shell polarizations for $Z$ and $\bar{Z}$, respectively, where $q^2=0$ is some null reference momentum.
- The tree-level pion amplitude can then be defined in two equivalent ways,
-\begin{equation}
-\label{eq:TwoNLSMMethods}
-A^{\text{NLSM}} = A(...,Y,...,Y,...) ~~~ \text{ and } ~~~ A^{\text{NLSM}}= A(...,\bar{Z},...) \, ,
-\end{equation}
-where the ellipses denote additional on-shell $Z$-particles.
-In a suitable gauge, the kinematic numerators in the latter definition for pion scattering are equivalent to those of $J$-theory, where $\bar{Z}$ corresponds to the root leg of $J$-theory \cite{Cheung:2021zvb}.
-
-It is instructive to see how both of the constructions in \cref{eq:TwoNLSMMethods} produce valid tree-level amplitudes for the pion.
-First we will start with $Y$ particles on legs 1 and 4.
-Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
-\begin{align}
-n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
-\\
- n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})\, .
-\end{align}
-Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result,
-\be\label{eq:NLSMYZ4point}
-A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}\, .
-\end{equation}
-For the $Z$ and $\bar{Z}$ configuration, the numerators are 
-\begin{align}
-n^{\bar{Z}Z}_s &= {}_4\langle F^{3}F^{2}\rangle_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
-\\
- n^{\bar{Z}Z}_t &=   {}_2\langle F^{3}F^{4}\rangle_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}\, ,
-\end{align}
-where we have used the shorthand
-\begin{equation}
-{}_x \langle F^{a_1}F^{a_2}\cdots F^{a_n}\rangle _{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}\, .
-\end{equation}
-The polarization vector of the $\bar{Z}$ particle has not been contracted into the numerators above, resulting in the free $\mu_1$ index.
-These numerators produce the partial amplitude
-\begin{equation}
-A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}\, .
-\end{equation}
-Plugging in the on-shell polarization of the conjugate field in \cref{eq:onShellZStates} produces precisely the desired result of \cref{eq:NLSMYZ4point}.
-Indeed, this construction is valid to all multiplicity at tree-level.
-One can see this by considering the only two possible factorization channels that contribute to each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut,
-\begin{align} \label{YZCut1}
-A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
-\\
-&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...) \, . \label{YZCut2}
-\end{align}
-Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states.
-As long as we plug in valid on-shell states for $Z$ and $\bar{Z}$ from \cref{eq:onShellZStates}, these numerators will produce NLSM ordered amplitudes.
-Given this special property of $YZ$-theory (namely that the $Z\bar{Z}$ and $YY$ constructions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell.
-This is essentially what $J$-theory does, as we will show below.
-
-\subsection{J-theory}
-$J$-theory is obtained through a first order reformulation of NLSM in terms of the chiral current \cite{Cheung:2021zvb}.\footnote{For related formulations of NLSM that do not
-treat color-kinematics duality see \cite{Freedman:1980us,
-  Slavnov:1971mz}.} Two constraints are placed on the chiral current.  First, the field strength associated with $J_\mu$ should vanish,
-\begin{equation}
-\label{eq:FieldStrengthJ}
-F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0\, ,
-\end{equation}
-which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
-The second condition is that the chiral current should be in Lorenz gauge,
-\begin{equation}
-\label{eq:LorenzGaugeJ}
-\partial_\mu J^\mu=0\, ,
-\end{equation}
-which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
-Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
-\begin{equation}
-\label{eq:JTheoryEOM}
-\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
-\end{equation}
-Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
-Since both theories are in Lorenz gauge this means that \emph{J-theory and semi-abelian YM are identical}.
-Furthermore, this theory is one-to-one with the observables amplitudes of $YZ$-theory when only considering on-shell $Z$$\bar{Z}$ states.
-As such, the single vertex in this theory is the same as the pure vector vertex of $YZ$ theory in Lorenz gauge,
-\begin{equation}
-\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =i(\varepsilon_1 p_{2})(\varepsilon_2\bar{\varepsilon}_3) - i(\varepsilon_2 p_{1})(\varepsilon_1\bar{\varepsilon}_3)\, .
-\end{equation}
-By calculating an off-shell four-point correlation function it is possible to check that the Lagrangians of $J$-theory and semi-YM theory automatically satisfies color-kinematics duality, as described in \cref{offShellCK}.
-As might be expected, the kinematic algebra is the diffeomorphism algebra \cite{Cheung:2021zvb}. Note that the different external particles break manifest Bose symmetry.
-
-\subsection{Zakharov-Mikhailov theory}
-\label{sec:ZMTheory}
-While $J$-theory manifests color-kinematics duality, it only does so at
-tree level because $J$-theory breaks manifest Bose symmetry.  Manifest
-color-kinematics duality can be achieved at all loop orders by
-restricting $J$-theory to two spacetime dimensions where the chiral
-current can be dualized to a scalar
-$J^\mu = \varepsilon^{\mu\nu} \partial_\nu \varphi$, which trivially
-enforces Lorenz gauge.  After plugging $\varphi$ into
-\cref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$
-(rather than some new field) can be integrated in to obtain the
-Zakharov-Mikhailov (ZM) Lagrangian,
-\begin{equation}
-\label{eq:ZMLagrangian}
-\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) .
-\end{equation}
-This procedure makes it clear that ZM and NLSM encode the same
-classical physics, since their equations of motion are dual to each
-other.  Furthermore, ZM theory can also be motivated from SDYM theory.
-The power counting of the interaction term in the SDYM equation of
-motion \cref{SDEOM} makes it clear that the theory is critical in 2D.
-This suggests that the two lightcone coordinates $u$ and $w$ should be
-identified as the coordinates of the 2D space.  The 4D d'Alembertian
-in lightcone coordinates,
-$\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$,
-cannot be interpreted as the 2D equivalent, so the kinetic term of
-SDYM must be replaced with the correct 2D version.
-However, changing the kinetic term in \cref{cubicCKLag} will have no effect on the Jacobi identity of \cref{jacID}, and thus does not interfere with color-kinematics duality.
-
-The color-stripped Feynman rule for the three-point vertex can be read
-off from the Lagrangian \cref{eq:ZMLagrangian}, giving
-\begin{equation}
-\langle ab\rangle \equiv p_a^\mu \varepsilon_{\mu\nu} p_b^\nu\, .
-\end{equation}
-Unlike $J$-theory and $YZ$-theory, the color-stripped vertex is functionally antisymmetric on all legs
-\begin{equation}
-\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle \, .
-\end{equation}
-This key property is due to momentum conservation alone.
-To prove off-shell color kinematics duality for any multiplicity and
-loop order it is enough to observe that the sum of the off-shell $s$-,
-$t$-, and $u$-channel numerators sum to zero
-\begin{equation}
-\label{eq:ZMJacobi}
-\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 
-\end{equation}
-by virtue of the 2D Levi-Civita identity
-$\varepsilon_{\mu\nu}\varepsilon_{\rho\sigma} =
-\eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
-Amusingly, \cref{eq:ZMJacobi} is simply a manifestation of the
-Schouten identity.
-Since ZM theory manifests color-kinematics duality without any
-reference to the on-shell condition, a mass term can be added to ZM
-theory without spoiling color-kinematics duality \cite{Cheung:2022mix}. In general, if the
-on-shell conditions are not used, color-kinematics duality is
-unaffected by the details of the propagator structure.
-
-Of course, dramatically altering the pole structure could spoil locality in the
-double-copied theory.  As already mentioned, the only difference
-classically between ZM and SDYM is the propagator structure.  While
-both theories are color dual for the same reason, altering the
-propagators has profound consequences since SDYM tree amplitudes
-vanish and manifest color-kinematics does not persist to all loop
-orders.
-
-Color dual theories with the same interactions but different
-kinetic terms have appeared in the literature before.  For example,
-$J$-theory and the theory of non-Abelian fluids presented in
-\cite{Cheung:2020djz} differ only in their propagators. Specifically,
-taking the static limit of the fluid's $(D+1)$-dimensional kinetic
-term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates
-yields the relativistic d'Alembertian of $D$-dimensional $J$-theory.
-
-While the color-dual nature of ZM theory is rather elegant, the
-loop-level construction introduces complications when applying
-dimensional regularization. Similar to the difficulties of
-renormalizing chiral fermions \cite{tHooft:1972tcz}, there is ambiguity
-in promoting the integrands to formal $D$-dimensional expressions. As
-such, in our two-loop bootstrap of NLSM we only used the ZM
-integrands as a mechanism for reducing the residual gauge freedom in
-our final solution.
-
-\section{Spinor-helicity and conventions}\label{Conventions}
-
-We use the same conventions as Ref.~\cite{jjmcTASI2014}, which
-we quote now. The component-wise definitions of the spinor brackets are
-\begin{align}
-\langle ab \rangle &= \frac{(a_1 + i a_2)(b_0+b_3)-(b_1 + i b_2)(a_0+a_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
-\\
-[ab] &= \frac{(b_1 - i b_2)(a_0+a_3)-(a_1 - i a_2)(b_0+b_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
-\end{align}
-where the $a_i$ are components of the four-vector,
-$k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$,
-one can apply the on-shell condition, $k_a^2=k_b^2=0$, to show that
-\begin{equation}
-s_{ab} = (k_a+k_b)^2= \langle ab \rangle[ba]\,.
-\end{equation}
-Four-dimensional polarization dot products with fixed helicity states
-are mapped to
-\begin{equation}\label{eq:4DPols}
-\begin{aligned}
-k_a \cdot \varepsilon_b^{(+)} &= \frac{\langle q a \rangle[ab]}{\sqrt{2}\langle q b\rangle}\,,
-\qquad\quad \qquad
-k_a \cdot \varepsilon_b^{(-)} = -\frac{[qa]\langle ab\rangle}{\sqrt{2}[qb]}\,,
-\\
-\varepsilon_a^{(-)}\cdot \varepsilon_b^{(+)} &= - \frac{\langle q a\rangle [qb]}{ [qa]\langle q b\rangle} \,,
-\qquad \qquad
-\varepsilon_a^{(\pm)}\cdot \varepsilon_b^{(\pm)} = 0 \,,
-\end{aligned}
-\end{equation}
-Note that given the above definition, the spinor helicity variables
-carry the same mass dimension for both the angle and square
-brackets. In terms of the light-cone coordinates that we employed in
-\cref{sec:CKLagrangians}, the angles and squares can be rewritten as
-\begin{align}
-\langle ab \rangle &= \frac{a_w b_u-a_u b_w}{\sqrt{a_ub_u}}\,,
-\\
-[ab] &= \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{\sqrt{a_ub_u}}\,.
-\end{align}
-The conventions we use in the text where the holomorphic spinor,
-$X(p,k)$, carries extra mass dimension amounts to shifting
-the bracket by an overall factor,
-\begin{align}
-\langle ab \rangle &\rightarrow a_w b_u-a_u b_w \equiv X(a,b)\,,
-\\
-[ab] &\rightarrow \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{a_ub_u}\equiv Q(a,b)\, .
-\end{align}
-With this choice we still obtain the same completeness relation for the SDYM spinors,
-\begin{equation}
-X(a,b)Q(b,a) = \frac{1}{2}s_{ab}\, .
-\end{equation}
-
-\section{Regulating BEL integrals}\label{BELreg}
-This appendix covers the bubble-on-external-leg (BEL) integrals that result from the $n$-gon numerator of $Y\!Z$ theory.
-Before covering the BEL integrals themselves, we will need the appropriate numerator.
-Weight counting tells us that the $n$-gon master
-numerator must have $n$ on-shell $Z$-particles. Unitarity requires
-that there are three distinct contributions to the $n$-gon: one from an off-shell $Y$-loop particle and then two more from
-different orientations of a $\bar{Z}Z$-loop.  Thus, $YZ$ theory gives
-us the following one-loop $n$-gon numerator:
-\begin{equation}
-N^{n\text{-gon},YZ}_{(12...n)} = \langle T^{1}T^{2}\cdots T^{n}\rangle+ \langle F^1F^2\cdots F^n\rangle
-\end{equation}
-where $\langle\,\cdots\rangle$ indicates an internal contraction over the $YY$ and
-$\bar{Z}Z$ loops and $T$ and $F$ were given in \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, respectively.
-In terms of the external momenta $k_i$ and the loop momenta $\ell_i$, where $\ell_i$ flows into $k_i$ and out of $k_{i-1}$, the NLSM numerator is
-\begin{equation}
-N_{(12...n)}^{\text{NLSM}}=\langle T^{1}T^{2}\cdots T^{n}\rangle =2^n (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n)
-\end{equation}
-which is the same as \cref{NLSMnGon} after using $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$.
-Similarly, there is a pure vector contribution that is identical to the semi-abelian YM $n$-gon numerator that we constructed in \cref{SDYMnGon} after projecting external states along longitudinal modes $\varepsilon \rightarrow k$,
-\begin{equation}
- \langle F^1F^2\cdots F^n \rangle= D (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n) + \mathcal{O}(D^0)\, .
-\end{equation}
-The dimension-dependent factor essentially counts that number of
-internal vector states. While this $n$-gon is manifestly color-dual,
-it does not produce the right cuts for NLSM. However, the scalar
-contribution, that comes dressed with an overall factor $D$
-\textit{does} manifest the duality globally, and satisfies all the
-desired pion cuts due to the factorization of \cref{YZCut1} and \cref{YZCut2}. In order for the Feynman rules for $Y\!Z$ theory
-compute one-loop color-dual numerators consistent with NLSM cuts, one would have to add additional states to cancel off the spurious poles, while
-preserving color-kinematics duality. We leave this as a direction of
-future work.
-
-While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $\bar{Y}Y$ loop alone gives us the desired expression for the $n$-gon.
-However, as we noted in the text, the $n$-gon numerator has the strange property that it produces \textit{non-vanishing} bubble-on-external-leg (BEL) graphs.
-However, the BEL diagram integrates to zero after integral reduction.
-As an example, the four-point BEL diagram can be reconstructed from the $n$-gon,
-\begin{equation}
-N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234|\ell)}-N^{\text{NLSM}}_{(1243|\ell)}-N^{\text{NLSM}}_{(1342|\ell)}+N^{\text{NLSM}}_{(1432|\ell)}\, ,
-\end{equation}
-where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $\ell_i$, the BEL reduces to
-\begin{equation}
-N^{\text{BEL}}_{1|2,34} = s_{12} (\ell+k_1)^2 \ell^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \,.
-\end{equation}
-Notice there is an overall factor that cancels one of the propagators. Plugging this numerator into the amplitude produces an integral of the form
-\begin{equation}
-\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D \ell}{i\pi^{D/2}} \frac{\ell^\mu }{\ell^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}\, ,
-\end{equation}
-where we have introduced a mass regulator that will be proportional to the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$.
-Thus, in sufficiently large dimension, $D>2$, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
-
 \bibliographystyle{JHEP}

### 2023-09-28 notes/2loopNLSM.tex
fresh pull
added CS appendix

@@
 rule for the cubic vertex is
-\begin{equation}
+\begin{equation}\label{semiYMvert}
   \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
@@
 where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply
-\be
+\be\label{semiYMprop}
 \propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}.
@@
 vanish and manifest color-kinematics does not persist to all loop
-orders.
-
-Color dual theories with the same interactions but different
+orders.  Color dual theories with the same interactions but different
 kinetic terms have appeared in the literature before.  For example,
@@
 
+\subsection{Chern-Simons theory}
+\label{sec:CSTheory}
+The final theory that is unified by semi-abelian Yang-Mills is that Chern-Simons (CS) theory.
+As we will show below, plugging in appropriate on-shell states to the semi-YM ntegrands constructed in the text will produce precisely the kinematic numerators for this theory.
+Much like SDYM and ZM theory, the (CS) action as a preferred integer dimension of $D=3$,
+\be
+S_{\text{CS}} = \int d^3 x \,\text{tr}\left[\epsilon^{\mu\nu\rho} \left(A_\mu \partial_\nu A_\rho + \frac{2}{3}A_{\mu}A_{\nu}A_{\rho}\right)\right]
+\ee
+The color-dual properties of this theory was previously studied in ref.~\cite{Ben-Shahar:2021zww}, which demonstrated that color-kinematics duality is manifest off-shell.
+The Feynman rules for this theory can be pulled directly from the action, giving the following color-stripped three-point vertex and propagator:
+\be\label{CSFrule}
+\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} = \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2\varepsilon^{\rho}_3 \qquad \qquad \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
+\ee
+where $\epsilon^{\mu\nu\rho}$ is a 3D Levi-Civita symbol.
+At first glance, this seems far removed from the semi-abelian Yang-Mills analogs in \cref{semiYMvert} and \cref{semiYMprop}.
+However, the construct the on-shell amplitudes for CS theory, we must plug in the Fourier transforms of the on-shell currents, $\bar{\varepsilon}(p)$, as described in ref.~\cite{Ben-Shahar:2021zww}.
+These are related to the polarizations in the Feynman rules above as follows:
+\be
+\varepsilon^{\mu}(p) = \epsilon^{\mu\nu\rho} p^\nu \bar{\varepsilon}^\rho(p)
+\ee
+With this definition of the on-shell states, it is clear how the Feyman rules of \cref{CSFrule} is related to those of \cref{semiYMvert} and \cref{semiYMprop}: we simply must canonicalize the CS kinetic term by absorbing $ \epsilon^{\mu\nu\rho} k^\rho$ into the definition of the three-point vertex.
+\be
+ \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
+\quad \longrightarrow \quad  \propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}
+\ee
+This has the effect of orienting the three-point vertex of \cref{CSFrule}, by making the replacement $\varepsilon_i \rightarrow \epsilon^{\mu\nu\rho} k_i^\nu \bar{\varepsilon}^\rho_i$ on one of the legs:
+\begin{align}
+\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} =  \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2 (\epsilon^{\rho \alpha \beta} k_3^\alpha \bar{\varepsilon}^\beta_3) =    (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
+  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
+\end{align}
+where we have used the identity, $\epsilon^{\mu\nu\rho}\epsilon^{\rho\alpha\beta} = \eta^{\mu \alpha} \eta^{\nu \beta} -  \eta^{\mu \beta} \eta^{\nu \alpha}$.
+Thus as desired, the CS vertex is precisely the three-point vertex of \cref{semiYMvert}.
+Moreover, in this form it is also clear how to map the $D$-dimensional amplitudes of semi-YM to the 3D observables of CS theory, one simply makes the following replacement on all the external states of semi-abelian YM,
+\be
+\varepsilon^\mu_i \rightarrow \epsilon^{\mu\nu\rho} k^\nu_i \bar{\varepsilon}^\rho_i \qquad\qquad  \bar{\varepsilon}_i^\mu \rightarrow \bar{\varepsilon}^\mu_i
+\ee
+Upon making this replacement, one can map the amplitudes of $D$-dimensional semi-YM to 3D CS theory, $\mathcal{A}^{\text{semi-YM}}\rightarrow \mathcal{A}^{\text{CS}}$.
+While this may seem like a marginal gain at tree-level, by using our $D$-dimensional construction at one-loop, the manifestly color-dual integrands of \cref{SDYMnGon} can resolve regularization ambiguity of CS theory at loop-level due to its explicit dependence on $D=3$.
+For more background on CS theory, we refer the reader to ref.~\cite{Ben-Shahar:2021zww}.
 \section{Spinor-helicity and conventions}\label{Conventions}

### 2023-09-28 notes/2loopNLSM.tex
looks good - my hands are off

--- 2023-09-27 notes/2loopNLSM.tex
@@
 
+\subsection{Chern-Simons theory}
+\label{sec:CSTheory}
+The final theory that is unified by the semi-abelian Yang-Mills construction is Chern-Simons (CS) theory.
+As we will show below, plugging in appropriate on-shell states to the semi-YM numerators that we constructed in the text will produce precisely the kinematic numerators for CS theory.
+Much like SDYM and ZM theory, the CS action as a preferred integer dimension of $D=3$,
+\be
+S_{\text{CS}} = \int d^3 x \,\text{tr}\left[\epsilon^{\mu\nu\rho} \left(A_\mu \partial_\nu A_\rho + \frac{2}{3}A_{\mu}A_{\nu}A_{\rho}\right)\right]
+\ee
+where $\epsilon^{\mu\nu\rho}$ is a 3D Levi-Civita symbol.
+The color-dual properties of this theory was previously studied in ref.~\cite{Ben-Shahar:2021zww}, which demonstrated that color-kinematics duality is manifest off-shell.
+The Feynman rules for this theory can be pulled directly from the action, giving the following color-stripped three-point vertex and propagator:
+\be\label{CSFrule}
+\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} = \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2\varepsilon^{\rho}_3 \qquad \qquad \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
+\ee
+At first glance, this seems far removed from the semi-abelian Yang-Mills analogs in \cref{semiYMvert} and \cref{semiYMprop}.
+After all, semi-YM makes no reference to an anti-symmetric 3-tensor, and doesn't even have the mass-dimension as the CS theory vertex.
+However, to construct the full on-shell amplitudes of CS theory, we must plug in the Fourier transforms of the on-shell currents, $\bar{\varepsilon}(p)$, as described in ref.~\cite{Ben-Shahar:2021zww}.
+These are related to the polarizations, $\varepsilon_i$, of the Feynman rules above as follows:
+\be
+\varepsilon^{\mu}(p) = \epsilon^{\mu\nu\rho} p^\nu \bar{\varepsilon}^\rho(p)
+\ee
+With this definition of the on-shell states, it is clear how the Feyman rules of \cref{CSFrule} are related to those of \cref{semiYMvert} and \cref{semiYMprop} -- we must simply canonicalize the CS kinetic term by absorbing $ \epsilon^{\mu\nu\rho} k^\rho$ into the definition of the three-point vertex:
+\be
+ \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
+\quad \longrightarrow \quad  \propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}
+\ee
+This has the effect of orienting the three-point vertex of \cref{CSFrule}, by making the replacement $\varepsilon_i \rightarrow \epsilon^{\mu\nu\rho} k_i^\nu \bar{\varepsilon}^\rho_i$ on one of the legs:
+\begin{align}
+\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} =  \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2 (\epsilon^{\rho \alpha \beta} k_3^\alpha \bar{\varepsilon}^\beta_3) =    (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
+  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
+\end{align}
+where we have used the identity, $\epsilon^{\mu\nu\rho}\epsilon^{\rho\alpha\beta} = \eta^{\mu \alpha} \eta^{\nu \beta} -  \eta^{\mu \beta} \eta^{\nu \alpha}$.
+Thus as desired, the CS vertex is precisely the three-point vertex of \cref{semiYMvert}.
+Moreover, in this form it is also clear how to map the $D$-dimensional amplitudes of semi-YM to the 3D observables of CS theory, one simply makes the following replacement on all the external states of semi-abelian YM,
+\be
+\varepsilon^\mu_i \rightarrow \epsilon^{\mu\nu\rho} k^\nu_i \bar{\varepsilon}^\rho_i \qquad\qquad  \bar{\varepsilon}_i^\mu \rightarrow \bar{\varepsilon}^\mu_i
+\ee
+Upon making this replacement, one can map the amplitudes of $D$-dimensional semi-YM to CS theory defined in $D=3$, $\mathcal{A}^{\text{semi-YM}}\rightarrow \mathcal{A}^{\text{CS}}$.
+While this may seem like a marginal gain at tree-level, by using our $D$-dimensional construction at one-loop, the manifestly color-dual integrands of \cref{SDYMnGon} can resolve regularization ambiguity of CS theory due to its explicit dependence on $D=3$.
+For more background on CS theory, we refer the reader to ref.~\cite{Ben-Shahar:2021zww}.
 \section{Spinor-helicity and conventions}\label{Conventions}

### 2023-09-28 notes/2loopNLSM.tex
small edit
CS edits

--- 2023-09-27 notes/2loopNLSM.tex
@@
 linewidth=4pt]{eBox}
+
+\newcommand{\jm}[1]{\textcolor{blue}{\textbf{JM: }{#1}}}
 
@@
 numerators for both NLSM and the self-dual sector of Yang-Mills
-through one-loop. The construction of this theory, which we dub
+through one-loop. \jm{Mention CS here?} The construction of this theory, which we dub
 \textit{semi-abelian Yang-Mills}, relies on isolating the cubic sector
@@
 \ee
-We direct the reader to ref.~\cite{Pavao:2022kog} for further details.
+We direct the reader to Ref.~\cite{Pavao:2022kog} for further details.
 The expansion of \cref{eq:pureVecRABD} comes with the added advantage of making the transmutation relations of \cite{Cheung:2017ems} absolutely manifest.
@@
 heart of $YZ$-theory \cite{Cheung:2016prv}, $J$-theory
-\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
-\cite{Monteiro2011pc}.  Specifically, semi-abelian YM is simply a
+\cite{Cheung:2020djz,Cheung:2021zvb}, self-dual Yang-Mills
+\cite{Monteiro2011pc}, and Chern-Simons theory \cite{Ben-Shahar:2021zww}. \jm{I mentioned CS.}  Specifically, semi-abelian YM is simply a
 clever reinterpretation of the Lagrangian obtained by integrating an
@@
 produced by semi-abelian YM correspond to those of SDYM in \cref{SDYMnGon} 
-and NLSM in \cref{NLSMnGon}.  Due to the
+and NLSM in \cref{NLSMnGon}.  \jm{Mention CS?  Maybe something like `SDYM in (), NLSM in (), and Chern-Simons theory in \cref{sec:CSTheory}.'?}  Due to the
 kinetic mixing that stems from the broken Bose symmetry, \cref{2loopTension} shows why it is
@@
 
-Below we review the four manifestly color-dual theories that we mention in
-the text, self-dual Yang-Mills (SDYM) \cite{Monteiro2011pc}, two formulations of NLSM \cite{Cheung:2016prv,Cheung:2020djz,Cheung:2021zvb}, and ZM \cite{Zakharov:1973pp, Cheung:2022mix}.  All
+Below we review the five manifestly color-dual theories that we mention in
+the text, self-dual Yang-Mills (SDYM) \cite{Monteiro2011pc}, two formulations of NLSM \cite{Cheung:2016prv,Cheung:2020djz,Cheung:2021zvb}, ZM \cite{Zakharov:1973pp, Cheung:2022mix}, and Chern-Simons theory \cite{Ben-Shahar:2021zww}.
+\jm{I added CS} All
 of these theories are closely tied together by the semi-abelian YM
@@
 
-\subsection{J-theory}
+\subsection{$J$-theory}
 $J$-theory is obtained through a first order reformulation of NLSM in terms of the chiral current \cite{Cheung:2021zvb}.\footnote{For related formulations of NLSM that do not
@@
 Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
-Since both theories are in Lorenz gauge this means that \emph{J-theory and semi-abelian YM are identical}.
+Since both theories are in Lorenz gauge this means that \emph{$J$-theory and semi-abelian YM are identical}.
 Furthermore, this theory is one-to-one with the observables amplitudes of $YZ$-theory when only considering on-shell $Z$$\bar{Z}$ states.
@@
 our final solution.
+
+\subsection{Chern-Simons theory}
+\label{sec:CSTheory}
+The final theory that is unified by the semi-abelian Yang-Mills construction is \jm{(tree level) ?} Chern-Simons (CS) theory.
+As we will show below, plugging in appropriate on-shell states to the semi-YM numerators that we constructed in the text will produce precisely the kinematic numerators for CS theory.
+Much like SDYM and ZM theory, the CS action has a preferred integer dimension of $D=3$,
+\be
+S_{\text{CS}} = \int d^3 x \,\text{tr}\left[\epsilon^{\mu\nu\rho} \left(A_\mu \partial_\nu A_\rho + \frac{2}{3}A_{\mu}A_{\nu}A_{\rho}\right)\right]
+\label{eq:CSAction}
+\ee
+where $\epsilon^{\mu\nu\rho}$ is a 3D Levi-Civita symbol.
+The color-dual properties of this theory were previously studied in Ref.~\cite{Ben-Shahar:2021zww}, which demonstrated that color-kinematics duality is manifest off-shell.
+\jm{The next 2-3 sentences are new.}
+At the classical level, CS is clearly related to $J$-theory (and thus semi-YM) since the CS equation of motion,
+\be
+\epsilon^{\rho \mu \nu}F_{\mu\nu} =0 \Leftrightarrow F_{\mu\nu}=0 \, ,
+\ee
+and the Lorenz gauge choice,
+\be
+\partial_\mu A^\mu=0 \, ,
+\ee
+are the same as the $J$-theory conditions in \cref{eq:FieldStrengthJ,eq:LorenzGaugeJ}, respectively.
+
+The correspondence between CS and semi-YM can be made more precise at the level of the Feynman rules.
+The color-stripped three-point vertex and propagator can be read off from the CS action in \cref{eq:CSAction} producing
+\be\label{CSFrule}
+\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} = \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2\varepsilon^{\rho}_3 \qquad \qquad \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho \, .
+\ee
+At first glance, this seems far removed from the semi-abelian Yang-Mills analogs in \cref{semiYMvert} and \cref{semiYMprop}.
+After all, semi-YM makes no reference to an anti-symmetric 3-tensor and the mass dimensions of the vertices do not agree.
+However, to construct the full on-shell amplitudes of CS theory, we must plug in the Fourier transforms of the on-shell currents, $\bar{\varepsilon}(p)$, as described in Ref.~\cite{Ben-Shahar:2021zww}.
+\jm{How about we use $\varepsilon_\mu$ and $\epsilon_\mu$ like Henrik and Maor?
+I'm worried that the bar is getting overused a little.
+Or how about $\varepsilon$ and $\tilde{\varepsilon}$ but this will eventually involve $\tilde{\bar{\varepsilon}}$ which is a little gross?} These are related to the polarizations, $\varepsilon_i$, of the Feynman rules above as follows:
+\be
+\varepsilon^{\mu}(p) = \epsilon^{\mu\nu\rho} p^\nu \bar{\varepsilon}^\rho(p)\, .
+\ee
+With this definition of the on-shell states, it is clear how the Feynman rules of \cref{CSFrule} are related to those of \cref{semiYMvert} and \cref{semiYMprop} -- we must simply canonicalize the CS kinetic term by absorbing $ \epsilon^{\mu\nu\rho} k^\rho$ into the definition of the three-point vertex:
+\be
+ \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
+\quad \longrightarrow \quad  \propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}\,.
+\ee
+This has the effect of orienting the three-point vertex of \cref{CSFrule} by making the replacement $\varepsilon_i \rightarrow \epsilon^{\mu\nu\rho} k_i^\nu \bar{\varepsilon}^\rho_i$ on one of the legs,
+\begin{align}
+\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} =  \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2 (\epsilon^{\rho \alpha \beta} k_3^\alpha \bar{\varepsilon}^\beta_3) =    (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
+  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)\, ,
+\end{align}
+where we have used the identity $\epsilon^{\mu\nu\rho}\epsilon^{\rho\alpha\beta} = \eta^{\mu \alpha} \eta^{\nu \beta} -  \eta^{\mu \beta} \eta^{\nu \alpha}$.
+As desired, the redefined CS vertex is precisely the three-point vertex of semi-YM in \cref{semiYMvert}.
+Clearly the $D$-dimensional amplitudes of semi-YM can be mapped to the 3D observables of CS theory by making the following replacement on all of the external states of semi-abelian YM:
+\be
+\varepsilon^\mu_i \rightarrow \epsilon^{\mu\nu\rho} k^\nu_i \bar{\varepsilon}^\rho_i \qquad\qquad  \bar{\varepsilon}_i^\mu \rightarrow \bar{\varepsilon}^\mu_i \, .
+\ee
+Upon making this replacement, the amplitudes of $D$-dimensional semi-YM are mapped onto 3D CS theory, $\mathcal{A}^{\text{semi-YM}}\rightarrow \mathcal{A}^{\text{CS}}$.
+While this may seem like a marginal gain at tree-level, by using our $D$-dimensional construction at one-loop, the manifestly color-dual integrands of \cref{SDYMnGon} can resolve regularization ambiguity of CS theory due to its explicit dependence on $D=3$.
+For more background on CS theory, we refer the reader to Ref.~\cite{Ben-Shahar:2021zww}.
+
+\jm{Do we want to mention something about how it's not obvious in this formulation of CS that the amplitudes vanish?
+This also happens for NLSM where it's not obvious why odd multiplicity semi-YM amplitudes with the NLSM external states vanish.}
 
@@
 \begin{equation}
-X(a,b)Q(b,a) = \frac{1}{2}s_{ab}\, .
+X(a,b)Q(b,a) = s_{ab}\, .
 \end{equation}

### 2023-09-28 notes/2loopNLSM.tex
Ran through spell check

@@
   successfully construct globally color-dual
-  \emph{local} two-loop four-point nonlinear sigma model (NLSM) numerators.  The double-copy of the
+  \emph{local} two-loop four-point nonlinear sigma model (NLSM) numerators.  The double-copy of
 these NLSM numerators with themselves, pure Yang-Mills, and
   $\mathcal{N}=4$ super-Yang-Mills correctly reproduce the known unitarity constructed integrands 
-  of special Gallileons, Born-Infeld theory,
+  of special Galileons, Born-Infeld theory,
   and Dirac-Born-Infeld-Volkov-Akulov theory, respectively. 
@@
   We pinpoint the failure to the
-  bowtie unitarity cut, and discuss a path forward towards \emph{non-local}
+  bowtie unitarity cut and discuss a path forward towards \emph{non-local}
   construction of color-dual integrands at generic loop order.
@@
 We begin with an overview of color-kinematics duality in
-\cref{background}, and define the notion of ``globally'' color-dual integrands in \cref{sec:bootstrap}. 
+\cref{background} and define the notion of ``globally'' color-dual integrands in \cref{sec:bootstrap}. 
 We then construct a manifestly color-dual theory in
@@
 Faced with this obstruction, we study the multi-loop sector of both
-NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz based
+NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz-based
 color-dual bootstrap. In contrast to much of the available literature
@@
 benchmark for color-dual representations in non-supersymmetric gauge
-theories.  However in sharp contrast, we find that Yang-Mills does
+theories.  However, in sharp contrast, we find that Yang-Mills does
 \emph{not} permit a globally color-dual representation, even when
@@
   \cite{Bern:2015ooa}.}  Concretely, the failure point can be
-pinpointed to a conflict between between the ``bowtie'' cut and the
+pinpointed to a conflict between the ``bowtie'' cut and the
 following Jacobi triple:
@@
 \end{equation}
-We comment on the implications of this finding in \cref{conclusions},
+We comment on the implications of this finding in \cref{conclusions}
 and discuss alternative approaches where one must relax field
@@
 \end{equation}
-with legs $1$ and $n$ fixed.  Since the the sum only contains $(n-2)!$
+with legs $1$ and $n$ fixed.  Since the sum only contains $(n-2)!$
 terms, there must be additional relations -- the
@@
 \begin{align}
-\text{anti-symmetry}:& \quad{}_{\mu_1}\langle W^{\mu_2} \rangle_{\mu_3}+\text{cyc}(23)=0
+\text{antisymmetry}:& \quad{}_{\mu_1}\langle W^{\mu_2} \rangle_{\mu_3}+\text{cyc}(23)=0
 \\
@@
   Ben-Shahar:2021doh}.
-Typically when one goes about constructing color-dual
+Typically, when one goes about constructing color-dual
 theories directly from a set of cubic interactions, higher point
@@
 antisymmetric and hence have signs built into their orientations.
-When used in conjuction with the Jacobi relations, \eg{}
+When used in conjunction with the Jacobi relations, \eg{}
 \cref{eq:TwoLoopJacobiOne}, the symmetry constraints of non-basis
 graphs still impose conditions on the basis ansatz.  In fact, since
-the symmetry properites of a graph are directly linked with
+the symmetry properties of a graph are directly linked with
 transformations of its color dressing, the resulting constraints can
@@
 \end{equation}
-This kinematic vertex is anti-symmetric in $1\leftrightarrow 2$
+This kinematic vertex is antisymmetric in $1\leftrightarrow 2$
 exchange, and from it we can construct the full Lorenz gauge
@@
 With this in hand, we can construct a Lagrangian description of the of
-the cubic sector for Yang-Mills, and will demonstrate that the
+the cubic sector for Yang-Mills and will demonstrate that the
 resulting amplitudes with manifestly color-dual Feynman rules are
@@
 As noted above, we can select out the manifestly cubic
-sector of semi-abelian Yang-Mills from the full theory of \cref{eq:ym-lag} by selecting only $(\varepsilon^+\varepsilon^+)$ in light-cone gauge (i.e.
-SDYM) and one-minus at tree-level or by plugging in the on-shell states of $J$-theory \cite{Cheung:2020djz,Cheung:2021zvb} and
+sector of semi-abelian Yang-Mills from the full theory of \cref{eq:ym-lag} by selecting only $(\varepsilon^+\varepsilon^+)$ in light-cone gauge (i.e., SDYM) and one-minus at tree-level or by plugging in the on-shell states of $J$-theory \cite{Cheung:2020djz,Cheung:2021zvb} and
 $YZ$-theory \cite{Cheung:2016prv}. Indeed, semi-YM is just the following sum over building blocks
@@
 reintroduce $D$-dimensional vertices from the diagonal group of
-$G_L\times G_R$ that have the wrong weight. Doing so will necessarily permit internal
+$G_L\times G_R$ that have the wrong weight.
+\jm{Should we say quartic vertices with the wrong weight or something like that?
+We don't have $G_L$ and $G_R$ anymore.} Doing so will necessarily permit internal
 contractions of $\bar{A}_\mu A^\mu$,
@@
 higher-loop numerators.  For pions in particular, the two-loop no-go statement
-is only for \emph{one particular representation of the theory} so it does
+is only for \emph{one particular representation of the theory}, so it does
 not completely preclude the existence of a two-loop color-dual
@@
   parameters, so a different method is desirable.  One possibility is
-  to use a sprase solver, as often employed for integral reduction.
+  to use a sparse solver, as often employed for integral reduction.
   However, these solvers typically assume that the matrix has a very
@@
 non-pathological cuts containing a three-point vertex (such as the maximal
-cut) vanishe.  Imposing all relevant cuts leaves 765 free parameters
+cut) vanish.  Imposing all relevant cuts leaves 765 free parameters
 representing the generalized gauge freedom in the answer.
@@
 amplitudes.  In particular, we produce numerators for special
-Gallileons, Born-Infeld theory, and DBIVA by double-copying against
-pions, pure YM, and $\mathcal{N}=4$ sYM respectively
+Galileons (sGal), Born-Infeld (BI) theory, and Dirac-Born-Infeld-Volkov-Akulov (DBIVA) by double-copying against
+pions, pure YM, and $\mathcal{N}=4$ super-Yang-Mills (sYM) respectively
 \cite{Cachazo:2014xea,Cheung:2015ota,Cheung:2016drk}.  Such double-copy constructions are important nontrivial
@@
 in the single copy conspire to produce the double-copy theory's
-version of linear diffeomorphism invariance: enhanced shift symmetry for special Galilleons and gauge
+version of linear diffeomorphism invariance: enhanced shift symmetry for special Galileons and gauge
 invariance of the BI photon and DBIVA supermultiplet \cite{Hinterbichler:2015pqa}.  All
@@
 impossible to construct a two-loop integrand for semi-abelian YM theory.
-In \cref{2loopBoot}, we overcame this obstruction by successfully constructing two-loop NLSM numerators with an ansatz based bootstrap.
+In \cref{2loopBoot}, we overcame this obstruction by successfully constructing two-loop NLSM numerators with an ansatz-based bootstrap.
 However, we found that the same approach fails for two-loop pure Yang-Mills, and pin-pointed the failure to a particular unitarity cut captured by \cref{chefsKiss}.
@@
 While introducing some type of worldsheet formulation of color-dual numerators might seem unjustified given the results of this work, our findings certainly suggest that we must do \textit{something} to relax the constraint of off-shell locality, and realize locality only in the limit of
-\textit{on-shell} kinematics. This could be acheived by either modifying the kinetic term or potentially something new and more exotic. Below we provide some simple examples
+\textit{on-shell} kinematics. This could be achieved by either modifying the kinetic term or potentially something new and more exotic. Below we provide some simple examples
 at tree-level of what one might consider for implementing such a construction.
@@
 where $N_s = N_{(12|34)}$, $N_t = N_{(14|23)}$ and $N_u = N_{(13|42)}$. By construction, this functionally symmetric numerator is
-anti-symmetric and obeys the Jacobi identity
+antisymmetric and obeys the Jacobi identity
 \begin{equation}\label{nonLocalNum}
@@
 of color-dual Feynman rules is that of Yang-Mills theory in the
-self-dual sector (SDYM).  We summarize the appoach of
+self-dual sector (SDYM).  We summarize the approach of
 Ref.~\cite{Monteiro2011pc} for extracting the kinematic algebra.
@@
 \end{equation}
-where momentum conservation requires\,,
+where momentum conservation requires,
 \begin{equation}
@@
 Since both theories are in Lorenz gauge this means that \emph{$J$-theory and semi-abelian YM are identical}.
-Furthermore, this theory is one-to-one with the observables amplitudes of $YZ$-theory when only considering on-shell $Z$$\bar{Z}$ states.
+Furthermore, this theory is one-to-one with the amplitudes of $YZ$-theory when only considering on-shell $Z$$\bar{Z}$ states.
 As such, the single vertex in this theory is the same as the pure vector vertex of $YZ$ theory in Lorenz gauge,
@@
 At first glance, this seems far removed from the semi-abelian Yang-Mills analogs in \cref{semiYMvert} and \cref{semiYMprop}.
-After all, semi-YM makes no reference to an anti-symmetric 3-tensor and the mass dimensions of the vertices do not agree.
+After all, semi-YM makes no reference to an antisymmetric 3-tensor and the mass dimensions of the vertices do not agree.
 However, to construct the full on-shell amplitudes of CS theory, we must plug in the Fourier transforms of the on-shell currents, $\bar{\varepsilon}(p)$, as described in Ref.~\cite{Ben-Shahar:2021zww}.

### 2023-09-28 notes/2loopNLSM.tex
Revised comments

@@
 produced by semi-abelian YM correspond to those of SDYM in \cref{SDYMnGon} 
-and NLSM in \cref{NLSMnGon}.  \jm{Mention CS?  Maybe something like `SDYM in (), NLSM in (), and Chern-Simons theory in \cref{sec:CSTheory}.'?}  Due to the
+and NLSM in \cref{NLSMnGon}.  \jm{Mention CS?  Maybe something like `SDYM in \cref{SDYMnGon} 
+and NLSM in \cref{NLSMnGon}, where Chern-Simons theory is discussed in \cref{sec:CSTheory}.'?}  Due to the
 kinetic mixing that stems from the broken Bose symmetry, \cref{2loopTension} shows why it is
@@
 However, to construct the full on-shell amplitudes of CS theory, we must plug in the Fourier transforms of the on-shell currents, $\bar{\varepsilon}(p)$, as described in Ref.~\cite{Ben-Shahar:2021zww}.
-\jm{How about we use $\varepsilon_\mu$ and $\epsilon_\mu$ like Henrik and Maor?
-I'm worried that the bar is getting overused a little.
-Or how about $\varepsilon$ and $\tilde{\varepsilon}$ but this will eventually involve $\tilde{\bar{\varepsilon}}$ which is a little gross?} These are related to the polarizations, $\varepsilon_i$, of the Feynman rules above as follows:
+\jm{I'm worried that the bar over epsilons is getting overused.
+Howe about we use $e_\mu$ instead of $\bar{\varepsilon}_\mu$?
+We could use a tilde or $\epsilon$ but those both have issues.} These are related to the polarizations, $\varepsilon_i$, of the Feynman rules above as follows:
 \be
@@
 
-\jm{Do we want to mention something about how it's not obvious in this formulation of CS that the amplitudes vanish?
-This also happens for NLSM where it's not obvious why odd multiplicity semi-YM amplitudes with the NLSM external states vanish.}
+\jm{Can we mention somewhere that CS amplitudes vanish because the theory is topological?
+From the point of view of semi-YM it isn't obvious why the CS amplitudes should vanish (at least it isn't obvious to me), but a similar thing happens for odd multiplicity NLSM amplitudes.}
 

### 2023-09-28 notes/2loopNLSM.tex
final run through
Addressed James' comments

@@
 \newcommand{\jm}[1]{\textcolor{blue}{\textbf{JM: }{#1}}}
+\newcommand{\nhp}[1]{\textcolor{nhpRed}{\textbf{NHP: }{#1}}}
 
@@
   We pinpoint the failure to the
-  bowtie unitarity cut and discuss a path forward towards \emph{non-local}
+  bowtie unitarity cut, and discuss a path forward towards \emph{non-local}
   construction of color-dual integrands at generic loop order.
@@
 to permit color-dual representations at tree-level
-\cite{Feng:2010my,Cachazo:2014xea}, as case studies for advancing our
-understanding of the kinematic algebra toward the multi-loop level.
+\cite{Feng:2010my,Cachazo:2014xea}, as case studies to advance our
+understanding of the kinematic algebra at the multi-loop level.
 
 We begin with an overview of color-kinematics duality in
-\cref{background} and define the notion of ``globally'' color-dual integrands in \cref{sec:bootstrap}. 
+\cref{background}, and define the notion of ``globally'' color-dual integrands in \cref{sec:bootstrap}. 
 We then construct a manifestly color-dual theory in
 \cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point
-numerators for both NLSM and the self-dual sector of Yang-Mills
-through one-loop. \jm{Mention CS here?} The construction of this theory, which we dub
+numerators at both tree-level and one-loop. When plugging in appropriate on-shell states, 
+we find that these numerators underpin color-dual representations of self-dual Yang-Mills, NLSM and Chern-Simons theory
+through one-loop. \jm{Mention CS here?} \nhp{Added sentence} The construction of this theory, which we dub
 \textit{semi-abelian Yang-Mills}, relies on isolating the cubic sector
@@
 needed to fully realize non-abelian gauge symmetry. Despite the
-potency of this theory at one-loop, the construction runs into an
+potency of this theory through one-loop, the construction runs into an
 obstruction at two-loop, which we describe in \cref{2LoopObstruction}.
@@
 where $ \varepsilon_{(ij)} = \varepsilon_{i}\cdot \varepsilon_{j}$.
-However, the remaining terms can be absorbed into the definition of the
-four-point kinematic numerator as follows
+One way to absorb the remainder is with the four-point contact of \cref{eq:ym-lag}, which preserves non-abelian gauge invariance off-shell.
+However, this additional term can also be absorbed into the definition of the
+four-point kinematic numerator in a way that preserves the cubic graph construction as follows,
 \begin{equation}
@@
 \cite{Cheung:2020djz,Cheung:2021zvb}, self-dual Yang-Mills
-\cite{Monteiro2011pc}, and Chern-Simons theory \cite{Ben-Shahar:2021zww}. \jm{I mentioned CS.}  Specifically, semi-abelian YM is simply a
+\cite{Monteiro2011pc}, and Chern-Simons theory \cite{Ben-Shahar:2021zww}. \jm{I mentioned CS.} \nhp{Looks good}. Specifically, semi-abelian YM is simply a
 clever reinterpretation of the Lagrangian obtained by integrating an
@@
 As we describe in detail in \cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to extract the $D$-dependent part
-that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional
+that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional,
 scalars
@@
 \end{equation}
-At loop-level, this construction needs to be analytically continued to
+A derivation of this Feynman rule and the definition of light cone coordinates can be found in \cref{sec:CKLagrangians}. At loop-level, this construction needs to be analytically continued to
 general dimension in order to apply dimensional regularization at
-one-loop. This can be done using the cubic semi-YM vertices of the
-previous section
+one-loop. This can be acheived by using the cubic semi-YM vertices of the
+previous section,
 \begin{equation} \label{DdimSDYM}
@@
 permitting a $D$-dimensional construction of the one-loop
-integrand. As an example, the four-point numerator is
+integrand. As an example, the four-point box numerator is
 \begin{equation}
@@
 In order to produce non-vanishing interactions, we would need to
-reintroduce $D$-dimensional vertices from the diagonal group of
-$G_L\times G_R$ that have the wrong weight.
+reintroduce $D$-dimensional vertices from the full Yang-Mills Lagrangian of \cref{eq:ym-lag} that we dropped in our construction semi-abelian YM.
+In terms of cubic graphs, the additional interaction must necessarily have the opposite number of $\bar{A}_\mu$ and unbarred $A_\mu$ fields to that of \cref{semiYMvert}.
 \jm{Should we say quartic vertices with the wrong weight or something like that?
-We don't have $G_L$ and $G_R$ anymore.} Doing so will necessarily permit internal
+We don't have $G_L$ and $G_R$ anymore.} \nhp{Good catch -- I changed the phrasing} Reintroducing these oppositely oriented vertices allows for new internal
 contractions of $\bar{A}_\mu A^\mu$,
@@
 four-point contact needed for color-kinematics to be satisfied on all
-internal edges. By a simple weight counting argument, one can see that
+internal edges. Thus, by a simple weight counting argument, one can see that
 including this wrong sign interactions is unavoidable at two-loop and
@@
 total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is
-  not suited to solving large sets of equations with sixteen thousand
+  not well suited for solving large sets of equations with sixteen thousand
   parameters, so a different method is desirable.  One possibility is
@@
 produced by semi-abelian YM correspond to those of SDYM in \cref{SDYMnGon} 
-and NLSM in \cref{NLSMnGon}.  \jm{Mention CS?  Maybe something like `SDYM in \cref{SDYMnGon} 
-and NLSM in \cref{NLSMnGon}, where Chern-Simons theory is discussed in \cref{sec:CSTheory}.'?}  Due to the
+and NLSM in \cref{NLSMnGon}, along with Chern-Simons theory, which we discuss in \cref{sec:CSTheory}.  \jm{Mention CS?  Maybe something like `SDYM in \cref{SDYMnGon} 
+and NLSM in \cref{NLSMnGon}, where Chern-Simons theory is discussed in \cref{sec:CSTheory}.'?} \nhp{Done.} Due to the
 kinetic mixing that stems from the broken Bose symmetry, \cref{2loopTension} shows why it is
@@
 the text, self-dual Yang-Mills (SDYM) \cite{Monteiro2011pc}, two formulations of NLSM \cite{Cheung:2016prv,Cheung:2020djz,Cheung:2021zvb}, ZM \cite{Zakharov:1973pp, Cheung:2022mix}, and Chern-Simons theory \cite{Ben-Shahar:2021zww}.
-\jm{I added CS} All
+\jm{I added CS} \nhp{awesome.} All
 of these theories are closely tied together by the semi-abelian YM
@@
 \label{sec:CSTheory}
-The final theory that is unified by the semi-abelian Yang-Mills construction is \jm{(tree level) ?} Chern-Simons (CS) theory.
+The final theory that is unified by the semi-abelian Yang-Mills construction is \jm{(tree level) ?} \nhp{nope.
+loop-level too.} Chern-Simons (CS) theory.
 As we will show below, plugging in appropriate on-shell states to the semi-YM numerators that we constructed in the text will produce precisely the kinematic numerators for CS theory.
@@
 The color-dual properties of this theory were previously studied in Ref.~\cite{Ben-Shahar:2021zww}, which demonstrated that color-kinematics duality is manifest off-shell.
-\jm{The next 2-3 sentences are new.}
+\jm{The next 2-3 sentences are new.}  \nhp{looks awesome!}
 At the classical level, CS is clearly related to $J$-theory (and thus semi-YM) since the CS equation of motion,
@@
 Howe about we use $e_\mu$ instead of $\bar{\varepsilon}_\mu$?
-We could use a tilde or $\epsilon$ but those both have issues.} These are related to the polarizations, $\varepsilon_i$, of the Feynman rules above as follows:
+We could use a tilde or $\epsilon$ but those both have issues.} \nhp{I think it conventiently matches the notation of Maor and Henrik, and also lines up perfectly with semi-YM vertices.
+I suggest we keep.} These are related to the polarizations, $\varepsilon_i$, of the Feynman rules above as follows:
 \be
@@
 \ee
-Upon making this replacement, the amplitudes of $D$-dimensional semi-YM are mapped onto 3D CS theory, $\mathcal{A}^{\text{semi-YM}}\rightarrow \mathcal{A}^{\text{CS}}$.
+Upon making this replacement, the amplitudes of $D$-dimensional semi-YM are mapped onto CS theory in $D=3$, $\mathcal{A}^{\text{semi-YM}}\rightarrow \mathcal{A}^{\text{CS}}$.
 While this may seem like a marginal gain at tree-level, by using our $D$-dimensional construction at one-loop, the manifestly color-dual integrands of \cref{SDYMnGon} can resolve regularization ambiguity of CS theory due to its explicit dependence on $D=3$.
@@
 \jm{Can we mention somewhere that CS amplitudes vanish because the theory is topological?
-From the point of view of semi-YM it isn't obvious why the CS amplitudes should vanish (at least it isn't obvious to me), but a similar thing happens for odd multiplicity NLSM amplitudes.}
+From the point of view of semi-YM it isn't obvious why the CS amplitudes should vanish (at least it isn't obvious to me), but a similar thing happens for odd multiplicity NLSM amplitudes.} \nhp{I suggest we just let people check that Maor and Henrik's numerators vanish rather than putting our neck out.}
 

### 2023-09-28 notes/2loopNLSM.tex
Thus -> Therefore
Prepping for arxiv upload.

@@
 \def\mystrut{\rule[-2ex]{0ex}{6ex}}
-
-\usepackage{tikz-feynman}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Comment the following out to compile new images
-%
-%\usetikzlibrary{external}  
-%\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
-%\tikzexternalize[                     %% Activate externalization
-%prefix=images/,                    %% Avoid cluttering the directory
-%system call={                       %% Use lualatex in system call
-%  % pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" %"\texsource" || rm "\image.pdf"
-%},
-%]
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 linewidth=4pt]{eBox}
-
-\newcommand{\jm}[1]{\textcolor{blue}{\textbf{JM: }{#1}}}
-\newcommand{\nhp}[1]{\textcolor{nhpRed}{\textbf{NHP: }{#1}}}
 
@@
 compute gauge and gravity observables to high orders in perturbation
-theory \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv,
-  Carrasco:2021otn}, color-kinematics remains a conjecture at loop
+theory \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv}, color-kinematics remains a conjecture at loop
 level. Indeed, there are many examples in the literature where
@@
 We begin with an overview of color-kinematics duality in
-\cref{background}, and define the notion of ``globally'' color-dual integrands in \cref{sec:bootstrap}. 
-We then construct a manifestly color-dual theory in
-\cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point
-numerators at both tree-level and one-loop. When plugging in appropriate on-shell states, 
-we find that these numerators underpin color-dual representations of self-dual Yang-Mills, NLSM and Chern-Simons theory
-through one-loop. \jm{Mention CS here?} \nhp{Added sentence} The construction of this theory, which we dub
-\textit{semi-abelian Yang-Mills}, relies on isolating the cubic sector
-of pure Yang-Mills amplitudes from the four-point contacts that are
-needed to fully realize non-abelian gauge symmetry. Despite the
-potency of this theory through one-loop, the construction runs into an
-obstruction at two-loop, which we describe in \cref{2LoopObstruction}.
+\cref{background}, and define the notion of ``globally'' color-dual
+integrands in \cref{sec:bootstrap}.  We then construct a manifestly
+color-dual theory in \cref{sec:cubic}, which generates $D$-dimensional
+color-dual $n$-point numerators at both tree-level and one-loop. When
+plugging in appropriate on-shell states, we find that these numerators
+underpin color-dual representations of self-dual Yang-Mills, NLSM and
+Chern-Simons theory through one-loop. The construction of this theory,
+which we dub \textit{semi-abelian Yang-Mills}, relies on isolating the
+cubic sector of pure Yang-Mills amplitudes from the four-point
+contacts that are needed to fully realize non-abelian gauge
+symmetry. Despite the potency of this theory through one-loop, the
+construction runs into an obstruction at two-loop, which we describe
+in \cref{2LoopObstruction}.
 
@@
 contains an explicit factor of $s$ that cancels with the propagator
-and the same goes for the $t$- and $u$-channels.
-The net result is that the amplitude is a local function, just as one would expect for the pion tree
-amplitude.
+and the same goes for the $t$- and $u$-channels.  The net result is
+that the amplitude is a local function, just as one would expect for
+the pion four-point tree amplitude.
 
@@
 \end{equation}
-This is known as the double-copy construction \cite{BCJ,Bern:2010ue,BCJreview}.
-Importantly, the $\tilde{N}_\Gamma$ do not need to respect
-color-kinematics duality.  The prototypical example of the double-copy
-is that YM double copied with YM results in gravity where the gauge
-invariance of each separate gluon produces the diffeomorphism
-invariance of the graviton.  The double copy can be proven at tree
-level using the Kawai-Lewellen-Tye (KLT) relations but there is significant evidence that
-the double copy persists to all loop orders \cite{FiveLoopN4,
-  GeneralizedDoubleCopyFiveLoops, Bern:2018jmv, Carrasco:2021otn, KLT,
-  KiermaierTalk}.  In addition to pointing at undiscovered
-structure hidden in the Lagrangian for gravity, the double copy is
-immensely useful at a utilitarian level since it is much more
-efficient at producing $\mathcal{M}_n^L$ than traditional methods like
-Feynman rules.
+This is known as the double-copy construction
+\cite{BCJ,Bern:2010ue,BCJreview}.  Importantly, the $\tilde{N}_\Gamma$
+do not need to respect color-kinematics duality.  The prototypical
+example of the double-copy is that YM double copied with YM results in
+gravity where the gauge invariance of each separate gluon produces the
+diffeomorphism invariance of the graviton.  The double copy can be
+proven at tree level using the Kawai-Lewellen-Tye (KLT) relations but
+there is significant evidence that the double copy persists to all
+loop orders \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops,
+  Bern:2018jmv, KLT, KiermaierTalk}.  In addition to pointing at
+undiscovered structure hidden in the Lagrangian for gravity, the
+double copy is immensely useful at a utilitarian level since it is
+much more efficient at producing $\mathcal{M}_n^L$ than traditional
+methods like Feynman rules.
 
@@
 diagram can be reduced to a half-ladder through successive
-applications of the Jacobi identity.  At one-loop, every diagram can be
-related to one topology as well, in this case the $n$-gon, which can be understood as a forward limit of the half-ladder.  Two-loop
+applications of the Jacobi identity.  At one-loop, every diagram can
+be related to one topology as well, in this case the $n$-gon, which
+can be understood as a forward limit of the half-ladder.  Two-loop
 calculations play an important role in our understanding of
 color-kinematics duality because this is the first order where
-multiple basis graphs are required, at least for a generic theory. We refer the reader to \cite{BCJreview} for more background on the topic.
+multiple basis graphs are required, at least for a generic theory. We
+refer the reader to Ref.~\cite{BCJreview} for more background on the
+topic.
 
@@
 \cite{Cheung:2020djz,Cheung:2021zvb}, self-dual Yang-Mills
-\cite{Monteiro2011pc}, and Chern-Simons theory \cite{Ben-Shahar:2021zww}. \jm{I mentioned CS.} \nhp{Looks good}. Specifically, semi-abelian YM is simply a
+\cite{Monteiro2011pc}, and Chern-Simons theory
+\cite{Ben-Shahar:2021zww}. Specifically, semi-abelian YM is simply a
 clever reinterpretation of the Lagrangian obtained by integrating an
@@
 \end{equation}
-where $[\,\cdots]_a$ are terms with appropriate powers of $(\varepsilon k)$ and $(kk)$.
-As we describe in detail in \cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to extract the $D$-dependent part
-that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional,
-scalars
+where $[\,\cdots]_a$ are terms with appropriate powers of
+$(\varepsilon k)$ and $(kk)$. As we describe in detail in
+\cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to
+extract the $D$-dependent part that corresponds to an internal
+$\bar{Y}Y$-loop from extra-dimensional scalars
 \begin{eBox}
@@
 Our first application of this theory for color-dual construction at
-loop level is for self-dual Yang-Mills (SDYM). As we have done throughout the text, we will set all coupling constants to unity. At tree-level, the
-off-shell cubic vertices can be written in terms of light cone
-coordinates \cite{Monteiro2011pc}
+loop level is for self-dual Yang-Mills (SDYM). As we have done
+throughout the text, we will set all coupling constants to unity. At
+tree-level, the off-shell cubic vertices can be written in terms of
+light cone coordinates \cite{Monteiro2011pc}
 \begin{equation}
@@
 \end{equation}
-that is, the theory is one-loop exact.
-In order to produce non-vanishing interactions, we would need to
-reintroduce $D$-dimensional vertices from the full Yang-Mills Lagrangian of \cref{eq:ym-lag} that we dropped in our construction semi-abelian YM.
-In terms of cubic graphs, the additional interaction must necessarily have the opposite number of $\bar{A}_\mu$ and unbarred $A_\mu$ fields to that of \cref{semiYMvert}.
-\jm{Should we say quartic vertices with the wrong weight or something like that?
-We don't have $G_L$ and $G_R$ anymore.} \nhp{Good catch -- I changed the phrasing} Reintroducing these oppositely oriented vertices allows for new internal
-contractions of $\bar{A}_\mu A^\mu$,
+that is, the theory is one-loop exact.  In order to produce
+non-vanishing interactions, we would need to reintroduce
+$D$-dimensional vertices from the full Yang-Mills Lagrangian of
+\cref{eq:ym-lag} that we dropped in our construction semi-abelian
+YM. In terms of cubic graphs, the additional interaction must
+necessarily have the opposite number of $\bar{A}_\mu$ and unbarred
+$A_\mu$ fields to that of \cref{semiYMvert}.  Reintroducing these
+oppositely oriented vertices allows for new internal contractions of
+$\bar{A}_\mu A^\mu$,
 \begin{equation}\label{2loopTension}
@@
 four-point contact needed for color-kinematics to be satisfied on all
-internal edges. Thus, by a simple weight counting argument, one can see that
+internal edges. Therefore, by a simple weight counting argument, one can see that
 including this wrong sign interactions is unavoidable at two-loop and
@@
 
-In addition to the tree-level construction, we found that kinetic mixing
-between the two gauge fields permits globally color-dual one-loop
-integrands. After plugging in suitable on-shell states, the integrands
-produced by semi-abelian YM correspond to those of SDYM in \cref{SDYMnGon} 
-and NLSM in \cref{NLSMnGon}, along with Chern-Simons theory, which we discuss in \cref{sec:CSTheory}.  \jm{Mention CS?  Maybe something like `SDYM in \cref{SDYMnGon} 
-and NLSM in \cref{NLSMnGon}, where Chern-Simons theory is discussed in \cref{sec:CSTheory}.'?} \nhp{Done.} Due to the
-kinetic mixing that stems from the broken Bose symmetry, \cref{2loopTension} shows why it is
-impossible to construct a two-loop integrand for semi-abelian YM theory.
-In \cref{2loopBoot}, we overcame this obstruction by successfully constructing two-loop NLSM numerators with an ansatz-based bootstrap.
-However, we found that the same approach fails for two-loop pure Yang-Mills, and pin-pointed the failure to a particular unitarity cut captured by \cref{chefsKiss}.
-Thus, obtaining a globally color-dual
-integrand beyond one-loop then requires sacrificing more than just Bose
-symmetry, and in this paper we have argued that off-shell locality\footnote{An example of this can already be found in the literature, where locality is relaxed in Ref.~\cite{Mogull:2015adi} in
-  order to obtain color-dual two-loop integrands with on-shell 4D states.} must
-be abandoned for color-dual constructions of multi-loop Yang-Mills.
-To expand the available function space, we propose that one should consider including rational functions of kinematics, rather than just polynomials.
+In addition to the tree-level construction, we found that kinetic
+mixing between the two gauge fields permits globally color-dual
+one-loop integrands. After plugging in suitable on-shell states, the
+integrands produced by semi-abelian YM correspond to those of SDYM in
+\cref{SDYMnGon} and NLSM in \cref{NLSMnGon}, along with Chern-Simons
+theory, which we discuss in \cref{sec:CSTheory}.  Due to the kinetic
+mixing that stems from the broken Bose symmetry, \cref{2loopTension}
+shows why it is impossible to construct a two-loop integrand for
+semi-abelian YM theory. In \cref{2loopBoot}, we overcame this
+obstruction by successfully constructing two-loop NLSM numerators with
+an ansatz-based bootstrap. However, we found that the same approach
+fails for two-loop pure Yang-Mills, and pin-pointed the failure to a
+particular unitarity cut captured by \cref{chefsKiss}. Thus, obtaining
+a globally color-dual integrand beyond one-loop then requires
+sacrificing more than just Bose symmetry, and in this paper we have
+argued that off-shell locality\footnote{An example of this can already
+  be found in the literature, where locality is relaxed in
+  Ref.~\cite{Mogull:2015adi} in order to obtain color-dual two-loop
+  integrands with on-shell 4D states.} must be abandoned for
+color-dual constructions of multi-loop Yang-Mills. To expand the
+available function space, we propose that one should consider
+including rational functions of kinematics, rather than just
+polynomials.
 
@@
 
-Below we review the five manifestly color-dual theories that we mention in
-the text, self-dual Yang-Mills (SDYM) \cite{Monteiro2011pc}, two formulations of NLSM \cite{Cheung:2016prv,Cheung:2020djz,Cheung:2021zvb}, ZM \cite{Zakharov:1973pp, Cheung:2022mix}, and Chern-Simons theory \cite{Ben-Shahar:2021zww}.
-\jm{I added CS} \nhp{awesome.} All
-of these theories are closely tied together by the semi-abelian YM
-theory in \cref{eq:semiYM}, which gives the cubic sector of pure YM.
-The manifestly color-dual equations of motion for SDYM and NLSM are
-derived by picking a gauge and then placing a constraint directly on the
-field strength. In almost all of these
-theories, Bose symmetry is broken or obscured at the Lagrangian level.
-Since Bose symmetry is broken, the ensuing kinetic mixing prevents color-dual representations beyond one-loop without the introduction of additional interactions.
+Below we review the five manifestly color-dual theories that we
+mention in the text, self-dual Yang-Mills (SDYM)
+\cite{Monteiro2011pc}, two formulations of NLSM
+\cite{Cheung:2016prv,Cheung:2020djz,Cheung:2021zvb}, ZM
+\cite{Zakharov:1973pp, Cheung:2022mix}, and Chern-Simons theory
+\cite{Ben-Shahar:2021zww}.  All of these theories are closely tied
+together by the semi-abelian YM theory in \cref{eq:semiYM}, which
+gives the cubic sector of pure YM.  The manifestly color-dual
+equations of motion for SDYM and NLSM are derived by picking a gauge
+and then placing a constraint directly on the field strength. In
+almost all of these theories, Bose symmetry is broken or obscured at
+the Lagrangian level.  Since Bose symmetry is broken, the ensuing
+kinetic mixing prevents color-dual representations beyond one-loop
+without the introduction of additional interactions.
 
@@
 \label{sec:CSTheory}
-The final theory that is unified by the semi-abelian Yang-Mills construction is \jm{(tree level) ?} \nhp{nope.
-loop-level too.} Chern-Simons (CS) theory.
-As we will show below, plugging in appropriate on-shell states to the semi-YM numerators that we constructed in the text will produce precisely the kinematic numerators for CS theory.
-Much like SDYM and ZM theory, the CS action has a preferred integer dimension of $D=3$,
-\be
-S_{\text{CS}} = \int d^3 x \,\text{tr}\left[\epsilon^{\mu\nu\rho} \left(A_\mu \partial_\nu A_\rho + \frac{2}{3}A_{\mu}A_{\nu}A_{\rho}\right)\right]
+The final theory that is unified -- through one loop -- by the
+semi-abelian Yang-Mills construction is Chern-Simons (CS) theory. As
+we will show below, plugging in appropriate on-shell states to the
+semi-YM numerators that we constructed in the text will produce
+precisely the kinematic numerators for CS theory. Much like SDYM and
+ZM theory, the CS action has a preferred integer dimension of $D=3$,
+\begin{equation} S_{\text{CS}} = \int
+d^3 x \,\text{tr}\left[\epsilon^{\mu\nu\rho} \left(A_\mu \partial_\nu
+    A_\rho + \frac{2}{3}A_{\mu}A_{\nu}A_{\rho}\right)\right]
 \label{eq:CSAction}
-\ee
-where $\epsilon^{\mu\nu\rho}$ is a 3D Levi-Civita symbol.
-The color-dual properties of this theory were previously studied in Ref.~\cite{Ben-Shahar:2021zww}, which demonstrated that color-kinematics duality is manifest off-shell.
-\jm{The next 2-3 sentences are new.}  \nhp{looks awesome!}
-At the classical level, CS is clearly related to $J$-theory (and thus semi-YM) since the CS equation of motion,
-\be
-\epsilon^{\rho \mu \nu}F_{\mu\nu} =0 \Leftrightarrow F_{\mu\nu}=0 \, ,
-\ee
-and the Lorenz gauge choice,
-\be
-\partial_\mu A^\mu=0 \, ,
-\ee
-are the same as the $J$-theory conditions in \cref{eq:FieldStrengthJ,eq:LorenzGaugeJ}, respectively.
+\end{equation}
+where $\epsilon^{\mu\nu\rho}$ is a 3D Levi-Civita symbol. The
+color-dual properties of this theory were previously studied in
+Ref.~\cite{Ben-Shahar:2021zww}, which demonstrated that
+color-kinematics duality is manifest off-shell.  At the classical
+level, CS is clearly related to $J$-theory (and thus semi-YM) since
+the CS equation of motion, \be \epsilon^{\rho \mu \nu}F_{\mu\nu} =0
+\Leftrightarrow F_{\mu\nu}=0 \, , \ee and the Lorenz gauge choice, \be
+\partial_\mu A^\mu=0 \, , \ee are the same as the $J$-theory
+conditions in \cref{eq:FieldStrengthJ,eq:LorenzGaugeJ}, respectively.
 
@@
 The color-stripped three-point vertex and propagator can be read off from the CS action in \cref{eq:CSAction} producing
-\be\label{CSFrule}
+\begin{equation}
+  \label{CSFrule}
 \cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} = \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2\varepsilon^{\rho}_3 \qquad \qquad \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho \, .
-\ee
-At first glance, this seems far removed from the semi-abelian Yang-Mills analogs in \cref{semiYMvert} and \cref{semiYMprop}.
-After all, semi-YM makes no reference to an antisymmetric 3-tensor and the mass dimensions of the vertices do not agree.
-However, to construct the full on-shell amplitudes of CS theory, we must plug in the Fourier transforms of the on-shell currents, $\bar{\varepsilon}(p)$, as described in Ref.~\cite{Ben-Shahar:2021zww}.
-\jm{I'm worried that the bar over epsilons is getting overused.
-Howe about we use $e_\mu$ instead of $\bar{\varepsilon}_\mu$?
-We could use a tilde or $\epsilon$ but those both have issues.} \nhp{I think it conventiently matches the notation of Maor and Henrik, and also lines up perfectly with semi-YM vertices.
-I suggest we keep.} These are related to the polarizations, $\varepsilon_i$, of the Feynman rules above as follows:
-\be
-\varepsilon^{\mu}(p) = \epsilon^{\mu\nu\rho} p^\nu \bar{\varepsilon}^\rho(p)\, .
-\ee
+\end{equation}
+At first glance, this seems far removed from the semi-abelian
+Yang-Mills analogs in \cref{semiYMvert} and \cref{semiYMprop}. After
+all, semi-YM makes no reference to an antisymmetric 3-tensor and the
+mass dimensions of the vertices do not agree. However, to construct
+the full on-shell amplitudes of CS theory, we must plug in the Fourier
+transforms of the on-shell currents, $\bar{\varepsilon}(p)$, as
+described in Ref.~\cite{Ben-Shahar:2021zww}.  These are related to the
+polarizations, $\varepsilon_i$, of the Feynman rules above as follows:
+\begin{equation}
+\varepsilon^{\mu}(k) = \epsilon^{\mu\nu\rho} k^\nu \bar{\varepsilon}^\rho(k)\, .
+\end{equation}
 With this definition of the on-shell states, it is clear how the Feynman rules of \cref{CSFrule} are related to those of \cref{semiYMvert} and \cref{semiYMprop} -- we must simply canonicalize the CS kinetic term by absorbing $ \epsilon^{\mu\nu\rho} k^\rho$ into the definition of the three-point vertex:
-\be
+\begin{equation}
  \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
 \quad \longrightarrow \quad  \propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}\,.
-\ee
+\end{equation}
 This has the effect of orienting the three-point vertex of \cref{CSFrule} by making the replacement $\varepsilon_i \rightarrow \epsilon^{\mu\nu\rho} k_i^\nu \bar{\varepsilon}^\rho_i$ on one of the legs,
 \begin{align}
-\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} =  \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2 (\epsilon^{\rho \alpha \beta} k_3^\alpha \bar{\varepsilon}^\beta_3) =    (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
+  \cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} \rightarrow \cubic{hgrey0}{}{fermion2}{}{fermion2}{}{fermion2} =
+  \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2 (\epsilon^{\rho \alpha \beta} k_3^\alpha \bar{\varepsilon}^\beta_3) =    (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
   -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)\, ,
 \end{align}
-where we have used the identity $\epsilon^{\mu\nu\rho}\epsilon^{\rho\alpha\beta} = \eta^{\mu \alpha} \eta^{\nu \beta} -  \eta^{\mu \beta} \eta^{\nu \alpha}$.
-As desired, the redefined CS vertex is precisely the three-point vertex of semi-YM in \cref{semiYMvert}.
-Clearly the $D$-dimensional amplitudes of semi-YM can be mapped to the 3D observables of CS theory by making the following replacement on all of the external states of semi-abelian YM:
-\be
-\varepsilon^\mu_i \rightarrow \epsilon^{\mu\nu\rho} k^\nu_i \bar{\varepsilon}^\rho_i \qquad\qquad  \bar{\varepsilon}_i^\mu \rightarrow \bar{\varepsilon}^\mu_i \, .
-\ee
-Upon making this replacement, the amplitudes of $D$-dimensional semi-YM are mapped onto CS theory in $D=3$, $\mathcal{A}^{\text{semi-YM}}\rightarrow \mathcal{A}^{\text{CS}}$.
-While this may seem like a marginal gain at tree-level, by using our $D$-dimensional construction at one-loop, the manifestly color-dual integrands of \cref{SDYMnGon} can resolve regularization ambiguity of CS theory due to its explicit dependence on $D=3$.
-For more background on CS theory, we refer the reader to Ref.~\cite{Ben-Shahar:2021zww}.
-
-\jm{Can we mention somewhere that CS amplitudes vanish because the theory is topological?
-From the point of view of semi-YM it isn't obvious why the CS amplitudes should vanish (at least it isn't obvious to me), but a similar thing happens for odd multiplicity NLSM amplitudes.} \nhp{I suggest we just let people check that Maor and Henrik's numerators vanish rather than putting our neck out.}
+where we have used the identity
+$\epsilon^{\mu\nu\rho}\epsilon^{\rho\alpha\beta} = \eta^{\mu \alpha}
+\eta^{\nu \beta} - \eta^{\mu \beta} \eta^{\nu \alpha}$. As desired,
+the redefined CS vertex is precisely the three-point vertex of semi-YM
+in \cref{semiYMvert}. Clearly the $D$-dimensional amplitudes of
+semi-YM can be mapped to the 3D observables of CS theory by making the
+following replacement on all of the external states of semi-abelian
+YM: \be \varepsilon^\mu_i \rightarrow \epsilon^{\mu\nu\rho} k^\nu_i
+\bar{\varepsilon}^\rho_i \qquad\qquad \bar{\varepsilon}_i^\mu
+\rightarrow \bar{\varepsilon}^\mu_i \, .  \ee Upon making this
+replacement, the amplitudes of $D$-dimensional semi-YM are mapped onto
+CS theory in $D=3$,
+$\mathcal{A}^{\text{semi-YM}}\rightarrow
+\mathcal{A}^{\text{CS}}$. While this may seem like a marginal gain at
+tree-level, by using our $D$-dimensional construction at one-loop, the
+manifestly color-dual integrands of \cref{SDYMnGon} can resolve
+regularization ambiguity of CS theory due to its explicit dependence
+on $D=3$. For more background on CS theory, we refer the reader to
+Ref.~\cite{Ben-Shahar:2021zww}.
 

### 2023-12-04 notes/2loopNLSM/2loopNLSM.tex
tar ball for JHEP

--- 2023-09-28 notes/2loopNLSM.tex
@@
 
-\input{tikz_nonsense.tex}
+\input{tikz_preamble.tex}
 
@@
 We were able overcome this barrier by employing a custom
-solver, \texttt{FiniteFieldSolve}, which will soon be made
-public.
+solver, \texttt{FiniteFieldSolve} \cite{finitefieldsolve}.
 
@@
   is no such separation of sectors in a scalar theory.  Thus the NLSM
-  constraint equations were solved using a custom solver, working name
+  constraint equations were solved using a custom solver, 
   \texttt{FiniteFieldSolve}, designed to exactly solve large linear
-  systems of arbitrary density.  \texttt{FiniteFieldSolve} will be
-  released publicly shortly.} Imposing the boundary Jacobi relations
+  systems of arbitrary density \cite{finitefieldsolve}.} Imposing the boundary Jacobi relations
 eliminates all but 4,473 of the original free parameters.  Further

### 2024-02-07 RefereeResponse/response/RefereeResponse.tex
Referee response v1

%\documentclass[notitlepage, 11pt]{revtex4-1}
%\linespread{1.4}

\documentclass[notitlepage, 12pt]{revtex4-1}
\linespread{1.2}

\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=0.75in,rmargin=0.75in}
\usepackage{color}
\usepackage{babel}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{esint}
\usepackage[T1]{fontenc}

\usepackage{enumitem}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{url}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{hyperref}
 \hypersetup{colorlinks=true,citecolor=blue,linkcolor=blue}
\renewcommand{\bibfont}{\footnotesize}
\usepackage{fancyheadings}
%\pagestyle{fancy}
\renewcommand{\headrulewidth}{12pt}

\makeatother

\usepackage{babel}
\begin{document}

\title{Response to Referee: JHEP\_031P\_1223}

\date{\today}

\maketitle

We would like to begin by sincerely thanking the referee for their careful reading of the manuscript.
We believe their thoughtful comments and suggestions have produced a better paper.

The referee pointed out that the manuscript contained insufficient context for the two-loop results.
Specifically, the referee noted that a comparison with $\mathcal{N}=4$ super-Yang Mills (sYM) was absent.
We could not agree more and we apologize for the oversight.
Below is summary of the modifications to the manuscript.
\begin{itemize}
\item A small comment has been added to the introduction at the top of page 2 reminding readers that color-dual representations of sYM have been found to high loop order.
\item At the bottom of page 2, when stating that there is no local 4pt 2-loop numerator for pure YM we remind readers that such a numerator exists for sYM.
\item At the end of the introduction at the top of page 3 we clarify that the bowtie cut failure is specific to pure YM.
We go on to speculate that this is because sYM and NLSM are simpler theories, at least as far as color-kinematics is concerned.
\item Although the referee suggested adding comments to the introduction and section 4, we have included one additional modification.
Section 2.3 deals with ansatz locality so this seemed like a natural place to mention that the sYM ans\"atze incorporate locality as a key simplifying assumption.
At the bottom of page 7 and the top of page 8, we emphasize that the sYM numerators through four loops are local.
Even though the double copy has been performed for sYM at five loops, local numerators have not been found.
We comment in footnote 4 that the full set of local numerators has never been fully explored for sYM at 4pt 5-loop.
\item The first paragraph in section 4 closes by putting our results in the context of sYM, specifically by reminding readers of the state of the art in that theory.
\item Footnote 10 at the beginning of section 4.3 reminds readers again of the state of the art in sYM.
\item After stating the bowtie failure condition for pure YM in (4.9) we state that NLSM and sYM do not suffer from this failure, likely because they are simpler theories in some sense.
\end{itemize}

We would like to thank the referees again for their carefully considered feedback.
Their suggestions have improved the readability of the manuscript.
We believe all of their comments have been addressed and the the paper should be ready for publication.

\

Best regards,

Alex Edison, James Mangan, and Nic Pavao

\end{document}

### 2024-02-07 RefereeResponse/paper/2loopNLSM.tex
Referee response v1

--- 2023-12-04 notes/2loopNLSM/2loopNLSM.tex
@@
 compute gauge and gravity observables to high orders in perturbation
-theory \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv}, color-kinematics remains a conjecture at loop
-level. Indeed, there are many examples in the literature where
+theory, notably $\mathcal{N}=4$ super-Yang Mills (sYM) at five loops \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv}, color-kinematics remains a conjecture at loop
+level. %Referee edit
+Indeed, there are many examples in the literature where
 identifying color-dual representations beyond one-loop has posed a
@@
 that globally manifests the duality off-shell. This represents a new
-benchmark for color-dual representations in non-supersymmetric gauge
-theories.  However, in sharp contrast, we find that Yang-Mills does
-\emph{not} permit a globally color-dual representation, even when
+benchmark for color-dual representations in non-supersymmetric
+theories.
+However, in sharp contrast to both sYM \cite{BRY} and NLSM, we find that Yang-Mills does %Referee edit.  Am I citing the right paper?
+\emph{not} permit a globally color-dual two-loop representation, even when
 considering the most general polynomial ansatz of Lorentz covariant
@@
   limited ansatz subject to certain loop power counting constraints
-  \cite{Bern:2015ooa}.}  Concretely, the failure point can be
+  \cite{Bern:2015ooa}.}
+  Concretely, the failure point can be
 pinpointed to a conflict between the ``bowtie'' cut and the
@@
 \begin{equation}
+\label{eq:IntroBowtieFailure}
    \NMCutC
@@
 \end{equation}
-We comment on the implications of this finding in \cref{conclusions}
+This failure is specific to Yang-Mills and does not occur for its maximally supersymmetric counterpart or for NLSM, indicating that pure Yang-Mills is a more complicated theory in some sense.
+%Referee edit
+We comment on the implications of \cref{eq:IntroBowtieFailure} in \cref{conclusions}
 and discuss alternative approaches where one must relax field
@@
 power counting and external states. Locality is physically motivated since Feynman
-rules produce polynomial numerators. Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of
-kinematics. However, insisting on a local numerator is
+rules produce polynomial numerators.
+Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of kinematics.
+However, insisting on a local numerator is
 partly a matter of convenience as the ansatz for a rational function
 would quickly grow out of control without a guiding principle for what
-terms to include.  While these
-assumptions are well motivated from a physical and complexity
+terms to include.  %Referee edit
+Historically, locality has also proved a highly successful tool for simplifying kinematic numerators. %Alex, can you add more relevant references to the next two sentences?
+For example, the four-point function for $\mathcal{N}=4$ super-Yang Mills admits local color-dual numerators through four loops \cite{FivePointN4BCJ}.\footnote{At five loops, the most general local ansatz has not been explored, but the double copy has been performed at five loops using alternative methods \cite{FivePointN4BCJ}.}
+While locality is well motivated from a physical and complexity
 standpoint, the literature has featured numerators that violate
@@
 search space beyond what was covered in Ref.~\cite{Bern:2015ooa} to include the most general local ansatz.
+Even though this work is concerned with non-supersymmetric theories, recall that \ansatze{} techniques have been very successful for sYM.  %Referee edit
+In particular, local color-dual representations have been found through 4pt 4-loop \cite{}. %What paper should we cite?
+While a local representation has not been found at five loops, the double copy has still be performed \cite{FivePointN4BCJ}.
 
@@
 to investigate the most general local numerator for YM, without any of
-the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.  We
-follow the same general procedure as in \cref{sec:pions}, again
+the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.\footnote{As mentioned at the beginning of this section, \emph{supersymmetric} Yang-Mills is known to have a local color-dual representation at least through four loops \cite{BRY}.
+A local but restricted ansatz fails at five loops, but the most general local ansatz has not been explored \cite{FivePointN4BCJ}.} %Referee edits.
+What papers should we cite?
+We follow the same general procedure as in \cref{sec:pions}, again
 identifying the double-box and penta-triangle as the
@@
 are incompatible with the ``bowtie'' cut.
+Note that NLSM and sYM do not suffer from this failure, suggesting that they are more privileged theories in some sense.%Referee edit
 

### 2024-02-08 RefereeResponse/paper/2loopNLSM.tex
Alex's pass on reference for RefReport.

@@
 
-Despite the tremendous success in leveraging this duality to
-compute gauge and gravity observables to high orders in perturbation
-theory, notably $\mathcal{N}=4$ super-Yang Mills (sYM) at five loops \cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv}, color-kinematics remains a conjecture at loop
-level. %Referee edit
-Indeed, there are many examples in the literature where
-identifying color-dual representations beyond one-loop has posed a
-formidable challenge
-\cite{Mogull:2015adi, Johansson:2017bfl, KalinN2TwoLoop, Bern:2015ooa}. In this work, we use
-the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven
-to permit color-dual representations at tree-level
-\cite{Feng:2010my,Cachazo:2014xea}, as case studies to advance our
-understanding of the kinematic algebra at the multi-loop level.
+Despite the tremendous success in leveraging this duality to compute
+gauge and gravity observables to high orders in perturbation theory,
+notably $\mathcal{N}=4$ super-Yang Mills (sYM) at five loops
+\cite{FiveLoopN4, GeneralizedDoubleCopyFiveLoops, Bern:2018jmv},
+color-kinematics remains a conjecture at loop level. %Referee edit
+Indeed, there are many examples in the literature where identifying
+color-dual representations beyond one-loop has posed a formidable
+challenge \cite{Mogull:2015adi, Johansson:2017bfl, KalinN2TwoLoop,
+  Bern:2015ooa}. In this work, we use the nonlinear sigma model (NLSM)
+and Yang-Mills, two theories proven to permit color-dual
+representations at tree-level \cite{Feng:2010my,Cachazo:2014xea}, as
+case studies to advance our understanding of the kinematic algebra at
+the multi-loop level.
 
@@
 local (polynomial) functions of the graph kinematics with the correct
-power counting and external states. Locality is physically motivated since Feynman
-rules produce polynomial numerators.
-Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of kinematics.
-However, insisting on a local numerator is
-partly a matter of convenience as the ansatz for a rational function
-would quickly grow out of control without a guiding principle for what
-terms to include.  %Referee edit
-Historically, locality has also proved a highly successful tool for simplifying kinematic numerators. %Alex, can you add more relevant references to the next two sentences?
-For example, the four-point function for $\mathcal{N}=4$ super-Yang Mills admits local color-dual numerators through four loops \cite{FivePointN4BCJ}.\footnote{At five loops, the most general local ansatz has not been explored, but the double copy has been performed at five loops using alternative methods \cite{FivePointN4BCJ}.}
-While locality is well motivated from a physical and complexity
-standpoint, the literature has featured numerators that violate
-locality, modify naive power counting through the inclusion of higher
-spin modes, and break manifest Lorentz invariance \cite{Square,
-  WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ,
-  Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv,
-  Cheung:2021zvb}.  These developments suggest that relaxing locality
-is a viable alternative when the condition proves too stringent for an
-ansatz.  However, simply requiring on-shell locality may suffice.
-This alternative will be discussed in \cref{nonLocalScattering}.
+power counting and external states. Locality is physically motivated
+since Feynman rules produce polynomial numerators.  Indeed, the most
+natural way to guarantee locality and avoid spurious poles is to
+require the off-shell numerators to be polynomial functions of
+kinematics.  However, insisting on a local numerator is partly a
+matter of convenience as the ansatz for a rational function would
+quickly grow out of control without a guiding principle for what terms
+to include.  %Referee edit
+Historically, locality has also proved a highly successful tool for
+simplifying kinematic
+numerators. %Alex, can you add more relevant references to the next two sentences?
+For example, the four-point function for $\mathcal{N}=4$ super-Yang
+Mills admits local color-dual numerators through four loops
+\cite{Bern:2012uf}.\footnote{At five loops, the most general local
+  ansatz has not been explored, but the double copy has been performed
+  at five loops using alternative methods \cite{GeneralizedDoubleCopy,
+    GeneralizedDoubleCopyFiveLoops}.}  While locality is
+well motivated from a physical and complexity standpoint, the
+literature has featured numerators that violate locality, modify naive
+power counting through the inclusion of higher spin modes, and break
+manifest Lorentz invariance \cite{Square, WeinzierlBCJLagrangian,
+  Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl,
+  Ben-Shahar:2022ixa, Cheung:2016prv, Cheung:2021zvb}.  These
+developments suggest that relaxing locality is a viable alternative
+when the condition proves too stringent for an ansatz.  However,
+simply requiring on-shell locality may suffice.  This alternative will
+be discussed in \cref{nonLocalScattering}.
 
@@
 theories, but that these methods cannot be reapplied to generate
-higher-loop numerators.  For pions in particular, the two-loop no-go statement
-is only for \emph{one particular representation of the theory}, so it does
-not completely preclude the existence of a two-loop color-dual
-integrand.  We thus turn to the color-dual bootstrap method
-described in \cref{sec:bootstrap} to construct a color-dual
-representation of two-loop four-point NLSM.  Because of the similarity
-of the problem setup, we will also use the opportunity to revisit the
-construction of a color-dual representation of pure YM, extending the
-search space beyond what was covered in Ref.~\cite{Bern:2015ooa} to include the most general local ansatz.
-Even though this work is concerned with non-supersymmetric theories, recall that \ansatze{} techniques have been very successful for sYM.  %Referee edit
-In particular, local color-dual representations have been found through 4pt 4-loop \cite{}. %What paper should we cite?
-While a local representation has not been found at five loops, the double copy has still be performed \cite{FivePointN4BCJ}.
+higher-loop numerators.  For pions in particular, the two-loop no-go
+statement is only for \emph{one particular representation of the
+  theory}, so it does not completely preclude the existence of a
+two-loop color-dual integrand.  We thus turn to the color-dual
+bootstrap method described in \cref{sec:bootstrap} to construct a
+color-dual representation of two-loop four-point NLSM.  Because of the
+similarity of the problem setup, we will also use the opportunity to
+revisit the construction of a color-dual representation of pure YM,
+extending the search space beyond what was covered in
+Ref.~\cite{Bern:2015ooa} to include the most general local ansatz.
+Even though this work is concerned with non-supersymmetric theories,
+recall that \ansatze{} techniques have been very successful for
+sYM.  %Referee edit
+In particular, local color-dual representations have been found
+through 4pt 4-loop \cite{Bern:2012uf}. %What paper should we cite?
+While a local representation has not been found at five loops, the
+double copy has still be performed
+\cite{GeneralizedDoubleCopy,GeneralizedDoubleCopyFiveLoops}.
 
@@
 to investigate the most general local numerator for YM, without any of
-the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.\footnote{As mentioned at the beginning of this section, \emph{supersymmetric} Yang-Mills is known to have a local color-dual representation at least through four loops \cite{BRY}.
-A local but restricted ansatz fails at five loops, but the most general local ansatz has not been explored \cite{FivePointN4BCJ}.} %Referee edits.
-What papers should we cite?
+the loop power counting assumptions of
+Ref.~\cite{Bern:2015ooa}.\footnote{As mentioned at the beginning of
+  this section, \emph{maximally supersymmetric} Yang-Mills is known to have a
+  local color-dual representation at least through four loops
+  \cite{Bern:2012uf}.  A local but restricted ansatz fails at five loops, but
+  the most general local ansatz has not been explored
+  \cite{GeneralizedDoubleCopyFiveLoops}.} %Referee edits.  What papers should we cite?
 We follow the same general procedure as in \cref{sec:pions}, again
-identifying the double-box and penta-triangle as the
-Jacobi basis graphs and building the most general ansatz for each of
-their numerators compatible with the assumptions in
-\cref{sec:bootstrap}.  Because we are now considering pure
-Yang-Mills, each monomial in the local ansatz must consist of five
-Lorentz scalar dot products instead of the six for NLSM, and each
-monomial must be linear in each of the four external gluon
-polarizations.  Thus, the numerator ansatz for both diagrams will be
-built from terms of the form
+identifying the double-box and penta-triangle as the Jacobi basis
+graphs and building the most general ansatz for each of their
+numerators compatible with the assumptions in \cref{sec:bootstrap}.
+Because we are now considering pure Yang-Mills, each monomial in the
+local ansatz must consist of five Lorentz scalar dot products instead
+of the six for NLSM, and each monomial must be linear in each of the
+four external gluon polarizations.  Thus, the numerator ansatz for
+both diagrams will be built from terms of the form
 \begin{equation}

### 2024-02-09 RefereeResponse/response/RefereeResponse.tex
added commentary, edited response

@@
 
-\title{Response to Referee: JHEP\_031P\_1223}
+\title{Response to Editor: JHEP\_031P\_1223}
 
@@
 \maketitle
+Dear Editor,
+
+\
 
@@
 We believe their thoughtful comments and suggestions have produced a better paper.
-
-The referee pointed out that the manuscript contained insufficient context for the two-loop results.
-Specifically, the referee noted that a comparison with $\mathcal{N}=4$ super-Yang Mills (sYM) was absent.
-We could not agree more and we apologize for the oversight.
-Below is summary of the modifications to the manuscript.
+The referee suggested more context for the two-loop results, and noted that a comparison with $\mathcal{N}=4$ super-Yang Mills (sYM) was absent.
+We agree that adding this context provides a necessary framing of the main technical results.
+To this end, below is a summary of the modifications to the manuscript:
 \begin{itemize}
@@
 We go on to speculate that this is because sYM and NLSM are simpler theories, at least as far as color-kinematics is concerned.
-\item Although the referee suggested adding comments to the introduction and section 4, we have included one additional modification.
+\item In addition to the comments in the introduction and section 4, we have included one additional modification.
 Section 2.3 deals with ansatz locality so this seemed like a natural place to mention that the sYM ans\"atze incorporate locality as a key simplifying assumption.
 At the bottom of page 7 and the top of page 8, we emphasize that the sYM numerators through four loops are local.
-Even though the double copy has been performed for sYM at five loops, local numerators have not been found.
 We comment in footnote 4 that the full set of local numerators has never been fully explored for sYM at 4pt 5-loop.
 \item The first paragraph in section 4 closes by putting our results in the context of sYM, specifically by reminding readers of the state of the art in that theory.
-\item Footnote 10 at the beginning of section 4.3 reminds readers again of the state of the art in sYM.
-\item After stating the bowtie failure condition for pure YM in (4.9) we state that NLSM and sYM do not suffer from this failure, likely because they are simpler theories in some sense.
+Another such reminder is included in footnote 10 at the beginning of section 4.3.
+\item After stating the bowtie failure condition for pure YM in (4.9) we give specific reasons for why NLSM and sYM are more privileged than pure YM consistent with the ``bow-tie'' cut. 
 \end{itemize}
@@
 We would like to thank the referees again for their carefully considered feedback.
-Their suggestions have improved the readability of the manuscript.
-We believe all of their comments have been addressed and the the paper should be ready for publication.
+Now that the referees comments have been addressed, and we believe that the improved the readability of the manuscript makes it an excellent fit for JHEP.
 

### 2024-02-09 RefereeResponse/paper/2loopNLSM.tex
added commentary, edited response

@@
   We pinpoint the failure to the
-  bowtie unitarity cut, and discuss a path forward towards \emph{non-local}
+  bowtie unitarity cut, and discuss a path forward towards non-local
   construction of color-dual integrands at generic loop order.
@@
 its concealed structures has expanded dramatically. At the heart of this
-progress is the mantra that physical observables are simpler when
-studied on-shell
+progress is the mantra that \emph{physical observables are simpler when
+studied on-shell}
 \cite{Parke:1986gb,TasiLance,Cheung:2017pzi}. However, while inserting on-shell states certainly offers a path towards taming the
@@
 \begin{equation}
-  \mathcal{A}_n = \sum \limits_{\sigma\in S_{n-1}} \text{Tr}(T^{a_{\sigma_1}} T^{a_{\sigma_2}}...T^{a_{\sigma_{n-1}}} T^{a_n}) A_n[\sigma_1, \sigma_2,...\sigma_{n-1}, n],
+  \mathcal{A}_n = \sum \limits_{\sigma\in S_{n-1}} \text{Tr}(T^{a_{\sigma_1}} T^{a_{\sigma_2}}\cdots T^{a_{\sigma_{n-1}}} T^{a_n}) A_n[\sigma_1, \sigma_2,...,\sigma_{n-1}, n],
   \label{eq:trace-basis}
@@
 \begin{equation}
-\text{DDM}[a_1, a_2,... a_n] \equiv f^{a_1 a_2 b_1} f^{b_1 a_3 b_2} f^{b_2 a_4 b_3}...f^{b_{n-3} a_{n-1} a_n}
+\text{DDM}[a_1, a_2,..., a_n] \equiv f^{a_1 a_2 b_1} f^{b_1 a_3 b_2} f^{b_2 a_4 b_3}\cdots f^{b_{n-3} a_{n-1} a_n}
 \end{equation}
@@
 \begin{equation}
-  \mathcal{A}_n = \sum \limits_{\sigma\in S_{n-2}} \text{DDM}[a_1, a_{\sigma_2}, a_{\sigma_3}, a_{\sigma_{n-1}}, a_n]  A_n[1, \sigma_2,...\sigma_{n-1}, n]
+  \mathcal{A}_n = \sum \limits_{\sigma\in S_{n-2}} \text{DDM}[a_1, a_{\sigma_2}, ..., a_{\sigma_{n-1}}, a_n]  A_n[1, \sigma_2,...,\sigma_{n-1}, n]
   \label{eq:ddm-basis}
@@
 \begin{equation}
-\sum \limits_{i=2}^{n-1} k_1 \cdot (k_2+...+k_i) A_n[2,...,i,1,i+1,...,n] =0.
+\sum \limits_{i=2}^{n-1} k_1 \cdot (k_2+\cdots+k_i) A_n[2,...,i,1,i+1,...,n] =0.
 \end{equation}
@@
 theories directly from a set of cubic interactions, higher point
-Jacobi and antisymmetry constraints require introducing additional operators \cite{Carrasco:2022lbm,Carrasco:2022sck} or propagating fields \cite{Ben-Shahar:2022ixa}.
+Jacobi and antisymmetry constraints require introducing additional operators \cite{Carrasco:2022lbm,Carrasco:2022sck,Carrasco:2023wib} or propagating fields \cite{Ben-Shahar:2022ixa}.
 Indeed, as we will show in \cref{sec:cubic}, Yang-Mills
@@
 elaborated on below.\footnote{The four ansatz conditions are similar
-  to those of Ref.~\cite{Bern:2015ooa} except that there the authors
-  demand that the numerators have the same loop power counting as
-  Feynman gauge Feynman rules.  This is an additional assumption that
-  is most emphatically not made here.}
+  to those of Ref.~\cite{Bern:2015ooa}. However, in that work the authors
+  demand that the numerators have the same loop power counting as Feynman rules for vector fields in Feynman gauge.
+This additional assumption of theirs, which most emphatically is not made here, places more restrictive constraints on the ansatz than our conditions.}
 After imposing the four constraints below, any remaining coefficients in the ansatz encode ``generalized gauge freedom'', meaning that the
@@
 this manifestly color-dual theory \textit{semi-abelian Yang-Mills},
-\begin{eBox}
 \begin{equation}
@@
 \end{equation}
-\end{eBox}
 where
@@
 \end{equation}
-and $A_\mu$ is in Lorenz gauge. We can construct this Lagrangian from \cref{eq:ym-lag} by keeping the right field strength covariant under
+and $A_\mu$ is in Lorenz gauge, so that $\partial_\mu A^\mu =0$. We can construct this Lagrangian from \cref{eq:ym-lag} by keeping the right field strength covariant under
 $U(N)$, and making the left field strength gauge covariant under
@@
 extract the $D$-dependent part that corresponds to an internal
-$\bar{Y}Y$-loop from extra-dimensional scalars
-\begin{eBox}
+$\bar{Y}Y$-loop from extra-dimensional scalars,
 \begin{equation}
@@
 \end{equation}
-\end{eBox}
 Why must we take the derivative with respect to $D$? After all,
@@
 four-point contact needed for color-kinematics to be satisfied on all
-internal edges. Therefore, by a simple weight counting argument, one can see that
+internal edges. Thus, by a simple weight counting argument, one can see that
 including this wrong sign interactions is unavoidable at two-loop and
@@
 
-Thus, to construct two-loop numerators prescriptively, as we have done at one-loop, would require knowledge of
+Therefore, to construct two-loop numerators prescriptively, as we have done at one-loop, would require knowledge of
 the full kinematic algebra for Yang-Mills off-shell.  Since this is presently unavailable, we will tackle the two-loop integrand using an ansatz approach.
@@
 The contrapositive to this surprising result can be summarized in the following diagrammatic statement, which prioritizes the physical unitarity cut:
-\begin{eBox}
 \begin{equation}\label{chefsKiss}
@@
 are incompatible with the ``bowtie'' cut.
-Note that NLSM and sYM do not suffer from this failure, suggesting that they are more privileged theories in some sense.%Referee edit
+Note that NLSM and $\mathcal{N}=4$ sYM do not suffer from this failure, suggesting that they are more privileged theories in some sense.
+
+Concretely, in this work we have found that the power counting of NLSM offers sufficient generalized gauge freedom to manifest the duality globally, while maintaining compatibility with the ``bowtie'' cut.
+Whereas in the case of $\mathcal{N}=4$ sYM, by virtue of permitting a local construction consistent with \cref{chefsKiss}, the supersymmetric state sum\footnote{Due to the presence of fermionic modes that propagate off-shell in $\mathcal{N}=4$ sYM amplitudes, some of the pure vector contributions will be cancelled in the ``bow-tie'' cut, which leads to simpler cut expressions \cite{SuperSum}.} must be sufficiently simple, in such a way that it absorbs cut contributions present in the pure gluon state sum that we have shown are inconsistent with a globally color-dual polynomial ansatz.
+As such, the result of \cref{chefsKiss} is due to the power counting of pure YM being too restrictive to account for the complexity posed by the pure gluon ``bow-tie'' cut.
+%Referee edit
 
@@
 Since there are no pole cancelling factors of $s_{ij} = (p_i+p_j)^2$, this definition of the kinematic algebra is manifestly cubic.
-Thus, the kinematic structure constants defined in terms of these generators are invariant under generalized gauge freedom because there are no quartic vertices.
+Thus, the kinematic structure constants, $F^{a}_{\,b|c}$, defined in terms of the generators, $T^a_{ij}$, are invariant under generalized gauge freedom because there are no quartic vertices.
 They can be defined implicitly through

### 2024-02-09 RefereeResponse/response/RefereeResponse.tex
Small referee edits

@@
 \documentclass[notitlepage, 12pt]{revtex4-1}
-\linespread{1.2}
+\linespread{1.1}
 
@@
 We believe their thoughtful comments and suggestions have produced a better paper.
-The referee suggested more context for the two-loop results, and noted that a comparison with $\mathcal{N}=4$ super-Yang Mills (sYM) was absent.
+The referee suggested more background for the two-loop results, and noted that a comparison with $\mathcal{N}=4$ super-Yang Mills (sYM) was absent.
 We agree that adding this context provides a necessary framing of the main technical results.
@@
 \item A small comment has been added to the introduction at the top of page 2 reminding readers that color-dual representations of sYM have been found to high loop order.
-\item At the bottom of page 2, when stating that there is no local 4pt 2-loop numerator for pure YM we remind readers that such a numerator exists for sYM.
+\item At the bottom of page 2, when stating that there is no local 4pt 2-loop numerator for pure YM, we remind readers that such a numerator exists for sYM.
 \item At the end of the introduction at the top of page 3 we clarify that the bowtie cut failure is specific to pure YM.
@@
 Another such reminder is included in footnote 10 at the beginning of section 4.3.
-\item After stating the bowtie failure condition for pure YM in (4.9) we give specific reasons for why NLSM and sYM are more privileged than pure YM consistent with the ``bow-tie'' cut. 
+\item After stating the bowtie failure condition for pure YM in (4.9) we have added a paragraph explaining why NLSM and sYM are more privileged with regards to color-kinematics duality and the bowtie cut.
 \end{itemize}
 
-We would like to thank the referees again for their carefully considered feedback.
-Now that the referees comments have been addressed, and we believe that the improved the readability of the manuscript makes it an excellent fit for JHEP.
+We would like to thank the referee again for their carefully considered feedback.
+Now that the referee's comments have been addressed and the readability of the manuscript has been improved, we believe that the paper would be an excellent fit for publication in JHEP.
 

### 2024-02-09 RefereeResponse/paper/2loopNLSM.tex
Small referee edits

@@
 theories.
-However, in sharp contrast to both sYM \cite{BRY} and NLSM, we find that Yang-Mills does %Referee edit.  Am I citing the right paper?
+However, in sharp contrast to both sYM \cite{BRY} and NLSM, we find that Yang-Mills does %Referee edit
 \emph{not} permit a globally color-dual two-loop representation, even when
@@
 simplifying kinematic
-numerators. %Alex, can you add more relevant references to the next two sentences?
+numerators.
 For example, the four-point function for $\mathcal{N}=4$ super-Yang
@@
 In particular, local color-dual representations have been found
-through 4pt 4-loop \cite{Bern:2012uf}. %What paper should we cite?
+through 4pt 4-loop \cite{Bern:2012uf}.
 While a local representation has not been found at five loops, the
-double copy has still be performed
+double copy has still been performed
 \cite{GeneralizedDoubleCopy,GeneralizedDoubleCopyFiveLoops}.
@@
   the most general local ansatz has not been explored
-  \cite{GeneralizedDoubleCopyFiveLoops}.} %Referee edits.  What papers should we cite?
+  \cite{GeneralizedDoubleCopyFiveLoops}.} %Referee edit
 We follow the same general procedure as in \cref{sec:pions}, again
@@
 Concretely, in this work we have found that the power counting of NLSM offers sufficient generalized gauge freedom to manifest the duality globally, while maintaining compatibility with the ``bowtie'' cut.
-Whereas in the case of $\mathcal{N}=4$ sYM, by virtue of permitting a local construction consistent with \cref{chefsKiss}, the supersymmetric state sum\footnote{Due to the presence of fermionic modes that propagate off-shell in $\mathcal{N}=4$ sYM amplitudes, some of the pure vector contributions will be cancelled in the ``bow-tie'' cut, which leads to simpler cut expressions \cite{SuperSum}.} must be sufficiently simple, in such a way that it absorbs cut contributions present in the pure gluon state sum that we have shown are inconsistent with a globally color-dual polynomial ansatz.
-As such, the result of \cref{chefsKiss} is due to the power counting of pure YM being too restrictive to account for the complexity posed by the pure gluon ``bow-tie'' cut.
+Whereas in the case of $\mathcal{N}=4$ sYM, by virtue of permitting a local construction consistent with \cref{chefsKiss}, the supersymmetric state sum\footnote{Due to the presence of fermionic modes that propagate off-shell in $\mathcal{N}=4$ sYM amplitudes, some of the pure vector contributions will be cancelled in the ``bowtie'' cut, which leads to simpler cut expressions \cite{SuperSum}.} must be sufficiently simple, in such a way that it absorbs cut contributions present in the pure gluon state sum that we have shown are inconsistent with a globally color-dual polynomial ansatz.
+As such, the result of \cref{chefsKiss} is due to the power counting of pure YM being too restrictive to account for the complexity posed by the pure gluon ``bowtie'' cut.
 %Referee edit

### 2024-03-20 RefereeResponse/paper/2loopNLSM.tex
Redline corrections

@@
 where $i$, $j$, and $k$ are three graphs.  Example Jacobi relations
-are presented in detail in \cref{sec:bootstrap}. The duality between color and kinematics is the statement that that there exists a way to rearrange factors between
+are presented in detail in \cref{sec:bootstrap}. The duality between color and kinematics is the statement that there exists a way to rearrange factors between
 the various kinematic numerators $N_\Gamma$ such that the numerators
@@
 power counting through the inclusion of higher spin modes, and break
-manifest Lorentz invariance \cite{Square, WeinzierlBCJLagrangian,
+manifest Lorentz invariance \cite{KiermaierTalk, WeinzierlBCJLagrangian,
   Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl,
@@
 \begin{equation}
-\label{eq:ZMLagrangian}
+%\label{eq:ZMLagrangian}
 \mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2
@@
 and the cubic $\mathcal{N}=4$ sYM representation from the well-known
-$n_{2\text{box}} = n_{\text{cross-box}} = s^2t\, \atree$ \cite{Bern:1997nh}.
+$n_{2\text{box}} = n_{\text{cross-box}} = s^2t\, \atree$ \cite{BRY}.
 On the other hand, we use the methods of Ref.~\cite{Carrasco:2023qgz}
